### 2016-01-29 bb_issuers.Rnw
first commit

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
#dev.off();
#library(knitr); knit2pdf('bb_issuers.Rnw', texi2dvi='texi2dvi'); file.remove(paste("bb_issuers",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists

#load("tmpfiles/bb_issuersALL.Rdata")
reload_data = 1

# Then to make it into Word: 
# pandoc -s bb_issuers.tex --bibliography=bibliography.bib --number-sections --reference-links -o wordfilename.docx

generate_all_data = 0 # set this to 1 if the data need to be re-generated from the csv's even though they already exist as .Rdata. 
# TIME ALIGNMENT IS KEY, SO WE HAVE A SEPARATE PART OF THE CODE FOR THIS
time_align_all_data = 0
# Some basic data generation that we need across events
rerun_buyback_data_code <- 0
rerun_issuers_data_code <- 0
# If we generate the cross-events data again
get_crossevent_data <- 0 # Old stuff, not used for now
# report_code is only customized to change the "high U-index" and "low U-index" companies, nothing else. Everything else is done in report_data.R
rerun_buyback_report_code <- 0
rerun_issuers_report_code <- 0
# All the RNW data
generate_rnw_data = 0

source("lib_helpers.R")
source("latex_code.R")
source("dataset/indices_and_factors/ff_industries_sic.R")
source("business_data_clean.R")
source("Paper_global_parameters.R")

if (generate_rnw_data == 1){
  source("bb_issuers.R")
}  else{
  if (reload_data)
    load("tmpfiles/bb_issuersALL.Rdata")
  source("lib_helpers.R") 
  source("latex_code.R")
  source("dataset/indices_and_factors/ff_industries_sic.R")
  source("business_data_clean.R")
  source("Paper_global_parameters.R")
}

firstyear = as.character(format(FirstTrade,"%Y"))
lastyear = as.character(format(Last,"%Y"))

# use comma for 1000s
knit_hooks$set(inline = function(x) {
  if(is.numeric(x)){
    return(prettyNum(x, big.mark=","))
  }else{
    return(x)
  }
})

@

%<<  Data loading, eval = TRUE,
\documentclass[12pt]{article}

% DEFAULT PACKAGE SETUP
\usepackage{setspace,graphicx,epstopdf,amsmath,amsfonts,amssymb,amsthm,versionPO}
\usepackage{marginnote,datetime,enumitem,subfigure,rotating,fancyvrb,graphics,siunitx}
\usepackage{capt-of,pdflscape}
\usepackage{hyperref,float}
\usepackage[longnamesfirst]{natbib}
\usepackage{booktabs}% http://ctan.org/pkg/booktabs

\usdate

%\usepackage[dvipsnames]{xcolor} % Refer to colors by name
%\usepackage[colorlinks=true,urlcolor=blue,linkcolor=Green,citecolor=RedViolet]{hyperref}           
%\usepackage{xcolor}
%\usepackage{colortbl}
%\usepackage{changepage}
%\usepackage{adjustbox}
%\usepackage{multirow}
%\usepackage{longtable}

% These next lines allow including or excluding different versions of text
% using versionPO.sty

\excludeversion{notes}  	% Include notes?
\includeversion{links}          % Turn hyperlinks on?

% Turn off hyperlinking if links is excluded
\iflinks{}{\hypersetup{draft=true}}

% Notes options
\ifnotes{%
\usepackage[margin=1in,paperwidth=10in,right=2.5in]{geometry}%
\usepackage[textwidth=1.4in,shadow,colorinlistoftodos]{todonotes}%
}{%
\usepackage[margin=1in]{geometry}%
\usepackage[disable]{todonotes}%
}

% Allow todonotes inside footnotes without blowing up LaTeX
% Next command works but now notes can overlap. Instead, we'll define 
% a special footnote note command that performs this redefinition.
%\renewcommand{\marginpar}{\marginnote}%

% Save original definition of \marginpar
\let\oldmarginpar\marginpar

% Workaround for todonotes problem with natbib (To Do list title comes out wrong)
\makeatletter\let\chapter\@undefined\makeatother % Undefine \chapter for todonotes

% Define note commands
\newcommand{\smalltodo}[2][] {\todo[caption={#2}, size=\scriptsize, fancyline, #1] {\begin{spacing}{.5}#2\end{spacing}}}
\newcommand{\rhs}[2][]{\smalltodo[color=green!30,#1]{{\bf RS:} #2}}
\newcommand{\rhsnolist}[2][]{\smalltodo[nolist,color=green!30,#1]{{\bf RS:} #2}}
\newcommand{\rhsfn}[2][]{%  To be used in footnotes (and in floats)
\renewcommand{\marginpar}{\marginnote}%
\smalltodo[color=green!30,#1]{{\bf RS:} #2}%
\renewcommand{\marginpar}{\oldmarginpar}}
%\newcommand{\textnote}[1]{\ifnotes{{\noindent\color{red}#1}}{}}
\newcommand{\textnote}[1]{\ifnotes{{\colorbox{yellow}{{\color{red}#1}}}}{}}

% Command to start a new page, starting on odd-numbered page if twoside option 
% is selected above
\newcommand{\clearRHS}{\clearpage\thispagestyle{empty}\cleardoublepage\thispagestyle{plain}}

% Number paragraphs and subparagraphs and include them in TOC
\setcounter{tocdepth}{2}

% JFE-specific includes:

\usepackage{indentfirst} % Indent first sentence of a new section.
\usepackage{jfe}          % JFE-specific formatting of sections, etc.
\usepackage[labelfont=bf]{caption} % bold captions

\newtheorem{theorem}{Theorem}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{proposition}{Proposition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}
\newtheorem{condition}{Condition}

\begin{document}

%Blind title page
\begin{titlepage}
\begin{center}
%  \centering
\vskip 60pt
\LARGE Share Buyback and Equity Issue Anomalies Revisited \par
\vskip 1.5em
\normalsize  \today
\noindent \\ 
\begin{abstract}
\noindent We re-examine the behavior of stock returns after share buyback and equity issuance announcements using the five-factor model proposed by \cite{FamaFrench2015a}. We confirm the findings of \cite{FamaFrench2015b} that the equity issue anomaly, i.e., the fact that equity issues are followed by negative long-term excess returns, disappears after replacing the \cite{FamaFrench1993} three-factor model with the five-factor model. However, long term positive excess returns after buyback announcements, first reported by Ikenberrry, Lakonishok and Vermaelen (1995), remain economically and statistically significant. Moreover, the Undervaluation Index proposed by \cite{PeyerVermaelen2009} remains a useful proxy for the likelihood that the buyback is driven by undervaluation. The buyback anomaly is robust over time and across sectors. Firms with low correlations with the market seem to be better at market timing, which is consistent with the hypothesis that the repurchase is driven by superior company-specific information. Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by Ikenberry and Vermaelen (1996). Finally, based on these findings, we develop an enhanced Undervaluation Index that improves abnormal returns relative to the index developed by \cite{PeyerVermaelen2009}.
\end{abstract}

\vspace{2cm}

\end{center}

\medskip

\noindent \textit{JEL classification}: G35

\medskip
\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings

\end{titlepage}

\setlist{noitemsep}  % Reduce space between list items (itemize, enumerate, etc.)
%\onehalfspacing      % Use 1.5 spacing
% Use endnotes instead of footnotes - redefine \footnote command

\title{Share Buyback and Equity Issue Anomalies Revisited}%\footnotetext{}

\author{Theodoros Evgeniou$^*$, Enric Junqu\'e de Fortuny$^*$,\\
Nick Nassuphis$^{**}$, and Theo Vermaelen\thanks{INSEAD, Bd de Constance, 77300 Fontainebleau, France, phone: +33(0)1 6072 4000, $^{**}$31, St. Martin's Lane WC2N 4ER London, United Kingdom, e-mail:   \href{mailto:theodoros.evgeniou@insead.edu}{theodoros.evgeniou@insead.edu}, \href{mailto:enric.junquedefortuny@insead.edu}{enric.junquedefortuny@insead.edu},  \href{mailto:nicknassuphis@gmail.com}{nicknassuphis@gmail.com}, and \href{mailto:theo.vermaelen@insead.edu}{theo.vermaelen@insead.edu}. }}

\date{\today}              % No date for final submission

% Create title page with no page number

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\singlespacing

\maketitle

\vspace{-.2in}
\begin{abstract}
\noindent We re-examine the behavior of stock returns after share buyback and equity issuance announcements using the five-factor model proposed by \cite{FamaFrench2015a}. We confirm the findings of \cite{FamaFrench2015b} that the equity issue anomaly, i.e., the fact that equity issues are followed by negative long-term excess returns, disappears after replacing the \cite{FamaFrench1993} three-factor model with the five-factor model. However, long term positive excess returns after buyback announcements, first reported by Ikenberrry, Lakonishok and Vermaelen (1995), remain economically and statistically significant. Moreover, the Undervaluation Index proposed by \cite{PeyerVermaelen2009} remains a useful proxy for the likelihood that the buyback is driven by undervaluation. The buyback anomaly is robust over time and across sectors. Firms with low correlations with the market seem to be better at market timing, which is consistent with the hypothesis that the repurchase is driven by superior company-specific information. Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by Ikenberry and Vermaelen (1996). Finally, based on these findings, we develop an enhanced Undervaluation Index that improves abnormal returns relative to the index developed by \cite{PeyerVermaelen2009}.

\end{abstract}
\vspace{2cm}

\medskip

\noindent \textit{JEL classification}: G35

\medskip
\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings

\thispagestyle{empty}

\clearpage

\onehalfspacing
\setcounter{footnote}{0}
\renewcommand{\thefootnote}{\arabic{footnote}}
\setcounter{page}{1}

\doublespacing

\section{Introduction}
\label{sec:Introduction}

The fact that companies experience long-term positive excess returns after share buybacks and negative long term excess returns after equity issues, has been documented extensively in the academic literature.\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}. For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}  In spite of these well documented anomalies investors are not less excited today about e.g., a buyback announcement than 30 years ago: on average stock prices increase by approximately 2 to 3$\%$ when companies announce that the board of directors has approved a buyback program. Moreover, we find very few funds that specialize in exploiting these anomalies.\footnote{  For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA. The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization. We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} The fact that these anomalies have not generated a significant response from investors and asset management firms is somewhat surprising considering that other anomalies have disappeared after being documented in academic research~\citep{McLean2015}. What makes these capital structure anomalies different so that they stand the test of time?

One straightforward explanation is that they are not really anomalous returns but compensation for risk. Excess returns in previous research are calculated using the \cite{FamaFrench1993} three-factor model or the Carhart (1997) 4-factor model as benchmarks. However, \cite{FamaFrench2015b} argue that the buyback and equity issue anomalies do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns. This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns (Novy-Marx (2013)). If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research. Note, however, that \cite{FamaFrench2015b} do not exactly replicate the papers that first reported the anomalies. First, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date as e.g., \cite{PeyerVermaelen2009}. For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization (Stephens and Weisbach (1998)). Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues). The part of their sample where net equity issues are positive is defined as the ``buyback sample''. But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations. Moreover the idea of pooling buybacks and equity issues in ``net issues'' assumes that the decision to issue equity is simply the mirror of buying back shares. However, issuing stock to new investors is not the same as buying back stock from ``old'' selling investors. In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only takes advantage of selling shareholders who leave the firm. In this paper we re-examine the anomaly using the \cite{FamaFrench2015a} model but use announcement dates and separate buyback announcements and equity announcements.

A second possible reason for the funds' lack of interest in the buyback anomaly is that event studies aggregate returns over a very long horizon. The fact that buying shares after a buyback announcement generates positive excess returns during for example 1990-2014 does not mean that, if one starts a fund in 2016, one can expect to beat the market during the next 3 years. In other words, the anomaly may be time dependent, and investor patience may not extend beyond 3 years. Moreover, because of the growth of institutional investors and the reduction in trading costs markets may have become more efficient in recent years as argued by \cite{FuHuang2015}. The anomaly may also be industry-specific so that an investor who follows a buyback strategy may end up with a highly undiversified portfolio.

Finally, the long-term event studies do not give much guidance about when to sell after a buyback or cover after shorting an equity issue. Trading strategies, such as $M\&A$ arbitrage (\cite{MitchellPulvino2001}), often have ``natural'' exit decision points (e.g., at $M\&A$ deal completion or termination), but the literature does not provide clear guidance about when to exit a buyback position.  Empirical studies tend to show that, on average, excess returns continue for up to 3 or 4 years after a buyback authorization, but there is no reason why such a horizon is optimal. The passive nature of the strategy may also give the impression that the strategy is too simple to justify management fees. One straightforward ``early'' selling strategy that we study is to combine the buyback and equity issuance anomalies by selling buyback stocks after the firm announces an equity issue. Note that the fact that equity issues in general are followed by negative abnormal returns does not necessarily imply that equity issues after buybacks should generate the same result. Given our focus on buybacks and equity issuance, we do not study other possible exit signals, such as missing analysts' estimates (e.g., \cite{PeyerVermaelen2009}), take over bids (e.g., \cite{Linetal2014}), or other company events.

The purpose of this paper is to explore these concerns by studying the robustness of the buybacks and issuance anomalies over the 30 year period starting in January \Sexpr{firstyear} and ending in December \Sexpr{lastyear}, using the \cite{FamaFrench2015a} five-factor model. Although there are other models of market equilibrium proposed to explain excess returns after buyback authorizations (i.e. \cite{Linetal2014}) our focus is on the \cite{FamaFrench2015a} challenge. We are also agnostic on the source of misvaluation, e.g., undervaluing cash flows or overestimating risk (\cite{GrullonMichaely2004}). We confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant. Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio. The interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive.

We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns and that the anomaly does not disappear if we exclude specific industries.  Moreover, the predictive capacity can be significantly enhanced if we incorporate two additional indicators that are expected to be correlated with misvaluation. First,  idiosyncratic risk, which measures to what extent stock prices are driven by company-specific information. Unlike \cite{Ang2006}, who find a negative relation between idiosyncratic volatility and future returns, and \cite{FamaFrench2015b}, who show similar evidence for small firms, we find  
a positive relation for buyback stocks. This is consistent with \cite{Stambaugh2015} who find a positive relation for undervalued\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  stocks. The second indicator to be correlated with misvaluation is  volatility. The argument is that a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks (\cite{IkenberryVermaelen1996}). Combining these new measures with the Peyer-Vermaelen (2009) Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.

This paper is organized as follows. In section 2 we describe our data. In section 3 we test whether buyback and equity issue anomalies survive when we use the \cite{FamaFrench2015a} five-factor model. We also compare firms that buy back stock and issue equity within 48 months of a buyback announcement with firms that do not issue stock subsequently. In section 4 we test whether the buyback anomaly is robust across time, investment horizon and industry. In section 5 we test whether idiosyncratic risk as well as volatility can improve the predictability of excess returns, relative to simply using the Undervaluation Index proposed by \cite{PeyerVermaelen2009}. Section 6 concludes.

\section{Data}
\label{sec:Data}

Our sample spans the period from January \Sexpr{firstyear} to December \Sexpr{lastyear}. We start in \Sexpr{firstyear} as SDC's coverage is poor before that year. We stop in \Sexpr{lastyear}, the last year all CRSP and Compustat data were available. We retrieved buyback authorization announcements and announcements of Secondary Equity Offerings (SEO's) from the Securities Data Corporation (SDC) database. Daily and monthly returns, pre-announcement daily closing prices and market capitalization data were taken from CRSP. Book value of equity (BE) was taken from Compustat. The Fama-French factors and breakpoints were obtained from Kenneth French's website.

For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request. An interactive online tool to explore data variations and robustness analyses of all results in this paper is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both. Finally, we removed the following events: no CRSP returns available (\Sexpr{cleanup_bb$get_crsp$NOPERMNO_remove + cleanup_bb$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_bb$compustat$NO_GVKEY_remove + cleanup_bb$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).  Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(BUYBACK_DATA$finance_Size_used)}  events).\footnote{We are using the industries from Kenneth French's Website. The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799). The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms. The average percent of share authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).

For the issuers, we started with \Sexpr{cleanup_iss$Standardise$SDC_initial_data} events from SDC, filtered to exclude rights issues, pure secondary offerings where existing shareholders sell shares without generating proceeds for the company,  issues made by non-U.S. firms or in non-U.S. markets, issues made by closed-end funds or unit investment trusts, as well as block trades, accelerated offers and best efforts. We removed all SDC events for which either the event date (\Sexpr{cleanup_iss$Standardise$SDC_NODATE} events) or the CUSIP (\Sexpr{cleanup_iss$Standardise$SDC_NOCUSIP} events) was missing or where we found duplicate events with mismatching information (\Sexpr{cleanup_iss$Standardise$BAD_DUPLICATES} events), a total of \Sexpr{cleanup_iss$Standardise$SDC_standardize_removal} events - given the overlap between these cases. Finally, as for the buybacks, we removed the following events: no CRSP returns available (\Sexpr{cleanup_iss$get_crsp$NOPERMNO_remove + cleanup_iss$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_iss$compustat$NO_GVKEY_remove + cleanup_iss$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_iss$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_iss$biz_clean$Penny_stock_filter} events), or  the stocks were not listed on the NYSE, Nasdaq or Amex (\Sexpr{cleanup_iss$biz_clean$major_markets_only} events). We again removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(ISSUERS_DATA$finance_Size_used)} events). Our final sample contains \Sexpr{length(cusip_iss)} issuers events made by \Sexpr{length(unique(cusip_iss))} firms. The average percent of shares issued was \Sexpr{datasummaryISS["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryISS["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{datasummaryISS["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryISS["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryISS["BE/ME", "Mean"]} (median of \Sexpr{datasummaryISS["BE/ME", "Median"]}).

Figure~\ref{fig:liveevents} shows the number of announcements per year in the sample period as well as the (standardized) level of the $S\&P$ 500. Buyback activity rises prior to stock market increases and tends to fall afterwards, especially during the financial crisis of 2008 when buyback announcements fell to a 15 year low. Note the structural decline in equity issues since 2000.

\section{Share Buybacks, Equity Issues and Abnormal Returns}
\label{sec:PastFindingsBB}

We start with revisiting past research but now using a longer time period and the five-factor model of \cite{FamaFrench2015a} to measure expected returns. In particular, we test whether buyback (equity issue) announcements are followed by significant positive (negative) long term excess returns, and if so, whether the returns can be explained by proxies for undervaluation as proposed by \cite{PeyerVermaelen2009}.

\subsection{Share buybacks and Equity Issues in Isolation }
\label{sec:AbnormalBuybacks}

Table~\ref{tbl:priorBuybacks}, Panel~A, shows long-term cumulative excess returns for various holding periods after the announcement using the Ibbotson RATS event study method. Each event month~$t$ we run cross-sectional regressions of stock returns against the factors. The intercept in the regression measures the average abnormal excess return in event month~$t$. We then accumulate these excess returns over various time horizons (up to 48 months after the event). The advantage of this method is that each event gets the same weight and that factor betas are allowed to change in event time, something that may be important as capital structure changes may signal a change in risk~\citep{GrullonMichaely2004}. The table compares the excess returns using the \cite{FamaFrench1993} three-factor model and the \cite{FamaFrench2015a} five-factor model. The results show that, although using a five-factor model lowers excess returns, the excess returns are statistically significantly positive over all investment horizons and reach \Sexpr{IRATS_table_all_bb["+48","CAR 5F"]}$\%$ after 4 years (t=\Sexpr{IRATS_table_all_bb["+48",5]}). So the buyback anomaly does not disappear when we use a five-factor model. In all the tables we also calculate cumulative excess returns in the 6 months prior to the buyback. Consistent with past research (e.g., \cite{PeyerVermaelen2009}) buyback authorization announcements are preceded by significant negative excess returns of around \Sexpr{round(IRATS_table_all_bb[reported_times[1],1],0)}$\%$. This is consistent with the hypothesis that the typical repurchase announcement is triggered by at least the perception of insiders that the stock is undervalued.

Table~\ref{tbl:priorIssuers}, Panel~A, shows the results for all equity issues, using the same methodology as in Table~\ref{tbl:priorBuybacks}, Panel~A. Our results are largely consistent with \cite{FamaFrench2015b}. Using the three-factor model, we find statistically significant long term (after 48 months) negative cumulative excess returns of \Sexpr{IRATS_table_all_iss["+48","CAR 3F"]}$\%$ (t=\Sexpr{IRATS_table_all_iss["+48",2]}). However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months. This shows that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure. Unlike buybacks, equity issues are firm commitments and announced and completed at the same point in time. Using actual shares issued (the measure used by Fama-French (1995b)) and equity announcements (our measure) should therefore produce similar results. Buyback authorization announcements on the other hand are not firm commitments and are often executed over a long period after the announcement. Actual repurchase dates thus do not correspond to announcement dates. Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(IRATS_table_all_iss[reported_times[1],1],0)}$\%$ in the 6 months prior to the equity issue. However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that these firms experienced a substantial increase in growth opportunities and issued equity to finance them. 
One critique of the \cite{ibbotson1975} RATS method is that the result may be time-specific. Indeed as every event is equally weighted the cumulative average abnormal returns are dominated by periods when there are a large number of events. So we also use the Calendar Time method where in each calendar month we form an equally-weighted portfolio of all firms that announce a buyback (or an equity issue) in the previous $t$~months. We then run a time series regression of the portfolio returns against the factors. The intercept of the regression is the average monthly excess return in the $t$~months after the event.

The results in Panel~B of Tables \ref{tbl:priorBuybacks} and  \ref{tbl:priorIssuers} are similar to Panel~A of the same tables. Abnormal returns after buybacks are smaller when the five-factor model is used but remain statistically significant over all horizons. For example, over the 48 month horizon the average monthly excess return is \Sexpr{CAL_table_all_bb["+48","CAL 5F"]}$\%$ (t=\Sexpr{CAL_table_all_bb["+48",5]}) which corresponds to \Sexpr{48*CAL_table_all_bb["+48","CAL 5F"]}$\%$ over 48 months. Note also that excess returns fall when the investment horizon increases. The largest monthly excess return (\Sexpr{CAL_table_all_bb["+1","CAL 5F"]}$\%$) is earned by the portfolio that holds buyback stocks for one month  (not reported in Table \ref{tbl:priorBuybacks})  and the smallest excess return (\Sexpr{CAL_table_all_bb["+48","CAL 5F"]}$\%$) is earned by the portfolio that picks buybacks announced during the previous 48 months. This clearly shows that forming portfolios after buybacks are completed (as is done by measuring net issues in \cite{FamaFrench2015b}) is introducing a downward bias as many repurchase programs are completed several months (sometimes years) after the buyback announcement. Waiting until the buyback is completed means missing the largest excess returns earned shortly after the buyback authorization. Finally, there are no statistically significant excess returns after equity issues, regardless whether we use the three or five-factor model.

Next we test whether the ``Undervaluation Index'' (U-index) developed by \cite{PeyerVermaelen2009} using buyback announcements from 1991 to 2002 is a robust indicator to separate companies that are buying back stock because they are undervalued from companies that repurchase shares for other reasons. We calculate the U-index as follows. Companies get a size score from 1 (large firms) to 5 (small firms) depending on the quantile of their market value of equity in the month prior to the buyback announcement. Then, we calculate the 11-months pre-announcement absolute returns of months -12 to -1 before announcement for all events and assign a score of 5 to the low returns firms and 1 to the high returns ones. Finally, companies get a book value to market value (BE/ME) score depending on the quantile of their BE/ME value of equity in the year prior to the buyback announcement, with a score of 1 to small BE/ME firms and 5 to large ones. Unlike \cite{PeyerVermaelen2009} who use all CRSP companies to define the quantile thresholds, we use the Fama-French breakpoints for prior returns the month before, ME the month before, and BE/ME the year before the event to rank the firms from 1 to 5: for example, firms falling below the $5^{th}$ BE/ME breakpoint are assigned a score of 1, while companies above the $16^{th}$ BE/ME breakpoint are assigned a score of 5.

We sum up these three scores for each firm and we then define as ``high U-index'' the firms with total score more than \Sexpr{quantile(valuation_index_bb,0.8)} and as ``low U-index'' those with total score less than \Sexpr{quantile(valuation_index_bb,0.2)}. Note that unlike \cite{PeyerVermaelen2009} we do not consider the stated reasons for the buyback in the press release, hence we define different thresholds for the high U-index and low U-index buyback firms. We end up with \Sexpr{sum(company_subset_undervalued_bb)} ``high U-index'' buyback stocks (\Sexpr{round(sum(company_subset_undervalued_bb)/length(cusip_bb)*100,2)}\% of all buyback events), and \Sexpr{sum(company_subset_overvalued_bb)} ``low U-index'' ones (\Sexpr{round(sum(company_subset_overvalued_bb)/length(cusip_bb)*100,2)}\% of all buyback events). The distribution of the U-index of all buyback events is shown in Figure~\ref{fig:undervaluationindex}.

Table~\ref{tbl:priorBuybacks}, Panel~A, shows the three-factor as well as the five-factor IRATS for high U-index and low U-index firms. The interesting conclusion is that using the five-factor model improves the predictive power of the U-index: high U-index firms earn 4 year excess returns of \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR5F"]}$\%$ (t=\Sexpr{IRATS_table_all_bb_undervaluation["+48",8]}) while low U-index firms only earn \Sexpr{IRATS_table_all_bb_undervaluation["+48","O:CAR5F"]}$\%$ (t=\Sexpr{IRATS_table_all_bb_undervaluation["+48",11]}), hence \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR5F"] - IRATS_table_all_bb_undervaluation["+48","O:CAR5F"]}$\%$ less than the high U-index ones. Starting from 12 months after the announcement, high U-index firms always beat low U-index firms. When we use the three-factor model, we find similar conclusions, but the results are weaker. For example after 48 months the high U-index firms now earn excess returns of \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR3F"]}$\%$, which is only \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR3F"] - IRATS_table_all_bb_undervaluation["+48","O:CAR3F"]}$\%$ higher than the low-U-index firms. Note that, consistent with \cite{PeyerVermaelen2009} the low U-index buyback stocks earn significant positive excess returns too. It is difficult to find a portfolio of buyback stocks that under-performs in the long run. So the term ``overvaluation'' should be interpreted with caution. The Undervaluation Index is a proxy for the likelihood that the buyback is driven by undervaluation. It does not imply that low U-index firms are overvalued. It means that for these firms the buyback is less likely to be driven by undervaluation, but by other reasons such as managing capital structure, avoiding dilution from executive stock options etc.

Table~\ref{tbl:priorBuybacks}, Panel~B, shows that this conclusion holds when we use the Calendar Time method. Regardless of the horizon, high U-index stocks almost always beat low U-index stocks. As in the case of IRATS, the five-factor model improves the selectivity of the Undervaluation Index: low U-index now no longer earn significant excess returns after 48 months.

Figure~\ref{fig:pastall} summarizes the IRATS results in more detail by showing the cumulative abnormal returns during the 6 month pre and 48 month post event period, using the five-factor model. Results are shown for the total sample of buybacks and equity issues, as well as for high and low U-index buyback samples.

\subsection{Buybacks followed by Equity Issues}
\label{sec:Eventexit}

The results so far show that firms that repurchase shares are good at market timing, in particular the small beaten up value stocks. On the other hand the average equity issuer does not seem to be driven by market timing in general. However, firms that are good at market timing when buying back undervalued stock are perhaps also good at recognizing when their shares are overvalued. Note that successful market timing requires two managerial characteristics: ability to time the market as well as willingness, i.e., accepting the idea that using superior information to benefit long term shareholders at the expense of other shareholders is the ``right'' thing to do.

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
SEO_exit_days = sapply(which(BUYBACK_DATA$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(BUYBACK_DATA$DATASET$SDC$Otherlater[i]) - event.date_bb[i])
BB_exit_days = sapply(which(ISSUERS_DATA$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(ISSUERS_DATA$DATASET$SDC$Otherlater[i]) - event.date_iss[i])
@

During our sample period (\Sexpr{firstyear}-\Sexpr{lastyear}) \Sexpr{length(unique(intersect(cusip_bb,cusip_iss)))} companies in our data set both announced buybacks and issued equity, but in only \Sexpr{length(SEO_exit_days)}  cases a company announced a subsequent equity issue within 4 years after the buyback announcement. We now compute the cumulative excess returns for these firms under two scenarios. First, the ``no exit'' scenario, where we hold the stock for 48 months after the buyback announcement. Second, the ``exit'' scenario, where we sell the shares as soon as the company announces an equity issue.

Of the \Sexpr{length(SEO_exit_days)} such events, \Sexpr{sum(abs(SEO_exit_days) < 1*365)} happen within 1 year from the buyback announcement, \Sexpr{sum(abs(SEO_exit_days) < 2*365)} happen within 2 years and \Sexpr{sum(abs(SEO_exit_days) < 3*365)} happen within 3 years. Note that this grouping of the events is done with hindsight: it is not possible to know at the time of the buyback announcement whether there will be a subsequent SEO or not. We are simply asking the question whether those firms that announced a buyback when they appeared undervalued issued equity when they were overvalued. Figure~\ref{fig:BBISSevents} shows the percentage of repurchasing firms that announced an equity issue within 48 months. The average percentage is \Sexpr{round(mean(BB_with_ISS_later_total),1)}$\%$ and there are only \Sexpr{sum(BB_with_ISS_later_total > 10)} years (1989 and 1990) where the percentage is larger than $10\%$.

Table~\ref{tbl:BBISSexit}  shows that repurchasing firms that issued stock within 48 months after the buyback are remarkable timers. Long-term excess returns after 4 years are \Sexpr{Exit_on_SEO_Abn_table["+48",4]}$\%$ (t=\Sexpr{Exit_on_SEO_Abn_table["+48",5]}), more than four times as large as for the overwhelming majority of firms that do not issue stock subsequently. These results are graphically displayed in Figure~\ref{fig:BBISSexit} (Panel~A). Repurchases by firms that do not issue equity in the next 48 months are followed by long term excess returns of only \Sexpr{Exit_on_SEO_Abn_table["+48",1]}$\%$. One interpretation is that these firms believe they are undervalued but as long as they remain undervalued they do not think it is appropriate to issue stock.

The Calendar Method results in Panel B of Table~\ref{tbl:BBISSexit} show a relatively large drop of the excess returns over time (e.g., from \Sexpr{Exit_on_SEO_Abn_table_cal["+12",4]}$\%$ after 12 months to \Sexpr{Exit_on_SEO_Abn_table_cal["+48",4]}$\%$ after 48 months) indicating potential benefits of exiting a buyback position when there is a subsequent issue. Figure  \ref{fig:BBISSexit} (Panel~B) shows the benefits of exiting early. The figure shows a strategy with hindsight where, starting in \Sexpr{firstyear}, we invest in an equally weighted portfolio of only firms that announced a buyback and subsequently issued equity within the 48 months after the buyback announcement. The dashed line shows the cumulative excess return if we sold the stock whenever the firm issued shares within 48 months (the exit strategy). The solid line shows the cumulative excess returns if we sold 48 months after the buyback announcement (the no exit case). The investor who had followed the exit strategy would have earned (after 30 years) a cumulative excess return of \Sexpr{round(tail(100*cumsum(BB_ISS_Exit_Hedged),1),1)}$\%$, significantly larger than the \Sexpr{round(tail(100*cumsum(BB_ISS_NoExit_Hedged),1),1)}$\%$ of a buy hold for 48 months strategy. Note, however, that because very few firms that buy back stock issue equity within 48 months,  a strategy ``without hindsight'' where one bought all companies after a buyback and sold only those after a subsequent equity issue would not substantially increase excess returns.

Table~\ref{tbl:BBISSexitAfter} shows the long run excess returns after the announcement of an equity issue for two samples. The first sample (After a Buyback) shows the excess returns for issues for which in the previous 48 months the firm announced a buyback.  The second sample (No Prior Buyback) shows the excess returns for all other issue announcements.  The fact that excess returns are not significantly different from zero for the post-buyback issuers agrees with the intuition of Figure~\ref{fig:BBISSexit}: exiting when there is a subsequent equity issue is the right thing to do for the long-term buyback investor.

\section{How robust is the buyback  anomaly?}
\label{sec:robust}

The results so far are based on a sample of all buyback and equity announcements over a thirty-year period. As the equity issue anomaly does not survive the \cite{FamaFrench2015a} five-factor model, the remainder of the paper focuses on better understanding the buyback anomaly and uses the five-factor model as a benchmark.\footnote{All analyses below are also done for equity announcements. However, in agreement with the results in Section \ref{sec:AbnormalBuybacks}, we find no consistent/robust results for issuers. All issuers results are available upon request.}  The purpose of this section is to test the robustness of this anomaly: has it become less important over time because markets have become more efficient? How sensitive is it to the length of the investment period? Could the anomaly be industry-specific?

\subsection{Robustness across time periods and investment horizons}
\label{sec:PastFindingsTime}

Table~\ref{tbl:PastFindingsTimeBB} shows excess returns, using both the IRATS and Calendar Time method for different time periods. We consider time periods, which overlap to some extent with past research (Ikenberry, Lakonishok, and Vermaelen 1995, Peyer and Vermaelen 2009, Manconi, Peyer, and Vermaelen 2015 and Fu and Huang 2015): 1985-1990; 1991-2000; 2001-2014 and 2008-2014. The last period was chosen to incorporate the financial crisis and to test whether indeed markets have become more efficient in recent years, or whether managers have been discouraged from market timing by the obvious mistakes that were made by buying back shares before a major financial crisis.

Table~\ref{tbl:PastFindingsTimeBB} shows that, regardless of the time period chosen or the method to calculate excess returns, the buyback anomaly remains economically and statistically significant and there is no clear time trend in the data that suggests that markets have become more efficient over time. For example, although the 2001-2014 period shows smaller timing ability than the 1990-2000 period, excess returns in the 2008-2014 period are as large as in 1991-2000 period: approximately \Sexpr{BBtable_time["+48",22]}$\%$  after 4 years using IRATS or \Sexpr{BBtable_time_cal["+48",22]}$\%$ per month (\Sexpr{48*BBtable_time_cal["+48",22]}$\%$ after 4 years) when we use the Calendar Time method. There is one exception to the consistency between the IRATS and the Calendar Time results: in the period of 1991-2000, the IRATS method generates excess returns after 48 months of \Sexpr{BBtable_time["+48",10]}$\%$ (t=\Sexpr{BBtable_time["+48",11]}) but the Calendar Time method produces statistically insignificant excess returns of \Sexpr{BBtable_time_cal["+48",10]}$\%$ per month. This result appears to also be inconsistent with \cite{PeyerVermaelen2009}. However, if one includes the financial sector firms or considers the three-factor model, as \cite{PeyerVermaelen2009} do, the calendar method abnormal returns do become significant.\footnote{Details available upon request.}

Table~\ref{tbl:PastFindingsTimeUnderBB} re-examines whether the U-index of \cite{PeyerVermaelen2009} predicts the five factor excess returns for different time periods. The first two columns show the IRATS results and the last two columns show the Calendar Time results. Regardless of the method to compute excess returns, the U-index is an excellent predictor: except for the very short 1985-1990 period, buybacks announced by high U-index firms are followed by significantly larger returns than buybacks announced by low U-index firms.  There is also no evidence that the U-index is losing its predictive power over time: for example, in the 2001-2014 period the difference between high U-index and low index firms (after 48 months, IRATS) was \Sexpr{BBtable_undertime["+48",31]-BBtable_undertime["+48",34]}$\%$, while in the most recent 2008-2014 period high U-index firms had \Sexpr{BBtable_undertime["+48",43]-BBtable_undertime["+48",46]}$\%$ larger abnormal returns than low U-index firms.

To further study the robustness of the buyback anomaly over time, we simulate a portfolio investment strategy starting in \Sexpr{firstyear}. The strategy uses past data to estimate the factor betas and measures the abnormal returns of buyback portfolios over different investment horizons. While this is not an accurate measure of the returns of a buyback fund - as we do not consider transaction costs, turnover issues, or other operational issues (see for example \cite{MitchellPulvino2001}) - it provides us with an estimate of what would have happened to an investor who starts investing in \Sexpr{firstyear} in an equally weighted portfolio of buyback stocks and holds them over various horizons.

<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
tmp = pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))
ri = remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)
expost_betas = beta_expost(ri,Risk_Factors_Monthly[,pnl_hedge_factors])
ri = remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_12M,min_date=FirstTrade)
expost_betas_unhedged = beta_expost(ri,Risk_Factors_Monthly[,pnl_hedge_factors])
@

Specifically, we consider the following trading strategy: construct the first day of every month an equally weighted portfolio of all companies that announced buybacks during the previous $N$ months, for a given holding period of length $N$ (which can be chosen). Thus, once a company makes an announcement, it enters the portfolio on the first day of the following month and remains there for $N$ months. Note that the portfolio is re-balanced (the first day of) each month. This ``unhedged'' strategy generates a time series of returns. Each month (when we re-balance the portfolio) we also use the previous \Sexpr{hedge_months}  monthly returns of this time series    to calculate the (portfolio level) time series betas of all five factors. This allows an investor to determine the betas for the factor risks using data available at the time of portfolio formation.

Note that, as there is no hindsight and all betas are estimated every month using past data, the portfolio used to estimate the betas may consist of firms that are different from those of the (newly created) portfolio that is hedged - as we do not know when companies will announce a buyback. On the other hand, note that unlike this strategy, both the IRATs and calendar event study results use hindsight to estimate risk. However, despite using pre-portfolio formation data to estimate the betas, the returns of the overall strategy have very low betas with the five factors.\footnote{For example for the $N =12$ months holding period discussed below, the betas for the five factors Market, SMB, HML, RMW, and CMA are respectively \Sexpr{round(expost_betas[2,1],3)}, \Sexpr{round(expost_betas[3,1],3)}, \Sexpr{round(expost_betas[4,1],3)}, \Sexpr{round(expost_betas[5,1],3)} and \Sexpr{round(expost_betas[6,1],3)}. The corresponding betas for the ``unhedged'' strategy are \Sexpr{round(expost_betas_unhedged[2,1],3)}, \Sexpr{round(expost_betas_unhedged[3,1],3)}, \Sexpr{round(expost_betas_unhedged[4,1],3)}, \Sexpr{round(expost_betas_unhedged[5,1],3)} and \Sexpr{round(expost_betas_unhedged[6,1],3)}. This also indicates that the returns shown in Figure~\ref{fig:ReturnsBB} and Table~\ref{tbl:allhedgedBB} are close to excess returns. Getting pure excess returns in practice requires more detailed hedging (without hindsight). }

<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade))
months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all3mshort_risk_factors,min_date=FirstTrade))
months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all6mshort_risk_factors,min_date=FirstTrade))
months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))
months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all24mshort_risk_factors,min_date=FirstTrade))
months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all36mshort_risk_factors,min_date=FirstTrade))
months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all48mshort_risk_factors,min_date=FirstTrade))

@

We report the returns of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns. Specifically, at the end of \Sexpr{lastyear} the cumulative returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$. This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer. However, Figure~\ref{fig:ReturnsBB} allows us to verify that the excess returns are not simply the result of outperformance during a particular time period. Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.  The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}. In only one year (\Sexpr{rownames(tmp)[which.min(tmp[,13])]}) the strategy generates an abnormal loss larger than \Sexpr{round(abs(sort(tmp[,13])[2]),1)}$\%$.

\subsection{Robustness across Sectors}
\label{sec:AllIndustries}

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
@

Figure~\ref{fig:industryeventsBB} shows the number of buyback events per industry in our sample. The software and semiconductor industries are the most active repurchasers. They also tend to be the most volatile industries, industries where disagreement about fundamental value is large - as we report later in Table \ref{tbl:industriesR2Vol}. Table~\ref{tbl:IndustriesBB} shows the IRATS cumulative abnormal returns and Table~\ref{tbl:IndustriesBB_cal} the Calendar Time method monthly average abnormal returns when we remove one industry at the time, for the top most frequent buyback industries (those for which there are at least \Sexpr{min_industry_sampleBB} events in our sample).  Note from Table~\ref{tbl:priorBuybacks} that, after 48 months, the cumulative abnormal returns for the whole sample (using IRATS) is \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ and the monthly average excess return (Calendar Time) is \Sexpr{round(CAL_table_all_bb["+48","CAL 5F"],2)}$\%$.  So the larger the difference between these numbers and the corresponding numbers for the industry indicated in Tables~\ref{tbl:IndustriesBB} and \ref{tbl:IndustriesBB_cal}, the larger the excess returns in the industry removed. For example, using IRATS, deleting the software industry lowers the CAR from \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ to \Sexpr{round(tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$, a \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"] - tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$ decline. This is the largest decline in Table~\ref{tbl:IndustriesBB}, indicating that buybacks in the software industry are followed by the largest excess returns. However, deleting Retail, Insurance, Machinery, Meals and especially Chemical stocks improves the excess returns.  Of course, these differences could be explained by differences in U-index levels or other indicators of the likelihood of misvaluation, a topic we turn to next.

\section{Enhancing the U-index: \\
Idiosyncratic Risk and Volatility}
\label{sec:infoassymetry}

\subsection{Idiosyncratic Risk}
\label{sec:idiorisk}

The main ``theory'' behind the buyback anomaly is that firms may have superior {\it company-specific} information. Such situations are more likely in industries or companies where the value is driven less by market wide factors, i.e., by highly ``idiosyncratic'' companies.  To test this hypothesis, for each event we measure the five-factor regression $R^2$ using the 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month, or using the idiosyncratic volatility as in \cite{Ang2006}, leads to the same conclusions - results available upon request. However, as we want to differentiate between ``idiosyncratic'' companies and ``high volatility'' ones, to consider both the effects of company specific information and of the option value of a buyback announcement, we separately study the relations with $R^2$ and volatility. See also \cite{Lietal2014} for a discussion on this issue.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$. We also define the idiosyncratic score of a firm to be the percentile of its $1-R^2$ across all CRSP firms that month. Note that we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only. Table~\ref{tbl:industriesR2Vol}, columns (1) and (2) show the percentage of high and low idiosyncratic risk events across all industries for which we have at least 100 buyback events in our sample. The healthcare industry has the largest percentage of firms classified as ``high idiosyncratic'', while cyclical industries such as steel, construction and chemicals contain a large number of ``low idiosyncratic'' firms.

Figure~\ref{fig:badpreviousR2}  shows the results of a strategy similar to the strategy of Figure~\ref{fig:ReturnsBB} (Panel~B): starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous N months and hold the stock for $N$ months. The graph shows two strategies, one for a short holding period ($N=12$) and one for a very long holding period ($N=48$). In both cases the excess returns for high idiosyncratic companies are higher.  Specifically, high idiosyncratic companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy. These excess returns are higher than the \Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged48m),1),1)}$\%$) of the corresponding low idiosyncratic sample.

Table~\ref{tbl:IdiosyncraticunderBB}  confirms this result in a more systematic way. It shows the IRATS and Calendar Time abnormal returns for high and low idiosyncratic buyback events-companies. Focusing on IRATS, high idiosyncratic buyback stocks earn \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$  after 48 months, more than three times the excess returns of the low idiosyncratic announcements. The results using the Calendar Time method confirm these findings.

Table~\ref{tbl:IdiosyncraticunderBB} also tests whether adjusting for idiosyncratic risk improves the predictive power of the U-index. Regardless of the time horizon and the event study method, the U-index works only for idiosyncratic companies. After 48 months, based on the IRATS methods, high U-index high idiosyncratic companies earn \Sexpr{R2_IRATStable_underBB["+48","High Idiosync.: U CAR"]}$\%$ (t=\Sexpr{R2_IRATStable_underBB["+48",8]}). Low idiosyncratic high U-index firms have only an insignificant excess return of \Sexpr{R2_IRATStable_underBB["+48",1]}$\%$ (t=\Sexpr{R2_IRATStable_underBB["+48",2]}), while for low idiosyncratic firms the low U-index IRATS excess returns are significant (\Sexpr{R2_IRATStable_underBB["+48",4]}$\%$, t=\Sexpr{R2_IRATStable_underBB["+48",5]}).  Note however that we only have few events in low idiosyncratic, high U-index (\Sexpr{R2_IRATStable_underBB["Observations",1]} events) and high idiosyncratic, low U-index (\Sexpr{R2_IRATStable_underBB["Observations",10]} events) categories. The Calendar Time results provide the same picture: only for the high idiosyncratic, high U-index firms we obtain significant (t=\Sexpr{R2_IRATStable_underBB_cal["+48",8]}) monthly excess returns of \Sexpr{R2_IRATStable_underBB_cal["+48",7]}$\%$. The high idiosyncratic and low U-index firms have  non-significant (t=\Sexpr{R2_IRATStable_underBB_cal["+48",11]}) monthly excess returns of \Sexpr{R2_IRATStable_underBB_cal["+48",10]}$\%$.

Figure \ref{fig:pastallidio} summarizes our results.  It shows the CAR based on IRATS (Panel~A for the high U-index firms, B for the low U-index firms, and C for all firms). In agreement with Table~\ref{tbl:IdiosyncraticunderBB}, the striking result (Panel~A) is that the U-index is not a good predictor of excess returns for stocks largely driven by market factors (low idiosyncratic firms). This is strong evidence that excess returns after buybacks are driven by superior company-specific information of the management.

The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \cite{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns. This is commonly referred to as the volatility puzzle. However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks. Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing. Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks.  Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).

\subsection{Volatility}
\label{sec:volbuybacks}

The announcement of a buyback program is not a firm commitment, but an option to buy back stock. Ikenberry and Vermaelen (1996) model this flexibility as an exchange option in which the market price of the stock is exchanged for the true value of the stock. They predict that, as with all options, the value increases with the volatility. The intuition is that the larger the volatility, the larger the probability that the market price may deviate from the true value. This enhances the timing ability of the manager-insider. Hence, perhaps total volatility is a better prediction of excess returns than idiosyncratic volatility or the U-index.  Or perhaps volatility can be an additional, next to the U-index and idiosyncratic volatility, indicator of the likelihood that the buyback is driven by undervaluation.

For each event we measure their pre-announce returns volatility with the standard deviation of their daily stock returns over the 6 months prior to the buyback announcement. We define two types of events: ``low volatility'' and ``high volatility'' events, depending on whether volatility was in the top or bottom \Sexpr{round(100*quantile_VOL,2)}$\%$ of the volatilities of all CRSP companies, as we did for $R^2$ above:
each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' daily returns volatilities. We also define the volatility score of a firm to be the percentile of its volatility across all CRSP firms that month. Note that, again, we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only.  In total we have \Sexpr{length(High_VOL_eventsBB)} ``high volatility'' buybacks-events and \Sexpr{length(Low_VOL_eventsBB)} ``low volatility'' ones. Table~\ref{tbl:industriesR2Vol}, columns (3) and (4)  show the percentage of high and low volatility events across all industries for which we have at least 100 buyback events in our sample.

Figure~\ref{fig:badpreviousVOL} shows the results of a strategy similar to the strategy of Figure~\ref{fig:ReturnsBB}: starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months. The graph shows two strategies, one for a short holding period ($N=12$) and one for a very long holding period ($N=48$). In both cases the excess returns for high volatility companies is higher. Specifically, high volatility companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy, which are higher than the \Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged48m),1),1)}$\%$) of the corresponding low volatility sample.

Table~\ref{tbl:VOLunderBB} confirms this result in a more systematic way. It shows the IRATS and Calendar Time abnormal returns for high and low volatility buybacks events-companies. Focusing on IRATS, high volatility buyback stocks earn \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$  after 48 months, while low volatility events have non significant abnormal returns for any period. The results using the Calendar Time method confirm these findings.

Table~\ref{tbl:VOLunderBB} also tests whether the U-index is valid for high volatility events, as well as whether adjusting for volatility improves the predictive power of the U-index. Regardless of the time horizon and the event study method, the U-index works for high volatile companies. After 48 months, based on the IRATS methods, high U-index high volatility companies earn \Sexpr{VOL_IRATStable_underBB["+48","High Vol: U CAR"]}$\%$ (t = \Sexpr{VOL_IRATStable_underBB["+48",8]}). Low U-index high volatility companies earn \Sexpr{VOL_IRATStable_underBB["+48",10]}$\%$ (t = \Sexpr{VOL_IRATStable_underBB["+48",11]}). The Calendar Time results provide the same picture. Figure~\ref{fig:badpreviousVOL} summarizes the results for the total sample and the high and low U-index sample. The main difference with Figure~\ref{fig:badpreviousR2} is that now also low volatility/high U-index firms earn significant excess returns of 15.3$\%$ after 48 months.

\subsection{An Enhanced U-index for Buybacks}
\label{sec:newindex}

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
EU_index_features = scrub(cbind(BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA$DATASET$SDC$pre_vol,BUYBACK_DATA$Valuation_Index))
colnames(EU_index_features) <- c("Idiosyncratic Score", "Volatility Score", "U-Index Score")
Under_IdioBB_cor = cor(EU_index_features)
@

Table~\ref{tbl:underidioallBB} shows how the high/low U-index  low/high idiosyncratic risk, and low/high volatility buyback events overlap, while Table~\ref{tbl:underidioallBBcor} shows the correlations between the idiosyncratic, volatility, and U-index scores. Overall we see that although high U-index firms tend to have high idiosyncratic risk and highly volatility, and high idiosyncratic risk firms tend to also have high volatility the overlap is not very high: for example from Table~\ref{tbl:underidioallBB} we learn that  only \Sexpr{round(Under_IdioBB["High Vol.","H Idiosync."],1)}$\%$ of the high volatility stocks that are classified as having either high or low idiosyncratic risk - note that we only consider the  \Sexpr{round(100*quantile_R2,2)}$\%$ tails - have high idiosyncratic risk. From Table~\ref{tbl:underidioallBBcor} we infer that the correlation between idiosyncratic risk and volatility is only \Sexpr{round(Under_IdioBB_cor["Volatility Score","Idiosyncratic Score"]*100,1)}$\%$.  A natural question is therefore whether one can further enhance the \cite{PeyerVermaelen2009} U-index by incorporating information about the firms pre-announce idiosyncratic risk and volatility. We consider one such combination where we simply take an equal-weighted combination of the 4 criteria into one ``Enhanced Undervaluation Index'' (EU-index). Specifically, in the spirit of the U-index of \cite{PeyerVermaelen2009}, we calculate the EU-index simply as the sum of three numbers: high U-index firms get a score of 2, low get a 0; high idiosyncratic firms get a score of 2, low get a 0; and high volatility firms get a score of 2, low get a 0. Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores.

Figure~\ref{fig:Eundervaluationindex} shows the distribution of the EU-index. The index has a symmetric distribution with a mean of \Sexpr{round(mean(EUindex_bb),2)}. Table~\ref{tbl:EUrelations} shows how the EU-index relates to a number of firm characteristics. Firm leverage, based on data the year before announcement, is defined as the ratio $debt/(debt+equity)$\footnote{We use the definitions from \url{http://www.ivo-welch.info/professional/leverage.placebo/}{Ivo Welch's website} following  \url{http://www.ivo-welch.info/professional/leverage.placebo/r-sourcecode/mksane.R}. Debt is the sum of the Compustat variables $dlc+ dltt$, where $dlc$ is ``Debt in Current Liabilities'' and $dltt$ is ``Long Term Debt - Total''. Equity is the Compustat variable $seq$ which is ``Total Parent Stockholders' Equity''. We use the most recent data pre-announce, and make the winsorization and other adjustments as in the websites above. Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.}. ``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. ``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement. Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available\footnote{As this SDC data was not available for many events, we did not consider the in the U-index calculation} (this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp_market_cap = round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb %in% c(4:6)])/1000,1)
@

First there is a striking negative relation between the EU index and financial leverage. This makes sense according to the static trade-off theory of optimal capital structure: high risky firms have more financial distress and should have less debt. Second, the high EU index firms are more likely to miss earnings forecasts. To the extent that analysts base their recommendations on these earnings misses, stock prices may become undervalued. Evidence that analyst extrapolation forecast errors are a partial explanation for the buyback anomaly is documented by \cite{PeyerVermaelen2009}.  High EU index firms are more likely to mention ``undervaluation'' as a motivation for the buyback.  High EU index firms tend to have more cash. This could of course be related to the fact that risky firms should have more cash holdings.  They also tend to follow up with equity offerings after the buyback which suggests that they are more likely to be in the ``market timing'' business. The table also shows a strong negative relation between market-to-book ratios and market capitalization and the EU index, which is not surprising as these are components of the index. It should be noted that the EU 6 portfolio is composed of very small stocks with an average market capitalization of \$\Sexpr{round(EU_relations["Market Cap.","EU6"],1)} million. The average market capitalization of portfolios with long term (after 48 months) monthly excess return of larger than 0.3$\%$ (i.e. portfolios EU4 through EU6 in Table~\ref{tbl:EUunderBBcal}) is \$\Sexpr{tmp_market_cap} billion (not indicated in the Table). So the buyback anomaly is to some extent a small cap anomaly, although portfolio EU3 for which the average market capitalization of its \Sexpr{sum(EUindex_bb==3)} firms is \$\Sexpr{round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb ==3])/1000,1)} billion still has significant abnormal returns.

Figure~\ref{fig:badpreviousEU} shows the results of a strategy similar to the strategy of Figure~\ref{fig:ReturnsBB}: starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months. The graph shows two strategies, one for a short holding period ($N=12$) and one for a very long holding period ($N=48$). In both cases the excess returns for high EU-index companies is significantly higher than for low EU-index companies. We define low EU-index firms those for which the EU-index is 0-1, and high for which it is 5-6 (note that the index takes values from 0 to 6). Specifically, the 12-month holding period high EU-index portfolio has average annual abnormal returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[1],1)}$\%$, while the low EU-index one earns only \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[1],1)}$\%$ annual excess returns. For the 48-month holding periods the high and low EU-index portfolio earn annual excess returns of  respectively, \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[1],1)}$\%$ and \Sexpr{round(pnl_stats(Low_EU_BB_Hedged48m)[1],1)}$\%$.

Tables  \ref{tbl:EUunderBB} and \ref{tbl:EUunderBBcal} show respectively the IRATS and Calendar Time monthly abnormal returns for all values of the EU-index. Focusing on IRATS, as the EU-index increases, the long term abnormal returns increase (from \Sexpr{round(EU_IRATStable_bb["+48",1],1)}$\%$ to \Sexpr{round(EU_IRATStable_bb["+48",19],1)}$\%$). Figure~\ref{fig:Epastall} show the same results over time for each EU-index. Long-term cumulative excess returns after 48 months are becoming statistically significantly positive at EU-index levels of 3 and higher, and then steadily increase from \Sexpr{round(EU_IRATStable_bb["+48",10],1)}$\%$ to \Sexpr{round(EU_IRATStable_bb["+48",19],1)}$\%$. The Calendar Time results are similar although they only show significance starting at EU-index levels of 4.  Investing in the very high EU index firms (EU=6) generates alphas of \Sexpr{round(EU_CALtable_bb["+48",19],2)}$\%$ per month for 48 months.

The bottom line is that combining volatility, idiosyncratic risk and the U-index in one EU- index generates a more selective predictor of excess returns than each of the indicators separately. Indeed, high U-index stocks, stocks with high idiosyncratic risk, and high volatile stocks generate cumulative excess returns of respectively \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR5F"]}$\%$ (Table~\ref{tbl:priorBuybacks}), \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$ (Table~\ref{tbl:IdiosyncraticunderBB}) and \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$ (Table~\ref{tbl:VOLunderBB}).

\subsection{Robustness of the EU-index over Time}
\label{sec:finalrobustness}

As volatility and idiosyncratic risk are time dependent, the performance of the new EU-index may not be robust over time - e.g., relative to the U-index of \cite{PeyerVermaelen2009}.  Tables \ref{tbl:EUTimeUnderBB} (IRATS) and \ref{tbl:EUTimeUnderBBcal} (Calendar Time method), like Table~\ref{tbl:PastFindingsTimeUnderBB} for the U-index, show the relative performance of high and low EU-index repurchases. In order to have roughly similar number of under/overvalued firms as when we use the U-index, we define low EU-index firms to those for which the EU-index is 0-1, and high for which it is 5-6 (the index takes values from 0 to 6). With this definition we have \Sexpr{sum(low_EU_bb)} low EU-index and \Sexpr{sum(high_EU_bb)}  high EU-index firms in our sample (in comparison with \Sexpr{sum(company_subset_overvalued_bb)} low U-index and \Sexpr{sum(company_subset_undervalued_bb)} high U-index ones).

Tables \ref{tbl:EUTimeUnderBB} and \ref{tbl:EUTimeUnderBBcal} indicate that the EU-index is robust over time, with the exception of the 1985-1990 period. However during this period our high EU index sample only contains \Sexpr{ECAL_table_undervaluation_time_bb["Observations",1]} observations which results in statistically insignificant excess returns beyond the 12 month horizon.

<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
tmp = pnl_matrix(remove_initialization_time(High_EU_BB_Hedged,min_date=FirstTrade))
tmp1 = pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))

@

Finally, Table~\ref{tbl:EUhedgedBB}, like Table~\ref{tbl:allhedgedBB}, shows the monthly and yearly returns of a five-factors hedged strategy investing only in the high EU-index repurchase events.  The table shows the robustness of the abnormal returns over time. Specifically, in \Sexpr{sum(tmp[,13] > 0)} out of the \Sexpr{sum(tmp[,13] != 0)} years the hedged strategy generates positive excess returns. As in Table~\ref{tbl:allhedgedBB},  \Sexpr{rownames(tmp)[which.min(tmp1[,13])]} has a large a loss of \Sexpr{tmp[which.min(tmp1[,13]),13]}$\%$ and the best year is \Sexpr{rownames(tmp)[which.max(tmp[,13])]} with an impressive \Sexpr{tmp[which.max(tmp[,13]),13]}$\%$.

\section{Conclusion}
\label{sec:conclusion}

The buyback anomaly first reported by Ikenberry, Lakonishok and Vermaelen (1995) is still alive and robust. Long term excess returns are large, highly statistically significant and robust even when we replace the Fama-French three-factor model with the Fama-French five-factor model. We believe that the difference with the conclusions of \cite{FamaFrench2015b} is a result of the fact that we do not pool buybacks and equity issues in a ``net issuance'' anomaly. A buyback is not simply the inverse of an equity issue, especially in a world with asymmetric information. Managers who buy back undervalued stock from selling investors benefit their long-term shareholders at the expense of selling shareholders who are ``leaving'' the company. Issuing overvalued stock to new investors is not exactly enhancing good investor relations.  Hence it is not surprising to find that the equity issue anomaly does not survive after appropriately adjusting for risk. Moreover buyback authorizations are options, not firm commitments such as equity issues. Using net issues as a measure of (negative) buyback activity ignores the reality that an actual repurchase may occur several months, if not years after a buyback authorization. By the time the buyback is completed the firm may already have experienced significant excess returns.

Not all buybacks are the same: we find that buybacks made by small beaten up risky low market to book companies earn the largest excess returns.  We find that both idiosyncratic risk (small $R^2$) and total risk are positively correlated with future returns. The results that idiosyncratic risk is positively correlated with returns is inconsistent with \cite{Ang2006} but consistent with \cite{Stambaugh2015} who show that for undervalued firms IVOL is positively related to expected returns. We combine these characteristics in a new measure: the EU index or Enhanced Undervaluation Index, building on the analysis of \cite{PeyerVermaelen2009}. Investing in very high EU index firms generates Fama-French five-factor adjusted returns of \Sexpr{round(EU_CALtable_bb["+48",19],2)}$\%$ per month during the 48 months after the buyback announcement.  These are also firms that mention in their press releases that they are buying back stock because they are undervalued.  They are more likely to miss earnings forecasts relative to the other buyback firms and therefore falling out of favor with analysts.  However investing in high EU index firms to some extent implies investing in small caps and micro-caps, which may explain partially why the anomaly persists as these firms may not satisfy, for example, liquidity risk constraints of many funds.

\newpage

\bibliographystyle{jfe}
\bibliography{Bibliography}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% FIRST ALL TABLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BASIC ANALYSIS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
printLatexTable2(
  cbind(IRATS_table_all_bb,IRATS_table_all_bb_undervaluation)[reported_times,],
  cbind(CAL_table_all_bb,CAL_table_all_bb_undervaluation)[reported_times,],
  columns = c("All 3F","All 5F","High U-index 3F","Low U-index 3F","High U-index 5F","Low U-index 5F"),
  title="Buyback announcements during 1985-2014",
  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
  title2 = "Panel B: Calendar Time Method Monthly Abnormal Returns",
  caption="The table presents the abnormal returns for firms after open market repurchase announcements from the announcement date until $t$ months after announcement. We include a version of the abnormal returns for the full sample and one for both companies with a high U-index and a low U-index. Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the Fama French (1993) three-factor model and the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regressions are run each event month~$j$:\\vspace{-1em}
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + \\epsilon_{i,t}, \\\\
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.
",
label = "tbl:priorBuybacks",
bigtitleontop=T,
titleontop=T,
metric1 = "CAR",
metric2 = "AR",
scale=1,
lastSpecial=T,
dorotate=T
)

@
\clearpage

\clearpage

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
printLatexTable2(
  IRATS_table_all_iss[reported_times,],
  CAL_table_all_iss[reported_times,],
  columns = c("All 3F","All 5F"),
  title="Issue announcements during 1985-2014",
  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
  caption= "The table presents the abnormal returns for firms after issue announcements from the announcement date until $t$ months after the announcement. Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the Fama French (1993) three-factor model and the Fama French (2015) five-factor model for the sample of firms that announced equity issuance plus various subsamples. The following regressions are run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + \\epsilon_{i,t}, \\\\
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.
",

label = "tbl:priorIssuers",
bigtitleontop=T,
titleontop=T,
metric1 = "CAR",
metric2 = "AR",
scale=1,
lastSpecial=T,
dorotate=F
)
@

%\clearpage

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
printLatexTable2(
  Exit_on_SEO_Abn_table[reported_times,],
  Exit_on_SEO_Abn_table_cal[reported_times,],
  columns = c("No Issue","Issue"),
  title="Buybacks with and without subsequent issue",
  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
  caption="The table presents the long-run abnormal returns for firms repurchase announcements for events with and without a subsequent SEO announcement. Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",

label = "tbl:BBISSexit",
bigtitleontop=T,
titleontop=T,
metric1 = "CAR",
metric2 = "AR",
scale=1,
lastSpecial=T,
dorotate=F
)

colnames(ISS_for_BB_Abn_table)[1]<- "Post-buyback SEOs"
colnames(ISS_for_BB_Abn_table)[4]<- "Other SEOs"

printLatexTable(ISS_for_BB_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
                label  = "tbl:BBISSexitAfter",
                columns= c("After a Buyback","No Prior Buyback"),
                title  ="Issue announcements with and without a prior buyback",
                caption = "The table presents the long-run abnormal returns (CAR) for firms after issue announcements for events with and without a prior buyback announcement within 48 months. We report the monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.",

lastSpecial=T,
titleontop = T
)
@

%%%%%%%%

%\clearpage
<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
if (0){
  printLatexTable2(
    Exit_on_BB_Abn_table[reported_times,],
    Exit_on_BB_Abn_table_cal[reported_times,],
    columns = c("No Buyback","Buyback"),
    title="SEOs with and without subsequent buyback",
    title1 = "Panel A: IRATs Cumulative Abnormal Returns",
    title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
    caption="The table presents the long-run abnormal returns for firms after issue announcements with and without a subsequent buyback announcement on the full sample for different periods in time. Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",

label = "tbl:ISSBBexit",
bigtitleontop=T,
titleontop=T,
scale=1,
lastSpecial=T,
dorotate=F
  )

  printLatexTable(BB_for_ISS_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
                  label  = "tbl:ISSBBexitAfter",
                  columns= c("post-Issue Buybacks: CAR","Other Buybacks: CAR"),
                  title  ="Long-run IRATS abnormal return of only the buybacks that are announced within 48 months after an SEO announcement versus the remaining buyback events.",lastSpecial=T)
}
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TIME ROBUSTNESS ANALYSIS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Robustness over time}
%\label{app:robusttime}

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp = BBtable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2014: CAR","t-stat","p-value","2008-2014: CAR","t-stat","p-value")
tmp2 = BBtable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2014: CAL","t-stat","p-value","2008-2014: CAL","t-stat","p-value")

printLatexTable2(
  tmp,
  tmp2,
  columns= c("1985-1990","1991-2000","2001-2014","2008-2014"),
  title="Buyback returns over different time periods",
  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
  caption="The table presents the long-run abnormal returns for firms after repurchase announcements for different time periods.  Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",

label = "tbl:PastFindingsTimeBB",
bigtitleontop=T,
titleontop=T,
metric1 = "CAR", metric2 = "AR",
scale=1,
lastSpecial=T,
dorotate=T
)

if (0){
  tmp = ISStable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
  colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2014: CAR","t-stat","p-value","2008-2014: CAR","t-stat","p-value")
  tmp2 = ISStable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
  colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2014: CAL","t-stat","p-value","2008-2014: CAL","t-stat","p-value")

  printLatexTable2(
    tmp,
    tmp2,
    columns= c("1985-1990","1991-2000","2001-2014","2008-2014"),
    title="SEOs returns over different time periods",
    title1 = "Panel A: IRATs Cumulative Abnormal Returns",
    title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
    caption="Long-run IRATS cumulative (Panel~A) and Calendar method monthly (Panel~B) abnormal return after issue announcements for different time periods.",
    label = "tbl:PastFindingsTimeISS",
    bigtitleontop=T,
    titleontop=T,
    scale=1,
    lastSpecial=T,
    dorotate=T
  )
}

@

\clearpage

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
one_table = cbind(BBtable_undertime[,7:12],BB_cal_table_undertime[,7:12],
                  BBtable_undertime[,19:24],BB_cal_table_undertime[,19:24],
                  BBtable_undertime[,31:36],BB_cal_table_undertime[,31:36],
                  BBtable_undertime[,43:48],BB_cal_table_undertime[,43:48]
)
#one_table = BBtable_undertime
printLatexTable(one_table[reported_times,1:12],
                columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),
                rowcolumn="1985-1990",
                title="Buyback returns for the U-index over time",
                caption="The table presents the long-run abnormal returns for firms after open market repurchase announcements for high and low U-index firms in different time periods and shows significantly larger returns by buybacks announced by high U-index firms compared to those with a low U-index. We report both the IRATS cumulative average abnormal returns (CAR, Panel~A) and the calender time method (AR, Panel~B) abnormal returns on the full sample. $t$-Statistics are provided and stars indicate significance at the $5\\%$ (*), and $1\\%$ level (**). \\\\",
                label="tbl:PastFindingsTimeUnderBB",metric=c("CAR", "CAR", "AR", "AR"),
                scale = 1,close=F,lastSpecial=T
)
printLatexTable(one_table[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
printLatexTable(one_table[reported_times,25:36],open=F,close=F,rowcolumn="2001-2014",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
printLatexTable(one_table[reported_times,37:48],open=F,rowcolumn="2008-2014",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)

if (0){
  paste(printLatexTable(BB_cal_table_undertime[reported_times,1:12],
                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
                        rowcolumn="1985-1990",
                        title="Calendar Method abnormal returns after open market repurchase announcements  for under and over valued companies over different time periods.",
                        label="tbl:PastFindingsTimeUnderBBcal",
                        scale = 0.8,close=F,lastSpecial=T
  ),
  printLatexTable(BB_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(BB_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(BB_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")

}
if (0){
  paste(printLatexTable(ISStable_undertime[reported_times,1:12],
                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
                        rowcolumn="1985-1990",
                        title="Long-run IRATS abnormal returns after issue announcements  for under and over valued companies over different time periods.",
                        label="tbl:PastFindingsTimeUnderISS",
                        scale = 0.9,close=F,lastSpecial=T
  ),
  printLatexTable(ISStable_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(ISStable_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(ISStable_undertime[reported_times,37:48],open=F,rowcolumn="2008-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")

  paste(printLatexTable(ISS_cal_table_undertime[reported_times,1:12],
                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
                        rowcolumn="1985-1990",
                        title="Calendar Method abnormal returns after issue announcements  for under and over valued companies over different time periods.",
                        label="tbl:PastFindingsTimeUnderISScal",
                        scale = 0.9,close=F,lastSpecial=T
  ),
  printLatexTable(ISS_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(ISS_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(ISS_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
}
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INDUSTRIES ANALYSIS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
tmp_cal = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,4:6] ))

printLatexTable2(
  tmp[reported_times,1:(3*6)],
  tmp[reported_times,(3*6+1):36],
  columns= names(industry_BB)[1:6],
  columns2= names(industry_BB)[7:12],
  title="Buyback IRATS Abnormal Returns: Industry Robustness",
  #title1 = "",
  #title2 = "",
  caption=paste("The table presents the long-run abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample. We report the monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. The 48 month abnormal return for the full sample is equal to ",round(IRATS_table_all_bb["+48","CAR 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),

label = "tbl:IndustriesBB",
bigtitleontop=T,
metric1 = "CAR", metric2 = "CAR",
#titleontop=T,
scale=1,
lastSpecial=T,
dorotate=T
)

printLatexTable2(
  tmp_cal[reported_times,1:(3*6)],
  tmp_cal[reported_times,(3*6+1):36],
  columns= names(industry_BB)[1:6],
  columns2= names(industry_BB)[7:12],
  title="Buyback Calendar Method Abnormal Returns: Industry Robustness",
  #title1 = "",
  #title2 = "",
  caption=paste("The table presents the long-run calendar method abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample.  Specifically, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors (the difference between the risk-free rate and the return on the equally weighted CRSP index, the monthly return on the size, book-to-market factor, profitability factor and investment factor in month) as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test. The 48 month abnormal return for the full sample is equal to ",round(CAL_table_all_bb["+48","CAL 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),
  label = "tbl:IndustriesBB_cal",
  bigtitleontop=T,
  metric1 = "AR", metric2 = "AR",
  #titleontop=T,
  scale=1,
  lastSpecial=T,
  dorotate=T
)

@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
latex_render_data_frame(
  pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)), 
  title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all buybacks",
  caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all buybacks. The holding period for each buyback is 12 months per event.",
  label="tbl:allhedgedBB", 
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F,dorotate=F
)
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cross Relations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\clearpage
%\subsection{Enhanced U-index}
%\label{app:enhanced}

\small
<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp = industry_BB_features[,c(1:4,9:10)]
if (colnames(tmp)[1] == "H Idsync.")
  colnames(tmp) <- paste(colnames(tmp), " (",1:ncol(tmp), ")",sep="")
latex_render_data_frame(
  round(tmp,1), 
  title = "Industry Characteristics",
  caption="Percentage of high and low idiosyncratic risk  and volatility companies for all industries for which we have at least 100 events in our sample.",
  label = "tbl:industriesR2Vol",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 1,
  digits=1,
  lastSpecial=F,dorotate=T
)
@
\normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% IDIOSYNCRATIC ANALYSIS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
printLatexTable2(
  cbind(R2_IRATStableBB,R2_IRATStable_underBB)[reported_times,],
  cbind(R2_IRATStableBB_cal,R2_IRATStable_underBB_cal)[reported_times,],
  columns= c("Low Id.","High Id.","Low Id./High U-Ind.","Low Id./Low U-Ind.","High Id./High U-Ind.","High Id./Low U-Ind."),
  title="Buyback for Low and High idiosyncratic and  for Low and and High U-index companies",
  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high idiosyncratic and for low and  high U-index companies. Regardless of event study method and time horizon, the U-index works only for idiosyncratic companies. Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",
label = "tbl:IdiosyncraticunderBB",
bigtitleontop=T,
titleontop=T,
metric1 = "CAR",
metric2 = "AR",
scale=1,
lastSpecial=T,
dorotate=T
)

@

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% VOL ANALYSIS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
printLatexTable2(
  cbind(VOL_IRATStableBB,VOL_IRATStable_underBB)[reported_times,],
  cbind(VOL_IRATStableBB_cal,VOL_IRATStable_underBB_cal)[reported_times,],
  columns= c("Low Vol.","High Vol.","Low Vol./High U-ind.","Low Vol./Low U-ind.","High Vol./High U-ind.","High Vol./Low U-ind."),
  title="Buyback for Low and High Volatility and  for Low and and High U-index companies",
  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility and  for low and  high U-index companies.  Regardless of event study method and time horizon, the U-index works only for idiosyncratic companies. Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",
label = "tbl:VOLunderBB",
bigtitleontop=T,
titleontop=T,
metric1 = "CAR",
metric2 = "AR",
scale=1,
lastSpecial=T,
dorotate=T
)
@

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
rownames(Under_IdioBB)[1:2] <- c("high U-index", "low U-index")
latex_render_data_frame(
  round(Under_IdioBB[1:6,1:4],1), 
  title = "Relations across firm characteristics for Buybacks",
  caption="Relation between Under/Overvaluation, High/Low Idiosyncratic Risk, High/Low volatilityfor buybacks. Numbers indicate percentage of firms in the row that are also categorized as noted in the columns.",
  label = "tbl:underidioallBB",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F,dorotate=F
)

latex_render_data_frame(
  round(Under_IdioBB_cor,2), 
  title = "Correlations of Buybacks Characteristics",
  caption="Correlation between the three buybacks characteristics considered: Idiosyncratic score (percentile across all CRSP companies of firm's $1-R^2$, 0 to 1), Volatility score  (percentile across all CRSP companies, 0 to 1) and U-index score (0 to 15). All scores are defined using the universe of all CRSP companies at the time of the announcement with data up to the month before the announcement.",
  label = "tbl:underidioallBBcor",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=2,
  lastSpecial=F,dorotate=F
)

@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NEW INDEX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
rownames(EU_relations)[1] <- "Low Leverage"
rownames(EU_relations)[2] <- "High Leverage"
latex_render_data_frame(
  round(EU_relations,1), 
  title = "EU relations with Firm Characteristics",
  caption="Firm characteristics for each of the 7 EU-index samples. Percentages indicated for all but the last 3 rows, and averages for the last 3 rows. We consider firm \\textit{leverage}, based on data the year before announcement, defined as the ratio $debt/(debt+equity)$. \\textit{Missed (Beat) EPS} measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. \\textit{ISS later} measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement. Next, we measure the percentage of buybacks financed with cash (\\textit{CASH}) when the data is available and whether the reported purpose included the term \\textit{Undervalued},  \\textit{Enhance Shareholder Value} or \\textit{stock option plan}. Market Cap. is in millions, BE/ME Score is from 1, for firms below the $4^{th}$ Fama-French BE/ME breakpoint, to 5 for firms above the $16^{th}$. Percentage Shares is the percentage shares authorized at announcement.",
  label = "tbl:EUrelations",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 1,
  digits=1,
  lastSpecial=F,dorotate=F
)
@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=

printLatexTable2(
  EU_IRATStable_bb[reported_times,1:(3*4)],
  EU_IRATStable_bb[reported_times,13:(3*7)],
  columns = c("EU-index 0", "EU-index 1","EU-index 2","EU-index 3"),
  columns2 = c("EU-index 4","EU-index 5","EU-index 6"),
  title="Buyback announcements IRATS for all EU-index Values",
  caption="IRATS five factor cumulative abnormal returns after open market repurchase announcements for each Enhanced Undervaluation Index value from 0 to 6.
 We calculate the EU-index simply as the sum of three numbers:  high Peyer and Vermaelen (2009) U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.  Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores. For each EU-index value, we report the monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.",
label = "tbl:EUunderBB",
bigtitleontop=T,
titleontop=T,
metric1="CAR",metric2="CAR",
scale=1,
lastSpecial=T,
dorotate=T
)

printLatexTable2(
  EU_CALtable_bb[reported_times,1:(3*4)],
  EU_CALtable_bb[reported_times,13:(3*7)],
  columns = c("EU-index 0", "EU-index 1","EU-index 2","EU-index 3"),
  columns2 = c("EU-index 4","EU-index 5","EU-index 6"),
  title="Buyback announcements Calendar for all EU-index Values",
  caption="IRATS five factor cumulative abnormal returns after open market repurchase announcements for each Enhanced Undervaluation Index value from 0 to 6.
 We calculate the EU-index simply as the sum of three numbers:  high Peyer and Vermaelen (2009) U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.  Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores. For each EU-index value, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors (the difference between the risk-free rate and the return on the equally weighted CRSP index, the monthly return on the size, book-to-market factor, profitability factor and investment factor in month) as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",
 label = "tbl:EUunderBBcal",
 bigtitleontop=T,
 titleontop=T,
 metric1="AR",metric2="AR",
 scale=1,
 lastSpecial=T,
 dorotate=T
)
@

\clearpage

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=

printLatexTable2(
  EIRATS_table_undervaluation_time_bb[reported_times,1:(3*4)],
  EIRATS_table_undervaluation_time_bb[reported_times,13:(3*8)],
  columns = c("1985-1990: High-EU", "Low-EU", "1991-2000: High-EU", "Low-EU"),
  columns2 = c("2001-2014: High-EU", "Low-EU", "2008-2014: High-EU", "Low-EU"),
  title="Long-run IRATS abnormal returns after open market repurchase announcements for low and high EU-index companies over different time periods.",
  caption="Long-run abnormal returns five factor monthly abnormal returns after open market repurchase announcements for low and high Enhanced Undervaluation (EU) Index companies over different time periods. We define low EU-index firms those for which the EU-index is 0-1, and high for which it is 5-6 (note that the index takes values from 0 to 6). IRATS five factor cumulative abnormal returns after open market repurchase announcements for each EU-index value from 0 to 6. We calculate the EU-index simply as the sum of three numbers:  high Peyer and Vermaelen (2009) U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.  Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores. For each EU-index value, we report the monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.",
label = "tbl:EUTimeUnderBB",
bigtitleontop=T,
titleontop=T,
metric1="CAR",metric2="CAR",
scale=1,
lastSpecial=T,
dorotate=T
)

printLatexTable2(
  ECAL_table_undervaluation_time_bb[reported_times,1:(3*4)],
  ECAL_table_undervaluation_time_bb[reported_times,13:(3*8)],
  columns = c("1985-1990: High-EU", "Low-EU", "1991-2000: High-EU", "Low-EU"),
  columns2 = c("2001-2014: High-EU", "Low-EU", "2008-2014: High-EU", "Low-EU"),
  title="Calendar method monthly abnormal returns after open market repurchase announcements for low and high EU-index companies over different time periods.",
  caption="Long-term monthly abnormal returns after open market repurchase announcements for low and high Enhanced Undervaluation (EU) Index companies over different time periods. We define low EU-index firms those for which the EU-index is 0-1, and high for which it is 5-6 (note that the index takes values from 0 to 6).  We calculate the EU-index simply as the sum of three numbers:  high Peyer and Vermaelen (2009) U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.  Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores. For each EU-index value, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors (the difference between the risk-free rate and the return on the equally weighted CRSP index, the monthly return on the size, book-to-market factor, profitability factor and investment factor in month) as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",
  label = "tbl:EUTimeUnderBBcal",
  bigtitleontop=T,
  titleontop=T,
  metric1="AR",metric2="AR",
  scale=1,
  lastSpecial=T,
  dorotate=T
)
@

\clearpage

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=

latex_render_data_frame(
  pnl_matrix(remove_initialization_time(High_EU_BB_Hedged,min_date=FirstTrade)), 
  title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all high EU-index buybacks",
  caption="Monthly and yearly  five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all high EU-index buybacks only. Holding period for each buyback is 12 months per event.",
  label="tbl:EUhedgedBB", 
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F,dorotate=F
)
@

%\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%XXXXXXX NOW ALL FIGURES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[H]
\centering
<<   fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
par(mfrow=c(2,1), mar=c(2.2,4.5,2.2,4.5))

number_eventsBB = table(format(BUYBACK_DATA$DATASET$SDC$Event.Date[BUYBACK_DATA$DATASET$SDC$Event.Date >= FirstTrade], "%Y"))
market_index = 100*(1+cumprod(1+Market_Monthly[names(Market_Monthly) >= "1985-01-01"]))
market_index = market_index[which(str_sub(names(market_index), start = 6, end = 7)=="12")]
names(market_index) <- str_sub(names(market_index), start = 1, end = 4)
df.bar <- barplot(number_eventsBB,col=c("grey"),main = "Panel A: Buyback Announcements", ylab = "Announcements", xlab = "Years",las=2,space=0.5, cex.names=0.6)
par(new = TRUE)
plot(market_index,type="l", lwd = 1.5, axes = FALSE, xlab = "", ylab = "")
points(market_index, pch=1,  lwd=1.5)
axis(side=4, at = pretty(range(market_index)))
mtext("Market Index", side=4, line=3)
for (iter in 1:floor(max(number_eventsBB)/100))
  abline(h = 100*iter)

number_eventsISS = table(format(ISSUERS_DATA$DATASET$SDC$Event.Date[ISSUERS_DATA$DATASET$SDC$Event.Date >= FirstTrade], "%Y"))
market_index = 100*(1+cumprod(1+Market_Monthly[names(Market_Monthly) > "1985-01-01"]))
market_index = market_index[which(str_sub(names(market_index), start = 6, end = 7)=="12")]
names(market_index) <- str_sub(names(market_index), start = 1, end = 4)
df.bar <- barplot(number_eventsISS,col=c("grey"),main = "Panel B: Equity SEO Announcements", ylab = "Announcements", xlab = "Years",las=2,space=0.5, cex.names=0.6)
par(new = TRUE)
plot(market_index,type="l", lwd = 1.5, axes = FALSE, xlab = "", ylab = "")
points(market_index, pch=1,  lwd=1.5)
axis(side=4, at = pretty(range(market_index)))
mtext("Market Index", side=4, line=3)
for (iter in 1:floor(max(number_eventsISS)/50))
  abline(h = 50*iter)
@
\caption{Buyback and equity announcements. Number of announcements per year. Panel~A: Buyback announcements; Panel~B: Equity SEO announcements. Solid line and right hand axis shows the $S\&P$ index at the end of each year, starting from 100 in January 1985. Buyback activity rises prior to stock market increases and tends to fall afterwards. Also note the structural decline in equity since 2000. }
\label{fig:liveevents}
\end{figure}

\clearpage

\begin{figure}[H]
\centering
<<  fig.width=10, fig.height=5, out.width='\\textwidth', echo=F >>=
#par(mfrow=c(2,1), mar=c(2.3,4,2.3,4))
#valuation_index_bb[which(valuation_index_bb==2)]<-3 # there is one company here. need to check why
tmp = table(valuation_index_bb)
tmp = structure(as.numeric(tmp), .Names = names(tmp))
barplot(tmp,main = "", ylab = "Number of Events", xlab = "",las=2,space=0.5, cex.names=0.8)
#tmp = table(valuation_index_iss)
#tmp = structure(as.numeric(tmp), .Names = names(tmp))
#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=0.8)
rm("tmp")
@
\caption{Distribution of the Undervaluation Index of all buyback events.}
\label{fig:undervaluationindex}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\begin{figure}[H]
\centering
<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
par(mfrow=c(2,2), mar=c(2.3,4,2.3,4))

IRATS_table_all_bb_plot = IRATS_table_all_bb
IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] <- -IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] 
IRATS_table_all_iss_plot = IRATS_table_all_iss
IRATS_table_all_iss_plot[rownames(IRATS_table_all_iss_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] <- -IRATS_table_all_iss_plot[rownames(IRATS_table_all_iss_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] 
IRATS_table_all_bb_undervaluation_plot = IRATS_table_all_bb_undervaluation
IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] 
IRATS_table_all_iss_undervaluation_plot = IRATS_table_all_iss_undervaluation
IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]

ylimit = c(min(
  #IRATS_table_all_bb_plot[reported_times_plots,"CAR 3F"], 
  IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], 
  #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
  #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
  IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
  IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR5F"]), 
  max(
    #IRATS_table_all_bb_plot[reported_times_plots,"CAR 3F"], 
    IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], 
    #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
    #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
    IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
    IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR5F"])
)

plot(IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="A. Buybacks - All", lwd=1.4)
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
#lines(IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"],  lty = 2,lwd=1.4)
abline(v=which(reported_times_plots == "0"), lwd=0.5)
abline(h=0, lwd=0.5)

plot(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="C. Buybacks - high/low U-index", lwd=1.4)
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
#tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"U:CAR3F"]
#points(tmp, pch=0)
#lines(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR3F"],lwd=1.6)
#tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"O:CAR3F"]
#points(tmp, pch=3)
#lines(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"],lty = 3, lwd=1.6)
#tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"U:CAR5F"]
#points(tmp, pch=0)
lines(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR5F"],  lty = 3,lwd=1.6)
#tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"O:CAR5F"]
#points(tmp, pch=3)
abline(v=which(reported_times_plots == "0"), lwd=0.5)
abline(h=0, lwd=0.5)

# SEOs
ylimit = c(min(
  #IRATS_table_all_iss_plot[reported_times_plots,"CAR 3F"], 
  IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"]#, 
  #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
  #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
  #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
  #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR5F"]
), 
max(
  #IRATS_table_all_iss_plot[reported_times_plots,"CAR 3F"], 
  IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"]#, 
  #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
  #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
  #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
  #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR5F"]
)
)

plot(IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="B. SEOs - All", lwd=1.4)
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
#lines(IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"],  lty = 2,lwd=1.4)
abline(v=which(reported_times_plots == "0"), lwd=0.5)
abline(h=0, lwd=0.5)

if (0){
  plot(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="SEOs - Under/Over-valuation", lwd=1.4)
  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
  axis(2,cex.axis=1.1)
  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"U:CAR3F"]
  #points(tmp, pch=0)
  #lines(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR3F"],lwd=1.6)
  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"O:CAR3F"]
  #points(tmp, pch=3)
  #lines(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"],lty = 3, lwd=1.6)
  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"U:CAR5F"]
  #points(tmp, pch=0)
  lines(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR5F"],  lty = 3,lwd=1.6)
  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"O:CAR5F"]
  #points(tmp, pch=3)
  abline(v=which(reported_times_plots == "0"), lwd=0.5)
  abline(h=0, lwd=0.5)
}
@
\caption{Long-run five factors cumulative average abnormal returns (CAR) of buyback and SEO portfolios. The x-axis indicates months from the date of the event announcement. Panel~A shows all buyback events, whereas Panel C shows all high (solid line) and low (dashed lines) U-index buyback events. Panel~B includes all SEOs.}
\label{fig:pastall}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CROSS-EVENTS ANALYSIS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

%\subsection{Combining Equity Issues and Stock Repurchases}
%\label{app:combine}

\begin{figure}[H]
\centering
<< BBISSevents, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
#par(mfrow=c(2,1), mar=c(3.8,4,3.8,4))

market_index = 100*(1+cumprod(1+Market_Monthly[names(Market_Monthly) >= "1985-01-01"]))
market_index = market_index[which(str_sub(names(market_index), start = 6, end = 7)=="12")]
names(market_index) <- str_sub(names(market_index), start = 1, end = 4)
df.bar <- barplot(BB_with_ISS_later_total,col=c("grey"),main = "", ylab = "Percent", xlab = "Years",las=2,space=0.5, cex.names=0.8)
for (iter in 1:floor(max(BB_with_ISS_later_total)/5))
  abline(h = 5*iter)
#par(new = TRUE)
#plot(market_index,type="l", col="red", lwd = 4, lty=3,axes = FALSE, xlab = "", ylab = "")
#points(market_index, pch=1, col="red", lwd=2)
#axis(side=4, at = pretty(range(market_index)))
#mtext("Market Index", side=4, line=3)

if (0){
  df.bar <- barplot(ISS_with_BB_later_total,col=c("grey"),main = "Issues with Follow-up Buyback", ylab = "Percent", xlab = "Years",las=2,space=0.5, cex.names=0.8)
  for (iter in 1:floor(max(ISS_with_BB_later_total)/5))
    abline(h = 5*iter)
  par(new = TRUE)
  plot(market_index,type="l", col="red", lwd = 4, lty=3,axes = FALSE, xlab = "", ylab = "")
  points(market_index, pch=1, col="red", lwd=2)
  axis(side=4, at = pretty(range(market_index)))
  mtext("Market Index", side=4, line=3)
}
@
\caption{Buybacks with a follow-up equity issue within 48 months. We show the percent of announced buyback events each year, that had a follow-up issue within 48 months after the event. The average percentage is \Sexpr{round(mean(BB_with_ISS_later_total),1)}$\%$ and there are only \Sexpr{sum(BB_with_ISS_later_total > 10)} years (1989 and 1990) where the percentage is larger than $10\%$.
%Top figure is buybacks and bottom is SEOs.
}
\label{fig:BBISSevents}
\end{figure}

\clearpage

\begin{figure}[H]
\centering
<< BBISSpnl, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
reported_times_plots_tmp = reported_times_plots
reported_times_plots = reported_times_plots[8:length(reported_times_plots)]

#par(mfrow=c(2,2), mar=c(3.8,4,3.8,4))
par(mfrow=c(2,1), mar=c(3,4,3,4))

ylimit = c(min(Exit_on_SEO_Abn_table[reported_times_plots,1], Exit_on_SEO_Abn_table[reported_times_plots,4]), 
           max(Exit_on_SEO_Abn_table[reported_times_plots,1], Exit_on_SEO_Abn_table[reported_times_plots,4]))
plot(Exit_on_SEO_Abn_table[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel A: Buybacks with SEO IRATS CAR", lwd=1.4)
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(Exit_on_SEO_Abn_table[reported_times_plots,4],lty = 2,lwd=1.4)
abline(h=0, lwd=0.5)
abline(v=which(reported_times_plots == "0"), lwd=0.5)
legend(x="topleft",
       c("Post Buyback Issuance","No Post Buyback Issuance"),
       lty=c("solid","dashed"),
       lwd=c(2,2),
       cex=1,bg="white",inset=0.01)

if (0){
  ylimit = c(min(Exit_on_SEO_Abn_table_cal[reported_times_plots,1], Exit_on_SEO_Abn_table_cal[reported_times_plots,4]), 
             max(Exit_on_SEO_Abn_table_cal[reported_times_plots,1], Exit_on_SEO_Abn_table_cal[reported_times_plots,4]))
  plot(Exit_on_SEO_Abn_table_cal[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: Buybacks with SEO: Calendar Method", lwd=1.4)
  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
  axis(2,cex.axis=1.1)
  lines(Exit_on_SEO_Abn_table_cal[reported_times_plots,4],lty = 2,lwd=1.4)
  abline(h=0, lwd=0.5)
  abline(v=which(reported_times_plots == "0"), lwd=0.5)
}

reported_times_plots = reported_times_plots_tmp

pnl_Exit_Hedged = BB_ISS_Exit_Hedged
pnl_NoExit_Hedged = BB_ISS_NoExit_Hedged
plot(cumsum(100*pnl_NoExit_Hedged),type="l",ylab="CAR", xlab = "",main = "Panel B: Strategy Returns", axes = FALSE, ylim=c(min(c(100*cumsum(pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged))), max(c(cumsum(100*pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged)))), cex.lab=1.1)
axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(cumsum(100*pnl_Exit_Hedged), lty = 2,lwd=1.4)
for (iter in floor(100*min(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/100):floor(100*max(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/100))
  abline(h = 100*iter)
#plot_crisis_dates(pnl_NoExit_Hedged) 
legend(x="topleft",
       c("Without Exit","With Exit"),
       lty=c("solid","dashed"),
       lwd=c(2,2),
       cex=1,bg="white",inset=0.01)

#### SEOs NOW (We combine the plots)
if (0){ 
  reported_times_plots_tmp = reported_times_plots
  reported_times_plots = reported_times_plots[8:length(reported_times_plots)]

  ylimit = c(min(Exit_on_BB_Abn_table[reported_times_plots,1], Exit_on_BB_Abn_table[reported_times_plots,4]), 
             max(Exit_on_BB_Abn_table[reported_times_plots,1], Exit_on_BB_Abn_table[reported_times_plots,4]))
  plot(Exit_on_BB_Abn_table[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: SEO with Buyback IRATS CAR", lwd=1.4)
  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
  axis(2,cex.axis=1.1)
  lines(Exit_on_BB_Abn_table[reported_times_plots,4],lty = 2,lwd=1.4)
  abline(h=0, lwd=0.5)
  abline(v=which(reported_times_plots == "0"), lwd=0.5)

  if (0){
    ylimit = c(min(Exit_on_BB_Abn_table_cal[reported_times_plots,1], Exit_on_BB_Abn_table_cal[reported_times_plots,4]), 
               max(Exit_on_BB_Abn_table_cal[reported_times_plots,1], Exit_on_BB_Abn_table_cal[reported_times_plots,4]))
    plot(Exit_on_BB_Abn_table_cal[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="SEO with Buyback: Calendar", lwd=1.4)
    axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
    axis(2,cex.axis=1.1)
    lines(Exit_on_BB_Abn_table_cal[reported_times_plots,4],lty = 2,lwd=1.4)
    abline(h=0, lwd=0.5)
    abline(v=which(reported_times_plots == "0"), lwd=0.5)
  }

  reported_times_plots = reported_times_plots_tmp

  pnl_Exit_Hedged = ISS_BB_Exit_Hedged
  pnl_NoExit_Hedged = ISS_BB_NoExit_Hedged
  plot(cumsum(100*pnl_NoExit_Hedged),type="l",ylab="CAR", xlab = "",main = "Strategy Returns",axes = FALSE, ylim=c(min(c(100*cumsum(pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged))), max(c(cumsum(100*pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged)))), cex.lab=1.1)
  axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
  axis(2,cex.axis=1.1)
  lines(cumsum(100*pnl_Exit_Hedged),lty = 2,lwd=1.4)
  for (iter in floor(100*min(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/50):floor(100*max(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/50))
    abline(h = 50*iter)
  #plot_crisis_dates(pnl_NoExit_Hedged) 
}
@
\caption{ Buybacks followed by equity issues within 48 months. 
Top Panel~A:  Five factor IRATS CAR for all buyback events that had (with hindsight) no subsequent SEO event within the 48 months post buyback announcement (solid line) versus those that did have (dashed line).  Bottom Panel~B: Abnormal (five-factor rolling hedged) returns of buybacks portfolio for only the \Sexpr{length(BB_with_ISS_later)} events for which there was a subsequent issue within 4 years. Dashed line is if we exit these positions the month after the subsequent SEO announcement. 
%(Average annual returns: \Sexpr{round(pnl_stats(BB_ISS_Exit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(BB_ISS_Exit_Hedged)[3],1)}), and solid line is if we do not (Average annual returns: \Sexpr{round(pnl_stats(BB_ISS_NoExit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(BB_ISS_NoExit_Hedged)[3],1)}). 
%{\bf Bottom Panel~B: Left:} Five factor IRATS CAR for all SEO events that had no subsequent buyback event within the 48 months post SEO announcement (black line) versus those that did have (dashed line). {\bf Right:} Abnormal (five-factor rolling hedged) returns of SEO portfolio for only the \Sexpr{length(ISS_with_BB_later)} events for which there was a subsequent buybacks announcement within 4 years. Dashed line is if we exit these positions  the month after the subsequent buyback announcement  (Average annual returns: \Sexpr{round(pnl_stats(ISS_BB_Exit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(ISS_BB_Exit_Hedged)[3],1)}), and solid line is if we do not (Average annual returns: \Sexpr{round(pnl_stats(ISS_BB_NoExit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(ISS_BB_NoExit_Hedged)[3],1)}). 
}
\label{fig:BBISSexit}
\end{figure}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PORTFOLIO RETURNS ANALYSIS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[H]
\centering
<< ReturnsBB, fig.width=10, fig.height=9, out.width='\\textwidth', echo=F >>=
par(mfrow=c(2,1), mar=c(2.8,4,2.8,4))

all_ret_values = data.frame(
  market = cumsum(100*Market_Monthly[str_sub(names(Market_Monthly), start = 1, end = 7) %in% str_sub(names(remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_1M,min_date=FirstTrade)), start = 1, end = 7)]),
  #market = cumsum(100*Market_Daily[names(remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_1M,min_date=FirstTrade))]),
  months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_1M,min_date=FirstTrade)),
  months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_3M,min_date=FirstTrade)),
  months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_6M,min_date=FirstTrade)),
  months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_12M,min_date=FirstTrade)),
  months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_24M,min_date=FirstTrade)),
  months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_36M,min_date=FirstTrade)),
  months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_48M,min_date=FirstTrade))
)
plot(all_ret_values$market, axes=FALSE, ylab="Cumulative Returns", xlab = "Time",ylim=c(min(as.vector(all_ret_values)), max(as.vector(all_ret_values))), main = "Panel A: Absolute Returns", cex.lab=1.1, lty = "dotdash", type = "l", lwd=2)
axis(1,at=seq(1,nrow(all_ret_values),length.out=10),labels=str_sub(rownames(all_ret_values)[seq(1,nrow(all_ret_values),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(all_ret_values$months1, lty="solid", lwd=2)
lines(all_ret_values$months3, lty="dashed", lwd=2)
lines(all_ret_values$months6, lty="dotted", lwd=3)
lines(all_ret_values$months12, lty="dotted", lwd=2.5)
lines(all_ret_values$months24, lty="dotted", lwd=2)
lines(all_ret_values$months36, lty="dotted", lwd=1.5)
lines(all_ret_values$months48, lty="dotted", lwd=1)
for (iter in 1:floor(max(as.vector(all_ret_values))/100))
  abline(h = 100*iter)
#plot_crisis_dates(all_ret_values)
legend(x="topleft",
       c("S&P500","1 Month","3 Months","12 Months","24 Months","36 Months","48 Months"),
       lty=c("dotdash","solid","dashed","dotted","dotted","dotted","dotted","dotted"),
       lwd=c(2,2,2,3,2.5,2,1.5,1),
       cex=1,bg="white",inset=0.01)

all_ret_values = data.frame(
  market = cumsum(100*Market_Monthly[str_sub(names(Market_Monthly), start = 1, end = 7) %in% str_sub(names(remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade)), start = 1, end = 7)]),
  #market = cumsum(100*Market_Daily[names(remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade))]),
  months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade)),
  months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all3mshort_risk_factors,min_date=FirstTrade)),
  months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all6mshort_risk_factors,min_date=FirstTrade)),
  months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)),
  months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all24mshort_risk_factors,min_date=FirstTrade)),
  months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all36mshort_risk_factors,min_date=FirstTrade)),
  months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all48mshort_risk_factors,min_date=FirstTrade))
)
plot(all_ret_values$market, axes=FALSE, ylab="CAR", xlab = "Time",ylim=c(min(as.vector(all_ret_values)), max(as.vector(all_ret_values))), main = "Panel B: Excess Returns", cex.lab=1.1, lty = "dotdash", type = "l", lwd=2)
axis(1,at=seq(1,nrow(all_ret_values),length.out=10),labels=str_sub(rownames(all_ret_values)[seq(1,nrow(all_ret_values),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(all_ret_values$months1, lty="solid", lwd=2)
lines(all_ret_values$months3, lty="dashed", lwd=2)
lines(all_ret_values$months6, lty="dotted", lwd=3)
lines(all_ret_values$months12, lty="dotted", lwd=2.5)
lines(all_ret_values$months24, lty="dotted", lwd=2)
lines(all_ret_values$months36, lty="dotted", lwd=1.5)
lines(all_ret_values$months48, lty="dotted", lwd=1)
for (iter in 1:floor(max(as.vector(all_ret_values))/50))
  abline(h = 50*iter)
abline(h = 50*6)
#plot_crisis_dates(all_ret_values)
#plot_crisis_dates(all_ret_values)
@ 
\caption{Cumulative returns of portfolios of all buybacks for different holding periods. Panel~A: Absolute returns; Panel~B: five-factor Rolling Hedged Abnormal returns using a rolling window of \Sexpr{hedge_months} months, lagging 1 month. Dotted-dashed line (e.g., lowest one in Panel~A) is the cumulative returns of the $S\&P$ Index, for comparison; solid line is with 1-month holding period, dashed line is with 3 months holding period; dotted lines are, from the most to the least dark ones, for 6, 12, 24, and 48 months holding periods. Note that the last few lines overlap to a large extend (especially in Panel~A).  We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
%Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}.
}
\label{fig:ReturnsBB}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INDUSTRIES ANALYSIS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\clearpage
%\subsection{Buybacks across Industries}
%\label{app:industries}

\begin{landscape}
\begin{figure}[H]
\centering
<<  fig.width=10, fig.height=5, echo=F >>=
df.bar <- barplot(industry_tableBB,col=c("grey"),main = "", ylab = "Buybacks", xlab = "",las=2,space=0.9, cex.names=0.6)
for (iter in 1:floor(max(industry_tableBB)/100))
  abline(h = 100*iter)
@
\caption{Number of buyback announcements per industry. }
\label{fig:industryeventsBB}
\end{figure}
\end{landscape}
%\begin{figure}[H]
%\centering
%<<  fig.width=10, fig.height=5, out.width='\\textwidth', echo=F >>=
%df.bar <- barplot(industry_tableISS,col=c("grey"),main = "", ylab = "Issues", xlab = "",las=2,space=0.9, cex.names=0.6)
%for (iter in 1:floor(max(industry_tableISS)/100))
%  abline(h = 100*iter)
%@
%\caption{Number of issue announcements per industry.  }
%\label{fig:industryeventsISS}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% IDIOSYNCRATIC ANALYSIS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\clearpage
%\subsection{Idiosyncratic Risk and Buybacks}
%\label{app:idiosync}

%\begin{figure}[H]
%\centering
<< R2thresholds, fig.width=7, fig.height=4, out.width='\\textwidth', echo=F >>=
if (0){
  #par(mfrow=c(2,1), mar=c(2.7,4.5,2.7,4.5))
  Market_Monthly_index = Market_Monthly
  names(Market_Monthly_index) <- paste(str_sub(names(Market_Monthly_index),start=1,end=4),str_sub(names(Market_Monthly_index),start=6,end=7),sep="")

  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[High_Idiosyncr_eventsBB]
  tmp = BUYBACK_DATA$DATASET$SDC$Rsq_returns[High_Idiosyncr_eventsBB]
  names(tmp)<-all_dates
  R2_thresholds_up_plot = sapply(names(Market_Monthly_index), function(i){
    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
  })
  R2_thresholds_up_plot = R2_thresholds_up_plot[!is.na(R2_thresholds_up_plot)]
  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[Low_Idiosyncr_eventsBB]
  tmp = BUYBACK_DATA$DATASET$SDC$Rsq_returns[Low_Idiosyncr_eventsBB]
  names(tmp)<-all_dates
  R2_thresholds_down_plot = sapply(names(Market_Monthly_index), function(i){
    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
  })
  R2_thresholds_down_plot = R2_thresholds_down_plot[!is.na(R2_thresholds_down_plot)]

  R2_thresholds_down_plot = R2_thresholds_down_plot[intersect(names(R2_thresholds_down_plot), names(R2_thresholds_up_plot))]
  R2_thresholds_up_plot = R2_thresholds_up_plot[intersect(names(R2_thresholds_down_plot), names(R2_thresholds_up_plot))]
  R2_thresholds_up_plot = R2_thresholds_up_plot[intersect(names(R2_thresholds_up_plot), names(Market_Monthly_index))]
  R2_thresholds_down_plot = R2_thresholds_down_plot[names(R2_thresholds_up_plot)]
  Market_Monthly_index = Market_Monthly_index[names(R2_thresholds_up_plot)]
  market_index = 100*(1+cumprod(1+Market_Monthly))

  plot(R2_thresholds_up_plot, col="black", axes=FALSE, ylab="five-factor R square", main = "Buybacks Average five-factor R square", xlab = "Time",ylim=c(min(c(R2_thresholds_down_plot[!is.na(R2_thresholds_down_plot)],R2_thresholds_up_plot[!is.na(R2_thresholds_up_plot)])), max(c(R2_thresholds_down_plot[!is.na(R2_thresholds_down_plot)],R2_thresholds_up_plot[!is.na(R2_thresholds_up_plot)]))),  cex.lab=1.1, type="l", lwd=2)
  lines(R2_thresholds_down_plot, col="black", lwd=2,lty="dotted")
  axis(1,at=seq(1,length(Market_Monthly_index),length.out=20),labels=str_sub(names(Market_Monthly_index)[seq(1,length(Market_Monthly_index),length.out=20)], start=1,end=4),cex.axis=0.8,las=3)
  axis(2,cex.axis=1.1)
  #par(new = TRUE)
  #plot(market_index,type="l", lwd = 2, axes = FALSE, xlab = "", ylab = "")
  #axis(side=4, at = pretty(range(market_index)))
  #mtext("Market Index", side=4, line=3)
}
@
%\caption{Monthly average (across all buybacks events that month) $R^2$ defined using all buybacks events announced in a given month. Solid line is for high idiosyncratic events, dotted  line is for low. 
%Note that as the idiosyncratic risk is estimated using 6 months returns before announcement, there is a time shift relative to the market returns. 
%}
%\label{fig:R2thresholds}
%\end{figure}

%\clearpage

%\clearpage

\begin{figure}[H]
\centering
<< badpreviousR2, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
#par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))

plot(cumsum(100*High_Idiosyncr_BB_Hedged),type="l",ylab="CAR", xlab = "Time",main = "",  lwd=2, axes = FALSE, 
     ylim=c(min(c(cumsum(100*High_Idiosyncr_BB_Hedged),cumsum(100*Low_Idiosyncr_BB_Hedged),cumsum(100*High_Idiosyncr_BB_Hedged48m),cumsum(100*Low_Idiosyncr_BB_Hedged48m))), 
            max(c(cumsum(100*High_Idiosyncr_BB_Hedged),cumsum(100*Low_Idiosyncr_BB_Hedged),cumsum(100*High_Idiosyncr_BB_Hedged48m),cumsum(100*Low_Idiosyncr_BB_Hedged48m)))), cex.lab=1.1)
axis(1,at=seq(1,length(High_Idiosyncr_BB_Hedged),length.out=10),labels=str_sub(names(High_Idiosyncr_BB_Hedged)[seq(1,length(High_Idiosyncr_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(cumsum(100*Low_Idiosyncr_BB_Hedged),lty="dotted", lwd=2)
lines(cumsum(100*High_Idiosyncr_BB_Hedged48m),lty="dashed", lwd=2)
lines(cumsum(100*Low_Idiosyncr_BB_Hedged48m),lty="dotdash", lwd=2)
for (iter in 1:floor(100*max(c(cumsum(High_Idiosyncr_BB_Hedged),cumsum(Low_Idiosyncr_BB_Hedged)))/50))
  abline(h = 50*iter)
abline(h = 200)
#plot_crisis_dates(High_Idiosyncr_BB_Hedged)
legend(x="topleft",
       c("12 Month High Idiosyncratic","12 Month Low Idiosyncratic","48 Month High Idiosyncratic","48 Month Low Idiosyncratic"),
       lty=c("solid","dotted","dashed","dotdash"),
       lwd=c(2,2,2,2),
       cex=1,bg="white",inset=0.01)

if (0){
  plot(cumsum(100*High_Idiosyncr_ISS_Hedged),type="l",ylab="CAR", xlab = "Time",main = "SEOs", axes = FALSE, 
       ylim=c(min(c(cumsum(100*High_Idiosyncr_ISS_Hedged),cumsum(100*Low_Idiosyncr_ISS_Hedged),cumsum(100*High_Idiosyncr_ISS_Hedged48m),cumsum(100*Low_Idiosyncr_ISS_Hedged48m))), 
              max(c(cumsum(100*High_Idiosyncr_ISS_Hedged),cumsum(100*Low_Idiosyncr_ISS_Hedged),cumsum(100*High_Idiosyncr_ISS_Hedged48m),cumsum(100*Low_Idiosyncr_ISS_Hedged48m)))), cex.lab=1.1)
  axis(1,at=seq(1,length(High_Idiosyncr_ISS_Hedged),length.out=10),labels=str_sub(names(High_Idiosyncr_ISS_Hedged)[seq(1,length(High_Idiosyncr_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
  axis(2,cex.axis=1.1)
  lines(cumsum(100*Low_Idiosyncr_ISS_Hedged), col="red")
  lines(cumsum(100*High_Idiosyncr_ISS_Hedged48m), col="blue")
  lines(cumsum(100*Low_Idiosyncr_ISS_Hedged48m), col="green")
  for (iter in 1:floor(100*max(c(cumsum(High_Idiosyncr_ISS_Hedged),cumsum(Low_Idiosyncr_ISS_Hedged)))/50))
    abline(h = 50*iter)
  #plot_crisis_dates(High_Idiosyncr_ISS_Hedged)
}
@
\caption{Buybacks: High versus Low Idiosyncratic Events. Returns of five-factor rolling hedged portfolio for only the buyback events for high and low idiosyncratic company. Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio; dashed line is ``high'' and a 48-months holding portfolio, dotted-dash line is ``low'' and a 48-months portfolio. 
%Red line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged)[3],1)}. Black line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged)[3],1)}. Green line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged48m)[3],1)}. Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged48m)[3],1)}. 
We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
%Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
}
\label{fig:badpreviousR2}
\end{figure}

\begin{figure}[H]
\centering
<< fig.width=8, fig.height=5, out.width='\\textwidth', echo=F >>=
par(mfrow=c(2,2), mar=c(2.3,4,2.3,4))

R2_IRATStableBB_plot = R2_IRATStableBB
R2_IRATStableBB_plot[rownames(R2_IRATStableBB_plot) %in% as.character((-6):(-1)),c("Low Idiosync.: CAR","High Idiosync.: CAR")] <- -R2_IRATStableBB_plot[rownames(R2_IRATStableBB_plot) %in% as.character((-6):(-1)),c("Low Idiosync.: CAR","High Idiosync.: CAR")] 
R2_IRATStable_underBB_plot = R2_IRATStable_underBB
R2_IRATStable_underBB_plot[rownames(R2_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)] <- -R2_IRATStable_underBB_plot[rownames(R2_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)]

ylimit = c(min(R2_IRATStableBB_plot[reported_times_plots,"High Idiosync.: CAR"], 
               R2_IRATStableBB_plot[reported_times_plots,"Low Idiosync.: CAR"],
               R2_IRATStable_underBB_plot[reported_times_plots,"Low Idiosync.: U CAR"],
               R2_IRATStable_underBB_plot[reported_times_plots,"High Idiosync.: U CAR"],
               R2_IRATStable_underBB_plot[reported_times_plots,4],
               R2_IRATStable_underBB_plot[reported_times_plots,10]), 
           max(R2_IRATStableBB_plot[reported_times_plots,"High Idiosync.: CAR"], 
               R2_IRATStableBB_plot[reported_times_plots,"Low Idiosync.: CAR"],
               R2_IRATStable_underBB_plot[reported_times_plots,"Low Idiosync.: U CAR"],
               R2_IRATStable_underBB_plot[reported_times_plots,"High Idiosync.: U CAR"],
               R2_IRATStable_underBB_plot[reported_times_plots,4],
               R2_IRATStable_underBB_plot[reported_times_plots,10]))

plot(R2_IRATStable_underBB_plot[reported_times_plots,"High Idiosync.: U CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel A: High U-index buybacks", lwd=1.4)
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(R2_IRATStable_underBB_plot[reported_times_plots,"Low Idiosync.: U CAR"],lty = 2,lwd=1.6)
abline(v=which(reported_times_plots == "0"), lwd=0.5)
abline(h=0, lwd=0.5)

plot(R2_IRATStable_underBB_plot[reported_times_plots,10], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: Low U-index buybacks", lwd=1.4)
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(R2_IRATStable_underBB_plot[reported_times_plots,4],lty = 2,lwd=1.6)
abline(v=which(reported_times_plots == "0"), lwd=0.5)
abline(h=0, lwd=0.5)

plot(R2_IRATStableBB_plot[reported_times_plots,"High Idiosync.: CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel C: All buybacks", lwd=1.4)
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(R2_IRATStableBB_plot[reported_times_plots,"Low Idiosync.: CAR"],  lty = 2,lwd=1.4)
abline(v=which(reported_times_plots == "0"), lwd=0.5)
abline(h=0, lwd=0.5)

@
\caption{Long-run five factors cumulative average abnormal returns (IRATS) of high (solid line) and low (dashed line) idiosyncratic buybacks. The x-axis indicates months from the date of the event announcement. Panel~A shows only the high  U-index companies, Panel~B  the low U-index ones, and bottom Panel C includes the whole sample.}
\label{fig:pastallidio}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% VOL ANALYSIS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\clearpage
%\subsection{Volatility and Buybacks}
%\label{app:volatility}

%\begin{figure}[H]
%\centering
<< VOLthresholds, fig.width=7, fig.height=4, out.width='\\textwidth', echo=F >>=
#par(mfrow=c(2,1), mar=c(2.7,4.5,2.7,4.5))
if (0){
  Market_Monthly_index = Market_Monthly
  names(Market_Monthly_index) <- paste(str_sub(names(Market_Monthly_index),start=1,end=4),str_sub(names(Market_Monthly_index),start=6,end=7),sep="")

  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[High_VOL_eventsBB]
  tmp = BUYBACK_DATA$DATASET$SDC$pre_vol[High_VOL_eventsBB]
  names(tmp)<-all_dates
  VOL_thresholds_up_plot = sapply(names(Market_Monthly_index), function(i){
    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
  })
  VOL_thresholds_up_plot = 100*VOL_thresholds_up_plot[!is.na(VOL_thresholds_up_plot)]
  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[Low_VOL_eventsBB]
  tmp = BUYBACK_DATA$DATASET$SDC$pre_vol[Low_VOL_eventsBB]
  names(tmp)<-all_dates
  VOL_thresholds_down_plot = sapply(names(Market_Monthly_index), function(i){
    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
  })
  VOL_thresholds_down_plot = 100*VOL_thresholds_down_plot[!is.na(VOL_thresholds_down_plot)]

  VOL_thresholds_down_plot = VOL_thresholds_down_plot[intersect(names(VOL_thresholds_down_plot), names(VOL_thresholds_up_plot))]
  VOL_thresholds_up_plot = VOL_thresholds_up_plot[intersect(names(VOL_thresholds_down_plot), names(VOL_thresholds_up_plot))]
  VOL_thresholds_up_plot = VOL_thresholds_up_plot[intersect(names(VOL_thresholds_up_plot), names(Market_Monthly_index))]
  VOL_thresholds_down_plot = VOL_thresholds_down_plot[names(VOL_thresholds_up_plot)]
  Market_Monthly_index = Market_Monthly_index[names(VOL_thresholds_up_plot)]
  market_index = 100*(1+cumprod(1+Market_Monthly))

  plot(VOL_thresholds_up_plot, col="black", axes=FALSE, ylab="Average Volatility (percent)", main = "Buybacks pre-Announce Returns Volatility", xlab = "Time",ylim=c(min(c(VOL_thresholds_down_plot,VOL_thresholds_up_plot)), max(c(VOL_thresholds_down_plot,VOL_thresholds_up_plot))),  cex.lab=1.1, type="l", lwd=1.2)
  lines(VOL_thresholds_down_plot, col="black", lwd=2,lty="dotted")
  axis(1,at=seq(1,length(Market_Monthly_index),length.out=20),labels=str_sub(names(Market_Monthly_index)[seq(1,length(Market_Monthly_index),length.out=20)], start=1,end=4),cex.axis=0.8,las=3)
  axis(2,cex.axis=1.1)
  #par(new = TRUE)
  #plot(market_index,type="l", lwd = 2, axes = FALSE, xlab = "", ylab = "")
  #axis(side=4, at = pretty(range(market_index)))
  #mtext("Market Index", side=4, line=3)
}
@
%\caption{Monthly average (across all buybacks events that month) volatility (standard deviation of daily$\%$ returns over 6 months before announcement) defined using all buybacks events announced in a given month. Solid line is for high idiosyncratic events, dotted line is for low. 
%Note that as the volatility is estimated using 6 months returns before announcement, there is a time shift relative to the market returns.  
%}
%\label{fig:VOLthresholds}
%\end{figure}

\begin{figure}[H]
\centering
<< badpreviousVOL, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
#par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))

plot(cumsum(100*High_VOL_BB_Hedged),type="l",ylab="CAR", xlab = "Time",main = "", lwd=2, axes = FALSE, 
     ylim=c(min(c(cumsum(100*High_VOL_BB_Hedged),cumsum(100*Low_VOL_BB_Hedged),cumsum(100*High_VOL_BB_Hedged48m),cumsum(100*Low_VOL_BB_Hedged48m))), 
            max(c(cumsum(100*High_VOL_BB_Hedged),cumsum(100*Low_VOL_BB_Hedged),cumsum(100*High_VOL_BB_Hedged48m),cumsum(100*Low_VOL_BB_Hedged48m)))), cex.lab=1.1)
axis(1,at=seq(1,length(High_VOL_BB_Hedged),length.out=10),labels=str_sub(names(High_VOL_BB_Hedged)[seq(1,length(High_VOL_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(cumsum(100*Low_VOL_BB_Hedged),lty="dotted", lwd=2)
lines(cumsum(100*High_VOL_BB_Hedged48m),lty="dashed", lwd=2)
lines(cumsum(100*Low_VOL_BB_Hedged48m),lty="dotdash", lwd=2)
for (iter in 1:floor(100*max(c(cumsum(High_VOL_BB_Hedged),cumsum(Low_VOL_BB_Hedged)))/50))
  abline(h = 50*iter)
#plot_crisis_dates(High_VOL_BB_Hedged)
legend(x="topleft",
       c("12 Month High Volatility","12 Month Low Volatility","48 Month High Volatility","48 Month Low Volatility"),
       lty=c("solid","dotted","dashed","dotdash"),
       lwd=c(2,2,2,2),
       cex=1,bg="white",inset=0.01)

if (0){
  plot(cumsum(100*High_VOL_ISS_Hedged),type="l",ylab="CAR", xlab = "Time",main = "SEOs", lwd=2, axes = FALSE, 
       ylim=c(min(c(cumsum(100*High_VOL_ISS_Hedged),cumsum(100*Low_VOL_ISS_Hedged),cumsum(100*High_VOL_ISS_Hedged48m),cumsum(100*Low_VOL_ISS_Hedged48m))), 
              max(c(cumsum(100*High_VOL_ISS_Hedged),cumsum(100*Low_VOL_ISS_Hedged),cumsum(100*High_VOL_ISS_Hedged48m),cumsum(100*Low_VOL_ISS_Hedged48m)))), cex.lab=1.1)
  axis(1,at=seq(1,length(High_VOL_ISS_Hedged),length.out=10),labels=str_sub(names(High_VOL_ISS_Hedged)[seq(1,length(High_VOL_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
  axis(2,cex.axis=1.1)
  lines(cumsum(100*Low_VOL_ISS_Hedged),lty="dotted", lwd=2)
  lines(cumsum(100*High_VOL_ISS_Hedged48m),lty="dashed", lwd=2)
  lines(cumsum(100*Low_VOL_ISS_Hedged48m),lty="dotdash", lwd=2)
  for (iter in 1:floor(100*max(c(cumsum(High_VOL_ISS_Hedged),cumsum(Low_VOL_ISS_Hedged)))/50))
    abline(h = 50*iter)
  #plot_crisis_dates(High_VOL_ISS_Hedged)
}
@
\caption{Buybacks: High vs Low Volatility Events. Returns of five-factor rolling hedged portfolio for only the buyback events for high and low volatility company. Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio; dashed line is ``high'' and a 48-months holding portfolio, dotted-dash line is ``low'' and a 48-months portfolio. 
%Red line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged)[3],1)}. Black line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged)[3],1)}. Green line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged48m)[3],1)}. Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged48m)[3],1)}. 
We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
%Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
}
\label{fig:badpreviousVOL}
\end{figure}

\begin{figure}[H]
\centering
<< fig.width=8, fig.height=5, out.width='\\textwidth', echo=F >>=
par(mfrow=c(2,2), mar=c(2.3,4,2.3,4))

VOL_IRATStableBB_plot = VOL_IRATStableBB
VOL_IRATStableBB_plot[rownames(VOL_IRATStableBB_plot) %in% as.character((-6):(-1)),c("Low Vol: CAR","High Vol: CAR")] <- -VOL_IRATStableBB_plot[rownames(VOL_IRATStableBB_plot) %in% as.character((-6):(-1)),c("Low Vol: CAR","High Vol: CAR")] 
VOL_IRATStable_underBB_plot = VOL_IRATStable_underBB
VOL_IRATStable_underBB_plot[rownames(VOL_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)] <- -VOL_IRATStable_underBB_plot[rownames(VOL_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)]

ylimit = c(min(VOL_IRATStableBB_plot[reported_times_plots,"High Vol: CAR"], 
               VOL_IRATStableBB_plot[reported_times_plots,"Low Vol: CAR"],
               VOL_IRATStable_underBB_plot[reported_times_plots,"Low Vol: U CAR"],
               VOL_IRATStable_underBB_plot[reported_times_plots,"High Vol: U CAR"],
               VOL_IRATStable_underBB_plot[reported_times_plots,4],
               VOL_IRATStable_underBB_plot[reported_times_plots,10]), 
           max(VOL_IRATStableBB_plot[reported_times_plots,"High Vol: CAR"], 
               VOL_IRATStableBB_plot[reported_times_plots,"Low Vol: CAR"],
               VOL_IRATStable_underBB_plot[reported_times_plots,"Low Vol: U CAR"],
               VOL_IRATStable_underBB_plot[reported_times_plots,"High Vol: U CAR"],
               VOL_IRATStable_underBB_plot[reported_times_plots,4],
               VOL_IRATStable_underBB_plot[reported_times_plots,10]))

plot(VOL_IRATStable_underBB_plot[reported_times_plots,"High Vol: U CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel A: High U-index buybacks", lwd=1.4)
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(VOL_IRATStable_underBB_plot[reported_times_plots,"Low Vol: U CAR"],lty = 2,lwd=1.6)
abline(v=which(reported_times_plots == "0"), lwd=0.5)
abline(h=0, lwd=0.5)

plot(VOL_IRATStable_underBB_plot[reported_times_plots,10], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: Low U-index buybacks", lwd=1.4)
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(VOL_IRATStable_underBB_plot[reported_times_plots,4],lty = 2,lwd=1.6)
abline(v=which(reported_times_plots == "0"), lwd=0.5)
abline(h=0, lwd=0.5)

plot(VOL_IRATStableBB_plot[reported_times_plots,"High Vol: CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel C: All buybacks", lwd=1.4)
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(VOL_IRATStableBB_plot[reported_times_plots,"Low Vol: CAR"],  lty = 2,lwd=1.4)
abline(v=which(reported_times_plots == "0"), lwd=0.5)
abline(h=0, lwd=0.5)

@
\caption{Volatility and the U-index. Long-run five factors cumulative average abnormal returns (IRATS) of high (solid line) and low (dashed line) volatility buybacks. The x-axis indicates months from the date of the event announcement. Panel~A shows only the high  U-index companies, Panel~B  the low U-index ones, and bottom Panel C includes the whole sample.}
\label{fig:pastallVOL}
\end{figure}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NEW INDEX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\begin{figure}[H]
\centering
<< fig.width=10, fig.height=4, out.width='\\textwidth', echo=F >>=
#par(mfrow=c(2,1), mar=c(2.3,4,2.3,4))
#valuation_index_bb[which(valuation_index_bb==2)]<-3 # there is one company here. need to check why
tmp = table(EUindex_bb)
tmp = structure(as.numeric(tmp), .Names = names(tmp))
barplot(tmp,main = "", ylab = "Number of Announcements", xlab = "",las=2,space=0.5, cex.names=0.8)
#tmp = table(valuation_index_iss)
#tmp = structure(as.numeric(tmp), .Names = names(tmp))
#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=0.8)
rm("tmp")
@
\caption{EU-index. Distribution of the EU-index of all buyback events.}
\label{fig:Eundervaluationindex}
\end{figure}

\begin{figure}[H]
\centering
<< badpreviousEU, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
#par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))
plot(cumsum(100*High_EU_BB_Hedged),type="l",ylab="CAR", xlab = "Time",main = "", lwd=2, axes = FALSE, 
     ylim=c(min(c(cumsum(100*High_EU_BB_Hedged),cumsum(100*Low_EU_BB_Hedged),cumsum(100*High_EU_BB_Hedged48m),cumsum(100*Low_EU_BB_Hedged48m))), 
            max(c(cumsum(100*High_EU_BB_Hedged),cumsum(100*Low_EU_BB_Hedged),cumsum(100*High_EU_BB_Hedged48m),cumsum(100*Low_EU_BB_Hedged48m)))), cex.lab=1.1)
axis(1,at=seq(1,length(High_EU_BB_Hedged),length.out=10),labels=str_sub(names(High_EU_BB_Hedged)[seq(1,length(High_EU_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(cumsum(100*Low_EU_BB_Hedged),lty="dotted", lwd=2)
lines(cumsum(100*High_EU_BB_Hedged48m),lty="dashed", lwd=2)
lines(cumsum(100*Low_EU_BB_Hedged48m),lty="dotdash", lwd=2)
for (iter in 1:floor(100*max(c(cumsum(High_EU_BB_Hedged),cumsum(Low_EU_BB_Hedged)))/50))
  abline(h = 50*iter)
#plot_crisis_dates(High_EU_BB_Hedged)
legend(x="topleft",
       c("12 Month High EU","12 Month Low EU","48 Month High EU","48 Month Low EU"),
       lty=c("solid","dotted","dashed","dotdash"),
       lwd=c(2,2,2,2),
       cex=1,bg="white",inset=0.01)

if (0){
  plot(cumsum(100*High_EU_ISS_Hedged),type="l",ylab="CAR", xlab = "Time",main = "SEOs", axes = FALSE, 
       ylim=c(min(c(cumsum(100*High_EU_ISS_Hedged),cumsum(100*Low_EU_ISS_Hedged),cumsum(100*High_EU_ISS_Hedged48m),cumsum(100*Low_EU_ISS_Hedged48m))), 
              max(c(cumsum(100*High_EU_ISS_Hedged),cumsum(100*Low_EU_ISS_Hedged),cumsum(100*High_EU_ISS_Hedged48m),cumsum(100*Low_EU_ISS_Hedged48m)))), cex.lab=1.1)
  axis(1,at=seq(1,length(High_EU_ISS_Hedged),length.out=10),labels=str_sub(names(High_EU_ISS_Hedged)[seq(1,length(High_EU_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
  axis(2,cex.axis=1.1)
  lines(cumsum(100*Low_EU_ISS_Hedged), col="red")
  lines(cumsum(100*High_EU_ISS_Hedged48m), col="blue")
  lines(cumsum(100*Low_EU_ISS_Hedged48m), col="green")
  for (iter in 1:floor(100*max(c(cumsum(High_EU_ISS_Hedged),cumsum(Low_VOL_ISS_Hedged)))/50))
    abline(h = 50*iter)
  #plot_crisis_dates(High_VOL_ISS_Hedged)
}
@
\caption{Buybacks: High vs Low EU-index Events. Returns of five-factor rolling hedged portfolio for only the buyback events for high and low EU-index companies.  We define low EU-index firms those for which the EU-index is 0-1, and high for which it is 5-6 (note that the index takes values from 0 to 6).  Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio; dashed line is ``high'' and a 48-months holding portfolio, dotted-dash line is ``low'' and a 48-months portfolio.
%Red line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[3],1)}. Black line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[3],1)}. Green line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged48m)[3],1)}. Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[3],1)}. 
We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
%Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
}
\label{fig:badpreviousEU}
\end{figure}

\begin{figure}[H]
\centering
<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=

IRATS_table_all_bb_plot = EU_IRATStable_bb
IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")] <- -IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")]

ylimit = c(min(as.vector(IRATS_table_all_bb_plot[reported_times_plots,which(colnames(IRATS_table_all_bb_plot)=="CAR")])), max(as.vector(IRATS_table_all_bb_plot[reported_times_plots,which(colnames(IRATS_table_all_bb_plot)=="CAR")])))

plot(IRATS_table_all_bb_plot[reported_times_plots,3*6+1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Buybacks - EU index", lwd=2, lty = "solid")
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)

lines(IRATS_table_all_bb_plot[reported_times_plots,1],lwd = 2, lty="dotted")
lines(IRATS_table_all_bb_plot[reported_times_plots,3*1+1],lwd = 2, lty="dotted")
tmp = IRATS_table_all_bb_plot[reported_times_plots,3*1+1]
tmp[c(3*(1:floor(length(tmp)/3)),3*(1:floor(length(tmp)/3))+1)] <- NA
points(tmp, pch=23,lwd=1)

lines(IRATS_table_all_bb_plot[reported_times_plots,3*2+1],lwd = 2, lty="dashed")
lines(IRATS_table_all_bb_plot[reported_times_plots,3*3+1],lwd = 2, lty="dashed")
tmp = IRATS_table_all_bb_plot[reported_times_plots,3*3+1]
tmp[c(3*(1:floor(length(tmp)/3)),3*(1:floor(length(tmp)/3))+1)] <- NA
points(tmp, pch=23,lwd=1)

lines(IRATS_table_all_bb_plot[reported_times_plots,3*4+1],lwd = 2, lty="dotdash")

lines(IRATS_table_all_bb_plot[reported_times_plots,3*5+1],lwd = 2, lty="solid")
tmp = IRATS_table_all_bb_plot[reported_times_plots,3*5+1]
tmp[c(3*(1:floor(length(tmp)/3)),3*(1:floor(length(tmp)/3))+1)] <- NA
points(tmp, pch=23,lwd=1)

abline(v=which(reported_times_plots == "0"), lwd=0.5)
abline(h=0, lwd=0.5)

legend(x="topleft",
       title="EU index value",
       legend = c("6","5","4","3","2","1","0"),
       lty=c("solid","solid","dotdash","dashed","dashed","dotted","dotted"),
       lwd=c(2,2,2,2,2,2),
       pch=c(NaN,23,NaN,23,NaN,23),
       cex=1,bg="white",inset=0.01)

@
\caption{Long-run IRATS five factors cumulative abnormal returns of buybacks depending on the EU-index. From the highest to the lowest lines: solid line is for EU-index 6, solid with diamonds for EU index 5, dotted-dashed for EU index 4, dashed with diamonds for EU index 3, dashed for EU index 2, dotted with diamonds for EU index 1, and finally the lowest dotted line is for EU index 0. The x-axis indicates months from the date of the event announcement.}
\label{fig:Epastall}
\end{figure}

\end{document}

### 2016-01-29 business_data_clean.R

@@ -1,0 +1,79 @@
+
+business_data_removal <- function(events){
+  
+  cleanup = events$cleanup # to avoid losing info when we remove data. we add back at the end of the file
+  
+  BIZ_initial_data = nrow(events$SDC)
+  
+  No_filter = rep(T,length(events$SDC$Event.Date))
+  Basic_filter =  No_filter # !is.na(events$SDC$ME_quantile) & !is.na(events$SDC$BEME_quantile)  
+  Period_filter <- (as.Date(events$SDC$Event.Date) >= First) & (as.Date(events$SDC$Event.Date) <= Last)
+  
+  Penny_stock_filter = ifelse(events$SDC$Event.Date < "1995-01-01", scrub(events$SDC$Closing.Price) >= penny_stock_price_old, scrub(events$SDC$Closing.Price) >= penny_stock_price_recent) 
+  
+  Event_Industry <- suppressWarnings(scrub(as.numeric(events$SDC$Industry))) # 9 industries are 499A or 619A or 619B.. they are removed
+  Industry_filter = Event_Industry %in% Industries
+  US_only = (events$SDC$Currency %in% good_currencies)
+  
+  major_markets_only = sapply(events$SDC$Stock.Exchange, function(i) sum(str_split(i, "\\+")[[1]] %in% major_markets)>0)
+  TOTAL_FILTER_basic = No_filter & Basic_filter & Period_filter & Penny_stock_filter  & Industry_filter & US_only & major_markets_only
+  
+  Market_cap_filter =  (scrub(events$SDC$Market.Cap) >= MIN_SIZE) & (scrub(events$SDC$Market.Cap) <= MAX_SIZE)
+  ME_quantile_filter    =  scrub(events$SDC$ME_quantile)   >= MIN_ME_quantile   & scrub(events$SDC$ME_quantile)    <= MAX_ME_quantile  # & !is.na(events$SDC$ME_quantile)
+  BEME_quantile_filter  =  scrub(events$SDC$BEME_quantile) >= MIN_BEME_quantile & scrub(events$SDC$BEME_quantile)  <= MAX_BEME_quantile #& !is.na(events$SDC$BEME_quantile)   
+  #Leverage_filter = (scrub(events$SDC$lt/events$SDC$at) > 0.5)*(!is.na(events$SDC$lt/events$SDC$at))
+  EventSize_filter = (events$SDC$Event.Size >= MIN_EVENT_SIZE) & (events$SDC$Event.Size <= MAX_EVENT_SIZE)
+  
[…]

### 2016-01-29 latex_code.R

@@ -1,0 +1,636 @@
+######################################################################################
+## Latex commands
+######################################################################################
+
+# CAN EDIT TO PRINT OUT WHATEVER LATEX WE NEED  
+latex_render_data_frame<-function(x,y=NULL, title="",caption="",label="",columns=NULL,bigtitleontop = F,show_rownames=FALSE,red_text="",green_text="",blue_text="",scale=1,digits,lastSpecial=F,dorotate=F) {
+  #Helper functions
+  p <- function(...){paste(...)}
+  pn <- function(...){paste(...,"\n")} #print newline
+  pc <- function(...){paste(...,"&")}  #print column
+  tostars <- function(x) ifelse(abs(x)<0.01,"**",ifelse(abs(x)<=0.05,"*",""))
+  
+  if(dorotate){
+    width = "\\linewidth"
+  } else {
+    width = "\\textwidth"
+  }  
+  #Start the table definition
+  l <- ""  
+  if(dorotate){
+    l <- pn(l,"\\clearpage\n")
+    l <- pn(l,"\\footnotesize")
+    l <- pn(l,"\\begin{landscape}")
+  }
+  l <- pn(l,"\\begin{table}[!htb]")
+  l <- pn(l," \\setlength\\tabcolsep{1pt}")
+  l <- pn(l,"\\centering")
+  #l <- pn(l,"\\medskip")
+  if(bigtitleontop){
+    if(title!="")
+      if(dorotate) {
+        l <- pn(l,"\\captionof{table}{",title,"}")
+      }else {
+        l <- pn(l,"\\caption{",title,"}")
+      }
+    if(caption!="") {
+      l <- pn(l,"\\parbox{",width,"}")
+      l <- pn(l,"{\\scriptsize \\singlespacing",caption,"}\\\\")
+      l <- pn(l,"\\vspace{.2in}")
+      
+    }
+  }
+  #l <- pn(l,"\\scalebox{",scale,"} {")
+  align <- "l"
+  for(i in 1:(ncol(x))) align<-paste(align,"c",sep="")
+  l <- pn(l,"\\footnotesize")  
+  l <- pn(l,"\\begin{tabular*}{",paste(scale,width),"}{@{\\extracolsep{\\fill} }",align,"}")  
+  cat(l)
+  
+  #### THE TABLE STARTS HERE
+  
+  cat("\\\\ \n")
[…]

### 2016-01-29 lib_helpers.R

@@ -1,0 +1,869 @@
+# Required R libraries (need to be installed - it can take a few minutes the first time you run the project)
+
+# installs all necessary libraries from CRAN
+get_libraries <- function(filenames_list) { 
+  lapply(filenames_list,function(thelibrary){    
+    if (do.call(require,list(thelibrary)) == FALSE) 
+      do.call(install.packages,list(thelibrary)) 
+    do.call(library,list(thelibrary))
+  })
+}
+
+libraries_used=c("stringr","gtools","foreign","reshape2","digest","timeDate","devtools","knitr","graphics",
+                 "grDevices","xtable","sqldf","stargazer",
+                 "Hmisc","vegan","fpc","GPArotation","FactoMineR","cluster",
+                 "psych","stringr","googleVis", "png","ggplot2","googleVis", "gridExtra","RcppArmadillo","xts","DescTools")
+
+get_libraries(libraries_used)
+
+options(stringsAsFactors=FALSE)
+
+remove_initialization_time <- function(x,min_date=NULL) { # Note: Added also min_date as an argument!! THis way we remove data from any given date!
+  if (!is.null(min_date)){
+    res = x[as.Date(names(x)) >= as.Date(min_date)]
+  } else {
+    if (x[1] != 0){
+      res = x
+    } else {
+      if (sum(x!=0) != 0){
+        #res = tail(res, -head(which(diff(res)!=0),1))
+        #names(res) <- tail(names(res), -head(which(diff(res)!=0),1))
+        
+        tmp <- names(x)
+        ending <- -head(which(diff(x)!=0),1)
+        res = tail(x, ending)
+        names(res) <- tail(tmp, ending)
+      }
+    }
+  }
+  res
+}
+
+yeardays<-function(x){
+  fd<-as.integer(as.Date(head(names(x),1),format="%Y-%m-%d"))
+  ld<-as.integer(as.Date(tail(names(x),1),format="%Y-%m-%d"))
+  365.25*length(x)/(ld-fd)
+}
+
+vol_pa<-function(x,exclude_zero=(x!=0), holidays = holidayNYSE()) {
+  if(is.null(names(x))){ good_days <- TRUE }else { good_days <- isBizday(as.timeDate(names(x)), holidays, wday = 1:5) }
[…]

### 2016-01-29 report_code.R

@@ -1,0 +1,533 @@
+
+# This file is run only in order to "customize" the over/under valuation events - the rest are all done in report_data.R
+
+reportcode_data<-new.env()
+
+with(reportcode_data,{
+  
+  DATASET = report_data$DATASET     
+  DATASET$Betas_PB6M  = report_data$Betas_PB6M    
+  cleanup = DATASET$cleanup # to avoid losing info when we remove data. we add back at the end of the file
+  # just add some names 
+  DATASET$SDC$event_name = paste(DATASET$SDC$CUSIP, DATASET$SDC$Event.Date, sep="_")
+  colnames(DATASET$Betas_PB6M) <- DATASET$SDC$event_name 
+  
+  #### FIRST THE BUSINESS DECISIONS CLEANUP
+  # Now remove all events for which there was at least another one less than MINIMUM_PERIOD_SINCE_LAST_EVENT before this event
+  recent_events <- which(sapply(1:length(DATASET$SDC$Event.Date), function(ev){
+    all_permno_events = which(DATASET$SDC$permno == DATASET$SDC$permno[ev])
+    sum((DATASET$SDC$Event.Date[ev] - DATASET$SDC$Event.Date[all_permno_events] < MINIMUM_PERIOD_SINCE_LAST_EVENT ) &
+          (DATASET$SDC$Event.Date[ev] - DATASET$SDC$Event.Date[all_permno_events] > 0)) !=0     
+  }))
+  with_recent_event = length(unique(recent_events))
+  cleanup$BIZ_have_previous_recent_event <- with_recent_event 
+  
+  to_remove = unique(recent_events)
+  if (length(to_remove) > 0){
+    # just in alphabetic order not to forget any    
+    DATASET$Abn_returns <- DATASET$Abn_returns[,-to_remove]
+    DATASET$Betas_PB6M <- DATASET$Betas_PB6M[,-to_remove]
+    DATASET$Dates <- DATASET$Dates[,-to_remove]
+    DATASET$DatesMonth <- DATASET$DatesMonth[,-to_remove]
+    DATASET$SDC <- DATASET$SDC[-to_remove,]
+    for(field in ls(DATASET$compustat_data))  DATASET$compustat_data[[field]] <- DATASET$compustat_data[[field]][-to_remove]
+    for(field in ls(DATASET$ibes))  DATASET$ibes[[field]] <- DATASET$ibes[[field]][-to_remove]
[…]

### 2016-01-29 report_data.R

@@ -1,0 +1,69 @@
+
+
+report_data<-new.env()
+
+# THIS CODE USES A DATASET TO GENERATE ALL NECESSARY SLOW TO COMPUTE DATA FOR THE .Rnw AND SAVE THEM IN A FILE WITH THE NAME OF THE DATASET
+with(report_data,{
+  
+  cleanup = DATASET$cleanup # to avoid losing info when we remove data. we add back at the end of the file
+
+  # Add the Dates and order in time
+  DATASET$Dates <- create_dates(as.Date(DATASET$SDC$Event.Date)) # We don't need this any more, can simplify to only get the dates needed... it's ok for now, as it is now slow
+  colnames(DATASET$Dates) <- DATASET$SDC$permno
+  ordered_events = sort(as.numeric(DATASET$SDC$Event.Date),index.return = T)$ix
+  if (length(unique(diff(ordered_events)))!=1)
+    stop(paste("The time order was messed up somewhere"), DATASET$name, sep=" ")
+  rm("ordered_events")
+  
+  DATASET$DatesMonth <- create_dates_month(as.Date(DATASET$SDC$Event.Date)) # We don't need this any more, can simplify to only get the dates needed... it's ok for now, as it is now slow
+  colnames(DATASET$DatesMonth) <- DATASET$SDC$permno
+  
+  ####### Move on with calculating what the .Rnw will later need - whatever is "slow"
+  
+  ########################################################################################################################
+  ### Idiosyncratic risk and Abnormal performance calculation
+  ########################################################################################################################
+  Betas_PB6M <- Betas_lm("Six.Month.Before","One.Day.Before",DATASET$Dates, DATASET$returns_by_event, Risk_Factors)
+  no_beta_available = which(apply(Betas_PB6M,2,function(r) (sum(is.na(r)) !=0)))
+  cleanup$REPORT_no_beta_available = length(no_beta_available) # last cleanup we do!
+  
+  DATASET$SDC$Rsq_returns <- Betas_PB6M["Rsq",]
+  Betas_PB6M  <- Betas_PB6M[setdiff(colnames(Risk_Factors),"RF"),]  
+  
[…]

### 2016-01-29 dataset/Documentation/Readme.Rmd
readme

---
title: "Dataset Documentation"
author: "Theodoros Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, and Theo Vermaelen"
output: html_document
---

<br>

**Share Buyback and Equity Issue Anomalies Revisited: Dataset Creation**

<br>

The datasets can be generated using the raw data from the following databases:

-	S&P500 daily and monthly returns from CRSP
-	The FF factors and breakpoints from the FF website
-	Event data from SDC
-	Daily closing prices, and returns as well as monthly returns, prices, and shares outstanding (to get the market capitalizations) from CRSP
-	All necessary data to calculate the BE/ME ratios of the firms from Compustat (see below) 
-	Quarterly EPS and Sale consensus forecasts and actual values from IBES

Note: when downloading data from the databases (e.g. from SDC), the variables’ names in the .csv files may change. The only changes in the code that may be needed to handle such changes are in x/standardize_data.R and any files used in that code. Moreover, the data period can change as needed.

In this document x notes the event data considered (e.g. buybacks, issuers, or possibly IPOs etc). The steps below are also followed in process_code/create_dataset.R. The final data for each event dataset “x” are saved in dataset/x.Rdata.

<hr>

**Step 1: Get the S&P daily and monthly returns data from CRSP**

Download the S&P monthly and daily returns from CRSP, as described in the query files *Documentation/CRSP Stock Market Indexes Monthly.pdf* and *Documentation/CRSP Stock Market Indexes Daily.pdf*. Save the data as *snp500_monthly.csv* and *snp500.csv* in the directory *indices_and_factors*.

**Step 1b: Get the CRSP universe data used to compute percentiles for various firm characteristics**

Download the daily and monthly returns of the all firms in CRSP during the period, as described in the query files *Documentation/CRSP_universe_returns.pdf and *Documentation/ CRSP_universe_returns_monthly.pdf.

<hr>

**Step 2: Get the Fama-French factors and breakpoints data**

We need both the Fama-French factors as well as the Size and B/P breakpoints. These can be found at FF’s website. We get the following files from that website (saved in the indices_and_factors directory):

-	Fama/French 5 Factors (2x3)
-	Fama/French 5 Factors (2x3) [Daily] (we typically don’t use daily)
-	ME Breakpoints
-	BE/ME Breakpoints

Delete any extra lines at the beginning and at the end of these downloaded csv files. Note that the FF data are available since 1963, hence they cover all reasonable periods.

Once the S&P ad FF csv files are saved, source the file *get_ff_and_market_data.R* (see file for the exact names of datafiles expected). This will format and combine all S&P and FF data and save them in *dataset/indices_and_factors/market_ff_data.Rdata* which will be used throughout the process.

<hr>

**Step 3:  Get the Event Data from SDC**

Both buybacks and issuers event data come from SDC.  Download the event data from SDC Platinum as described in the powerpoint files in

-	*Documentation/SDC Documentation/sdc_x_screenshots.pptx*.

The SDC session and report files used can also be found in the *Documentation/SDC Documentation/* directory. The data need to be saved in x/sdc/sdc_output_x.csv*.  Note: SDC outputs .xls files. When saving them as .csv, make sure to delete the first row of the .xls that says Source: Thomson Reuters   Date: …

<br>

**Step 3b:** Buybacks .csv creation from SDC

Buyback events come from 2 different SDC databases, as indicated in the corresponding .pptx screenshots: the Repurchases and the US Targets, both in the Mergers & Acquisitions database of SDC.  Hence, we manually get from SDC two .csv files for buybacks:

-	*buybacks/sdc/sdc_output_buybacks_repurchases.csv*
-	*buybacks/sdc/sdc_output_buybacks_ma.csv*.

These two files are combined into one file called *buybacks/sdc/sdc_output_buybacks.csv* by *buybacks/sdc/buybacks_rawdata_combine.R*. The latter is sourced within *buybacks/standardise_data.R*, which is called in *process_code/create_dataset.R*. This .csv file combines all features available across the 2 buybacks event data from SDC, leaving missing values as 0s or NA.

<br>

**Step 3c**: Standardize the event datasets

File x/standardize_data.R removes any events for which there is a missing CUSIP or Event Date, renames a number of variables into standard names across event datasets (see Appendix A), and handles duplicate events, defined as those that have the same CUSIP and Event Date. See x/standardize_data.R in each event directory for more details on how duplicates are handled for that event.

 <hr>

**Step 4: Get the daily and monthly data from CRSP**

This step requires a combination of R, python, and manual data download from CRSP. The R and python codes used are in *process_code/get_crsp_data.R*

<br>

**Step 4a: Get the SDC CUSIPs – CRSP PERMNOs Links from CRSP**

First get all cusip-permno pairs in the whole time period, using the CRSP query in 
*Documentation/CRSP_CUSIP_PERMNO.pdf*  (we need the daily data, as events can happen any day of the month), and save in crsp_permno_cusip_pairs/crsp_permno_cusip_pairs.csv.

Note: this data can be used for any data (not only issuers and buybacks) as it covers the whole universe of stocks in the period (e.g. 1980-2014).

Now run the code in process_code/get_crsp_data.R, including the manual python described there. All this does is to create the following two .csv files:

-	*tmp_files/crsp_sdc_link_x.csv*
-	*x/returns/permno_for_crsp_x.csv*

The first file matches the CUSIP-Date pairs from the SDC event data with the CRSP PERMNOS using the *crsp_permno_cusip_pairs/crsp_permno_cusip_pairs.csv* data created above. It is used to append the CRSP PERMNO to the SDC data. The second file is used below to get the data from CRSP using the PERMNOS. When running python one can also see how many CUSIP-Date pairs were not found (as reported in the .Rnw and the paper).

Note: some events data only have 6-digits CUSIP (e.g. the buybacks events from the M&A database in SDC). We have the following options:

-	Option 1: append a 10 at the end of the 6-digits CUSIPs hence creating 8-digit ones. See also the [official CUSIP documentation.](https://www.cusip.com/pdf/CUSIP_Intro_03.14.11.pdf)
-	Option 2: Use the 6-digit CUSIPs whenever the 8-digits one is not available, else use the 8-digits ones, and remove any CRSP data that are duplicate matches (e.g. one 6-digit CUSIP matching multiple 8-digits ones);
-	Option 3: we use only the first 6-digits of all the CUSIPs and again remove any CRSP data that are duplicate matches (e.g. one 6-digit CUSIP matching multiple 8-digits ones);
-	Option 4: Do the same as option (2), but for the available 8-digits CUSIPS we remove all those that do not end in a 10 or 11.

Based on tests done using the code described in *process_code/get_crsp_data.R* and *process_code/cusip6vs8tests.py*, as well as because IBES later (Step 5) needs 8-digits CUSIPs, we follow Option 1. The difference between the various options is minimal. Details are provided in the .Rnw (the paper).

<br>

**Step 4b: Get the daily and monthly data from CRSP**

Get the CRSP daily and monthly data (adjusted returns, closing prices, shares outstanding) from CRSP by using the CRSP queries described in *Documentation/CRSPreturns_daily.pdf*  (for daily) and *Documentation/CRSPreturns_monthly.pdf* (for monthly) and uploading to CRSP the permnos from file x/returns/permno_for_crsp_x.csv created above. Save the downloaded CRSP datasets in:

-	*x/returns/crsp_returns.csv*, for the daily data
-	*x/returns/crsp_returns_monthly.csv*, for the monthly data

<hr>

**Step 5: Get the BE related, ME related, and other data from Compustat**

We use Compustat to get the annual BE/ME ratios of the firm as described in Appendix 1 of 
*Disappearing dividends: changing firm characteristics or lower propensity to pay?, Fama-French, JFE 2001*:

The Preferred Stock and Book Equity equation variables (except the Post Retirement Asset which we get from the *Compustat Monthly Updates - Pension Annual Database*) correspond to the following variables in the CRSP/Compustat Merged - Fundamentals Annual database, in the same order as they appear in the equation:

We use two databases in this step:

-	*CRSP/Compustat Merged - Fundamentals Annual* (under CRSP in WRDS)
-	*Compustat Monthly Updates - Pension Annual* (under Compustat in WRDS)

In this step we also find the appropriate BE/ME and ME thresholds that will then be used in merge_dataset.R to find the BE/ME and ME quantiles. The FF beakpoints require that we use the appropriately lagged BE/ME and Market Capitalization (ME) of the firms (see also Appendix).

<br>

**Step 5a:** First get the *CRSP PERMNO/Compustat GVKEY links* from the *CRSP/Compustat Merged* database using the CRSP/Compustat Merged query described in *Documentation/ CRSP/ LINK CRSP COMPUSTAT.pdf*. Save this data in 
*crsp_compustat_gvkey_pairs/crsp_compustat_gvkey_pairs.csv*

Note that this data can be used for any data (not only issuers and buybacks) as it covers the whole universe of stocks in the period (e.g. 1980-2014).

<br>

**Step 5b:** Run the first part of *get_compustat_data.R*  (see code) to generate this file:

-	*x/compustat/gvkeys_for_compustat_x.csv*

This is a file of all the GVKEYs of the events we found through matching PERMNOs with GVKEYs using *crsp_compustat_gvkey_pairs/crsp_compustat_gvkey_pairs.csv*. It also appends the GVKEYs to the SDC data (so at this stage the SDC data have both PERMNOs and GVKEYs). It also removes all rows for which the assets (AT) or the revenues (REVT) of the firm that year were missing (NAs) or <= 0; all cases for which the “LINKPRIM” was “J” or “N” (see [CRSP documentation here](http://www.crsp.com/files/ccm_data_guide_0.pdf)); and all cases corresponding to PERMNOs that are linked to multiple GVKEYs.

<br>
**Step 5c:** Get the data from CRSP/Compustat Merged - Fundamentals Annual by uploading to this WRDS database the *x/compustat/gvkeys_for_compustat_x.csv* file and using the CRSP/Compustat Merged query described in *Documentation/ CRSP/Compustat Merged - Fundamentals Annual.pdf*. Save this data in:

*x/compustat/compustat_fundamental_annual .csv*

<br>

**Step 5d:** Get the data from Compustat Monthly Updates - Pension Annual by uploading to this WRDS database the *x/compustat/gvkeys_for_compustat_x.csv* file and using the Compustat query described in the Compustat query file *Documentation/Compustat Monthly Updates - Pension Annual.pdf*.  Save this data in:

*x/compustat/compustat_pension_annual .csv*

Note: As indicated in the Compustat queries pdf files, we get data from Compustat for more than 6 years before the first event from SDC, so we can get the BE/ME for them from the very beginning.

<br>

**Step 5e:** Run the second part of *get_compustat_data.R*  (see code) to merge the Compustat data with the existing SDC data so far. The new SDC data with the added Compustat data will be saved again in file dataset/x.Rdata. 
Note: We will deal with the cases where BE < 0 in Step 7 (in *merge_dataset.R*), following the steps described at Ivo Welch’s website – see also Appendix.

<br>

**Step 6: Get x/ibes/ibes_x.csv from IBES**

File *x/ibes/cusip_for_ibes.csv* is generated in *create_dataset.R* and it has all 8-digit CUSIPs from SDC (as noted in Step 2 above, we appended 10 at the of 6-digits CUSIPS). Use this .csv file to get the IBES data from IBES (SUMMARY HISTORY -> SUMMARY STATISTICS) as described in *Documentation/IBES.pdf*. Get the data in .csv format, both EPS and SLS in one file, saved at *x/ibes/ibes_all.csv*. This file will be used next in Step 7 by *merge_data.R* to merge all data.

Note: make sure the data in *x/ibes/cusip_for_ibes.csv* do not have any special characters (e.g. + due to general format), as IBES may then exit.

<hr>

**Step 7: Merge all SDC, CRSP, Compustat and IBES data**

We now merge the CRSP and IBES data into the SDC data (which already has the Compustat information – see above) using *process_code/merge_dataset.R*. See that file to confirm that all necessary .csv and .Rdata files are generated before that file is sourced. Events for which no CRSP return data were found are removed at this stage (see paper for details).

<hr>

**Step 8:  “Light Scrubbing” of the data**

Data scrubbing (e.g. remove further missing values etc, as described in the paper) is done by first *scrub_dataset.R*. This is a “light” data scrubing, removing only any remaining problematic data (see code), in addition to the events removed in *x/standardize_data.R* (see above) and in  *process_code/merge_dataset.R* (see above). The output is the final data that is used by the .Rnw file.

The final data saved in *dataset/x.Rdata*

**Running the report code**

The data generated above is then used by the .Rnw to generate the paper (.pdf file). Part of the analysis may require that further data is removed based on possible new filters.  All these “filters” used for the final paper are included in *load_data.R*, *business_data_clean.R* and *report_data.R*. Moreover, the parameters used by the data filters are in *Paper_global_parameters.R*. Notice that load_data.R also date-aligns all market, Fama-French, and stock returns that are then used throughout the .Rnw.

All analyses in the paper are finally done based on the data coming out of *bb_issuers.R* and any code in the .Rnw of the paper.

**Appendix A: Event Data Names Standardization**

The variable names of the event data (e.g. from SDC) are standardized in x/standardize_data.R so that the code afterwards treats all event data the same.

All standardise_data.R files in the respective datasets' directories need to output these features, plus any other that may be dataset specific (with names exactly like those from SDC so that we can easily find their meaning). We assume all these have NA or 0 for missing values.

**THESE ARE THE STANDARDIZED FEATURES ALL EVENTS DATASETS NEED TO HAVE BEFORE** *process_code/get_crsp_data.R* in *create_dataset.R*:

Note:  Some of these variables that come from Compustat are from a year or more before the event. See *get_compustat_data.R* and *merge_dataset.R* for more information.

<hr>

**Appendix: FF Breakpoints, ME and BE/ME calculations**

File *get_compustat_data.R* and *merge_dataset.R* also calculate the BE, ME, BE/ME, and the 5-quantile features of the companies based on the FF breakpoints from the FF website. FF note that:

-	"We compute BE/ME breakpoints at the end of each June. The BE used in June of year t is the book equity for the last fiscal year end in t-1. ME is price times shares outstanding at the end of December of t-1."    
-	"We compute ME breakpoints for each month. ME is price times shares outstanding (divided by 1,000,000) at month end.”
-	“The (ME) breakpoints for month t use all NYSE stocks that have a CRSP share code of 10 or 11 and have good shares and price data. We exclude closed end funds and REITs.”

Based on these, we do the following:

For BE/ME breakpoints:

We always get the ME/BE breakpoints of the first June before the date of the event – this can be the same or the previous year’s June, depending on whether the date of the event is before/in (hence we get the previous year) or after (hence we get the same year) June.

For BE:

-	If the date of the event is after June, we get the first available BE before the first December before the event (hence in the whole previous year). This is because we compare in this case with the BE/ME breakpoint of the June in the current year. 
-	If the date of the event is before/in June, we get the first available BE before the second December before the date of the event (hence in the year two years before). This is because we compare in this case with the BE/ME breakpoint of the June in the previous year. Note: we consider for now December as the fiscal year end. Since BE does not change fast, this is a reasonable approximation to simplify the code. However, this will be fixed/refined.

For the ME used in the BE/ME calculation:

We do as for the BE, but we use only December ME values of the years selected. ME is the product of CRSP monthly (December) price times CRSP monthly shares outstanding, divided by 1000 (as shares outstanding are in 1000s).

For ME breakpoints and corresponding ME of the companies:

We get the ME breakpoints and companies’ ME the month before the date of the event – we have these monthly.

Dealing with negative BEs values:

BE values are sometimes negative (see also Ivo Welch’s website) We deal with them as suggested in that website (see merge_dataset.R):

-	First we set to NA those cases for which the debt (Compustat dlc_dltt) is negative;
-	For the remaining cases, we set BE to the max(0, (1/100)*(dlc+dltt), (0.1/100)*at)

**Appendix C: Other data to consider**

-	[Ivo Welch Website](http://www.ivo-welch.info/professional/leverage.placebo/)

### 2016-01-29 dataset/Documentation/Readme.Rmd
doc figs

@@
 We use Compustat to get the annual BE/ME ratios of the firm as described in Appendix 1 of 
-*Disappearing dividends: changing firm characteristics or lower propensity to pay?, Fama-French, JFE 2001*:
+[Disappearing dividends: changing firm characteristics or lower propensity to pay?, Fama-French, JFE 2001](http://www.ulb.ac.be/cours/solvay/farber/Ofin/Reading%206%20Disappearing%20dividend.pdf):
 
 The Preferred Stock and Book Equity equation variables (except the Post Retirement Asset which we get from the *Compustat Monthly Updates - Pension Annual Database*) correspond to the following variables in the CRSP/Compustat Merged - Fundamentals Annual database, in the same order as they appear in the equation:
+
+![Preferred Stock and Book Equity equation variables ](fig3.png)
+
+The Preferred Stock and Book Equity equation variables (except the Post Retirement Asset which we get from the Compustat Monthly Updates - Pension Annual Database) correspond to the following variables in the CRSP/Compustat Merged - Fundamentals Annual database, in the same order as they appear in the equation:
+
+![Preferred Stock and Book Equity equation variables Selected](fig2.png)
 
@@
 
+![(Draft) List of Dataset Variables](fig1.png)
+
+At the end we have the following variables (for buybacks and issuers):
+
+![(Draft) List of Dataset Variables](buybacks.png)
+
+![(Draft) List of Dataset Variables](issuers.png)
+
 <hr>

### 2016-02-01 index.Rmd
interactive tool draft 1

---
title: "Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool"
author: "Theodoros Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, and Theo Vermaelen"
output:  
  html_document:
    fig_width: 6
    fig_height: 2.5
    fig_align: center
runtime: shiny
---

```{r, eval=TRUE, echo = FALSE}
#load("bb_issuersALL.Rdata")
load("bb_issuersTOOL.Rdata")

#library(googleVis)
#library("shiny")
#library("reshape2")  
#library("ggplot2")
# Why are these not found when deployed?!
library("stringr")
library("RcppArmadillo")
library("gtools")
library("timeDate")
source("lib/lib_helpers_shiny.R")
source("lib/Paper_global_parameters.R")
source("lib/heatmapOutput.R")
source("lib/plots.R")

DATASET = BUYBACK_DATA$DATASET

```

This is an interactive tool for the article **Share Buyback and Equity Issue Anomalies Revisited**. Users can explore the effects of various parameters as well as data sampling choices. For any given choice, users can generate and download a new *customized* version of the paper by clicking the button below at any time:**
<br>
<br>

```{r, fig.width=6, fig.height=5,echo=FALSE}
downloadHandler(
  filename = "report.pdf",
  content = function(file) {
    src <- normalizePath('BBtool_pdf.Rmd')
    # temporarily switch to the temp dir, in case you do not have write
    # permission to the current working directory
    #owd <- setwd(tempdir())
    #on.exit(setwd(owd))
    #file.copy(src, 'ExerciseSet2v2pdf.Rmd')
    #library(rmarkdown)
    out <- render('BBtool_pdf.Rmd', pdf_document(),envir=environment())
    file.rename(out, file)
  }
)
```

<hr>

### Descriptive Statistics

This tool allows the user to explore descriptive statistics of some of the key firm characteristics. When the name of the firm characteristics ends with ".Score" it is  either the 1-5 score relative to the Fama-French breakpoints (for Size, Prior returns, and BE/ME ratio) or the percentile relative to all firms in the CRSP universe at the time of the buyback announcement, as discussed in the paper. Otherwise it is the raw values of the firm characteristic.

```{r, eval=TRUE, echo = FALSE}
acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index","Industry", "Market.Cap",          "Percent.Shares", "Purpose.Code","Source.of.funds","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio", "Year")

fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[1]),
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Histogram",
                         renderPlot({
                           feature = BUYBACK_DATA$DATASET$SDC[[which(names(BUYBACK_DATA$DATASET$SDC) == input$characteristic)]]
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Summary Statistics",
                         renderDataTable({
                           feature = BUYBACK_DATA$DATASET$SDC[[which(names(BUYBACK_DATA$DATASET$SDC) == input$characteristic)]]
                           #feature = feature[!is.na(feature)]
                           if (length(unique(feature)) > 20 & is.numeric(feature)){
                             res = t(as.matrix(summary(feature)))
                             colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                           }
                           if (is.character(feature) | length(unique(feature)) <= 20){
                             tmp = table(feature)
                             res = t(as.matrix(tmp))
                           }
                           as.data.frame(res)
                           #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                           #print(m1,'chart')
                         })
                )
    ),style='width: 100%;'))
```

### Robustness Analysis

Two types of robustness analysis has been considered in the paper: over different time periods, and across industries. This tool allows a more detailed robustness analysis along the lines of the results presented in the paper:

<hr>

### Buybacks and Firm Characteristics

The article relates 5 firm characteristics (pre-buyback-announcement returns, idiosyncratic volatility, and volatility, as well as BE/ME and Firm Size). This tool allows the user to study the effects of combining any of these firm characteristics, as well as some other ones not studied in the paper for simplicity.

```{r, eval=TRUE, echo = FALSE}
acceptaple_features1 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio")

selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features1,selected = acceptaple_features1[1])

selectInput("quantile_used","Enter the quantile to use to define High and Low Firms:", choices = 0.02*(1:20), selected = "0.2")

feature_IRATStable <- reactive({
  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    car_table(DATASET$returns_by_event_monthly[,Low_feature_events], DATASET$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    car_table(DATASET$returns_by_event_monthly[,High_feature_events], DATASET$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

High_feature_Hedged_react <- reactive({
  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET$DatesMonth, DATASET$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
})

Low_feature_Hedged_react <- reactive({
  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats)]]  
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET$DatesMonth, DATASET$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

```

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         renderTable({
                           feature_IRATStable()
                         })),
                tabPanel("Cumulative Abnormal Returns,High, 12m hold",
                         renderDygraph({
                           pnl_plot_interactive(High_feature_Hedged_react())
                         })),
                tabPanel("Monthly and Yearly Returns, High, 12m hold",
                         renderUI({
                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react()))
                         })
                )
    ),style='width: 100%;'))
```

### Customizable Buyback Index

Must like the EU-index in the paper, one can create other indices by combining different firm characteristics as needed.

```{r, eval=TRUE, echo = FALSE}
acceptaple_features2 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","None")
```

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats1", "Select First Firm Characteristic for your new index:", choices = acceptaple_features2,selected = acceptaple_features2[1], width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}

selectInput("characteristic_irats2", "Select Second Firm Characteristic for your new index:", choices = acceptaple_features2,selected ="None", width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}

selectInput("characteristic_irats3", "Select Third Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}

selectInput("characteristic_irats4", "Select Fourth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}

selectInput("characteristic_irats5", "Select Fifth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}

selectInput("characteristic_irats6", "Select Sixth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}

selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low), 1 (middle), 2 (High) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}

selectInput("quantile_used_all","Enter the quantile to use to define High and Low Firms for the total index created (sum of the scores of the firm characteristics selected):", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

```{r, eval=TRUE, echo = FALSE}
selected_features = reactive({
  paste(setdiff(unique(c(input$characteristic_irats1,input$characteristic_irats2,input$characteristic_irats3,input$characteristic_irats4,input$characteristic_irats5,input$characteristic_irats6)), "None"), sep=",")
})

```

<br>

<br> 
Here are the results for your new index:

<br>
```{r, eval=TRUE, echo = FALSE}

Index_Score_rect <- reactive({

  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats1)]]  
  High_feature_events1 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  Low_feature_events1 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))

  High_feature_events2 <- High_feature_events3 <- High_feature_events4 <- High_feature_events5 <- High_feature_events6 <- rep(FALSE,length(High_feature_events1))
  Low_feature_events2 <- Low_feature_events3 <- Low_feature_events4 <- Low_feature_events5 <- Low_feature_events6 <- 
    rep(FALSE,length(Low_feature_events1))

  if (input$characteristic_irats2 != "None"){
    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats2)]]  
    High_feature_events2 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events2 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats3 != "None"){
    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats3)]]  
    High_feature_events3 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events3 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats4 != "None"){
    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats4)]]  
    High_feature_events4 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events4 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats5 != "None"){
    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats5)]]  
    High_feature_events5 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events5 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats6 != "None"){
    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats6)]]  
    High_feature_events6 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events6 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }

  Index_score = 
    2*High_feature_events1 + 1*(!High_feature_events1 & !Low_feature_events1) + 
    (input$characteristic_irats2 != "None")*(2*High_feature_events2 + 1*(!High_feature_events2 & !Low_feature_events2) ) + 
    (input$characteristic_irats3 != "None")*(2*High_feature_events3 + 1*(!High_feature_events3 & !Low_feature_events3) ) + 
    (input$characteristic_irats4 != "None")*(2*High_feature_events4 + 1*(!High_feature_events4 & !Low_feature_events4) ) + 
    (input$characteristic_irats5 != "None")*(2*High_feature_events5 + 1*(!High_feature_events5 & !Low_feature_events5) ) + 
    (input$characteristic_irats6 != "None")*(2*High_feature_events6 + 1*(!High_feature_events6 & !Low_feature_events6) )

  Index_score

})

feature_IRATStable_index <- reactive({

  thefeature = Index_Score_rect()

  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))

  res = round(cbind(
    car_table(DATASET$returns_by_event_monthly[,Low_feature_events], DATASET$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    car_table(DATASET$returns_by_event_monthly[,High_feature_events], DATASET$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

High_feature_Hedged_react_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET$DatesMonth, DATASET$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
})

Low_feature_Hedged_react_index <- reactive({
  thefeature = Index_Score_rect()
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET$DatesMonth, DATASET$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

```

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         renderTable({
                           feature_IRATStable_index()
                         })),
                tabPanel("Histogram of the New Index",
                         renderPlot({
                           feature = Index_Score_rect()
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Cumulative Abnormal Returns,High, 12m hold",
                         renderDygraph({
                           pnl_plot_interactive(High_feature_Hedged_react_index())
                         })),
                tabPanel("Monthly and Yearly Returns, High, 12m hold",
                         renderUI({
                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index()))
                         })
                )
    ),style='width: 100%;'))
```

### 2016-02-15 bb_issuers.Rnw
updating tool

@@
 #load("tmpfiles/bb_issuersALL.Rdata")
-reload_data = 1
+reload_data = 0
 
 # Then to make it into Word: 
-# pandoc -s bb_issuers.tex --bibliography=bibliography.bib --number-sections --reference-links -o wordfilename.docx
+# pandoc -s bb_issuers.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx
 
@@
 
-%Blind title page
-\begin{titlepage}
-\begin{center}
+%%Blind title page
+%\begin{titlepage}
+%\begin{center}
 %  \centering
-\vskip 60pt
-\LARGE Share Buyback and Equity Issue Anomalies Revisited \par
-\vskip 1.5em
-\normalsize  \today
-\noindent \\ 
-\begin{abstract}
-\noindent We re-examine the behavior of stock returns after share buyback and equity issuance announcements using the five-factor model proposed by \cite{FamaFrench2015a}.
+%\vskip 60pt
+%\LARGE Share Buyback and Equity Issue Anomalies Revisited \par
+%\vskip 1.5em
+%\normalsize  \today
+%\noindent \\ 
+%\begin{abstract}
+%\noindent We re-examine the behavior of stock returns after share buyback and equity issuance announcements using the five-factor model proposed by \cite{FamaFrench2015a}.
 We confirm the findings of \cite{FamaFrench2015b} that the equity issue anomaly, i.e., the fact that equity issues are followed by negative long-term excess returns, disappears after replacing the \cite{FamaFrench1993} three-factor model with the five-factor model.
-However, long term positive excess returns after buyback announcements, first reported by Ikenberrry, Lakonishok and Vermaelen (1995), remain economically and statistically significant.
+However, long term positive excess returns after buyback announcements, first reported by \cite{IkenberryLakonishokVermaelen1995}, remain economically and statistically significant.
 Moreover, the Undervaluation Index proposed by \cite{PeyerVermaelen2009} remains a useful proxy for the likelihood that the buyback is driven by undervaluation.
@@
 Firms with low correlations with the market seem to be better at market timing, which is consistent with the hypothesis that the repurchase is driven by superior company-specific information.
-Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by Ikenberry and Vermaelen (1996).
+Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by \cite{IkenberryVermaelen1996}.
+This result is also consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks, unlike the well-known low volatility anomaly across all stocks.
 Finally, based on these findings, we develop an enhanced Undervaluation Index that improves abnormal returns relative to the index developed by \cite{PeyerVermaelen2009}.
-\end{abstract}
-
-\vspace{2cm}
-
-\end{center}
-
-\medskip
-
-\noindent \textit{JEL classification}: G35
-
-\medskip
-\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings
-
-\end{titlepage}
+%\end{abstract}
+%\vspace{2cm}
+%\end{center}
+%\medskip
+%\noindent \textit{JEL classification}: G35
+%\medskip
+%\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings
+%\end{titlepage}
 
@@
 We confirm the findings of \cite{FamaFrench2015b} that the equity issue anomaly, i.e., the fact that equity issues are followed by negative long-term excess returns, disappears after replacing the \cite{FamaFrench1993} three-factor model with the five-factor model.
-However, long term positive excess returns after buyback announcements, first reported by Ikenberrry, Lakonishok and Vermaelen (1995), remain economically and statistically significant.
+However, long term positive excess returns after buyback announcements, first reported by \cite{IkenberryLakonishokVermaelen1995}, remain economically and statistically significant.
 Moreover, the Undervaluation Index proposed by \cite{PeyerVermaelen2009} remains a useful proxy for the likelihood that the buyback is driven by undervaluation.
@@
 Firms with low correlations with the market seem to be better at market timing, which is consistent with the hypothesis that the repurchase is driven by superior company-specific information.
-Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by Ikenberry and Vermaelen (1996).
+Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by \cite{IkenberryVermaelen1996}.
+This result is also consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks, unlike the well-known low volatility anomaly across all stocks.
 Finally, based on these findings, we develop an enhanced Undervaluation Index that improves abnormal returns relative to the index developed by \cite{PeyerVermaelen2009}.
@@
 
-Finally, the long-term event studies do not give much guidance about when to sell after a buyback or cover after shorting an equity issue.
+The long-term event studies also do not give much guidance about when to sell after a buyback or cover after shorting an equity issue.
 Trading strategies, such as $M\&A$ arbitrage (\cite{MitchellPulvino2001}), often have ``natural'' exit decision points (e.g., at $M\&A$ deal completion or termination), but the literature does not provide clear guidance about when to exit a buyback position.
 Empirical studies tend to show that, on average, excess returns continue for up to 3 or 4 years after a buyback authorization, but there is no reason why such a horizon is optimal.
-The passive nature of the strategy may also give the impression that the strategy is too simple to justify management fees.
 One straightforward ``early'' selling strategy that we study is to combine the buyback and equity issuance anomalies by selling buyback stocks after the firm announces an equity issue.
 Note that the fact that equity issues in general are followed by negative abnormal returns does not necessarily imply that equity issues after buybacks should generate the same result.
-Given our focus on buybacks and equity issuance, we do not study other possible exit signals, such as missing analysts' estimates (e.g., \cite{PeyerVermaelen2009}), take over bids (e.g., \cite{Linetal2014}), or other company events.
+
+Finally, the results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously.
+Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information.
+If the buyback signals a change in risk (\cite{GrullonMichaely2004}) hedging market risk may be complicated.
+That is why in this paper we also simulate hedged investment strategies where we estimate risk {\it before} forming the portfolios.
 
@@
 \cite{Linetal2014}) our focus is on the \cite{FamaFrench2015a} challenge.
-We are also agnostic on the source of misvaluation, e.g., undervaluing cash flows or overestimating risk (\cite{GrullonMichaely2004}).
 We confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
@@
 The interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive.
-
-We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns and that the anomaly does not disappear if we exclude specific industries.
-Moreover, the predictive capacity can be significantly enhanced if we incorporate two additional indicators that are expected to be correlated with misvaluation.
-First,  idiosyncratic risk, which measures to what extent stock prices are driven by company-specific information.
-Unlike \cite{Ang2006}, who find a negative relation between idiosyncratic volatility and future returns, and \cite{FamaFrench2015b}, who show similar evidence for small firms, we find
-a positive relation for buyback stocks.
-This is consistent with \cite{Stambaugh2015} who find a positive relation for undervalued\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  stocks.
-The second indicator to be correlated with misvaluation is  volatility.
-The argument is that a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks (\cite{IkenberryVermaelen1996}).
-Combining these new measures with the Peyer-Vermaelen (2009) Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns.
+We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries.
+
+We also test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}: that (idiosyncratic) volatility is negatively related to future returns.
+For example, \cite{Ang2006} find negative alphas for high volatility and high idiosyncratic volatility stocks, using the 3 factor \cite{FamaFrench1993} model.
+Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms.
+However, in our buyback sample we find a significant positive relation between excess returns, using  the Fama-French 5-factor model as a benchmark.
+This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market.
+The result is also consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  stocks.
+
+Turning to total volatility we also find that buyback authorizations of high risk stocks are followed by larger excess returns.
+This is consistent with the {\it option hypothesis}:  a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks (\cite{IkenberryVermaelen1996}).
+If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.
+Combining idiosyncratic risk and total volatility  with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns.
 In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
@@
 
-To further study the robustness of the buyback anomaly over time, we simulate a portfolio investment strategy starting in \Sexpr{firstyear}.
+\subsection{Robustness with respect to estimation of factor betas}
+\label{sec:robustbeta}
+
+Note that both event study methods measure alpha (excess return) and betas jointly.
+In other words, we do not use prior (to investing) information to estimate risk.
+An investor who wants to exploit the anomaly, however, may want to hedge market (and other) risk and would need to estimate betas using past data.
+If the buyback signals a change in risk (\cite{GrullonMichaely2004}) it is not obvious that such a hedged strategy would work.
+
+To further study the robustness of the buyback anomaly, we simulate a portfolio investment strategy starting in \Sexpr{firstyear}.
 The strategy uses past data to estimate the factor betas and measures the abnormal returns of buyback portfolios over different investment horizons.
@@
 This allows an investor to determine the betas for the factor risks using data available at the time of portfolio formation.
-
-Note that, as there is no hindsight and all betas are estimated every month using past data, the portfolio used to estimate the betas may consist of firms that are different from those of the (newly created) portfolio that is hedged - as we do not know when companies will announce a buyback.
-On the other hand, note that unlike this strategy, both the IRATs and calendar event study results use hindsight to estimate risk.
-However, despite using pre-portfolio formation data to estimate the betas, the returns of the overall strategy have very low betas with the five factors.\footnote{For example for the $N =12$ months holding period discussed below, the betas for the five factors Market, SMB, HML, RMW, and CMA are respectively \Sexpr{round(expost_betas[2,1],3)}, \Sexpr{round(expost_betas[3,1],3)}, \Sexpr{round(expost_betas[4,1],3)}, \Sexpr{round(expost_betas[5,1],3)} and \Sexpr{round(expost_betas[6,1],3)}.
-The corresponding betas for the ``unhedged'' strategy are \Sexpr{round(expost_betas_unhedged[2,1],3)}, \Sexpr{round(expost_betas_unhedged[3,1],3)}, \Sexpr{round(expost_betas_unhedged[4,1],3)}, \Sexpr{round(expost_betas_unhedged[5,1],3)} and \Sexpr{round(expost_betas_unhedged[6,1],3)}.
-This also indicates that the returns shown in Figure~\ref{fig:ReturnsBB} and Table~\ref{tbl:allhedgedBB} are close to excess returns.
-Getting pure excess returns in practice requires more detailed hedging (without hindsight).
-}
 
@@
 In only one year (\Sexpr{rownames(tmp)[which.min(tmp[,13])]}) the strategy generates an abnormal loss larger than \Sexpr{round(abs(sort(tmp[,13])[2]),1)}$\%$.
+
+Despite using pre-portfolio formation data to estimate the betas, unlike both the IRATs and Calendar Time methods that use hindsight to estimate risk, the hedged portfolio has very low betas with the five factors.
+For example for the $N =12$ months holding period, the betas for the five factors Market, SMB, HML, RMW, and CMA are respectively \Sexpr{round(expost_betas[2,1],3)}, \Sexpr{round(expost_betas[3,1],3)}, \Sexpr{round(expost_betas[4,1],3)}, \Sexpr{round(expost_betas[5,1],3)} and \Sexpr{round(expost_betas[6,1],3)}.
+The corresponding betas for the ``unhedged'' strategy are \Sexpr{round(expost_betas_unhedged[2,1],3)}, \Sexpr{round(expost_betas_unhedged[3,1],3)}, \Sexpr{round(expost_betas_unhedged[4,1],3)}, \Sexpr{round(expost_betas_unhedged[5,1],3)} and \Sexpr{round(expost_betas_unhedged[6,1],3)}.
+This also indicates that the returns shown in Figure~\ref{fig:ReturnsBB} and Table~\ref{tbl:allhedgedBB} are close to ``excess'' returns, i.e.
+returns that have basically eliminated all factors risk.
+This is also consistent with the hypothesis that the buyback announcement itself does not materially change the risk of the repurchasing firms (in the short term).
 
@@
 
-\section{Enhancing the U-index: \\
-Idiosyncratic Risk and Volatility}
+\section{Excess returns and volatility}
 \label{sec:infoassymetry}
+
+There exists a large literature on volatility and stock returns.
+One of the most puzzling findings is the fact that total volatility and idiosyncratic volatility are negatively correlated with future abnormal returns, when expected returns are calculated using the 3 factor \cite{FamaFrench1993} model  (see e.g.
+\cite{Ang2006} (Table VII)).
+This volatility anomaly also survives after using the \cite{FamaFrench2015a} 5-factor model, at least for small firms.
+Perhaps the buyback and the volatility anomaly are related: are the buyback firms with the largest excess returns also firms with the smallest (idiosyncratic) risk?
+Or can we make arguments that the opposite is true, if we accept the fundamental proposition of this paper, i.e.
+that excess returns are a result of the fact that managers are on average successful in taking advantage of an undervalued stock price?
 
@@
 Such situations are more likely in industries or companies where the value is driven less by market wide factors, i.e., by highly ``idiosyncratic'' companies.
+So if buybacks are driven by market timing this superior information hypothesis predicts that there should be a positive relation between idiosyncratic returns and volatility.
 To test this hypothesis, for each event we measure the five-factor regression $R^2$ using the 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month, or using the idiosyncratic volatility as in \cite{Ang2006}, leads to the same conclusions - results available upon request.
@@
 
-Figure~\ref{fig:badpreviousR2}  shows the results of a strategy similar to the strategy of Figure~\ref{fig:ReturnsBB} (Panel~B): starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous N months and hold the stock for $N$ months.
-The graph shows two strategies, one for a short holding period ($N=12$) and one for a very long holding period ($N=48$).
-In both cases the excess returns for high idiosyncratic companies are higher.
-Specifically, high idiosyncratic companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy.
-These excess returns are higher than the \Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged48m),1),1)}$\%$) of the corresponding low idiosyncratic sample.
-
-Table~\ref{tbl:IdiosyncraticunderBB}  confirms this result in a more systematic way.
-It shows the IRATS and Calendar Time abnormal returns for high and low idiosyncratic buyback events-companies.
+Table~\ref{tbl:IdiosyncraticunderBB} shows the IRATS and Calendar Time abnormal returns for high and low idiosyncratic buyback events-companies.
 Focusing on IRATS, high idiosyncratic buyback stocks earn \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$  after 48 months, more than three times the excess returns of the low idiosyncratic announcements.
 The results using the Calendar Time method confirm these findings.
-
 Table~\ref{tbl:IdiosyncraticunderBB} also tests whether adjusting for idiosyncratic risk improves the predictive power of the U-index.
@@
 The Calendar Time results provide the same picture: only for the high idiosyncratic, high U-index firms we obtain significant (t=\Sexpr{R2_IRATStable_underBB_cal["+48",8]}) monthly excess returns of \Sexpr{R2_IRATStable_underBB_cal["+48",7]}$\%$.
-The high idiosyncratic and low U-index firms have  non-significant (t=\Sexpr{R2_IRATStable_underBB_cal["+48",11]}) monthly excess returns of \Sexpr{R2_IRATStable_underBB_cal["+48",10]}$\%$.
+The high idiosyncratic and low U-index firms have  non-significant (t=\Sexpr{R2_IRATStable_underBB_cal["+48",11]}) monthly excess returns of \Sexpr{R2_IRATStable_underBB_cal["+48",10]}$\%$.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
+Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
+High idiosyncratic companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy.
+These excess returns are higher than the \Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged48m),1),1)}$\%$) of the corresponding low idiosyncratic sample.}
 
@@
 The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \cite{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns.
-This is commonly referred to as the volatility puzzle.
 However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks.
@@
 This enhances the timing ability of the manager-insider.
+They show that this option can have a lot of value, something that may not be realized at the time of the announcement of the buyback authorization.
 Hence, perhaps total volatility is a better prediction of excess returns than idiosyncratic volatility or the U-index.
@@
 
-Figure~\ref{fig:badpreviousVOL} shows the results of a strategy similar to the strategy of Figure~\ref{fig:ReturnsBB}: starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
-The graph shows two strategies, one for a short holding period ($N=12$) and one for a very long holding period ($N=48$).
-In both cases the excess returns for high volatility companies is higher.
-Specifically, high volatility companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy, which are higher than the \Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged48m),1),1)}$\%$) of the corresponding low volatility sample.
-
-Table~\ref{tbl:VOLunderBB} confirms this result in a more systematic way.
-It shows the IRATS and Calendar Time abnormal returns for high and low volatility buybacks events-companies.
+Table~\ref{tbl:VOLunderBB} shows the IRATS and Calendar Time abnormal returns for high and low volatility buybacks events-companies.
 Focusing on IRATS, high volatility buyback stocks earn \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$  after 48 months, while low volatility events have non significant abnormal returns for any period.
-The results using the Calendar Time method confirm these findings.
+The results using the Calendar Time method confirm these findings.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
+Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
+High volatility companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy, which are higher than the \Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged48m),1),1)}$\%$) of the corresponding low volatility sample.}
 
@@
 The Calendar Time results provide the same picture.
-Figure~\ref{fig:badpreviousVOL} summarizes the results for the total sample and the high and low U-index sample.
-The main difference with Figure~\ref{fig:badpreviousR2} is that now also low volatility/high U-index firms earn significant excess returns of 15.3$\%$ after 48 months.
+Figure~\ref{fig:pastallVOL} summarizes the results for the total sample and the high and low U-index sample.
+The main difference with Figure~\ref{fig:pastallidio} is that now also low volatility/high U-index firms earn significant excess returns of \Sexpr{VOL_IRATStable_underBB["+48",1]}$\%$ after 48 months.
 
@@
 Table~\ref{tbl:underidioallBB} shows how the high/low U-index  low/high idiosyncratic risk, and low/high volatility buyback events overlap, while Table~\ref{tbl:underidioallBBcor} shows the correlations between the idiosyncratic, volatility, and U-index scores.
-Overall we see that although high U-index firms tend to have high idiosyncratic risk and highly volatility, and high idiosyncratic risk firms tend to also have high volatility the overlap is not very high: for example from Table~\ref{tbl:underidioallBB} we learn that  only \Sexpr{round(Under_IdioBB["High Vol.","H Idiosync."],1)}$\%$ of the high volatility stocks that are classified as having either high or low idiosyncratic risk - note that we only consider the  \Sexpr{round(100*quantile_R2,2)}$\%$ tails - have high idiosyncratic risk.
+Overall we see that although high U-index firms tend to have high idiosyncratic risk and high volatility, while high idiosyncratic risk firms tend to also have high volatility, the overlap is not very high.
+For example from Table~\ref{tbl:underidioallBB} we learn that  only \Sexpr{round(Under_IdioBB["High Vol.","H Idiosync."],1)}$\%$ of the high volatility stocks that are classified as having either high or low idiosyncratic risk - note that we only consider the  \Sexpr{round(100*quantile_R2,2)}$\%$ tails - have high idiosyncratic risk.
 From Table~\ref{tbl:underidioallBBcor} we infer that the correlation between idiosyncratic risk and volatility is only \Sexpr{round(Under_IdioBB_cor["Volatility Score","Idiosyncratic Score"]*100,1)}$\%$.
@@
 
-Figure~\ref{fig:badpreviousEU} shows the results of a strategy similar to the strategy of Figure~\ref{fig:ReturnsBB}: starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
-The graph shows two strategies, one for a short holding period ($N=12$) and one for a very long holding period ($N=48$).
-In both cases the excess returns for high EU-index companies is significantly higher than for low EU-index companies.
-We define low EU-index firms those for which the EU-index is 0-1, and high for which it is 5-6 (note that the index takes values from 0 to 6).
-Specifically, the 12-month holding period high EU-index portfolio has average annual abnormal returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[1],1)}$\%$, while the low EU-index one earns only \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[1],1)}$\%$ annual excess returns.
-For the 48-month holding periods the high and low EU-index portfolio earn annual excess returns of  respectively, \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[1],1)}$\%$ and \Sexpr{round(pnl_stats(Low_EU_BB_Hedged48m)[1],1)}$\%$.
-
 Tables  \ref{tbl:EUunderBB} and \ref{tbl:EUunderBBcal} show respectively the IRATS and Calendar Time monthly abnormal returns for all values of the EU-index.
@@
 The Calendar Time results are similar although they only show significance starting at EU-index levels of 4.
-Investing in the very high EU index firms (EU=6) generates alphas of \Sexpr{round(EU_CALtable_bb["+48",19],2)}$\%$ per month for 48 months.
+Investing in the very high EU index firms (EU=6) generates alphas of \Sexpr{round(EU_CALtable_bb["+48",19],2)}$\%$ per month for 48 months.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
+Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
+The 12-month holding period high EU-index portfolio has average annual abnormal returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[1],1)}$\%$, while the low EU-index one earns only \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[1],1)}$\%$ annual excess returns.
+For the 48-month holding periods the high and low EU-index portfolio earn annual excess returns of  respectively, \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[1],1)}$\%$ and \Sexpr{round(pnl_stats(Low_EU_BB_Hedged48m)[1],1)}$\%$.}
 
@@
 
-Finally, Table~\ref{tbl:EUhedgedBB}, like Table~\ref{tbl:allhedgedBB}, shows the monthly and yearly returns of a five-factors hedged strategy investing only in the high EU-index repurchase events.
+%Finally, Table~\ref{tbl:EUhedgedBB}, like Table~\ref{tbl:allhedgedBB}, shows the monthly and yearly returns of a five-factors hedged strategy investing only in the high EU-index repurchase events.
 The table shows the robustness of the abnormal returns over time.
@@
   columns2 = c("EU-index 4","EU-index 5","EU-index 6"),
-  title="Buyback announcements Calendar for all EU-index Values",
+  title="Buyback announcements Calendar Time for all EU-index Values",
   caption="IRATS five factor cumulative abnormal returns after open market repurchase announcements for each Enhanced Undervaluation Index value from 0 to 6.
@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-
+if (0){
   latex_render_data_frame(
@@
   )
+}
 @
@@
 
-\begin{figure}[H]
-\centering
+%\begin{figure}[H]
+%\centering
 << badpreviousR2, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
 #par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))
-
+if (0){
   plot(cumsum(100*High_Idiosyncr_BB_Hedged),type="l",ylab="CAR", xlab = "Time",main = "",  lwd=2, axes = FALSE, 
@@
   }
-@
-\caption{Buybacks: High versus Low Idiosyncratic Events.
+}
+@
+%\caption{Buybacks: High versus Low Idiosyncratic Events.
 Returns of five-factor rolling hedged portfolio for only the buyback events for high and low idiosyncratic company.
@@
 Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged48m)[3],1)}.
-We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
+%We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
 %Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
-}
-\label{fig:badpreviousR2}
-\end{figure}
+%}
+%\label{fig:badpreviousR2}
+%\end{figure}
 
@@
 
-\begin{figure}[H]
-\centering
+%\begin{figure}[H]
+%\centering
 << badpreviousVOL, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
 #par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))
-
+if (0){
   plot(cumsum(100*High_VOL_BB_Hedged),type="l",ylab="CAR", xlab = "Time",main = "", lwd=2, axes = FALSE, 
@@
   }
-@
-\caption{Buybacks: High vs Low Volatility Events.
+}
+@
+%\caption{Buybacks: High vs Low Volatility Events.
 Returns of five-factor rolling hedged portfolio for only the buyback events for high and low volatility company.
@@
 Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged48m)[3],1)}.
-We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
+%We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
 %Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
-}
-\label{fig:badpreviousVOL}
-\end{figure}
+%}
+%\label{fig:badpreviousVOL}
+%\end{figure}
 
@@
 
-\begin{figure}[H]
-\centering
+%\begin{figure}[H]
+%\centering
 << badpreviousEU, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
+if (0){
   #par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))
@@
   }
-@
-\caption{Buybacks: High vs Low EU-index Events.
+}
+@
+%\caption{Buybacks: High vs Low EU-index Events.
 Returns of five-factor rolling hedged portfolio for only the buyback events for high and low EU-index companies.
@@
 Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[3],1)}.
-We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
+%We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
 %Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
-}
-\label{fig:badpreviousEU}
-\end{figure}
+%}
+%\label{fig:badpreviousEU}
+%\end{figure}
 

### 2016-02-15 index.Rmd
updating tool

@@
 title: "Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool"
-author: "Theodoros Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, and Theo Vermaelen"
+author: "[Theodoros Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), [Enric Junque de Fortuny](ciri.be/), [Nick Nassuphis](https://www.linkedin.com/in/nick-nassuphis-8029372), and [Theo Vermaelen](http://faculty.insead.edu/theo-vermaelen/)"
 output:  
@@
 
-DATASET = BUYBACK_DATA$DATASET
-
+DATASET_INI = BUYBACK_DATA$DATASET
+DATASET_INI$SDC = as.data.frame(DATASET_INI$SDC)
 ```
 
-This is an interactive tool for the article **Share Buyback and Equity Issue Anomalies Revisited**.
-Users can explore the effects of various parameters as well as data sampling choices.
-For any given choice, users can generate and download a new *customized* version of the paper by clicking the button below at any time:**
+<br>
+
+**NOTE:** Please always wait until all tables load (and "fade in")...
+
+<hr>
+
+This is an interactive tool for the article [Share Buyback and Equity Issue Anomalies Revisited]().
+Users can explore the effects of various parameters as well as data filtering choices.
+For any given choices, users can generate and download a new **customized pdf version of the paper** by clicking the button below at any time.
+Note that it may take a couple of minutes to create and download the new paper.
 <br>
@@
   content = function(file) {
-    src <- normalizePath('BBtool_pdf.Rmd')
-    # temporarily switch to the temp dir, in case you do not have write
-    # permission to the current working directory
-    #owd <- setwd(tempdir())
-    #on.exit(setwd(owd))
-    #file.copy(src, 'ExerciseSet2v2pdf.Rmd')
-    #library(rmarkdown)
-    out <- render('BBtool_pdf.Rmd', pdf_document(),envir=environment())
-    file.rename(out, file)
+    cat("knitting")
+    #knitr::knit("report.Rnw",envir=environment())
+    cat("texing")
+    #tools::texi2pdf("report.tex")
+    knitr::knit2pdf("report.Rnw",envir=globalenv())
+    #toremove <- c("report.aux","report.bbl","report.blg","report.log","report.out")
+    #file.remove(normalizePath(toremove))
+    cat("done")
+    file.rename(normalizePath('report.pdf'), file)
   }
@@
 <hr>
+<hr>
+
+### Dataset Filtering
+
+You can select some filters for the dataset. All analyses below will be done only for the companies that are selected.
+
+Every time you change these filters you may **need to wait a few seconds** until all results of this tool are updated (all tables/figures "fade in").
+
+<br>
+
+Select the time period for which you would like to do the analyses below:
+
+<br>
+
+```{r, eval=TRUE, echo = FALSE}
+dateInput("startdate", "Starting Date:", 
+          value = min(DATASET_INI$SDC$Event.Date) - 10, min = min(DATASET_INI$SDC$Event.Date), max = max(DATASET_INI$SDC$Event.Date)-3*370,
+          startview = "year",
+          width='100%')
+```
+<br>
+```{r, eval=TRUE, echo = FALSE}
+dateInput("enddate", "End Date (allow at least 3 years from the starting day you selected - else it will automatically use data up to 3 years after your start date):", 
+          value = max(DATASET_INI$SDC$Event.Date) + 10, 
+          min = min(DATASET_INI$SDC$Event.Date)+3*370, 
+          max = max(DATASET_INI$SDC$Event.Date)+10,startview = "year",
+          width='100%')
+```
+
+<br>
+
+Selet the minimum size of the firms (in $millions) for which you would like to do the analyses below.
+The maximum selected should be larger than the minimum, else the maximum is automatically set to 10e6:
+
+```{r, eval=TRUE, echo = FALSE}
+selectInput("market_cap_min","Enter the Minimum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20))), selected = "0", width = "1000px")
+```
+<br>
+```{r, eval=TRUE, echo = FALSE}
+selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), ceiling(max(DATASET_INI$SDC$Market.Cap)))), selected = as.character(ceiling(max(DATASET_INI$SDC$Market.Cap))), width = "1000px")
+```
+
+```{r, eval=TRUE, echo = FALSE}
+DATASET_NEW <- reactive({
+  starting = input$startdate 
+  ending = input$enddate   
+  if (ending - starting < 3*365)
+    ending = starting + 3*365
+
+  market_cap_min = as.numeric(input$market_cap_min)
+  market_cap_max = as.numeric(input$market_cap_max)
+  if (market_cap_max < market_cap_min)
+    market_cap_max = ceiling(max(DATASET_INI$SDC$Market.Cap))
+
+  useonly_report = which(DATASET_INI$SDC$Event.Date >= starting & DATASET_INI$SDC$Event.Date <= ending & scrub(DATASET_INI$SDC$Market.Cap) >= market_cap_min & scrub(DATASET_INI$SDC$Market.Cap) <= market_cap_max)
+
+  list(
+    returns_by_event_monthly = DATASET_INI$returns_by_event_monthly[,useonly_report],
+    DatesMonth = DATASET_INI$DatesMonth[,useonly_report],
+    SDC = DATASET_INI$SDC[useonly_report,]
+    #returns_by_event_monthly = DATASET_INI$returns_by_event_monthly,
+    #DatesMonth = DATASET_INI$DatesMonth,
+    #SDC = DATASET_INI$SDC
+  )
+})
+```
+
+<hr>
+<hr>
 
@@
 This tool allows the user to explore descriptive statistics of some of the key firm characteristics.
-When the name of the firm characteristics ends with ".Score" it is  either the 1-5 score relative to the Fama-French breakpoints (for Size, Prior returns, and BE/ME ratio) or the percentile relative to all firms in the CRSP universe at the time of the buyback announcement, as discussed in the paper.
-Otherwise it is the raw values of the firm characteristic.
+When the name of the firm characteristics ends with ".Score" it is  either the 1-5 score relative to the Fama-French breakpoints (e.g.
+for Size, Prior returns, and BE/ME ratio) or the percentile relative to all firms in the CRSP universe at the time of the buyback announcement, as discussed in the paper.
+Otherwise it is the raw value of the firm characteristic.
 
@@
                          renderPlot({
-                           feature = BUYBACK_DATA$DATASET$SDC[[which(names(BUYBACK_DATA$DATASET$SDC) == input$characteristic)]]
+                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                            feature = feature[!is.na(feature)]
@@
                          renderDataTable({
-                           feature = BUYBACK_DATA$DATASET$SDC[[which(names(BUYBACK_DATA$DATASET$SDC) == input$characteristic)]]
+                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                            #feature = feature[!is.na(feature)]
@@
                            if (is.character(feature) | length(unique(feature)) <= 20){
-                             tmp = table(feature)
+                             tmp = sort(table(feature), decreasing = TRUE)
                              res = t(as.matrix(tmp))
@@
 
-### Robustness Analysis
+<hr>
+<hr>
+
+### Industry Robustness Analysis of U-Index
 
 Two types of robustness analysis has been considered in the paper: over different time periods, and across industries.
-This tool allows a more detailed robustness analysis along the lines of the results presented in the paper:
+We can select industries to remove here (make sure there are enough data left for the analysis):
 
+<br>
+
+```{r, eval=TRUE, echo = FALSE}
+checkboxGroupInput("industry", "Select Industries  to remove:", choices = unique(DATASET_INI$SDC$Industry),selected = "Software",inline=TRUE)
+
+```
+
+<br>
+
+```{r, eval=TRUE, echo = FALSE}
+
+feature_IRATStable_industry <- reactive({
+  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
+  res = round(cbind(
+    car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
+    car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
+  ),2)[reported_times,]
+  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
+  as.data.frame(res)
+})
+
+feature_CALtable_industry <- reactive({
+  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
+  res = round(cbind(
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
+  ),2)[reported_times,]
+  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
+  as.data.frame(res)
+})
+
+fluidPage(
+  mainPanel(
+    tabsetPanel("Example",
+                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
+                         renderTable({
+                           feature_IRATStable_industry()
+                         })),
+                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
+                         renderTable({
+                           feature_CALtable_industry()
+                         }))    
+    ),style='width: 100%;'))
+```
+
+<hr>
 <hr>
@@
 The article relates 5 firm characteristics (pre-buyback-announcement returns, idiosyncratic volatility, and volatility, as well as BE/ME and Firm Size).
-This tool allows the user to study the effects of combining any of these firm characteristics, as well as some other ones not studied in the paper for simplicity.
+This tool allows the user to study the effects of combining any of these firm characteristics, as well as some other ones not discussed in the paper.
 
@@
 
-selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features1,selected = acceptaple_features1[1])
+selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features1,selected = acceptaple_features1[1], width = "1000px")
 
-selectInput("quantile_used","Enter the quantile to use to define High and Low Firms:", choices = 0.02*(1:20), selected = "0.2")
+selectInput("quantile_used","Enter the quantile to use to define High and Low Firms:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
+
+checkboxInput("characteristic_irats_sign", "If you would like to change the sign of the firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
 
 feature_IRATStable <- reactive({
-  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats)]]  
+  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
+  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
   High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
@@
   res = round(cbind(
-    car_table(DATASET$returns_by_event_monthly[,Low_feature_events], DATASET$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
-    car_table(DATASET$returns_by_event_monthly[,High_feature_events], DATASET$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
+    car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
+    car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
   ),2)[reported_times,]
   colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
-  res
+  as.data.frame(res)
+})
+
+feature_CALtable <- reactive({
+  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
+  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
+  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
+  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
+  res = round(cbind(
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
+  ),2)[reported_times,]
+  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
+  as.data.frame(res)
 })
@@
 High_feature_Hedged_react <- reactive({
-  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats)]]  
+  thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
   High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
-  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET$DatesMonth, DATASET$returns_by_event_monthly,event=1),1,non_zero_mean)
+  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
   remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
@@
 Low_feature_Hedged_react <- reactive({
-  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats)]]  
+  thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
   Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
-  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET$DatesMonth, DATASET$returns_by_event_monthly,event=1),1,non_zero_mean)
+  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
   remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
@@
 ```
+
+<br>
 
@@
                          })),
+                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
+                         renderTable({
+                           feature_CALtable()
+                         })),
                 tabPanel("Cumulative Abnormal Returns,High, 12m hold",
@@
                          })),
+                tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
+                         renderDygraph({
+                           pnl_plot_interactive(Low_feature_Hedged_react())
+                         })),
                 tabPanel("Monthly and Yearly Returns, High, 12m hold",
@@
                            renderHeatmapX(pnl_matrix(High_feature_Hedged_react()))
-                         })
-                )
+                         })),
+                tabPanel("Monthly and Yearly Returns, Low, 12m hold",
+                         renderUI({
+                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react()))
+                         }))
     ),style='width: 100%;'))
@@
 
-### Customizable Buyback Index
+<hr>
+<hr>
 
-Must like the EU-index in the paper, one can create other indices by combining different firm characteristics as needed.
+### Customized Buyback Index
+
+Much like the EU-index in the paper, one can create other indices by combining different firm characteristics as needed.
 
@@
 selectInput("characteristic_irats1", "Select First Firm Characteristic for your new index:", choices = acceptaple_features2,selected = acceptaple_features2[1], width = "1000px")
+checkboxInput("characteristic_irats1_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
 ```
@@
 ```{r, eval=TRUE, echo = FALSE}
-
 selectInput("characteristic_irats2", "Select Second Firm Characteristic for your new index:", choices = acceptaple_features2,selected ="None", width = "1000px")
+checkboxInput("characteristic_irats2_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
 ```
@@
 ```{r, eval=TRUE, echo = FALSE}
-
 selectInput("characteristic_irats3", "Select Third Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
+checkboxInput("characteristic_irats3_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
 ```
@@
 ```{r, eval=TRUE, echo = FALSE}
-
 selectInput("characteristic_irats4", "Select Fourth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
+checkboxInput("characteristic_irats4_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
 ```
@@
 ```{r, eval=TRUE, echo = FALSE}
-
 selectInput("characteristic_irats5", "Select Fifth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
+checkboxInput("characteristic_irats5_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
 ```
@@
 ```{r, eval=TRUE, echo = FALSE}
-
 selectInput("characteristic_irats6", "Select Sixth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
+checkboxInput("characteristic_irats6_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
 ```
@@
 ```{r, eval=TRUE, echo = FALSE}
-
 selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low), 1 (middle), 2 (High) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
@@
 
-  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats1)]]  
+  thesign = ifelse(input$characteristic_irats1_sign, -1, +1)
+  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats1)]]  
   High_feature_events1 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
@@
   if (input$characteristic_irats2 != "None"){
-    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats2)]]  
+    thesign = ifelse(input$characteristic_irats2_sign, -1, +1)
+    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats2)]]  
     High_feature_events2 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
@@
   if (input$characteristic_irats3 != "None"){
-    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats3)]]  
+    thesign = ifelse(input$characteristic_irats3_sign, -1, +1)
+    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats3)]]  
     High_feature_events3 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
@@
   if (input$characteristic_irats4 != "None"){
-    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats4)]]  
+    thesign = ifelse(input$characteristic_irats4_sign, -1, +1)
+    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats4)]]  
     High_feature_events4 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
@@
   if (input$characteristic_irats5 != "None"){
-    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats5)]]  
+    thesign = ifelse(input$characteristic_irats5_sign, -1, +1)
+    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats5)]]  
     High_feature_events5 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
@@
   if (input$characteristic_irats6 != "None"){
-    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats6)]]  
+    thesign = ifelse(input$characteristic_irats6_sign, -1, +1)
+    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats6)]]  
     High_feature_events6 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
@@
 feature_IRATStable_index <- reactive({
-
   thefeature = Index_Score_rect()
-
   High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
   Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
-
   res = round(cbind(
-    car_table(DATASET$returns_by_event_monthly[,Low_feature_events], DATASET$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
-    car_table(DATASET$returns_by_event_monthly[,High_feature_events], DATASET$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
+    car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
+    car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
   ),2)[reported_times,]
   colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
+  res
+})
+
+feature_CALtable_index <- reactive({
+  thefeature = Index_Score_rect()
+  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
+  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
+  res = round(cbind(
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
+  ),2)[reported_times,]
+  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
   res
@@
   High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
-  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET$DatesMonth, DATASET$returns_by_event_monthly,event=1),1,non_zero_mean)
+  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
   remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
@@
   Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
-  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET$DatesMonth, DATASET$returns_by_event_monthly,event=1),1,non_zero_mean)
+  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
   remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
@@
                          })),
+                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
+                         renderTable({
+                           feature_CALtable_index()
+                         })),
                 tabPanel("Histogram of the New Index",
@@
                          })),
+                tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
+                         renderDygraph({
+                           pnl_plot_interactive(Low_feature_Hedged_react_index())
+                         })),
                 tabPanel("Monthly and Yearly Returns, High, 12m hold",
@@
                            renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index()))
-                         })
-                )
+                         })),
+                tabPanel("Monthly and Yearly Returns, Low, 12m hold",
+                         renderUI({
+                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react_index()))
+                         }))
     ),style='width: 100%;'))
 ```
+
+<br>
+<hr>
+As noted above **you can interactively change various report parameters throughout this document, and for any of your choices create a customized paper using the button at the begining of this page at any time.**
+<br>
+
+<hr>
+
+<br>
+
+<br>
+<br>

### 2016-02-15 bb_issuers.R

@@ -75,98 +75,6 @@ if (rerun_issuers_data_code) {
   source("report_data.R"); rm("report_data","filename_to_save")
 } 
 
-##################################################################
-# First get the quantiles for the pre-announce performance and any cross-event data we need (no more for now)
-##################################################################
-if (get_crossevent_data*0){ # THIS IS OLD STUFF. NOT USED ANY MORE. keeping it here for now just in case (a bit slow to rewrite/run)
-  
-  load("tmpfiles/report_dataBuybacks.Rdata")
-  report_dataBB = report_data
-  permnosBB = report_data$DATASET$SDC$permno
-  returnsBB = report_data$DATASET$returns_by_event
-  returnsBBabn = report_data$DATASET$Abn_returns
-  BBdates = report_data$DATASET$SDC$Event.Date
-  
-  load("tmpfiles/report_dataIssuers.Rdata")
-  report_dataISS = report_data
-  permnosISS = report_data$DATASET$SDC$permno
-  returnsISS = report_data$DATASET$returns_by_event
-  returnsISSabn = report_data$DATASET$Abn_returns
-  ISSdates = report_data$DATASET$SDC$Event.Date  
-  
-  # Get the cross-events stats now. first the raw returns
-  useonly = intersect(rownames(returnsBB), rownames(returnsISS))
-  tmp = cbind(returnsBB[useonly,],returnsISS[useonly,])
-  colnames(tmp) <- str_sub(colnames(tmp), start = 1, end = 5)
-  colnames(returnsBB) <- str_sub(colnames(returnsBB), start = 1, end = 5)    
-  colnames(returnsISS) <- str_sub(colnames(returnsISS), start = 1, end = 5)    
-  tmp = tmp[,unique(colnames(tmp))]
-  allreturns_nonzero = apply(tmp!=0,2,function(r) ms(r,prior_performance_period_days))
-  allreturns_rets = apply(tmp,2,function(r) ms(r,prior_performance_period_days))
-  allreturns_rets = shift(allreturns_rets,5)
-  rets_used = allreturns_rets*(allreturns_nonzero > 0.8*prior_performance_period_days) # just to avoid using cases where there are many 0 days
-  rets_used = shift(rets_used,5)
-  rownames(allreturns_rets) <- rownames(tmp)
-  rownames(rets_used) <- rownames(tmp)  
-  #now the abnormal returns
[…]

### 2016-02-15 latex_code.R

@@ -158,7 +158,7 @@ latex_render_data_frame<-function(x,y=NULL, title="",caption="",label="",columns
 
 
 #Work in progress, generic latex printer
-printLatexTable2 <- function(df1,df2, title="",title1="", title2="",caption="",bigtitleontop = F, titleontop=F, metric1="CAR",metric2="AR",label="",rowcolumn="",columns=NULL,columns2=NULL,scale=1,lastSpecial=F,dorotate=F) {
+printLatexTable2 <- function(df1,df2, title="",title1="", title2="",caption="",bigtitleontop = F, titleontop=F, metric1="CAR",metric2="AR",label="",rowcolumn="",columns=NULL,columns2=NULL,scale=1,lastSpecial=F,dorotate=F,returntext=F) {
   #Helper functions
   p <- function(...){paste(...)}
   pn <- function(...){paste(...,"\n")} #print newline
@@ -202,7 +202,7 @@ printLatexTable2 <- function(df1,df2, title="",title1="", title2="",caption="",b
   #############################################
   # TABLE 1 NOW
   #############################################
-  #convert input
+  #convertprintLatexTable2 input
   pval   <- df1[,3* (1:(ncol(df1)/3))]
   tstat  <- df1[,3* (1:(ncol(df1)/3))-1]
   df     <- df1[,3* (1:(ncol(df1)/3))-2]
@@ -392,6 +392,8 @@ printLatexTable2 <- function(df1,df2, title="",title1="", title2="",caption="",b
   if(dorotate) #{
     l <- pn(l,"\\end{landscape}") 
   
+  if(returntext)
+    return(l)
   cat(l)
 }  
 

### 2016-02-16 index.Rmd
tool update

@@
 title: "Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool"
-author: "[Theodoros Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), [Enric Junque de Fortuny](ciri.be/), [Nick Nassuphis](https://www.linkedin.com/in/nick-nassuphis-8029372), and [Theo Vermaelen](http://faculty.insead.edu/theo-vermaelen/)"
+author: "[Theodoros Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), [Enric Junque de Fortuny](http://ciri.be/), [Nick Nassuphis](https://www.linkedin.com/in/nick-nassuphis-8029372), and [Theo Vermaelen](http://faculty.insead.edu/theo-vermaelen/)"
 output:  
@@
  fig_align: center
+ in_header: header.html
+ runtime: shiny
 runtime: shiny
@@
 
-```{r, eval=TRUE, echo = FALSE}
-#load("bb_issuersALL.Rdata")
+```{r, eval=TRUE, echo = FALSE,message=FALSE}
+# rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
+# source("create_tool_data.R")
 load("bb_issuersTOOL.Rdata")
+#load("tmpfiles/bb_issuersALL.Rdata")
 
@@
 # Why are these not found when deployed?!
+library("shiny") 
+library("shinysky") #  devtools::install_github("AnalytixWare/ShinySky")
+
 library("stringr")
@@
 source("lib/plots.R")
+source("report_helpers.R")
 
@@
 DATASET_INI$SDC = as.data.frame(DATASET_INI$SDC)
+
+if(0) {
+  CACHE <- car_table_cache(DATASET_INI$returns_by_event_monthly,
+                           DATASET_INI$SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)
+  save("CACHE",file = "cache.Rdata")
+}else {
+  load("cache.Rdata")  
+}
+report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)
+
 ```
@@
 
-This is an interactive tool for the article [Share Buyback and Equity Issue Anomalies Revisited]().
+This is an interactive tool for the article [Share Buyback and Equity Issue Anomalies Revisited](http://tevgeniou.github.io/BuybacksIssuers/).
 Users can explore the effects of various parameters as well as data filtering choices.
 For any given choices, users can generate and download a new **customized pdf version of the paper** by clicking the button below at any time.
-Note that it may take a couple of minutes to create and download the new paper.
+
 <br>
+
+**Note that it takes a few minutes (possibly five) to create and download the new paper - work in progress.**
+
 <br>
@@
     DatesMonth = DATASET_INI$DatesMonth[,useonly_report],
-    SDC = DATASET_INI$SDC[useonly_report,]
+    SDC = DATASET_INI$SDC[useonly_report,],
+    subset = useonly_report
     #returns_by_event_monthly = DATASET_INI$returns_by_event_monthly,
@@
 ```{r, eval=TRUE, echo = FALSE}
-acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index","Industry", "Market.Cap",          "Percent.Shares", "Purpose.Code","Source.of.funds","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio", "Year")
+acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index","Industry", "Market.Cap",          "Percent.Shares", "Purpose.Code","Source.of.funds","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio")
 
@@
                 tabPanel("Histogram",
+                         busyIndicator("Please wait while we load the data for you... This shouldn't take more than a few seconds...",wait = 0),
                          renderPlot({
@@
                 )
-    ),style='width: 100%;'))
+    ),
+    style='width: 100%;'))
 ```
@@
   res = round(cbind(
-    car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
-    car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
+    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
+    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
+    car_table_cached(CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
+    car_table_cached(CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
   ),2)[reported_times,]
@@
   res = round(cbind(
-    calendar_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
-    calendar_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
+    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly,report_months_cal)$results,
+    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly,report_months_cal)$results
   ),2)[reported_times,]
@@
                 tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
+                         busyIndicator("Calculating results ...",wait = 0),
                          renderTable({
@@
                 tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
+                         busyIndicator("Calculating results ...",wait = 0),
                          renderTable({
@@
   res = round(cbind(
-    car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
-    car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
+    #car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
+    #car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
+    car_table_cached(CACHE,Low_feature_events)$results,
+    car_table_cached(CACHE,High_feature_events)$results
   ),2)[reported_times,]
@@
   res = round(cbind(
-    calendar_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
-    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
+    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly,report_months_cal)$results,
+    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly,report_months_cal)$results
   ),2)[reported_times,]
@@
                 tabPanel("Cumulative Abnormal Returns,High, 12m hold",
+                         busyIndicator("Calculating results ...",wait = 0),
                          renderDygraph({
@@
                 tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
+                         busyIndicator("Calculating results ...",wait = 0),
                          renderDygraph({
@@
                 tabPanel("Monthly and Yearly Returns, High, 12m hold",
+                         busyIndicator("Calculating results ...",wait = 0),
                          renderUI({
@@
                 tabPanel("Monthly and Yearly Returns, Low, 12m hold",
+                         busyIndicator("Calculating results ...",wait = 0),
                          renderUI({
@@
                 tabPanel("Histogram of the New Index",
+                         busyIndicator("Calculating results ...",wait = 0),
                          renderPlot({

### 2016-02-16 report.Rnw
tool update

--- 2016-02-15 bb_issuers.Rnw
@@
 #dev.off();
-#library(knitr); knit2pdf('bb_issuers.Rnw', texi2dvi='texi2dvi'); file.remove(paste("bb_issuers",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
+#library(knitr); knit2pdf('report.Rnw', texi2dvi='texi2dvi'); file.remove(paste("report",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
 #dir.create("tmpfiles") # need to comment this if the directory already exists
 
-#load("tmpfiles/bb_issuersALL.Rdata")
-reload_data = 0
+#Timing: 
+require(tictoc)
+tic() #without report_tool.R: 77s
+
+###################################################
+## SAME AS bb_issuers.Rnw
+reload_data = 1
 
@@
   if (reload_data)
-    load("tmpfiles/bb_issuersALL.Rdata")
+    #load("tmpfiles/bb_issuersALL.Rdata")
+    load("bb_issuersTOOL.Rdata")
   source("lib_helpers.R") 
@@
 })
+
+########################################################################################################
+## REPORT.RNW SPECIAL CODE:
+########################################################################################################
+
+#Add any/all choices made in the tool here
+if(!exists("input")){
+  input = list()
+  input$startdate <- as.Date("2000-12-31")
+  input$enddate <- as.Date("2014-12-31")
+  input$market_cap_min = 50
+  input$market_cap_max = 505755
+  input$quantile_used_ind = 0.2
+  input$quantile_used_all = 0.4
+
+  #for extra sections
+  input$characteristic_irats1 <- "BE.ME.Score"
+  input$characteristic_irats1_sign <- T
+
+  input$characteristic_irats2 <- "Pre.Vol.Score"
+  input$characteristic_irats2_sign <- T
+}
+
+options(warn=-1) #because some period don't have data
+source("report_helpers.R")
+source("report_tool.R")
+source("report_tool_section.R")
+options(warn=0)
+
+#Now overwrite any variables that need redefining
+firstyear = as.character(format(input$startdate,"%Y"))
+lastyear = as.character(format(input$enddate,"%Y"))
+FirstTrade = input$startdate
 
@@
 \begin{document}
+%\SweaveOpts{concordance=TRUE}
 
@@
 As in Table~\ref{tbl:allhedgedBB},  \Sexpr{rownames(tmp)[which.min(tmp1[,13])]} has a large a loss of \Sexpr{tmp[which.min(tmp1[,13]),13]}$\%$ and the best year is \Sexpr{rownames(tmp)[which.max(tmp[,13])]} with an impressive \Sexpr{tmp[which.max(tmp[,13]),13]}$\%$.
+
+%########################################################################################################
+%## REPORT.RNW SPECIAL CODE:
+%########################################################################################################
+
+\section{Additional Variables Exploration}
+<< Generate extra sections, echo=F,eval=T,results='asis' >>=
+#this cats the text but returns some tables to be place at the end
+options(warn=-1) #because some period don't have data
+
+sec1 <- generate_section(input$characteristic_irats1,input$characteristic_irats1_sign,input$quantile_used_ind)
+sec2 <- generate_section(input$characteristic_irats2,input$characteristic_irats2_sign,input$quantile_used_ind)
+sec3 <- generate_section(input$characteristic_irats3,input$characteristic_irats3_sign,input$quantile_used_ind)
+sec4 <- generate_section(input$characteristic_irats4,input$characteristic_irats4_sign,input$quantile_used_ind)
+sec5 <- generate_section(input$characteristic_irats5,input$characteristic_irats5_sign,input$quantile_used_ind)
+sec6 <- generate_section(input$characteristic_irats6,input$characteristic_irats6_sign,input$quantile_used_ind)
+
+secU <- generate_U_section(sec1,sec2,sec3,sec4,sec5,sec6, input$quantile_used_ind,input$quantile_used_all)
+options(warn=0) #because some period don't have data
+
+@
+%########################################################################################################
+%########################################################################################################
 
@@
 
+if(! is.null(ISS_for_BB_Abn_table)) {
   colnames(ISS_for_BB_Abn_table)[1]<- "Post-buyback SEOs"
@@
   )
+} else {
+  cat("\\begin{table}
+  \\caption{Issue announcements with and without a prior buyback: not enough data to generate}
+  \\label{tbl:BBISSexitAfter}
+  \\end{table}
+  ");
+}
 @
@@
 <<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-one_table = cbind(BBtable_undertime[,7:12],BB_cal_table_undertime[,7:12],
-                  BBtable_undertime[,19:24],BB_cal_table_undertime[,19:24],
-                  BBtable_undertime[,31:36],BB_cal_table_undertime[,31:36],
-                  BBtable_undertime[,43:48],BB_cal_table_undertime[,43:48]
+one_table = cbind(BBtable_undertime[reported_times,7:12],BB_cal_table_undertime[reported_times,7:12],
+                  BBtable_undertime[reported_times,19:24],BB_cal_table_undertime[reported_times,19:24],
+                  BBtable_undertime[reported_times,31:36],BB_cal_table_undertime[reported_times,31:36],
+                  BBtable_undertime[reported_times,43:48],BB_cal_table_undertime[reported_times,43:48]
 )
 #one_table = BBtable_undertime
-printLatexTable(one_table[reported_times,1:12],
+printLatexTable(one_table[,1:12],
                 columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),
@@
 
+%########################################################################################################
+%## REPORT.RNW SPECIAL CODE:
+%########################################################################################################
+
+<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+#cat all the tables for the individual variables
+for(i in 1:6) {
+  sec <- eval(parse(text=paste("sec",i,sep="")))
+  if(!is.null(sec)) {
+    cat(sec$car_table)
+    cat(sec$under_table)
+  }
+}
+#cat the U-index table and others
+cat(secU$car_table)
+cat(secU$CEU_IRATStable_bb_latex)
+cat(secU$CEU_CALtable_bb_latex)
+
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Special table combining industry characteristics and High/Low of all additional variables
+\small
+<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+tmp = generate_industry_table(sec1,sec2,sec3,sec5,sec5,sec6)
+latex_render_data_frame(
+  round(tmp,1), 
+  title = "Industry Characteristics",
+  caption="Percentage of high and low subset companies for all industries for which we have at least 100 events in our sample.",
+  label = "tbl:industriesAdditional",
+  columns=NULL,
+  bigtitleontop = T,
+  show_rownames=TRUE,
+  scale = 1,
+  digits=1,
+  lastSpecial=F,dorotate=T
+)
+@
+\normalsize
+
+<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+rownames(secU$Under_IdioBB2)[1:2] <- c("high U-index", "low U-index")
+latex_render_data_frame(
+  round(secU$Under_IdioBB2[1:6,1:4],1), 
+  title = "Relations across firm characteristics for Buybacks",
+  caption="Relation between Under/Overvaluation and High/Low samples of the additional variables for buybacks.
+Numbers indicate percentage of firms in the row that are also categorized as noted in the columns.",
+  label = "tbl:underidioallBB2",
+  columns=NULL,
+  bigtitleontop = T,
+  show_rownames=TRUE,
+  scale = 0.9,
+  digits=1,
+  lastSpecial=F,dorotate=F
+)
+
+latex_render_data_frame(
+  round(secU$Under_IdioBB_cor2,2), 
+  title = "Correlations of Buybacks Characteristics",
+  caption="Correlation between all of the buybacks characteristics considered and the U-index score.
+All scores are defined using the universe of all CRSP companies at the time of the announcement with data up to the month before the announcement.",
+  label = "tbl:underidioallBBcor2",
+  columns=NULL,
+  bigtitleontop = T,
+  show_rownames=TRUE,
+  scale = 0.9,
+  digits=2,
+  lastSpecial=F,dorotate=F
+)
+@
+
+%########################################################################################################
+%## REPORT.RNW SPECIAL CODE ENDS HERE
+%########################################################################################################
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\clearpage
 \begin{figure}[H]
@@
 pnl_Exit_Hedged = BB_ISS_Exit_Hedged
-pnl_NoExit_Hedged = BB_ISS_NoExit_Hedged
+pnl_NoExit_Hedged = BB_ISS_NoExit_Hedged[(which(pnl_NoExit_Hedged!=0)[1]):(tail(which(pnl_NoExit_Hedged!=0),1))]
 plot(cumsum(100*pnl_NoExit_Hedged),type="l",ylab="CAR", xlab = "",main = "Panel B: Strategy Returns", axes = FALSE, ylim=c(min(c(100*cumsum(pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged))), max(c(cumsum(100*pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged)))), cex.lab=1.1)
+
 axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
@@
 
+%########################################################################################################
+%## REPORT.RNW SPECIAL CODE:
+%########################################################################################################
+
+\begin{figure}[H]
+\centering
+<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
+IRATS_table_all_bb_plot = secU$CEU_IRATStable_bb
+IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")] <- -IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")]
+
+ylimit = c(min(as.vector(IRATS_table_all_bb_plot[reported_times_plots,which(colnames(IRATS_table_all_bb_plot)=="CAR")])), max(as.vector(IRATS_table_all_bb_plot[reported_times_plots,which(colnames(IRATS_table_all_bb_plot)=="CAR")])))
+
+#plot maximal first
+plot(IRATS_table_all_bb_plot[reported_times_plots,dim(IRATS_table_all_bb_plot)[2]-2], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Buybacks - CEU index", lwd=1, lty = "solid")
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(2,cex.axis=1.1)
+
+#now others
+linestyle  = c("solid","dotted","dotted","dashed","dashed","dotdash","solid")
+withpoints = c(F,    F,        T      ,F       ,T       ,F        ,T      )
+
+theindex = rev(1:(dim(IRATS_table_all_bb_plot)[2]/3))
+for(i in 1:length(theindex)) {
+  lines(IRATS_table_all_bb_plot[reported_times_plots,3*(theindex[i]-1)+1],lwd = 2, lty=linestyle[i])
+  if(withpoints[i]) {
+    tmp = IRATS_table_all_bb_plot[reported_times_plots,3*(theindex[i]-1)+1]
+    tmp[c(3*(1:floor(length(tmp)/3)),3*(1:floor(length(tmp)/3))+1)] <- NA
+    points(tmp, pch=23,lwd=1)
+  }
+}
+
+abline(v=which(reported_times_plots == "0"), lwd=0.5)
+abline(h=0, lwd=0.5)
+
+pchs = withpoints[1:length(theindex)]
+pchs[pchs] = 23
+pchs[!pchs] = NA
+legend(x="topleft",
+       title="CEU index value",
+       legend = theindex,
+       lty=linestyle[1:length(theindex)],
+       lwd=(1:length(theindex))*0+2,
+       pch=pchs,
+       cex=1,bg="white",inset=0.01)
+@
+\caption{Long-run IRATS five factors cumulative abnormal returns of buybacks depending on the CEU-index.
+From the highest to the lowest lines as indicated by the legend.
+The x-axis indicates months from the date of the event announcement.}
+\label{fig:CEpastall}
+\end{figure}
+
+This document took \Sexpr{toc()$tic/1000} seconds to produce.
+%########################################################################################################
+%## REPORT.RNW SPECIAL CODE ENDS HERE
+%########################################################################################################
+
 \end{document}

### 2016-02-16 bb_issuers.R

@@ -452,99 +452,6 @@ colnames(ISS_for_BB_Abn_table_cal) <- c("Buyback SEO: CAR", "t-stat", "p-value",
 rownames(ISS_for_BB_Abn_table_cal)[nrow(ISS_for_BB_Abn_table_cal)] <- "Observations"
 
 ###############################################################################################
-#<< A Helper function for all feature based analyses
-###############################################################################################
-
-# Define a helper function that we can use for any firm characteristic:
-get_feature_results <- function(DATASET,feature_name, company_subset_undervalued,company_subset_overvalued,quantile_feature,featurewindow, method="Complex"){
-  
-  if (method == "Simple"){
-    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == feature_name)]]  
-    #High_feature_events = which(scrub(thefeature) > 1-quantile_feature & !is.na(thefeature))
-    #Low_feature_events = which(scrub(thefeature) < quantile_feature & !is.na(thefeature))
-    High_feature_events = which(scrub(thefeature) > quantile(thefeature[!is.na(thefeature)],1-quantile_feature) & !is.na(thefeature))
-    Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],quantile_feature) & !is.na(thefeature))
-  } else {
-    # Thresholds
-    thetimes = DATASET$SDC$Event.Date
-    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == feature_name)]]  
-    thres = Reduce(cbind,lapply(1:length(thetimes), function(i){
-      useonly = thetimes <= thetimes[i] & thetimes >= thetimes[i] - featurewindow & 1:length(thetimes) != i
-      useonly = useonly & !is.na(thefeature)
-      res = c(0,0)
-      if (length(thefeature[useonly]) >= 5)
-        res = c(quantile(thefeature[useonly], quantile_feature),quantile(thefeature[useonly], 1-quantile_feature))
-      res
-    }))
-    feature_down = thres[1,]
-    feature_up = thres[2,]
-    names(feature_down) <- format(DATASET$SDC$Event.Date, "%Y%m")
-    names(feature_up) <- format(DATASET$SDC$Event.Date, "%Y%m")
-    tmp = feature_down
-    feature_thresholds_down = sapply(sort(unique(names(tmp))), function(i) {
[…]

### 2016-02-16 create_tool_data.R

@@ -1,0 +1,143 @@
+
+##########################################################################################
+# Creates a small subset of the data only used for the interactive tool - to load faster
+##########################################################################################
+
+rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
+
+source("lib_helpers.R") 
+source("latex_code.R")
+source("dataset/indices_and_factors/ff_industries_sic.R")
+source("business_data_clean.R")
+source("Paper_global_parameters.R")
+initial_vars = ls(all = TRUE) # takes time to save and load!!! so we save only what is needed at the end. 
+
+load("tmpfiles/bb_issuersALL.Rdata")
+rm("buybacks_ma", "buybacks_repurchases", "CRSP_prc", "CRSP_returns_monthly","CRSP_returns",
+   "CRSP_prc_monthly","idx_Compustat_availBE","LEV_randomization",
+   "crsp_sdc_link", "CRSP_shrout_monthly","fundamental_annual",
+   "ibes","ibes_data","ibes_eps",
+   #"ibes_sIs",
+   "ibes_cusip_permno_from_python","Indices_Daily",
+   "BE.MEbreakpoints","BEMEthres","all_compustat_data","all_characteristics",
+   "MEbreakpoints","MEthres","mom_monthly","noBBdelistings_all","pension_annual",
+   "returns_by_event","returns_by_event_monthly","SDCstandardised","SDC",
+   "backfilled","BE_used_all","compustat_data","dataset","Market_Daily","previous",
+   "R2_randomization","tmp_test1","VOL_randomization","x","EPSunc_randomization")
+
+
+Betas_PB6M <- Betas_lm("Six.Month.Before","One.Day.Before",BUYBACK_DATA$DATASET$Dates, BUYBACK_DATA$DATASET$returns_by_event, Risk_Factors)
+rm("Risk_Factors")
+
[…]

### 2016-02-16 latex_code.R

@@ -399,7 +399,7 @@ printLatexTable2 <- function(df1,df2, title="",title1="", title2="",caption="",b
 
 
 #Work in progress, generic latex printer
-printLatexTable <- function(df, title="",metric="CAR",caption="",label="",titleontop = F, rowcolumn="",columns=NULL,scale=1,close=T,open=T,lastSpecial=F) {
+printLatexTable <- function(df, title="",metric="CAR",caption="",label="",titleontop = F, rowcolumn="",columns=NULL,scale=1,close=T,open=T,lastSpecial=F,returntext=F) {
   #convert input
   pval   <- df[,3* (1:(ncol(df)/3))]
   tstat  <- df[,3* (1:(ncol(df)/3))-1]
@@ -539,6 +539,8 @@ printLatexTable <- function(df, title="",metric="CAR",caption="",label="",titleo
       l <- pn(l,"\\end{table}")
     }
   }
+  if(returntext)
+    return(l)
   cat(l)
 }
 

### 2016-02-16 lib/Paper_global_parameters.R

@@ -1,0 +1,174 @@
+############################################################################################ 
+# All global parameters of the project
+############################################################################################ 
+
+##########################################################################################
+### Parameters for the "business_data_clean" of the data
+
+# business_data_clean.R parameters
+First = as.Date("1976-01-01")
+Last = as.Date("2014-12-31")
+# BUT THIS IS THE FIRST DAY WE TRADE ANY PORTFOLIOS IN THE PORTFOLIOS SECTION: 
+# we need some time to get enough live evnents and to hedge
+FirstTrade = as.Date("1985-01-01")
+# Dates used for the events we consider
+AbsoluteMinimumDate = as.Date("1976-01-01")
+
+periods_considered = rbind(
+  c("1985-01-01", "1990-12-31"),
+  c("1991-01-01", "2000-12-31"),
+  c("2001-01-01", "2014-12-31"),
+  c("2008-01-01", "2014-12-31")
+)
+finance_period = "2001-01-01"
+
+penny_stock_price_recent = 3 # penny stock threshold price - post 1990
+penny_stock_price_old = 1 # penny stock threshold price - pre 1990
+good_currencies = c("US")
+major_markets = c("N", "NM", "NY", "NK",      "New York", "Nasdaq", "NYSE Amex", "American")
+
+MIN_SIZE = 0 #micro caps are those with a market cap <300m
+MAX_SIZE = 1e20 #already in million (e6)
+MIN_ME_quantile = 0 # the minimum ff ME quantile
+MAX_ME_quantile = 20 # the maximum ff ME quantile
+MIN_BEME_quantile = 0 # the minimum ff BE/ME quantile
+MAX_BEME_quantile = 20 # the maximum ff BE/ME quantile
+MIN_EVENT_SIZE = 0 # Required minimum "event size" (e.g. % of shares repurchased/issued)
+MAX_EVENT_SIZE = 50 # not allow more than this percent of shares for the event
+
+days_live = 0 # minimum number of days a stock needs to be live before announcement date
+remove_returns_outliers = 0 # remove the reutrns outliers?
+MAX_DR_abs = 100 # Max absolute daily return to consider a stock is an outliers
+max_vol_outlier = 100000.1 # max daily standard deviation in 6 months before announcement
+
[…]

### 2016-02-16 lib/heatmapOutput.R

@@ -1,0 +1,108 @@
+
+#  Copyright 2013, Satrapade
+#  by V. Kapartzianis 
+#  Dual licensed under the MIT or GPL Version 2 licenses.
+#  01/2016 Patched to handle NA's E. Junqué de Fortuny
+library(shiny)
+library(htmlwidgets)
+renderHeatmapX <- function(data, style="norm", include.rownames = TRUE, include.colnames=TRUE, nsmall=2, border=0) {
+  #vmax <- max(Filter(is.numeric, data))
+  vmax = max(data[is.numeric(data) & !is.na(data)])
+  sigmoid <- function(v) { return(1 / (1 + exp(-v))) }
+  toRGB <- function(intensity, sign) {
+    rgb <- "rgb("
+    darkness <- floor((1 - intensity) * 256)
+    if(is.na(sign)) 
+      rgb <- paste(rgb,"255,255,255",sep="")
+    else if(sign) 
+      rgb <- paste(rgb, darkness, ",255,", darkness, sep="")
+    else
+      rgb <- paste(rgb, "255,", darkness, ",", darkness, sep="")
+    rgb <- paste(rgb, ")", sep="")
+    return (rgb)
+  }
+  heatmap <- function(x, style="norm") {
+    if ("squashed" == style) {
+      squashed <- sigmoid(x) - 0.5
+      intensity <- abs(squashed) / 0.5
+      rgb <- toRGB(intensity, squashed >= 0)
+    } else { # ("norm" == style)
+      intensity <- abs(x) / vmax
+      rgb <- toRGB(intensity, x > 0)
+    }
+    return (paste("background-color:", rgb))
+  }
+  if (is.null(colnames(data))) colnames(data) <- 1:ncol(data)
+  if (is.null(rownames(data))) rownames(data) <- 1:nrow(data)  
+  as.character(
+    tags$table(
+      border = border,
+      class = 'data table table-bordered table-condensed',
+      tagList({
+        if (include.colnames)
+          tags$thead(
+            class = 'thead',
+            tags$tr(
+              tagList({
+                if (include.rownames)
+                  tags$th()
+                else
+                  list()
+              }),
+              lapply(colnames(data), function(name) {
+                tags$th(name)
+              })
+            )
+          )
+        else
+          list()
+      }),
+      tags$tbody(
+        lapply(1:nrow(data), function(i) {
+          tags$tr(
+            tagList({
+              if (include.rownames)
+                tags$td(
+                  align="right",
+                  rownames(data)[i]
+                )
+              else
[…]

### 2016-02-16 lib/heatmapwidget/R/heatmapwidget.R

@@ -1,0 +1,141 @@
+#'  Heatmap widget based on original code with the following copyright:
+#'  Copyright 2013, Satrapade
+#'  by V. Kapartzianis
+#'  Dual licensed under the MIT or GPL Version 2 licenses.
+#'
+#'  01/2016 Patched to handle NA's, widget E. Junqué de Fortuny
+#'
+#' @import htmlwidgets
+#' @import htmltools
+#' @import shiny
+#'
+#' @export
+heatmapwidget <- function(data,  width = NULL, height = NULL) {
+  # forward options using x
+  params = list(
+    data = data#,
+    #options = list(..., height = height, width = width),
+    #width = width , height = height
+  )
+  params = Filter(Negate(is.null), params)
+  # create widget
+  #htmlwidgets::createWidget(
+  #  name = 'heatmapwidgetGenerate',
+  #  params,
+  #  width = width,
+  #  height = height,
+  #  package = 'heatmapwidget'
+  #)
+  heatmapwidgetGenerate(data)
+}
+
+#' Widget output function for use in Shiny
+#'
+#' @export
+heatmapwidgetOutput <- function(outputId, width = '100%', height = '400px'){
+  #shinyWidgetOutput(outputId, 'heatmapwidget', width, height, package = 'heatmapwidget')
+  tableOutput(outputId, 'heatmapwidget', width, height, package = 'heatmapwidget')
+}
+
+#' Widget render function for use in Shiny
+#'
+#' @export
+renderHeatmapwidget <- function(expr, env = parent.frame(), quoted = FALSE) {
+  if (!quoted) { expr <- substitute(expr) } # force quoted
+  shinyRenderWidget(expr, heatmapwidgetOutput, env, quoted = TRUE)
+}
+heatmapwidgetGenerate <- function(data,style="norm", include.rownames = TRUE, include.colnames=TRUE, nsmall=2, border=0) {#these last ones are not used
+  if(is.null(data)) {
+    cat("NO data ...")
+    return
+  }else{
+    cat(paste(data))
+    cat(data[is.numeric(data)])
+  }
+  #vmax <- max(Filter(is.numeric, data))
+  vmax = max(data[is.numeric(data) & !is.na(data)])
+  sigmoid <- function(v) { return(1 / (1 + exp(-v))) }
+  toRGB <- function(intensity, sign) {
+    rgb <- "rgb("
+    darkness <- floor((1 - intensity) * 256)
[…]

### 2016-02-16 lib/heatmapwidget/inst/htmlwidgets/heatmapwidget.js

@@ -1,0 +1,25 @@
+HTMLWidgets.widget({
+
+  name: 'heatmapwidget',
+
+  type: 'output',
+
+  initialize: function(el, width, height) {
+
+    return {
+      // TODO: add instance fields as required
+    }
+
+  },
+
+  renderValue: function(el, x, instance) {
+
+    el.innerText = x.message;
+
+  },
+
+  resize: function(el, width, height, instance) {
+
+  }
+
+});

### 2016-02-16 lib/heatmapwidget/install.R

@@ -1,0 +1,10 @@
+#https://cran.r-project.org/web/packages/htmlwidgets/vignettes/develop_intro.html
+#installing
+
+if(0) {
+  devtools::create("heatmapwidget")               # create package using devtools
+  setwd("heatmapwidget")                          # navigate to package dir
+  htmlwidgets::scaffoldWidget("heatmapwidget")    # create widget scaffolding
+}
+library(heatmapwidget)
+devtools::install()                        # install the package so we can try it

### 2016-02-16 lib/lib_helpers_shiny.R

@@ -14,7 +14,7 @@ libraries_used=c("stringr","gtools","foreign","reshape2","digest","timeDate","de
                  "Hmisc","vegan","fpc","GPArotation","FactoMineR","cluster",
                  "psych","stringr","googleVis", "png","ggplot2","googleVis", "gridExtra","RcppArmadillo","xts","DescTools")
 
-get_libraries(libraries_used)
+#get_libraries(libraries_used)
 
 options(stringsAsFactors=FALSE)
 
@@ -731,105 +731,6 @@ exit_helper_rnw <- function(event,exit_signal_name,holding_period_pnl = "Four.Ye
               pnl_Exit_Hedged = pnl_Exit_Hedged, pnl_NoExit_Hedged = pnl_NoExit_Hedged, 
               number_events = number_events 
   ))
-}
-
-
-###############################################################################################
-#<< A Helper function for all feature based analyses
-###############################################################################################
-
-# Define a helper function that we can use for any firm characteristic:
-get_feature_results <- function(DATASET,feature_name, company_subset_undervalued,company_subset_overvalued,quantile_feature,featurewindow, method="Complex"){
-  
-  if (method == "Simple"){
-    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == feature_name)]]  
-    #High_feature_events = which(scrub(thefeature) > 1-quantile_feature & !is.na(thefeature))
-    #Low_feature_events = which(scrub(thefeature) < quantile_feature & !is.na(thefeature))
-    High_feature_events = which(scrub(thefeature) > quantile(thefeature[!is.na(thefeature)],1-quantile_feature) & !is.na(thefeature))
-    Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],quantile_feature) & !is.na(thefeature))
-    if (length(High_feature_events) == 0)
-      High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-quantile_feature) & !is.na(thefeature))
-    if (length(Low_feature_events) == 0)
-      Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],quantile_feature) & !is.na(thefeature))
-    
-  } else {
[…]

### 2016-02-16 lib/plots.R

@@ -1,0 +1,60 @@
+library("dygraphs")
+library("reshape")
+library("ggplot2")
+
+mainColor= "#E69F00"
+secondaryColor = "#333333"
+
+pnl_plot_interactive <- function(x,...){
+  x = remove_initialization_time(x)
+  pargs<-as.list(match.call(expand.dots=TRUE))
+  if(!"ylab" %in% names(pargs)) ylab<-"Return" else ylab<-pargs$ylab #deparse(substitute(x)) 
+  if(!"main" %in% names(pargs)) main<-paste(names(pnl_stats(x)),pnl_stats(x),sep=":",collapse=" ") else main<-pargs$main
+  plot_arguments<-c(list(data=cumsum(x*100) ,ylab=ylab, main=main),
+                    pargs[setdiff(names(pargs),c("","x","ylab","main"))])
+  plot_arguments$expand.dots = NULL
+
+  
+  CustomAxisLabel <- 'function (d, gran) {
+                      return Dygraph.zeropad(d.getMonth()+1) + "/"+ Dygraph.zeropad(d.getFullYear());
+                    }'
+  CustomValueFormat = 'function (ms) {
+                      var d = new Date(ms);
+                      return Dygraph.zeropad(d.getMonth()+1) + "/"+ Dygraph.zeropad(d.getFullYear());
+                     }'
+  
+  do.call(dygraph,plot_arguments)  %>% 
+    dyRangeSelector() %>%
+    dySeries("V1", label = "Cumulative Return (%)",color=mainColor) %>%
+    dyAxis("x",pixelsPerLabel=48,axisLabelFormatter =JS(CustomAxisLabel),valueFormatter=JS(CustomValueFormat),ticker="Dygraph.dateTicker") 
+}
+
+plotComponentBars <- function(Main_Factors,Comparison_Factors,futures_data,comp,threshold=0.3)  {
+  df <- rbind(      Main_Factors[rownames(Comparison_Factors)[!is.na(Comparison_Factors[,comp])],comp],
+              Comparison_Factors[rownames(Comparison_Factors)[!is.na(Comparison_Factors[,comp])],comp])
+  
+  keep <- apply(abs(df) > threshold,2,sum) > 0
+  df <- df[,keep]
+  
+  colnames(df) <- rownames(Comparison_Factors)[keep]
+  rownames(df) <- c("2001-2016",paste(head(rownames(futures_data),1),"-", tail(rownames(futures_data),1) ,sep=""))
+  
+  #order bars
[…]

### 2016-02-16 report_helpers.R

@@ -1,0 +1,247 @@
+car_table_cache <- function(returns,Event.Date,Risk_Factors_Monthly,min_window = -6, max_window = 48,formula_used="(ri - RF) ~ Delta + SMB + HML + RMW + CMA") {
+  factors_used = setdiff(unlist(str_split(gsub("~", ",", gsub("\\-", ",", gsub("\\+", ",", gsub("\\)", "",gsub("\\(", "",formula_used))))), " , ")),"ri")
+ 
+  if (sum(!(factors_used %in% colnames(Risk_Factors_Monthly))))
+    stop(paste("car_table misses the risk factors: ",factors_used[!(factors_used %in% colnames(Risk_Factors_Monthly))]))
+  
+  factors_used_noRF = setdiff(factors_used, "RF")
+  if (ncol(returns) < length(factors_used_noRF) + 1){
+    results = matrix(0,nrow=length(allmonths), ncol = 3)
+    results = rbind(results, rep(ncol(returns)))
+    betas = matrix(0,nrow=length(allmonths), ncol = length(factors_used_noRF))
+    betasstderr = matrix(0,nrow=length(allmonths), ncol = length(factors_used_noRF)) 
+    colnames(results) <- c("CAL","t-stat","p-value")
+    rownames(results) <- c(ifelse(allmonths > 0, paste("+",allmonths,sep=""), allmonths),"Observations")
+    colnames(results) <- c("CAR","t-stat","p-value")
+    colnames(betas) <- factors_used_noRF
+    colnames(betasstderr) <- factors_used_noRF
+    all_results = list(results = results, betas = betas, betasstderr = betasstderr)
+    return(all_results) 
+  }
+  
+  #Step 1: Build an event matrix, where all the events are aligned by event month as opposed to calendar month
+  Event.Date = paste(str_sub(Event.Date,start=1,end=7), "01", sep="-") # just in case
+  Row.Date <- as.Date(rownames(returns))
+  firstHit = sapply(Event.Date, function(i) ifelse(i > tail(Row.Date,1), length(Row.Date)+1, ifelse(i < head(Row.Date,1), 0, which(Row.Date == i))))
+  form  = as.formula(formula_used)
+  Risk_Factors_Monthly = Risk_Factors_Monthly[,factors_used]
+  if (!("RF" %in% factors_used)){
[…]

### 2016-02-16 report_tool.R

@@ -1,0 +1,449 @@
+
+report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)
+report_months_car = c((-3:24)*2,1)
+reported_times_plots <-  c("-6","-4","-2","0","+1","+2","+4","+6","+8","+10","+12","+14","+16","+18","+20","+22","+24","+26","+28","+30","+32","+34","+36","+38","+40","+42","+44","+46","+48")  
+
+#general variables and overwriting 
+useonly_bb = which(BUYBACK_DATA$DATASET$SDC$Event.Date >= input$startdate & BUYBACK_DATA$DATASET$SDC$Event.Date <= input$enddate & scrub(BUYBACK_DATA$DATASET$SDC$Market.Cap) >= input$market_cap_min & scrub(BUYBACK_DATA$DATASET$SDC$Market.Cap) <= input$market_cap_max) 
+useonly_is = which(ISSUERS_DATA$DATASET$SDC$Event.Date >= input$startdate & ISSUERS_DATA$DATASET$SDC$Event.Date <= input$enddate & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) >= input$market_cap_min & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) <= input$market_cap_max) 
+
+ret_bb <- BUYBACK_DATA$DATASET$returns_by_event_monthly[,useonly_bb]
+sdc_bb <- BUYBACK_DATA$DATASET$SDC[useonly_bb,]
+subset_undervalued_bb <- company_subset_undervalued_bb[useonly_bb]
+subset_overvalued_bb <- company_subset_overvalued_bb[useonly_bb]
+datesmonth_bb <- BUYBACK_DATA$DATASET$DatesMonth[,useonly_bb]
+EUindex_bb2 <- EUindex_bb[useonly_bb]
+
+ret_is <- ISSUERS_DATA$DATASET$returns_by_event_monthly[,useonly_is]
+sdc_is <- ISSUERS_DATA$DATASET$SDC[useonly_is,]
+company_subset_undervalued_is <- company_subset_undervalued_iss[useonly_is]
+company_subset_overvalued_is <- company_subset_overvalued_iss[useonly_is]
+datesmonth_is <- ISSUERS_DATA$DATASET$DatesMonth[,useonly_is]
+
+if(0) { #remove periods: not done now
+  valididx <- NULL
+  for(i in 1:dim(periods_considered)[1]) {
[…]

### 2016-02-16 report_tool_section.R

@@ -1,0 +1,454 @@
+#overwrite some variables that we need
+if(!exists("BUYBACK_DATA2")) {
+  BUYBACK_DATA2 <- BUYBACK_DATA
+}
+useonly_bb = which(BUYBACK_DATA2$DATASET$SDC$Event.Date >= input$startdate & BUYBACK_DATA2$DATASET$SDC$Event.Date <= input$enddate & scrub(BUYBACK_DATA2$DATASET$SDC$Market.Cap) >= input$market_cap_min & scrub(BUYBACK_DATA2$DATASET$SDC$Market.Cap) <= input$market_cap_max) 
+useonly_is = which(ISSUERS_DATA$DATASET$SDC$Event.Date >= input$startdate & ISSUERS_DATA$DATASET$SDC$Event.Date <= input$enddate & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) >= input$market_cap_min & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) <= input$market_cap_max) 
+subset_undervalued_bb <- company_subset_undervalued_bb[useonly_bb]
+subset_overvalued_bb <- company_subset_overvalued_bb[useonly_bb]
+
+BUYBACK_DATA$DATASET$SDC$Pre.Vol.Score <- BUYBACK_DATA$DATASET$SDC$pre_vol_Score
+BUYBACK_DATA2$DATASET$SDC$Pre.Vol.Score <- BUYBACK_DATA2$DATASET$SDC$pre_vol_Score
+
+###########################################################################
+# HELPER FUNCTIONS FOR GENERATING SECTIONS
+#
+#
+generate_section <- function(variable_name,reverse,quantile_used_ind) {
+  if(is.null(variable_name)) {
+    return(NULL) 
+  }
+  DS <- BUYBACK_DATA2$DATASET
+  
+  #do analysis first, add text later
+  thesign = ifelse(reverse, -1, +1)
+  thefeature = thesign*DS$SDC[[which(names(DS$SDC) == variable_name)]]  
+  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(quantile_used_ind)) & !is.na(thefeature))
+  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(quantile_used_ind)) & !is.na(thefeature))
+  
+  #Test example: car table
+  IRATStableBB = round(cbind(
[…]

### 2016-02-17 index.Rmd
debugging

@@
 
-if(0) {
-  CACHE <- car_table_cache(DATASET_INI$returns_by_event_monthly,
-                           DATASET_INI$SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)
-  save("CACHE",file = "cache.Rdata")
-}else {
-  load("cache.Rdata")  
-}
+#if(1) {
+#  CACHE <- car_table_cache(DATASET_INI$returns_by_event_monthly,
+#                           DATASET_INI$SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)
+#  save("CACHE",file = "cache.Rdata")
+#} else {
+#  load("cache.Rdata")  
+#}
 report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)
@@
 
-**Note that it takes a few minutes (possibly five) to create and download the new paper - work in progress.**
+**Note that it takes a few minutes (possibly more than five) to create and download the new paper (work in progress).
+Please wait without changing any parameters until you are prompted to download the new paper.**
 
@@
 
+  SDC = DATASET_INI$SDC[useonly_report,]
+  returns_by_event_monthly = DATASET_INI$returns_by_event_monthly[,useonly_report]
+  DatesMonth = DATASET_INI$DatesMonth[,useonly_report]
+
+  CACHE <- car_table_cache(returns_by_event_monthly,
+                         SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)
+
   list(
-    returns_by_event_monthly = DATASET_INI$returns_by_event_monthly[,useonly_report],
-    DatesMonth = DATASET_INI$DatesMonth[,useonly_report],
-    SDC = DATASET_INI$SDC[useonly_report,],
+    CACHE = CACHE,
+    returns_by_event_monthly = returns_by_event_monthly,
+    DatesMonth = DatesMonth,
+    SDC = SDC,
     subset = useonly_report
@@
 })
+
 ```
@@
     #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
-    car_table_cached(CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
-    car_table_cached(CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
+    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
+    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
   ),2)[reported_times,]
@@
     #car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
-    car_table_cached(CACHE,Low_feature_events)$results,
-    car_table_cached(CACHE,High_feature_events)$results
+    car_table_cached(DATASET_NEW()$CACHE,Low_feature_events)$results,
+    car_table_cached(DATASET_NEW()$CACHE,High_feature_events)$results
   ),2)[reported_times,]

### 2016-02-17 report.Rnw
debugging

@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+if (0){
   tmp = generate_industry_table(sec1,sec2,sec3,sec5,sec5,sec6)
@@
     caption="Percentage of high and low subset companies for all industries for which we have at least 100 events in our sample.",
-  label = "tbl:industriesAdditional",
+    label = "tbl:CEUrelations",
     columns=NULL,
@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+if (0){
   rownames(secU$Under_IdioBB2)[1:2] <- c("high U-index", "low U-index")
@@
 << fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>= 
-
 IRATS_table_all_bb_plot = EU_IRATStable_bb
@@
 %########################################################################################################
+
+\begin{figure}[H]
+\centering
+<< fig.width=10, fig.height=4, out.width='\\textwidth', echo=F >>=
+#par(mfrow=c(2,1), mar=c(2.3,4,2.3,4))
+#valuation_index_bb[which(valuation_index_bb==2)]<-3 # there is one company here. need to check why
+tmp = table(secU$Index_score)
+tmp = structure(as.numeric(tmp), .Names = names(tmp))
+barplot(tmp,main = "", ylab = "Number of Announcements", xlab = "",las=2,space=0.5, cex.names=0.8)
+#tmp = table(valuation_index_iss)
+#tmp = structure(as.numeric(tmp), .Names = names(tmp))
+#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=0.8)
+rm("tmp")
+@
+\caption{CEU-index. Distribution of the CEU-index of all buyback events.}
+\label{fig:CEundervaluationindex}
+\end{figure}
 

### 2016-02-17 report_helpers.R

@@ -1,8 +1,10 @@
 car_table_cache <- function(returns,Event.Date,Risk_Factors_Monthly,min_window = -6, max_window = 48,formula_used="(ri - RF) ~ Delta + SMB + HML + RMW + CMA") {
   factors_used = setdiff(unlist(str_split(gsub("~", ",", gsub("\\-", ",", gsub("\\+", ",", gsub("\\)", "",gsub("\\(", "",formula_used))))), " , ")),"ri")
- 
+  
   if (sum(!(factors_used %in% colnames(Risk_Factors_Monthly))))
     stop(paste("car_table misses the risk factors: ",factors_used[!(factors_used %in% colnames(Risk_Factors_Monthly))]))
+  
+  allmonths = min_window:max_window 
   
   factors_used_noRF = setdiff(factors_used, "RF")
   if (ncol(returns) < length(factors_used_noRF) + 1){
@@ -49,27 +51,31 @@ car_table_cache <- function(returns,Event.Date,Risk_Factors_Monthly,min_window =
     "factors_used_noRF" = factors_used_noRF
   ))
 }
-car_table_cached <- function(cache,subset=NULL,allmonths=NULL,min_window = -6, max_window = 48) {
-  if(is.null(subset)) 
-    subset = 1:length(cache$Event.Date)
-  EVENT_ALIGNED        <- cache$EVENT_ALIGNED[,subset,]
-  Event.Date           <- cache$Event.Date[subset]
+#ignore allmonths for now, I don't think this can work
+car_table_cached <- function(cache,thesubset=NULL,allmonths=NULL,min_window = -6, max_window = 48) {
+  if(is.null(thesubset)) 
+    thesubset = 1:length(cache$Event.Date)
+  #if(!is.null(allmonths)) {
+  #monthindex = ifelse(allmonths > 0, paste("+",allmonths,sep=""), allmonths)
+  #} else {
+  monthindex = rownames(cache$EVENT_ALIGNED)
+  min_window = min(1,min_window)
+  max_window = max(-1,max_window)
+  allmonths = min_window:max_window 
+  #}
+  EVENT_ALIGNED        <- cache$EVENT_ALIGNED[monthindex,thesubset,]
+  Event.Date           <- cache$Event.Date[thesubset]
   Row.Date             <- cache$Row.Date
   form                 <- cache$form
   factors_used_noRF    <- cache$factors_used_noRF
[…]

### 2016-02-17 report_tool_section.R

@@ -53,10 +53,11 @@ generate_section <- function(variable_name,reverse,quantile_used_ind) {
       types of events: low ",variable_name," and high ",variable_name," events, 
       depending on whether the variable was in the top or bottom quantile of the ",variable_name,"of
       all CRSP companies in the pre-event month. In total we have ", sum(High_feature_events), " low ",variable_name," and ",sum(Low_feature_events),  " high ",variable_name," events. 
-      Table~\\ref{tbl:industriesAdditional} shows the 
-      percentage of high and low ",variable_name," events across all industries for which we have at 
-      least 100 buyback events in our sample.
   ")
+  #Table~\\ref{tbl:industriesAdditional} shows the 
+  #percentage of high and low ",variable_name," events across all industries for which we have at 
+  #least 100 buyback events in our sample.
+  
   cat("Table~\\ref{tbl:",variable_name,"} shows the IRATS and Calendar Time abnormal returns for high
        and low ",variable_name," buybacks events-companies. Focusing on IRATS, high ",variable_name," 
        buyback stocks earn ",IRATStableBB["+48","High: CAR"],"$\\%$  after 48 months (t=" ,IRATStableBB["+48",5] ,"), while low ",variable_name," 
@@ -149,7 +150,7 @@ generate_U_section <- function(sec1,sec2,sec3,sec4,sec5,sec6,quantile_used_ind,q
   High_feature_events2 <- High_feature_events3 <- High_feature_events4 <- High_feature_events5 <- High_feature_events6 <- rep(FALSE,length(High_feature_events1))
   Low_feature_events2 <- Low_feature_events3 <- Low_feature_events4 <- Low_feature_events5 <- Low_feature_events6 <- 
     rep(FALSE,length(Low_feature_events1))
-
+  
   feature_used_names= gsub("\\.", " ",sec1$name) 
   
   if (!is.null(sec2$name)){
@@ -175,7 +176,7 @@ generate_U_section <- function(sec1,sec2,sec3,sec4,sec5,sec6,quantile_used_ind,q
   }
   if (!is.null(sec5$name)){
     thesign = ifelse(sec5$reverse_sign, -1, +1)
-    thefeature = thesign*DS$SDC[[which(names(DS$SDC) == sec5$name)]]  
+    thefeature = thesign*DS$SDC[[which(names(DS$SDC) == sec5$name)]]   
[…]

### 2016-02-17 report.Rnw
debugging tool report

@@
   input = list()
-  input$startdate <- as.Date("2000-12-31")
+  input$startdate <- as.Date("1984-12-31")
   input$enddate <- as.Date("2014-12-31")
-  input$market_cap_min = 50
+  input$market_cap_min = 250
   input$market_cap_max = 505755

### 2016-02-24 bb_issuers.Rnw
tool

@@
 %\begin{abstract}
-%\noindent We re-examine the behavior of stock returns after share buyback and equity issuance announcements using the five-factor model proposed by \cite{FamaFrench2015a}.
-We confirm the findings of \cite{FamaFrench2015b} that the equity issue anomaly, i.e., the fact that equity issues are followed by negative long-term excess returns, disappears after replacing the \cite{FamaFrench1993} three-factor model with the five-factor model.
-However, long term positive excess returns after buyback announcements, first reported by \cite{IkenberryLakonishokVermaelen1995}, remain economically and statistically significant.
-Moreover, the Undervaluation Index proposed by \cite{PeyerVermaelen2009} remains a useful proxy for the likelihood that the buyback is driven by undervaluation.
-The buyback anomaly is robust over time and across sectors.
-Firms with low correlations with the market seem to be better at market timing, which is consistent with the hypothesis that the repurchase is driven by superior company-specific information.
-Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by \cite{IkenberryVermaelen1996}.
-This result is also consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks, unlike the well-known low volatility anomaly across all stocks.
-Finally, based on these findings, we develop an enhanced Undervaluation Index that improves abnormal returns relative to the index developed by \cite{PeyerVermaelen2009}.
+%\noindent We re-examine the behavior of stock returns after net issue  announcements using the five-factor model proposed by Fama and French (2015a).
+We confirm their findings that the equity issue anomaly disappears  with the five-factor model, but the buyback anomaly does not..
+Buyback announcements by firms  with high pre-announcement (idiosyncratic) volatility  are followed by higher long-term abnormal returns.
+This is inconsistent with the widely documented low volatility anomaly, but consistent with Stambaugh, Yu, and Yuan (2015) who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.
 %\end{abstract}
@@
 \begin{abstract}
-\noindent We re-examine the behavior of stock returns after share buyback and equity issuance announcements using the five-factor model proposed by \cite{FamaFrench2015a}.
-We confirm the findings of \cite{FamaFrench2015b} that the equity issue anomaly, i.e., the fact that equity issues are followed by negative long-term excess returns, disappears after replacing the \cite{FamaFrench1993} three-factor model with the five-factor model.
-However, long term positive excess returns after buyback announcements, first reported by \cite{IkenberryLakonishokVermaelen1995}, remain economically and statistically significant.
-Moreover, the Undervaluation Index proposed by \cite{PeyerVermaelen2009} remains a useful proxy for the likelihood that the buyback is driven by undervaluation.
-The buyback anomaly is robust over time and across sectors.
-Firms with low correlations with the market seem to be better at market timing, which is consistent with the hypothesis that the repurchase is driven by superior company-specific information.
-Firms with high pre-announce stock returns volatility also have higher abnormal returns, which is consistent with the hypothesis that a repurchase authorization is an option to take advantage of undervaluation as argued by \cite{IkenberryVermaelen1996}.
-This result is also consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks, unlike the well-known low volatility anomaly across all stocks.
-Finally, based on these findings, we develop an enhanced Undervaluation Index that improves abnormal returns relative to the index developed by \cite{PeyerVermaelen2009}.
+\noindent We re-examine the behavior of stock returns after net issue  announcements using the five-factor model proposed by Fama and French (2015a).
+We confirm their findings that the equity issue anomaly disappears  with the five-factor model, but the buyback anomaly does not.
+Buyback announcements by firms  with high pre-announcement (idiosyncratic) volatility  are followed by higher long-term abnormal returns.
+This is inconsistent with the widely documented low volatility anomaly, but consistent with Stambaugh, Yu, and Yuan (2015) who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.
 

### 2016-02-24 index.Rmd
tool

@@
 title: "Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool"
-author: "[Theodoros Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), [Enric Junque de Fortuny](http://ciri.be/), [Nick Nassuphis](https://www.linkedin.com/in/nick-nassuphis-8029372), and [Theo Vermaelen](http://faculty.insead.edu/theo-vermaelen/)"
+author: "[Theodoros Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), [Enric Junqué de Fortuny](http://ciri.be/), [Nick Nassuphis](https://www.linkedin.com/in/nick-nassuphis-8029372), and [Theo Vermaelen](http://faculty.insead.edu/theo-vermaelen/)"
 output:  
@@
 report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)
-
 ```
@@
   content = function(file) {
-    cat("knitting")
-    #knitr::knit("report.Rnw",envir=environment())
-    cat("texing")
-    #tools::texi2pdf("report.tex")
-    knitr::knit2pdf("report.Rnw",envir=globalenv())
-    #toremove <- c("report.aux","report.bbl","report.blg","report.log","report.out")
-    #file.remove(normalizePath(toremove))
-    cat("done")
+    knitr::knit2pdf("report.Rnw",envir=environment())
     file.rename(normalizePath('report.pdf'), file)
@@
 ```{r, eval=TRUE, echo = FALSE}
-acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index","Industry", "Market.Cap",          "Percent.Shares", "Purpose.Code","Source.of.funds","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio")
+acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Idiosyncraticness","Industry", "Purpose.Code","Source.of.funds")
 
@@
 ```{r, eval=TRUE, echo = FALSE}
-acceptaple_features1 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio")
+acceptaple_features1 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Idiosyncraticness")
 
@@
   thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]
-  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
-  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
+
+  thefeature = as.numeric(scrub(thefeature))
+  quantile_used_ind = as.numeric(input$quantile_used_ind)
+
+  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
+  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)
+
+  #High_feature_events = which(scrub(thefeature) > quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
+  #Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
   res = round(cbind(
@@
   thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
-  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
-  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
+  High_feature_events = which(scrub(thefeature) > quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
+  Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
   res = round(cbind(
@@
 High_feature_Hedged_react <- reactive({
-  thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
-  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
+  thefeature = as.numeric(DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]])
+  quantile_used <- as.numeric(input$quantile_used)
+
+  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used)
+
   High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
@@
   thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
-  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
+  Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
   Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
@@
 Much like the EU-index in the paper, one can create other indices by combining different firm characteristics as needed.
+You can select your own firm characteristics below and also indicate whether you would like to reverse the sign of this firm characteristic (Low will be High and vice versa).
 
 ```{r, eval=TRUE, echo = FALSE}
-acceptaple_features2 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","None")
+acceptaple_features2 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Idiosyncraticness","None")
 ```
@@
 ```{r, eval=TRUE, echo = FALSE}
-selectInput("characteristic_irats1", "Select First Firm Characteristic for your new index:", choices = acceptaple_features2,selected = acceptaple_features2[1], width = "1000px")
-checkboxInput("characteristic_irats1_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
-```
-
-<br>
-```{r, eval=TRUE, echo = FALSE}
-selectInput("characteristic_irats2", "Select Second Firm Characteristic for your new index:", choices = acceptaple_features2,selected ="None", width = "1000px")
-checkboxInput("characteristic_irats2_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
-```
-
-<br>
-```{r, eval=TRUE, echo = FALSE}
-selectInput("characteristic_irats3", "Select Third Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
-checkboxInput("characteristic_irats3_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
-```
-
-<br>
-```{r, eval=TRUE, echo = FALSE}
-selectInput("characteristic_irats4", "Select Fourth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
-checkboxInput("characteristic_irats4_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
-```
-
-<br>
-```{r, eval=TRUE, echo = FALSE}
-selectInput("characteristic_irats5", "Select Fifth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
-checkboxInput("characteristic_irats5_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
-```
-
-<br>
-```{r, eval=TRUE, echo = FALSE}
-selectInput("characteristic_irats6", "Select Sixth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
-checkboxInput("characteristic_irats6_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
+fluidPage( 
+  h4("Firm Characteristics of the new index"),
+  fluidRow(
+    column(6,
+      selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features2,selected = acceptaple_features2[1], width = "425px"),
+      checkboxInput("characteristic_irats1_sign", "Reverse", value = FALSE),
+      selectInput("characteristic_irats2", "Second Firm Characteristic:", choices = acceptaple_features2,selected ="None", width = "425px"),
+checkboxInput("characteristic_irats2_sign", "Reverse", value = FALSE),
+    selectInput("characteristic_irats3", "Third Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
+checkboxInput("characteristic_irats3_sign", "Reverse", value = FALSE)
+     ),
+  column(6,
+      selectInput("characteristic_irats4", "Fourth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
+      checkboxInput("characteristic_irats4_sign", "Reverse", value = FALSE),
+    selectInput("characteristic_irats5", "Fifth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
+    checkboxInput("characteristic_irats5_sign", "Reverse", value = FALSE),
+    selectInput("characteristic_irats6", "Sixth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
+    checkboxInput("characteristic_irats6_sign", "Reverse", value = FALSE)
+    )
+  )
+)
 ```

### 2016-02-24 report.Rnw
tool

--- 2016-02-17 report.Rnw
@@
-<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+<< Data loading and recalculation, eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
 #rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
@@
 tic() #without report_tool.R: 77s
-
 ###################################################
@@
 
-source("lib_helpers.R")
-source("latex_code.R")
-source("dataset/indices_and_factors/ff_industries_sic.R")
-source("business_data_clean.R")
-source("Paper_global_parameters.R")
+source("lib_helpers.R",local=environment())
+source("latex_code.R",local=environment())
+source("dataset/indices_and_factors/ff_industries_sic.R",local=environment())
+source("business_data_clean.R",local=environment())
+source("Paper_global_parameters.R",local=environment())
 
 if (generate_rnw_data == 1){
-  source("bb_issuers.R")
+  source("bb_issuers.R",local=environment())
 }  else{
   if (reload_data)
-    #load("tmpfiles/bb_issuersALL.Rdata")
-    load("bb_issuersTOOL.Rdata")
-  source("lib_helpers.R") 
-  source("latex_code.R")
-  source("dataset/indices_and_factors/ff_industries_sic.R")
-  source("business_data_clean.R")
-  source("Paper_global_parameters.R")
+    load(normalizePath("bb_issuersTOOL.Rdata"))
+  source("lib_helpers.R",local=environment()) 
+  source("latex_code.R",local=environment())
+  source("dataset/indices_and_factors/ff_industries_sic.R",local=environment())
+  source("business_data_clean.R",local=environment())
+  source("Paper_global_parameters.R",local=environment())
 }
@@
 #Add any/all choices made in the tool here
-if(!exists("input")){
+if(!exists("input") ){#& FALSE
   input = list()
-  input$startdate <- as.Date("2000-12-31")
+  input$startdate <- as.Date("1984-12-31")
   input$enddate <- as.Date("2014-12-31")
-  input$market_cap_min = 50
-  input$market_cap_max = 505755
-  input$quantile_used_ind = 0.2
-  input$quantile_used_all = 0.4
+  market_cap_min = "10"
+  market_cap_max = "10000"
+  quantile_used_ind = "0.2"
+  quantile_used_all = "0.4"
 
@@
 
-  input$characteristic_irats2 <- "Pre.Vol.Score"
+  input$characteristic_irats2 <- "pre.vol.Score"
   input$characteristic_irats2_sign <- T
 }
-
+market_cap_min = as.numeric(input$market_cap_min)
+market_cap_max = as.numeric(input$market_cap_max)
+quantile_used_ind = as.numeric(input$quantile_used_ind)
+quantile_used_all = as.numeric(input$quantile_used_all)
+
+#need to add environment here because this is called from Rmd
 options(warn=-1) #because some period don't have data
-source("report_helpers.R")
-source("report_tool.R")
-source("report_tool_section.R")
+source("report_helpers.R",local=environment()) 
+source("report_tool.R",local=environment())
+source("report_tool_section.R",local=environment())
 options(warn=0)
@@
 Finally, we removed the following events: no CRSP returns available (\Sexpr{cleanup_bb$get_crsp$NOPERMNO_remove + cleanup_bb$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_bb$compustat$NO_GVKEY_remove + cleanup_bb$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).
-Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(BUYBACK_DATA$finance_Size_used)}  events).\footnote{We are using the industries from Kenneth French's Website.
+Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(BUYBACK_DATA_NEW$finance_Size_used)}  events).\footnote{We are using the industries from Kenneth French's Website.
 The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799).
@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-SEO_exit_days = sapply(which(BUYBACK_DATA$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(BUYBACK_DATA$DATASET$SDC$Otherlater[i]) - event.date_bb[i])
+SEO_exit_days = sapply(which(BUYBACK_DATA_NEW$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(BUYBACK_DATA_NEW$DATASET$SDC$Otherlater[i]) - event.date_bb[i])
 BB_exit_days = sapply(which(ISSUERS_DATA$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(ISSUERS_DATA$DATASET$SDC$Otherlater[i]) - event.date_iss[i])
@@
 << fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-tmp = pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))
-ri = remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)
+tmp = pnl_matrix(remove_initialization_time(BUYBACK_DATA_NEW$long_all12mshort_risk_factors,min_date=FirstTrade))
+ri = remove_initialization_time(BUYBACK_DATA_NEW$long_all12mshort_risk_factors,min_date=FirstTrade)
 expost_betas = beta_expost(ri,Risk_Factors_Monthly[,pnl_hedge_factors])
-ri = remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_12M,min_date=FirstTrade)
+ri = remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_12M,min_date=FirstTrade)
 expost_betas_unhedged = beta_expost(ri,Risk_Factors_Monthly[,pnl_hedge_factors])
@@
 << fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade))
-months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all3mshort_risk_factors,min_date=FirstTrade))
-months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all6mshort_risk_factors,min_date=FirstTrade))
-months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))
-months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all24mshort_risk_factors,min_date=FirstTrade))
-months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all36mshort_risk_factors,min_date=FirstTrade))
-months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all48mshort_risk_factors,min_date=FirstTrade))
+months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all1mshort_risk_factors,min_date=FirstTrade))
+months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all3mshort_risk_factors,min_date=FirstTrade))
+months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all6mshort_risk_factors,min_date=FirstTrade))
+months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all12mshort_risk_factors,min_date=FirstTrade))
+months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all24mshort_risk_factors,min_date=FirstTrade))
+months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all36mshort_risk_factors,min_date=FirstTrade))
+months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all48mshort_risk_factors,min_date=FirstTrade))
 
@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-EU_index_features = scrub(cbind(BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA$DATASET$SDC$pre_vol,BUYBACK_DATA$Valuation_Index))
+EU_index_features = scrub(cbind(BUYBACK_DATA_NEW$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA_NEW$DATASET$SDC$pre_vol,BUYBACK_DATA_NEW$Valuation_Index))
 colnames(EU_index_features) <- c("Idiosyncratic Score", "Volatility Score", "U-Index Score")
@@
 ``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement.
-Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available\footnote{As this SDC data was not available for many events, we did not consider the in the U-index calculation} (this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.
+Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available\footnote{As this SDC data was not available for many events, we did not consider the in the U-index calculation} (this data was available only for \Sexpr{sum(!(BUYBACK_DATA_NEW$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA_NEW$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.
 
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-tmp_market_cap = round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb %in% c(4:6)])/1000,1)
+tmp_market_cap = round(non_zero_mean(BUYBACK_DATA_NEW$DATASET$SDC$Market.Cap[EUindex_bb %in% c(4:6)])/1000,1)
 @
@@
 portfolios EU4 through EU6 in Table~\ref{tbl:EUunderBBcal}) is \$\Sexpr{tmp_market_cap} billion (not indicated in the Table).
-So the buyback anomaly is to some extent a small cap anomaly, although portfolio EU3 for which the average market capitalization of its \Sexpr{sum(EUindex_bb==3)} firms is \$\Sexpr{round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb ==3])/1000,1)} billion still has significant abnormal returns.
+So the buyback anomaly is to some extent a small cap anomaly, although portfolio EU3 for which the average market capitalization of its \Sexpr{sum(EUindex_bb==3)} firms is \$\Sexpr{round(non_zero_mean(BUYBACK_DATA_NEW$DATASET$SDC$Market.Cap[EUindex_bb ==3])/1000,1)} billion still has significant abnormal returns.
 
@@
 tmp = pnl_matrix(remove_initialization_time(High_EU_BB_Hedged,min_date=FirstTrade))
-tmp1 = pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))
+tmp1 = pnl_matrix(remove_initialization_time(BUYBACK_DATA_NEW$long_all12mshort_risk_factors,min_date=FirstTrade))
 
@@
 latex_render_data_frame(
-  pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)), 
+  pnl_matrix(remove_initialization_time(BUYBACK_DATA_NEW$long_all12mshort_risk_factors,min_date=FirstTrade)), 
   title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all buybacks",
@@
 
-number_eventsBB = table(format(BUYBACK_DATA$DATASET$SDC$Event.Date[BUYBACK_DATA$DATASET$SDC$Event.Date >= FirstTrade], "%Y"))
+number_eventsBB = table(format(BUYBACK_DATA_NEW$DATASET$SDC$Event.Date[BUYBACK_DATA_NEW$DATASET$SDC$Event.Date >= FirstTrade], "%Y"))
 market_index = 100*(1+cumprod(1+Market_Monthly[names(Market_Monthly) >= "1985-01-01"]))
@@
 all_ret_values = data.frame(
-  market = cumsum(100*Market_Monthly[str_sub(names(Market_Monthly), start = 1, end = 7) %in% str_sub(names(remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_1M,min_date=FirstTrade)), start = 1, end = 7)]),
-  #market = cumsum(100*Market_Daily[names(remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_1M,min_date=FirstTrade))]),
-  months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_1M,min_date=FirstTrade)),
-  months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_3M,min_date=FirstTrade)),
-  months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_6M,min_date=FirstTrade)),
-  months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_12M,min_date=FirstTrade)),
-  months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_24M,min_date=FirstTrade)),
-  months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_36M,min_date=FirstTrade)),
-  months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_48M,min_date=FirstTrade))
+  market = cumsum(100*Market_Monthly[str_sub(names(Market_Monthly), start = 1, end = 7) %in% str_sub(names(remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_1M,min_date=FirstTrade)), start = 1, end = 7)]),
+  #market = cumsum(100*Market_Daily[names(remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_1M,min_date=FirstTrade))]),
+  months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_1M,min_date=FirstTrade)),
+  months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_3M,min_date=FirstTrade)),
+  months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_6M,min_date=FirstTrade)),
+  months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_12M,min_date=FirstTrade)),
+  months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_24M,min_date=FirstTrade)),
+  months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_36M,min_date=FirstTrade)),
+  months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_48M,min_date=FirstTrade))
 )
@@
 all_ret_values = data.frame(
-  market = cumsum(100*Market_Monthly[str_sub(names(Market_Monthly), start = 1, end = 7) %in% str_sub(names(remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade)), start = 1, end = 7)]),
-  #market = cumsum(100*Market_Daily[names(remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade))]),
-  months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade)),
-  months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all3mshort_risk_factors,min_date=FirstTrade)),
-  months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all6mshort_risk_factors,min_date=FirstTrade)),
-  months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)),
-  months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all24mshort_risk_factors,min_date=FirstTrade)),
-  months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all36mshort_risk_factors,min_date=FirstTrade)),
-  months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all48mshort_risk_factors,min_date=FirstTrade))
+  market = cumsum(100*Market_Monthly[str_sub(names(Market_Monthly), start = 1, end = 7) %in% str_sub(names(remove_initialization_time(BUYBACK_DATA_NEW$long_all1mshort_risk_factors,min_date=FirstTrade)), start = 1, end = 7)]),
+  #market = cumsum(100*Market_Daily[names(remove_initialization_time(BUYBACK_DATA_NEW$long_all1mshort_risk_factors,min_date=FirstTrade))]),
+  months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all1mshort_risk_factors,min_date=FirstTrade)),
+  months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all3mshort_risk_factors,min_date=FirstTrade)),
+  months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all6mshort_risk_factors,min_date=FirstTrade)),
+  months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all12mshort_risk_factors,min_date=FirstTrade)),
+  months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all24mshort_risk_factors,min_date=FirstTrade)),
+  months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all36mshort_risk_factors,min_date=FirstTrade)),
+  months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all48mshort_risk_factors,min_date=FirstTrade))
 )
@@
 
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[High_Idiosyncr_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$Rsq_returns[High_Idiosyncr_eventsBB]
+  all_dates = paste(str_sub((BUYBACK_DATA_NEW$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA_NEW$DATASET$SDC$Event.Date),start=6,end=7),sep="")[High_Idiosyncr_eventsBB]
+  tmp = BUYBACK_DATA_NEW$DATASET$SDC$Rsq_returns[High_Idiosyncr_eventsBB]
   names(tmp)<-all_dates
@@
   R2_thresholds_up_plot = R2_thresholds_up_plot[!is.na(R2_thresholds_up_plot)]
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[Low_Idiosyncr_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$Rsq_returns[Low_Idiosyncr_eventsBB]
+  all_dates = paste(str_sub((BUYBACK_DATA_NEW$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA_NEW$DATASET$SDC$Event.Date),start=6,end=7),sep="")[Low_Idiosyncr_eventsBB]
+  tmp = BUYBACK_DATA_NEW$DATASET$SDC$Rsq_returns[Low_Idiosyncr_eventsBB]
   names(tmp)<-all_dates
@@
 
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[High_VOL_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$pre_vol[High_VOL_eventsBB]
+  all_dates = paste(str_sub((BUYBACK_DATA_NEW$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA_NEW$DATASET$SDC$Event.Date),start=6,end=7),sep="")[High_VOL_eventsBB]
+  tmp = BUYBACK_DATA_NEW$DATASET$SDC$pre_vol[High_VOL_eventsBB]
   names(tmp)<-all_dates
@@
   VOL_thresholds_up_plot = 100*VOL_thresholds_up_plot[!is.na(VOL_thresholds_up_plot)]
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[Low_VOL_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$pre_vol[Low_VOL_eventsBB]
+  all_dates = paste(str_sub((BUYBACK_DATA_NEW$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA_NEW$DATASET$SDC$Event.Date),start=6,end=7),sep="")[Low_VOL_eventsBB]
+  tmp = BUYBACK_DATA_NEW$DATASET$SDC$pre_vol[Low_VOL_eventsBB]
   names(tmp)<-all_dates
@@
 
-%########################################################################################################
+%#######################################################################
 %## REPORT.RNW SPECIAL CODE:
@@
 << fig.width=10, fig.height=4, out.width='\\textwidth', echo=F >>=
-#par(mfrow=c(2,1), mar=c(2.3,4,2.3,4))
-#valuation_index_bb[which(valuation_index_bb==2)]<-3 # there is one company here. need to check why
 tmp = table(secU$Index_score)
@@
 barplot(tmp,main = "", ylab = "Number of Announcements", xlab = "",las=2,space=0.5, cex.names=0.8)
-#tmp = table(valuation_index_iss)
-#tmp = structure(as.numeric(tmp), .Names = names(tmp))
-#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=0.8)
 rm("tmp")

### 2016-02-24 create_tool_data.R

@@ -56,7 +56,7 @@ with(BUYBACK_DATA_TOOL,{
   DATASET$compustat_data = BUYBACK_DATA$DATASET$compustat_data
   
   SDC = data.frame(
-    
+    permno = BUYBACK_DATA$DATASET$SDC$permno,
     Otherlater = BUYBACK_DATA$DATASET$SDC$Otherlater,
     OtherlaterEvent = BUYBACK_DATA$DATASET$SDC$OtherlaterEvent,
     Source...of..Funds..Code = BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code,
@@ -84,6 +84,7 @@ with(BUYBACK_DATA_TOOL,{
     CMA.beta = BUYBACK_DATA$DATASET$SDC$CMAbeta,
     
     minus_Rsq_returns = BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns,
+    Idiosyncraticness = BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns,
     Rsq_returns = BUYBACK_DATA$DATASET$SDC$Rsq_returns,
     one.minus.Rsq.Score = BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns,
     pre_vol = BUYBACK_DATA$DATASET$SDC$pre_vol,
@@ -125,6 +126,7 @@ with(ISSUERS_DATA_TOOL,{
   DATASET$DatesMonth = ISSUERS_DATA$DATASET$DatesMonth
   
   SDC = data.frame(
+    permno     = ISSUERS_DATA$DATASET$SDC$permno,
     Otherlater = ISSUERS_DATA$DATASET$SDC$Otherlater,
     Event.Date = ISSUERS_DATA$DATASET$SDC$Event.Date,
     

### 2016-02-24 report_helpers.R

@@ -7,7 +7,7 @@ car_table_cache <- function(returns,Event.Date,Risk_Factors_Monthly,min_window =
   allmonths = min_window:max_window 
   
   factors_used_noRF = setdiff(factors_used, "RF")
-  if (ncol(returns) < length(factors_used_noRF) + 1){
+  if (ncol(returns) < length(factors_used_noRF) + 1){ 
     results = matrix(0,nrow=length(allmonths), ncol = 3)
     results = rbind(results, rep(ncol(returns)))
     betas = matrix(0,nrow=length(allmonths), ncol = length(factors_used_noRF))
@@ -48,19 +48,21 @@ car_table_cache <- function(returns,Event.Date,Risk_Factors_Monthly,min_window =
     "Row.Date"      = Row.Date,
     "Risk_Factors_Monthly" = Risk_Factors_Monthly,
     "form"          = form,
-    "factors_used_noRF" = factors_used_noRF
+    "factors_used_noRF" = factors_used_noRF,
+    "min_window"    = min_window,
+    "max_window"    = max_window
   ))
 }
 #ignore allmonths for now, I don't think this can work
-car_table_cached <- function(cache,thesubset=NULL,allmonths=NULL,min_window = -6, max_window = 48) {
+car_table_cached <- function(cache,thesubset=NULL) {
   if(is.null(thesubset)) 
     thesubset = 1:length(cache$Event.Date)
   #if(!is.null(allmonths)) {
   #monthindex = ifelse(allmonths > 0, paste("+",allmonths,sep=""), allmonths)
   #} else {
   monthindex = rownames(cache$EVENT_ALIGNED)
-  min_window = min(1,min_window)
-  max_window = max(-1,max_window)
+  min_window = min(1,cache$min_window)
+  max_window = max(-1,cache$max_window)
   allmonths = min_window:max_window 
   #}
   EVENT_ALIGNED        <- cache$EVENT_ALIGNED[monthindex,thesubset,]

### 2016-02-24 report_tool.R

@@ -1,12 +1,11 @@
 #disable for debugging
-#load("bb_issuersALL.Rdata")
 report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)
 report_months_car = sort(c((-3:24)*2,1))
-reported_times_plots <-  c("-6","-4","-2","0","+1","+2","+4","+6","+8","+10","+12","+14","+16","+18","+20","+22","+24","+26","+28","+30","+32","+34","+36","+38","+40","+42","+44","+46","+48")  
+#reported_times_plots <-  c("-6","-4","-2","0","+1","+2","+4","+6","+8","+10","+12","+14","+16","+18","+20","+22","+24","+26","+28","+30","+32","+34","+36","+38","+40","+42","+44","+46","+48")  
 
 #general variables and overwriting 
-useonly_bb = which(BUYBACK_DATA$DATASET$SDC$Event.Date >= input$startdate & BUYBACK_DATA$DATASET$SDC$Event.Date <= input$enddate & scrub(BUYBACK_DATA$DATASET$SDC$Market.Cap) >= input$market_cap_min & scrub(BUYBACK_DATA$DATASET$SDC$Market.Cap) <= input$market_cap_max) 
-useonly_is = which(ISSUERS_DATA$DATASET$SDC$Event.Date >= input$startdate & ISSUERS_DATA$DATASET$SDC$Event.Date <= input$enddate & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) >= input$market_cap_min & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) <= input$market_cap_max) 
+useonly_bb = which(BUYBACK_DATA$DATASET$SDC$Event.Date >= input$startdate & BUYBACK_DATA$DATASET$SDC$Event.Date <= input$enddate & scrub(BUYBACK_DATA$DATASET$SDC$Market.Cap) >= market_cap_min & scrub(BUYBACK_DATA$DATASET$SDC$Market.Cap) <= market_cap_max) 
+useonly_is = which(ISSUERS_DATA$DATASET$SDC$Event.Date >= input$startdate & ISSUERS_DATA$DATASET$SDC$Event.Date <= input$enddate & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) >= market_cap_min & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) <= market_cap_max) 
 
[…]

### 2016-02-24 report_tool_section.R

@@ -1,35 +1,42 @@
 #overwrite some variables that we need
-if(!exists("BUYBACK_DATA2")) {
-  BUYBACK_DATA2 <- BUYBACK_DATA
+if(!exists("BUYBACK_DATA_NEW")) {
+  BUYBACK_DATA_NEW <- BUYBACK_DATA
 }
-useonly_bb = which(BUYBACK_DATA2$DATASET$SDC$Event.Date >= input$startdate & BUYBACK_DATA2$DATASET$SDC$Event.Date <= input$enddate & scrub(BUYBACK_DATA2$DATASET$SDC$Market.Cap) >= input$market_cap_min & scrub(BUYBACK_DATA2$DATASET$SDC$Market.Cap) <= input$market_cap_max) 
-useonly_is = which(ISSUERS_DATA$DATASET$SDC$Event.Date >= input$startdate & ISSUERS_DATA$DATASET$SDC$Event.Date <= input$enddate & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) >= input$market_cap_min & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) <= input$market_cap_max) 
+useonly_bb = which(BUYBACK_DATA_NEW$DATASET$SDC$Event.Date >= input$startdate & BUYBACK_DATA_NEW$DATASET$SDC$Event.Date <= input$enddate & scrub(BUYBACK_DATA_NEW$DATASET$SDC$Market.Cap) >= market_cap_min & scrub(BUYBACK_DATA_NEW$DATASET$SDC$Market.Cap) <= market_cap_max) 
+useonly_is = which(ISSUERS_DATA$DATASET$SDC$Event.Date >= input$startdate & ISSUERS_DATA$DATASET$SDC$Event.Date <= input$enddate & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) >= market_cap_min & scrub(ISSUERS_DATA$DATASET$SDC$Market.Cap) <= market_cap_max) 
 subset_undervalued_bb <- company_subset_undervalued_bb[useonly_bb]
 subset_overvalued_bb <- company_subset_overvalued_bb[useonly_bb]
 
 BUYBACK_DATA$DATASET$SDC$Pre.Vol.Score <- BUYBACK_DATA$DATASET$SDC$pre_vol_Score
-BUYBACK_DATA2$DATASET$SDC$Pre.Vol.Score <- BUYBACK_DATA2$DATASET$SDC$pre_vol_Score
[…]

### 2016-02-25 index.Rmd
updates

@@
   content = function(file) {
-    knitr::knit2pdf("report.Rnw",envir=environment())
+    tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
+    newinput <- list()
+    for(i in tosave) {
+      newinput[[i]] <- input[[i]]
+    }
+
+    save("newinput",file=normalizePath("input.Rdata"))
+    knitr::knit2pdf("report.Rnw",envir=globalenv())
     file.rename(normalizePath('report.pdf'), file)
@@
   useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
+  cat(paste("Total left after filtering industry:",sum(useonly_industry)))
   res = round(cbind(

### 2016-02-25 report.Rnw
updates

@@
 
+options(warn=-1) #because some packages give warnings
 source("lib_helpers.R",local=environment())
@@
 source("Paper_global_parameters.R",local=environment())
+options(warn=0)
 
@@
 if(!exists("input") ){#& FALSE
-  input = list()
-  input$startdate <- as.Date("1984-12-31")
-  input$enddate <- as.Date("2014-12-31")
-  market_cap_min = "10"
-  market_cap_max = "10000"
-  quantile_used_ind = "0.2"
-  quantile_used_all = "0.4"
-
-  #for extra sections
-  input$characteristic_irats1 <- "BE.ME.Score"
-  input$characteristic_irats1_sign <- T
-
-  input$characteristic_irats2 <- "pre.vol.Score"
-  input$characteristic_irats2_sign <- T
+  load(normalizePath("input.Rdata")) #this is updated by the Rmd
+  input <- newinput
 }
@@
 FirstTrade = input$startdate
-
 @
@@
 BB_exit_days = sapply(which(ISSUERS_DATA$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(ISSUERS_DATA$DATASET$SDC$Otherlater[i]) - event.date_iss[i])
+
+SEO_exit_days = ifelse(is.null(SEO_exit_days),list(),SEO_exit_days)
+BB_exit_days = ifelse(is.null(BB_exit_days),list(),BB_exit_days)
 @

### 2016-02-25 report_tool.R

@@ -96,7 +96,7 @@ CACHE5 <- car_table_cache(ret_bb,sdc_bb$Event.Date,Risk_Factors_Monthly,formula_
 CACHE3IS <- car_table_cache(ret_is,sdc_is$Event.Date,Risk_Factors_Monthly,formula_used = three_factor_model)
 CACHE5IS <- car_table_cache(ret_is,sdc_is$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)
 
-if(FALSE) {  #FOR DEBUGGING SECTIONS
+if(TRUE) {  #FOR DEBUGGING SECTIONS
 #****************************
 # Table modification 1
 IRATS_table_all_3f = car_table_cached(CACHE3)

### 2016-03-03 bb_issuers.Rnw
update

@@
 %\noindent We re-examine the behavior of stock returns after net issue  announcements using the five-factor model proposed by Fama and French (2015a).
-We confirm their findings that the equity issue anomaly disappears  with the five-factor model, but the buyback anomaly does not..
+We confirm their findings that the equity issue anomaly disappears  with the five-factor model, but the buyback anomaly does not.
 Buyback announcements by firms  with high pre-announcement (idiosyncratic) volatility  are followed by higher long-term abnormal returns.
@@
 For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}  In spite of these well documented anomalies investors are not less excited today about e.g., a buyback announcement than 30 years ago: on average stock prices increase by approximately 2 to 3$\%$  when companies announce that the board of directors has approved a buyback program.
-Moreover, we find very few funds that specialize in exploiting these anomalies.\footnote{  For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA.
+Moreover, we find very few funds that specialize in exploiting these anomalies.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA.
 The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization.
-We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} The fact that these anomalies have not generated a significant response from investors and asset management firms is somewhat surprising considering that other anomalies have disappeared after being documented in academic research~\citep{McLean2015}.
+We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} The fact that these anomalies have not generated a significant response from investors and asset management firms is somewhat surprising considering that other anomalies have disappeared after being documented in academic research~\citep{McLean2016}.
 What makes these capital structure anomalies different so that they stand the test of time?
@@
 Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues).
-The part of their sample where net equity issues are positive is defined as the ``buyback sample''.
+The part of their sample where net equity issues are positive is defined as the "buyback sample".
 But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations.
-Moreover the idea of pooling buybacks and equity issues in ``net issues'' assumes that the decision to issue equity is simply the mirror of buying back shares.
-However, issuing stock to new investors is not the same as buying back stock from ``old'' selling investors.
+Moreover the idea of pooling buybacks and equity issues in "net issues" assumes that the decision to issue equity is simply the mirror of buying back shares.
+However, issuing stock to new investors is not the same as buying back stock from "old" selling investors.
 In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only takes advantage of selling shareholders who leave the firm.
@@
 
-A second possible reason for the funds' lack of interest in the buyback anomaly is that event studies aggregate returns over a very long horizon.
-The fact that buying shares after a buyback announcement generates positive excess returns during for example 1990-2014 does not mean that, if one starts a fund in 2016, one can expect to beat the market during the next 3 years.
-In other words, the anomaly may be time dependent, and investor patience may not extend beyond 3 years.
-Moreover, because of the growth of institutional investors and the reduction in trading costs markets may have become more efficient in recent years as argued by \cite{FuHuang2015}.
-The anomaly may also be industry-specific so that an investor who follows a buyback strategy may end up with a highly undiversified portfolio.
-
-The long-term event studies also do not give much guidance about when to sell after a buyback or cover after shorting an equity issue.
-Trading strategies, such as $M\&A$ arbitrage (\cite{MitchellPulvino2001}), often have ``natural'' exit decision points (e.g., at $M\&A$ deal completion or termination), but the literature does not provide clear guidance about when to exit a buyback position.
-Empirical studies tend to show that, on average, excess returns continue for up to 3 or 4 years after a buyback authorization, but there is no reason why such a horizon is optimal.
-One straightforward ``early'' selling strategy that we study is to combine the buyback and equity issuance anomalies by selling buyback stocks after the firm announces an equity issue.
-Note that the fact that equity issues in general are followed by negative abnormal returns does not necessarily imply that equity issues after buybacks should generate the same result.
-
-Finally, the results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously.
-Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information.
-If the buyback signals a change in risk (\cite{GrullonMichaely2004}) hedging market risk may be complicated.
-That is why in this paper we also simulate hedged investment strategies where we estimate risk {\it before} forming the portfolios.
-
-The purpose of this paper is to explore these concerns by studying the robustness of the buybacks and issuance anomalies over the 30 year period starting in January \Sexpr{firstyear} and ending in December \Sexpr{lastyear}, using the \cite{FamaFrench2015a} five-factor model.
-Although there are other models of market equilibrium proposed to explain excess returns after buyback authorizations (i.e.
-\cite{Linetal2014}) our focus is on the \cite{FamaFrench2015a} challenge.
-We confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
+Using buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, we confirm the Fama and French (2015b) conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
 Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio.
@@
 We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries.
-
-We also test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}: that (idiosyncratic) volatility is negatively related to future returns.
-For example, \cite{Ang2006} find negative alphas for high volatility and high idiosyncratic volatility stocks, using the 3 factor \cite{FamaFrench1993} model.
+The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2015}.
+
+<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
+months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade))
+months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all3mshort_risk_factors,min_date=FirstTrade))
+months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all6mshort_risk_factors,min_date=FirstTrade))
+months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))
+months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all24mshort_risk_factors,min_date=FirstTrade))
+months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all36mshort_risk_factors,min_date=FirstTrade))
+months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all48mshort_risk_factors,min_date=FirstTrade))
+
+@
+
+The results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously.
+Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information.
+If the buyback signals a change in risk (\cite{GrullonMichaely2004}) hedging market risk may be complicated.
+That is why in this paper we also simulate hedged investment strategies where we estimate risk before forming the portfolios.
+We show that an investor who followed this strategy starting in \Sexpr{firstyear} would by \Sexpr{lastyear} have realized cumulative excess returns between \Sexpr{round(tail(months1,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$, depending on the length of the holding period.
+
+The second major purpose of this paper is to test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}, i.e.
+(idiosyncratic) volatility is negatively related to expected returns.
+For example, \cite{Ang2006} find negative alphas for high volatility and high idiosyncratic volatility stocks, using the 3-factor \cite{FamaFrench1993} model.
 Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms.
@@
 This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market.
-The result is also consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  stocks.
+The result is also consistent with the  {\it costly arbitrage hypothesis} of \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued  stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  Their argument is that idiosyncratic volatility represents arbitrage risk and deters arbitrage and the resulting reduction in mispricing.
+So, among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.
 
@@
 If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.
-Combining idiosyncratic risk and total volatility  with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns.
+
+Combining idiosyncratic risk and total volatility with the Peyer and Vermaelen (2009) Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns.
 In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
@@
 
-<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade))
-months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all3mshort_risk_factors,min_date=FirstTrade))
-months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all6mshort_risk_factors,min_date=FirstTrade))
-months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))
-months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all24mshort_risk_factors,min_date=FirstTrade))
-months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all36mshort_risk_factors,min_date=FirstTrade))
-months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all48mshort_risk_factors,min_date=FirstTrade))
-
-@
-
-We report the returns of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns.
-Specifically, at the end of \Sexpr{lastyear} the cumulative returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$.
+We report the returns and excess returns of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns.
+Specifically, at the end of \Sexpr{lastyear} the cumulative excess returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$.
 This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer.
@@
 
-There exists a large literature on volatility and stock returns.
-One of the most puzzling findings is the fact that total volatility and idiosyncratic volatility are negatively correlated with future abnormal returns, when expected returns are calculated using the 3 factor \cite{FamaFrench1993} model  (see e.g.
+There exists a large literature on volatility and stock returns.\footnote{For the most recent overview of the literature and potential hypotheses, see \cite{LiRodneyGarcia2016}.} One of the most puzzling findings is the fact that total volatility and idiosyncratic volatility are negatively correlated with future abnormal returns, when expected returns are calculated using the 3 factor \cite{FamaFrench1993} model  (see e.g.
 \cite{Ang2006} (Table VII)).
@@
 However, as we want to differentiate between ``idiosyncratic'' companies and ``high volatility'' ones, to consider both the effects of company specific information and of the option value of a buyback announcement, we separately study the relations with $R^2$ and volatility.
-See also \cite{Lietal2014} for a discussion on this issue.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$.
+See also \cite{LiRajgopaletal2014} for a discussion on this issue.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$.
 We also define the idiosyncratic score of a firm to be the percentile of its $1-R^2$ across all CRSP firms that month.
@@
 Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).
+So our results are also consistent with the \cite{Stambaugh2015} interpretation.
 
@@
 They show that this option can have a lot of value, something that may not be realized at the time of the announcement of the buyback authorization.
+For example, the market may underestimate the maturity of the option if they don't realize that firms who are announcing a buyback authorization for say 2 years are likely to renew the authorization many times in the future.
 Hence, perhaps total volatility is a better prediction of excess returns than idiosyncratic volatility or the U-index.

### 2016-03-03 index.Rmd
update

--- 2016-02-24 index.Rmd
@@
 
-#library(googleVis)
-#library("shiny")
-#library("reshape2")  
-#library("ggplot2")
+if(T) {
+  library(googleVis)
+  library("shiny")
+  library("reshape2")  
+  library("ggplot2")
   # Why are these not found when deployed?!
@@
   library("timeDate")
+  library("dygraphs")
+  library("reshape")
+  library("ggplot2")
+}
 source("lib/lib_helpers_shiny.R")
@@
 Users can explore the effects of various parameters as well as data filtering choices.
-For any given choices, users can generate and download a new **customized pdf version of the paper** by clicking the button below at any time.
+For any given choices, users can generate and download a new **customized pdf version of the paper** by clicking the buttons which will appear below at any time.
 
@@
 ```{r, fig.width=6, fig.height=5,echo=FALSE}
-downloadHandler(
+shinyApp(
+  ui = fluidPage(
+    fluidRow(
+      column(2,
+        conditionalPanel(
+          condition = "!$('makeReport').hasClass('shiny-busy')",
+          actionButton("makeReport","Generate Report",icon=icon("file"))
+        )
+      ),
+      column(4,
+      conditionalPanel(
+        condition = "!$('makeReport').hasClass('shiny-busy')",
+        uiOutput("downloadButton")
+        #downloadButton("downloadReport", "Download Report")
+      )
+      )
+    ),
+    busyIndicator("Please wait while we prepare the report ...",wait = 0)
+  ),
+  server = function(input, output) {
+    output$download_button <- renderUI({
+        downloadButton("downloadReport", "Download Results")
+     })
+    makeReportAction <- eventReactive(input$makeReport, {
+      #Create the pdf here
+      #Sys.sleep(1);return()
+      #first check if we didn't already create a paper with these parameters, if so, load from cache
+      #filename <- paste("reports/")
+      #file.exists()
+      tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
+        newinput <- list()
+        for(i in tosave) {
+          newinput[[i]] <- input[[i]]
+        }
+        #save("newinput",file=normalizePath("input.Rdata"))
+        knitr::knit2pdf("report.Rnw",envir=globalenv())
+    })
+    output$downloadButton <- renderUI({
+      makeReportAction() #only appear after first click on generate
+      downloadButton("downloadReport", "Download Report")
+    })
+    output$downloadReport <- downloadHandler(
       filename = "report.pdf",
       content = function(file) {
-    knitr::knit2pdf("report.Rnw",envir=environment())
+        cat(paste("Does the pdf exist?",file.exists("report.pdf")))
         file.rename(normalizePath('report.pdf'), file)
@@
     )
+  },
+  options = list(height = 120,width=800)
+)
+
 ```
@@
 ```{r, eval=TRUE, echo = FALSE}
-acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Idiosyncraticness","Industry", "Purpose.Code","Source.of.funds")
+acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Industry", "Purpose.Code","Source.of.funds")
 
 fluidPage(
-  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[1]),
+  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[4]),
   mainPanel(
@@
 ```{r, eval=TRUE, echo = FALSE}
-checkboxGroupInput("industry", "Select Industries  to remove:", choices = unique(DATASET_INI$SDC$Industry),selected = "Software",inline=TRUE)
+checkboxGroupInput("industry", "Select Industries to remove:", choices = unique(DATASET_INI$SDC$Industry),selected = NULL,inline=TRUE)
 
@@
   useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
+  #cat(paste("Total left after filtering industry:",sum(useonly_industry)))
+  #instead of using company_subset_undervalued and _overvalued, use Valuation Index
+  thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == "Valuation.Index")]]
+  thefeature = as.numeric(scrub(thefeature))
+  quantile_used_ind = as.numeric(0.2)
+  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
+  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)
+
   res = round(cbind(
-    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
-    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
-    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
-    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
+    #car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
+    #car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
+    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & Low_feature_events)$results,
+    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & High_feature_events)$results
   ),2)[reported_times,]
@@
 feature_CALtable_industry <- reactive({
+    thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == "Valuation.Index")]]
+  thefeature = as.numeric(scrub(thefeature))
+  quantile_used_ind = as.numeric(0.2)
+  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
+  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)
+
   useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
   res = round(cbind(
-    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly,report_months_cal)$results,
-    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly,report_months_cal)$results
+    #calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly,report_months_cal)$results,
+    #calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly,report_months_cal)$results
+    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & Low_feature_events], DATASET_NEW()$SDC$Event.Date[useonly_industry& Low_feature_events], Risk_Factors_Monthly,report_months_cal)$results,
+        calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & High_feature_events], DATASET_NEW()$SDC$Event.Date[useonly_industry & High_feature_events], Risk_Factors_Monthly,report_months_cal)$results
+
   ),2)[reported_times,]
@@
 ```{r, eval=TRUE, echo = FALSE}
-acceptaple_features1 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Idiosyncraticness")
+acceptaple_features1 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio")
 
-selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features1,selected = acceptaple_features1[1], width = "1000px")
+selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features1,selected = acceptaple_features1[4], width = "1000px")
 
@@
   thefeature = as.numeric(scrub(thefeature))
-  quantile_used_ind = as.numeric(input$quantile_used_ind)
+  quantile_used_ind = as.numeric(input$quantile_used)
 
@@
 ```{r, eval=TRUE, echo = FALSE}
-acceptaple_features2 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Idiosyncraticness","None")
+acceptaple_features2 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","None")
 ```
@@
     column(6,
-      selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features2,selected = acceptaple_features2[1], width = "425px"),
+      selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features2,selected = acceptaple_features2[4], width = "425px"),
       checkboxInput("characteristic_irats1_sign", "Reverse", value = FALSE),
@@
     tabsetPanel("Example",
+                tabPanel("Histogram of the New Index",
+                         busyIndicator("Calculating results ...",wait = 0),
+                         renderPlot({
+                           feature = Index_Score_rect()
+                           feature = feature[!is.na(feature)]
+                           if (!is.numeric(feature))
+                             feature = 1
+                           hist(feature, density = 100, breaks = 20,main="Index Histogram",xlab="Score")
+                         })),
                 tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
@@
                            feature_CALtable_index()
-                         })),
-                tabPanel("Histogram of the New Index",
-                         busyIndicator("Calculating results ...",wait = 0),
-                         renderPlot({
-                           feature = Index_Score_rect()
-                           feature = feature[!is.na(feature)]
-                           if (!is.numeric(feature))
-                             feature = 1
-                           hist(feature, density = 100, breaks = 100)
                          })),

### 2016-03-19 bb_issuers.Rnw
update paper

@@
 
-\noindent \textit{JEL classification}: G35
+\noindent  \textit{JEL classification}: G35; G14; G32
 
 \medskip
-\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings
+\noindent \textit{Keywords}: Share Buybacks; Seasoned Equity Offerings; Anomalies
 
@@
 One straightforward explanation is that they are not really anomalous returns but compensation for risk.
-Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the Carhart (1997) 4-factor model as benchmarks.
+Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the \cite{Carhart1997} 4-factor model as benchmarks.
 However, \cite{FamaFrench2015b}  argue that the buyback and equity issue anomalies do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns.
-This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns (Novy-Marx (2013)).
+This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns \citep{NovyMarx2013}.
 If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research.
@@
 First, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date as e.g., \cite{PeyerVermaelen2009}.
-For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization (Stephens and Weisbach (1998)).
+For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization \citep{StephensWeisbach1998}.
 Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues).
-The part of their sample where net equity issues are positive is defined as the "buyback sample".
+The part of their sample where net equity issues are positive is defined as the ``buyback sample''.
 But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations.
-Moreover the idea of pooling buybacks and equity issues in "net issues" assumes that the decision to issue equity is simply the mirror of buying back shares.
-However, issuing stock to new investors is not the same as buying back stock from "old" selling investors.
-In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only takes advantage of selling shareholders who leave the firm.
+Moreover the idea of pooling buybacks and equity issues in ``net issues'' assumes that the decision to issue equity is simply the mirror of buying back shares.
+However, issuing stock to new investors is not the same as buying back stock from ``old'' selling investors.
+In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only affects selling shareholders who leave the firm.
 In this paper we re-examine the anomaly using the \cite{FamaFrench2015a} model but use announcement dates and separate buyback announcements and equity announcements.
 
-Using buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, we confirm the Fama and French (2015b) conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
+Using buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, we confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
 Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio.
-The interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive.
+An interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive.
 We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries.
@@
 Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information.
-If the buyback signals a change in risk (\cite{GrullonMichaely2004}) hedging market risk may be complicated.
+If the buyback signals a change in risk \citep{GrullonMichaely2004} hedging market risk may be complicated.
 That is why in this paper we also simulate hedged investment strategies where we estimate risk before forming the portfolios.
-We show that an investor who followed this strategy starting in \Sexpr{firstyear} would by \Sexpr{lastyear} have realized cumulative excess returns between \Sexpr{round(tail(months1,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$, depending on the length of the holding period.
+We show that an investor who followed such a strategy starting in \Sexpr{firstyear} would by \Sexpr{lastyear} have realized cumulative excess returns between \Sexpr{round(tail(months1,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$, depending on the length of the holding period.
 
@@
 (idiosyncratic) volatility is negatively related to expected returns.
-For example, \cite{Ang2006} find negative alphas for high volatility and high idiosyncratic volatility stocks, using the 3-factor \cite{FamaFrench1993} model.
+For example, \cite{Ang2006} find {\it negative} alphas for high volatility and high idiosyncratic volatility stocks, using the 3-factor \cite{FamaFrench1993} model.
 Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms.
-However, in our buyback sample we find a significant positive relation between excess returns, using the Fama-French 5-factor model as a benchmark.
+However, in our buyback sample we find a significant {\it positive} relation between excess returns, using the Fama-French 5-factor model as a benchmark.
 This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market.
@@
 Turning to total volatility we also find that buyback authorizations of high risk stocks are followed by larger excess returns.
-This is consistent with the {\it option hypothesis}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks (\cite{IkenberryVermaelen1996}).
+This is consistent with the {\it option hypothesis}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks \citep{IkenberryVermaelen1996}.
 If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.
 
-Combining idiosyncratic risk and total volatility with the Peyer and Vermaelen (2009) Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns.
+Combining idiosyncratic risk and total volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns.
 In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
@@
 For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request.
-An interactive online tool to explore data variations and robustness analyses of all results in this paper is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both.
+An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both.
 Finally, we removed the following events: no CRSP returns available (\Sexpr{cleanup_bb$get_crsp$NOPERMNO_remove + cleanup_bb$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_bb$compustat$NO_GVKEY_remove + cleanup_bb$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).
@@
 The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms.
-The average percent of share authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).
+The average percent of shares authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).
 
@@
 We again removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(ISSUERS_DATA$finance_Size_used)} events).
-Our final sample contains \Sexpr{length(cusip_iss)} issuers events made by \Sexpr{length(unique(cusip_iss))} firms.
+Our final sample contains \Sexpr{length(cusip_iss)} events made by \Sexpr{length(unique(cusip_iss))} firms.
 The average percent of shares issued was \Sexpr{datasummaryISS["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryISS["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{datasummaryISS["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryISS["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryISS["BE/ME", "Mean"]} (median of \Sexpr{datasummaryISS["BE/ME", "Median"]}).
@@
 In all the tables we also calculate cumulative excess returns in the 6 months prior to the buyback.
-Consistent with past research (e.g., \cite{PeyerVermaelen2009}) buyback authorization announcements are preceded by significant negative excess returns of around \Sexpr{round(IRATS_table_all_bb[reported_times[1],1],0)}$\%$.
-This is consistent with the hypothesis that the typical repurchase announcement is triggered by at least the perception of insiders that the stock is undervalued.
+Consistent with past research [see e.g., \citep{PeyerVermaelen2009}] buyback authorization announcements are preceded by significant negative excess returns of around \Sexpr{round(IRATS_table_all_bb[reported_times[1],1],0)}$\%$.
+This is consistent with the hypothesis that the typical repurchase announcement is triggered by a stock price decline that insiders may feel is not justified given their long-term prospects about the company.
 
@@
 However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months.
-This shows that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure.
+This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure.
 Unlike buybacks, equity issues are firm commitments and announced and completed at the same point in time.
-Using actual shares issued (the measure used by Fama-French (1995b)) and equity announcements (our measure) should therefore produce similar results.
+Using actual shares issued, the measure used by \cite{FamaFrench2015b}, and equity announcements (our measure) should therefore produce similar results.
 Buyback authorization announcements on the other hand are not firm commitments and are often executed over a long period after the announcement.
@@
 Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(IRATS_table_all_iss[reported_times[1],1],0)}$\%$ in the 6 months prior to the equity issue.
-However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that these firms experienced a substantial increase in growth opportunities and issued equity to finance them.
+However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.
+
 One critique of the \cite{ibbotson1975} RATS method is that the result may be time-specific.
 Indeed as every event is equally weighted the cumulative average abnormal returns are dominated by periods when there are a large number of events.
-So we also use the Calendar Time method where in each calendar month we form an equally-weighted portfolio of all firms that announce a buyback (or an equity issue) in the previous $t$~months.
+So we also use the Calendar Time method where in each calendar month we form an equally-weighted portfolio of all firms that announced a buyback (or an equity issue) in the previous $t$~months.
 We then run a time series regression of the portfolio returns against the factors.
 The intercept of the regression is the average monthly excess return in the $t$~months after the event.
-
-The results in Panel~B of Tables \ref{tbl:priorBuybacks} and  \ref{tbl:priorIssuers} are similar to Panel~A of the same tables.
+The results are shown in Panel~B of Tables \ref{tbl:priorBuybacks} and  \ref{tbl:priorIssuers} and are similar to Panel~A of the same tables.
 Abnormal returns after buybacks are smaller when the five-factor model is used but remain statistically significant over all horizons.
@@
 The largest monthly excess return (\Sexpr{CAL_table_all_bb["+1","CAL 5F"]}$\%$) is earned by the portfolio that holds buyback stocks for one month  (not reported in Table \ref{tbl:priorBuybacks})  and the smallest excess return (\Sexpr{CAL_table_all_bb["+48","CAL 5F"]}$\%$) is earned by the portfolio that picks buybacks announced during the previous 48 months.
-This clearly shows that forming portfolios after buybacks are completed (as is done by measuring net issues in \cite{FamaFrench2015b}) is introducing a downward bias as many repurchase programs are completed several months (sometimes years) after the buyback announcement.
+This clearly shows that forming portfolios after buybacks are completed, as is done by measuring net issues in \cite{FamaFrench2015b}, is introducing a downward bias as many repurchase programs are completed several months (sometimes years) after the buyback announcement.
 Waiting until the buyback is completed means missing the largest excess returns earned shortly after the buyback authorization.
@@
 
-Of the \Sexpr{length(SEO_exit_days)} such events, \Sexpr{sum(abs(SEO_exit_days) < 1*365)} happen within 1 year from the buyback announcement, \Sexpr{sum(abs(SEO_exit_days) < 2*365)} happen within 2 years and \Sexpr{sum(abs(SEO_exit_days) < 3*365)} happen within 3 years.
+Of the \Sexpr{length(SEO_exit_days)} such events, \Sexpr{sum(abs(SEO_exit_days) < 1*365)} SEOs happen within 1 year from the buyback announcement, \Sexpr{sum(abs(SEO_exit_days) < 2*365)} happen within 2 years and \Sexpr{sum(abs(SEO_exit_days) < 3*365)} happen within 3 years.
 Note that this grouping of the events is done with hindsight: it is not possible to know at the time of the buyback announcement whether there will be a subsequent SEO or not.
@@
 The figure shows a strategy with hindsight where, starting in \Sexpr{firstyear}, we invest in an equally weighted portfolio of only firms that announced a buyback and subsequently issued equity within the 48 months after the buyback announcement.
-The dashed line shows the cumulative excess return if we sold the stock whenever the firm issued shares within 48 months (the exit strategy).
-The solid line shows the cumulative excess returns if we sold 48 months after the buyback announcement (the no exit case).
-The investor who had followed the exit strategy would have earned (after 30 years) a cumulative excess return of \Sexpr{round(tail(100*cumsum(BB_ISS_Exit_Hedged),1),1)}$\%$, significantly larger than the \Sexpr{round(tail(100*cumsum(BB_ISS_NoExit_Hedged),1),1)}$\%$ of a buy hold for 48 months strategy.
+The dashed line shows the cumulative excess return if we sold the stock whenever the firm issued shares within 48 months (the ``exit strategy'').
+The solid line shows the cumulative excess returns if we only sold 48 months after the buyback announcement (the ``no exit strategy'').
+The investor who had followed the exit strategy would have earned (after 30 years) a cumulative excess return of \Sexpr{round(tail(100*cumsum(BB_ISS_Exit_Hedged),1),1)}$\%$, compared to the \Sexpr{round(tail(100*cumsum(BB_ISS_NoExit_Hedged),1),1)}$\%$ of a buy and hold for 48 months strategy.
 Note, however, that because very few firms that buy back stock issue equity within 48 months,  a strategy ``without hindsight'' where one bought all companies after a buyback and sold only those after a subsequent equity issue would not substantially increase excess returns.
 
-Table~\ref{tbl:BBISSexitAfter} shows the long run excess returns after the announcement of an equity issue for two samples.
+%Table~\ref{tbl:BBISSexitAfter} shows the long run excess returns after the announcement of an equity issue for two samples.
 The first sample (After a Buyback) shows the excess returns for issues for which in the previous 48 months the firm announced a buyback.
 The second sample (No Prior Buyback) shows the excess returns for all other issue announcements.
-The fact that excess returns are not significantly different from zero for the post-buyback issuers agrees with the intuition of Figure~\ref{fig:BBISSexit}: exiting when there is a subsequent equity issue is the right thing to do for the long-term buyback investor.
+The fact that excess returns are not significantly different from zero for the post-buyback issuers agrees with the intuition of Figure~\ref{fig:BBISSexit}: exiting when there is a subsequent equity issue is a better strategy for the long-term buyback investor.
 
@@
 Table~\ref{tbl:PastFindingsTimeBB} shows excess returns, using both the IRATS and Calendar Time method for different time periods.
-We consider time periods, which overlap to some extent with past research (Ikenberry, Lakonishok, and Vermaelen 1995, Peyer and Vermaelen 2009, Manconi, Peyer, and Vermaelen 2015 and Fu and Huang 2015): 1985-1990; 1991-2000; 2001-2014 and 2008-2014.
-The last period was chosen to incorporate the financial crisis and to test whether indeed markets have become more efficient in recent years, or whether managers have been discouraged from market timing by the obvious mistakes that were made by buying back shares before a major financial crisis.
+We consider time periods, which overlap to some extent with past research [\cite{IkenberryLakonishokVermaelen1995}; \cite{PeyerVermaelen2009}; \cite{ManconiPeyerVermaelen2015}; and \cite{FuHuang2015}]: 1985-1990; 1991-2000; 2001-2014 and 2008-2014.
+The last period was chosen to incorporate the financial crisis and to test whether indeed markets have become more efficient in recent years, or whether managers have for example been discouraged from market timing by the obvious mistakes that were made by buying back shares before a major financial crisis.
 
 Table~\ref{tbl:PastFindingsTimeBB} shows that, regardless of the time period chosen or the method to calculate excess returns, the buyback anomaly remains economically and statistically significant and there is no clear time trend in the data that suggests that markets have become more efficient over time.
-For example, although the 2001-2014 period shows smaller timing ability than the 1990-2000 period, excess returns in the 2008-2014 period are as large as in 1991-2000 period: approximately \Sexpr{BBtable_time["+48",22]}$\%$  after 4 years using IRATS or \Sexpr{BBtable_time_cal["+48",22]}$\%$ per month (\Sexpr{48*BBtable_time_cal["+48",22]}$\%$ after 4 years) when we use the Calendar Time method.
+For example, although the 2001-2014 period shows smaller timing ability than the 1990-2000 period, excess returns in the 2008-2014 period are as large as in the 1991-2000 period: approximately \Sexpr{BBtable_time["+48",22]}$\%$  after 4 years using IRATS or \Sexpr{BBtable_time_cal["+48",22]}$\%$ per month (\Sexpr{48*BBtable_time_cal["+48",22]}$\%$ after 4 years) when we use the Calendar Time method.
 There is one exception to the consistency between the IRATS and the Calendar Time results: in the period of 1991-2000, the IRATS method generates excess returns after 48 months of \Sexpr{BBtable_time["+48",10]}$\%$ (t=\Sexpr{BBtable_time["+48",11]}) but the Calendar Time method produces statistically insignificant excess returns of \Sexpr{BBtable_time_cal["+48",10]}$\%$ per month.
@@
 Regardless of the method to compute excess returns, the U-index is an excellent predictor: except for the very short 1985-1990 period, buybacks announced by high U-index firms are followed by significantly larger returns than buybacks announced by low U-index firms.
-There is also no evidence that the U-index is losing its predictive power over time: for example, in the 2001-2014 period the difference between high U-index and low index firms (after 48 months, IRATS) was \Sexpr{BBtable_undertime["+48",31]-BBtable_undertime["+48",34]}$\%$, while in the most recent 2008-2014 period high U-index firms had \Sexpr{BBtable_undertime["+48",43]-BBtable_undertime["+48",46]}$\%$ larger abnormal returns than low U-index firms.
+There is also no evidence that the U-index is losing its predictive power over time: for example, in the 2001-2014 period the difference between high and low U-index firms (after 48 months, IRATS) was \Sexpr{BBtable_undertime["+48",31]-BBtable_undertime["+48",34]}$\%$, while in the most recent 2008-2014 period high U-index firms had \Sexpr{BBtable_undertime["+48",43]-BBtable_undertime["+48",46]}$\%$ larger abnormal returns than low U-index firms.
 
@@
 An investor who wants to exploit the anomaly, however, may want to hedge market (and other) risk and would need to estimate betas using past data.
-If the buyback signals a change in risk (\cite{GrullonMichaely2004}) it is not obvious that such a hedged strategy would work.
+If the buyback signals a change in risk \citep{GrullonMichaely2004} it is not obvious that such a hedged strategy would work, which may make a buyback strategy impractical for some funds.
 
@@
 The strategy uses past data to estimate the factor betas and measures the abnormal returns of buyback portfolios over different investment horizons.
-While this is not an accurate measure of the returns of a buyback fund - as we do not consider transaction costs, turnover issues, or other operational issues (see for example \cite{MitchellPulvino2001}) - it provides us with an estimate of what would have happened to an investor who starts investing in \Sexpr{firstyear} in an equally weighted portfolio of buyback stocks and holds them over various horizons.
+While this is not an accurate measure of the returns of a buyback fund - as we do not consider transaction costs, turnover issues, or other operational issues as discussed for example in \cite{MitchellPulvino2001} - it provides us with an estimate of what would have happened to an investor who starts investing in \Sexpr{firstyear} in an equally weighted portfolio of buyback stocks and holds them over various horizons.
 
@@
 Each month (when we re-balance the portfolio) we also use the previous \Sexpr{hedge_months}  monthly returns of this time series    to calculate the (portfolio level) time series betas of all five factors.
-This allows an investor to determine the betas for the factor risks using data available at the time of portfolio formation.
-
-We report the returns and excess returns of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns.
+This allows an investor to determine the betas for the factor risks using data available at the time of portfolio formation, and then hedge these factor risks (including the market) using these betas to get a ``hedged'' portfolio.
+
+Despite using pre-portfolio formation data to estimate the betas, unlike both the IRATs and Calendar Time methods that use hindsight to estimate risk, the hedged portfolio indeed has very low betas with the five factors.
+For example for the $N =12$ months holding period, the betas for the five factors Market, SMB, HML, RMW, and CMA are respectively \Sexpr{round(expost_betas[2,1],3)}, \Sexpr{round(expost_betas[3,1],3)}, \Sexpr{round(expost_betas[4,1],3)}, \Sexpr{round(expost_betas[5,1],3)} and \Sexpr{round(expost_betas[6,1],3)}.
+The corresponding betas for the ``unhedged'' strategy are \Sexpr{round(expost_betas_unhedged[2,1],3)}, \Sexpr{round(expost_betas_unhedged[3,1],3)}, \Sexpr{round(expost_betas_unhedged[4,1],3)}, \Sexpr{round(expost_betas_unhedged[5,1],3)} and \Sexpr{round(expost_betas_unhedged[6,1],3)}.
+This indicates that the returns of the hedged strategy are indeed close to ``excess'' returns, i.e.
+returns that have basically eliminated all factors risk.
+This is also consistent with the hypothesis that the buyback announcement itself does not materially change the risk of the repurchasing firms (in the short term).
+
+We report the returns (unhedged strategy) and excess returns (hedged strategy) of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns.
 Specifically, at the end of \Sexpr{lastyear} the cumulative excess returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$.
@@
 Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.
-The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}.
+The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the excess returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}.
 In only one year (\Sexpr{rownames(tmp)[which.min(tmp[,13])]}) the strategy generates an abnormal loss larger than \Sexpr{round(abs(sort(tmp[,13])[2]),1)}$\%$.
-
-Despite using pre-portfolio formation data to estimate the betas, unlike both the IRATs and Calendar Time methods that use hindsight to estimate risk, the hedged portfolio has very low betas with the five factors.
-For example for the $N =12$ months holding period, the betas for the five factors Market, SMB, HML, RMW, and CMA are respectively \Sexpr{round(expost_betas[2,1],3)}, \Sexpr{round(expost_betas[3,1],3)}, \Sexpr{round(expost_betas[4,1],3)}, \Sexpr{round(expost_betas[5,1],3)} and \Sexpr{round(expost_betas[6,1],3)}.
-The corresponding betas for the ``unhedged'' strategy are \Sexpr{round(expost_betas_unhedged[2,1],3)}, \Sexpr{round(expost_betas_unhedged[3,1],3)}, \Sexpr{round(expost_betas_unhedged[4,1],3)}, \Sexpr{round(expost_betas_unhedged[5,1],3)} and \Sexpr{round(expost_betas_unhedged[6,1],3)}.
-This also indicates that the returns shown in Figure~\ref{fig:ReturnsBB} and Table~\ref{tbl:allhedgedBB} are close to ``excess'' returns, i.e.
-returns that have basically eliminated all factors risk.
-This is also consistent with the hypothesis that the buyback announcement itself does not materially change the risk of the repurchasing firms (in the short term).
 
@@
 
-There exists a large literature on volatility and stock returns.\footnote{For the most recent overview of the literature and potential hypotheses, see \cite{LiRodneyGarcia2016}.} One of the most puzzling findings is the fact that total volatility and idiosyncratic volatility are negatively correlated with future abnormal returns, when expected returns are calculated using the 3 factor \cite{FamaFrench1993} model  (see e.g.
-\cite{Ang2006} (Table VII)).
+There exists a large literature on volatility and stock returns.\footnote{For the most recent overview of the literature and potential hypotheses, see \cite{LiRodneyGarcia2016}.} One of the most puzzling findings is the fact that total volatility and idiosyncratic volatility are negatively correlated with future abnormal returns, when expected returns are calculated using the 3-factor \cite{FamaFrench1993} model  [see e.g., \cite{Ang2006} (Table VII)].
 This volatility anomaly also survives after using the \cite{FamaFrench2015a} 5-factor model, at least for small firms.
@@
 
-The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \cite{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns.
+The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \citep{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \citep{Ang2006} who find a negative relation between IVOL and expected returns.
 However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks.
@@
 The announcement of a buyback program is not a firm commitment, but an option to buy back stock.
-Ikenberry and Vermaelen (1996) model this flexibility as an exchange option in which the market price of the stock is exchanged for the true value of the stock.
+\cite{IkenberryVermaelen1996} model this flexibility as an exchange option in which the market price of the stock is exchanged for the true value of the stock.
 They predict that, as with all options, the value increases with the volatility.
@@
 Overall we see that although high U-index firms tend to have high idiosyncratic risk and high volatility, while high idiosyncratic risk firms tend to also have high volatility, the overlap is not very high.
-For example from Table~\ref{tbl:underidioallBB} we learn that  only \Sexpr{round(Under_IdioBB["High Vol.","H Idiosync."],1)}$\%$ of the high volatility stocks that are classified as having either high or low idiosyncratic risk - note that we only consider the  \Sexpr{round(100*quantile_R2,2)}$\%$ tails - have high idiosyncratic risk.
+For example from Table~\ref{tbl:underidioallBB} we see that  only \Sexpr{round(Under_IdioBB["High Vol.","H Idiosync."],1)}$\%$ of the high volatility stocks that are classified as having either high or low idiosyncratic risk - note that we only consider the  \Sexpr{round(100*quantile_R2,2)}$\%$ tails - have high idiosyncratic risk.
 From Table~\ref{tbl:underidioallBBcor} we infer that the correlation between idiosyncratic risk and volatility is only \Sexpr{round(Under_IdioBB_cor["Volatility Score","Idiosyncratic Score"]*100,1)}$\%$.
-A natural question is therefore whether one can further enhance the \cite{PeyerVermaelen2009} U-index by incorporating information about the firms pre-announce idiosyncratic risk and volatility.
+A natural question is therefore whether one can further enhance the \cite{PeyerVermaelen2009} U-index by incorporating information about the firms' pre-announce idiosyncratic risk and volatility.
 We consider one such combination where we simply take an equal-weighted combination of the 4 criteria into one ``Enhanced Undervaluation Index'' (EU-index).
@@
 Table~\ref{tbl:EUrelations} shows how the EU-index relates to a number of firm characteristics.
-Firm leverage, based on data the year before announcement, is defined as the ratio $debt/(debt+equity)$\footnote{We use the definitions from \url{http://www.ivo-welch.info/professional/leverage.placebo/}{Ivo Welch's website} following  \url{http://www.ivo-welch.info/professional/leverage.placebo/r-sourcecode/mksane.R}.
+Firm leverage, based on data the year before announcement, is defined as the ratio $debt/(debt+equity)$.\footnote{We use the definitions from \url{http://www.ivo-welch.info/professional/leverage.placebo/}{Ivo Welch's website} following  \url{http://www.ivo-welch.info/professional/leverage.placebo/r-sourcecode/mksane.R}.
 Debt is the sum of the Compustat variables $dlc+ dltt$, where $dlc$ is ``Debt in Current Liabilities'' and $dltt$ is ``Long Term Debt - Total''.
@@
 We use the most recent data pre-announce, and make the winsorization and other adjustments as in the websites above.
-Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.}.
-``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement.
+Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.} ``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement.
 ``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement.
-Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available\footnote{As this SDC data was not available for many events, we did not consider the in the U-index calculation} (this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.
+Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available\footnote{As this SDC data was not available for many events, we did not consider the in the U-index calculation.} (this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.
 
@@
 This could of course be related to the fact that risky firms should have more cash holdings.
-They also tend to follow up with equity offerings after the buyback which suggests that they are more likely to be in the ``market timing'' business.
+They also tend to follow up more often with equity offerings after the buyback which suggests that they are more likely to be in the ``market timing'' business.
 The table also shows a strong negative relation between market-to-book ratios and market capitalization and the EU index, which is not surprising as these are components of the index.
-It should be noted that the EU 6 portfolio is composed of very small stocks with an average market capitalization of \$\Sexpr{round(EU_relations["Market Cap.","EU6"],1)} million.
+It should be noted that the EU6 portfolio (consisting of all firms with EU index equal to 6) is composed of very small stocks with an average market capitalization of \$\Sexpr{round(EU_relations["Market Cap.","EU6"],1)} million.
 The average market capitalization of portfolios with long term (after 48 months) monthly excess return of larger than 0.3$\%$ (i.e.
@@
 
-The bottom line is that combining volatility, idiosyncratic risk and the U-index in one EU- index generates a more selective predictor of excess returns than each of the indicators separately.
+The bottom line is that combining volatility, idiosyncratic risk and the U-index in one EU-index generates a more selective predictor of excess returns than each of the indicators separately.
 Indeed, high U-index stocks, stocks with high idiosyncratic risk, and high volatile stocks generate cumulative excess returns of respectively \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR5F"]}$\%$ (Table~\ref{tbl:priorBuybacks}), \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$ (Table~\ref{tbl:IdiosyncraticunderBB}) and \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$ (Table~\ref{tbl:VOLunderBB}).
@@
 Tables \ref{tbl:EUTimeUnderBB} (IRATS) and \ref{tbl:EUTimeUnderBBcal} (Calendar Time method), like Table~\ref{tbl:PastFindingsTimeUnderBB} for the U-index, show the relative performance of high and low EU-index repurchases.
-In order to have roughly similar number of under/overvalued firms as when we use the U-index, we define low EU-index firms to those for which the EU-index is 0-1, and high for which it is 5-6 (the index takes values from 0 to 6).
+In order to have roughly similar number of under/overvalued firms as when we use the U-index, we define low EU-index firms to be those for which the EU-index is 0-1, and high for which it is 5-6 (the index takes values from 0 to 6).
 With this definition we have \Sexpr{sum(low_EU_bb)} low EU-index and \Sexpr{sum(high_EU_bb)}  high EU-index firms in our sample (in comparison with \Sexpr{sum(company_subset_overvalued_bb)} low U-index and \Sexpr{sum(company_subset_undervalued_bb)} high U-index ones).
@@
 
-The buyback anomaly first reported by Ikenberry, Lakonishok and Vermaelen (1995) is still alive and robust.
+The buyback anomaly first reported by \cite{IkenberryLakonishokVermaelen1995} is still alive and robust.
 Long term excess returns are large, highly statistically significant and robust even when we replace the Fama-French three-factor model with the Fama-French five-factor model.
-We believe that the difference with the conclusions of \cite{FamaFrench2015b} is a result of the fact that we do not pool buybacks and equity issues in a ``net issuance'' anomaly.
+We believe that the difference with the conclusions of \cite{FamaFrench2015b} is a result of the fact that we do not pool buybacks and equity issues in a ``net issuance'' anomaly, which unfortunately has become the standard in the anomaly literature.
 A buyback is not simply the inverse of an equity issue, especially in a world with asymmetric information.
 Managers who buy back undervalued stock from selling investors benefit their long-term shareholders at the expense of selling shareholders who are ``leaving'' the company.
-Issuing overvalued stock to new investors is not exactly enhancing good investor relations.
-Hence it is not surprising to find that the equity issue anomaly does not survive after appropriately adjusting for risk.
+Issuing overvalued stock hurts new investors and therefore may not be in the interest of long-term shareholder value.
 Moreover buyback authorizations are options, not firm commitments such as equity issues.
@@
 Investing in very high EU index firms generates Fama-French five-factor adjusted returns of \Sexpr{round(EU_CALtable_bb["+48",19],2)}$\%$ per month during the 48 months after the buyback announcement.
-These are also firms that mention in their press releases that they are buying back stock because they are undervalued.
+These are also firms that are more likely to mention in their press releases that they are buying back stock because they are undervalued.
 They are more likely to miss earnings forecasts relative to the other buyback firms and therefore falling out of favor with analysts.
 However investing in high EU index firms to some extent implies investing in small caps and micro-caps, which may explain partially why the anomaly persists as these firms may not satisfy, for example, liquidity risk constraints of many funds.
-
-\newpage
-
-\bibliographystyle{jfe}
-\bibliography{Bibliography}
 
@@
 We include a version of the abnormal returns for the full sample and one for both companies with a high U-index and a low U-index.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the Fama French (1993) three-factor model and the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench1993} three-factor model and the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regressions are run each event month~$j$:\\vspace{-1em}
@@
   caption= "The table presents the abnormal returns for firms after issue announcements from the announcement date until $t$ months after the announcement.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the Fama French (1993) three-factor model and the Fama French (2015) five-factor model for the sample of firms that announced equity issuance plus various subsamples.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench1993} three-factor model and the Fama French (2015) five-factor model for the sample of firms that announced equity issuance plus various subsamples.
 The following regressions are run each event month~$j$:
@@
   caption="The table presents the long-run abnormal returns for firms repurchase announcements for events with and without a subsequent SEO announcement.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
 
+if (0){
   printLatexTable(ISS_for_BB_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
@@
                   caption = "The table presents the long-run abnormal returns (CAR) for firms after issue announcements for events with and without a prior buyback announcement within 48 months.
-We report the monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
     caption="The table presents the long-run abnormal returns for firms after issue announcements with and without a subsequent buyback announcement on the full sample for different periods in time.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
   caption="The table presents the long-run abnormal returns for firms after repurchase announcements for different time periods.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
   caption=paste("The table presents the long-run abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample.
-We report the monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
 Regardless of event study method and time horizon, the U-index works only for idiosyncratic companies.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
   caption="IRATS five factor cumulative abnormal returns after open market repurchase announcements for each Enhanced Undervaluation Index value from 0 to 6.
- We calculate the EU-index simply as the sum of three numbers:  high Peyer and Vermaelen (2009) U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.
+ We calculate the EU-index simply as the sum of three numbers:  high \\cite{PeyerVermaelen2009} U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.
 Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores.
-For each EU-index value, we report the monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+For each EU-index value, we report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
   caption="IRATS five factor cumulative abnormal returns after open market repurchase announcements for each Enhanced Undervaluation Index value from 0 to 6.
- We calculate the EU-index simply as the sum of three numbers:  high Peyer and Vermaelen (2009) U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.
+ We calculate the EU-index simply as the sum of three numbers:  high \\cite{PeyerVermaelen2009} U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.
 Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores.
@@
 IRATS five factor cumulative abnormal returns after open market repurchase announcements for each EU-index value from 0 to 6.
-We calculate the EU-index simply as the sum of three numbers:  high Peyer and Vermaelen (2009) U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.
+We calculate the EU-index simply as the sum of three numbers:  high \\cite{PeyerVermaelen2009} U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.
 Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores.
-For each EU-index value, we report the monthly cumulative average abnormal returns (CAR) in percent using Ibbotson's (1975) returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+For each EU-index value, we report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
 We define low EU-index firms those for which the EU-index is 0-1, and high for which it is 5-6 (note that the index takes values from 0 to 6).
-We calculate the EU-index simply as the sum of three numbers:  high Peyer and Vermaelen (2009) U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.
+We calculate the EU-index simply as the sum of three numbers:  high \\cite{PeyerVermaelen2009} U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.
 Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores.
@@
 names(market_index) <- str_sub(names(market_index), start = 1, end = 4)
-df.bar <- barplot(number_eventsBB,col=c("grey"),main = "Panel A: Buyback Announcements", ylab = "Announcements", xlab = "Years",las=2,space=0.5, cex.names=0.6)
+df.bar <- barplot(number_eventsBB,col=c("grey"),main = "Panel A: Buyback Announcements", ylab = "Announcements", xlab = "Years",las=2,space=0.5, cex.names=0.9)
 par(new = TRUE)
@@
 names(market_index) <- str_sub(names(market_index), start = 1, end = 4)
-df.bar <- barplot(number_eventsISS,col=c("grey"),main = "Panel B: Equity SEO Announcements", ylab = "Announcements", xlab = "Years",las=2,space=0.5, cex.names=0.6)
+df.bar <- barplot(number_eventsISS,col=c("grey"),main = "Panel B: Equity SEO Announcements", ylab = "Announcements", xlab = "Years",las=2,space=0.5, cex.names=0.9)
 par(new = TRUE)
@@
 tmp = structure(as.numeric(tmp), .Names = names(tmp))
-barplot(tmp,main = "", ylab = "Number of Events", xlab = "",las=2,space=0.5, cex.names=0.8)
+barplot(tmp,main = "", ylab = "Number of Events", xlab = "",las=2,space=0.5, cex.names=1)
 #tmp = table(valuation_index_iss)
 #tmp = structure(as.numeric(tmp), .Names = names(tmp))
-#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=0.8)
+#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=1)
 rm("tmp")
@@
 plot(IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="A. Buybacks - All", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
 axis(2,cex.axis=1.1)
@@
 plot(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="C. Buybacks - high/low U-index", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
 axis(2,cex.axis=1.1)
@@
 plot(IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="B. SEOs - All", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
 axis(2,cex.axis=1.1)
@@
   plot(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="SEOs - Under/Over-valuation", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
   axis(2,cex.axis=1.1)
@@
 names(market_index) <- str_sub(names(market_index), start = 1, end = 4)
-df.bar <- barplot(BB_with_ISS_later_total,col=c("grey"),main = "", ylab = "Percent", xlab = "Years",las=2,space=0.5, cex.names=0.8)
+df.bar <- barplot(BB_with_ISS_later_total,col=c("grey"),main = "", ylab = "Percent", xlab = "Years",las=2,space=0.5, cex.names=1)
 for (iter in 1:floor(max(BB_with_ISS_later_total)/5))
@@
 if (0){
-  df.bar <- barplot(ISS_with_BB_later_total,col=c("grey"),main = "Issues with Follow-up Buyback", ylab = "Percent", xlab = "Years",las=2,space=0.5, cex.names=0.8)
+  df.bar <- barplot(ISS_with_BB_later_total,col=c("grey"),main = "Issues with Follow-up Buyback", ylab = "Percent", xlab = "Years",las=2,space=0.5, cex.names=1)
   for (iter in 1:floor(max(ISS_with_BB_later_total)/5))
@@
 plot(Exit_on_SEO_Abn_table[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel A: Buybacks with SEO IRATS CAR", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
 axis(2,cex.axis=1.1)
@@
   plot(Exit_on_SEO_Abn_table_cal[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: Buybacks with SEO: Calendar Method", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
   axis(2,cex.axis=1.1)
@@
 plot(cumsum(100*pnl_NoExit_Hedged),type="l",ylab="CAR", xlab = "",main = "Panel B: Strategy Returns", axes = FALSE, ylim=c(min(c(100*cumsum(pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged))), max(c(cumsum(100*pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged)))), cex.lab=1.1)
-axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
+axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
 axis(2,cex.axis=1.1)
@@
   plot(Exit_on_BB_Abn_table[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: SEO with Buyback IRATS CAR", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
   axis(2,cex.axis=1.1)
@@
     plot(Exit_on_BB_Abn_table_cal[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="SEO with Buyback: Calendar", lwd=1.4)
-    axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+    axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
     axis(2,cex.axis=1.1)
@@
   plot(cumsum(100*pnl_NoExit_Hedged),type="l",ylab="CAR", xlab = "",main = "Strategy Returns",axes = FALSE, ylim=c(min(c(100*cumsum(pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged))), max(c(cumsum(100*pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
+  axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
   axis(2,cex.axis=1.1)
@@
 plot(all_ret_values$market, axes=FALSE, ylab="Cumulative Returns", xlab = "Time",ylim=c(min(as.vector(all_ret_values)), max(as.vector(all_ret_values))), main = "Panel A: Absolute Returns", cex.lab=1.1, lty = "dotdash", type = "l", lwd=2)
-axis(1,at=seq(1,nrow(all_ret_values),length.out=10),labels=str_sub(rownames(all_ret_values)[seq(1,nrow(all_ret_values),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
+axis(1,at=seq(1,nrow(all_ret_values),length.out=10),labels=str_sub(rownames(all_ret_values)[seq(1,nrow(all_ret_values),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
 axis(2,cex.axis=1.1)
@@
 plot(all_ret_values$market, axes=FALSE, ylab="CAR", xlab = "Time",ylim=c(min(as.vector(all_ret_values)), max(as.vector(all_ret_values))), main = "Panel B: Excess Returns", cex.lab=1.1, lty = "dotdash", type = "l", lwd=2)
-axis(1,at=seq(1,nrow(all_ret_values),length.out=10),labels=str_sub(rownames(all_ret_values)[seq(1,nrow(all_ret_values),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
+axis(1,at=seq(1,nrow(all_ret_values),length.out=10),labels=str_sub(rownames(all_ret_values)[seq(1,nrow(all_ret_values),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
 axis(2,cex.axis=1.1)
@@
 <<  fig.width=10, fig.height=5, echo=F >>=
-df.bar <- barplot(industry_tableBB,col=c("grey"),main = "", ylab = "Buybacks", xlab = "",las=2,space=0.9, cex.names=0.6)
+df.bar <- barplot(industry_tableBB,col=c("grey"),main = "", ylab = "Buybacks", xlab = "",las=2,space=0.9, cex.names=0.62)
 for (iter in 1:floor(max(industry_tableBB)/100))
@@
 %<<  fig.width=10, fig.height=5, out.width='\\textwidth', echo=F >>=
-%df.bar <- barplot(industry_tableISS,col=c("grey"),main = "", ylab = "Issues", xlab = "",las=2,space=0.9, cex.names=0.6)
+%df.bar <- barplot(industry_tableISS,col=c("grey"),main = "", ylab = "Issues", xlab = "",las=2,space=0.9, cex.names=1)
 %for (iter in 1:floor(max(industry_tableISS)/100))
@@
   lines(R2_thresholds_down_plot, col="black", lwd=2,lty="dotted")
-  axis(1,at=seq(1,length(Market_Monthly_index),length.out=20),labels=str_sub(names(Market_Monthly_index)[seq(1,length(Market_Monthly_index),length.out=20)], start=1,end=4),cex.axis=0.8,las=3)
+  axis(1,at=seq(1,length(Market_Monthly_index),length.out=20),labels=str_sub(names(Market_Monthly_index)[seq(1,length(Market_Monthly_index),length.out=20)], start=1,end=4),cex.axis=1,las=3)
   axis(2,cex.axis=1.1)
@@
               max(c(cumsum(100*High_Idiosyncr_BB_Hedged),cumsum(100*Low_Idiosyncr_BB_Hedged),cumsum(100*High_Idiosyncr_BB_Hedged48m),cumsum(100*Low_Idiosyncr_BB_Hedged48m)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(High_Idiosyncr_BB_Hedged),length.out=10),labels=str_sub(names(High_Idiosyncr_BB_Hedged)[seq(1,length(High_Idiosyncr_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
+  axis(1,at=seq(1,length(High_Idiosyncr_BB_Hedged),length.out=10),labels=str_sub(names(High_Idiosyncr_BB_Hedged)[seq(1,length(High_Idiosyncr_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
   axis(2,cex.axis=1.1)
@@
                 max(c(cumsum(100*High_Idiosyncr_ISS_Hedged),cumsum(100*Low_Idiosyncr_ISS_Hedged),cumsum(100*High_Idiosyncr_ISS_Hedged48m),cumsum(100*Low_Idiosyncr_ISS_Hedged48m)))), cex.lab=1.1)
-    axis(1,at=seq(1,length(High_Idiosyncr_ISS_Hedged),length.out=10),labels=str_sub(names(High_Idiosyncr_ISS_Hedged)[seq(1,length(High_Idiosyncr_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
+    axis(1,at=seq(1,length(High_Idiosyncr_ISS_Hedged),length.out=10),labels=str_sub(names(High_Idiosyncr_ISS_Hedged)[seq(1,length(High_Idiosyncr_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
     axis(2,cex.axis=1.1)
@@
 plot(R2_IRATStable_underBB_plot[reported_times_plots,"High Idiosync.: U CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel A: High U-index buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
 axis(2,cex.axis=1.1)
@@
 plot(R2_IRATStable_underBB_plot[reported_times_plots,10], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: Low U-index buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
 axis(2,cex.axis=1.1)
@@
 plot(R2_IRATStableBB_plot[reported_times_plots,"High Idiosync.: CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel C: All buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
 axis(2,cex.axis=1.1)
@@
   lines(VOL_thresholds_down_plot, col="black", lwd=2,lty="dotted")
-  axis(1,at=seq(1,length(Market_Monthly_index),length.out=20),labels=str_sub(names(Market_Monthly_index)[seq(1,length(Market_Monthly_index),length.out=20)], start=1,end=4),cex.axis=0.8,las=3)
+  axis(1,at=seq(1,length(Market_Monthly_index),length.out=20),labels=str_sub(names(Market_Monthly_index)[seq(1,length(Market_Monthly_index),length.out=20)], start=1,end=4),cex.axis=1,las=3)
   axis(2,cex.axis=1.1)
@@
               max(c(cumsum(100*High_VOL_BB_Hedged),cumsum(100*Low_VOL_BB_Hedged),cumsum(100*High_VOL_BB_Hedged48m),cumsum(100*Low_VOL_BB_Hedged48m)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(High_VOL_BB_Hedged),length.out=10),labels=str_sub(names(High_VOL_BB_Hedged)[seq(1,length(High_VOL_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
+  axis(1,at=seq(1,length(High_VOL_BB_Hedged),length.out=10),labels=str_sub(names(High_VOL_BB_Hedged)[seq(1,length(High_VOL_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
   axis(2,cex.axis=1.1)
@@
                 max(c(cumsum(100*High_VOL_ISS_Hedged),cumsum(100*Low_VOL_ISS_Hedged),cumsum(100*High_VOL_ISS_Hedged48m),cumsum(100*Low_VOL_ISS_Hedged48m)))), cex.lab=1.1)
-    axis(1,at=seq(1,length(High_VOL_ISS_Hedged),length.out=10),labels=str_sub(names(High_VOL_ISS_Hedged)[seq(1,length(High_VOL_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
+    axis(1,at=seq(1,length(High_VOL_ISS_Hedged),length.out=10),labels=str_sub(names(High_VOL_ISS_Hedged)[seq(1,length(High_VOL_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
     axis(2,cex.axis=1.1)
@@
 plot(VOL_IRATStable_underBB_plot[reported_times_plots,"High Vol: U CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel A: High U-index buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
 axis(2,cex.axis=1.1)
@@
 plot(VOL_IRATStable_underBB_plot[reported_times_plots,10], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: Low U-index buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
 axis(2,cex.axis=1.1)
@@
 plot(VOL_IRATStableBB_plot[reported_times_plots,"High Vol: CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel C: All buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
 axis(2,cex.axis=1.1)
@@
 tmp = structure(as.numeric(tmp), .Names = names(tmp))
-barplot(tmp,main = "", ylab = "Number of Announcements", xlab = "",las=2,space=0.5, cex.names=0.8)
+barplot(tmp,main = "", ylab = "Number of Announcements", xlab = "",las=2,space=0.5, cex.names=1)
 #tmp = table(valuation_index_iss)
 #tmp = structure(as.numeric(tmp), .Names = names(tmp))
-#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=0.8)
+#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=1)
 rm("tmp")
@@
               max(c(cumsum(100*High_EU_BB_Hedged),cumsum(100*Low_EU_BB_Hedged),cumsum(100*High_EU_BB_Hedged48m),cumsum(100*Low_EU_BB_Hedged48m)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(High_EU_BB_Hedged),length.out=10),labels=str_sub(names(High_EU_BB_Hedged)[seq(1,length(High_EU_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
+  axis(1,at=seq(1,length(High_EU_BB_Hedged),length.out=10),labels=str_sub(names(High_EU_BB_Hedged)[seq(1,length(High_EU_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
   axis(2,cex.axis=1.1)
@@
                 max(c(cumsum(100*High_EU_ISS_Hedged),cumsum(100*Low_EU_ISS_Hedged),cumsum(100*High_EU_ISS_Hedged48m),cumsum(100*Low_EU_ISS_Hedged48m)))), cex.lab=1.1)
-    axis(1,at=seq(1,length(High_EU_ISS_Hedged),length.out=10),labels=str_sub(names(High_EU_ISS_Hedged)[seq(1,length(High_EU_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
+    axis(1,at=seq(1,length(High_EU_ISS_Hedged),length.out=10),labels=str_sub(names(High_EU_ISS_Hedged)[seq(1,length(High_EU_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
     axis(2,cex.axis=1.1)
@@
 plot(IRATS_table_all_bb_plot[reported_times_plots,3*6+1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Buybacks - EU index", lwd=2, lty = "solid")
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
+axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
 axis(2,cex.axis=1.1)
@@
 
+\clearpage
+
+\bibliographystyle{jfe}
+\bibliography{Bibliography}
+
 \end{document}

### 2016-04-17 bb_issuers_new.Rnw
new version - first commit. Files ending with "new" plus create_bbissuers_data.R

--- 2016-03-19 bb_issuers.Rnw
@@
 << eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-#rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
 #dev.off();
-#library(knitr); knit2pdf('bb_issuers.Rnw', texi2dvi='texi2dvi'); file.remove(paste("bb_issuers",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
+#library(knitr); knit2pdf('bb_issuers_new.Rnw', texi2dvi='texi2dvi'); file.remove(paste("bb_issuers_new",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
 #dir.create("tmpfiles") # need to comment this if the directory already exists
-
-#load("tmpfiles/bb_issuersALL.Rdata")
-reload_data = 0
-
 # Then to make it into Word: 
-# pandoc -s bb_issuers.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx
-
-generate_all_data = 0 # set this to 1 if the data need to be re-generated from the csv's even though they already exist as .Rdata. 
-# TIME ALIGNMENT IS KEY, SO WE HAVE A SEPARATE PART OF THE CODE FOR THIS
-time_align_all_data = 0
-# Some basic data generation that we need across events
-rerun_buyback_data_code <- 0
-rerun_issuers_data_code <- 0
-# If we generate the cross-events data again
-get_crossevent_data <- 0 # Old stuff, not used for now
-# report_code is only customized to change the "high U-index" and "low U-index" companies, nothing else. Everything else is done in report_data.R
-rerun_buyback_report_code <- 0
-rerun_issuers_report_code <- 0
-# All the RNW data
-generate_rnw_data = 0
-
-source("lib_helpers.R")
-source("latex_code.R")
-source("dataset/indices_and_factors/ff_industries_sic.R")
-source("business_data_clean.R")
+# pandoc -s bb_issuers_new.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx
+
+rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
+
+generate_all_data = 0 # set this to 1 if the data need to be re-generated from scratch
+generate_rnw_data = 0 # set this to 1 to generate the .Rnw data
+
+if (generate_all_data == 1){
+  source("create_bbissuers_data.R")
+}
+if (generate_rnw_data == 1){
+  source("bb_issuers_new.R")
+} else {
+  load("bb_issuers_new.Rdata")
+}
+
+source("../FinanceLibraries/lib_helpers.R")
+source("../FinanceLibraries/latex_code.R")
+source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
 source("Paper_global_parameters.R")
-
-if (generate_rnw_data == 1){
-  source("bb_issuers.R")
-}  else{
-  if (reload_data)
-    load("tmpfiles/bb_issuersALL.Rdata")
-  source("lib_helpers.R") 
-  source("latex_code.R")
-  source("dataset/indices_and_factors/ff_industries_sic.R")
-  source("business_data_clean.R")
-  source("Paper_global_parameters.R")
-}
 
@@
 
+inline_hook <- function (x) {
+  if (is.numeric(x)) {
+    # ifelse does a vectorized comparison
+    # If integer, print without decimal; otherwise print two places
+    res <- ifelse(x == round(x),
                   # use comma for 1000s
-knit_hooks$set(inline = function(x) {
-  if(is.numeric(x)){
-    return(prettyNum(x, big.mark=","))
-  }else{
-    return(x)
-  }
-})
-
+                  sprintf("%s", prettyNum(x, big.mark=",")),
+                  sprintf("%.2f", x)
+    )
+    paste(res, collapse = ", ")
+  } else {
+    x
+  }
+}
+knit_hooks$set(inline = inline_hook)
 @
@@
 \begin{abstract}
-\noindent We re-examine the behavior of stock returns after net issue announcements using the five-factor model proposed by Fama and French (2015a).
-We confirm their findings that the equity issue anomaly disappears with the five-factor model, but the buyback anomaly does not.
-Buyback announcements by firms with high pre-announcement (idiosyncratic) volatility are followed by higher long-term abnormal returns.
-This is inconsistent with the widely documented low volatility anomaly, but consistent with Stambaugh, Yu, and Yuan (2015) who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.
-
+\noindent  We find that, inconsistent with the well-known low volatility anomaly, post-buyback announcement long-term abnormal returns are higher when the pre-announcement (idiosyncratic) volatility is high, and not significant otherwise.
+This is consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.
+The results hold for both small and large firms.
+We also find no post-equity issue abnormal returns when using the five-factor model proposed by Fama and French (2015a).
+However, the post-buyback announcement abnormal returns are also higher for firms that subsequently announce an equity issue.
+Finally, based on our findings we extend the Undervaluation Index of \citep{PeyerVermaelen2009}.
 \end{abstract}
@@
 
+<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
+cleanup_bb = list()
+cleanup_bb$Standardise <- BUYBACK_DATA$cleanupSDC$Standardise
+cleanup_bb$biz_clean <- BUYBACK_DATA$cleanupBIZ
+cusip_bb = BUYBACK_DATA$DATASET$SDC$CUSIP
+event.date_bb = BUYBACK_DATA$DATASET$SDC$Event.Date
+permno_bb = BUYBACK_DATA$DATASET$SDC$permno
+
+cleanup_iss = list()
+cleanup_iss$Standardise <- ISSUERS_DATA$cleanupSDC$Standardise
+cleanup_iss$biz_clean <- ISSUERS_DATA$cleanupBIZ
+cusip_iss = ISSUERS_DATA$DATASET$SDC$CUSIP
+event.date_iss = ISSUERS_DATA$DATASET$SDC$Event.Date
+permno_iss = ISSUERS_DATA$DATASET$SDC$permno
+@
+
 Our sample spans the period from January \Sexpr{firstyear} to December \Sexpr{lastyear}.
@@
 An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both.
-Finally, we removed the following events: no CRSP returns available (\Sexpr{cleanup_bb$get_crsp$NOPERMNO_remove + cleanup_bb$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_bb$compustat$NO_GVKEY_remove + cleanup_bb$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).
-Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(BUYBACK_DATA$finance_Size_used)}  events).\footnote{We are using the industries from Kenneth French's Website.
+Finally, we removed the following events: no CRSP returns or not all Compustat data available (\Sexpr{BUYBACK_DATA$cleanupNoPermno +  BUYBACK_DATA$cleanupNoCRSPdata + BUYBACK_DATA$cleanupMissingSomeValues} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).
+Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{sum(BUYBACK_DATA$cleanupBIZ$Industry_filter)}  events).\footnote{We are using the industries from Kenneth French's Website.
 The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799).
@@
 We removed all SDC events for which either the event date (\Sexpr{cleanup_iss$Standardise$SDC_NODATE} events) or the CUSIP (\Sexpr{cleanup_iss$Standardise$SDC_NOCUSIP} events) was missing or where we found duplicate events with mismatching information (\Sexpr{cleanup_iss$Standardise$BAD_DUPLICATES} events), a total of \Sexpr{cleanup_iss$Standardise$SDC_standardize_removal} events - given the overlap between these cases.
-Finally, as for the buybacks, we removed the following events: no CRSP returns available (\Sexpr{cleanup_iss$get_crsp$NOPERMNO_remove + cleanup_iss$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_iss$compustat$NO_GVKEY_remove + cleanup_iss$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_iss$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_iss$biz_clean$Penny_stock_filter} events), or  the stocks were not listed on the NYSE, Nasdaq or Amex (\Sexpr{cleanup_iss$biz_clean$major_markets_only} events).
-We again removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(ISSUERS_DATA$finance_Size_used)} events).
+Finally, as for the buybacks, we removed the following events: no CRSP returns or not all Compustat data available (\Sexpr{ISSUERS_DATA$cleanupNoPermno +  ISSUERS_DATA$cleanupNoCRSPdata + ISSUERS_DATA$cleanupMissingSomeValues} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_iss$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_iss$biz_clean$Penny_stock_filter} events), or  the stocks were not listed on the NYSE, Nasdaq or Amex (\Sexpr{cleanup_iss$biz_clean$major_markets_only} events).
+We again removed all events from firms in the Financial and Utilities sectors (\Sexpr{sum(ISSUERS_DATA$cleanupBIZ$Industry_filter)} events).
 Our final sample contains \Sexpr{length(cusip_iss)} events made by \Sexpr{length(unique(cusip_iss))} firms.
@@
 Table~\ref{tbl:PastFindingsTimeBB} shows excess returns, using both the IRATS and Calendar Time method for different time periods.
-We consider time periods, which overlap to some extent with past research [\cite{IkenberryLakonishokVermaelen1995}; \cite{PeyerVermaelen2009}; \cite{ManconiPeyerVermaelen2015}; and \cite{FuHuang2015}]: 1985-1990; 1991-2000; 2001-2014 and 2008-2014.
+We consider time periods, which overlap to some extent with past research [\cite{IkenberryLakonishokVermaelen1995}; \cite{PeyerVermaelen2009}; \cite{ManconiPeyerVermaelen2015}; and \cite{FuHuang2015}]: 1985-1990; 1991-2000; 2001-2015 and 2008-2015.
 The last period was chosen to incorporate the financial crisis and to test whether indeed markets have become more efficient in recent years, or whether managers have for example been discouraged from market timing by the obvious mistakes that were made by buying back shares before a major financial crisis.
@@
 Table~\ref{tbl:PastFindingsTimeBB} shows that, regardless of the time period chosen or the method to calculate excess returns, the buyback anomaly remains economically and statistically significant and there is no clear time trend in the data that suggests that markets have become more efficient over time.
-For example, although the 2001-2014 period shows smaller timing ability than the 1990-2000 period, excess returns in the 2008-2014 period are as large as in the 1991-2000 period: approximately \Sexpr{BBtable_time["+48",22]}$\%$  after 4 years using IRATS or \Sexpr{BBtable_time_cal["+48",22]}$\%$ per month (\Sexpr{48*BBtable_time_cal["+48",22]}$\%$ after 4 years) when we use the Calendar Time method.
+For example, although the 2001-2015 period shows smaller timing ability than the 1990-2000 period, excess returns in the 2008-2015 period are as large as in the 1991-2000 period: approximately \Sexpr{BBtable_time["+48",22]}$\%$  after 4 years using IRATS or \Sexpr{BBtable_time_cal["+48",22]}$\%$ per month (\Sexpr{48*BBtable_time_cal["+48",22]}$\%$ after 4 years) when we use the Calendar Time method.
 There is one exception to the consistency between the IRATS and the Calendar Time results: in the period of 1991-2000, the IRATS method generates excess returns after 48 months of \Sexpr{BBtable_time["+48",10]}$\%$ (t=\Sexpr{BBtable_time["+48",11]}) but the Calendar Time method produces statistically insignificant excess returns of \Sexpr{BBtable_time_cal["+48",10]}$\%$ per month.
@@
 Regardless of the method to compute excess returns, the U-index is an excellent predictor: except for the very short 1985-1990 period, buybacks announced by high U-index firms are followed by significantly larger returns than buybacks announced by low U-index firms.
-There is also no evidence that the U-index is losing its predictive power over time: for example, in the 2001-2014 period the difference between high and low U-index firms (after 48 months, IRATS) was \Sexpr{BBtable_undertime["+48",31]-BBtable_undertime["+48",34]}$\%$, while in the most recent 2008-2014 period high U-index firms had \Sexpr{BBtable_undertime["+48",43]-BBtable_undertime["+48",46]}$\%$ larger abnormal returns than low U-index firms.
+There is also no evidence that the U-index is losing its predictive power over time: for example, in the 2001-2015 period the difference between high and low U-index firms (after 48 months, IRATS) was \Sexpr{BBtable_undertime["+48",31]-BBtable_undertime["+48",34]}$\%$, while in the most recent 2008-2015 period high U-index firms had \Sexpr{BBtable_undertime["+48",43]-BBtable_undertime["+48",46]}$\%$ larger abnormal returns than low U-index firms.
 
@@
 Note that, again, we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only.
-In total we have \Sexpr{length(High_VOL_eventsBB)} ``high volatility'' buybacks-events and \Sexpr{length(Low_VOL_eventsBB)} ``low volatility'' ones.
+In total we have \Sexpr{sum(High_VOL_eventsBB)} ``high volatility'' buybacks-events and \Sexpr{sum(Low_VOL_eventsBB)} ``low volatility'' ones.
 Table~\ref{tbl:industriesR2Vol}, columns (3) and (4)  show the percentage of high and low volatility events across all industries for which we have at least 100 buyback events in our sample.
@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-EU_index_features = scrub(cbind(BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA$DATASET$SDC$pre_vol,BUYBACK_DATA$Valuation_Index))
-colnames(EU_index_features) <- c("Idiosyncratic Score", "Volatility Score", "U-Index Score")
-Under_IdioBB_cor = cor(EU_index_features)
+#EU_index_features = scrub(cbind(BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA$DATASET$SDC$pre_vol,BUYBACK_DATA$Valuation_Index))
+#colnames(EU_index_features) <- c("Idiosyncratic Score", "Volatility Score", "U-Index Score")
+#Under_IdioBB_cor = cor(EU_index_features)
 @
@@
   columns = c("All 3F","All 5F","High U-index 3F","Low U-index 3F","High U-index 5F","Low U-index 5F"),
-  title="Buyback announcements during 1985-2014",
+  title="Buyback announcements during 1985-2015",
   title1 = "Panel A: IRATs Cumulative Abnormal Returns",
@@
 A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
 ",
@@
   columns = c("All 3F","All 5F"),
-  title="Issue announcements during 1985-2014",
+  title="Issue announcements during 1985-2015",
   title1 = "Panel A: IRATs Cumulative Abnormal Returns",
@@
 A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
 
@@
 
+if (0){
   colnames(ISS_for_BB_Abn_table)[1]<- "Post-buyback SEOs"
   colnames(ISS_for_BB_Abn_table)[4]<- "Other SEOs"
-
-if (0){
   printLatexTable(ISS_for_BB_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
@@
 tmp = BBtable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2014: CAR","t-stat","p-value","2008-2014: CAR","t-stat","p-value")
+colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2015: CAR","t-stat","p-value","2008-2015: CAR","t-stat","p-value")
 tmp2 = BBtable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2014: CAL","t-stat","p-value","2008-2014: CAL","t-stat","p-value")
+colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2015: CAL","t-stat","p-value","2008-2015: CAL","t-stat","p-value")
 
@@
   tmp2,
-  columns= c("1985-1990","1991-2000","2001-2014","2008-2014"),
+  columns= c("1985-1990","1991-2000","2001-2015","2008-2015"),
   title="Buyback returns over different time periods",
@@
   tmp = ISStable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-  colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2014: CAR","t-stat","p-value","2008-2014: CAR","t-stat","p-value")
+  colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2015: CAR","t-stat","p-value","2008-2015: CAR","t-stat","p-value")
   tmp2 = ISStable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-  colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2014: CAL","t-stat","p-value","2008-2014: CAL","t-stat","p-value")
+  colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2015: CAL","t-stat","p-value","2008-2015: CAL","t-stat","p-value")
 
@@
     tmp2,
-    columns= c("1985-1990","1991-2000","2001-2014","2008-2014"),
+    columns= c("1985-1990","1991-2000","2001-2015","2008-2015"),
     title="SEOs returns over different time periods",
@@
 printLatexTable(one_table[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
-printLatexTable(one_table[reported_times,25:36],open=F,close=F,rowcolumn="2001-2014",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
-printLatexTable(one_table[reported_times,37:48],open=F,rowcolumn="2008-2014",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
+printLatexTable(one_table[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
+printLatexTable(one_table[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
 
@@
   printLatexTable(BB_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(BB_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(BB_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
+  printLatexTable(BB_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
+  printLatexTable(BB_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
 
@@
   printLatexTable(ISStable_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISStable_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISStable_undertime[reported_times,37:48],open=F,rowcolumn="2008-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
+  printLatexTable(ISStable_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
+  printLatexTable(ISStable_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
 
@@
   printLatexTable(ISS_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISS_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISS_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2014",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
+  printLatexTable(ISS_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
+  printLatexTable(ISS_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
 }
@@
 A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors (the difference between the risk-free rate and the return on the equally weighted CRSP index, the monthly return on the size, book-to-market factor, profitability factor and investment factor in month) as the independent variables.
-The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
 The 48 month abnormal return for the full sample is equal to ",round(CAL_table_all_bb["+48","CAL 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),
@@
 A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
 label = "tbl:IdiosyncraticunderBB",
@@
 A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
 label = "tbl:VOLunderBB",
@@
 A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors (the difference between the risk-free rate and the return on the equally weighted CRSP index, the monthly return on the size, book-to-market factor, profitability factor and investment factor in month) as the independent variables.
-The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
  label = "tbl:EUunderBBcal",
@@
   columns = c("1985-1990: High-EU", "Low-EU", "1991-2000: High-EU", "Low-EU"),
-  columns2 = c("2001-2014: High-EU", "Low-EU", "2008-2014: High-EU", "Low-EU"),
+  columns2 = c("2001-2015: High-EU", "Low-EU", "2008-2015: High-EU", "Low-EU"),
   title="Long-run IRATS abnormal returns after open market repurchase announcements for low and high EU-index companies over different time periods.",
@@
   columns = c("1985-1990: High-EU", "Low-EU", "1991-2000: High-EU", "Low-EU"),
-  columns2 = c("2001-2014: High-EU", "Low-EU", "2008-2014: High-EU", "Low-EU"),
+  columns2 = c("2001-2015: High-EU", "Low-EU", "2008-2015: High-EU", "Low-EU"),
   title="Calendar method monthly abnormal returns after open market repurchase announcements for low and high EU-index companies over different time periods.",
@@
 A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors (the difference between the risk-free rate and the return on the equally weighted CRSP index, the monthly return on the size, book-to-market factor, profitability factor and investment factor in month) as the independent variables.
-The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
   label = "tbl:EUTimeUnderBBcal",
@@
 IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]
-IRATS_table_all_iss_undervaluation_plot = IRATS_table_all_iss_undervaluation
-IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]
+#IRATS_table_all_iss_undervaluation_plot = IRATS_table_all_iss_undervaluation
+#IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]
 
@@
            max(Exit_on_SEO_Abn_table[reported_times_plots,1], Exit_on_SEO_Abn_table[reported_times_plots,4]))
-plot(Exit_on_SEO_Abn_table[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel A: Buybacks with SEO IRATS CAR", lwd=1.4)
+plot(Exit_on_SEO_Abn_table[reported_times_plots,4], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel A: Buybacks with SEO IRATS CAR", lwd=1.4)
 axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
 axis(2,cex.axis=1.1)
-lines(Exit_on_SEO_Abn_table[reported_times_plots,4],lty = 2,lwd=1.4)
+lines(Exit_on_SEO_Abn_table[reported_times_plots,1],lty = 2,lwd=1.4)
 abline(h=0, lwd=0.5)

### 2016-04-17 bb_issuers_new.R

@@ -1,0 +1,693 @@
+
+####################################################################################
+# These are one by one the tables in the .Rnw. 
+####################################################################################
+
+rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
+
+###
+# Just to check with the older version
+#load("../FinanceData/created_projects_datasets/bb_issuersALL.Rdata")
+#BUYBACK_DATA_old = BUYBACK_DATA
+#ISSUERS_DATA_old = ISSUERS_DATA
+###
+
+source("../FinanceLibraries/lib_helpers.R")
+source("../FinanceLibraries/latex_code.R")
+source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
+source("Paper_global_parameters.R")
+
+initial_vars = ls(all = TRUE) # takes time to save and load, so we save only what is needed at the end. 
+
+load("../FinanceData/created_projects_datasets/BUYBACKSnew.Rdata")
+
+remove_financials_utilities = 1 # This is defined in the Paper_global_parameters.R file... default is 1
+if (remove_financials_utilities){
+  
+  # Buybacks first
+  Industry_filter = BUYBACK_DATA$DATASET$SDC$Industry %in% INDUSTRY_USED 
+  to_remove = which(!Industry_filter)
+  if (length(to_remove) > 0){
+    # just in alphabetic order not to forget any    
+    BUYBACK_DATA$BEME_used <- BUYBACK_DATA$BEME_used[-to_remove]
+    BUYBACK_DATA$Performance_used <- BUYBACK_DATA$Performance_used[-to_remove]
+    BUYBACK_DATA$Size_used <- BUYBACK_DATA$Size_used[-to_remove]
+    BUYBACK_DATA$Valuation_Index <- BUYBACK_DATA$Valuation_Index[-to_remove]
+    
+    BUYBACK_DATA$DATASET$returns_by_event_monthly <- BUYBACK_DATA$DATASET$returns_by_event_monthly[,-to_remove]
[…]

### 2016-04-17 create_bbissuers_data.R

@@ -1,0 +1,525 @@
+
+##########################################################################################
+# Creates the data for the Buybacks-Issuers paper
+##########################################################################################
+
+rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
+
+source("../FinanceLibraries/lib_helpers.R")
+source("../FinanceLibraries/latex_code.R")
+source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
+source("Paper_global_parameters.R")
+
+load("../FinanceData/created_monthly_data/GLOBAL_MONTHLY_DATABASE.Rdata")
+load("../FinanceData/created_yearly_data/GLOBAL_YEARLY_DATABASE.Rdata")
+load("../FinanceData/created_ibes_data/GLOBAL_IBES_DATABASE.Rdata")
+load("../FinanceData/created_buyback_data/GLOBAL_BUYBACK.Rdata")
+load("../FinanceData/created_issuers_data/GLOBAL_ISSUERS.Rdata")
+
+# Some extra universe data variables we need for this project (based on the raw data)
+
+month_dates = str_sub(rownames(GLOBAL_MONTHLY_DATABASE$returns_monthly), start = 1, end = 7) 
+GLOBAL_MONTHLY_DATABASE$market_cap = GLOBAL_MONTHLY_DATABASE$prices_monthly*GLOBAL_MONTHLY_DATABASE$sharesout_monthly
+GLOBAL_MONTHLY_DATABASE$market_cap_score = get_cross_section_score(GLOBAL_MONTHLY_DATABASE$market_cap)
+# BE/ME using just this month data:
+GLOBAL_MONTHLY_DATABASE$BE.ME = ifelse(GLOBAL_MONTHLY_DATABASE$market_cap, GLOBAL_YEARLY_DATABASE$book_value/GLOBAL_MONTHLY_DATABASE$market_cap, NA)
+GLOBAL_MONTHLY_DATABASE$BE.ME_score = get_cross_section_score(GLOBAL_MONTHLY_DATABASE$BE.ME)
+rownames(GLOBAL_MONTHLY_DATABASE$BE.ME) <- rownames(GLOBAL_MONTHLY_DATABASE$returns_monthly)
[…]

### 2016-04-25 bb_issuers_new.Rnw
new version

@@
 # Then to make it into Word: 
-# pandoc -s bb_issuers_new.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx
+# system("pandoc -s bb_issuers_new.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx")
 
@@
 lastyear = as.character(format(Last,"%Y"))
+
+if (0){ # To add later
+  qfactors <- read.csv("dataset/indices_and_factors/qfactors.csv", sep=";", dec=".")
+  rownames(qfactors) <- paste(qfactors[,1],ifelse(str_length(qfactors[,2]) == 2, qfactors[,2], paste("0",qfactors[,2], sep="")), sep="-")
+  useonly = which(rownames(qfactors) %in% str_sub(rownames(Risk_Factors_Monthly), start = 1, end=7))
+  qfactors = qfactors[useonly,]
+  rownames(qfactors) <- rownames(Risk_Factors_Monthly)[match(rownames(qfactors), str_sub(rownames(Risk_Factors_Monthly), start = 1, end=7))]
+  qfactors = qfactors[,3:6]
+  qfactors = apply(qfactors,2,function(r) as.numeric(str_replace(r,",",".")))
+  qfactors = qfactors/100
+  qfactors = cbind(qfactors,Risk_Factors_Monthly[,c("SMB", "HML","RF","RMW","CMA")])
+  formula_used="(ri - RF) ~ MKT + HML + ME + I.A + ROE"
+  qfactors_irats_MKT_HML_ME_IA_ROE = car_table(BUYBACK_DATA$DATASET$returns_by_event_monthly, BUYBACK_DATA$DATASET$SDC$Event.Date, qfactors, formula_used = formula_used)$results
+  qfactors_irats_MKT_HML_ME_IA_ROE = qfactors_irats_MKT_HML_ME_IA_ROE[reported_times,]
+
+}
 
@@
 
-\title{Share Buyback and Equity Issue Anomalies Revisited}%\footnotetext{}
+\title{Volatility and the Buyback Anomaly}%\footnotetext{}
 
@@
 \begin{abstract}
-\noindent  We find that, inconsistent with the well-known low volatility anomaly, post-buyback announcement long-term abnormal returns are higher when the pre-announcement (idiosyncratic) volatility is high, and not significant otherwise.
-This is consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.
-The results hold for both small and large firms.
-We also find no post-equity issue abnormal returns when using the five-factor model proposed by Fama and French (2015a).
-However, the post-buyback announcement abnormal returns are also higher for firms that subsequently announce an equity issue.
-Finally, based on our findings we extend the Undervaluation Index of \citep{PeyerVermaelen2009}.
+\noindent  We find that, inconsistent with the well-known low volatility anomaly, post-buyback announcement long-term abnormal returns are higher when the pre-announcement volatility and idiosyncratic volatility is high, and not significant otherwise.
+This is consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks as well with the prediction that a repurchase authorization is an option to take advantage of undervalued stock prices \citep{IkenberryVermaelen1996}.
+We also confirm that the buyback anomaly survives  when using the five-factor model proposed by Fama and French (2015a).
+Combining volatility with idiosyncratic volatility with other indicators of undervaluation proposed by \citep{PeyerVermaelen2009} improves the predictive power of long term excess returns after buyback anouncements.
 \end{abstract}
@@
 
-The fact that companies experience long-term positive excess returns after share buybacks and negative long term excess returns after equity issues, has been documented extensively in the academic literature.\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}.
-For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}  In spite of these well documented anomalies investors are not less excited today about e.g., a buyback announcement than 30 years ago: on average stock prices increase by approximately 2 to 3$\%$  when companies announce that the board of directors has approved a buyback program.
-Moreover, we find very few funds that specialize in exploiting these anomalies.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA.
-The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization.
-We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} The fact that these anomalies have not generated a significant response from investors and asset management firms is somewhat surprising considering that other anomalies have disappeared after being documented in academic research~\citep{McLean2016}.
-What makes these capital structure anomalies different so that they stand the test of time?
-
-One straightforward explanation is that they are not really anomalous returns but compensation for risk.
+The first purpose of this paper is to test whether there is a link between two well-known anomalies: the net issue anomaly, i.e.
+the fact that share buybacks (equity issues) are followed by long run positive (negative) excess returns\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}.
+For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.} and the volatility anomaly, i.e.
+the fact that (idiosyncratic) volatility is negatively related to expected returns \cite{Ang2006}.
+This link is plausible considering the fact that \cite{Stambaugh2015} find that the relation between idiosyncratic volatility and future returns reverses for undervalued stocks\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}, i.e.
+for undervalued stocks there is a positive relation between idiosyncratic volatility and future returns.
+They argue that their result is consistent with their costly {\it arbitrage hypothesis}: idiosyncratic volatility represents arbitrage risk and deters arbitrage and the resulting reduction in mispricing.
+So, among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.
+It should be noted that in the volatility literature idiosyncratic volatility is estimated by residual variance of of an asset pricing model such as the Fama-French three factor model.
+Empirically there is a very high correlation between residual variance and total variance (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study) so for the remainder of this paper we will refer to this hypothesis as the volatility anomaly.
+
+As the positive (negative) long run returns after buybacks (equity issues) are generally interpreted as evidence of undervaluation (overvaluation), we would predict also a positive (negative) relation between volatility and future returns after firms announce a buyback (equity issue).
+Another reason for expecting a positive relation between volatility and future returns after buyback authorization announcements is provided by \cite{IkenberryVermaelen1996}'s {\it option hypothesis}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks.
+If markets underestimate the value of this option at the time of the buyback authorization, long term excess returns should be positively correlated with volatility.
+Note that this option hypothesis makes no predictions about excess returns after equity issues, unlike buyback authorizations, are firm commitments, not options.
+Because residual variance is highly correlated with total volatility, we use an alternative measure of idiosyncratic volatility that is not correlated with volatility: $1-R^2$.
+It measures to what extent the volatility of stock returns is explained by company-specific (non-factor related) information.
+As the market timing hypothesis (e.g., \cite{IkenberryLakonishokVermaelen1995}) assumes that managers exploit company-specific information it predicts that buyback announcements of firms with high idiosyncratic volatility will generate higher long term excess returns.
+
+However, before proceeding with examining the link between anomalies, it is important to verify that these anomalies are real and not simply a proxy for risk, or have disappeared in recent years as has happened with many other anomalies~\citep{McLean2016}.
 Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the \cite{Carhart1997} 4-factor model as benchmarks.
-However, \cite{FamaFrench2015b}  argue that the buyback and equity issue anomalies do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns.
+However, \cite{FamaFrench2015b}  argue that many anomalies are weakened or  do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns.
 This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns \citep{NovyMarx2013}.
+They find that the volatility anomaly survives for small firms, but the net issue anomaly does not.
 If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research.
@@
 In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only affects selling shareholders who leave the firm.
-In this paper we re-examine the anomaly using the \cite{FamaFrench2015a} model but use announcement dates and separate buyback announcements and equity announcements.
-
-Using buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, we confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
+So before concluding that the buyback and equity issue anomalies have disappeared, they have to be examined separately, using announcement dates.
+
+So the second major purpose of this paper is to verify whether the buyback and equity issue anomalies still exist using the more recent \cite{FamaFrench2015a} five-factor  model, for buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}.\footnote{Using throughout this paper the q-factor model of \cite{Houetal2015} instead of the five-factor model of \cite{FamaFrench2015a} leads to the same conclusions.} We confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
 Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio.
@@
 The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2015}.
+It remains a fact though that the buyback anomaly is a small firm anomaly: value-weighting all the events (as suggested by~\cite{MitchellStafford2000}) makes the alphas disappear.
+So the anomaly does not challenge the view that 99$\%$ of all stocks may well be priced efficiently.
+It simply shows that small cap firms are priced less efficiently and can take advantage of undervaluation, at least on average.
+Moreover, while we do not value-weight the events, as argued by \cite{PeyerVermaelen2009}, if anything, to increase the power of the test to detect mispricing, any weighting should be based on the inverse of size.
 
@@
 
-The results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously.
-Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information.
-If the buyback signals a change in risk \citep{GrullonMichaely2004} hedging market risk may be complicated.
-That is why in this paper we also simulate hedged investment strategies where we estimate risk before forming the portfolios.
-We show that an investor who followed such a strategy starting in \Sexpr{firstyear} would by \Sexpr{lastyear} have realized cumulative excess returns between \Sexpr{round(tail(months1,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$, depending on the length of the holding period.
-
-The second major purpose of this paper is to test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}, i.e.
-(idiosyncratic) volatility is negatively related to expected returns.
-For example, \cite{Ang2006} find {\it negative} alphas for high volatility and high idiosyncratic volatility stocks, using the 3-factor \cite{FamaFrench1993} model.
-Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms.
-However, in our buyback sample we find a significant {\it positive} relation between excess returns, using the Fama-French 5-factor model as a benchmark.
-This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market.
-The result is also consistent with the  {\it costly arbitrage hypothesis} of \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued  stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  Their argument is that idiosyncratic volatility represents arbitrage risk and deters arbitrage and the resulting reduction in mispricing.
-So, among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.
-
-Turning to total volatility we also find that buyback authorizations of high risk stocks are followed by larger excess returns.
-This is consistent with the {\it option hypothesis}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks \citep{IkenberryVermaelen1996}.
-If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.
-
-Combining idiosyncratic risk and total volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns.
+After having established that the buyback anomaly survives the Fama-French five factor model, we test for the relation between volatility measurers and long term excess returns.
+We find a significant {\it  positive} relation between excess returns and volatility as well as idiosyncratic volatility measured by $1-R^2$.
+Note although there is a high correlation (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$) between total volatility and residual variance (the proxy used in the literature for idiosyncratic volatility), the correlation between standardized idiosyncratic volatility and total volatility is only \Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$.
+The positive relation between $1-R^2$ and excess returns is consistent with the {\it information advantage hypothesis}: in firms with high standardized idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market.
+The positive correlation between volatility and excess returns is consistent with the costly arbitrage hypothesis of~\cite{Stambaugh2015} as well as with the option hypothesis of~\cite{IkenberryVermaelen1996}.
+
+Combining  idiosyncratic volatility  and total volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns.
 In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
 Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.
+However the strong negative correlation between size and alpha may explain why this anomaly persists after 30 years and has attracted very little attention in the asset management industry.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA.
+The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization.
+We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} Indeed because management fees are proportional to fund size one expects relatively less interest in anomalies concentrated in small caps or microcaps.
+
+In order to address the issue of size (which suggests the buyback anomaly is not economically important), we close with a section on buyback anomalies for large firms.
+We find that there is a buyback anomaly for large firms, but only if we focus on large volatility stocks.
+This suggests that when there is large uncertainty about fundamental value, even in large firms the option to repurchase stock at prices below fair value is worth a lot.
+Note however that the alpha for these large high volatility firms is significantly smaller than the alpha of the high Enhanced undervaluation index so there remains a tradeoff between excess returns and firm size.
 
@@
 In section 4 we test whether the buyback anomaly is robust across time, investment horizon and industry.
-In section 5 we test whether idiosyncratic risk as well as volatility can improve the predictability of excess returns, relative to simply using the Undervaluation Index proposed by \cite{PeyerVermaelen2009}.
+In section 5 we test whether  idiosyncratic risk as well as total volatility can improve the predictability of excess returns, relative to simply using the Undervaluation Index proposed by \cite{PeyerVermaelen2009}.
 Section 6 concludes.
@@
 However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months.
-This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure.
+This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure, a habit unfortunately adopted by numerous authors.
 Unlike buybacks, equity issues are firm commitments and announced and completed at the same point in time.
@@
 
+So far all our events are equally weighted.
+\cite{MitchellStafford2000} argue that events should be value weighted to test whether represent an economically important anomaly.
+However, as we know from past research, for theoretical as well as empirical reasons, one would expect that managers in small firms are better able and willing to take advantage of mispricing than in large firms.
+So value weighting would simply bias the results toward zero.
+And indeed, when we value-weight the events (results available upon request) long-term excess returns become statistically insignificantly different from zero.
+So the buyback anomaly is not economically important and does not challenge the basic premise that ``the market'' represented by a value-weighted index is priced correctly.
+
 Next we test whether the ``Undervaluation Index'' (U-index) developed by \cite{PeyerVermaelen2009} using buyback announcements from 1991 to 2002 is a robust indicator to separate companies that are buying back stock because they are undervalued from companies that repurchase shares for other reasons.
@@
 
-Figure~\ref{fig:pastall} summarizes the IRATS results in more detail by showing the cumulative abnormal returns during the 6 month pre and 48 month post event period, using the five-factor model.
+%Figure~\ref{fig:pastall} summarizes the IRATS results in more detail by showing the cumulative abnormal returns during the 6 month pre and 48 month post event period, using the five-factor model.
 Results are shown for the total sample of buybacks and equity issues, as well as for high and low U-index buyback samples.
@@
 However, Figure~\ref{fig:ReturnsBB} allows us to verify that the excess returns are not simply the result of outperformance during a particular time period.
-Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.
+%Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.
 The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the excess returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}.
@@
 
-\subsection{Robustness across Sectors}
-\label{sec:AllIndustries}
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
-@
-
-Figure~\ref{fig:industryeventsBB} shows the number of buyback events per industry in our sample.
+%\subsection{Robustness across Sectors}
+%\label{sec:AllIndustries}
+
+%<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+%tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
+%@
+
+%Figure~\ref{fig:industryeventsBB} shows the number of buyback events per industry in our sample.
 The software and semiconductor industries are the most active repurchasers.
@@
 
-There exists a large literature on volatility and stock returns.\footnote{For the most recent overview of the literature and potential hypotheses, see \cite{LiRodneyGarcia2016}.} One of the most puzzling findings is the fact that total volatility and idiosyncratic volatility are negatively correlated with future abnormal returns, when expected returns are calculated using the 3-factor \cite{FamaFrench1993} model  [see e.g., \cite{Ang2006} (Table VII)].
-This volatility anomaly also survives after using the \cite{FamaFrench2015a} 5-factor model, at least for small firms.
+Now that we have established that the buyback anomaly is real and robust even after using the 5-factor Fama-French factor model, we turn to the second major question: are the buyback and volatility anomalies related?
+There exists a large literature on volatility and stock returns.\footnote{For the most recent overview of the literature and potential hypotheses, see \cite{LiRodneyGarcia2016}.} One of the most puzzling findings is the fact that total volatility and idiosyncratic volatility (measured by residual variance)  are negatively correlated with future abnormal returns, when expected returns are calculated using the 3-factor \cite{FamaFrench1993} model  [see e.g., \cite{Ang2006} (Table VII)].
+As noted above volatility and idiosyncratic volatility (measured as residual variance in the literature) are highly correlated (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$).
+Fama and French (2015b) find that this volatility anomaly also survives after using the \cite{FamaFrench2015a} 5-factor model, at least for small firms.
 Perhaps the buyback and the volatility anomaly are related: are the buyback firms with the largest excess returns also firms with the smallest (idiosyncratic) risk?
@@
 that excess returns are a result of the fact that managers are on average successful in taking advantage of an undervalued stock price?
-
-\subsection{Idiosyncratic Risk}
+In that case we expect a negative relation using the \cite{Stambaugh2015} arbitrage hypothesis and the \cite{IkenberryVermaelen1996} option hypothesis.
+However before answering this question, we want to examine the impact of {\it standardized} idiosyncratic risk on future returns, a measure that unlike residual variance is almost not correlated with total volatility and measures more precisely the fraction of total volatility explained by company-specific news.\footnote{As noted in our sample the correlation between $1-R^2$ and residual variance (the typical measure of idiosyncratic risk in the literature) is only \Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$, compared to that between residual variance (the measure of idiosyncratic risk used in the literature) and total volatility which is \Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$.
+See also \cite{LiRajgopaletal2014} for a related discussion on this issue.}
+
+\subsection{Standardized Idiosyncratic Risk and excess returns}
 \label{sec:idiorisk}
@@
 The main ``theory'' behind the buyback anomaly is that firms may have superior {\it company-specific} information.
-Such situations are more likely in industries or companies where the value is driven less by market wide factors, i.e., by highly ``idiosyncratic'' companies.
-So if buybacks are driven by market timing this superior information hypothesis predicts that there should be a positive relation between idiosyncratic returns and volatility.
-To test this hypothesis, for each event we measure the five-factor regression $R^2$ using the 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month, or using the idiosyncratic volatility as in \cite{Ang2006}, leads to the same conclusions - results available upon request.
-However, as we want to differentiate between ``idiosyncratic'' companies and ``high volatility'' ones, to consider both the effects of company specific information and of the option value of a buyback announcement, we separately study the relations with $R^2$ and volatility.
-See also \cite{LiRajgopaletal2014} for a discussion on this issue.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$.
+Such situations are more likely in industries or companies where the volatility is largely driven by company-specific volatility.
+So if buybacks are driven by market timing this superior information hypothesis predicts that there should be a positive relation between excess returns and the percentage of the volatility explained by company-specific factors, i.e.
+the standardized idiosyncratic volatility, which we will for brevity simply define as idiosyncratic risk, however not to be confused with residual variance.
+To test this hypothesis, for each event we measure the five-factor regression $R^2$ using the 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month,  leads to the same conclusions - results available upon request.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$.
 We also define the idiosyncratic score of a firm to be the percentile of its $1-R^2$ across all CRSP firms that month.
 Note that we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only.
+
+Figure \ref{fig:industryeventsBB} shows the number of buyback events per industry in our sample.
+The software, retail and semiconductor industries are the most active repurchasers.
 Table~\ref{tbl:industriesR2Vol}, columns (1) and (2) show the percentage of high and low idiosyncratic risk events across all industries for which we have at least 100 buyback events in our sample.
@@
 
-The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \citep{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \citep{Ang2006} who find a negative relation between IVOL and expected returns.
+%The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \citep{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns.
 However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks.
@@
 
-\subsection{Volatility}
+\subsection{Volatility and excess returns}
 \label{sec:volbuybacks}
@@
 For example, the market may underestimate the maturity of the option if they don't realize that firms who are announcing a buyback authorization for say 2 years are likely to renew the authorization many times in the future.
-Hence, perhaps total volatility is a better prediction of excess returns than idiosyncratic volatility or the U-index.
+
+Although \cite{Stambaugh2015} argue that idiosyncratic volatility, and not total volatility, should be positively related to future returns for undervalued stocks, the empirical fact is that their estimate of idiosyncratic volatility (residual variance) is highly correlated (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$) with total volatility.
+Their argument is that idiosyncratic volatility represents risk that deters arbitrage and therefore creates mispricing.
+Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between residual variance and future returns for undervalued stocks.
+But considering the almost perfect correlation between residual variance and total variance, their hypothesis would also predict a positive correlation between total volatility and future returns for undervalued stocks.
+Hence, perhaps total volatility is a better prediction of excess returns than (standardized) idiosyncratic volatility (defined as $1-R^2$) or the U-index.
 Or perhaps volatility can be an additional, next to the U-index and idiosyncratic volatility, indicator of the likelihood that the buyback is driven by undervaluation.
@@
 Table~\ref{tbl:industriesR2Vol}, columns (3) and (4)  show the percentage of high and low volatility events across all industries for which we have at least 100 buyback events in our sample.
+Software and chips tend to be the most volatile sectors and they are also two of the three sectors where buybacks are more frequent.
 
@@
 Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
-High volatility companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy, which are higher than the \Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged48m),1),1)}$\%$) of the corresponding low volatility sample.}
-
-Table~\ref{tbl:VOLunderBB} also tests whether the U-index is valid for high volatility events, as well as whether adjusting for volatility improves the predictive power of the U-index.
+High volatility companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy, which are higher than the \Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged48m),1),1)}$\%$) of the corresponding low volatility sample.}   So we find support for the \cite{Stambaugh2015} costly arbitrage hypothesis as well as the option hypothesis proposed by \cite{IkenberryVermaelen1996}.
+
+Table~\ref{tbl:VOLunderBB} also tests whether the U-index can further differentiate high volatility events, as well as whether adjusting for volatility improves the predictive power of the U-index.
 Regardless of the time horizon and the event study method, the U-index works for high volatile companies.
@@
 Figure~\ref{fig:pastallVOL} summarizes the results for the total sample and the high and low U-index sample.
-The main difference with Figure~\ref{fig:pastallidio} is that now also low volatility/high U-index firms earn significant excess returns of \Sexpr{VOL_IRATStable_underBB["+48",1]}$\%$ after 48 months.
 
@@
 We use the most recent data pre-announce, and make the winsorization and other adjustments as in the websites above.
-Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.} ``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement.
+Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.}
+%``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. 
 ``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement.
@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-tmp_market_cap = round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb %in% c(4:6)])/1000,1)
+tmp_market_cap = round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb %in% c(4:6)]),1)
 @
@@
 portfolios EU4 through EU6 in Table~\ref{tbl:EUunderBBcal}) is \$\Sexpr{tmp_market_cap} billion (not indicated in the Table).
-So the buyback anomaly is to some extent a small cap anomaly, although portfolio EU3 for which the average market capitalization of its \Sexpr{sum(EUindex_bb==3)} firms is \$\Sexpr{round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb ==3])/1000,1)} billion still has significant abnormal returns.
+So the buyback anomaly is to some extent a small cap anomaly, although portfolio EU3 for which the average market capitalization of its \Sexpr{sum(EUindex_bb==3)} firms is \$\Sexpr{round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb ==3]),1)} billion still has significant abnormal returns.
 
@@
 We find that both idiosyncratic risk (small $R^2$) and total risk are positively correlated with future returns.
-The results that idiosyncratic risk is positively correlated with returns is inconsistent with \cite{Ang2006} but consistent with \cite{Stambaugh2015} who show that for undervalued firms IVOL is positively related to expected returns.
+This result is inconsistent with \cite{Ang2006} but consistent with \cite{Stambaugh2015} who show that for undervalued firms residual variance (almost perfectly correlated with total volatility) is positively related to future returns.
+It is also consistent with the argument of Ikenberry and Vermaelen (1996) that a buyback authorization creates an option to take advantage of an undervalued stock, and options on high volatility stocks are more valuable.
 We combine these characteristics in a new measure: the EU index or Enhanced Undervaluation Index, building on the analysis of \cite{PeyerVermaelen2009}.
@@
 
+if (0){
   printLatexTable2(
@@
 
-@
-
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+}
+@
+
+<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+if (0){
   latex_render_data_frame(
@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+
+#\\textit{Missed (Beat) EPS} measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. 
+EU_relations <- EU_relations[-which(rownames(EU_relations) %in% c("Missed EPS","Beat EPS")),]
+
 rownames(EU_relations)[1] <- "Low Leverage"
@@
 We consider firm \\textit{leverage}, based on data the year before announcement, defined as the ratio $debt/(debt+equity)$.
-\\textit{Missed (Beat) EPS} measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement.
 \\textit{ISS later} measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement.
@@
 
-\begin{figure}[H]
-\centering
+%\begin{figure}[H]
+%\centering
 << fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
+if (0){
   par(mfrow=c(2,2), mar=c(2.3,4,2.3,4))
@@
 
+}
 if (0){
@@
 @
-\caption{Long-run five factors cumulative average abnormal returns (CAR) of buyback and SEO portfolios.
+%\caption{Long-run five factors cumulative average abnormal returns (CAR) of buyback and SEO portfolios.
 The x-axis indicates months from the date of the event announcement.
@@
 Panel~B includes all SEOs.}
-\label{fig:pastall}
-\end{figure}
+%\label{fig:pastall}
+%\end{figure}
 
@@
 \end{document}
+
+%%%% LARGE FIRMS ANALYSIS NOW
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+printLatexTable2(
+  VOL_large_IRATStableBB[reported_times,],
+  VOL_large_IRATStableBB_cal[reported_times,],
+  columns= c("Low Vol.","High Vol."),
+  title="Buyback for Low and High Volatility for Large Firms only",
+  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
+  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
+  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+The following regression is run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
+label = "tbl:VOLlargeunderBB",
+bigtitleontop=T,
+titleontop=T,
+metric1 = "CAR",
+metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=T
+)
+@
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+printLatexTable2(
+  VOL_large_IRATStableBB_time[reported_times,],
+  VOL_large_time_cal[reported_times,],
+  columns= colnames(VOL_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
+  title="Buyback for Low and High Volatility for Large Firms only over Time",
+  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
+  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
+  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+The following regression is run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
+label = "tbl:VOLlargeunderBBTime",
+bigtitleontop=T,
+titleontop=T,
+metric1 = "CAR",
+metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=T
+)
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% TO REMOVE LATER
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+printLatexTable2(
+  IVOL_large_IRATStableBB_time[reported_times,],
+  IVOL_large_time_cal[reported_times,],
+  columns= colnames(IVOL_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
+  title="Buyback for Low and High IVOL for Large Firms only over Time",
+  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
+  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
+  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+The following regression is run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
+label = "tbl:IVOLlargeunderBBTime",
+bigtitleontop=T,
+titleontop=T,
+metric1 = "CAR",
+metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=T
+)
+@
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+printLatexTable2(
+  Idio_large_IRATStableBB_time[reported_times,],
+  Idio_large_time_cal[reported_times,],
+  columns= colnames(Idio_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
+  title="Buyback for Low and High Idiosyncratic for Large Firms only over Time",
+  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
+  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
+  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+The following regression is run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
+label = "tbl:IdiolargeunderBBTime",
+bigtitleontop=T,
+titleontop=T,
+metric1 = "CAR",
+metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=T
+)
+@
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+printLatexTable2(
+  Uindex_large_IRATStableBB_time[reported_times,],
+  Uindex_large_time_cal[reported_times,],
+  columns= colnames(Uindex_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
+  title="Buyback for Low and High U-index for Large Firms only over Time",
+  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
+  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
+  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+The following regression is run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
+label = "tbl:UindexlargeunderBBTime",
+bigtitleontop=T,
+titleontop=T,
+metric1 = "CAR",
+metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=T
+)
+@
+
+%%%%%%%%%
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+printLatexTable2(
+  VOL_small_IRATStableBB_time[reported_times,],
+  VOL_small_time_cal[reported_times,],
+  columns= colnames(VOL_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
+  title="Buyback for Low and High Volatility for Small Firms only over Time",
+  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
+  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
+  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+The following regression is run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
+label = "tbl:VOLlargeunderBBTime",
+bigtitleontop=T,
+titleontop=T,
+metric1 = "CAR",
+metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=T
+)
+@
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+printLatexTable2(
+  IVOL_small_IRATStableBB_time[reported_times,],
+  IVOL_small_time_cal[reported_times,],
+  columns= colnames(IVOL_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
+  title="Buyback for Low and High IVOL for Small Firms only over Time",
+  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
+  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
+  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+The following regression is run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
+label = "tbl:IVOLlargeunderBBTime",
+bigtitleontop=T,
+titleontop=T,
+metric1 = "CAR",
+metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=T
+)
+@
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+printLatexTable2(
+  Idio_small_IRATStableBB_time[reported_times,],
+  Idio_small_time_cal[reported_times,],
+  columns= colnames(Idio_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
+  title="Buyback for Low and High Idiosyncratic for Small Firms only over Time",
+  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
+  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
+  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+The following regression is run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
+label = "tbl:IdiolargeunderBBTime",
+bigtitleontop=T,
+titleontop=T,
+metric1 = "CAR",
+metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=T
+)
+@
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+printLatexTable2(
+  Uindex_small_IRATStableBB_time[reported_times,],
+  Uindex_small_time_cal[reported_times,],
+  columns= colnames(Uindex_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
+  title="Buyback for Low and High U-index for Small Firms only over Time",
+  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
+  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
+  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+The following regression is run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
+label = "tbl:UindexlargeunderBBTime",
+bigtitleontop=T,
+titleontop=T,
+metric1 = "CAR",
+metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=T
+)
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% TO REMOVE TILL HERE 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-04-25 Paper_global_parameters.R

@@ -1,174 +1,0 @@
-############################################################################################ 
-# All global parameters of the project
-############################################################################################ 
-
-##########################################################################################
-### Parameters for the "business_data_clean" of the data
-
-# business_data_clean.R parameters
-First = as.Date("1976-01-01")
-Last = as.Date("2014-12-31")
-# BUT THIS IS THE FIRST DAY WE TRADE ANY PORTFOLIOS IN THE PORTFOLIOS SECTION: 
-# we need some time to get enough live evnents and to hedge
-FirstTrade = as.Date("1985-01-01")
-# Dates used for the events we consider
-AbsoluteMinimumDate = as.Date("1976-01-01")
-
-periods_considered = rbind(
-  c("1985-01-01", "1990-12-31"),
-  c("1991-01-01", "2000-12-31"),
-  c("2001-01-01", "2014-12-31"),
-  c("2008-01-01", "2014-12-31")
-)
-finance_period = "2001-01-01"
-
-penny_stock_price_recent = 3 # penny stock threshold price - post 1990
-penny_stock_price_old = 1 # penny stock threshold price - pre 1990
-good_currencies = c("US")
-major_markets = c("N", "NM", "NY", "NK",      "New York", "Nasdaq", "NYSE Amex", "American")
-
-MIN_SIZE = 0 #micro caps are those with a market cap <300m
-MAX_SIZE = 1e20 #already in million (e6)
-MIN_ME_quantile = 0 # the minimum ff ME quantile
-MAX_ME_quantile = 20 # the maximum ff ME quantile
-MIN_BEME_quantile = 0 # the minimum ff BE/ME quantile
-MAX_BEME_quantile = 20 # the maximum ff BE/ME quantile
-MIN_EVENT_SIZE = 0 # Required minimum "event size" (e.g. % of shares repurchased/issued)
-MAX_EVENT_SIZE = 50 # not allow more than this percent of shares for the event
-
-days_live = 0 # minimum number of days a stock needs to be live before announcement date
-remove_returns_outliers = 0 # remove the reutrns outliers?
-MAX_DR_abs = 100 # Max absolute daily return to consider a stock is an outliers
-max_vol_outlier = 100000.1 # max daily standard deviation in 6 months before announcement
-
[…]

### 2016-04-25 bb_issuers.R

@@ -1,1648 +1,0 @@
-
-initial_vars = ls(all = TRUE) # takes time to save and load!!! so we save only what is needed at the end. 
-# load("tmpfiles/vol_analysis.Rdata")
-# load("tmpfiles/bb_issuersALL.Rdata") # If we want to add/change things without rerunning all...
-
-##################################################################
-# Load the data: EVENTS ARE ORDERED IN TIME AND TIME ALIGNED
-##################################################################
-if (time_align_all_data){
-  source("dataset/process_code/get_ff_and_market_data.R")
-  if (!file.exists("dataset/buybacks.Rdata") | generate_all_data){
-    datasetname = "buybacks" 
-    source("dataset/process_code/create_dataset.R")
-    buybacks = events; rm("events") 
-  } else {
-    load("dataset/buybacks.Rdata")    
-    buybacks = events; rm("events")
-  }
-  
-  if (!file.exists("dataset/issuers.Rdata") | generate_all_data){
-    datasetname = "issuers" 
-    source("dataset/process_code/create_dataset.R")
-    issuers = events; rm("events") 
-  } else {
-    load("dataset/issuers.Rdata") 
-    issuers = events; rm("events") 
-  }
-  
-  ####################################################################################
-  # Get the FF and market data and ALWAYS time align all data!
-  load("dataset/indices_and_factors/market_ff_data.Rdata")
-  # MAKE SURE ALL DATASETS USE THE SAME TRADING DAYS. USE ONLY THE COMMON DAILY RETURNS DAYS WITH THE MARKET
-  used_days = intersect(rownames(Risk_Factors),intersect(intersect(names(Market_Daily), rownames(issuers$returns_by_event)), rownames(buybacks$returns_by_event)))
-  Market_Daily = Market_Daily[used_days]
-  Risk_Factors = Risk_Factors[used_days,]  
-  issuers$returns_by_event = issuers$returns_by_event[used_days,]
-  buybacks$returns_by_event = buybacks$returns_by_event[used_days,]
[…]

### 2016-04-25 bb_issuers_new.R

@@ -21,7 +21,7 @@ initial_vars = ls(all = TRUE) # takes time to save and load, so we save only wha
 
 load("../FinanceData/created_projects_datasets/BUYBACKSnew.Rdata")
 
-remove_financials_utilities = 1 # This is defined in the Paper_global_parameters.R file... default is 1
+# remove_financials_utilities is defined in the Paper_global_parameters.R file... default is 1
 if (remove_financials_utilities){
   
   # Buybacks first
@@ -63,17 +63,26 @@ if (remove_financials_utilities){
 
 Risk_Factors_Monthly = BUYBACK_DATA$Risk_Factors_Monthly
 Market_Monthly = BUYBACK_DATA$Market_Monthly
-   
-value.weights_bb = BUYBACK_DATA$DATASET$CRSP$Market.Cap
-value.weights_iss = ISSUERS_DATA$DATASET$CRSP$Market.Cap
-# value.weights_bb = rep(1,length(BUYBACK_DATA$DATASET$CRSP$Market.Cap)) # This is the first version of the paper - no value weighted calendar method
+
+if (do.value.weight == 1){   
+  value.weights_bb = BUYBACK_DATA$DATASET$CRSP$Market.Cap
+  value.weights_iss = ISSUERS_DATA$DATASET$CRSP$Market.Cap
+} else {
+  value.weights_bb = rep(1,length(BUYBACK_DATA$DATASET$CRSP$Market.Cap)) # This is the first version of the paper - no value weighted calendar method
+  value.weights_iss = rep(1,length(ISSUERS_DATA$DATASET$CRSP$Market.Cap)) # This is the first version of the paper - no value weighted calendar method
+}
 
 company_subset_undervalued_bb = BUYBACK_DATA$Valuation_Index > 10
 company_subset_overvalued_bb = BUYBACK_DATA$Valuation_Index < 7
 High_Idiosyncr_eventsBB = BUYBACK_DATA$DATASET$CRSP$Rsq_score < quantile(BUYBACK_DATA$DATASET$CRSP$Rsq_score, quantile_R2)
 Low_Idiosyncr_eventsBB  = BUYBACK_DATA$DATASET$CRSP$Rsq_score > quantile(BUYBACK_DATA$DATASET$CRSP$Rsq_score, 1-quantile_R2)
[…]

### 2016-04-25 business_data_clean.R

@@ -1,79 +1,0 @@
-
-business_data_removal <- function(events){
-  
-  cleanup = events$cleanup # to avoid losing info when we remove data. we add back at the end of the file
-  
-  BIZ_initial_data = nrow(events$SDC)
-  
-  No_filter = rep(T,length(events$SDC$Event.Date))
-  Basic_filter =  No_filter # !is.na(events$SDC$ME_quantile) & !is.na(events$SDC$BEME_quantile)  
-  Period_filter <- (as.Date(events$SDC$Event.Date) >= First) & (as.Date(events$SDC$Event.Date) <= Last)
-  
-  Penny_stock_filter = ifelse(events$SDC$Event.Date < "1995-01-01", scrub(events$SDC$Closing.Price) >= penny_stock_price_old, scrub(events$SDC$Closing.Price) >= penny_stock_price_recent) 
-  
-  Event_Industry <- suppressWarnings(scrub(as.numeric(events$SDC$Industry))) # 9 industries are 499A or 619A or 619B.. they are removed
-  Industry_filter = Event_Industry %in% Industries
-  US_only = (events$SDC$Currency %in% good_currencies)
-  
-  major_markets_only = sapply(events$SDC$Stock.Exchange, function(i) sum(str_split(i, "\\+")[[1]] %in% major_markets)>0)
-  TOTAL_FILTER_basic = No_filter & Basic_filter & Period_filter & Penny_stock_filter  & Industry_filter & US_only & major_markets_only
-  
-  Market_cap_filter =  (scrub(events$SDC$Market.Cap) >= MIN_SIZE) & (scrub(events$SDC$Market.Cap) <= MAX_SIZE)
-  ME_quantile_filter    =  scrub(events$SDC$ME_quantile)   >= MIN_ME_quantile   & scrub(events$SDC$ME_quantile)    <= MAX_ME_quantile  # & !is.na(events$SDC$ME_quantile)
-  BEME_quantile_filter  =  scrub(events$SDC$BEME_quantile) >= MIN_BEME_quantile & scrub(events$SDC$BEME_quantile)  <= MAX_BEME_quantile #& !is.na(events$SDC$BEME_quantile)   
-  #Leverage_filter = (scrub(events$SDC$lt/events$SDC$at) > 0.5)*(!is.na(events$SDC$lt/events$SDC$at))
-  EventSize_filter = (events$SDC$Event.Size >= MIN_EVENT_SIZE) & (events$SDC$Event.Size <= MAX_EVENT_SIZE)
-  
[…]

### 2016-04-25 create_bbissuers_data.R

@@ -10,22 +10,43 @@ source("../FinanceLibraries/latex_code.R")
 source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
 source("Paper_global_parameters.R")
 
+load("../FinanceData/created_daily_data/GLOBAL_DAILY_DATABASE.Rdata")
 load("../FinanceData/created_monthly_data/GLOBAL_MONTHLY_DATABASE.Rdata")
 load("../FinanceData/created_yearly_data/GLOBAL_YEARLY_DATABASE.Rdata")
 load("../FinanceData/created_ibes_data/GLOBAL_IBES_DATABASE.Rdata")
 load("../FinanceData/created_buyback_data/GLOBAL_BUYBACK.Rdata")
 load("../FinanceData/created_issuers_data/GLOBAL_ISSUERS.Rdata")
 
-# Some extra universe data variables we need for this project (based on the raw data)
+###################################################################################################
+# We only use permnos that traded at least once in only these exchanges: NYSE (11), American Stock Exchange (12), Nasdaq (14)
+# So we update all data accordingly
+###################################################################################################
+good_exchange_traded = apply(GLOBAL_YEARLY_DATABASE$exchange,2, function(r) sum(scrub(r) %in% c(11,12,14)))
+good_exchange_traded = which(good_exchange_traded !=0)
 
+for(field in setdiff(ls(GLOBAL_DAILY_DATABASE), "FamaFrench_five_factors")) 
+  if (!is.null(dim(GLOBAL_DAILY_DATABASE[[field]])))
+    GLOBAL_DAILY_DATABASE[[field]]<- GLOBAL_DAILY_DATABASE[[field]][,good_exchange_traded]
+for(field in setdiff(ls(GLOBAL_MONTHLY_DATABASE), "FamaFrench_five_factors")) 
+  if (!is.null(dim(GLOBAL_MONTHLY_DATABASE[[field]])))
+    GLOBAL_MONTHLY_DATABASE[[field]]<- GLOBAL_MONTHLY_DATABASE[[field]][,good_exchange_traded]
+for(field in ls(GLOBAL_YEARLY_DATABASE)) 
[…]

### 2016-04-25 create_tool_data.R

@@ -1,145 +1,0 @@
-
-##########################################################################################
-# Creates a small subset of the data only used for the interactive tool - to load faster
-##########################################################################################
-
-rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
-
-source("lib_helpers.R") 
-source("latex_code.R")
-source("dataset/indices_and_factors/ff_industries_sic.R")
-source("business_data_clean.R")
-source("Paper_global_parameters.R")
-initial_vars = ls(all = TRUE) # takes time to save and load!!! so we save only what is needed at the end. 
-
-load("tmpfiles/bb_issuersALL.Rdata")
-rm("buybacks_ma", "buybacks_repurchases", "CRSP_prc", "CRSP_returns_monthly","CRSP_returns",
-   "CRSP_prc_monthly","idx_Compustat_availBE","LEV_randomization",
-   "crsp_sdc_link", "CRSP_shrout_monthly","fundamental_annual",
-   "ibes","ibes_data","ibes_eps",
-   #"ibes_sIs",
-   "ibes_cusip_permno_from_python","Indices_Daily",
-   "BE.MEbreakpoints","BEMEthres","all_compustat_data","all_characteristics",
-   "MEbreakpoints","MEthres","mom_monthly","noBBdelistings_all","pension_annual",
-   "returns_by_event","returns_by_event_monthly","SDCstandardised","SDC",
-   "backfilled","BE_used_all","compustat_data","dataset","Market_Daily","previous",
-   "R2_randomization","tmp_test1","VOL_randomization","x","EPSunc_randomization")
-
-
-Betas_PB6M <- Betas_lm("Six.Month.Before","One.Day.Before",BUYBACK_DATA$DATASET$Dates, BUYBACK_DATA$DATASET$returns_by_event, Risk_Factors)
-rm("Risk_Factors")
-
[…]

### 2016-04-25 dataset/buybacks/sdc/buybacks_rawdata_combine.R

@@ -1,358 +1,0 @@
-
-################################################################
-# INPUT FILES
-################################################################
-
-# Needs these 2 csv files (from SDC - see README)
-file_in_repurchases_dataset  = "dataset/buybacks/sdc/sdc_output_buybacks_repurchases.csv"
-file_in_MnA_dataset  = "dataset/buybacks/sdc/sdc_output_buybacks_ma.csv"
-
-################################################################
-# OUTPUT FILE
-################################################################
-
-# Passes this file to dataset/buybacks/standardise_data.R
-file_out_for_standardize_data  = "dataset/buybacks/sdc/sdc_output_buybacks.csv"
-#all_buybacks_orig <- read.csv(file_out_for_standardize_data,header=T,stringsAsFactors = F,sep=",")
-
-
-################################################################
-
-buybacks_repurchases <- read.csv(file_in_repurchases_dataset,header=T,stringsAsFactors = F,sep=";")
-buybacks_ma <- read.csv(file_in_MnA_dataset,header=T,stringsAsFactors = F,sep=";")
-
-# just in case there is an empty column
-buybacks_repurchases$X <- NULL
-buybacks_ma$X <- NULL
-
-cleanup = list()
-cleanup$Standardise = list()
-
-cleanup$Standardise$initial_MA = length(buybacks_ma$Acquiror..CUSIP)
-cleanup$Standardise$initial_repurchase = length(buybacks_repurchases$Initial.Auth..Date)
-
-####################################################################################
-# First clean up the M&A data.  ALWAYS CHECK HOW MANY EVENTS ARE DROPPED. IF TOO MANY, INVESTIGATE...
-####################################################################################
-
-# Remove duplicate events
-buybacks_ma$tmp1 <- sapply(1:length(buybacks_ma$X.Deal.Number), function(i) 
-  paste(tolower(buybacks_ma$Acquiror..CUSIP[i]),
-        buybacks_ma$X..Date.Announced[i],
-        collapse = ""))
[…]

### 2016-04-25 dataset/buybacks/standardise_data.R

@@ -1,121 +1,0 @@
-#standardizes the SDC data
-datasetname="buybacks"
-
-################################################################
-# INPUT FILES
-################################################################
-# Uses the input and output files from 'dataset/buybacks/sdc/buybacks_rawdata_combine.R'
-
-################################################################
-# OUTPUT FILE
-################################################################
-# The usual file where all the data will be finally saved, after augmenting them at each step
-# global_output_file: see create_dataset.R
-
-
-################################################################
-
-# For  buybacks we do all the standarization when we merge the M&A and repurchases data!
-source('dataset/buybacks/sdc/buybacks_rawdata_combine.R')
-SDC <- all_buybacks
-rm("all_buybacks")
-
-################################################################
-### SOME IMMEDIATE DATA CLEAN FOR THIS SPECIFIC PROJECT
-################################################################
-the_dates = SDC$Event.Date
-inside_range = ifelse(!is.na(the_dates), the_dates >= FirstTrade & the_dates <= Last, T)
-SDC = SDC[inside_range,]
-
-the_dates = SDC$Event.Date
-SDC_NODATE = (is.na(the_dates))  
-SDC_tooearly <- rep(F,length(SDC_NODATE))
-SDC_tooearly[!(is.na(the_dates))] <- the_dates[!(is.na(the_dates))] < AbsoluteMinimumDate
-SDC_NOCUSIP = (SDC$X6.CUSIP == "")  # Note that we check only the 6 digit CUSIP here, as the buybacks M&A have only that
-
-to_keep = !SDC_NODATE & !SDC_tooearly & !SDC_NOCUSIP
-total_orig = nrow(SDC)
-SDC = SDC[to_keep,]
-total_sdc_clean = nrow(SDC)
-
-SDC$X <- NULL # just in case there was any empty columns left (should not be as they are removed in buybacks_rawdata_combine.R)
-
-# We do no more filtering at this stage. All filtering will be done at the business decision level. For now we get all the data. 
[…]

### 2016-04-25 dataset/issuers/standardise_data.R

@@ -1,152 +1,0 @@
-#standardizes the SDC data
-datasetname="issuers"
-
-################################################################
-# INPUT FILES
-################################################################
-
-SDC_datafile = paste("dataset/",datasetname,"/sdc/sdc_output_",datasetname,".csv",sep="")
-
-################################################################
-# OUTPUT FILE
-################################################################
-
-# The usual file where all the data will be finally saved, after augmenting them at each step
-# global_output_file: see create_dataset.R
-
-
-################################################################
-
-SDC <- read.csv(SDC_datafile,header=T,stringsAsFactors = F,sep=";")
-#Make sure we have: Event.Date, CUSIP, and all other standardised data characteristics as described in README in the datasets directory
-the_dates = as.Date(SDC$X.Filing...Date,format="%d/%m/%y",origin="19700101")
-inside_range = ifelse(!is.na(the_dates), the_dates >= FirstTrade & the_dates <= Last, T)
-SDC = SDC[inside_range,]
-
-the_dates = as.Date(SDC$X.Filing...Date,format="%d/%m/%y",origin="19700101")
-SDC_NODATE = (is.na(the_dates))  
-SDC_NOCUSIP = (SDC$X9.Digit.CUSIP == "")  
-
-to_keep = !SDC_NODATE & !SDC_NOCUSIP
-total_orig = nrow(SDC)
-SDC = SDC[to_keep,]
-total_sdc_clean = nrow(SDC)
-
-SDC$X <- NULL # just in case there was any empty column in the .csv from SDC
-
-# We do no more filtering at this stage. All filtering will be done at the business decision level. For now we get all the data. 
-#useonly = (SDC$IPO.Flag..Y.N. %in% c("No") & SDC$Issue.Type %in% c("FO")
-#           #& as.Date(SDC$X.Filing...Date,format="%d/%m/%y",origin="19700101") >= First
-#           )
-#SDC = SDC[useonly,]
-
-################################################################
-# THE REQUIRED FIELDS FIRST
[…]

### 2016-04-25 dataset/process_code/breakpoints_R2.py

@@ -1,90 +1,0 @@
-import pandas as pd
-import matplotlib.pyplot as plt
-import numpy as np
-import statsmodels.api as sm
-import time
-
-#cd "/home/enric/Dropbox/Research/Active Research/BuybacksIssuers/dataset/process_code" #for testing
-
-################################################################
-# Code to compute quantile breakpoints
-#
-
-sourcefile = "../universe/crsp_returns.csv"
-factorfile = "../indices_and_factors/ff_research_data_5_factors_2x3_daily.csv"
-outputfile = "../tmp_files/matrix_R2.csv"
-
-#Step 0A: Read in the returns and convert to a matrix
-df = pd.read_csv(sourcefile,na_values=["B","C"],usecols=["PERMNO","date","RET"])
-df['RET']  = df['RET'].astype(np.float)
-df['date'] = pd.to_datetime(df.date,format="%Y%m%d")
-df = df.pivot('date','PERMNO','RET')
-
-#TESTING ONLY:
-#df = df.ix[:,df.columns[0:1000]]
-
-print "The universe contains",df.shape[0],"recorded days for each of the ",df.shape[1],"companies."
-
-#Step 0B: read the FF factors data
-factors = pd.read_csv(factorfile,sep=r"\s*",engine="python",index_col="date")
-factors.index= pd.to_datetime(factors.index,format="%Y%m%d")
-factors = sm.add_constant(factors)
-
-#Step 1: define breakpoints as last days of month and stop at 2013-12-31
-breakpoints = pd.date_range('31/1/1985', periods=30*12, freq="M")
-#breakpoints = pd.date_range('31/1/2000', periods=15*12, freq="M") #TESTING ONLY
-
-#Create & align X/y vector
-nz_sum = lambda x : np.sum(x[~pd.isnull(x)])
-y = df.apply(nz_sum,1)
-X = sm.add_constant(factors)
-idx = np.intersect1d(y.index,X.index)
-y = y[idx]
-X = X.ix[idx,]
-df = df.ix[idx,]
-
-#Calculation 1: find R2 for the sum of the universe as check
-def find_R2(breakpoint):
-	window = (y.index >= (breakpoint - pd.DateOffset(6*21))) & (y.index <= (breakpoint - pd.DateOffset(1)))
-	yi = (y[window] - X.RF[window])
[…]

### 2016-04-25 dataset/process_code/breakpoints_vol.py

@@ -1,96 +1,0 @@
-import pandas as pd
-import matplotlib.pyplot as plt
-import numpy as np
-
-################################################################
-# Code to compute quantile breakpoints
-#
-if 1:
-	sourcefile = "../universe/crsp_returns.csv"
-	outputfile = "../tmp_files/breakpoints_vol.csv"
-
-	#Step 0: Read in the returns and convert to a matrix
-	#cd "/home/enric/Dropbox/Research/Active Research/BuybacksIssuers/dataset/process_code" #for testing
-	df = pd.read_csv(sourcefile,na_values=["B","C"],usecols=["PERMNO","date","RET"])
-	df['RET']  = df['RET'].astype(np.float)
-	df['date'] = pd.to_datetime(df.date,format="%Y%m%d")
-	df = df.pivot('date','PERMNO','RET')
-	#df = df.ix[:,df.columns[1:100]]
-
-	print "The universe contains",df.shape[0],"recorded days for each of the ",df.shape[1],"companies."
-
-	#Step 1: define breakpoints as last days of month and stop at 2013-12-31
-	breakpoints = pd.date_range('31/1/1985', periods=30*12, freq="M")
-	Q = np.array(range(5,100,5))/100.
-	quantiles   = np.zeros([breakpoints.shape[0],len(Q)])
-
-	#Step 2: for each of the breakpoints, calculate sd vector and extract breakpoints for the previous 6 months
-	for i in range(0,len(breakpoints)):
-	    b = breakpoints[i]
-	    #6*21 = 6 months, -1 day = 30/29th of the month
-	    window = (df.index >= (b - pd.DateOffset(21))) & (df.index <= (b - pd.DateOffset(1)))
-	    #calculate the volatility as the SD per company over it's non NA entries
-	    vol    = (df[window].apply(np.std)).dropna()
-	    quantiles[i] = vol.quantile(Q)
-
-	#Step 3: save the quantiles to file
-	output = pd.DataFrame(quantiles)
-	output.index = breakpoints
-	output.to_csv(outputfile)
-
-################################################################
-# Code to compute quantile membership for buybacks
-#
-sourcefile = "../buybacks/returns/crsp_returns.csv"
-breakfile = "../tmp_files/breakpoints_vol.csv"
-outputfile = "../tmp_files/breakpoints_vol_buybacks.csv"
-
-#for testing
[…]

### 2016-04-25 dataset/process_code/create_dataset.R

@@ -1,80 +1,0 @@
-
-#datasetname = "issuers" 
-#datasetname = "buybacks" 
-
-# Variable "cleanup" is gathering all data cleaning information for EACH step, indicated by the name of the step 
-# (so we can easily track back where we removed any data)
-
-# This is the file where each step reads and writes to. It is first created by standardise_data.R below
-global_output_file= paste("dataset/",datasetname,".Rdata",sep="")
-
-############################################################
-cat("\n\n*******\n\nGetting the Market and Fama-French data \n") 
-# it is ok, this is done for each dataset, for consistency 
-# across dataset: it is the same data in all cases anyway.
-############################################################
-
-# This assumes the S&P daily and monthly returns as well as the FF data are in the files
-# defined as inputs in get_ff_and_market_data.R (see README)
-source("dataset/process_code/get_ff_and_market_data.R")
-
-############################################################
-#standardize the SDC (or other input) data, generates tmp_files/sdc_output_X_standardised.csv
-############################################################
-
-# This assumes the SDC data are in 
-# x/sdc/sdc_output_x.csv (2 files for the buybacks, one from "Repurchaces" 
-# and one from "US Targets" of the SDC database as described in README)
-# It also removes any events for which either the CUSIP or the Event Date is missing
-
-cat("\n\n******\n\nRunning standardise\n cleanup$Standardize should have all data cleaning info at the end of this stage\n")
-source(paste("dataset/", datasetname, "/standardise_data.R", sep=""))
-
-############################################################
-cat("\n\n**********\n\nGetting the CRSP data - NOTE!!! requires manual interventions, descibed in get_crsp_data.R and Steps 2 and 3 in README: Have you done them?\n")
-############################################################
-
-#cat("\nFrom the ",sum(SDC$missingCUSIP8 == "0")," 8-digits CUSIPs available, out of the ",length(SDC$missingCUSIP8)," events, ", sum(str_sub(SDC$CUSIP[SDC$missingCUSIP8 == "0"],start=7,end=8) == "10"), " end with a 10, ", sum(str_sub(SDC$CUSIP[SDC$missingCUSIP8 == "0"],start=7,end=8) == "11"), " end with an 11, and  ", sum(!(str_sub(SDC$CUSIP[SDC$missingCUSIP8 == "0"],start=7,end=8) %in% c("10","11"))), "with other digits\n")
-source("dataset/process_code/get_crsp_data.R")
-
-############################################################
[…]

### 2016-04-25 dataset/process_code/cusip6vs8tests.py

@@ -1,219 +1,0 @@
-#!/usr/bin/python
-import sys
-
-if(len(sys.argv) < 2):
-	print "Usage: python cusiptopermno.py [buybacks|issuers]"
-	exit()
-dataset = str(sys.argv[1])
-
-#Read the readme first!
-import pandas as pd
-import numpy as np
-import timeit
-
-# SEE README
-
-# Do 4 versions (UPDATE BASED ON README) of matching and report the results:
-# Version 1:  using the 8-digit CUSIPs for all cases 
-# Version 2: using the 6-digits CUSIPs for all cases 
-#         Record duplicates for the 6-digit cases, as well as how many 10s and 11s there were for these duplicates.
-# Version 3: use the 8-digit cusips when they are available (see "missing8"), and the 6-digit CUSIPs for the other cases. 
-#         Record duplicates for the 6-digit cases, as well as how many 10s and 11s there were for these duplicates.
-
-# Enric: TO CHECK THESE 3 VERSIONS BELOW. THE FIRST 2 VERSIONS SHOULD BE FINE, BUT GOOD TO CHECK. 
-# ALSO, LET'S COUNT HOW MANY OF THE CRPS NCUSIPS HAVE 10 AND HOW MANY HAVE 11 AT THE END - so we say "we used the majority", 
-# which i guess it is 10 like for the SDC 8-digit CUSIPS
-
-# For buybacks the results are as follows (to update once the tests are confirmed):
-# Version 1: 
-# Finished with a total of 18738 valid matches, 0 doubles and 5429 empty results.
-# Version 2:
-# Finished with a total of 19987 valid matches, 285 doubles and 3895 empty results.
-# (seems the 6 digits ones find more... but how come only 285 duplicates!! this is less than 18738 - 19987. 
-# Also, how many of these are 10 and how many are 11 at the end?!)
-# Version 3: (haven't run it yet, needs fixing)
-# 
-
-# For issuers the results are as follows (to update once the tests are confirmed):
-# Version 1: 
-# Finished with a total of 7562 valid matches, 0 doubles and 2651 empty results.
-# Version 2:
-# Finished with a total of 7868 valid matches, 31 doubles and 2314 empty results.
-# (seems the 6 digits ones find more... but how come only 31 duplicates!! this is less than 7868 - 7562
[…]

### 2016-04-25 dataset/process_code/cusiptopermno.py

@@ -1,132 +1,0 @@
-#!/usr/bin/python
-#Read the readme first!
-"""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""
-" INPUT FILES
-"
-" ../crsp_permno_cusip_pairs/crsp_permno_cusip_pairs.csv (from CRSP, see Step 2 of README)
-" ../tmp_files/sdc_x_cusips_for_python.csv (from get_crsp_data.R)
-"
-" OUTPUT FILES
-"
-" ../tmp_files/crsp_sdc_link_x.csv" (to be used by merge_dataset.R - step 6 of README)
-"  x/permno_for_crsp_x.csv" (to be used to get CRSP returns data - Step 3 of README)
-" ../tmp_files/python_log_x_y.csv (with x the dataset and y the mode)
-"""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""""
-
-import sys
-import pandas as pd
-import numpy as np
-import timeit
-
-mode = 1
-if(len(sys.argv) < 2 or (sys.argv[1] !="buybacks" and sys.argv[1] != "issuers" )):
-	print "Usage: python cusiptopermno.py [buybacks|issuers] [1-4]"
-	print "\tMode 1: use C8 when available, append 10 to C6 otherwise"
-	print "\tMode 2: use C8 when available, use C6 when not"
-	print "\tMode 3: use only C6 digits for all"
-	print "\tMode 4: same as mode 2, but remove C8 that don't end on 10/11"	
-	exit()
-elif(len(sys.argv) > 2):
-	mode = int(sys.argv[2])
-dataset = str(sys.argv[1])
-
-print "Processing dataset "+dataset+" in mode "+str(mode)+"."
-print "Reading PERMNO-CUSIP-DATE universe database."
-crsp = pd.read_csv("../crsp_permno_cusip_pairs/crsp_permno_cusip_pairs.csv",usecols=["PERMNO","date","NCUSIP"])
-sdc = pd.read_csv("../tmp_files/sdc_"+dataset+"_cusips_for_python.csv")
-sdc.date = sdc.date.map(lambda x: int(str(x).replace("-","")))
-
-flog = open("../tmp_files/python_log_"+dataset+"_"+str(mode)+".txt", 'w')
-print >> flog, 'Universe size :',str(np.shape(crsp))
[…]

### 2016-04-25 dataset/process_code/get_compustat_data.R

@@ -1,267 +1,0 @@
-
-######################################################################## 
-######################################################################## 
-## FIRST PART (See README)
-######################################################################## 
-######################################################################## 
-
-#################################################### 
-# Input files
-#################################################### 
-
-# Get the usual file where all data is saved at each step:
-# global_output_file: see create_dataset.R
-load(global_output_file) # always get the data from the previous step, add new data, and save back to it again
-
-# Assumes this file exists (see README)
-# THIS IS THE MASTER CRSP-COMPUSTAT UNIVERSE PAIRS FILE FROM CRSP/COMPUSTAT MERGED (can be used for whatever data)
-# See README on how to get it from CRSP/COMPUSTAT Merged
-crsp_compustat_gvkey_pairs <- read.csv("dataset/crsp_compustat_gvkey_pairs/crsp_compustat_gvkey_pairs.csv",header=T,stringsAsFactors = F,sep=",")
-
-# This file has all the FF and market data, already done by get_ff_and_market_data.R - so it should be already in memory.
-load("dataset/indices_and_factors/market_ff_data.Rdata")
-
-#################################################### 
-# Output files:
-#################################################### 
-
-# this will be used to manually get the data from Compustat. This file is not used again after getting the data from Compustat
-file_out_gvkey = paste("dataset/",datasetname,"/compustat/gvkeys_for_compustat_",datasetname,".csv",sep="")
-
-#################################################### 
-# CLEAN UP IN THIS FILE:
-# We remove the SDC events for which we do not find any GVKEY
-
-#################################################### 
-# Match SDC permnos to the gvkeys, also appending the GVKEYs to the SDC data
-
-# First clean up crsp_compustat_gvkey_pairs
-# keep always the last available
-crsp_compustat_gvkey_pairs = crsp_compustat_gvkey_pairs[sort(crsp_compustat_gvkey_pairs[,"datadate"], index.return=T)$ix,]
[…]

### 2016-04-25 dataset/process_code/get_crsp_data.R

@@ -1,94 +1,0 @@
-
-# Most of this file is manual or python based. See Steps 2 and 3 of README
-
-#################################################### 
-# Input files
-#################################################### 
-
-# Get the usual file where all data is saved at each step:
-# global_output_file: see create_dataset.R
-load(global_output_file) # always get the data from the previous step, add new data, and save back to it again
-
-# Assumes this file exists (See README)
-# THIS IS THE MASTER CRSP UNIVERSE PAIRS FILE FROM CRSP (can be used for whatever data)
-# "dataset/crsp_permno_cusip_pairs/crsp_permno_cusip_pairs.csv"
-
-#################################################### 
-# Output files:
-#################################################### 
-
-# Python generates these files (do not remove them as Python is slow): 
-# "x/returns/permno_for_crsp_"+dataset+".csv", used to manually get the data from CRSP (see README)
-crsp_sdc_link_file = paste("dataset/tmp_files/crsp_sdc_link_",datasetname,".csv",sep="") # used below to append the permnos in the SDC data
-
-# These are from CRSP manually as described in Step 3 in README, which are then used by merge_dataset.R
-#file_in_CRSP_daily = paste("dataset/",datasetname,"/returns/crsp_returns_",datasetname,".csv",sep="")
-#file_in_CRSP_monthly = paste("dataset/",datasetname,"/returns/crsp_returns_",datasetname,"_monthly.csv",sep="")
-
-# This is a temporary file, not used again outside get_crsp_data.R
-# It is used by python, and then removed - see below
-tmp_file = paste("dataset/tmp_files/sdc_",datasetname,"_cusips_for_python.csv",sep="") 
-
-#################################################### 
-# CLEAN UP IN THIS FILE:
-
-# We remove any data with missing PERMNOs
-
-#################################################### 
-
-# We find PERMNOS using the 8-digit CUSIPS. If SDC had only 6-digit CUSIP we append them with a 10 (see standardise_data.R and step 3 of README)
[…]

### 2016-04-25 dataset/process_code/get_ff_and_market_data.R

@@ -1,102 +1,0 @@
-
-##################################################################
-# INPUT files needed
-
-# From CRSP:
-# 1. dataset/indices_and_factors/snp500.csv
-# 2. dataset/indices_and_factors/snp500_monthly.csv
-
-# From http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_library.html 
-# 1. dataset/indices_and_factors/ff_research_data_5_factors_2x3_daily.CSV
-# 2. dataset/indices_and_factors/ff_research_data_5_factors_2x3.CSV
-# 3. dataset/indices_and_factors/me_breakpoints.csv
-# 4. dataset/indices_and_factors/be_me_breakpoints.csv
-
-##################################################################
-# OUTPUT files 
-
-#1. dataset/indices_and_factors/market_ff_data.Rdata
-##################################################################
-
-##################################################################
-# Market for trading days only 
-##################################################################
-
-#Daily index data using CRSP, S.P.500 only, did not double check these with the rest of the code!
-Indices_Daily <- read.csv("dataset/indices_and_factors/snp500.csv", header=TRUE, sep=",", dec=".")
-rownames(Indices_Daily) <- as.Date(as.character(Indices_Daily$DATE),format="%Y%m%d")
-# These are the trading days we will use throughout
-trading.days <- rownames(Indices_Daily)[isBizday(as.timeDate(rownames(Indices_Daily)), holidayNYSE(), wday = 1:5)]
-trading.days = setdiff(trading.days,c("2001-09-11", "2012-10-29" ))
-Indices_Daily = Indices_Daily[trading.days,]
-Market_Daily <- structure(Indices_Daily$sprtrn, .Names = rownames(Indices_Daily) )
-
-#Monthly version of indices: S.P.500 only
-Indices_Monthly <- read.csv("dataset/indices_and_factors/snp500_monthly.csv", header=TRUE, sep=",", dec=".")
-rownames(Indices_Monthly) <- as.Date(as.character(Indices_Monthly$DATE),format="%Y%m%d")
-Market_Monthly <- structure(Indices_Monthly$sprtrn, .Names = rownames(Indices_Monthly)) 
-
[…]

### 2016-04-25 dataset/process_code/merge_dataset.R

@@ -1,388 +1,0 @@
-
-########################################################################
-# INPUT FILES (see also README in the Documentation)
-########################################################################
-
-# Get the usual file where all data is saved at each step:
-# global_output_file: see create_dataset.R
-# by now this one has the SDC with the added COMPUSTAT data
-load(global_output_file) # always get the data from the previous step, add new data, and save back to it again
-
-# Market and FF Data
-# This file has all the FF and market data, already done by get_ff_and_market_data.R
-load("dataset/indices_and_factors/market_ff_data.Rdata")
-
-# CRSP data
-# These 3 .csv files are assumed to be there. 
-# These 2 are generated manually from CRSP as described in Steps 3 in README
-file_in_CRSP_daily   = paste("dataset/",datasetname,"/returns/crsp_returns.csv",sep="")
-file_in_CRSP_monthly = paste("dataset/",datasetname,"/returns/crsp_returns_monthly.csv",sep="")
-
-# IBES data
-# This file is generated manually from IBES as described in Step 5 in README
-file_in_IBES <- paste("dataset/",datasetname,"/ibes/ibes_all.csv",sep="")
-
-########################################################################
-# OUTPUT FILES 
-########################################################################
-
-# again to the usual file:
-# global_output_file: see create_dataset.R
-
-#################################################### 
-# CLEAN UP IN THIS FILE:
-
-# we remove these events here:
-# sum(dropi | duplicatesi | notfoundi)
-# these are events for which we could not find the CRSP data (notfoundi) or 
-# did not have enough pre-event CRSP returns (min 20 non-zero daily 
-# prices to get the penny-stock filter related price) (dropi)
-# or we had multiple  CRSP data (duplicatesi)
-
-
-######################################################################
[…]

### 2016-04-25 dataset/process_code/scrub_dataset.R

@@ -1,67 +1,0 @@
-############################################################################################ 
-#
-# SCRUBBING THE DATA
-#
-# Input: Dataset/X.Rdata generated by merge_dataset.R
-#
-# scrub removes any remaining data issues only (beyond what was removed in standardize_data.R and in
-# merge_dataset.R). In load_data we then remove data based only on "business filters" 
-#
-#############################################################################################
-
-# Get the usual file where all data is saved at each step:
-# global_output_file: see create_dataset.R
-load(global_output_file) # always get the data from the previous step, add new data, and save back to it again
-
-events = dataset$SDC
-returns_by_event        <- dataset$returns_by_event
-returns_by_event_monthly<- dataset$returns_by_event_monthly
-ibes                    <- dataset$ibes
-compustat_data          <- dataset$compustat_data
-
-## DATA CLEAN-UP
-initial_rawdata  = nrow(events)
-cleanup$scrub$initial_rawdata <- initial_rawdata
-
-PERMNOS_NA       = is.na(events$permno)
-duplicate_events = duplicated(paste(events$X6.CUSIP, " (", events$Event.Date,")",sep="")) # WE SHOULD HAVE AT THIS STAGE! THEY ARE REMOVED IN STANDARDIZE.DATA.R...
-No_Closing_Price = is.na(events$Closing.Price) # WE DON'T NEED TO DO THIS HERE, WE CAN CLEAN THIS IN BUSINESS DECISIONS | events$Closing.Price == 0  
-No_Event_Size    = is.na(events$Event.Size) # WE DON'T NEED TO DO THIS HERE, WE CAN CLEAN THIS IN BUSINESS DECISIONS | events$Event.Size == 0
-
-cleanup$scrub$PERMNOS_NA       <- sum(PERMNOS_NA)
-cleanup$scrub$duplicate_events <- sum(duplicate_events)
-cleanup$scrub$No_Closing_Price <- sum(No_Closing_Price)
-cleanup$scrub$No_Event_Size    <- sum(No_Event_Size) 
-
-scrub_to_remove = PERMNOS_NA | duplicate_events | No_Closing_Price | No_Event_Size
-cleanup$scrub$removed    <- sum(scrub_to_remove) 
-
-if (sum(scrub_to_remove) !=0){
-  events                    <- events[!scrub_to_remove,]
-  returns_by_event          <- returns_by_event[,!scrub_to_remove]  
-  returns_by_event_monthly  <- returns_by_event_monthly[,!scrub_to_remove]  
[…]

### 2016-04-25 dataset/universe/process.py

@@ -1,51 +1,0 @@
-import pandas as pd
-import matplotlib.pyplot as plt
-import numpy as np
-
-sourcefile = "../universe/crsp_returns.csv"
-outputfile = "../tmp_files/breakpoints_vol.csv"
-
-#Step 0: Read in the returns and convert to a matrix
-print "Reading the universe data."
-#cd "/home/enric/Dropbox/Research/Active Research/BuybacksIssuers/dataset/process_code/" #for testing
-df = pd.read_csv(sourcefile,na_values=["B","C"],usecols=["PERMNO","date","RET","NCUSIP"])
-df['RET']  = df['RET'].astype(np.float)
-df['date'] = pd.to_datetime(df.date,format="%Y%m%d")
-df = df.pivot('date','PERMNO','RET')
-
-print "The universe contains",df.shape[0],"recorded days for each of the ",df.shape[1],"companies."
-
-#Step 1: define breakpoints as last days of month and stop at 2013-12-31
-breakpoints = pd.date_range('31/1/1986', periods=28*12, freq="M")
-Q           = np.array(range(5,100,5))/100.
-quantiles   = np.zeros([breakpoints.shape[0],len(Q)])
-
-print "Calculating breakpoints ..."
-#Step 2: for each of the breakpoints, calculate sd vector and extract breakpoints for the previous 6 months
-for i in range(0,len(breakpoints)):
-    b = breakpoints[i]
-    #6*21 = 6 months, -1 day = 30/29th of the month
-    window = (df.index >= b - pd.DateOffset(6*21)) & (df.index <= (b - pd.DateOffset(1)))
-    #calculate the volatility as the SD per company over it's non NA entries
-    vol    = (df[window].apply(np.std)).dropna()
-    quantiles[i] = vol.quantile(Q)
-
-#Step 3: save the quantiles to file
-output = pd.DataFrame(quantiles)
-output.index = breakpoints
-output.to_csv(outputfile)
-
-print "Done, quitting!"
-
-#Quick checks
-if 0:
-  plt.plot(np.cumsum(comp_ret))
-  fname = "/home/enric/Dropbox/Research/Active Research/BuybacksIssuers/dataset/buybacks/sdc/  sdc_output_buybacks.csv"
-  df2 = pd.read_csv(fname,usecols=["CUSIP"],sep=";")
-
-  #2000 drop here
[…]

### 2016-04-25 latex_code.R

@@ -1,640 +1,0 @@
-######################################################################################
-## Latex commands
-######################################################################################
-
-# CAN EDIT TO PRINT OUT WHATEVER LATEX WE NEED  
-latex_render_data_frame<-function(x,y=NULL, title="",caption="",label="",columns=NULL,bigtitleontop = F,show_rownames=FALSE,red_text="",green_text="",blue_text="",scale=1,digits,lastSpecial=F,dorotate=F) {
-  #Helper functions
-  p <- function(...){paste(...)}
-  pn <- function(...){paste(...,"\n")} #print newline
-  pc <- function(...){paste(...,"&")}  #print column
-  tostars <- function(x) ifelse(abs(x)<0.01,"**",ifelse(abs(x)<=0.05,"*",""))
-  
-  if(dorotate){
-    width = "\\linewidth"
-  } else {
-    width = "\\textwidth"
-  }  
-  #Start the table definition
-  l <- ""  
-  if(dorotate){
-    l <- pn(l,"\\clearpage\n")
-    l <- pn(l,"\\footnotesize")
-    l <- pn(l,"\\begin{landscape}")
-  }
-  l <- pn(l,"\\begin{table}[!htb]")
-  l <- pn(l," \\setlength\\tabcolsep{1pt}")
-  l <- pn(l,"\\centering")
-  #l <- pn(l,"\\medskip")
-  if(bigtitleontop){
-    if(title!="")
-      if(dorotate) {
-        l <- pn(l,"\\captionof{table}{",title,"}")
-      }else {
-        l <- pn(l,"\\caption{",title,"}")
-      }
-    if(caption!="") {
-      l <- pn(l,"\\parbox{",width,"}")
-      l <- pn(l,"{\\scriptsize \\singlespacing",caption,"}\\\\")
-      l <- pn(l,"\\vspace{.2in}")
-      
-    }
-  }
-  #l <- pn(l,"\\scalebox{",scale,"} {")
-  align <- "l"
-  for(i in 1:(ncol(x))) align<-paste(align,"c",sep="")
-  l <- pn(l,"\\footnotesize")  
-  l <- pn(l,"\\begin{tabular*}{",paste(scale,width),"}{@{\\extracolsep{\\fill} }",align,"}")  
-  cat(l)
-  
-  #### THE TABLE STARTS HERE
-  
-  cat("\\\\ \n")
[…]

### 2016-04-25 lib/heatmapOutput.R

@@ -1,108 +1,0 @@
-
-#  Copyright 2013, Satrapade
-#  by V. Kapartzianis 
-#  Dual licensed under the MIT or GPL Version 2 licenses.
-#  01/2016 Patched to handle NA's E. Junqué de Fortuny
-library(shiny)
-library(htmlwidgets)
-renderHeatmapX <- function(data, style="norm", include.rownames = TRUE, include.colnames=TRUE, nsmall=2, border=0) {
-  #vmax <- max(Filter(is.numeric, data))
-  vmax = max(data[is.numeric(data) & !is.na(data)])
-  sigmoid <- function(v) { return(1 / (1 + exp(-v))) }
-  toRGB <- function(intensity, sign) {
-    rgb <- "rgb("
-    darkness <- floor((1 - intensity) * 256)
-    if(is.na(sign)) 
-      rgb <- paste(rgb,"255,255,255",sep="")
-    else if(sign) 
-      rgb <- paste(rgb, darkness, ",255,", darkness, sep="")
-    else
-      rgb <- paste(rgb, "255,", darkness, ",", darkness, sep="")
-    rgb <- paste(rgb, ")", sep="")
-    return (rgb)
-  }
-  heatmap <- function(x, style="norm") {
-    if ("squashed" == style) {
-      squashed <- sigmoid(x) - 0.5
-      intensity <- abs(squashed) / 0.5
-      rgb <- toRGB(intensity, squashed >= 0)
-    } else { # ("norm" == style)
-      intensity <- abs(x) / vmax
-      rgb <- toRGB(intensity, x > 0)
-    }
-    return (paste("background-color:", rgb))
-  }
-  if (is.null(colnames(data))) colnames(data) <- 1:ncol(data)
-  if (is.null(rownames(data))) rownames(data) <- 1:nrow(data)  
-  as.character(
-    tags$table(
-      border = border,
-      class = 'data table table-bordered table-condensed',
-      tagList({
-        if (include.colnames)
-          tags$thead(
-            class = 'thead',
-            tags$tr(
-              tagList({
-                if (include.rownames)
-                  tags$th()
-                else
-                  list()
-              }),
-              lapply(colnames(data), function(name) {
-                tags$th(name)
-              })
-            )
-          )
-        else
-          list()
-      }),
-      tags$tbody(
-        lapply(1:nrow(data), function(i) {
-          tags$tr(
-            tagList({
-              if (include.rownames)
-                tags$td(
-                  align="right",
-                  rownames(data)[i]
-                )
-              else
[…]

### 2016-04-25 lib/heatmapwidget/R/heatmapwidget.R

@@ -1,141 +1,0 @@
-#'  Heatmap widget based on original code with the following copyright:
-#'  Copyright 2013, Satrapade
-#'  by V. Kapartzianis
-#'  Dual licensed under the MIT or GPL Version 2 licenses.
-#'
-#'  01/2016 Patched to handle NA's, widget E. Junqué de Fortuny
-#'
-#' @import htmlwidgets
-#' @import htmltools
-#' @import shiny
-#'
-#' @export
-heatmapwidget <- function(data,  width = NULL, height = NULL) {
-  # forward options using x
-  params = list(
-    data = data#,
-    #options = list(..., height = height, width = width),
-    #width = width , height = height
-  )
-  params = Filter(Negate(is.null), params)
-  # create widget
-  #htmlwidgets::createWidget(
-  #  name = 'heatmapwidgetGenerate',
-  #  params,
-  #  width = width,
-  #  height = height,
-  #  package = 'heatmapwidget'
-  #)
-  heatmapwidgetGenerate(data)
-}
-
-#' Widget output function for use in Shiny
-#'
-#' @export
-heatmapwidgetOutput <- function(outputId, width = '100%', height = '400px'){
-  #shinyWidgetOutput(outputId, 'heatmapwidget', width, height, package = 'heatmapwidget')
-  tableOutput(outputId, 'heatmapwidget', width, height, package = 'heatmapwidget')
-}
-
-#' Widget render function for use in Shiny
-#'
-#' @export
-renderHeatmapwidget <- function(expr, env = parent.frame(), quoted = FALSE) {
-  if (!quoted) { expr <- substitute(expr) } # force quoted
-  shinyRenderWidget(expr, heatmapwidgetOutput, env, quoted = TRUE)
-}
-heatmapwidgetGenerate <- function(data,style="norm", include.rownames = TRUE, include.colnames=TRUE, nsmall=2, border=0) {#these last ones are not used
-  if(is.null(data)) {
-    cat("NO data ...")
-    return
-  }else{
-    cat(paste(data))
-    cat(data[is.numeric(data)])
-  }
-  #vmax <- max(Filter(is.numeric, data))
-  vmax = max(data[is.numeric(data) & !is.na(data)])
-  sigmoid <- function(v) { return(1 / (1 + exp(-v))) }
-  toRGB <- function(intensity, sign) {
-    rgb <- "rgb("
-    darkness <- floor((1 - intensity) * 256)
[…]

### 2016-04-25 lib/heatmapwidget/inst/htmlwidgets/heatmapwidget.js

@@ -1,25 +1,0 @@
-HTMLWidgets.widget({
-
-  name: 'heatmapwidget',
-
-  type: 'output',
-
-  initialize: function(el, width, height) {
-
-    return {
-      // TODO: add instance fields as required
-    }
-
-  },
-
-  renderValue: function(el, x, instance) {
-
-    el.innerText = x.message;
-
-  },
-
-  resize: function(el, width, height, instance) {
-
-  }
-
-});

### 2016-04-25 lib/heatmapwidget/install.R

@@ -1,10 +1,0 @@
-#https://cran.r-project.org/web/packages/htmlwidgets/vignettes/develop_intro.html
-#installing
-
-if(0) {
-  devtools::create("heatmapwidget")               # create package using devtools
-  setwd("heatmapwidget")                          # navigate to package dir
-  htmlwidgets::scaffoldWidget("heatmapwidget")    # create widget scaffolding
-}
-library(heatmapwidget)
-devtools::install()                        # install the package so we can try it

### 2016-04-25 lib/plots.R

@@ -1,57 +1,0 @@
-
-mainColor= "#E69F00"
-secondaryColor = "#333333"
-
-pnl_plot_interactive <- function(x,...){
-  x = remove_initialization_time(x)
-  pargs<-as.list(match.call(expand.dots=TRUE))
-  if(!"ylab" %in% names(pargs)) ylab<-"Return" else ylab<-pargs$ylab #deparse(substitute(x)) 
-  if(!"main" %in% names(pargs)) main<-paste(names(pnl_stats(x)),pnl_stats(x),sep=":",collapse=" ") else main<-pargs$main
-  plot_arguments<-c(list(data=cumsum(x*100) ,ylab=ylab, main=main),
-                    pargs[setdiff(names(pargs),c("","x","ylab","main"))])
-  plot_arguments$expand.dots = NULL
-
-  
-  CustomAxisLabel <- 'function (d, gran) {
-                      return Dygraph.zeropad(d.getMonth()+1) + "/"+ Dygraph.zeropad(d.getFullYear());
-                    }'
-  CustomValueFormat = 'function (ms) {
-                      var d = new Date(ms);
-                      return Dygraph.zeropad(d.getMonth()+1) + "/"+ Dygraph.zeropad(d.getFullYear());
-                     }'
-  
-  do.call(dygraph,plot_arguments)  %>% 
-    dyRangeSelector() %>%
-    dySeries("V1", label = "Cumulative Return (%)",color=mainColor) %>%
-    dyAxis("x",pixelsPerLabel=48,axisLabelFormatter =JS(CustomAxisLabel),valueFormatter=JS(CustomValueFormat),ticker="Dygraph.dateTicker") 
-}
-
-plotComponentBars <- function(Main_Factors,Comparison_Factors,futures_data,comp,threshold=0.3)  {
-  df <- rbind(      Main_Factors[rownames(Comparison_Factors)[!is.na(Comparison_Factors[,comp])],comp],
-              Comparison_Factors[rownames(Comparison_Factors)[!is.na(Comparison_Factors[,comp])],comp])
-  
-  keep <- apply(abs(df) > threshold,2,sum) > 0
-  df <- df[,keep]
-  
-  colnames(df) <- rownames(Comparison_Factors)[keep]
-  rownames(df) <- c("2001-2016",paste(head(rownames(futures_data),1),"-", tail(rownames(futures_data),1) ,sep=""))
-  
-  #order bars
[…]

### 2016-04-25 lib_helpers.R

@@ -1,969 +1,0 @@
-# Required R libraries (need to be installed - it can take a few minutes the first time you run the project)
-
-# installs all necessary libraries from CRAN
-get_libraries <- function(filenames_list) { 
-  lapply(filenames_list,function(thelibrary){    
-    #SKIP INSTALLATION ON SERVER, THIS CAUSES BUGS
-    #if (do.call(require,list(thelibrary)) == FALSE) 
-    #  do.call(install.packages,list(thelibrary)) 
-    do.call(library,list(thelibrary))
-  })
-}
-
-libraries_used=c("stringr","gtools","foreign","reshape2","digest","timeDate","devtools","knitr","graphics",
-                 "grDevices","xtable","sqldf","stargazer",
-                 "Hmisc","vegan","fpc","GPArotation","FactoMineR","cluster",
-                 "psych","stringr","googleVis", "png","ggplot2","googleVis", "gridExtra","RcppArmadillo","xts","DescTools")
-
-get_libraries(libraries_used)
-
-options(stringsAsFactors=FALSE)
-
-remove_initialization_time <- function(x,min_date=NULL) { # Note: Added also min_date as an argument!! THis way we remove data from any given date!
-  if (!is.null(min_date)){
-    res = x[as.Date(names(x)) >= as.Date(min_date)]
-  } else {
-    if (x[1] != 0){
-      res = x
-    } else {
-      if (sum(x!=0) != 0){
-        #res = tail(res, -head(which(diff(res)!=0),1))
-        #names(res) <- tail(names(res), -head(which(diff(res)!=0),1))
-        
-        tmp <- names(x)
-        ending <- -head(which(diff(x)!=0),1)
-        res = tail(x, ending)
-        names(res) <- tail(tmp, ending)
-      }
-    }
-  }
-  res
-}
-
-yeardays<-function(x){
-  fd<-as.integer(as.Date(head(names(x),1),format="%Y-%m-%d"))
-  ld<-as.integer(as.Date(tail(names(x),1),format="%Y-%m-%d"))
-  365.25*length(x)/(ld-fd)
-}
-
-vol_pa<-function(x,exclude_zero=(x!=0), holidays = holidayNYSE()) {
[…]

### 2016-04-25 report_code.R

@@ -1,533 +1,0 @@
-
-# This file is run only in order to "customize" the over/under valuation events - the rest are all done in report_data.R
-
-reportcode_data<-new.env()
-
-with(reportcode_data,{
-  
-  DATASET = report_data$DATASET     
-  DATASET$Betas_PB6M  = report_data$Betas_PB6M    
-  cleanup = DATASET$cleanup # to avoid losing info when we remove data. we add back at the end of the file
-  # just add some names 
-  DATASET$SDC$event_name = paste(DATASET$SDC$CUSIP, DATASET$SDC$Event.Date, sep="_")
-  colnames(DATASET$Betas_PB6M) <- DATASET$SDC$event_name 
-  
-  #### FIRST THE BUSINESS DECISIONS CLEANUP
-  # Now remove all events for which there was at least another one less than MINIMUM_PERIOD_SINCE_LAST_EVENT before this event
-  recent_events <- which(sapply(1:length(DATASET$SDC$Event.Date), function(ev){
-    all_permno_events = which(DATASET$SDC$permno == DATASET$SDC$permno[ev])
-    sum((DATASET$SDC$Event.Date[ev] - DATASET$SDC$Event.Date[all_permno_events] < MINIMUM_PERIOD_SINCE_LAST_EVENT ) &
-          (DATASET$SDC$Event.Date[ev] - DATASET$SDC$Event.Date[all_permno_events] > 0)) !=0     
-  }))
-  with_recent_event = length(unique(recent_events))
-  cleanup$BIZ_have_previous_recent_event <- with_recent_event 
-  
-  to_remove = unique(recent_events)
-  if (length(to_remove) > 0){
-    # just in alphabetic order not to forget any    
-    DATASET$Abn_returns <- DATASET$Abn_returns[,-to_remove]
-    DATASET$Betas_PB6M <- DATASET$Betas_PB6M[,-to_remove]
-    DATASET$Dates <- DATASET$Dates[,-to_remove]
-    DATASET$DatesMonth <- DATASET$DatesMonth[,-to_remove]
-    DATASET$SDC <- DATASET$SDC[-to_remove,]
-    for(field in ls(DATASET$compustat_data))  DATASET$compustat_data[[field]] <- DATASET$compustat_data[[field]][-to_remove]
-    for(field in ls(DATASET$ibes))  DATASET$ibes[[field]] <- DATASET$ibes[[field]][-to_remove]
[…]

### 2016-04-25 report_data.R

@@ -1,69 +1,0 @@
-
-
-report_data<-new.env()
-
-# THIS CODE USES A DATASET TO GENERATE ALL NECESSARY SLOW TO COMPUTE DATA FOR THE .Rnw AND SAVE THEM IN A FILE WITH THE NAME OF THE DATASET
-with(report_data,{
-  
-  cleanup = DATASET$cleanup # to avoid losing info when we remove data. we add back at the end of the file
-
-  # Add the Dates and order in time
-  DATASET$Dates <- create_dates(as.Date(DATASET$SDC$Event.Date)) # We don't need this any more, can simplify to only get the dates needed... it's ok for now, as it is now slow
-  colnames(DATASET$Dates) <- DATASET$SDC$permno
-  ordered_events = sort(as.numeric(DATASET$SDC$Event.Date),index.return = T)$ix
-  if (length(unique(diff(ordered_events)))!=1)
-    stop(paste("The time order was messed up somewhere"), DATASET$name, sep=" ")
-  rm("ordered_events")
-  
-  DATASET$DatesMonth <- create_dates_month(as.Date(DATASET$SDC$Event.Date)) # We don't need this any more, can simplify to only get the dates needed... it's ok for now, as it is now slow
-  colnames(DATASET$DatesMonth) <- DATASET$SDC$permno
-  
-  ####### Move on with calculating what the .Rnw will later need - whatever is "slow"
-  
-  ########################################################################################################################
-  ### Idiosyncratic risk and Abnormal performance calculation
-  ########################################################################################################################
-  Betas_PB6M <- Betas_lm("Six.Month.Before","One.Day.Before",DATASET$Dates, DATASET$returns_by_event, Risk_Factors)
-  no_beta_available = which(apply(Betas_PB6M,2,function(r) (sum(is.na(r)) !=0)))
-  cleanup$REPORT_no_beta_available = length(no_beta_available) # last cleanup we do!
-  
-  DATASET$SDC$Rsq_returns <- Betas_PB6M["Rsq",]
-  Betas_PB6M  <- Betas_PB6M[setdiff(colnames(Risk_Factors),"RF"),]  
-  
[…]

### 2016-04-25 report_helpers.R

@@ -1,255 +1,0 @@
-car_table_cache <- function(returns,Event.Date,Risk_Factors_Monthly,min_window = -6, max_window = 48,formula_used="(ri - RF) ~ Delta + SMB + HML + RMW + CMA") {
-  factors_used = setdiff(unlist(str_split(gsub("~", ",", gsub("\\-", ",", gsub("\\+", ",", gsub("\\)", "",gsub("\\(", "",formula_used))))), " , ")),"ri")
-  
-  if (sum(!(factors_used %in% colnames(Risk_Factors_Monthly))))
-    stop(paste("car_table misses the risk factors: ",factors_used[!(factors_used %in% colnames(Risk_Factors_Monthly))]))
-  
-  allmonths = min_window:max_window 
-  
-  factors_used_noRF = setdiff(factors_used, "RF")
-  if (ncol(returns) < length(factors_used_noRF) + 1){ 
-    results = matrix(0,nrow=length(allmonths), ncol = 3)
-    results = rbind(results, rep(ncol(returns)))
-    betas = matrix(0,nrow=length(allmonths), ncol = length(factors_used_noRF))
-    betasstderr = matrix(0,nrow=length(allmonths), ncol = length(factors_used_noRF)) 
-    colnames(results) <- c("CAL","t-stat","p-value")
-    rownames(results) <- c(ifelse(allmonths > 0, paste("+",allmonths,sep=""), allmonths),"Observations")
-    colnames(results) <- c("CAR","t-stat","p-value")
-    colnames(betas) <- factors_used_noRF
-    colnames(betasstderr) <- factors_used_noRF
-    all_results = list(results = results, betas = betas, betasstderr = betasstderr)
-    return(all_results) 
-  }
-  
-  #Step 1: Build an event matrix, where all the events are aligned by event month as opposed to calendar month
-  Event.Date = paste(str_sub(Event.Date,start=1,end=7), "01", sep="-") # just in case
-  Row.Date <- as.Date(rownames(returns))
-  firstHit = sapply(Event.Date, function(i) ifelse(i > tail(Row.Date,1), length(Row.Date)+1, ifelse(i < head(Row.Date,1), 0, which(Row.Date == i))))
-  form  = as.formula(formula_used)
-  Risk_Factors_Monthly = Risk_Factors_Monthly[,factors_used]
-  if (!("RF" %in% factors_used)){
[…]

### 2016-04-25 bb_issuers_new.Rnw
update

@@
 \end{document}
-
-%%%% LARGE FIRMS ANALYSIS NOW
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  VOL_large_IRATStableBB[reported_times,],
-  VOL_large_IRATStableBB_cal[reported_times,],
-  columns= c("Low Vol.","High Vol."),
-  title="Buyback for Low and High Volatility for Large Firms only",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:VOLlargeunderBB",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  VOL_large_IRATStableBB_time[reported_times,],
-  VOL_large_time_cal[reported_times,],
-  columns= colnames(VOL_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High Volatility for Large Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:VOLlargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% TO REMOVE LATER
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  IVOL_large_IRATStableBB_time[reported_times,],
-  IVOL_large_time_cal[reported_times,],
-  columns= colnames(IVOL_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High IVOL for Large Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:IVOLlargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  Idio_large_IRATStableBB_time[reported_times,],
-  Idio_large_time_cal[reported_times,],
-  columns= colnames(Idio_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High Idiosyncratic for Large Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:IdiolargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  Uindex_large_IRATStableBB_time[reported_times,],
-  Uindex_large_time_cal[reported_times,],
-  columns= colnames(Uindex_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High U-index for Large Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:UindexlargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-%%%%%%%%%
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  VOL_small_IRATStableBB_time[reported_times,],
-  VOL_small_time_cal[reported_times,],
-  columns= colnames(VOL_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High Volatility for Small Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:VOLlargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  IVOL_small_IRATStableBB_time[reported_times,],
-  IVOL_small_time_cal[reported_times,],
-  columns= colnames(IVOL_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High IVOL for Small Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:IVOLlargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  Idio_small_IRATStableBB_time[reported_times,],
-  Idio_small_time_cal[reported_times,],
-  columns= colnames(Idio_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High Idiosyncratic for Small Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:IdiolargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  Uindex_small_IRATStableBB_time[reported_times,],
-  Uindex_small_time_cal[reported_times,],
-  columns= colnames(Uindex_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High U-index for Small Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:UindexlargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% TO REMOVE TILL HERE 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-04-25 bb_issuers_new.R

@@ -648,391 +648,6 @@ rm("tmp")
 
 # Done above.
 
-
-####################################################################################
-# Large firms analysis
-
-useonly = which(Low_VOL_eventsBB & BUYBACK_DATA$DATASET$CRSP$Market.Cap > 100 & BUYBACK_DATA$Size_used <=3)
-tmp11 = car_table(BUYBACK_DATA$DATASET$returns_by_event_monthly[,useonly], BUYBACK_DATA$DATASET$SDC$Event.Date[useonly], Risk_Factors_Monthly)$results
-tmp21 = calendar_table(BUYBACK_DATA$DATASET$returns_by_event_monthly[,useonly], BUYBACK_DATA$DATASET$SDC$Event.Date[useonly], Risk_Factors_Monthly,value.weights = value.weights_bb[useonly])$results
-useonly = which(High_VOL_eventsBB & BUYBACK_DATA$DATASET$CRSP$Market.Cap > 100 & BUYBACK_DATA$Size_used <=3)
-tmp12 = car_table(BUYBACK_DATA$DATASET$returns_by_event_monthly[,useonly], BUYBACK_DATA$DATASET$SDC$Event.Date[useonly], Risk_Factors_Monthly)$results
-tmp22 = calendar_table(BUYBACK_DATA$DATASET$returns_by_event_monthly[,useonly], BUYBACK_DATA$DATASET$SDC$Event.Date[useonly], Risk_Factors_Monthly,value.weights = value.weights_bb[useonly])$results
-
-VOL_large_IRATStableBB = cbind(tmp11, tmp12)
-VOL_large_IRATStableBB_cal = cbind(tmp21, tmp22)
-colnames(VOL_large_IRATStableBB) <- c("Low Vol: CAR", "t-stat","p-value","High Vol: CAR", "t-stat","p-value")
-colnames(VOL_large_IRATStableBB_cal) <- c("Low Vol: CAL", "t-stat","p-value","High Vol: CAL", "t-stat","p-value")
-
-rm("tmp11","tmp12","tmp21","tmp22", "useonly")
-
-# Time analysis now
-
-VOL_large_IRATStableBB_time = Reduce(cbind, lapply(2:nrow(periods_considered), function(i){
-  periodnow = (BUYBACK_DATA$DATASET$SDC$Event.Date >= periods_considered[i,1] & BUYBACK_DATA$DATASET$SDC$Event.Date <= periods_considered[i,2])
[…]

### 2016-04-25 bb_issuers_new.Rnw
clean up

@@
 \begin{document}
-
-%%Blind title page
-%\begin{titlepage}
-%\begin{center}
-%  \centering
-%\vskip 60pt
-%\LARGE Share Buyback and Equity Issue Anomalies Revisited \par
-%\vskip 1.5em
-%\normalsize  \today
-%\noindent \\ 
-%\begin{abstract}
-%\noindent We re-examine the behavior of stock returns after net issue  announcements using the five-factor model proposed by Fama and French (2015a).
-We confirm their findings that the equity issue anomaly disappears  with the five-factor model, but the buyback anomaly does not.
-Buyback announcements by firms  with high pre-announcement (idiosyncratic) volatility  are followed by higher long-term abnormal returns.
-This is inconsistent with the widely documented low volatility anomaly, but consistent with Stambaugh, Yu, and Yuan (2015) who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.
-%\end{abstract}
-%\vspace{2cm}
-%\end{center}
-%\medskip
-%\noindent \textit{JEL classification}: G35
-%\medskip
-%\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings
-%\end{titlepage}
 
@@
 
-%Figure~\ref{fig:pastall} summarizes the IRATS results in more detail by showing the cumulative abnormal returns during the 6 month pre and 48 month post event period, using the five-factor model.
-Results are shown for the total sample of buybacks and equity issues, as well as for high and low U-index buyback samples.
-
 \subsection{Buybacks followed by Equity Issues}
@@
 
-%Table~\ref{tbl:BBISSexitAfter} shows the long run excess returns after the announcement of an equity issue for two samples.
-The first sample (After a Buyback) shows the excess returns for issues for which in the previous 48 months the firm announced a buyback.
-The second sample (No Prior Buyback) shows the excess returns for all other issue announcements.
-The fact that excess returns are not significantly different from zero for the post-buyback issuers agrees with the intuition of Figure~\ref{fig:BBISSexit}: exiting when there is a subsequent equity issue is a better strategy for the long-term buyback investor.
-
 \section{How robust is the buyback  anomaly?}
@@
 However, Figure~\ref{fig:ReturnsBB} allows us to verify that the excess returns are not simply the result of outperformance during a particular time period.
-%Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.
-The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the excess returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}.
-In only one year (\Sexpr{rownames(tmp)[which.min(tmp[,13])]}) the strategy generates an abnormal loss larger than \Sexpr{round(abs(sort(tmp[,13])[2]),1)}$\%$.
-
-%\subsection{Robustness across Sectors}
-%\label{sec:AllIndustries}
-
-%<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-%tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
-%@
-
-%Figure~\ref{fig:industryeventsBB} shows the number of buyback events per industry in our sample.
-The software and semiconductor industries are the most active repurchasers.
-They also tend to be the most volatile industries, industries where disagreement about fundamental value is large - as we report later in Table \ref{tbl:industriesR2Vol}.
-Table~\ref{tbl:IndustriesBB} shows the IRATS cumulative abnormal returns and Table~\ref{tbl:IndustriesBB_cal} the Calendar Time method monthly average abnormal returns when we remove one industry at the time, for the top most frequent buyback industries (those for which there are at least \Sexpr{min_industry_sampleBB} events in our sample).
-Note from Table~\ref{tbl:priorBuybacks} that, after 48 months, the cumulative abnormal returns for the whole sample (using IRATS) is \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ and the monthly average excess return (Calendar Time) is \Sexpr{round(CAL_table_all_bb["+48","CAL 5F"],2)}$\%$.
-So the larger the difference between these numbers and the corresponding numbers for the industry indicated in Tables~\ref{tbl:IndustriesBB} and \ref{tbl:IndustriesBB_cal}, the larger the excess returns in the industry removed.
-For example, using IRATS, deleting the software industry lowers the CAR from \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ to \Sexpr{round(tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$, a \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"] - tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$ decline.
-This is the largest decline in Table~\ref{tbl:IndustriesBB}, indicating that buybacks in the software industry are followed by the largest excess returns.
-However, deleting Retail, Insurance, Machinery, Meals and especially Chemical stocks improves the excess returns.
-Of course, these differences could be explained by differences in U-index levels or other indicators of the likelihood of misvaluation, a topic we turn to next.
 
@@
 
-%The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \citep{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns.
-However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks.
-Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing.
-Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks.
-Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).
-So our results are also consistent with the \cite{Stambaugh2015} interpretation.
-
 \subsection{Volatility and excess returns}
@@
 We use the most recent data pre-announce, and make the winsorization and other adjustments as in the websites above.
-Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.}
-%``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. 
-``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement.
+Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.} ``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement.
 Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available\footnote{As this SDC data was not available for many events, we did not consider the in the U-index calculation.} (this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.
@@
 @
-
-%Finally, Table~\ref{tbl:EUhedgedBB}, like Table~\ref{tbl:allhedgedBB}, shows the monthly and yearly returns of a five-factors hedged strategy investing only in the high EU-index repurchase events.
-The table shows the robustness of the abnormal returns over time.
-Specifically, in \Sexpr{sum(tmp[,13] > 0)} out of the \Sexpr{sum(tmp[,13] != 0)} years the hedged strategy generates positive excess returns.
-As in Table~\ref{tbl:allhedgedBB},  \Sexpr{rownames(tmp)[which.min(tmp1[,13])]} has a large a loss of \Sexpr{tmp[which.min(tmp1[,13]),13]}$\%$ and the best year is \Sexpr{rownames(tmp)[which.max(tmp[,13])]} with an impressive \Sexpr{tmp[which.max(tmp[,13]),13]}$\%$.
 
@@
 
-if (0){
-  colnames(ISS_for_BB_Abn_table)[1]<- "Post-buyback SEOs"
-  colnames(ISS_for_BB_Abn_table)[4]<- "Other SEOs"
-  printLatexTable(ISS_for_BB_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
-                  label  = "tbl:BBISSexitAfter",
-                  columns= c("After a Buyback","No Prior Buyback"),
-                  title  ="Issue announcements with and without a prior buyback",
-                  caption = "The table presents the long-run abnormal returns (CAR) for firms after issue announcements for events with and without a prior buyback announcement within 48 months.
-We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.",
-
-lastSpecial=T,
-titleontop = T
-  )
-}
 @
@@
 %%%%%%%%
-
-%\clearpage
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-if (0){
-  printLatexTable2(
-    Exit_on_BB_Abn_table[reported_times,],
-    Exit_on_BB_Abn_table_cal[reported_times,],
-    columns = c("No Buyback","Buyback"),
-    title="SEOs with and without subsequent buyback",
-    title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-    title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-    caption="The table presents the long-run abnormal returns for firms after issue announcements with and without a subsequent buyback announcement on the full sample for different periods in time.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-
-label = "tbl:ISSBBexit",
-bigtitleontop=T,
-titleontop=T,
-scale=1,
-lastSpecial=T,
-dorotate=F
-  )
-
-  printLatexTable(BB_for_ISS_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
-                  label  = "tbl:ISSBBexitAfter",
-                  columns= c("post-Issue Buybacks: CAR","Other Buybacks: CAR"),
-                  title  ="Long-run IRATS abnormal return of only the buybacks that are announced within 48 months after an SEO announcement versus the remaining buyback events.",lastSpecial=T)
-}
-@
 
@@
 )
-
-if (0){
-  tmp = ISStable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-  colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2015: CAR","t-stat","p-value","2008-2015: CAR","t-stat","p-value")
-  tmp2 = ISStable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-  colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2015: CAL","t-stat","p-value","2008-2015: CAL","t-stat","p-value")
-
-  printLatexTable2(
-    tmp,
-    tmp2,
-    columns= c("1985-1990","1991-2000","2001-2015","2008-2015"),
-    title="SEOs returns over different time periods",
-    title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-    title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-    caption="Long-run IRATS cumulative (Panel~A) and Calendar method monthly (Panel~B) abnormal return after issue announcements for different time periods.",
-    label = "tbl:PastFindingsTimeISS",
-    bigtitleontop=T,
-    titleontop=T,
-    scale=1,
-    lastSpecial=T,
-    dorotate=T
-  )
-}
-
 @
@@
 
-if (0){
-  paste(printLatexTable(BB_cal_table_undertime[reported_times,1:12],
-                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
-                        rowcolumn="1985-1990",
-                        title="Calendar Method abnormal returns after open market repurchase announcements  for under and over valued companies over different time periods.",
-                        label="tbl:PastFindingsTimeUnderBBcal",
-                        scale = 0.8,close=F,lastSpecial=T
-  ),
-  printLatexTable(BB_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(BB_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(BB_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
-
-}
-if (0){
-  paste(printLatexTable(ISStable_undertime[reported_times,1:12],
-                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
-                        rowcolumn="1985-1990",
-                        title="Long-run IRATS abnormal returns after issue announcements  for under and over valued companies over different time periods.",
-                        label="tbl:PastFindingsTimeUnderISS",
-                        scale = 0.9,close=F,lastSpecial=T
-  ),
-  printLatexTable(ISStable_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISStable_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISStable_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
-
-  paste(printLatexTable(ISS_cal_table_undertime[reported_times,1:12],
-                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
-                        rowcolumn="1985-1990",
-                        title="Calendar Method abnormal returns after issue announcements  for under and over valued companies over different time periods.",
-                        label="tbl:PastFindingsTimeUnderISScal",
-                        scale = 0.9,close=F,lastSpecial=T
-  ),
-  printLatexTable(ISS_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISS_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISS_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
-}
 @
@@
 \clearpage
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
-tmp_cal = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,4:6] ))
-
-if (0){
-  printLatexTable2(
-    tmp[reported_times,1:(3*6)],
-    tmp[reported_times,(3*6+1):36],
-    columns= names(industry_BB)[1:6],
-    columns2= names(industry_BB)[7:12],
-    title="Buyback IRATS Abnormal Returns: Industry Robustness",
-    #title1 = "",
-    #title2 = "",
-    caption=paste("The table presents the long-run abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample.
-We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-The 48 month abnormal return for the full sample is equal to ",round(IRATS_table_all_bb["+48","CAR 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),
-
-label = "tbl:IndustriesBB",
-bigtitleontop=T,
-metric1 = "CAR", metric2 = "CAR",
-#titleontop=T,
-scale=1,
-lastSpecial=T,
-dorotate=T
-  )
-
-  printLatexTable2(
-    tmp_cal[reported_times,1:(3*6)],
-    tmp_cal[reported_times,(3*6+1):36],
-    columns= names(industry_BB)[1:6],
-    columns2= names(industry_BB)[7:12],
-    title="Buyback Calendar Method Abnormal Returns: Industry Robustness",
-    #title1 = "",
-    #title2 = "",
-    caption=paste("The table presents the long-run calendar method abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample.
-Specifically, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors (the difference between the risk-free rate and the return on the equally weighted CRSP index, the monthly return on the size, book-to-market factor, profitability factor and investment factor in month) as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
-The 48 month abnormal return for the full sample is equal to ",round(CAL_table_all_bb["+48","CAL 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),
-    label = "tbl:IndustriesBB_cal",
-    bigtitleontop=T,
-    metric1 = "AR", metric2 = "AR",
-    #titleontop=T,
-    scale=1,
-    lastSpecial=T,
-    dorotate=T
-  )
-
-}
-@
-
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-if (0){
-  latex_render_data_frame(
-    pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)), 
-    title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all buybacks",
-    caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all buybacks.
-The holding period for each buyback is 12 months per event.",
-    label="tbl:allhedgedBB", 
-    columns=NULL,
-    bigtitleontop = T,
-    show_rownames=TRUE,
-    scale = 0.9,
-    digits=1,
-    lastSpecial=F,dorotate=F
-  )
-}
-@
 
@@
 
-#\\textit{Missed (Beat) EPS} measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. 
 EU_relations <- EU_relations[-which(rownames(EU_relations) %in% c("Missed EPS","Beat EPS")),]
-
 rownames(EU_relations)[1] <- "Low Leverage"
@@
 
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-if (0){
-  latex_render_data_frame(
-    pnl_matrix(remove_initialization_time(High_EU_BB_Hedged,min_date=FirstTrade)), 
-    title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all high EU-index buybacks",
-    caption="Monthly and yearly  five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all high EU-index buybacks only.
-Holding period for each buyback is 12 months per event.",
-    label="tbl:EUhedgedBB", 
-    columns=NULL,
-    bigtitleontop = T,
-    show_rownames=TRUE,
-    scale = 0.9,
-    digits=1,
-    lastSpecial=F,dorotate=F
-  )
-}
-@
-
-%\clearpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\clearpage
-
-%\begin{figure}[H]
-%\centering
-<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-if (0){
-  par(mfrow=c(2,2), mar=c(2.3,4,2.3,4))
-
-  IRATS_table_all_bb_plot = IRATS_table_all_bb
-  IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] <- -IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")]
-  IRATS_table_all_iss_plot = IRATS_table_all_iss
-  IRATS_table_all_iss_plot[rownames(IRATS_table_all_iss_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] <- -IRATS_table_all_iss_plot[rownames(IRATS_table_all_iss_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")]
-  IRATS_table_all_bb_undervaluation_plot = IRATS_table_all_bb_undervaluation
-  IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]
-  #IRATS_table_all_iss_undervaluation_plot = IRATS_table_all_iss_undervaluation
-  #IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]
-
-  ylimit = c(min(
-    #IRATS_table_all_bb_plot[reported_times_plots,"CAR 3F"], 
-    IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], 
-    #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
-    #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
-    IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
-    IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR5F"]), 
-    max(
-      #IRATS_table_all_bb_plot[reported_times_plots,"CAR 3F"], 
-      IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], 
-      #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
-      #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
-      IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
-      IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR5F"])
-  )
-
-  plot(IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="A. Buybacks - All", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #lines(IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"],  lty = 2,lwd=1.4)
-  abline(v=which(reported_times_plots == "0"), lwd=0.5)
-  abline(h=0, lwd=0.5)
-
-  plot(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="C. Buybacks - high/low U-index", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"U:CAR3F"]
-  #points(tmp, pch=0)
-  #lines(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR3F"],lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"O:CAR3F"]
-  #points(tmp, pch=3)
-  #lines(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"],lty = 3, lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"U:CAR5F"]
-  #points(tmp, pch=0)
-  lines(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR5F"],  lty = 3,lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"O:CAR5F"]
-  #points(tmp, pch=3)
-  abline(v=which(reported_times_plots == "0"), lwd=0.5)
-  abline(h=0, lwd=0.5)
-
-  # SEOs
-  ylimit = c(min(
-    #IRATS_table_all_iss_plot[reported_times_plots,"CAR 3F"], 
-    IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"]#, 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR5F"]
-  ), 
-  max(
-    #IRATS_table_all_iss_plot[reported_times_plots,"CAR 3F"], 
-    IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"]#, 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR5F"]
-  )
-  )
-
-  plot(IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="B. SEOs - All", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #lines(IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"],  lty = 2,lwd=1.4)
-  abline(v=which(reported_times_plots == "0"), lwd=0.5)
-  abline(h=0, lwd=0.5)
-
-}
-if (0){
-  plot(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="SEOs - Under/Over-valuation", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"U:CAR3F"]
-  #points(tmp, pch=0)
-  #lines(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR3F"],lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"O:CAR3F"]
-  #points(tmp, pch=3)
-  #lines(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"],lty = 3, lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"U:CAR5F"]
-  #points(tmp, pch=0)
-  lines(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR5F"],  lty = 3,lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"O:CAR5F"]
-  #points(tmp, pch=3)
-  abline(v=which(reported_times_plots == "0"), lwd=0.5)
-  abline(h=0, lwd=0.5)
-}
-@
-%\caption{Long-run five factors cumulative average abnormal returns (CAR) of buyback and SEO portfolios.
-The x-axis indicates months from the date of the event announcement.
-Panel~A shows all buyback events, whereas Panel C shows all high (solid line) and low (dashed lines) U-index buyback events.
-Panel~B includes all SEOs.}
-%\label{fig:pastall}
-%\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   abline(h = 5*iter)
-#par(new = TRUE)
-#plot(market_index,type="l", col="red", lwd = 4, lty=3,axes = FALSE, xlab = "", ylab = "")
-#points(market_index, pch=1, col="red", lwd=2)
-#axis(side=4, at = pretty(range(market_index)))
-#mtext("Market Index", side=4, line=3)
-
-if (0){
-  df.bar <- barplot(ISS_with_BB_later_total,col=c("grey"),main = "Issues with Follow-up Buyback", ylab = "Percent", xlab = "Years",las=2,space=0.5, cex.names=1)
-  for (iter in 1:floor(max(ISS_with_BB_later_total)/5))
-    abline(h = 5*iter)
-  par(new = TRUE)
-  plot(market_index,type="l", col="red", lwd = 4, lty=3,axes = FALSE, xlab = "", ylab = "")
-  points(market_index, pch=1, col="red", lwd=2)
-  axis(side=4, at = pretty(range(market_index)))
-  mtext("Market Index", side=4, line=3)
-}
+
 @
@@
        cex=1,bg="white",inset=0.01)
-
-if (0){
-  ylimit = c(min(Exit_on_SEO_Abn_table_cal[reported_times_plots,1], Exit_on_SEO_Abn_table_cal[reported_times_plots,4]), 
-             max(Exit_on_SEO_Abn_table_cal[reported_times_plots,1], Exit_on_SEO_Abn_table_cal[reported_times_plots,4]))
-  plot(Exit_on_SEO_Abn_table_cal[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: Buybacks with SEO: Calendar Method", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  lines(Exit_on_SEO_Abn_table_cal[reported_times_plots,4],lty = 2,lwd=1.4)
-  abline(h=0, lwd=0.5)
-  abline(v=which(reported_times_plots == "0"), lwd=0.5)
-}
 
@@
 #### SEOs NOW (We combine the plots)
-if (0){ 
-  reported_times_plots_tmp = reported_times_plots
-  reported_times_plots = reported_times_plots[8:length(reported_times_plots)]
-
-  ylimit = c(min(Exit_on_BB_Abn_table[reported_times_plots,1], Exit_on_BB_Abn_table[reported_times_plots,4]), 
-             max(Exit_on_BB_Abn_table[reported_times_plots,1], Exit_on_BB_Abn_table[reported_times_plots,4]))
-  plot(Exit_on_BB_Abn_table[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: SEO with Buyback IRATS CAR", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  lines(Exit_on_BB_Abn_table[reported_times_plots,4],lty = 2,lwd=1.4)
-  abline(h=0, lwd=0.5)
-  abline(v=which(reported_times_plots == "0"), lwd=0.5)
-
-  if (0){
-    ylimit = c(min(Exit_on_BB_Abn_table_cal[reported_times_plots,1], Exit_on_BB_Abn_table_cal[reported_times_plots,4]), 
-               max(Exit_on_BB_Abn_table_cal[reported_times_plots,1], Exit_on_BB_Abn_table_cal[reported_times_plots,4]))
-    plot(Exit_on_BB_Abn_table_cal[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="SEO with Buyback: Calendar", lwd=1.4)
-    axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-    axis(2,cex.axis=1.1)
-    lines(Exit_on_BB_Abn_table_cal[reported_times_plots,4],lty = 2,lwd=1.4)
-    abline(h=0, lwd=0.5)
-    abline(v=which(reported_times_plots == "0"), lwd=0.5)
-  }
-
-  reported_times_plots = reported_times_plots_tmp
-
-  pnl_Exit_Hedged = ISS_BB_Exit_Hedged
-  pnl_NoExit_Hedged = ISS_BB_NoExit_Hedged
-  plot(cumsum(100*pnl_NoExit_Hedged),type="l",ylab="CAR", xlab = "",main = "Strategy Returns",axes = FALSE, ylim=c(min(c(100*cumsum(pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged))), max(c(cumsum(100*pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  lines(cumsum(100*pnl_Exit_Hedged),lty = 2,lwd=1.4)
-  for (iter in floor(100*min(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/50):floor(100*max(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/50))
-    abline(h = 50*iter)
-  #plot_crisis_dates(pnl_NoExit_Hedged) 
-}
 @
@@
 Dashed line is if we exit these positions the month after the subsequent SEO announcement.
-%(Average annual returns: \Sexpr{round(pnl_stats(BB_ISS_Exit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(BB_ISS_Exit_Hedged)[3],1)}), and solid line is if we do not (Average annual returns: \Sexpr{round(pnl_stats(BB_ISS_NoExit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(BB_ISS_NoExit_Hedged)[3],1)}).
-%{\bf Bottom Panel~B: Left:} Five factor IRATS CAR for all SEO events that had no subsequent buyback event within the 48 months post SEO announcement (black line) versus those that did have (dashed line).
-{\bf Right:} Abnormal (five-factor rolling hedged) returns of SEO portfolio for only the \Sexpr{length(ISS_with_BB_later)} events for which there was a subsequent buybacks announcement within 4 years.
-Dashed line is if we exit these positions  the month after the subsequent buyback announcement  (Average annual returns: \Sexpr{round(pnl_stats(ISS_BB_Exit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(ISS_BB_Exit_Hedged)[3],1)}), and solid line is if we do not (Average annual returns: \Sexpr{round(pnl_stats(ISS_BB_NoExit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(ISS_BB_NoExit_Hedged)[3],1)}).
 }
@@
 \end{landscape}
-%\begin{figure}[H]
-%\centering
-%<<  fig.width=10, fig.height=5, out.width='\\textwidth', echo=F >>=
-%df.bar <- barplot(industry_tableISS,col=c("grey"),main = "", ylab = "Issues", xlab = "",las=2,space=0.9, cex.names=1)
-%for (iter in 1:floor(max(industry_tableISS)/100))
-%  abline(h = 100*iter)
-%@
-%\caption{Number of issue announcements per industry.  }
-%\label{fig:industryeventsISS}
-%\end{figure}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\clearpage
-%\subsection{Idiosyncratic Risk and Buybacks}
-%\label{app:idiosync}
-
-%\begin{figure}[H]
-%\centering
-<< R2thresholds, fig.width=7, fig.height=4, out.width='\\textwidth', echo=F >>=
-if (0){
-  #par(mfrow=c(2,1), mar=c(2.7,4.5,2.7,4.5))
-  Market_Monthly_index = Market_Monthly
-  names(Market_Monthly_index) <- paste(str_sub(names(Market_Monthly_index),start=1,end=4),str_sub(names(Market_Monthly_index),start=6,end=7),sep="")
-
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[High_Idiosyncr_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$Rsq_returns[High_Idiosyncr_eventsBB]
-  names(tmp)<-all_dates
-  R2_thresholds_up_plot = sapply(names(Market_Monthly_index), function(i){
-    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
-  })
-  R2_thresholds_up_plot = R2_thresholds_up_plot[!is.na(R2_thresholds_up_plot)]
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[Low_Idiosyncr_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$Rsq_returns[Low_Idiosyncr_eventsBB]
-  names(tmp)<-all_dates
-  R2_thresholds_down_plot = sapply(names(Market_Monthly_index), function(i){
-    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
-  })
-  R2_thresholds_down_plot = R2_thresholds_down_plot[!is.na(R2_thresholds_down_plot)]
-
-  R2_thresholds_down_plot = R2_thresholds_down_plot[intersect(names(R2_thresholds_down_plot), names(R2_thresholds_up_plot))]
-  R2_thresholds_up_plot = R2_thresholds_up_plot[intersect(names(R2_thresholds_down_plot), names(R2_thresholds_up_plot))]
-  R2_thresholds_up_plot = R2_thresholds_up_plot[intersect(names(R2_thresholds_up_plot), names(Market_Monthly_index))]
-  R2_thresholds_down_plot = R2_thresholds_down_plot[names(R2_thresholds_up_plot)]
-  Market_Monthly_index = Market_Monthly_index[names(R2_thresholds_up_plot)]
-  market_index = 100*(1+cumprod(1+Market_Monthly))
-
-  plot(R2_thresholds_up_plot, col="black", axes=FALSE, ylab="five-factor R square", main = "Buybacks Average five-factor R square", xlab = "Time",ylim=c(min(c(R2_thresholds_down_plot[!is.na(R2_thresholds_down_plot)],R2_thresholds_up_plot[!is.na(R2_thresholds_up_plot)])), max(c(R2_thresholds_down_plot[!is.na(R2_thresholds_down_plot)],R2_thresholds_up_plot[!is.na(R2_thresholds_up_plot)]))),  cex.lab=1.1, type="l", lwd=2)
-  lines(R2_thresholds_down_plot, col="black", lwd=2,lty="dotted")
-  axis(1,at=seq(1,length(Market_Monthly_index),length.out=20),labels=str_sub(names(Market_Monthly_index)[seq(1,length(Market_Monthly_index),length.out=20)], start=1,end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #par(new = TRUE)
-  #plot(market_index,type="l", lwd = 2, axes = FALSE, xlab = "", ylab = "")
-  #axis(side=4, at = pretty(range(market_index)))
-  #mtext("Market Index", side=4, line=3)
-}
-@
-%\caption{Monthly average (across all buybacks events that month) $R^2$ defined using all buybacks events announced in a given month.
-Solid line is for high idiosyncratic events, dotted  line is for low.
-%Note that as the idiosyncratic risk is estimated using 6 months returns before announcement, there is a time shift relative to the market returns. 
-%}
-%\label{fig:R2thresholds}
-%\end{figure}
-
-%\clearpage
-
-%\clearpage
-
-%\begin{figure}[H]
-%\centering
-<< badpreviousR2, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-#par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))
-if (0){
-  plot(cumsum(100*High_Idiosyncr_BB_Hedged),type="l",ylab="CAR", xlab = "Time",main = "",  lwd=2, axes = FALSE, 
-       ylim=c(min(c(cumsum(100*High_Idiosyncr_BB_Hedged),cumsum(100*Low_Idiosyncr_BB_Hedged),cumsum(100*High_Idiosyncr_BB_Hedged48m),cumsum(100*Low_Idiosyncr_BB_Hedged48m))), 
-              max(c(cumsum(100*High_Idiosyncr_BB_Hedged),cumsum(100*Low_Idiosyncr_BB_Hedged),cumsum(100*High_Idiosyncr_BB_Hedged48m),cumsum(100*Low_Idiosyncr_BB_Hedged48m)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(High_Idiosyncr_BB_Hedged),length.out=10),labels=str_sub(names(High_Idiosyncr_BB_Hedged)[seq(1,length(High_Idiosyncr_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  lines(cumsum(100*Low_Idiosyncr_BB_Hedged),lty="dotted", lwd=2)
-  lines(cumsum(100*High_Idiosyncr_BB_Hedged48m),lty="dashed", lwd=2)
-  lines(cumsum(100*Low_Idiosyncr_BB_Hedged48m),lty="dotdash", lwd=2)
-  for (iter in 1:floor(100*max(c(cumsum(High_Idiosyncr_BB_Hedged),cumsum(Low_Idiosyncr_BB_Hedged)))/50))
-    abline(h = 50*iter)
-  abline(h = 200)
-  #plot_crisis_dates(High_Idiosyncr_BB_Hedged)
-  legend(x="topleft",
-         c("12 Month High Idiosyncratic","12 Month Low Idiosyncratic","48 Month High Idiosyncratic","48 Month Low Idiosyncratic"),
-         lty=c("solid","dotted","dashed","dotdash"),
-         lwd=c(2,2,2,2),
-         cex=1,bg="white",inset=0.01)
-
-  if (0){
-    plot(cumsum(100*High_Idiosyncr_ISS_Hedged),type="l",ylab="CAR", xlab = "Time",main = "SEOs", axes = FALSE, 
-         ylim=c(min(c(cumsum(100*High_Idiosyncr_ISS_Hedged),cumsum(100*Low_Idiosyncr_ISS_Hedged),cumsum(100*High_Idiosyncr_ISS_Hedged48m),cumsum(100*Low_Idiosyncr_ISS_Hedged48m))), 
-                max(c(cumsum(100*High_Idiosyncr_ISS_Hedged),cumsum(100*Low_Idiosyncr_ISS_Hedged),cumsum(100*High_Idiosyncr_ISS_Hedged48m),cumsum(100*Low_Idiosyncr_ISS_Hedged48m)))), cex.lab=1.1)
-    axis(1,at=seq(1,length(High_Idiosyncr_ISS_Hedged),length.out=10),labels=str_sub(names(High_Idiosyncr_ISS_Hedged)[seq(1,length(High_Idiosyncr_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-    axis(2,cex.axis=1.1)
-    lines(cumsum(100*Low_Idiosyncr_ISS_Hedged), col="red")
-    lines(cumsum(100*High_Idiosyncr_ISS_Hedged48m), col="blue")
-    lines(cumsum(100*Low_Idiosyncr_ISS_Hedged48m), col="green")
-    for (iter in 1:floor(100*max(c(cumsum(High_Idiosyncr_ISS_Hedged),cumsum(Low_Idiosyncr_ISS_Hedged)))/50))
-      abline(h = 50*iter)
-    #plot_crisis_dates(High_Idiosyncr_ISS_Hedged)
-  }
-}
-@
-%\caption{Buybacks: High versus Low Idiosyncratic Events.
-Returns of five-factor rolling hedged portfolio for only the buyback events for high and low idiosyncratic company.
-Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio; dashed line is ``high'' and a 48-months holding portfolio, dotted-dash line is ``low'' and a 48-months portfolio.
-%Red line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged)[3],1)}.
-Black line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged)[3],1)}.
-Green line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged48m)[3],1)}.
-Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged48m)[3],1)}.
-%We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
-%Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
-%}
-%\label{fig:badpreviousR2}
-%\end{figure}
 
@@
 
-%\clearpage
-%\subsection{Volatility and Buybacks}
-%\label{app:volatility}
-
-%\begin{figure}[H]
-%\centering
-<< VOLthresholds, fig.width=7, fig.height=4, out.width='\\textwidth', echo=F >>=
-#par(mfrow=c(2,1), mar=c(2.7,4.5,2.7,4.5))
-if (0){
-  Market_Monthly_index = Market_Monthly
-  names(Market_Monthly_index) <- paste(str_sub(names(Market_Monthly_index),start=1,end=4),str_sub(names(Market_Monthly_index),start=6,end=7),sep="")
-
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[High_VOL_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$pre_vol[High_VOL_eventsBB]
-  names(tmp)<-all_dates
-  VOL_thresholds_up_plot = sapply(names(Market_Monthly_index), function(i){
-    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
-  })
-  VOL_thresholds_up_plot = 100*VOL_thresholds_up_plot[!is.na(VOL_thresholds_up_plot)]
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[Low_VOL_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$pre_vol[Low_VOL_eventsBB]
-  names(tmp)<-all_dates
-  VOL_thresholds_down_plot = sapply(names(Market_Monthly_index), function(i){
-    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
-  })
-  VOL_thresholds_down_plot = 100*VOL_thresholds_down_plot[!is.na(VOL_thresholds_down_plot)]
-
-  VOL_thresholds_down_plot = VOL_thresholds_down_plot[intersect(names(VOL_thresholds_down_plot), names(VOL_thresholds_up_plot))]
-  VOL_thresholds_up_plot = VOL_thresholds_up_plot[intersect(names(VOL_thresholds_down_plot), names(VOL_thresholds_up_plot))]
-  VOL_thresholds_up_plot = VOL_thresholds_up_plot[intersect(names(VOL_thresholds_up_plot), names(Market_Monthly_index))]
-  VOL_thresholds_down_plot = VOL_thresholds_down_plot[names(VOL_thresholds_up_plot)]
-  Market_Monthly_index = Market_Monthly_index[names(VOL_thresholds_up_plot)]
-  market_index = 100*(1+cumprod(1+Market_Monthly))
-
-  plot(VOL_thresholds_up_plot, col="black", axes=FALSE, ylab="Average Volatility (percent)", main = "Buybacks pre-Announce Returns Volatility", xlab = "Time",ylim=c(min(c(VOL_thresholds_down_plot,VOL_thresholds_up_plot)), max(c(VOL_thresholds_down_plot,VOL_thresholds_up_plot))),  cex.lab=1.1, type="l", lwd=1.2)
-  lines(VOL_thresholds_down_plot, col="black", lwd=2,lty="dotted")
-  axis(1,at=seq(1,length(Market_Monthly_index),length.out=20),labels=str_sub(names(Market_Monthly_index)[seq(1,length(Market_Monthly_index),length.out=20)], start=1,end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #par(new = TRUE)
-  #plot(market_index,type="l", lwd = 2, axes = FALSE, xlab = "", ylab = "")
-  #axis(side=4, at = pretty(range(market_index)))
-  #mtext("Market Index", side=4, line=3)
-}
-@
-%\caption{Monthly average (across all buybacks events that month) volatility (standard deviation of daily$\%$ returns over 6 months before announcement) defined using all buybacks events announced in a given month.
-Solid line is for high idiosyncratic events, dotted line is for low.
-%Note that as the volatility is estimated using 6 months returns before announcement, there is a time shift relative to the market returns.  
-%}
-%\label{fig:VOLthresholds}
-%\end{figure}
-
-%\begin{figure}[H]
-%\centering
-<< badpreviousVOL, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-#par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))
-if (0){
-  plot(cumsum(100*High_VOL_BB_Hedged),type="l",ylab="CAR", xlab = "Time",main = "", lwd=2, axes = FALSE, 
-       ylim=c(min(c(cumsum(100*High_VOL_BB_Hedged),cumsum(100*Low_VOL_BB_Hedged),cumsum(100*High_VOL_BB_Hedged48m),cumsum(100*Low_VOL_BB_Hedged48m))), 
-              max(c(cumsum(100*High_VOL_BB_Hedged),cumsum(100*Low_VOL_BB_Hedged),cumsum(100*High_VOL_BB_Hedged48m),cumsum(100*Low_VOL_BB_Hedged48m)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(High_VOL_BB_Hedged),length.out=10),labels=str_sub(names(High_VOL_BB_Hedged)[seq(1,length(High_VOL_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  lines(cumsum(100*Low_VOL_BB_Hedged),lty="dotted", lwd=2)
-  lines(cumsum(100*High_VOL_BB_Hedged48m),lty="dashed", lwd=2)
-  lines(cumsum(100*Low_VOL_BB_Hedged48m),lty="dotdash", lwd=2)
-  for (iter in 1:floor(100*max(c(cumsum(High_VOL_BB_Hedged),cumsum(Low_VOL_BB_Hedged)))/50))
-    abline(h = 50*iter)
-  #plot_crisis_dates(High_VOL_BB_Hedged)
-  legend(x="topleft",
-         c("12 Month High Volatility","12 Month Low Volatility","48 Month High Volatility","48 Month Low Volatility"),
-         lty=c("solid","dotted","dashed","dotdash"),
-         lwd=c(2,2,2,2),
-         cex=1,bg="white",inset=0.01)
-
-  if (0){
-    plot(cumsum(100*High_VOL_ISS_Hedged),type="l",ylab="CAR", xlab = "Time",main = "SEOs", lwd=2, axes = FALSE, 
-         ylim=c(min(c(cumsum(100*High_VOL_ISS_Hedged),cumsum(100*Low_VOL_ISS_Hedged),cumsum(100*High_VOL_ISS_Hedged48m),cumsum(100*Low_VOL_ISS_Hedged48m))), 
-                max(c(cumsum(100*High_VOL_ISS_Hedged),cumsum(100*Low_VOL_ISS_Hedged),cumsum(100*High_VOL_ISS_Hedged48m),cumsum(100*Low_VOL_ISS_Hedged48m)))), cex.lab=1.1)
-    axis(1,at=seq(1,length(High_VOL_ISS_Hedged),length.out=10),labels=str_sub(names(High_VOL_ISS_Hedged)[seq(1,length(High_VOL_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-    axis(2,cex.axis=1.1)
-    lines(cumsum(100*Low_VOL_ISS_Hedged),lty="dotted", lwd=2)
-    lines(cumsum(100*High_VOL_ISS_Hedged48m),lty="dashed", lwd=2)
-    lines(cumsum(100*Low_VOL_ISS_Hedged48m),lty="dotdash", lwd=2)
-    for (iter in 1:floor(100*max(c(cumsum(High_VOL_ISS_Hedged),cumsum(Low_VOL_ISS_Hedged)))/50))
-      abline(h = 50*iter)
-    #plot_crisis_dates(High_VOL_ISS_Hedged)
-  }
-}
-@
-%\caption{Buybacks: High vs Low Volatility Events.
-Returns of five-factor rolling hedged portfolio for only the buyback events for high and low volatility company.
-Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio; dashed line is ``high'' and a 48-months holding portfolio, dotted-dash line is ``low'' and a 48-months portfolio.
-%Red line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged)[3],1)}.
-Black line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged)[3],1)}.
-Green line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged48m)[3],1)}.
-Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged48m)[3],1)}.
-%We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
-%Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
-%}
-%\label{fig:badpreviousVOL}
-%\end{figure}
-
 \begin{figure}[H]
@@
 << fig.width=10, fig.height=4, out.width='\\textwidth', echo=F >>=
-#par(mfrow=c(2,1), mar=c(2.3,4,2.3,4))
-#valuation_index_bb[which(valuation_index_bb==2)]<-3 # there is one company here. need to check why
 tmp = table(EUindex_bb)
@@
 barplot(tmp,main = "", ylab = "Number of Announcements", xlab = "",las=2,space=0.5, cex.names=1)
-#tmp = table(valuation_index_iss)
-#tmp = structure(as.numeric(tmp), .Names = names(tmp))
-#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=1)
 rm("tmp")
@@
 \end{figure}
-
-%\begin{figure}[H]
-%\centering
-<< badpreviousEU, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-if (0){
-  #par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))
-  plot(cumsum(100*High_EU_BB_Hedged),type="l",ylab="CAR", xlab = "Time",main = "", lwd=2, axes = FALSE, 
-       ylim=c(min(c(cumsum(100*High_EU_BB_Hedged),cumsum(100*Low_EU_BB_Hedged),cumsum(100*High_EU_BB_Hedged48m),cumsum(100*Low_EU_BB_Hedged48m))), 
-              max(c(cumsum(100*High_EU_BB_Hedged),cumsum(100*Low_EU_BB_Hedged),cumsum(100*High_EU_BB_Hedged48m),cumsum(100*Low_EU_BB_Hedged48m)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(High_EU_BB_Hedged),length.out=10),labels=str_sub(names(High_EU_BB_Hedged)[seq(1,length(High_EU_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  lines(cumsum(100*Low_EU_BB_Hedged),lty="dotted", lwd=2)
-  lines(cumsum(100*High_EU_BB_Hedged48m),lty="dashed", lwd=2)
-  lines(cumsum(100*Low_EU_BB_Hedged48m),lty="dotdash", lwd=2)
-  for (iter in 1:floor(100*max(c(cumsum(High_EU_BB_Hedged),cumsum(Low_EU_BB_Hedged)))/50))
-    abline(h = 50*iter)
-  #plot_crisis_dates(High_EU_BB_Hedged)
-  legend(x="topleft",
-         c("12 Month High EU","12 Month Low EU","48 Month High EU","48 Month Low EU"),
-         lty=c("solid","dotted","dashed","dotdash"),
-         lwd=c(2,2,2,2),
-         cex=1,bg="white",inset=0.01)
-
-  if (0){
-    plot(cumsum(100*High_EU_ISS_Hedged),type="l",ylab="CAR", xlab = "Time",main = "SEOs", axes = FALSE, 
-         ylim=c(min(c(cumsum(100*High_EU_ISS_Hedged),cumsum(100*Low_EU_ISS_Hedged),cumsum(100*High_EU_ISS_Hedged48m),cumsum(100*Low_EU_ISS_Hedged48m))), 
-                max(c(cumsum(100*High_EU_ISS_Hedged),cumsum(100*Low_EU_ISS_Hedged),cumsum(100*High_EU_ISS_Hedged48m),cumsum(100*Low_EU_ISS_Hedged48m)))), cex.lab=1.1)
-    axis(1,at=seq(1,length(High_EU_ISS_Hedged),length.out=10),labels=str_sub(names(High_EU_ISS_Hedged)[seq(1,length(High_EU_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-    axis(2,cex.axis=1.1)
-    lines(cumsum(100*Low_EU_ISS_Hedged), col="red")
-    lines(cumsum(100*High_EU_ISS_Hedged48m), col="blue")
-    lines(cumsum(100*Low_EU_ISS_Hedged48m), col="green")
-    for (iter in 1:floor(100*max(c(cumsum(High_EU_ISS_Hedged),cumsum(Low_VOL_ISS_Hedged)))/50))
-      abline(h = 50*iter)
-    #plot_crisis_dates(High_VOL_ISS_Hedged)
-  }
-}
-@
-%\caption{Buybacks: High vs Low EU-index Events.
-Returns of five-factor rolling hedged portfolio for only the buyback events for high and low EU-index companies.
-We define low EU-index firms those for which the EU-index is 0-1, and high for which it is 5-6 (note that the index takes values from 0 to 6).
-Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio; dashed line is ``high'' and a 48-months holding portfolio, dotted-dash line is ``low'' and a 48-months portfolio.
-%Red line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[3],1)}.
-Black line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[3],1)}.
-Green line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged48m)[3],1)}.
-Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[3],1)}.
-%We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
-%Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
-%}
-%\label{fig:badpreviousEU}
-%\end{figure}
 

### 2016-05-03 manuscriptJF.Rnw
minor

--- 2016-03-19 bb_issuers.Rnw
@@
 << eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-#rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
 #dev.off();
-#library(knitr); knit2pdf('bb_issuers.Rnw', texi2dvi='texi2dvi'); file.remove(paste("bb_issuers",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
+#library(knitr); knit2pdf('manuscriptJF.Rnw', texi2dvi='texi2dvi'); file.remove(paste("manuscriptJF",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
 #dir.create("tmpfiles") # need to comment this if the directory already exists
-
-#load("tmpfiles/bb_issuersALL.Rdata")
-reload_data = 0
-
 # Then to make it into Word: 
-# pandoc -s bb_issuers.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx
-
-generate_all_data = 0 # set this to 1 if the data need to be re-generated from the csv's even though they already exist as .Rdata. 
-# TIME ALIGNMENT IS KEY, SO WE HAVE A SEPARATE PART OF THE CODE FOR THIS
-time_align_all_data = 0
-# Some basic data generation that we need across events
-rerun_buyback_data_code <- 0
-rerun_issuers_data_code <- 0
-# If we generate the cross-events data again
-get_crossevent_data <- 0 # Old stuff, not used for now
-# report_code is only customized to change the "high U-index" and "low U-index" companies, nothing else. Everything else is done in report_data.R
-rerun_buyback_report_code <- 0
-rerun_issuers_report_code <- 0
-# All the RNW data
-generate_rnw_data = 0
-
-source("lib_helpers.R")
-source("latex_code.R")
-source("dataset/indices_and_factors/ff_industries_sic.R")
-source("business_data_clean.R")
+# system("pandoc -s manuscriptJF.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx")
+
+rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
+
+generate_all_data = 0 # set this to 1 if the data need to be re-generated from scratch
+generate_rnw_data = 0 # set this to 1 to generate the .Rnw data
+
+if (generate_all_data == 1){
+  source("create_bbissuers_data.R")
+}
+if (generate_rnw_data == 1){
+  source("bb_issuers_new.R")
+} else {
+  load("bb_issuers_new.Rdata")
+}
+
+source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
+source("../FinanceLibraries/latex_code.R")
+source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
 source("Paper_global_parameters.R")
-
-if (generate_rnw_data == 1){
-  source("bb_issuers.R")
-}  else{
-  if (reload_data)
-    load("tmpfiles/bb_issuersALL.Rdata")
-  source("lib_helpers.R") 
-  source("latex_code.R")
-  source("dataset/indices_and_factors/ff_industries_sic.R")
-  source("business_data_clean.R")
-  source("Paper_global_parameters.R")
-}
 
@@
 
+if (0){ # To add later
+  qfactors <- read.csv("dataset/indices_and_factors/qfactors.csv", sep=";", dec=".")
+  rownames(qfactors) <- paste(qfactors[,1],ifelse(str_length(qfactors[,2]) == 2, qfactors[,2], paste("0",qfactors[,2], sep="")), sep="-")
+  useonly = which(rownames(qfactors) %in% str_sub(rownames(Risk_Factors_Monthly), start = 1, end=7))
+  qfactors = qfactors[useonly,]
+  rownames(qfactors) <- rownames(Risk_Factors_Monthly)[match(rownames(qfactors), str_sub(rownames(Risk_Factors_Monthly), start = 1, end=7))]
+  qfactors = qfactors[,3:6]
+  qfactors = apply(qfactors,2,function(r) as.numeric(str_replace(r,",",".")))
+  qfactors = qfactors/100
+  qfactors = cbind(qfactors,Risk_Factors_Monthly[,c("SMB", "HML","RF","RMW","CMA")])
+  formula_used="(ri - RF) ~ MKT + HML + ME + I.A + ROE"
+  qfactors_irats_MKT_HML_ME_IA_ROE = car_table(BUYBACK_DATA$DATASET$returns_by_event_monthly, BUYBACK_DATA$DATASET$SDC$Event.Date, qfactors, formula_used = formula_used)$results
+  qfactors_irats_MKT_HML_ME_IA_ROE = qfactors_irats_MKT_HML_ME_IA_ROE[reported_times,]
+
+}
+
+inline_hook <- function (x) {
+  if (is.numeric(x)) {
+    # ifelse does a vectorized comparison
+    # If integer, print without decimal; otherwise print two places
+    res <- ifelse(x == round(x),
                   # use comma for 1000s
-knit_hooks$set(inline = function(x) {
-  if(is.numeric(x)){
-    return(prettyNum(x, big.mark=","))
-  }else{
-    return(x)
-  }
-})
-
+                  sprintf("%s", prettyNum(x, big.mark=",")),
+                  sprintf("%.2f", x)
+    )
+    paste(res, collapse = ", ")
+  } else {
+    x
+  }
+}
+knit_hooks$set(inline = inline_hook)
 @
@@
 
-% Notes options
-\ifnotes{%
-\usepackage[margin=1in,paperwidth=10in,right=2.5in]{geometry}%
-\usepackage[textwidth=1.4in,shadow,colorinlistoftodos]{todonotes}%
-}{%
-\usepackage[margin=1in]{geometry}%
+\usepackage[margin=1in,top=1.5in,bottom=1.5in]{geometry}%
 \usepackage[disable]{todonotes}%
-}
+%\linespread{1.3}
+\onehalfspacing      % Use 1.5 spacing
 
@@
 
-% JFE-specific includes:
-
+% JF-specific includes:
 \usepackage{indentfirst} % Indent first sentence of a new section.
-\usepackage{jfe}          % JFE-specific formatting of sections, etc.
-\usepackage[labelfont=bf]{caption} % bold captions
+\usepackage{endnotes}    % Use endnotes instead of footnotes
+\usepackage{jf}          % JF-specific formatting of sections, etc.
+\usepackage[labelfont=bf,labelsep=period,justification=centering]{caption}   % Format figure captions
+\captionsetup[table]{labelsep=newline,labelfont=bf,textfont=bf}
+\captionsetup[figure]{labelfont=bf,justification=justified}
+\pagestyle{myheadings}
 
@@
 \setlist{noitemsep}  % Reduce space between list items (itemize, enumerate, etc.)
-%\onehalfspacing      % Use 1.5 spacing
+
 % Use endnotes instead of footnotes - redefine \footnote command
 
-\title{Share Buyback and Equity Issue Anomalies Revisited}%\footnotetext{}
-
-\author{Theodoros Evgeniou$^*$, Enric Junqu\'e de Fortuny$^*$,\\
-Nick Nassuphis$^{**}$, and Theo Vermaelen\thanks{INSEAD, Bd de Constance, 77300 Fontainebleau, France, phone: +33(0)1 6072 4000, $^{**}$31, St.
-Martin's Lane WC2N 4ER London, United Kingdom, e-mail:   \href{mailto:theodoros.evgeniou@insead.edu}{theodoros.evgeniou@insead.edu}, \href{mailto:enric.junquedefortuny@insead.edu}{enric.junquedefortuny@insead.edu},  \href{mailto:nicknassuphis@gmail.com}{nicknassuphis@gmail.com}, and \href{mailto:theo.vermaelen@insead.edu}{theo.vermaelen@insead.edu}.
+\title{\textbf{Volatility and the Buyback Anomaly}}%\footnotetext{}
+
+\author{\uppercase{ Theodoros Evgeniou$^*$, Enric Junqu\'e de Fortuny$^{**}$,\\
+Nick Nassuphis$^{***}$,} and \uppercase{Theo Vermaelen}\thanks{INSEAD, Bd de Constance, 77300 Fontainebleau, France, phone: +33(0)1 6072 4000, $^{**}$Rotterdam School of Management, Burgemeester Oudlaan 50, 3062 PA Rotterdam, The Netherlands, $^{***}$31, St.
+Martin's Lane WC2N 4ER London, United Kingdom, e-mail:   \href{mailto:theodoros.evgeniou@insead.edu}{theodoros.evgeniou@insead.edu}, \href{mailto:enric.junquedefortuny@insead.edu}{enric.junquedefortuny@rsm.nl},  \href{mailto:nicknassuphis@gmail.com}{nicknassuphis@gmail.com}, and \href{mailto:theo.vermaelen@insead.edu}{theo.vermaelen@insead.edu}.
 }}
@@
 \begin{abstract}
-\noindent We re-examine the behavior of stock returns after net issue announcements using the five-factor model proposed by Fama and French (2015a).
-We confirm their findings that the equity issue anomaly disappears with the five-factor model, but the buyback anomaly does not.
-Buyback announcements by firms with high pre-announcement (idiosyncratic) volatility are followed by higher long-term abnormal returns.
-This is inconsistent with the widely documented low volatility anomaly, but consistent with Stambaugh, Yu, and Yuan (2015) who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.
-
+\noindent  We find that, inconsistent with the low volatility anomaly, post-buyback announcement long-term abnormal returns are higher when the pre-announcement (idiosyncratic) volatility is high.
+This is consistent with \cite{Stambaugh2015} who find a positive relation between returns and idiosyncratic volatility for undervalued stocks, and with the prediction that a repurchase authorization is an option for undervalued stocks \citep{IkenberryVermaelen1996}.
+The buyback anomaly also survives  when using the five-factor model of Fama and French (2015a).
+Combining volatility with undervaluation indicators proposed by \cite{PeyerVermaelen2009} improves the predictive power of excess returns after buyback announcements.
 \end{abstract}
@@
 
-\noindent  \textit{JEL classification}: G35; G14; G32
+%\noindent  \textit{JEL classification}: G35; G14; G32
 
 \medskip
-\noindent \textit{Keywords}: Share Buybacks; Seasoned Equity Offerings; Anomalies
+%\noindent \textit{Keywords}: Share Buybacks; Seasoned Equity Offerings; Anomalies; Volatility
 
@@
 
-The fact that companies experience long-term positive excess returns after share buybacks and negative long term excess returns after equity issues, has been documented extensively in the academic literature.\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}.
-For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}  In spite of these well documented anomalies investors are not less excited today about e.g., a buyback announcement than 30 years ago: on average stock prices increase by approximately 2 to 3$\%$  when companies announce that the board of directors has approved a buyback program.
-Moreover, we find very few funds that specialize in exploiting these anomalies.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA.
-The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization.
-We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} The fact that these anomalies have not generated a significant response from investors and asset management firms is somewhat surprising considering that other anomalies have disappeared after being documented in academic research~\citep{McLean2016}.
-What makes these capital structure anomalies different so that they stand the test of time?
-
-One straightforward explanation is that they are not really anomalous returns but compensation for risk.
+The main purpose of this paper is to test whether there is a link between two well-known anomalies: the net issue anomaly, i.e.
+the fact that share buybacks (equity issues) are followed by long run positive (negative) excess returns\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}.
+For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}, and the volatility anomaly, i.e.
+the fact that (idiosyncratic) volatility is negatively related to expected returns \citep{Ang2006}.
+This link is plausible considering the fact that \cite{Stambaugh2015} find that the relation between idiosyncratic volatility and future returns reverses and becomes {\it positive} for undervalued stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.} They argue that their result is consistent with the costly {\it arbitrage hypothesis}: idiosyncratic volatility represents risk that deters arbitrage and the resulting reduction in mispricing, hence among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.
+As the positive (negative) long run returns after buybacks (equity issues) are generally interpreted as evidence of undervaluation (overvaluation), we would predict also a positive (negative) relation between volatility and future returns after firms announce a buyback (equity issue).
+
+A positive relation between volatility and future returns after buyback authorization announcements is also expected based on the {\it option hypothesis} of \cite{IkenberryVermaelen1996}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks.
+If markets underestimate the value of this option at the time of the buyback authorization, long term excess returns should be positively correlated with volatility.
+Note that this option hypothesis makes no predictions about excess returns after equity issues which, unlike buyback authorizations, are firm commitments, not options.
+
+In the volatility literature idiosyncratic volatility is estimated by the residual variance of an asset pricing model such as the Fama-French three factor model.
+Empirically there is a very high correlation between residual variance and total variance (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study) so for the remainder of this paper we will use the latter when we refer to just volatility, the volatility anomaly, or the hypotheses above.
+We also use an alternative measure of idiosyncratic volatility that is not correlated (\Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study) with volatility: $1-R^2$.
+For the remainder of the paper we will use this when we refer to {\it idiosyncratic} volatility.
+It measures to what extent the volatility of stock returns is explained by company-specific (non-factor related) information [see also \cite{LiRajgopaletal2014}].
+The hypothesis that managers are able to time the market [e.g., \cite{IkenberryLakonishokVermaelen1995}] is based on the assumption that managers have superior knowledge about company-specific information.
+Hence the prediction of the {\it information advantage hypothesis} is that buyback announcements of firms with high idiosyncratic volatility will also generate higher long term excess returns.
+
+Before proceeding with examining the link between anomalies, it is important to verify that these anomalies are real and not simply a proxy for risk, or have disappeared in recent years as has happened with many other ones~\citep{McLean2016}.
 Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the \cite{Carhart1997} 4-factor model as benchmarks.
-However, \cite{FamaFrench2015b}  argue that the buyback and equity issue anomalies do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns.
+However, \cite{FamaFrench2015b}  argue that many anomalies are weakened or  do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns.
 This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns \citep{NovyMarx2013}.
+They find that the volatility anomaly survives for small firms, but the net issue anomaly does not.
 If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research.
@@
 In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only affects selling shareholders who leave the firm.
-In this paper we re-examine the anomaly using the \cite{FamaFrench2015a} model but use announcement dates and separate buyback announcements and equity announcements.
-
-Using buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, we confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
-Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio.
+So before concluding that the buyback and equity issue anomalies have disappeared, they have to be examined separately, using announcement dates.
+
+So the second purpose of this paper is to verify whether the buyback and equity issue anomalies still exist using the more recent \cite{FamaFrench2015a} five-factor  model, for buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}.\footnote{Using throughout this paper the q-factor model of \cite{Houetal2015} instead of the five-factor model of \cite{FamaFrench2015a} leads to the same conclusions.} We confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
+However, even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio.
 An interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive.
-We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries.
+We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms.
+%, and that the anomaly does not disappear if we exclude specific industries. 
 The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2015}.
+
+It remains a fact though that the buyback anomaly is to some extent a small firm anomaly, as also found by \cite{PeyerVermaelen2009}: value-weighting all the events (as suggested by~\cite{MitchellStafford2000}) makes the (Calendar Time event study method) alphas disappear, although {\it not} for high volatility stocks as we note below.\footnote{Value weighted Calendar Time method results are available upon request.}  So the anomaly does not challenge the view that 99$\%$ of all stocks may well be priced efficiently.
+It simply shows that small cap firms are priced less efficiently and managers of these firms are able to take advantage of undervaluation, at least on average.
+Moreover, while we do not value-weight the events, as argued by \cite{PeyerVermaelen2009}, if anything, to increase the power of the test to detect mispricing, any weighting should be based on the inverse of size.
+However the negative relation between size and alpha may partly explain why this anomaly persists after 30 years and has attracted very little attention in the asset management industry.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA.
+The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization.
+We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} Indeed because management fees are proportional to fund size one expects relatively less interest in anomalies concentrated in small caps or microcaps.
 
@@
 
-The results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously.
-Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information.
-If the buyback signals a change in risk \citep{GrullonMichaely2004} hedging market risk may be complicated.
-That is why in this paper we also simulate hedged investment strategies where we estimate risk before forming the portfolios.
-We show that an investor who followed such a strategy starting in \Sexpr{firstyear} would by \Sexpr{lastyear} have realized cumulative excess returns between \Sexpr{round(tail(months1,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$, depending on the length of the holding period.
-
-The second major purpose of this paper is to test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}, i.e.
-(idiosyncratic) volatility is negatively related to expected returns.
-For example, \cite{Ang2006} find {\it negative} alphas for high volatility and high idiosyncratic volatility stocks, using the 3-factor \cite{FamaFrench1993} model.
-Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms.
-However, in our buyback sample we find a significant {\it positive} relation between excess returns, using the Fama-French 5-factor model as a benchmark.
-This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market.
-The result is also consistent with the  {\it costly arbitrage hypothesis} of \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued  stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  Their argument is that idiosyncratic volatility represents arbitrage risk and deters arbitrage and the resulting reduction in mispricing.
-So, among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.
-
-Turning to total volatility we also find that buyback authorizations of high risk stocks are followed by larger excess returns.
-This is consistent with the {\it option hypothesis}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks \citep{IkenberryVermaelen1996}.
-If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.
-
-Combining idiosyncratic risk and total volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns.
-In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
+After having established that the buyback anomaly survives the Fama-French five factor model and is robust over time, we test for the relation between volatility measures and long term excess returns.
+We find a significant {\it  positive} relation between excess returns and volatility as well as idiosyncratic volatility measured by $1-R^2$.
+%Note although there is a high correlation (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$) between total volatility and residual variance (the proxy used in the literature for idiosyncratic volatility), the correlation between standardized idiosyncratic volatility and total volatility is only \Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$.
+In summary, the positive relation between volatility and excess returns is consistent with the costly arbitrage hypothesis of~\cite{Stambaugh2015} as well as with the option hypothesis of~\cite{IkenberryVermaelen1996}, while the positive relation between $1-R^2$ and excess returns is consistent with the information advantage hypothesis.
+
+Combining  total volatility  and idiosyncratic volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index (EU-Index), improves the predictability of excess returns.
+In particular, during the four years following the buyback announcement, the high EU-Index Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
 Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.
+
+%In order to address the issue of size (which suggests the buyback anomaly is not economically important), we close with a section on buyback anomalies for large firms.
+We find that there is a buyback anomaly for large firms, but only if we focus on large volatility stocks.
+This suggests that when there is large uncertainty about fundamental value, even in large firms the option to repurchase stock at prices below fair value is worth a lot.
+Note however that the alpha for these large high volatility firms is significantly smaller than the alpha of the high EU-Index index so there remains a tradeoff between excess returns and firm size.
 
@@
 In section 2 we describe our data.
-In section 3 we test whether buyback and equity issue anomalies survive when we use the \cite{FamaFrench2015a} five-factor model.
+In section 3 we test whether the buyback and equity issue anomalies survive when we use the \cite{FamaFrench2015a} five-factor model.
 We also compare firms that buy back stock and issue equity within 48 months of a buyback announcement with firms that do not issue stock subsequently.
-In section 4 we test whether the buyback anomaly is robust across time, investment horizon and industry.
-In section 5 we test whether idiosyncratic risk as well as volatility can improve the predictability of excess returns, relative to simply using the Undervaluation Index proposed by \cite{PeyerVermaelen2009}.
+In section 4 we test whether the buyback anomaly is robust across time and investment horizon.
+%and industry. 
+In section 5 we test whether (total) volatility as well as idiosyncratic volatility ($1-R^2$) can improve the predictability of excess returns, relative to simply using the Undervaluation Index proposed by \cite{PeyerVermaelen2009}.
 Section 6 concludes.
@@
 \label{sec:Data}
+
+<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
+cleanup_bb = list()
+cleanup_bb$Standardise <- BUYBACK_DATA$cleanupSDC$Standardise
+cleanup_bb$biz_clean <- BUYBACK_DATA$cleanupBIZ
+cusip_bb = BUYBACK_DATA$DATASET$SDC$CUSIP
+event.date_bb = BUYBACK_DATA$DATASET$SDC$Event.Date
+permno_bb = BUYBACK_DATA$DATASET$SDC$permno
+
+cleanup_iss = list()
+cleanup_iss$Standardise <- ISSUERS_DATA$cleanupSDC$Standardise
+cleanup_iss$biz_clean <- ISSUERS_DATA$cleanupBIZ
+cusip_iss = ISSUERS_DATA$DATASET$SDC$CUSIP
+event.date_iss = ISSUERS_DATA$DATASET$SDC$Event.Date
+permno_iss = ISSUERS_DATA$DATASET$SDC$permno
+@
 
@@
 Book value of equity (BE) was taken from Compustat.
-The Fama-French factors and breakpoints were obtained from Kenneth French's website.
+The Fama-French factors were obtained from Kenneth French's website.
 
 For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request.
-An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both.
-Finally, we removed the following events: no CRSP returns available (\Sexpr{cleanup_bb$get_crsp$NOPERMNO_remove + cleanup_bb$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_bb$compustat$NO_GVKEY_remove + cleanup_bb$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).
-Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(BUYBACK_DATA$finance_Size_used)}  events).\footnote{We are using the industries from Kenneth French's Website.
+An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, will also be available at \href{http://tevgeniou.github.io/BuybacksIssuers/}{tevgeniou.github.io/BuybacksIssuers.}}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both.
+Finally, we removed the following events: no CRSP returns or not all Compustat data available (\Sexpr{BUYBACK_DATA$cleanupNoPermno +  BUYBACK_DATA$cleanupNoCRSPdata + BUYBACK_DATA$cleanupMissingSomeValues} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).
+Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{sum(BUYBACK_DATA$cleanupBIZ$Industry_filter)}  events).\footnote{We are using the industries from Kenneth French's Website.
 The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799).
@@
 Note the structural decline in equity issues since 2000.
+A similar decline in IPOs is also observed by \cite{GaoRitterZhu2013}.
+%Figure \ref{fig:industryeventsBB} shows the number of buyback events per industry in our sample. The software, retail and semiconductor industries are the most active repurchasers.
 
@@
 
-We start with revisiting past research but now using a longer time period and the five-factor model of \cite{FamaFrench2015a} to measure expected returns.
+We start with revisiting past research but now using a longer and more recent time period and the five-factor model of \cite{FamaFrench2015a} to measure expected returns.
 In particular, we test whether buyback (equity issue) announcements are followed by significant positive (negative) long term excess returns, and if so, whether the returns can be explained by proxies for undervaluation as proposed by \cite{PeyerVermaelen2009}.
@@
 However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months.
-This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure.
-Unlike buybacks, equity issues are firm commitments and announced and completed at the same point in time.
+This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure, as done by numerous authors.
+Unlike buybacks, equity issues are firm commitments announced and completed at the same point in time.
 Using actual shares issued, the measure used by \cite{FamaFrench2015b}, and equity announcements (our measure) should therefore produce similar results.
@@
 Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(IRATS_table_all_iss[reported_times[1],1],0)}$\%$ in the 6 months prior to the equity issue.
-However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.
+However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that, for example, these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.
 
@@
 
+So far all our events are equally weighted.
+\cite{MitchellStafford2000} argue that events should be value weighted to test whether they represent an economically important anomaly.
+However, as we know from past research, for theoretical as well as empirical reasons, one would expect that managers in small firms are better able and willing to take advantage of mispricing than in large firms.
+So value weighting would simply bias the results toward zero.
+And indeed, when we value-weight the events (results available upon request) long-term excess returns become statistically insignificantly different from zero when using the total sample of events.
+So the buyback anomaly is not economically important and does not challenge the basic premise that ``the market'' represented by a value-weighted index is priced correctly.
+
 Next we test whether the ``Undervaluation Index'' (U-index) developed by \cite{PeyerVermaelen2009} using buyback announcements from 1991 to 2002 is a robust indicator to separate companies that are buying back stock because they are undervalued from companies that repurchase shares for other reasons.
@@
 Finally, companies get a book value to market value (BE/ME) score depending on the quantile of their BE/ME value of equity in the year prior to the buyback announcement, with a score of 1 to small BE/ME firms and 5 to large ones.
-Unlike \cite{PeyerVermaelen2009} who use all CRSP companies to define the quantile thresholds, we use the Fama-French breakpoints for prior returns the month before, ME the month before, and BE/ME the year before the event to rank the firms from 1 to 5: for example, firms falling below the $5^{th}$ BE/ME breakpoint are assigned a score of 1, while companies above the $16^{th}$ BE/ME breakpoint are assigned a score of 5.
-
-We sum up these three scores for each firm and we then define as ``high U-index'' the firms with total score more than \Sexpr{quantile(valuation_index_bb,0.8)} and as ``low U-index'' those with total score less than \Sexpr{quantile(valuation_index_bb,0.2)}.
+Like \cite{PeyerVermaelen2009} we use all CRSP companies to define the quantile thresholds each month.
+
+We sum up these three scores for each firm and we then define as ``high U-index'' the firms with total score more than \Sexpr{quantile(valuation_index_bb,1-quantile_Uindex)} and as ``low U-index'' those with total score less than \Sexpr{quantile(valuation_index_bb,quantile_Uindex)}.
 Note that unlike \cite{PeyerVermaelen2009} we do not consider the stated reasons for the buyback in the press release, hence we define different thresholds for the high U-index and low U-index buyback firms.
@@
 Regardless of the horizon, high U-index stocks almost always beat low U-index stocks.
-As in the case of IRATS, the five-factor model improves the selectivity of the Undervaluation Index: low U-index now no longer earn significant excess returns after 48 months.
-
-Figure~\ref{fig:pastall} summarizes the IRATS results in more detail by showing the cumulative abnormal returns during the 6 month pre and 48 month post event period, using the five-factor model.
+As in the case of IRATS, the five-factor model improves the selectivity of the Undervaluation Index: low U-index now earn marginally significant excess returns after 48 months.
+
+%Figure~\ref{fig:pastall} summarizes the IRATS results in more detail by showing the cumulative abnormal returns during the 6 month pre and 48 month post event period, using the five-factor model.
 Results are shown for the total sample of buybacks and equity issues, as well as for high and low U-index buyback samples.
@@
 During our sample period (\Sexpr{firstyear}-\Sexpr{lastyear}) \Sexpr{length(unique(intersect(cusip_bb,cusip_iss)))} companies in our data set both announced buybacks and issued equity, but in only \Sexpr{length(SEO_exit_days)}  cases a company announced a subsequent equity issue within 4 years after the buyback announcement.
-We now compute the cumulative excess returns for these firms under two scenarios.
-First, the ``no exit'' scenario, where we hold the stock for 48 months after the buyback announcement.
-Second, the ``exit'' scenario, where we sell the shares as soon as the company announces an equity issue.
-
 Of the \Sexpr{length(SEO_exit_days)} such events, \Sexpr{sum(abs(SEO_exit_days) < 1*365)} SEOs happen within 1 year from the buyback announcement, \Sexpr{sum(abs(SEO_exit_days) < 2*365)} happen within 2 years and \Sexpr{sum(abs(SEO_exit_days) < 3*365)} happen within 3 years.
@@
 Table~\ref{tbl:BBISSexit}  shows that repurchasing firms that issued stock within 48 months after the buyback are remarkable timers.
-Long-term excess returns after 4 years are \Sexpr{Exit_on_SEO_Abn_table["+48",4]}$\%$ (t=\Sexpr{Exit_on_SEO_Abn_table["+48",5]}), more than four times as large as for the overwhelming majority of firms that do not issue stock subsequently.
+Long-term excess returns after 4 years are \Sexpr{Exit_on_SEO_Abn_table["+48",4]}$\%$ (t=\Sexpr{Exit_on_SEO_Abn_table["+48",5]}), about four times as large as for the overwhelming majority of firms that do not issue stock subsequently.
 These results are graphically displayed in Figure~\ref{fig:BBISSexit} (Panel~A).
@@
 How sensitive is it to the length of the investment period?
-Could the anomaly be industry-specific?
+%Could the anomaly be industry-specific?
 
@@
 Table~\ref{tbl:PastFindingsTimeBB} shows that, regardless of the time period chosen or the method to calculate excess returns, the buyback anomaly remains economically and statistically significant and there is no clear time trend in the data that suggests that markets have become more efficient over time.
-For example, although the 2001-2014 period shows smaller timing ability than the 1990-2000 period, excess returns in the 2008-2014 period are as large as in the 1991-2000 period: approximately \Sexpr{BBtable_time["+48",22]}$\%$  after 4 years using IRATS or \Sexpr{BBtable_time_cal["+48",22]}$\%$ per month (\Sexpr{48*BBtable_time_cal["+48",22]}$\%$ after 4 years) when we use the Calendar Time method.
+%For example, although the 2001-2015 period shows smaller timing ability than the 1990-2000 period, excess returns in the 2008-2015 period are as large as in the 1991-2000 period: approximately \Sexpr{BBtable_time["+48",22]}$\%$  after 4 years using IRATS or \Sexpr{BBtable_time_cal["+48",22]}$\%$ per month (\Sexpr{48*BBtable_time_cal["+48",22]}$\%$ after 4 years) when we use the Calendar Time method.
 There is one exception to the consistency between the IRATS and the Calendar Time results: in the period of 1991-2000, the IRATS method generates excess returns after 48 months of \Sexpr{BBtable_time["+48",10]}$\%$ (t=\Sexpr{BBtable_time["+48",11]}) but the Calendar Time method produces statistically insignificant excess returns of \Sexpr{BBtable_time_cal["+48",10]}$\%$ per month.
@@
 The first two columns show the IRATS results and the last two columns show the Calendar Time results.
-Regardless of the method to compute excess returns, the U-index is an excellent predictor: except for the very short 1985-1990 period, buybacks announced by high U-index firms are followed by significantly larger returns than buybacks announced by low U-index firms.
-There is also no evidence that the U-index is losing its predictive power over time: for example, in the 2001-2014 period the difference between high and low U-index firms (after 48 months, IRATS) was \Sexpr{BBtable_undertime["+48",31]-BBtable_undertime["+48",34]}$\%$, while in the most recent 2008-2014 period high U-index firms had \Sexpr{BBtable_undertime["+48",43]-BBtable_undertime["+48",46]}$\%$ larger abnormal returns than low U-index firms.
+Regardless of the method to compute excess returns, the U-index is an excellent predictor: except for the very short 1985-1990 period when we also have few events, buybacks announced by high U-index firms are followed by significantly larger returns than buybacks announced by low U-index firms.
+%There is also no evidence that the U-index is losing its predictive power over time: for example, in the 2001-2015 period the difference between high and low U-index firms (after 48 months, IRATS) was \Sexpr{BBtable_undertime["+48",31]-BBtable_undertime["+48",34]}$\%$, while in the most recent 2008-2015 period high U-index firms had \Sexpr{BBtable_undertime["+48",43]-BBtable_undertime["+48",46]}$\%$ larger abnormal returns than low U-index firms.
 
@@
 This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer.
-However, Figure~\ref{fig:ReturnsBB} allows us to verify that the excess returns are not simply the result of outperformance during a particular time period.
-Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.
+However, Figure~\ref{fig:ReturnsBB} also allows us to verify that the excess returns are not simply the result of outperformance during a particular time period.
+%Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.
 The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the excess returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}.
@@
 
-There exists a large literature on volatility and stock returns.\footnote{For the most recent overview of the literature and potential hypotheses, see \cite{LiRodneyGarcia2016}.} One of the most puzzling findings is the fact that total volatility and idiosyncratic volatility are negatively correlated with future abnormal returns, when expected returns are calculated using the 3-factor \cite{FamaFrench1993} model  [see e.g., \cite{Ang2006} (Table VII)].
-This volatility anomaly also survives after using the \cite{FamaFrench2015a} 5-factor model, at least for small firms.
-Perhaps the buyback and the volatility anomaly are related: are the buyback firms with the largest excess returns also firms with the smallest (idiosyncratic) risk?
-Or can we make arguments that the opposite is true, if we accept the fundamental proposition of this paper, i.e.
-that excess returns are a result of the fact that managers are on average successful in taking advantage of an undervalued stock price?
-
-\subsection{Idiosyncratic Risk}
+Having established the robustness of the buyback anomaly also after using the 5-factor Fama-French model, we turn to our main question: are the buyback and volatility anomalies related?
+One of the most puzzling findings in the large literature on volatility and stock returns\footnote{For the most recent overview of the literature and potential hypotheses, see \cite{LiRodneyGarcia2016}.} is the fact that total volatility and idiosyncratic volatility (measured by residual variance which is, as noted above, highly correlated with total volatility, e.g., \Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study)  are negatively correlated with future abnormal returns, when expected returns are calculated using the 3-factor \cite{FamaFrench1993} model  [see e.g., \cite{Ang2006} (Table VII)].
+Fama and French (2015b) find that this volatility anomaly also survives after using the \cite{FamaFrench2015a} 5-factor model, at least for small firms.
+Perhaps the buyback and the volatility anomaly are related: are the buyback firms with the largest excess returns also firms with the smallest volatility?
+Or can we make arguments that the opposite is true, if we accept a key proposition of this paper, i.e.
+that excess returns are related to the fact that managers are on average successful in taking advantage of an undervalued stock price?
+In that case we expect a negative relation using the \cite{Stambaugh2015} arbitrage hypothesis and the \cite{IkenberryVermaelen1996} option hypothesis.
+Moreover, what about $1-R^2$, a measure of ``standardized'' idiosyncratic risk that unlike residual variance is little correlated with total volatility and measures more precisely the fraction of total volatility explained by company-specific news?\footnote{As noted above, in our sample the correlation between $1-R^2$ and residual variance (the typical measure of idiosyncratic risk in the literature) is only \Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$, compared to that between residual variance (the measure of idiosyncratic risk used in the literature) and total volatility which is \Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$.
+See also \cite{LiRajgopaletal2014} for a related discussion on this issue.} We start with the latter first, then consider the former, and finally we combine the two in the next section.
+
+\subsection{Standardized Idiosyncratic Risk and excess returns}
 \label{sec:idiorisk}
@@
 The main ``theory'' behind the buyback anomaly is that firms may have superior {\it company-specific} information.
-Such situations are more likely in industries or companies where the value is driven less by market wide factors, i.e., by highly ``idiosyncratic'' companies.
-So if buybacks are driven by market timing this superior information hypothesis predicts that there should be a positive relation between idiosyncratic returns and volatility.
-To test this hypothesis, for each event we measure the five-factor regression $R^2$ using the 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month, or using the idiosyncratic volatility as in \cite{Ang2006}, leads to the same conclusions - results available upon request.
-However, as we want to differentiate between ``idiosyncratic'' companies and ``high volatility'' ones, to consider both the effects of company specific information and of the option value of a buyback announcement, we separately study the relations with $R^2$ and volatility.
-See also \cite{LiRajgopaletal2014} for a discussion on this issue.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$.
+Such situations are more likely in industries or companies where the volatility is largely driven by company-specific volatility.
+So if buybacks are driven by market timing this superior information hypothesis predicts that there should be a positive relation between excess returns and the percentage of the volatility explained by company-specific factors, i.e.
+our measure of idiosyncratic volatility ($1-R^2$), however not to be confused with residual variance.
+
+To test this hypothesis, for each event we measure the five-factor regression $R^2$ using the 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month,  leads to the same conclusions - results available upon request.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$.
 We also define the idiosyncratic score of a firm to be the percentile of its $1-R^2$ across all CRSP firms that month.
-Note that we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only.
 Table~\ref{tbl:industriesR2Vol}, columns (1) and (2) show the percentage of high and low idiosyncratic risk events across all industries for which we have at least 100 buyback events in our sample.
@@
 Table~\ref{tbl:IdiosyncraticunderBB} shows the IRATS and Calendar Time abnormal returns for high and low idiosyncratic buyback events-companies.
-Focusing on IRATS, high idiosyncratic buyback stocks earn \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$  after 48 months, more than three times the excess returns of the low idiosyncratic announcements.
+Focusing on IRATS, high idiosyncratic buyback stocks earn \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$  after 48 months, more than the excess returns of the low idiosyncratic announcements.
 The results using the Calendar Time method confirm these findings.
@@
 After 48 months, based on the IRATS methods, high U-index high idiosyncratic companies earn \Sexpr{R2_IRATStable_underBB["+48","High Idiosync.: U CAR"]}$\%$ (t=\Sexpr{R2_IRATStable_underBB["+48",8]}).
-Low idiosyncratic high U-index firms have only an insignificant excess return of \Sexpr{R2_IRATStable_underBB["+48",1]}$\%$ (t=\Sexpr{R2_IRATStable_underBB["+48",2]}), while for low idiosyncratic firms the low U-index IRATS excess returns are significant (\Sexpr{R2_IRATStable_underBB["+48",4]}$\%$, t=\Sexpr{R2_IRATStable_underBB["+48",5]}).
+Low idiosyncratic high U-index firms have only an insignificant excess return of \Sexpr{R2_IRATStable_underBB["+48",1]}$\%$ (t=\Sexpr{R2_IRATStable_underBB["+48",2]}), while for low idiosyncratic firms the low U-index IRATS excess returns are marginally significant (\Sexpr{R2_IRATStable_underBB["+48",4]}$\%$, t=\Sexpr{R2_IRATStable_underBB["+48",5]}).
 Note however that we only have few events in low idiosyncratic, high U-index (\Sexpr{R2_IRATStable_underBB["Observations",1]} events) and high idiosyncratic, low U-index (\Sexpr{R2_IRATStable_underBB["Observations",10]} events) categories.
@@
 This enhances the timing ability of the manager-insider.
-They show that this option can have a lot of value, something that may not be realized at the time of the announcement of the buyback authorization.
-For example, the market may underestimate the maturity of the option if they don't realize that firms who are announcing a buyback authorization for say 2 years are likely to renew the authorization many times in the future.
-Hence, perhaps total volatility is a better prediction of excess returns than idiosyncratic volatility or the U-index.
+They show that this option can have large value, something that may not be realized at the time of the announcement of the buyback authorization.
+For example, the market may underestimate the maturity of the option if they do not realize that firms who are announcing a buyback authorization for say 2 years are likely to renew the authorization many times in the future.
+Moreover, although \cite{Stambaugh2015} argue that idiosyncratic volatility, and not total volatility, should be positively related to future returns for undervalued stocks, the empirical fact is that their estimate of idiosyncratic volatility (residual variance) is highly correlated (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$) with total volatility.
+Their argument is that idiosyncratic volatility represents risk that deters arbitrage and therefore creates mispricing.
+Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between residual variance and future returns for undervalued stocks.
+But considering the very high correlation between residual variance and total variance, their hypothesis would also predict a positive correlation between total volatility and future returns for undervalued stocks.
+Hence, perhaps total volatility is a better prediction of excess returns than (standardized) idiosyncratic volatility (defined as $1-R^2$) or the U-index of \cite{PeyerVermaelen2009}.
 Or perhaps volatility can be an additional, next to the U-index and idiosyncratic volatility, indicator of the likelihood that the buyback is driven by undervaluation.
@@
 We also define the volatility score of a firm to be the percentile of its volatility across all CRSP firms that month.
-Note that, again, we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only.
-In total we have \Sexpr{length(High_VOL_eventsBB)} ``high volatility'' buybacks-events and \Sexpr{length(Low_VOL_eventsBB)} ``low volatility'' ones.
+For simplicity we focus again on the two extreme quantiles only.
+In total we have \Sexpr{sum(High_VOL_eventsBB)} ``high volatility'' buybacks-events and \Sexpr{sum(Low_VOL_eventsBB)} ``low volatility'' ones.
 Table~\ref{tbl:industriesR2Vol}, columns (3) and (4)  show the percentage of high and low volatility events across all industries for which we have at least 100 buyback events in our sample.
-
-Table~\ref{tbl:VOLunderBB} shows the IRATS and Calendar Time abnormal returns for high and low volatility buybacks events-companies.
-Focusing on IRATS, high volatility buyback stocks earn \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$  after 48 months, while low volatility events have non significant abnormal returns for any period.
-The results using the Calendar Time method confirm these findings.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
+Software and chips tend to be the most volatile sectors and they are also two of the three sectors where buybacks are more frequent.
+
+Table~\ref{tbl:VOLunderBB} shows the IRATS and Calendar Time abnormal returns for high and low volatility buybacks events-companies.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
 Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
-High volatility companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy, which are higher than the \Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged48m),1),1)}$\%$) of the corresponding low volatility sample.}
-
-Table~\ref{tbl:VOLunderBB} also tests whether the U-index is valid for high volatility events, as well as whether adjusting for volatility improves the predictive power of the U-index.
+High volatility companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy, which are higher than the \Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged48m),1),1)}$\%$) of the corresponding low volatility sample.} Focusing on IRATS, high volatility buyback stocks earn \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$  after 48 months, while low volatility events have non significant abnormal returns for any period.
+The results using the Calendar Time method confirm these findings.\footnote{As mentioned in Section \ref{sec:Introduction}, the value weighted Calendar Time method alphas are also significant for the high volatility sample: for example the alpha after 48 months is \Sexpr{VOL_IRATStableBB_calValue["+48","CAL"]}$\%$ (t = \Sexpr{VOL_IRATStableBB_calValue["+48","t-stat"]}).
+} So we find support for the \cite{Stambaugh2015} costly arbitrage hypothesis as well as the option hypothesis proposed by \cite{IkenberryVermaelen1996}.
+
+Table~\ref{tbl:VOLunderBB} also tests whether the U-index can further differentiate high volatility events, as well as whether adjusting for volatility improves the predictive power of the U-index.
 Regardless of the time horizon and the event study method, the U-index works for high volatile companies.
@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-EU_index_features = scrub(cbind(BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA$DATASET$SDC$pre_vol,BUYBACK_DATA$Valuation_Index))
-colnames(EU_index_features) <- c("Idiosyncratic Score", "Volatility Score", "U-Index Score")
-Under_IdioBB_cor = cor(EU_index_features)
-@
-
-Table~\ref{tbl:underidioallBB} shows how the high/low U-index  low/high idiosyncratic risk, and low/high volatility buyback events overlap, while Table~\ref{tbl:underidioallBBcor} shows the correlations between the idiosyncratic, volatility, and U-index scores.
+#EU_index_features = scrub(cbind(BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA$DATASET$SDC$pre_vol,BUYBACK_DATA$Valuation_Index))
+#colnames(EU_index_features) <- c("Idiosyncratic Score", "Volatility Score", "U-Index Score")
+#Under_IdioBB_cor = cor(EU_index_features)
+@
+
+Table~\ref{tbl:underidioallBB} shows how the high/low U-index  high/low idiosyncratic risk, and high/low volatility buyback events overlap, while Table~\ref{tbl:underidioallBBcor} shows the correlations between the idiosyncratic, volatility, and U-index scores.
 Overall we see that although high U-index firms tend to have high idiosyncratic risk and high volatility, while high idiosyncratic risk firms tend to also have high volatility, the overlap is not very high.
 For example from Table~\ref{tbl:underidioallBB} we see that  only \Sexpr{round(Under_IdioBB["High Vol.","H Idiosync."],1)}$\%$ of the high volatility stocks that are classified as having either high or low idiosyncratic risk - note that we only consider the  \Sexpr{round(100*quantile_R2,2)}$\%$ tails - have high idiosyncratic risk.
-From Table~\ref{tbl:underidioallBBcor} we infer that the correlation between idiosyncratic risk and volatility is only \Sexpr{round(Under_IdioBB_cor["Volatility Score","Idiosyncratic Score"]*100,1)}$\%$.
+From Table~\ref{tbl:underidioallBBcor} we infer that the correlation between idiosyncratic risk and volatility scores is only \Sexpr{round(Under_IdioBB_cor["Volatility Score","Idiosyncratic Score"]*100,1)}$\%$.
 A natural question is therefore whether one can further enhance the \cite{PeyerVermaelen2009} U-index by incorporating information about the firms' pre-announce idiosyncratic risk and volatility.
@@
 We use the most recent data pre-announce, and make the winsorization and other adjustments as in the websites above.
-Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.} ``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement.
+Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.}
+%``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. 
 ``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement.
-Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available\footnote{As this SDC data was not available for many events, we did not consider the in the U-index calculation.} (this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.
-
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-tmp_market_cap = round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb %in% c(4:6)])/1000,1)
+Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available
+%\footnote{As this SDC data was not available for many events, we did not consider it in the U-index calculation.} 
+(this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.
+
+<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+tmp_market_cap = round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb %in% c(5:6)]),1)
 @
@@
 This makes sense according to the static trade-off theory of optimal capital structure: high risky firms have more financial distress and should have less debt.
-Second, the high EU index firms are more likely to miss earnings forecasts.
+%Second, the high EU index firms are more likely to miss earnings forecasts.
 To the extent that analysts base their recommendations on these earnings misses, stock prices may become undervalued.
 Evidence that analyst extrapolation forecast errors are a partial explanation for the buyback anomaly is documented by \cite{PeyerVermaelen2009}.
-High EU index firms are more likely to mention ``undervaluation'' as a motivation for the buyback.
-High EU index firms tend to have more cash.
+High EU index firms are also more likely to mention ``undervaluation'' as a motivation for the buyback and to use cash.
 This could of course be related to the fact that risky firms should have more cash holdings.
 They also tend to follow up more often with equity offerings after the buyback which suggests that they are more likely to be in the ``market timing'' business.
+Note that all these firm characteristics have not been used to define the EU-Index.
+
 The table also shows a strong negative relation between market-to-book ratios and market capitalization and the EU index, which is not surprising as these are components of the index.
 It should be noted that the EU6 portfolio (consisting of all firms with EU index equal to 6) is composed of very small stocks with an average market capitalization of \$\Sexpr{round(EU_relations["Market Cap.","EU6"],1)} million.
-The average market capitalization of portfolios with long term (after 48 months) monthly excess return of larger than 0.3$\%$ (i.e.
-portfolios EU4 through EU6 in Table~\ref{tbl:EUunderBBcal}) is \$\Sexpr{tmp_market_cap} billion (not indicated in the Table).
-So the buyback anomaly is to some extent a small cap anomaly, although portfolio EU3 for which the average market capitalization of its \Sexpr{sum(EUindex_bb==3)} firms is \$\Sexpr{round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb ==3])/1000,1)} billion still has significant abnormal returns.
+The average market capitalization of portfolios with long term (after 48 months) monthly excess return of larger than 0.5$\%$ (i.e.
+portfolios EU5 - EU6 in Table~\ref{tbl:EUunderBBcal}) is \$\Sexpr{tmp_market_cap} million (not indicated in the Table).
+So the buyback anomaly is to some extent a small cap anomaly.
+%, although portfolio EU3 for which the average market capitalization of its \Sexpr{sum(EUindex_bb==3)} firms is \$\Sexpr{round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb ==3]),1)} billion still has significant abnormal returns.
 
@@
 Long-term cumulative excess returns after 48 months are becoming statistically significantly positive at EU-index levels of 3 and higher, and then steadily increase from \Sexpr{round(EU_IRATStable_bb["+48",10],1)}$\%$ to \Sexpr{round(EU_IRATStable_bb["+48",19],1)}$\%$.
-The Calendar Time results are similar although they only show significance starting at EU-index levels of 4.
+The Calendar Time results are similar although they only show significance starting at EU-index levels of 5.
 Investing in the very high EU index firms (EU=6) generates alphas of \Sexpr{round(EU_CALtable_bb["+48",19],2)}$\%$ per month for 48 months.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
 Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
-The 12-month holding period high EU-index portfolio has average annual abnormal returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[1],1)}$\%$, while the low EU-index one earns only \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[1],1)}$\%$ annual excess returns.
+The 12-month holding period high EU-index portfolio has average annual excess returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[1],1)}$\%$, while the low EU-index one earns only \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[1],1)}$\%$ annual excess returns.
 For the 48-month holding periods the high and low EU-index portfolio earn annual excess returns of  respectively, \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[1],1)}$\%$ and \Sexpr{round(pnl_stats(Low_EU_BB_Hedged48m)[1],1)}$\%$.}
@@
 Tables \ref{tbl:EUTimeUnderBB} and \ref{tbl:EUTimeUnderBBcal} indicate that the EU-index is robust over time, with the exception of the 1985-1990 period.
-However during this period our high EU index sample only contains \Sexpr{ECAL_table_undervaluation_time_bb["Observations",1]} observations which results in statistically insignificant excess returns beyond the 12 month horizon.
+However during this period our high EU index sample only contains \Sexpr{ECAL_table_undervaluation_time_bb["Observations",1]} observations which results in statistically insignificant excess returns.% beyond the 12 month horizon.
 
@@
 
-The buyback anomaly first reported by \cite{IkenberryLakonishokVermaelen1995} is still alive and robust.
+The buyback anomaly first reported by \cite{IkenberryLakonishokVermaelen1995} is still present and robust.
 Long term excess returns are large, highly statistically significant and robust even when we replace the Fama-French three-factor model with the Fama-French five-factor model.
@@
 These are also firms that are more likely to mention in their press releases that they are buying back stock because they are undervalued.
-They are more likely to miss earnings forecasts relative to the other buyback firms and therefore falling out of favor with analysts.
+%They are more likely to miss earnings forecasts relative to the other buyback firms and therefore falling out of favor with analysts.  
 However investing in high EU index firms to some extent implies investing in small caps and micro-caps, which may explain partially why the anomaly persists as these firms may not satisfy, for example, liquidity risk constraints of many funds.
@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+
+#\\textit{Missed (Beat) EPS} measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. 
+#EU_relations <- EU_relations[-which(rownames(EU_relations) %in% c("Missed EPS","Beat EPS")),]
+
 rownames(EU_relations)[1] <- "Low Leverage"
@@
 <<   fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
-par(mfrow=c(2,1), mar=c(2.2,4.5,2.2,4.5))
+par(mfrow=c(2,1), mar=c(2.8,4.5,2.8,4.5))
 
@@
   IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]
-IRATS_table_all_iss_undervaluation_plot = IRATS_table_all_iss_undervaluation
-IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]
+  #IRATS_table_all_iss_undervaluation_plot = IRATS_table_all_iss_undervaluation
+  #IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]
 
@@
 
-\begin{landscape}
-\begin{figure}[H]
-\centering
-<<  fig.width=10, fig.height=5, echo=F >>=
-df.bar <- barplot(industry_tableBB,col=c("grey"),main = "", ylab = "Buybacks", xlab = "",las=2,space=0.9, cex.names=0.62)
-for (iter in 1:floor(max(industry_tableBB)/100))
-  abline(h = 100*iter)
-@
-\caption{Number of buyback announcements per industry. }
-\label{fig:industryeventsBB}
-\end{figure}
-\end{landscape}
+%\begin{landscape}
+%\begin{figure}[H]
+%\centering
+%<<  fig.width=10, fig.height=5, echo=F >>=
+%df.bar <- barplot(industry_tableBB,col=c("grey"),main = "", ylab = "Buybacks", xlab = "",las=2,space=0.9, cex.names=0.62)
+%for (iter in 1:floor(max(industry_tableBB)/100))
+%  abline(h = 100*iter)
+%@
+%\caption{Number of buyback announcements per industry. }
+%\label{fig:industryeventsBB}
+%\end{figure}
+%\end{landscape}
 %\begin{figure}[H]
@@
 << fig.width=8, fig.height=5, out.width='\\textwidth', echo=F >>=
-par(mfrow=c(2,2), mar=c(2.3,4,2.3,4))
+par(mfrow=c(2,2), mar=c(2.7,4,2.7,4))
 
@@
 
-\bibliographystyle{jfe}
+\bibliographystyle{jf}
 \bibliography{Bibliography}

### 2016-05-08 index.Rmd
shiny simplification

@@
 ---
-title: "Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool"
+title: "Volatility and the Buyback Anomaly: Interactive Tool"
 author: "[Theodoros Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), [Enric Junqué de Fortuny](http://ciri.be/), [Nick Nassuphis](https://www.linkedin.com/in/nick-nassuphis-8029372), and [Theo Vermaelen](http://faculty.insead.edu/theo-vermaelen/)"
@@
 # rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
-# source("create_tool_data.R")
 load("bb_issuersTOOL.Rdata")
-#load("tmpfiles/bb_issuersALL.Rdata")
 
@@
 }
-source("lib/lib_helpers_shiny.R")
-source("lib/Paper_global_parameters.R")
-source("lib/heatmapOutput.R") 
-source("lib/plots.R")
-source("report_helpers.R")
 
-DATASET_INI = BUYBACK_DATA$DATASET
-DATASET_INI$SDC = as.data.frame(DATASET_INI$SDC)
+source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
+source("../FinanceLibraries/latex_code.R")
+source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
+source("Paper_global_parameters.R")
+source("../FinanceLibraries/heatmapOutput.R") 
+source("../FinanceLibraries/shiny_plots.R")
 
-#if(1) {
-#  CACHE <- car_table_cache(DATASET_INI$returns_by_event_monthly,
-#                           DATASET_INI$SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)
-#  save("CACHE",file = "cache.Rdata")
-#} else {
-#  load("cache.Rdata")  
-#}
 report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)
+BUYBACK_DATA_TOOL$None <- 1:length(BUYBACK_DATA_TOOL$Prior.Returns.Score)
+
+value.weights = rep(1,length(BUYBACK_DATA_TOOL$Prior.Returns.Score))
+acceptaple_features = setdiff(names(BUYBACK_DATA_TOOL),c("Event.Date", "Industry_name","Event.Size"))
 ```
@@
                condition = "!$('makeReport').hasClass('shiny-busy')",
-          actionButton("makeReport","Generate Report",icon=icon("file"))
+               actionButton("makeReport","Generate Report (Work in Progress)",icon=icon("file"))
              )
@@
       }
-        #save("newinput",file=normalizePath("input.Rdata"))
-        knitr::knit2pdf("report.Rnw",envir=globalenv())
+      # Not yet available
+      #knitr::knit2pdf("report.Rnw",envir=globalenv())
     })
@@
 dateInput("startdate", "Starting Date:", 
-          value = min(DATASET_INI$SDC$Event.Date) - 10, min = min(DATASET_INI$SDC$Event.Date), max = max(DATASET_INI$SDC$Event.Date)-3*370,
+          value = min(BUYBACK_DATA_TOOL$Event.Date) - 10, min = min(BUYBACK_DATA_TOOL$Event.Date), max = max(BUYBACK_DATA_TOOL$Event.Date)-3*370,
           startview = "year",
@@
 dateInput("enddate", "End Date (allow at least 3 years from the starting day you selected - else it will automatically use data up to 3 years after your start date):", 
-          value = max(DATASET_INI$SDC$Event.Date) + 10, 
-          min = min(DATASET_INI$SDC$Event.Date)+3*370, 
-          max = max(DATASET_INI$SDC$Event.Date)+10,startview = "year",
+          value = max(BUYBACK_DATA_TOOL$Event.Date) + 10, 
+          min = min(BUYBACK_DATA_TOOL$Event.Date)+3*370, 
+          max = max(BUYBACK_DATA_TOOL$Event.Date)+10,startview = "year",
           width='100%')
@@
 ```{r, eval=TRUE, echo = FALSE}
-selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), ceiling(max(DATASET_INI$SDC$Market.Cap)))), selected = as.character(ceiling(max(DATASET_INI$SDC$Market.Cap))), width = "1000px")
+selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), ceiling(max(BUYBACK_DATA_TOOL$Market.Cap)))), selected = as.character(ceiling(max(BUYBACK_DATA_TOOL$Market.Cap))), width = "1000px")
 ```
@@
   if (market_cap_max < market_cap_min)
-    market_cap_max = ceiling(max(DATASET_INI$SDC$Market.Cap))
+    market_cap_max = ceiling(max(BUYBACK_DATA_TOOL$Market.Cap))
 
-  useonly_report = which(DATASET_INI$SDC$Event.Date >= starting & DATASET_INI$SDC$Event.Date <= ending & scrub(DATASET_INI$SDC$Market.Cap) >= market_cap_min & scrub(DATASET_INI$SDC$Market.Cap) <= market_cap_max)
-
-  SDC = DATASET_INI$SDC[useonly_report,]
-  returns_by_event_monthly = DATASET_INI$returns_by_event_monthly[,useonly_report]
-  DatesMonth = DATASET_INI$DatesMonth[,useonly_report]
-
-  CACHE <- car_table_cache(returns_by_event_monthly,
-                         SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)
+  useonly_report = which(BUYBACK_DATA_TOOL$Event.Date >= starting & BUYBACK_DATA_TOOL$Event.Date <= ending & scrub(BUYBACK_DATA_TOOL$Market.Cap) >= market_cap_min & scrub(BUYBACK_DATA_TOOL$Market.Cap) <= market_cap_max)
 
   list(
-    CACHE = CACHE,
-    returns_by_event_monthly = returns_by_event_monthly,
-    DatesMonth = DatesMonth,
-    SDC = SDC,
+    BUYBACK_DATA_TOOL=BUYBACK_DATA_TOOL[useonly_report,],
+    returns_by_event_monthly = returns_by_event_monthly[,useonly_report],
+    DatesMonth  = DatesMonth[,useonly_report],
     subset = useonly_report
-    #returns_by_event_monthly = DATASET_INI$returns_by_event_monthly,
-    #DatesMonth = DATASET_INI$DatesMonth,
-    #SDC = DATASET_INI$SDC
   )
@@
 ```{r, eval=TRUE, echo = FALSE}
-acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Industry", "Purpose.Code","Source.of.funds")
-
 fluidPage(
@@
                          renderPlot({
-                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
+                           feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
                            feature = feature[!is.na(feature)]
@@
                          renderDataTable({
-                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
-                           #feature = feature[!is.na(feature)]
+                           feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
+                           feature = feature[!is.na(feature)]
                            if (length(unique(feature)) > 20 & is.numeric(feature)){
@@
 ```{r, eval=TRUE, echo = FALSE}
-checkboxGroupInput("industry", "Select Industries to remove:", choices = unique(DATASET_INI$SDC$Industry),selected = NULL,inline=TRUE)
-
+checkboxGroupInput("industry", "Select Industries to remove:", choices = unique(BUYBACK_DATA_TOOL$Industry_name),selected = NULL,inline=TRUE) 
+```
+<br>
+<br>
+```{r, eval=TRUE, echo = FALSE}
+selectInput("quantile_used_industry","Enter the quantile to use to define High and Low Firms for this analysis:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
 ```
@@
 feature_IRATStable_industry <- reactive({
-  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
-  #cat(paste("Total left after filtering industry:",sum(useonly_industry)))
-  #instead of using company_subset_undervalued and _overvalued, use Valuation Index
-  thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == "Valuation.Index")]]
-  thefeature = as.numeric(scrub(thefeature))
-  quantile_used_ind = as.numeric(0.2)
+  useonly_industry = !(DATASET_NEW()$BUYBACK_DATA_TOOL$Industry_name %in% input$industry) 
+  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "Valuation.Index")]]
+  #quantile_used_ind = as.numeric(0.2)
+  quantile_used_ind = as.numeric(input$quantile_used_industry)
+
   High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
@@
   res = round(cbind(
-    #car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
-    #car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
-    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & Low_feature_events)$results,
-    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & High_feature_events)$results
+    car_table(returns_by_event_monthly[,useonly_industry & Low_feature_events],
+              BUYBACK_DATA_TOOL$Event.Date[useonly_industry & Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
+    car_table(returns_by_event_monthly[,useonly_industry & High_feature_events],
+              BUYBACK_DATA_TOOL$Event.Date[useonly_industry & High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
   ),2)[reported_times,]
@@
 feature_CALtable_industry <- reactive({
-    thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == "Valuation.Index")]]
-  thefeature = as.numeric(scrub(thefeature))
-  quantile_used_ind = as.numeric(0.2)
+  useonly_industry = !(DATASET_NEW()$BUYBACK_DATA_TOOL$Industry_name %in% input$industry) 
+  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "Valuation.Index")]]
+  #quantile_used_ind = as.numeric(0.2)
+  quantile_used_ind = as.numeric(input$quantile_used_industry)
+
   High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
@@
 
-  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
   res = round(cbind(
-    #calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly,report_months_cal)$results,
-    #calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly,report_months_cal)$results
-    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & Low_feature_events], DATASET_NEW()$SDC$Event.Date[useonly_industry& Low_feature_events], Risk_Factors_Monthly,report_months_cal)$results,
-        calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & High_feature_events], DATASET_NEW()$SDC$Event.Date[useonly_industry & High_feature_events], Risk_Factors_Monthly,report_months_cal)$results
-
+    calendar_table(returns_by_event_monthly[,useonly_industry & Low_feature_events],
+                   BUYBACK_DATA_TOOL$Event.Date[useonly_industry & Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[useonly_industry & Low_feature_events])$results,
+    calendar_table(returns_by_event_monthly[,useonly_industry & High_feature_events],
+                   BUYBACK_DATA_TOOL$Event.Date[useonly_industry & High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[useonly_industry & Low_feature_events])$results
   ),2)[reported_times,]
@@
 ```{r, eval=TRUE, echo = FALSE}
-acceptaple_features1 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio")
-
-selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features1,selected = acceptaple_features1[4], width = "1000px")
+selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features,selected = acceptaple_features[4], width = "1000px")
 
@@
   thesign = ifelse(input$characteristic_irats_sign, -1, +1)
-  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]
+  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]
 
@@
 
-  #High_feature_events = which(scrub(thefeature) > quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
-  #Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
   res = round(cbind(
-    #car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
-    #car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
-    car_table_cached(DATASET_NEW()$CACHE,Low_feature_events)$results,
-    car_table_cached(DATASET_NEW()$CACHE,High_feature_events)$results
+    car_table(returns_by_event_monthly[, Low_feature_events],
+              BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
+    car_table(returns_by_event_monthly[, High_feature_events],
+              BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
   ),2)[reported_times,]
+
   colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
@@
   thesign = ifelse(input$characteristic_irats_sign, -1, +1)
-  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
+  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]  
   High_feature_events = which(scrub(thefeature) > quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
   Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
+
   res = round(cbind(
-    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly,report_months_cal)$results,
-    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly,report_months_cal)$results
+    calendar_table(returns_by_event_monthly[, Low_feature_events],
+                   BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[Low_feature_events])$results,
+    calendar_table(returns_by_event_monthly[,High_feature_events],
+                   BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[High_feature_events])$results
   ),2)[reported_times,]
+
   colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
@@
 High_feature_Hedged_react <- reactive({
-  thefeature = as.numeric(DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]])
+  thefeature = as.numeric(DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]])
   quantile_used <- as.numeric(input$quantile_used)
@@
 Low_feature_Hedged_react <- reactive({
-  thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
+  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]  
   Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
@@
 
-```{r, eval=TRUE, echo = FALSE}
-acceptaple_features2 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","None")
-```
-
 <br>
@@
     column(6,
-      selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features2,selected = acceptaple_features2[4], width = "425px"),
+           selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[4], width = "425px"),
            checkboxInput("characteristic_irats1_sign", "Reverse", value = FALSE),
-      selectInput("characteristic_irats2", "Second Firm Characteristic:", choices = acceptaple_features2,selected ="None", width = "425px"),
+           selectInput("characteristic_irats2", "Second Firm Characteristic:", choices = acceptaple_features,selected ="None", width = "425px"),
            checkboxInput("characteristic_irats2_sign", "Reverse", value = FALSE),
-    selectInput("characteristic_irats3", "Third Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
+           selectInput("characteristic_irats3", "Third Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
            checkboxInput("characteristic_irats3_sign", "Reverse", value = FALSE)
@@
     column(6,
-      selectInput("characteristic_irats4", "Fourth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
+           selectInput("characteristic_irats4", "Fourth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
            checkboxInput("characteristic_irats4_sign", "Reverse", value = FALSE),
-    selectInput("characteristic_irats5", "Fifth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
+           selectInput("characteristic_irats5", "Fifth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
            checkboxInput("characteristic_irats5_sign", "Reverse", value = FALSE),
-    selectInput("characteristic_irats6", "Sixth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
+           selectInput("characteristic_irats6", "Sixth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
            checkboxInput("characteristic_irats6_sign", "Reverse", value = FALSE)
@@
   thesign = ifelse(input$characteristic_irats1_sign, -1, +1)
-  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats1)]]  
-  High_feature_events1 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
-  Low_feature_events1 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
+  thefeature1 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats1)]]  
+  High_feature_events1 = (scrub(thefeature1) >= quantile(thefeature1[!is.na(thefeature1)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
+  Low_feature_events1 = (scrub(thefeature1) <= quantile(thefeature1[!is.na(thefeature1)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
 
+  thefeature2 <- thefeature3 <- thefeature4 <- thefeature5 <- thefeature6 <- rep(0,length(High_feature_events1))
   High_feature_events2 <- High_feature_events3 <- High_feature_events4 <- High_feature_events5 <- High_feature_events6 <- rep(FALSE,length(High_feature_events1))
@@
     thesign = ifelse(input$characteristic_irats2_sign, -1, +1)
-    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats2)]]  
-    High_feature_events2 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
-    Low_feature_events2 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
+    thefeature2 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats2)]]  
+    High_feature_events2 = (scrub(thefeature2) >= quantile(thefeature2[!is.na(thefeature2)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
+    Low_feature_events2 = (scrub(thefeature2) <= quantile(thefeature2[!is.na(thefeature2)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
   }
@@
     thesign = ifelse(input$characteristic_irats3_sign, -1, +1)
-    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats3)]]  
-    High_feature_events3 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
-    Low_feature_events3 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
+    thefeature3 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats3)]]  
+    High_feature_events3 = (scrub(thefeature3) >= quantile(thefeature3[!is.na(thefeature3)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature3))
+    Low_feature_events3 = (scrub(thefeature3) <= quantile(thefeature3[!is.na(thefeature3)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature3))
   }
@@
     thesign = ifelse(input$characteristic_irats4_sign, -1, +1)
-    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats4)]]  
-    High_feature_events4 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
-    Low_feature_events4 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
+    thefeature4 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats4)]]  
+    High_feature_events4 = (scrub(thefeature4) >= quantile(thefeature4[!is.na(thefeature4)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature4))
+    Low_feature_events4 = (scrub(thefeature4) <= quantile(thefeature4[!is.na(thefeature4)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature4))
   }
@@
     thesign = ifelse(input$characteristic_irats5_sign, -1, +1)
-    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats5)]]  
-    High_feature_events5 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
-    Low_feature_events5 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
+    thefeature5 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats5)]]  
+    High_feature_events5 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
+    Low_feature_events5 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
   }
@@
     thesign = ifelse(input$characteristic_irats6_sign, -1, +1)
-    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats6)]]  
-    High_feature_events6 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
-    Low_feature_events6 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
+    thefeature6 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats6)]]  
+    High_feature_events6 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
+    Low_feature_events6 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
   }
@@
 
+  Index_score = thefeature1 + 
+    ifelse(input$characteristic_irats2 != "None",thefeature2,0)+ 
+    ifelse(input$characteristic_irats3 != "None",thefeature3,0) + 
+    ifelse(input$characteristic_irats4 != "None",thefeature4,0) + 
+    ifelse(input$characteristic_irats5 != "None",thefeature5,0) + 
+    ifelse(input$characteristic_irats6 != "None",thefeature6,0)
   Index_score
@@
   Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
+
   res = round(cbind(
-    #car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
-    #car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
-    car_table_cached(DATASET_NEW()$CACHE,Low_feature_events)$results,
-    car_table_cached(DATASET_NEW()$CACHE,High_feature_events)$results
+    car_table(returns_by_event_monthly[, Low_feature_events],
+              BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
+    car_table(returns_by_event_monthly[, High_feature_events],
+              BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
   ),2)[reported_times,]
@@
   Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
+
   res = round(cbind(
-    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly,report_months_cal)$results,
-    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly,report_months_cal)$results
+    calendar_table(returns_by_event_monthly[, Low_feature_events],
+                   BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[Low_feature_events])$results,
+    calendar_table(returns_by_event_monthly[,High_feature_events],
+                   BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[High_feature_events])$results
   ),2)[reported_times,]
+
   colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")

### 2016-05-12 index.Rmd
tool update + copyright

@@
+<!--
+ Copyright 2015, INSEAD
+ by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
+ Dual licensed under the MIT or GPL Version 2 licenses.  -->
+
 ---
@@
 ```{r, eval=TRUE, echo = FALSE,message=FALSE}
+# need this to avoid loading the R libraries when the tool is deployed on shinyapps (needs to be 1 when run localy, 1 when deployed on a shinyapps server)
+
+run_shiny_tool = 0
+
+```
+
+```{r, eval=TRUE, echo = FALSE,message=FALSE}
 # rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
@@
 
-if(T) {
+if(run_shiny_tool) {
   library(googleVis)
@@
   library("dygraphs")
-  library("reshape")
+  #library("reshape")
   library("ggplot2")
@@
 
-source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
-source("../FinanceLibraries/latex_code.R")
-source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
+source("interactive_tool_files/lib_helpers.R", chdir=TRUE)
+source("interactive_tool_files/ff_industries_sic.R")
 source("Paper_global_parameters.R")
-source("../FinanceLibraries/heatmapOutput.R") 
-source("../FinanceLibraries/shiny_plots.R")
+source("interactive_tool_files/heatmapOutput.R")
 
@@
 
-This is an interactive tool for the article [Share Buyback and Equity Issue Anomalies Revisited](http://tevgeniou.github.io/BuybacksIssuers/).
+This is an interactive tool for the article [Volatility and the Buyback Anomaly](http://tevgeniou.github.io/BuybacksIssuers/).
 Users can explore the effects of various parameters as well as data filtering choices.
-For any given choices, users can generate and download a new **customized pdf version of the paper** by clicking the buttons which will appear below at any time.
-
-<br>
+For any given choices, users can generate and download a new **customized pdf version of the paper** (work in progress) by clicking the button below at any time.
 
@@
 Please wait without changing any parameters until you are prompted to download the new paper.**
-
-<br>
 
@@
 <hr>
-<hr>
 
@@
 
-You can select some filters for the dataset. All analyses below will be done only for the companies that are selected.
+You can select some filters for the dataset. All analyses below will be done only for the events that are selected.
 
@@
 Selet the minimum size of the firms (in $millions) for which you would like to do the analyses below.
-The maximum selected should be larger than the minimum, else the maximum is automatically set to 10e6:
+The maximum selected should be larger than the minimum, else the maximum is automatically set to infinity:
 
@@
 ```{r, eval=TRUE, echo = FALSE}
-selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), ceiling(max(BUYBACK_DATA_TOOL$Market.Cap)))), selected = as.character(ceiling(max(BUYBACK_DATA_TOOL$Market.Cap))), width = "1000px")
+selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), 10e10)), selected = as.character(10e10), width = "1000px")
 ```
+
+We can also see the effects of removing some industries: we can select industries to remove here (make sure there are enough data left for the analysis):
+
+<br>
+
+```{r, eval=TRUE, echo = FALSE}
+selectInput("industry", "Select Industries to remove:", choices = unique(BUYBACK_DATA_TOOL$Industry_name),selected = NULL,multiple=TRUE,width="100%") 
+```
+<br>
 
@@
 
-  useonly_report = which(BUYBACK_DATA_TOOL$Event.Date >= starting & BUYBACK_DATA_TOOL$Event.Date <= ending & scrub(BUYBACK_DATA_TOOL$Market.Cap) >= market_cap_min & scrub(BUYBACK_DATA_TOOL$Market.Cap) <= market_cap_max)
+  useonly_industry = !(BUYBACK_DATA_TOOL$Industry_name %in% input$industry)
+
+  useonly_report = which(BUYBACK_DATA_TOOL$Event.Date >= starting & BUYBACK_DATA_TOOL$Event.Date <= ending &
+                           scrub(BUYBACK_DATA_TOOL$Market.Cap) >= market_cap_min & 
+                           scrub(BUYBACK_DATA_TOOL$Market.Cap) <= market_cap_max &
+                           useonly_industry)
 
@@
     DatesMonth  = DatesMonth[,useonly_report],
+    value.weights = value.weights[useonly_report],
     subset = useonly_report
@@
 This tool allows the user to explore descriptive statistics of some of the key firm characteristics.
-When the name of the firm characteristics ends with ".Score" it is  either the 1-5 score relative to the Fama-French breakpoints (e.g.
-for Size, Prior returns, and BE/ME ratio) or the percentile relative to all firms in the CRSP universe at the time of the buyback announcement, as discussed in the paper.
+When the name of the firm characteristics ends with ".Score" it is the percentile (0 to 1) relative to all firms in the CRSP universe at the time of the buyback announcement, as discussed in the paper.
 Otherwise it is the raw value of the firm characteristic.
+
+<br>
 
@@
 fluidPage(
-  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[4]),
+  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = "EU.Index"),
   mainPanel(
-    tabsetPanel("Example",
+    navlistPanel(
       tabPanel("Histogram",
@@
                  if (length(unique(feature)) > 20 & is.numeric(feature)){
-                             res = t(as.matrix(summary(feature)))
+                   res = t(round(as.matrix(summary(feature)),2))
                    colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
@@
                  if (is.character(feature) | length(unique(feature)) <= 20){
-                             tmp = sort(table(feature), decreasing = TRUE)
+                   tmp = table(feature)
                    res = t(as.matrix(tmp))
@@
                })
-                )
       ),
+      widths = c(3, 9)),
     style='width: 100%;'))
@@
 <hr>
-<hr>
 
-### Industry Robustness Analysis of U-Index
+### The EU-Index
 
-Two types of robustness analysis has been considered in the paper: over different time periods, and across industries.
-We can select industries to remove here (make sure there are enough data left for the analysis):
+For the subset of events selected the High/Low EU index events (for the selected thresholds) have the abnormal returns below:
 
 <br>
+```{r, eval=TRUE, echo = FALSE}
+selectInput("high_EU_index_thres","Enter the EU index threshold above which (>=) we define the High EU-Index firms (need minimum 10 firms High EU firms):", choices = sort(unique(BUYBACK_DATA_TOOL$EU.Index)), selected = "5", width = "1000px")
+```
 
 ```{r, eval=TRUE, echo = FALSE}
-checkboxGroupInput("industry", "Select Industries to remove:", choices = unique(BUYBACK_DATA_TOOL$Industry_name),selected = NULL,inline=TRUE) 
-```
-<br>
-<br>
-```{r, eval=TRUE, echo = FALSE}
-selectInput("quantile_used_industry","Enter the quantile to use to define High and Low Firms for this analysis:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
+selectInput("low_EU_index_thres","Enter the EU index threshold below which (<=) we define the Low EU-Index firms (need minimum 10 firms Low EU firms):", choices = sort(unique(BUYBACK_DATA_TOOL$EU.Index)), selected = "1", width = "1000px")
 ```
@@
 ```{r, eval=TRUE, echo = FALSE}
+EU_index_table <- reactive({
+  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]
+  res = matrix(table(thefeature),nrow=1)
+  colnames(res) <- paste("EU Index", names(table(thefeature)), sep=": ")
+  rownames(res) <- "# of Events"
+  res
+})
 
 feature_IRATStable_industry <- reactive({
-  useonly_industry = !(DATASET_NEW()$BUYBACK_DATA_TOOL$Industry_name %in% input$industry) 
-  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "Valuation.Index")]]
-  #quantile_used_ind = as.numeric(0.2)
-  quantile_used_ind = as.numeric(input$quantile_used_industry)
+  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]
 
-  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
-  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)
+  high_EU_index_thres = as.numeric(input$high_EU_index_thres)
+  low_EU_index_thres = as.numeric(input$low_EU_index_thres)
+
+  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= high_EU_index_thres
+  if (sum(High_feature_events) < 10)
+    High_feature_events = !is.na(thefeature) & scrub(thefeature) >= high_EU_index_thres-1
+
+  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= low_EU_index_thres
+  if (sum(Low_feature_events) < 10)
+    Low_feature_events = !is.na(thefeature) & scrub(thefeature) <= Low_feature_events+1
 
   res = round(cbind(
-    car_table(returns_by_event_monthly[,useonly_industry & Low_feature_events],
-              BUYBACK_DATA_TOOL$Event.Date[useonly_industry & Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
-    car_table(returns_by_event_monthly[,useonly_industry & High_feature_events],
-              BUYBACK_DATA_TOOL$Event.Date[useonly_industry & High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
+    car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events],
+              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
+    car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
+              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
   ),2)[reported_times,]
-  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
+  colnames(res) <- c("Low EU: CAR", "t-stat","p-value", "High EU: CAR", "t-stat","p-value")
   as.data.frame(res)
@@
 feature_CALtable_industry <- reactive({
-  useonly_industry = !(DATASET_NEW()$BUYBACK_DATA_TOOL$Industry_name %in% input$industry) 
-  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "Valuation.Index")]]
-  #quantile_used_ind = as.numeric(0.2)
-  quantile_used_ind = as.numeric(input$quantile_used_industry)
+  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]
 
-  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
-  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)
+  high_EU_index_thres = as.numeric(input$high_EU_index_thres)
+  low_EU_index_thres = as.numeric(input$low_EU_index_thres)
+
+  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= high_EU_index_thres
+  if (sum(High_feature_events) < 10)
+    High_feature_events = !is.na(thefeature) & scrub(thefeature) >= high_EU_index_thres-1
+
+  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= low_EU_index_thres
+  if (sum(Low_feature_events) < 10)
+    Low_feature_events = !is.na(thefeature) & scrub(thefeature) <= Low_feature_events+1
 
   res = round(cbind(
-    calendar_table(returns_by_event_monthly[,useonly_industry & Low_feature_events],
-                   BUYBACK_DATA_TOOL$Event.Date[useonly_industry & Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[useonly_industry & Low_feature_events])$results,
-    calendar_table(returns_by_event_monthly[,useonly_industry & High_feature_events],
-                   BUYBACK_DATA_TOOL$Event.Date[useonly_industry & High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[useonly_industry & Low_feature_events])$results
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events],
+                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[Low_feature_events])$results,
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
+                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[High_feature_events])$results
   ),2)[reported_times,]
-  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
+  colnames(res) <- c("Low EU: CAL", "t-stat","p-value", "High EU: CAL", "t-stat","p-value")
   as.data.frame(res)
@@
   mainPanel(
-    tabsetPanel("Example",
+    navlistPanel(
+      tabPanel("Number of Firms per EU Index Value",
+               busyIndicator("Calculating results ...",wait = 0),
+               renderTable({
+                 EU_index_table()
+               })),
       tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
@@
                  feature_CALtable_industry()
-                         }))    
-    ),style='width: 100%;'))
+               })),
+      widths = c(3, 9)),style='width: 100%;'))
 ```
 
-<hr>
 <hr>
@@
 The article relates 5 firm characteristics (pre-buyback-announcement returns, idiosyncratic volatility, and volatility, as well as BE/ME and Firm Size).
-This tool allows the user to study the effects of combining any of these firm characteristics, as well as some other ones not discussed in the paper.
+This tool allows the user to study the effects of combining any of these firm characteristics, as well as others not discussed in the paper.
+We consider here high/low events defined using the quantiles of the selected event charactetistic.
 
 ```{r, eval=TRUE, echo = FALSE}
-selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features,selected = acceptaple_features[4], width = "1000px")
+selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features,selected = "EU.Index", width = "1000px")
 
-selectInput("quantile_used","Enter the quantile to use to define High and Low Firms:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
+selectInput("quantile_used","Enter the quantile to use to define High (>=) and Low (<=) Firms:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
 
@@
   res = round(cbind(
-    car_table(returns_by_event_monthly[, Low_feature_events],
-              BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
-    car_table(returns_by_event_monthly[, High_feature_events],
-              BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
+    car_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
+              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
+    car_table(DATASET_NEW()$returns_by_event_monthly[, High_feature_events],
+              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
   ),2)[reported_times,]
@@
   thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]
-  High_feature_events = which(scrub(thefeature) > quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
-  Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
+
+  thefeature = as.numeric(scrub(thefeature))
+  quantile_used_ind = as.numeric(input$quantile_used)
+
+  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
+  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)
 
   res = round(cbind(
-    calendar_table(returns_by_event_monthly[, Low_feature_events],
-                   BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[Low_feature_events])$results,
-    calendar_table(returns_by_event_monthly[,High_feature_events],
-                   BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[High_feature_events])$results
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
+                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[Low_feature_events])$results,
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
+                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[High_feature_events])$results
   ),2)[reported_times,]
@@
   thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]  
-  Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
+  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
   Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
@@
   mainPanel(
-    tabsetPanel("Example",
+    navlistPanel(
       tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
@@
                busyIndicator("Calculating results ...",wait = 0),
-                         renderUI({
-                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react()))
-                         })),
+               renderUI(
+                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react())))
+               )),
       tabPanel("Monthly and Yearly Returns, Low, 12m hold",
                busyIndicator("Calculating results ...",wait = 0),
-                         renderUI({
-                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react()))
-                         }))
-    ),style='width: 100%;'))
+               renderUI(
+                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react())))
+               )),
+      widths = c(3, 9)),style='width: 100%;'))
 ```
@@
 
-### Customized Buyback Index
+### Customized Buyback Indices
 
@@
     column(6,
-           selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[4], width = "425px"),
+           selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features,selected = "EU.Index", width = "425px"),
            checkboxInput("characteristic_irats1_sign", "Reverse", value = FALSE),
@@
 ```{r, eval=TRUE, echo = FALSE}
-selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low), 1 (middle), 2 (High) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
+selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low, <=), 1 (middle), 2 (High, >=) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
 ```
@@
 
-selectInput("quantile_used_all","Enter the quantile to use to define High and Low Firms for the total index created (sum of the scores of the firm characteristics selected):", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
+selectInput("quantile_used_all","Enter the quantile to use to define High (>=) and Low (<=) Firms for the total index created (sum of the scores of the firm characteristics selected):", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
 ```
@@
 <br> 
-Here are the results for your new index:
+Here are the results for your new customized index:
 
@@
 
-  Index_score = thefeature1 + 
-    ifelse(input$characteristic_irats2 != "None",thefeature2,0)+ 
-    ifelse(input$characteristic_irats3 != "None",thefeature3,0) + 
-    ifelse(input$characteristic_irats4 != "None",thefeature4,0) + 
-    ifelse(input$characteristic_irats5 != "None",thefeature5,0) + 
-    ifelse(input$characteristic_irats6 != "None",thefeature6,0)
   Index_score
@@
   res = round(cbind(
-    calendar_table(returns_by_event_monthly[, Low_feature_events],
-                   BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[Low_feature_events])$results,
-    calendar_table(returns_by_event_monthly[,High_feature_events],
-                   BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[High_feature_events])$results
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
+                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[Low_feature_events])$results,
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
+                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[High_feature_events])$results
   ),2)[reported_times,]
@@
   mainPanel(
-    tabsetPanel("Example",
+    navlistPanel(
       tabPanel("Histogram of the New Index",
@@
                busyIndicator("Calculating results ...",wait = 0),
-                         renderUI({
-                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index()))
-                         })),
+               renderUI(
+                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index())))
+               )),
       tabPanel("Monthly and Yearly Returns, Low, 12m hold",
                busyIndicator("Calculating results ...",wait = 0),
-                         renderUI({
-                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react_index()))
-                         }))
-    ),style='width: 100%;'))
+               renderUI(
+                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react_index())))
+               )),
+      widths = c(3, 9)),style='width: 100%;'))
 ```
@@
 <hr>
-As noted above **you can interactively change various report parameters throughout this document, and for any of your choices create a customized paper using the button at the begining of this page at any time.**
+As noted above **you can interactively change various report parameters throughout this tool, and for any of your choices create a customized paper using the button at the begining of this page at any time.**
 <br>

### 2016-05-12 Paper_global_parameters.R

@@ -1,3 +1,7 @@
+#  Copyright 2015, INSEAD
+#  by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
+#  Dual licensed under the MIT or GPL Version 2 licenses.
+
 ############################################################################################ 
 # All global parameters of the project
 ############################################################################################ 
@@ -59,7 +63,7 @@ years_across_cross_events = 4 # for BB then ISS or vice verca years.
 # Industries and industry filter
 
 All = 1:9999
-source("../../FinanceData/rawdata_fama_french/ff_industries_sic.R")
+source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
 Finance1 = 6000:6799
 # Select the industries to use
 Industries = All
@@ -118,26 +122,3 @@ BEAR_YEARS_text = list( #http://www.gold-eagle.com/article/history-us-bear-bull-
   dotcom = c("March 2000", "October 2002"),
   financial1 = c("October 2007", "March 2009")
 )
-
-
-if (0){
-  ##########################################################################################
-  ### OTHER THAT WE USED IN EARLIER VERSIONS. We may need these for earlier versions of the code
-  R2window = 180 # rolling window to get the R2 thresholds
-  VOLwindow = 180 # rolling window to get the R2 thresholds
-  LEVwindow = 180 # rolling window to get the R2 thresholds
-  EPSwindow = 180 # rolling window to get the R2 thresholds
-  randomizationiterations = 10 # how many times to run the volatility randomization test
-  MIN_ME_quantile = 0 # the minimum ff ME quantile
-  MAX_ME_quantile = 20 # the maximum ff ME quantile
-  MIN_BEME_quantile = 0 # the minimum ff BE/ME quantile
-  MAX_BEME_quantile = 20 # the maximum ff BE/ME quantile
-  days_live = 0 # minimum number of days a stock needs to be live before announcement date
-  remove_returns_outliers = 0 # remove the reutrns outliers?
-  MAX_DR_abs = 100 # Max absolute daily return to consider a stock is an outliers
-  max_vol_outlier = 100000.1 # max daily standard deviation in 6 months before announcement
-  MINIMUM_PERIOD_SINCE_LAST_EVENT = 0# we require that there were at least that many days before the previous event
-  CRISIS_SLACK_pre = 0 # in case we want to add some window around the recession years
-  CRISIS_SLACK_post = 0 # in case we want to add some window around the recession years
-  end_date_event = "Three.Month.After"
-}

### 2016-05-12 bb_issuers_new.R

@@ -1,3 +1,7 @@
+#  Copyright 2015, INSEAD
+#  by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
+#  Dual licensed under the MIT or GPL Version 2 licenses.
+
 
 ####################################################################################
 # These are one by one the tables in the .Rnw. 
@@ -108,6 +112,12 @@ Low_LEV_eventsBB  = scrub(tmp) < quantile(tmp[!is.na(tmp)], quantile_LEV)  & !is
 tmp = BUYBACK_DATA$DATASET$ibes$month_minus1$mean_rec_score
 High_EPS_eventsBB = scrub(tmp) > quantile(tmp[!is.na(tmp)], 1-quantile_EPS)  & !is.na(tmp)
 Low_EPS_eventsBB  = scrub(tmp) < quantile(tmp[!is.na(tmp)], quantile_EPS)  & !is.na(tmp)
+EUindex_bb = sapply(1:length(BUYBACK_DATA$DATASET$SDC$Event.Date), function(i){
+  ifelse(High_Idiosyncr_eventsBB[i], 2, ifelse(Low_Idiosyncr_eventsBB[i], 0, 1)) +
+    ifelse(High_VOL_eventsBB[i], 2, ifelse(Low_VOL_eventsBB[i], 0, 1)) +
+    ifelse(company_subset_undervalued_bb[i], 2, ifelse(company_subset_overvalued_bb[i], 0, 1))
+})
+
 rm("tmp")
 
 
@@ -497,11 +507,6 @@ Under_IdioBB_cor = cor(EU_index_features)
 
 ####################################################################################
 #round(EU_relations,1), 
-EUindex_bb = sapply(1:length(BUYBACK_DATA$DATASET$SDC$Event.Date), function(i){
-  ifelse(High_Idiosyncr_eventsBB[i], 2, ifelse(Low_Idiosyncr_eventsBB[i], 0, 1)) +
-    ifelse(High_VOL_eventsBB[i], 2, ifelse(Low_VOL_eventsBB[i], 0, 1)) +
-    ifelse(company_subset_undervalued_bb[i], 2, ifelse(company_subset_overvalued_bb[i], 0, 1))
-})
 
 all_fund_sources = unique(unlist(sapply(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code, function(i) unlist(str_split(i,"\\+")))))
 cash_funds = c("CR")

### 2016-05-12 create_bbissuers_data.R

@@ -1,3 +1,7 @@
+#  Copyright 2015, INSEAD
+#  by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
+#  Dual licensed under the MIT or GPL Version 2 licenses.
+
 if (memory.limit()<40*1024) memory.limit(40*1024) # allow at least 40GB of memory to be allocated (Windows)
 ##########################################################################################
 # Creates the data for the Buybacks-Issuers paper
@@ -12,7 +16,7 @@ source("../FinanceLibraries/latex_code.R")
 source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
 source("Paper_global_parameters.R")
 # Used to get WRDS data through the API
-source("../financedataDev/wrds_helpers.R", chdir=TRUE)
+source("../FinanceLibraries/wrds_helpers.R", chdir=TRUE)
 source("~/Documents/WRDS_Drivers/startWRDSconnection.R") # This file has the username pasword for WRDS. These lines below. See wrds_config.R in FinanceLibraries
 # wrds_user <- "my_username"
 # wrds_pass <- "{SAS002}DBCC5712369DE1C65B19864C1564FB850F398DCF"
@@ -31,7 +35,7 @@ if (1){
   GLOBAL_DAILY_DATABASE$volume_daily <- NULL
   GLOBAL_DAILY_DATABASE$recent_volatility_daily <- NULL
   GLOBAL_DAILY_DATABASE$FamaFrench_five_factors <- NULL
-} else{  # For next version of creating data directly from WRDS
+} else{ 
   GLOBAL_DAILY_DATABASE = list()
   GLOBAL_DAILY_DATABASE$returns_daily <- wrdsQueryStockFieldMatrix(wrds_handle, colnames(GLOBAL_MONTHLY_DATABASE$returns_monthly), "RET",start=as.Date("1980-01-01"))
 }

### 2016-05-12 filter_bbissuers_data.R

@@ -1,3 +1,7 @@
+#  Copyright 2015, INSEAD
+#  by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
+#  Dual licensed under the MIT or GPL Version 2 licenses.
+
 
 ##########################################################################################
 ##########################################################################################
@@ -62,6 +66,52 @@ if (length(to_remove) > 0){
   rm("field","field1")
 }
 ISSUERS_DATA$cleanupMissingSomeValues = length(to_remove)
+
+
+############################################################################################################
+
+if (remove_missing_permnosV2){
+  
+  # Buybacks first
+  to_remove = which(is.na(BUYBACK_DATA$DATASET$SDC$permnoV2))
+  if (length(to_remove) > 0){
+    # just in alphabetic order not to forget any    
+    BUYBACK_DATA$BEME_used <- BUYBACK_DATA$BEME_used[-to_remove]
+    BUYBACK_DATA$Performance_used <- BUYBACK_DATA$Performance_used[-to_remove]
+    BUYBACK_DATA$Size_used <- BUYBACK_DATA$Size_used[-to_remove]
+    BUYBACK_DATA$Valuation_Index <- BUYBACK_DATA$Valuation_Index[-to_remove]
+    
+    BUYBACK_DATA$DATASET$returns_by_event_monthly <- BUYBACK_DATA$DATASET$returns_by_event_monthly[,-to_remove]
+    BUYBACK_DATA$DATASET$SDC <- BUYBACK_DATA$DATASET$SDC[-to_remove,]
+    for(field in ls(BUYBACK_DATA$DATASET$CRSP))  BUYBACK_DATA$DATASET$CRSP[[field]] <- BUYBACK_DATA$DATASET$CRSP[[field]][-to_remove]
+    for(field1 in ls(BUYBACK_DATA$DATASET$ibes))  
+      for (field in ls(BUYBACK_DATA$DATASET$ibes[[field1]])) 
+        BUYBACK_DATA$DATASET$ibes[[field1]][[field]]<- BUYBACK_DATA$DATASET$ibes[[field1]][[field]][-to_remove]
+    rm("field","field1")
+  }
[…]

### 2016-05-12 index.Rmd
industries

@@
-<!--
- Copyright 2015, INSEAD
- by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
- Dual licensed under the MIT or GPL Version 2 licenses.  -->
-
 ---
@@
 ```{r, eval=TRUE, echo = FALSE,message=FALSE}
+# Copyright 2015, INSEAD
+# by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
+# Dual licensed under the MIT or GPL Version 2 licenses.  
+```
+
+```{r, eval=TRUE, echo = FALSE,message=FALSE}
 # need this to avoid loading the R libraries when the tool is deployed on shinyapps (needs to be 1 when run localy, 1 when deployed on a shinyapps server)
 
-run_shiny_tool = 0
+run_shiny_tool = 1
 
@@
 source("interactive_tool_files/heatmapOutput.R") 
+source("interactive_tool_files/ff_industries_sic.R")
 

### 2016-05-12 Paper_global_parameters.R

@@ -63,7 +63,6 @@ years_across_cross_events = 4 # for BB then ISS or vice verca years.
 # Industries and industry filter
 
 All = 1:9999
-source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
 Finance1 = 6000:6799
 # Select the industries to use
 Industries = All

### 2016-05-12 manuscriptJF.Rnw
tool update + copyright
latex

@@
 
-source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
-source("../FinanceLibraries/latex_code.R")
-source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
+source("interactive_tool_files/lib_helpers.R", chdir=TRUE)
+source("interactive_tool_files/latex_code.R")
+source("interactive_tool_files/ff_industries_sic.R")
 source("Paper_global_parameters.R")

### 2016-05-12 index.Rmd
minor

@@
 
-selectInput("quantile_used","Enter the quantile to use to define High (>=) and Low (<=) Firms:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
+selectInput("quantile_used","Enter the quantile to use to define High (>=) and Low (<=) Firms:", choices = 0.02*(1:20), selected = "0.1", width = "1000px")
 
@@
 ```{r, eval=TRUE, echo = FALSE}
-selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low, <=), 1 (middle), 2 (High, >=) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
+selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low, <=), 1 (middle), 2 (High, >=) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.1", width = "1000px")
 ```
@@
 
-selectInput("quantile_used_all","Enter the quantile to use to define High (>=) and Low (<=) Firms for the total index created (sum of the scores of the firm characteristics selected):", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
+selectInput("quantile_used_all","Enter the quantile to use to define High (>=) and Low (<=) Firms for the total index created (sum of the scores of the firm characteristics selected):", choices = 0.02*(1:20), selected = "0.1", width = "1000px")
 ```

### 2016-05-13 index.Rmd
cleanup tool

@@
 
+### Buybacks and Firm Characteristics
+
+The article relates 5 firm characteristics (pre-buyback-announcement returns, idiosyncratic volatility, and volatility, as well as BE/ME and Firm Size).
+This tool allows the user to study the effects of combining any of these firm characteristics, as well as others not discussed in the paper.
+We consider here high/low events defined using the quantiles of the selected event charactetistic.
+
+```{r, eval=TRUE, echo = FALSE}
+selectInput("characteristic_single_analysis", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features,selected = "EU.Index", width = "1000px")
+
+selectInput("quantile_used","Enter the quantile to use to define High (>=) and Low (<=) Firms:", choices = 0.02*(1:20), selected = "0.1", width = "1000px")
+
+checkboxInput("characteristic_single_analysis_sign", "If you would like to change the sign of the firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
+
+feature_IRATStable <- reactive({
+  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
+  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
+  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
+  quantile_used_ind = as.numeric(input$quantile_used)
+
+  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),1-quantile_used_ind)
+  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),quantile_used_ind)
+
+  res = round(cbind(
+    car_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
+              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
+    car_table(DATASET_NEW()$returns_by_event_monthly[, High_feature_events],
+              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
+  ),2)[reported_times,]
+
+  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
+  as.data.frame(res)
+})
+
+feature_CALtable <- reactive({
+  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
+  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
+  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
+  quantile_used_ind = as.numeric(input$quantile_used)
+
+  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),1-quantile_used_ind)
+  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),quantile_used_ind)
+
+  res = round(cbind(
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
+                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[Low_feature_events])$results,
+    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
+                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[High_feature_events])$results
+  ),2)[reported_times,]
+
+  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
+  as.data.frame(res)
+})
+
+High_feature_Hedged_react <- reactive({
+  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
+  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
+  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
+  quantile_used_ind = as.numeric(input$quantile_used)
+
+  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),1-quantile_used_ind)
+
+  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
+  remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
+})
+
+Low_feature_Hedged_react <- reactive({
+  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
+  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
+  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
+  quantile_used_ind = as.numeric(input$quantile_used)
+
+  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),quantile_used_ind)
+
+  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
+  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
+})
+
+```
+
+<br>
+
+```{r, eval=TRUE, echo = FALSE}
+fluidPage(
+  mainPanel(
+    navlistPanel(
+      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
+               busyIndicator("Calculating results ...",wait = 0),
+               renderTable({
+                 feature_IRATStable()
+               })),
+      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
+               busyIndicator("Calculating results ...",wait = 0),
+               renderTable({
+                 feature_CALtable()
+               })),
+      tabPanel("Cumulative Abnormal Returns,High, 12m hold",
+               busyIndicator("Calculating results ...",wait = 0),
+               renderDygraph({
+                 pnl_plot_interactive(High_feature_Hedged_react())
+               })),
+      tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
+               busyIndicator("Calculating results ...",wait = 0),
+               renderDygraph({
+                 pnl_plot_interactive(Low_feature_Hedged_react())
+               })),
+      tabPanel("Monthly and Yearly Returns, High, 12m hold",
+               busyIndicator("Calculating results ...",wait = 0),
+               renderUI(
+                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react())))
+               )),
+      tabPanel("Monthly and Yearly Returns, Low, 12m hold",
+               busyIndicator("Calculating results ...",wait = 0),
+               renderUI(
+                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react())))
+               )),
+      widths = c(3, 9)),style='width: 100%;'))
+```
+
+<hr>
+
 ### The EU-Index
 
-For the subset of events selected the High/Low EU index events (for the selected thresholds) have the abnormal returns below:
+For the subset of events selected the High/Low EU index events (for the selected EU thresholds below - you may need to change them depending on the sample of events used) have these abnormal returns:
 
@@
 
-### Buybacks and Firm Characteristics
-
-The article relates 5 firm characteristics (pre-buyback-announcement returns, idiosyncratic volatility, and volatility, as well as BE/ME and Firm Size).
-This tool allows the user to study the effects of combining any of these firm characteristics, as well as others not discussed in the paper.
-We consider here high/low events defined using the quantiles of the selected event charactetistic.
-
-```{r, eval=TRUE, echo = FALSE}
-selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features,selected = "EU.Index", width = "1000px")
-
-selectInput("quantile_used","Enter the quantile to use to define High (>=) and Low (<=) Firms:", choices = 0.02*(1:20), selected = "0.1", width = "1000px")
-
-checkboxInput("characteristic_irats_sign", "If you would like to change the sign of the firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
-
-feature_IRATStable <- reactive({
-  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
-  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]
-
-  thefeature = as.numeric(scrub(thefeature))
-  quantile_used_ind = as.numeric(input$quantile_used)
-
-  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
-  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)
-
-  res = round(cbind(
-    car_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
-              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
-    car_table(DATASET_NEW()$returns_by_event_monthly[, High_feature_events],
-              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
-  ),2)[reported_times,]
-
-  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
-  as.data.frame(res)
-})
-
-feature_CALtable <- reactive({
-   thesign = ifelse(input$characteristic_irats_sign, -1, +1)
-  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]
-
-  thefeature = as.numeric(scrub(thefeature))
-  quantile_used_ind = as.numeric(input$quantile_used)
-
-  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
-  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)
-
-  res = round(cbind(
-    calendar_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
-                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[Low_feature_events])$results,
-    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
-                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[High_feature_events])$results
-  ),2)[reported_times,]
-
-  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
-  as.data.frame(res)
-})
-
-High_feature_Hedged_react <- reactive({
-  thefeature = as.numeric(DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]])
-  quantile_used <- as.numeric(input$quantile_used)
-
-  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used)
-
-  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
-  remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
-})
-
-Low_feature_Hedged_react <- reactive({
-  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]  
-  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
-  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
-  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
-})
-
-```
-
-<br>
-
-```{r, eval=TRUE, echo = FALSE}
-fluidPage(
-  mainPanel(
-    navlistPanel(
-      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
-               busyIndicator("Calculating results ...",wait = 0),
-               renderTable({
-                 feature_IRATStable()
-               })),
-      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
-               busyIndicator("Calculating results ...",wait = 0),
-               renderTable({
-                 feature_CALtable()
-               })),
-      tabPanel("Cumulative Abnormal Returns,High, 12m hold",
-               busyIndicator("Calculating results ...",wait = 0),
-               renderDygraph({
-                 pnl_plot_interactive(High_feature_Hedged_react())
-               })),
-      tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
-               busyIndicator("Calculating results ...",wait = 0),
-               renderDygraph({
-                 pnl_plot_interactive(Low_feature_Hedged_react())
-               })),
-      tabPanel("Monthly and Yearly Returns, High, 12m hold",
-               busyIndicator("Calculating results ...",wait = 0),
-               renderUI(
-                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react())))
-               )),
-      tabPanel("Monthly and Yearly Returns, Low, 12m hold",
-               busyIndicator("Calculating results ...",wait = 0),
-               renderUI(
-                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react())))
-               )),
-      widths = c(3, 9)),style='width: 100%;'))
-```
-
-<hr>
-<hr>
-
 ### Customized Buyback Indices
@@
   thefeature1 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats1)]]  
-  High_feature_events1 = (scrub(thefeature1) >= quantile(thefeature1[!is.na(thefeature1)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
-  Low_feature_events1 = (scrub(thefeature1) <= quantile(thefeature1[!is.na(thefeature1)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
+  thefeature1Q = (thesign==-1) + thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_irats1)]]  
+  High_feature_events1 = (scrub(thefeature1) >= quantile(thefeature1Q[!is.na(thefeature1Q)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
+  Low_feature_events1 = (scrub(thefeature1) <= quantile(thefeature1Q[!is.na(thefeature1Q)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
 
@@
     thefeature2 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats2)]]  
-    High_feature_events2 = (scrub(thefeature2) >= quantile(thefeature2[!is.na(thefeature2)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
-    Low_feature_events2 = (scrub(thefeature2) <= quantile(thefeature2[!is.na(thefeature2)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
+    thefeature2Q = (thesign==-1) + thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_irats2)]]  
+    High_feature_events2 = (scrub(thefeature2) >= quantile(thefeature2Q[!is.na(thefeature2Q)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
+    Low_feature_events2 = (scrub(thefeature2) <= quantile(thefeature2Q[!is.na(thefeature2Q)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
   }

### 2016-05-15 index.Rmd
minor rename

@@
 
-source("interactive_tool_files/lib_helpers.R", chdir=TRUE)
-source("interactive_tool_files/ff_industries_sic.R")
+source("library_files/lib_helpers.R", chdir=TRUE)
+source("library_files/ff_industries_sic.R")
 source("Paper_global_parameters.R")
-source("interactive_tool_files/heatmapOutput.R") 
-source("interactive_tool_files/ff_industries_sic.R")
+source("library_files/heatmapOutput.R") 
+source("library_files/ff_industries_sic.R")
 

### 2016-05-15 manuscriptJF.Rnw
test
almost final
minor
minor rename

@@
+%  Copyright 2015, INSEAD
+%  by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
+%  Dual licensed under the MIT or GPL Version 2 licenses.
+
 << eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
@@
 
-source("interactive_tool_files/lib_helpers.R", chdir=TRUE)
-source("interactive_tool_files/latex_code.R")
-source("interactive_tool_files/ff_industries_sic.R")
+source("library_files/lib_helpers.R", chdir=TRUE)
+source("library_files/latex_code.R")
+source("library_files/ff_industries_sic.R")
 source("Paper_global_parameters.R")
@@
 Combining volatility with undervaluation indicators proposed by \cite{PeyerVermaelen2009} improves the predictive power of excess returns after buyback announcements.
+
 \end{abstract}
 \vspace{2cm}
+
+\noindent An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, is available at \href{http://tevgeniou.github.io/BuybacksIssuers/}{tevgeniou.github.io/BuybacksIssuers.}
 

### 2016-05-15 bb_issuers_new.R

@@ -9,9 +9,9 @@
 
 rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
 
-source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
-source("../FinanceLibraries/latex_code.R")
-source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
+source("library_files/lib_helpers.R", chdir=TRUE)
+source("library_files/latex_code.R")
+source("library_files/ff_industries_sic.R")
 source("Paper_global_parameters.R")
 
 initial_vars = ls(all = TRUE) # takes time to save and load, so we save only what is needed at the end. 

### 2016-05-15 create_bbissuers_data.R

@@ -11,9 +11,9 @@ rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
 
 use_major_market_score = 0 # We use all CRSP universe for the scores 
 
-source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
-source("../FinanceLibraries/latex_code.R")
-source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
+source("library_files/lib_helpers.R", chdir=TRUE)
+source("library_files/latex_code.R")
+source("library_files/ff_industries_sic.R")
 source("Paper_global_parameters.R")
 # Used to get WRDS data through the API
 source("../FinanceLibraries/wrds_helpers.R", chdir=TRUE)

### 2016-05-15 interactive_tool_files/ff_industries_sic.R

@@ -1,55 +1,0 @@
-FF_industries = list(
- Agriculture = c(0100:0199, 0200:0299, 0700:0799, 0910:0919, 2048:2048),
- Food_Prod. = c(2000:2009, 2010:2019, 2020:2029, 2030:2039, 2040:2046, 2050:2059, 2060:2063, 2070:2079, 2090:2092, 2095:2095, 2098:2099),
- Candy_Soda = c(2064:2068, 2086:2086, 2087:2087, 2096:2096, 2097:2097),
- Beer_Liquor = c(2080:2080, 2082:2082, 2083:2083, 2084:2084, 2085:2085),
- Tobacco = c(2100:2199),
- Recreation = c(0920:0999, 3650:3651, 3652:3652, 3732:3732, 3930:3931, 3940:3949),
- Entertainment = c(7800:7829, 7830:7833, 7840:7841, 7900:7900, 7910:7911, 7920:7929, 7930:7933, 7940:7949, 7980:7980, 7990:7999),
- Print_Pub. = c(2700:2709, 2710:2719, 2720:2729, 2730:2739, 2740:2749, 2770:2771, 2780:2789, 2790:2799),
- Consumer_Goods = c(2047:2047, 2391:2392, 2510:2519, 2590:2599, 2840:2843, 2844:2844, 3160:3161, 3170:3171, 3172:3172, 3190:3199, 3229:3229, 3260:3260, 3262:3263, 3269:3269, 3230:3231, 3630:3639, 3750:3751, 3800:3800, 3860:3861, 3870:3873, 3910:3911, 3914:3914, 3915:3915, 3960:3962, 3991:3991, 3995:3995),
- Apparel = c(2300:2390, 3020:3021, 3100:3111, 3130:3131, 3140:3149, 3150:3151, 3963:3965),
- Healthcare = c(8000:8099),
- Med._Equip. = c(3693:3693, 3840:3849, 3850:3851),
- Pharm._Prod. = c(2830:2830, 2831:2831, 2833:2833, 2834:2834, 2835:2835, 2836:2836),
- Chemicals = c(2800:2809, 2810:2819, 2820:2829, 2850:2859, 2860:2869, 2870:2879, 2890:2899),
- Plastic_Prod. = c(3031:3031, 3041:3041, 3050:3053, 3060:3069, 3070:3079, 3080:3089, 3090:3099),
[…]

### 2016-05-15 interactive_tool_files/heatmapOutput.R

@@ -1,108 +1,0 @@
-
-#  Copyright 2013, Satrapade
-#  by V. Kapartzianis 
-#  Dual licensed under the MIT or GPL Version 2 licenses.
-
-library(shiny)
-library(htmlwidgets)
-renderHeatmapX <- function(data, style="norm", include.rownames = TRUE, include.colnames=TRUE, nsmall=2, border=0) {
-  #vmax <- max(Filter(is.numeric, data))
-  vmax = max(data[is.numeric(data) & !is.na(data)])
-  sigmoid <- function(v) { return(1 / (1 + exp(-v))) }
-  toRGB <- function(intensity, sign) {
-    rgb <- "rgb("
-    darkness <- floor((1 - intensity) * 256)
-    if(is.na(sign)) 
-      rgb <- paste(rgb,"255,255,255",sep="")
-    else if(sign) 
-      rgb <- paste(rgb, darkness, ",255,", darkness, sep="")
-    else
-      rgb <- paste(rgb, "255,", darkness, ",", darkness, sep="")
-    rgb <- paste(rgb, ")", sep="")
-    return (rgb)
-  }
-  heatmap <- function(x, style="norm") {
-    if ("squashed" == style) {
-      squashed <- sigmoid(x) - 0.5
-      intensity <- abs(squashed) / 0.5
-      rgb <- toRGB(intensity, squashed >= 0)
-    } else { # ("norm" == style)
-      intensity <- abs(x) / vmax
-      rgb <- toRGB(intensity, x > 0)
-    }
-    return (paste("background-color:", rgb))
-  }
-  if (is.null(colnames(data))) colnames(data) <- 1:ncol(data)
-  if (is.null(rownames(data))) rownames(data) <- 1:nrow(data)  
-  as.character(
-    tags$table(
-      border = border,
-      class = 'data table table-bordered table-condensed',
-      tagList({
-        if (include.colnames)
-          tags$thead(
-            class = 'thead',
-            tags$tr(
-              tagList({
-                if (include.rownames)
-                  tags$th()
-                else
-                  list()
-              }),
-              lapply(colnames(data), function(name) {
-                tags$th(name)
-              })
-            )
-          )
-        else
-          list()
-      }),
-      tags$tbody(
-        lapply(1:nrow(data), function(i) {
-          tags$tr(
-            tagList({
-              if (include.rownames)
-                tags$td(
-                  align="right",
-                  rownames(data)[i]
-                )
-              else
-                list()
-            }),
[…]

### 2016-05-15 interactive_tool_files/latex_code.R

@@ -1,643 +1,0 @@
-#  Copyright 2013, Satrapade
-#  by T. Evgeniou, V. Kapartzianis, N. Nassuphis and D. Spinellis
-#  Dual licensed under the MIT or GPL Version 2 licenses.
-#  11/2015 functions printLatexTable and printLatexTable2 added by T. Evgeniou and E. Junqué de Fortuny
-
-
-######################################################################################
-## Latex commands
-######################################################################################
-
-tostars <- function(x) ifelse(abs(x)<=0.01,"**",ifelse(abs(x)<=0.05,"*",ifelse(abs(x)<=0.1,"$^+$","")))
-
-# CAN EDIT TO PRINT OUT WHATEVER LATEX WE NEED  
-latex_render_data_frame<-function(x,y=NULL, title="",caption="",label="",columns=NULL,bigtitleontop = F,show_rownames=FALSE,red_text="",green_text="",blue_text="",scale=1,digits,lastSpecial=F,dorotate=F, tostars_used = function(r) "") {
-  #Helper functions
-  p <- function(...){paste(...)}
-  pn <- function(...){paste(...,"\n")} #print newline
-  pc <- function(...){paste(...,"&")}  #print column
-
-  if(dorotate){
-    width = "\\linewidth"
-  } else {
-    width = "\\textwidth"
-  }  
-  #Start the table definition
-  l <- ""  
-  if(dorotate){
-    l <- pn(l,"\\clearpage\n")
-    l <- pn(l,"\\footnotesize")
-    l <- pn(l,"\\begin{landscape}")
-  }
-  l <- pn(l,"\\begin{table}[!htb]")
-  l <- pn(l," \\setlength\\tabcolsep{1pt}")
-  l <- pn(l,"\\centering")
-  #l <- pn(l,"\\medskip")
-  if(bigtitleontop){
-    if(title!="")
-      if(dorotate) {
-        l <- pn(l,"\\captionof{table}{",title,"}")
-      }else {
-        l <- pn(l,"\\caption{",title,"}")
-      }
-    if(caption!="") {
-      l <- pn(l,"\\parbox{",width,"}")
-      l <- pn(l,"{\\scriptsize \\singlespacing",caption,"}\\\\")
-      l <- pn(l,"\\vspace{.2in}")
-      
-    }
-  }
[…]

### 2016-05-15 interactive_tool_files/lib_helpers.cpp

@@ -1,88 +1,0 @@
-//  Copyright 2016, INSEAD
-//  by V. Kapartzianis 
-//  Dual licensed under the MIT or GPL Version 2 licenses.
-
-#include <Rcpp.h>
-using namespace Rcpp;
-
-// [[Rcpp::plugins(openmp)]]
-
-// [[Rcpp::export]]
-NumericVector row_weights(NumericMatrix x, NumericVector weight) {
-  int nX = x.ncol();
-  int nY = x.nrow();
-  NumericVector v = no_init(nY);
-  
-  #pragma omp parallel for schedule(static)
-  for (int i=0; i < nY; i++) {
-    NumericMatrix::Row row = x(i, _);
-
-    double w = 0;
-    for (int j=0; j < nX; j++) {
-      if(row[j]!=0 && !R_IsNA(row[j])) {
-        w += weight[j];
-      }
-    }
-
-    double o = 0;
-    if (w!=0) {
-      for(int j=0; j < nX; j++) {
-        if(row[j]!=0 && !R_IsNA(row[j])) {
-          o += row[j]*weight[j] / w;
-        }
-      }
-    }
-    
-    v[i] = o;
-  }
-  
-  v.attr("names") = rownames(x);
-  return v;
-}
-
-
-// [[Rcpp::export]]
-NumericMatrix calendar_table_helper1(NumericMatrix x, NumericVector Row_Date_number, NumericVector Event_Date_number, NumericVector hitnow) {
-//NOTE: it would be much faster to update the matrix without cloning it, but
-//that could lead to unexpected bugs, as R wouldn't know the matrix was updated.
-  NumericMatrix ret = Rcpp::clone(x);
-  int nX = ret.ncol();
-  int nY = ret.nrow();
-  
-  #pragma omp parallel for schedule(static)
-  for (int col=0; col < nX; col++) {
-    for (int row=0; row < nY; row++) {
-      if (Row_Date_number[row] <= Event_Date_number[col] || Row_Date_number[row] > hitnow[col]) {
-        ret(row, col) = 0;
-      }
-    }
-  }
-  return ret;
-}
-// [[Rcpp::export]]
-NumericMatrix calendar_table_helper2(NumericMatrix x, NumericVector Row_Date_number, NumericVector Event_Date_number, NumericVector hitnow) {
-//NOTE: it would be much faster to update the matrix without cloning it, but
[…]

### 2016-05-15 index.Rmd
tool deployment

@@
 ```{r, eval=TRUE, echo = FALSE,message=FALSE}
-# need this to avoid loading the R libraries when the tool is deployed on shinyapps (needs to be 1 when run localy, 1 when deployed on a shinyapps server)
+# need this to avoid loading the R libraries when the tool is deployed on shinyapps (needs to be 0 when run localy, 1 when deployed on a shinyapps server)
 
@@
 
-if(run_shiny_tool) {
+if(!run_shiny_tool) {
   library(googleVis)
@@
   library("ggplot2")
-}
+} #else{
+  #install.packages("Rcpp")
+#}
 
@@
       #file.exists()
-      tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
-      newinput <- list()
-      for(i in tosave) {
-        newinput[[i]] <- input[[i]]
-      }
+      #tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
+      #newinput <- list()
+      #for(i in tosave) {
+      #  newinput[[i]] <- input[[i]]
+      #}
       # Not yet available

### 2016-05-15 library_files/lib_helpers.R

@@ -15,7 +15,7 @@ if (ifelse(!exists("run_shiny_tool"), T, run_shiny_tool == 0)) { # When deployin
     })
   }
   libraries_used=c("stringr","gtools","foreign","reshape2","digest","timeDate","devtools","knitr","graphics",
-                   "grDevices","xtable","sqldf","stargazer","data.table",
+                   "grDevices","xtable","sqldf","stargazer","data.table","shiny","htmlwidgets",
                    "Hmisc","vegan","fpc","GPArotation","FactoMineR","cluster",
                    "psych","stringr","googleVis", "png","ggplot2","googleVis", "gridExtra","RcppArmadillo","xts","DescTools")
   

### 2016-05-16 index.Rmd
tool

@@
   library("shinysky") #  devtools::install_github("AnalytixWare/ShinySky")
-
+  library("htmlwidgets")
   library("stringr")
@@
 
-source("library_files/lib_helpers.R", chdir=TRUE)
-source("library_files/ff_industries_sic.R")
+source("lib_helpers.R", chdir=TRUE, local = TRUE)
+source("latex_code.R", chdir=TRUE, local = TRUE)
+source("ff_industries_sic.R", chdir=TRUE, local = TRUE)
 source("Paper_global_parameters.R")
-source("library_files/heatmapOutput.R") 
-source("library_files/ff_industries_sic.R")
+source("heatmapOutput.R", chdir=TRUE, local = TRUE) 
+source("ff_industries_sic.R", chdir=TRUE, local = TRUE)
 
@@
 ```{r, fig.width=6, fig.height=5,echo=FALSE}
+suppressPackageStartupMessages(library(shinyjs))
 shinyApp(
   ui = fluidPage(
-    fluidRow(
-      column(2,
-             conditionalPanel(
-               condition = "!$('makeReport').hasClass('shiny-busy')",
-               actionButton("makeReport","Generate Report (Work in Progress)",icon=icon("file"))
-             )
+    useShinyjs(),
+    actionButton("compileReport","Compile Report",icon=icon("spinner")),
+    downloadButton("downloadReport", "Download Report")
   ),
-      column(4,
-             conditionalPanel(
-               condition = "!$('makeReport').hasClass('shiny-busy')",
-               uiOutput("downloadButton")
-               #downloadButton("downloadReport", "Download Report")
-             )
-      )
-    ),
-    busyIndicator("Please wait while we prepare the report ...",wait = 0)
-  ),
-  server = function(input, output) {
-    output$download_button <- renderUI({
-      downloadButton("downloadReport", "Download Results")
+  server = function(input, output, session) {
+    disable("downloadReport")
+    report.data <- paste0("session.", session$token, ".report.data.Rdata")
+    report.script <- paste0("session.", session$token, ".report.script.R")
+    report.source <- paste0("session.", session$token, ".report.Rnw")
+    report.file <- paste0("session.", session$token, ".report.pdf")
+    observeEvent(input$compileReport, {
+      disable("compileReport")
+      report.list <- list("startdate","enddate","market_cap_min","market_cap_max","characteristic", "characteristic_single_analysis", "quantile_used", "characteristic_single_analysis_sign", "high_EU_index_thres", "low_EU_index_thres", "quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
+      save(report.list, file=report.data)
+      file.copy("toolreport.Rnw", report.source)
+      cat(paste0("load ('", report.data, "')\n"), file=report.script)
+      cat(paste0("knitr::knit2pdf('", report.source,"')\n"), file=report.script, append=TRUE)
+      system(paste0("Rscript --vanilla ", report.script), wait=FALSE)
     })
-    makeReportAction <- eventReactive(input$makeReport, {
-      #Create the pdf here
-      #Sys.sleep(1);return()
-      #first check if we didn't already create a paper with these parameters, if so, load from cache
-      #filename <- paste("reports/")
-      #file.exists()
-      #tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
-      #newinput <- list()
-      #for(i in tosave) {
-      #  newinput[[i]] <- input[[i]]
-      #}
-      # Not yet available
-      #knitr::knit2pdf("report.Rnw",envir=globalenv())
-    })
-    output$downloadButton <- renderUI({
-      makeReportAction() #only appear after first click on generate
-      downloadButton("downloadReport", "Download Report")
+    observe({
+      invalidateLater(1000, session)
+      if (file.exists(report.file)) enable("downloadReport")
     })
@@
       content = function(file) {
-        cat(paste("Does the pdf exist?",file.exists("report.pdf")))
-        file.rename(normalizePath('report.pdf'), file)
+        file.copy(report.file, file)
+        file.remove(list.files(pattern=paste0("session.", session$token)))
+        enable("compileReport")
+        disable("downloadReport")
       }
     )
-  },
-  options = list(height = 120,width=800)
+  }
 )

### 2016-05-16 toolreport.Rnw
tool

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=

inline_hook <- function (x) {
  if (is.numeric(x)) {
    # ifelse does a vectorized comparison
    # If integer, print without decimal; otherwise print two places
    res <- ifelse(x == round(x),
                  # use comma for 1000s
                  sprintf("%s", prettyNum(x, big.mark=",")),
                  sprintf("%.2f", x)
    )
    paste(res, collapse = ", ")
  } else {
    x
  }
}
knit_hooks$set(inline = inline_hook)

###

source("lib_helpers.R", chdir=TRUE)
source("latex_code.R")
source("ff_industries_sic.R")
source("Paper_global_parameters.R")

# All the report parameters
startdate = report.list$startdate
enddate= report.list$enddate
market_cap_min = report.list$market_cap_min
market_cap_max= report.list$market_cap_max
characteristic= report.list$characteristic
characteristic_single_analysis= characteristic_single_analysis
quantile_used = report.list$quantile_used
characteristic_single_analysis_sign= report.list$characteristic_single_analysis_sign 
high_EU_index_thres= report.list$high_EU_index_thres 
low_EU_index_thres= report.list$low_EU_index_thres 
quantile_used_ind= report.list$quantile_used_ind
quantile_used_all= report.list$quantile_used_all
characteristic_irats1= report.list$characteristic_irats1
characteristic_irats2= report.list$characteristic_irats2
characteristic_irats3= report.list$characteristic_irats3
characteristic_irats4= report.list$characteristic_irats4
characteristic_irats5= report.list$characteristic_irats5
characteristic_irats6= report.list$characteristic_irats6
characteristic_irats1_sign= report.list$characteristic_irats1_sign
characteristic_irats2_sign= report.list$characteristic_irats2_sign
characteristic_irats3_sign= report.list$characteristic_irats3_sign 
characteristic_irats4_sign= report.list$characteristic_irats4_sign
characteristic_irats5_sign= report.list$characteristic_irats5_sign
characteristic_irats6_sign = report.list$characteristic_irats6_sign

###
@

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
# Filter the data now - as in Index.rmd

starting = startdate 
ending = enddate   
if (ending - starting < 3*365)
  ending = starting + 3*365

market_cap_min = as.numeric(market_cap_min)
market_cap_max = as.numeric(market_cap_max)
if (market_cap_max < market_cap_min)
  market_cap_max = ceiling(max(BUYBACK_DATA_TOOL$Market.Cap))

useonly_industry = !(BUYBACK_DATA_TOOL$Industry_name %in% industry)

useonly_report = which(BUYBACK_DATA_TOOL$Event.Date >= starting & BUYBACK_DATA_TOOL$Event.Date <= ending &
                         scrub(BUYBACK_DATA_TOOL$Market.Cap) >= market_cap_min & 
                         scrub(BUYBACK_DATA_TOOL$Market.Cap) <= market_cap_max &
                         useonly_industry)

DATASET_NEW = list(
  BUYBACK_DATA_TOOL=BUYBACK_DATA_TOOL[useonly_report,],
  returns_by_event_monthly = returns_by_event_monthly[,useonly_report],
  DatesMonth  = DatesMonth[,useonly_report],
  value.weights = value.weights[useonly_report],
  subset = useonly_report
)

@

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=

firstyear = as.character(format(stardate,"%Y"))
lastyear = as.character(format(enddate,"%Y"))
report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)
value.weights = rep(1,length(BUYBACK_DATA_TOOL$Prior.Returns.Score))

@

\documentclass{article}

\begin{document}

\title{\textbf{Volatility and the Buyback Anomaly: Online Interactive Tool Report}}%\footnotetext{}

\author{\uppercase{ Theodoros Evgeniou$^*$, Enric Junqu\'e de Fortuny$^{**}$,\\
Nick Nassuphis$^{***}$,} and \uppercase{Theo Vermaelen}\thanks{INSEAD, Bd de Constance, 77300 Fontainebleau, France, phone: +33(0)1 6072 4000, $^{**}$Rotterdam School of Management, Burgemeester Oudlaan 50, 3062 PA Rotterdam, The Netherlands, $^{***}$31, St. Martin's Lane WC2N 4ER London, United Kingdom, e-mail:   \href{mailto:theodoros.evgeniou@insead.edu}{theodoros.evgeniou@insead.edu}, \href{mailto:enric.junquedefortuny@insead.edu}{enric.junquedefortuny@rsm.nl},  \href{mailto:nicknassuphis@gmail.com}{nicknassuphis@gmail.com}, and \href{mailto:theo.vermaelen@insead.edu}{theo.vermaelen@insead.edu}. }}

\date{\today}              % No date for final submission

% Create title page with no page number

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\singlespacing

\maketitle

\vspace{-.2in}
\begin{abstract}
\noindent This is a customized report of the online interactive tool for the paper "{\it Volatility and the Buyback Anomaly}" by T. Evgeniou, Enric Junqu\'e de Fortuny, Nick Nassuphis, and Theo Vermaelen.

\end{abstract}
\vspace{2cm}

\medskip
%\noindent \textit{Keywords}: Share Buybacks; Seasoned Equity Offerings; Anomalies; Volatility

\thispagestyle{empty}

\setcounter{page}{1}

\doublespacing

\section{Report Parameters}
\label{sec:parameters}

The time period used in this report is from \Sexpr{startdate} to \Sexpr{enddate}. We only consider firms with a market capitalization the month before the event being between \Sexpr{market_cap_min} and \Sexpr{market_cap_max}. In addition to the financial and utilities sectors, we also remove the following sectors: \Sexpr{paste(industry, sep=", ")}.

\section{\Sexpr{gsub("\\.", " ", characteristic_single_analysis)} and Excess Returns}

Ww consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the quantiles of events defined using the selected event characteristics, namely \Sexpr{gsub("\\.", " ", characteristic_single_analysis)}. Table \ref{tbl:indcharacteristic} shows the results. Figure \ref{fig:indcharacteristic} shows the excess returns of a strategy for that trades only the high or low quantile stocks for this event characteristics (the strategy is designed as described in the paper). Table \ref{tbl:indcharacteristicpnl} shows the monthly and yearly returns of the "high" events strategy.

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
# FOllowing Index.Rmd, generate first the tables as needed

thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
thefeature = thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
quantile_used_ind = as.numeric(input$quantile_used)

High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),1-quantile_used_ind)
Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),quantile_used_ind)

res = round(cbind(
  car_table(DATASET_NEW$returns_by_event_monthly[, Low_feature_events],
            DATASET_NEW$BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
  car_table(DATASET_NEW$returns_by_event_monthly[, High_feature_events],
            DATASET_NEW$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
),2)[reported_times,]

colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
feature_IRATStable = as.data.frame(res)

##
thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
thefeature = thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
quantile_used_ind = as.numeric(input$quantile_used)

High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),1-quantile_used_ind)
Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),quantile_used_ind)

res = round(cbind(
  calendar_table(DATASET_NEW$returns_by_event_monthly[, Low_feature_events],
                 DATASET_NEW$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW$value.weights[Low_feature_events])$results,
  calendar_table(DATASET_NEW$returns_by_event_monthly[,High_feature_events],
                 DATASET_NEW$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW$value.weights[High_feature_events])$results
),2)[reported_times,]

colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
feature_CALtable= as.data.frame(res)

##
thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
thefeature = thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
quantile_used_ind = as.numeric(input$quantile_used)

High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),1-quantile_used_ind)

High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW$DatesMonth, DATASET_NEW$returns_by_event_monthly,event=1),1,non_zero_mean)
High_feature_Hedged_react = remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)

##
thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
thefeature = thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
quantile_used_ind = as.numeric(input$quantile_used)

Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),quantile_used_ind)

Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW$DatesMonth, DATASET_NEW$returns_by_event_monthly,event=1),1,non_zero_mean)
Low_feature_Hedged_react = remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)

@

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp = cbind(feature_IRATStable,feature_CALtable)[reported_times,]
colnames(tmp)[1]<-colnames(tmp)[4] <-  "CAR"

printLatexTable(
  tmp,
  columns = c("IRATS CAR","Calendar Time AR"),
  title= paste("Buyback IRATS and Calendar Time Abnormals Returns for ",gsub("\\."," ", characteristic_single_analysis),sep=" "),
  caption= "The tables presents the abnormal returns for firms after issue announcements from the announcement date until $t$ months after the announcement. Left table reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench1993} three-factor model and the Fama French (2015) five-factor model for the sample of firms that announced equity issuance plus various subsamples. The following regressions are run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + \\epsilon_{i,t}, \\\\
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Right table reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
",

label = "tbl:indcharacteristic",
titleontop=T,
metric = "CAR",
scale=1,
lastSpecial=T,
dorotate=F
)
@

\begin{figure}[H]
\centering
<< BBISSpnl, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=

plot(cumsum(100*Low_feature_Hedged_react),type="l",ylab="CAR", xlab = "",main = paste("Excess Returns of a Buyback Strategy based on ",gsub("\\."," ", characteristic_single_analysis),sep=" "), axes = FALSE, ylim=c(min(c(100*cumsum(Low_feature_Hedged_react),cumsum(100*High_feature_Hedged_react))), max(c(cumsum(100*Low_feature_Hedged_react),cumsum(100*High_feature_Hedged_react)))), cex.lab=1.1)
axis(1,at=seq(1,length(Low_feature_Hedged_react),length.out=10),labels=str_sub(names(Low_feature_Hedged_react)[seq(1,length(Low_feature_Hedged_react),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
axis(2,cex.axis=1.1)
lines(cumsum(100*High_feature_Hedged_react), lty = 2,lwd=1.4)
for (iter in floor(100*min(c(cumsum(Low_feature_Hedged_react),cumsum(High_feature_Hedged_react)))/100):floor(100*max(c(cumsum(Low_feature_Hedged_react),cumsum(High_feature_Hedged_react)))/100))
  abline(h = 100*iter)
#plot_crisis_dates(Low_feature_Hedged_react) 
legend(x="topleft",
       c("High Quantile","Low Quantile"),
       lty=c("solid","dashed"),
       lwd=c(2,2),
       cex=1,bg="white",inset=0.01)

@
\caption{Buybacks: Returns of five-factor rolling hedged portfolio for only the buyback events for high and low quantile events Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio. 
}
\label{fig:indcharacteristic}
\end{figure}

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
latex_render_data_frame(
  pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)), 
  title = paste("Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in the high quantile buybacks defined using the event characteristic",gsub("\\."," ", characteristic_single_analysis), sep=" "),
  caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of selected buybacks. The holding period for each buyback is 12 months per event.",
  label="tbl:indcharacteristicpnl", 
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F,dorotate=F
)

@

\clearpage

\section{Customized Undervaluation Indicator and Excess Returns}

We define a customized Undervaluation index using the following event characteristics:

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=

thesign = ifelse(input$characteristic_irats1_sign, -1, +1)
thefeature1 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats1)]]  
thefeature1Q = (thesign==-1) + thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_irats1)]]  
High_feature_events1 = (scrub(thefeature1) >= quantile(thefeature1Q[!is.na(thefeature1Q)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
Low_feature_events1 = (scrub(thefeature1) <= quantile(thefeature1Q[!is.na(thefeature1Q)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))

thefeature2 <- thefeature3 <- thefeature4 <- thefeature5 <- thefeature6 <- rep(0,length(High_feature_events1))
High_feature_events2 <- High_feature_events3 <- High_feature_events4 <- High_feature_events5 <- High_feature_events6 <- rep(FALSE,length(High_feature_events1))
Low_feature_events2 <- Low_feature_events3 <- Low_feature_events4 <- Low_feature_events5 <- Low_feature_events6 <- 
  rep(FALSE,length(Low_feature_events1))

if (input$characteristic_irats2 != "None"){
  thesign = ifelse(input$characteristic_irats2_sign, -1, +1)
  thefeature2 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats2)]]  
  thefeature2Q = (thesign==-1) + thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_irats2)]]  
  High_feature_events2 = (scrub(thefeature2) >= quantile(thefeature2Q[!is.na(thefeature2Q)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
  Low_feature_events2 = (scrub(thefeature2) <= quantile(thefeature2Q[!is.na(thefeature2Q)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
}
if (input$characteristic_irats3 != "None"){
  thesign = ifelse(input$characteristic_irats3_sign, -1, +1)
  thefeature3 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats3)]]  
  High_feature_events3 = (scrub(thefeature3) >= quantile(thefeature3[!is.na(thefeature3)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature3))
  Low_feature_events3 = (scrub(thefeature3) <= quantile(thefeature3[!is.na(thefeature3)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature3))
}
if (input$characteristic_irats4 != "None"){
  thesign = ifelse(input$characteristic_irats4_sign, -1, +1)
  thefeature4 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats4)]]  
  High_feature_events4 = (scrub(thefeature4) >= quantile(thefeature4[!is.na(thefeature4)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature4))
  Low_feature_events4 = (scrub(thefeature4) <= quantile(thefeature4[!is.na(thefeature4)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature4))
}
if (input$characteristic_irats5 != "None"){
  thesign = ifelse(input$characteristic_irats5_sign, -1, +1)
  thefeature5 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats5)]]  
  High_feature_events5 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
  Low_feature_events5 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
}
if (input$characteristic_irats6 != "None"){
  thesign = ifelse(input$characteristic_irats6_sign, -1, +1)
  thefeature6 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats6)]]  
  High_feature_events6 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
  Low_feature_events6 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
}

Index_score = 
  2*High_feature_events1 + 1*(!High_feature_events1 & !Low_feature_events1) + 
  (input$characteristic_irats2 != "None")*(2*High_feature_events2 + 1*(!High_feature_events2 & !Low_feature_events2) ) + 
  (input$characteristic_irats3 != "None")*(2*High_feature_events3 + 1*(!High_feature_events3 & !Low_feature_events3) ) + 
  (input$characteristic_irats4 != "None")*(2*High_feature_events4 + 1*(!High_feature_events4 & !Low_feature_events4) ) + 
  (input$characteristic_irats5 != "None")*(2*High_feature_events5 + 1*(!High_feature_events5 & !Low_feature_events5) ) + 
  (input$characteristic_irats6 != "None")*(2*High_feature_events6 + 1*(!High_feature_events6 & !Low_feature_events6) )

Index_Score_rect = Index_score

###
thefeature = Index_Score_rect
High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))

res = round(cbind(
  car_table(DATASET_NEW$returns_by_event_monthly[, Low_feature_events],
            DATASET_NEW$BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
  car_table(DATASET_NEW$returns_by_event_monthly[, High_feature_events],
            DATASET_NEW$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
),2)[reported_times,]
colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
feature_IRATStable_index = res

###
thefeature = Index_Score_rect
High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))

res = round(cbind(
  calendar_table(DATASET_NEW$returns_by_event_monthly[, Low_feature_events],
                 DATASET_NEW$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW$value.weights[Low_feature_events])$results,
  calendar_table(DATASET_NEW$returns_by_event_monthly[,High_feature_events],
                 DATASET_NEW$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW$value.weights[High_feature_events])$results
),2)[reported_times,]

colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
feature_CALtable_index = res

###
thefeature = Index_Score_rect
High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW$DatesMonth, DATASET_NEW$returns_by_event_monthly,event=1),1,non_zero_mean)
High_feature_Hedged_react_index = remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)

###
thefeature = Index_Score_rect
Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW$DatesMonth, DATASET_NEW$returns_by_event_monthly,event=1),1,non_zero_mean)
Low_feature_Hedged_react_index = remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
@

\begin{figure}[H]
\centering
<<  fig.width=10, fig.height=5, out.width='\\textwidth', echo=F >>=
#par(mfrow=c(2,1), mar=c(2.3,4,2.3,4))
#valuation_index_bb[which(valuation_index_bb==2)]<-3 # there is one company here. need to check why
tmp = table(Index_Score_rect)
tmp = structure(as.numeric(tmp), .Names = names(tmp))
barplot(tmp,main = "", ylab = "Number of Events", xlab = "",las=2,space=0.5, cex.names=1)
#tmp = table(valuation_index_iss)
#tmp = structure(as.numeric(tmp), .Names = names(tmp))
#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=1)
rm("tmp")
@
\caption{Distribution of the Customized Undervaluation Index of all buyback events.}
\label{fig:undervaluationindex}
\end{figure}

\end{document}

### 2016-05-16 library_files/lib_helpers.R

@@ -1,1212 +1,0 @@
-#  Copyright 2013, Satrapade
-#  by T. Evgeniou, V. Kapartzianis, N. Nassuphis and D. Spinellis
-#  Dual licensed under the MIT or GPL Version 2 licenses.
-#  11/2015 functions car_table and calendar_table added by T. Evgeniou and E. Junqué de Fortuny
-
-# Required R libraries (need to be installed - it can take a few minutes the first time you run the project)
-
-if (ifelse(!exists("run_shiny_tool"), T, run_shiny_tool == 0)) { # When deploying a shiny app on the shiny server we should not load all R libraries
-  # installs all necessary libraries from CRAN
-  get_libraries <- function(filenames_list) { 
-    lapply(filenames_list,function(thelibrary){    
-      if (do.call(require,list(thelibrary)) == FALSE) 
-        do.call(install.packages,list(thelibrary)) 
-      do.call(library,list(thelibrary))
-    })
-  }
-  libraries_used=c("stringr","gtools","foreign","reshape2","digest","timeDate","devtools","knitr","graphics",
-                   "grDevices","xtable","sqldf","stargazer","data.table","shiny","htmlwidgets",
-                   "Hmisc","vegan","fpc","GPArotation","FactoMineR","cluster",
-                   "psych","stringr","googleVis", "png","ggplot2","googleVis", "gridExtra","RcppArmadillo","xts","DescTools")
-  
-  get_libraries(libraries_used)
-}
-
-Rcpp::sourceCpp('lib_helpers.cpp', embeddedR=FALSE)
-options(stringsAsFactors=FALSE)
-
-
-# Summary table
-my_summary <- function(x){
-  nas = sum(is.na(x))
-  x=x[!is.na(x)]
-  res = c(mean(x), median(x),min(x),quantile(x,0.1), quantile(x,0.25), quantile(x,0,95), quantile(x,0.9), max(x), sd(x), length(x))
-  names(res) <- c("mean", "p50", "min", "p10", "p25", "p75","p90","max","sd", "N")
-  res
-}
-
-non_na_mean <- function(x) { mean(x[!is.na(x) & x != 0]) }
-non_na_sd <- function(x) { sd(x[!is.na(x) & x != 0]) }
-
-remove_initialization_time <- function(x,min_date=NULL) { # Note: Added also min_date as an argument!! THis way we remove data from any given date!
[…]

### 2016-05-16 index.Rmd
tool report

--- 2016-05-15 index.Rmd
@@
 
-run_shiny_tool = 1
+run_shiny_tool = 0
 
@@
   # Why are these not found when deployed?!
-  library("shiny") 
-  library("shinysky") #  devtools::install_github("AnalytixWare/ShinySky")
-
+  suppressWarnings(library("shiny"))
+  suppressWarnings(library("shinyjs"))
+  suppressWarnings(library("shinysky")) #  devtools::install_github("AnalytixWare/ShinySky")
+  suppressWarnings(library("htmlwidgets"))
   library("stringr")
@@
 
-source("library_files/lib_helpers.R", chdir=TRUE)
-source("library_files/ff_industries_sic.R")
+source("lib_helpers.R", local = TRUE)
+source("latex_code.R")
+source("ff_industries_sic.R")
 source("Paper_global_parameters.R")
-source("library_files/heatmapOutput.R") 
-source("library_files/ff_industries_sic.R")
+source("heatmapOutput.R") 
+source("ff_industries_sic.R")
 
@@
   ui = fluidPage(
-    fluidRow(
-      column(2,
-             conditionalPanel(
-               condition = "!$('makeReport').hasClass('shiny-busy')",
-               actionButton("makeReport","Generate Report (Work in Progress)",icon=icon("file"))
-             )
+    useShinyjs(),
+    actionButton("compileReport","Compile Report",icon=icon("spinner")),
+    downloadButton("downloadReport", "Download Report")
   ),
-      column(4,
-             conditionalPanel(
-               condition = "!$('makeReport').hasClass('shiny-busy')",
-               uiOutput("downloadButton")
-               #downloadButton("downloadReport", "Download Report")
-             )
-      )
-    ),
-    busyIndicator("Please wait while we prepare the report ...",wait = 0)
-  ),
-  server = function(input, output) {
-    output$download_button <- renderUI({
-      downloadButton("downloadReport", "Download Results")
+  server = function(input, output, session) {
+    disable("downloadReport")
+    report.data <- paste0("session.", session$token, ".report.data.Rdata")
+    report.script <- paste0("session.", session$token, ".report.script.R")
+    report.source <- paste0("session.", session$token, ".report.Rnw")
+    report.file <- paste0("session.", session$token, ".report.pdf")
+    observeEvent(input$compileReport, {
+      disable("compileReport")
+      report.list <- list("startdate","enddate","market_cap_min","market_cap_max","characteristic", "characteristic_single_analysis", "quantile_used", "characteristic_single_analysis_sign", "high_EU_index_thres", "low_EU_index_thres", "quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
+      save(report.list, file=report.data)
+      file.copy("toolreport.Rnw", report.source)
+      cat(paste0("load ('", report.data, "')\n"), file=report.script)
+      cat(paste0("knitr::knit2pdf('", report.source,"')\n"), file=report.script, append=TRUE)
+      system(paste0("Rscript --vanilla ", report.script), wait=FALSE)
     })
-    makeReportAction <- eventReactive(input$makeReport, {
-      #Create the pdf here
-      #Sys.sleep(1);return()
-      #first check if we didn't already create a paper with these parameters, if so, load from cache
-      #filename <- paste("reports/")
-      #file.exists()
-      #tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
-      #newinput <- list()
-      #for(i in tosave) {
-      #  newinput[[i]] <- input[[i]]
-      #}
-      # Not yet available
-      #knitr::knit2pdf("report.Rnw",envir=globalenv())
-    })
-    output$downloadButton <- renderUI({
-      makeReportAction() #only appear after first click on generate
-      downloadButton("downloadReport", "Download Report")
+    observe({
+      invalidateLater(1000, session)
+      if (file.exists(report.file)) enable("downloadReport")
     })
@@
       content = function(file) {
-        cat(paste("Does the pdf exist?",file.exists("report.pdf")))
-        file.rename(normalizePath('report.pdf'), file)
+        file.copy(report.file, file)
+        file.remove(list.files(pattern=paste0("session.", session$token)))
+        enable("compileReport")
+        disable("downloadReport")
       }
     )
-  },
-  options = list(height = 120,width=800)
+  }
 )
-
 ```

### 2016-05-16 toolreport.Rnw
tool report

@@
 market_cap_max= report.list$market_cap_max
+industry  = report.list$industry
 characteristic= report.list$characteristic
-characteristic_single_analysis= characteristic_single_analysis
+characteristic_single_analysis= report.list$characteristic_single_analysis
 quantile_used = report.list$quantile_used
@@
 
+FirstTrade = startdate
 starting = startdate 
@@
 We only consider firms with a market capitalization the month before the event being between \Sexpr{market_cap_min} and \Sexpr{market_cap_max}.
-In addition to the financial and utilities sectors, we also remove the following sectors: \Sexpr{paste(industry, sep=", ")}.
+In addition to the financial and utilities sectors, we also remove the following sectors: \Sexpr{paste(industry, collapse=", ")}.
+This leaves a total of \Sexpr{length(DATASET_NEW$value.weights)} buyback events.
 
@@
 
-Ww consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the quantiles of events defined using the selected event characteristics, namely \Sexpr{gsub("\\.", " ", characteristic_single_analysis)}.
+Ww consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the quantiles of events defined using the selected event characteristic, namely \Sexpr{gsub("\\.", " ", characteristic_single_analysis)}.
 Table \ref{tbl:indcharacteristic} shows the results.
@@
 
-thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
-thefeature = thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
-thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
-quantile_used_ind = as.numeric(input$quantile_used)
+thesign = ifelse(characteristic_single_analysis_sign, -1, +1)
+thefeature = thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == characteristic_single_analysis)]]
+thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == characteristic_single_analysis)]]  
+quantile_used_ind = as.numeric(quantile_used)
 
@@
 ##
-thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
-thefeature = thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
-thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
-quantile_used_ind = as.numeric(input$quantile_used)
+thesign = ifelse(characteristic_single_analysis_sign, -1, +1)
+thefeature = thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == characteristic_single_analysis)]]
+thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == characteristic_single_analysis)]]  
+quantile_used_ind = as.numeric(quantile_used)
 
@@
 @
-\caption{Buybacks: Returns of five-factor rolling hedged portfolio for only the buyback events for high and low quantile events Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio.
+\caption{Buybacks: Returns of five-factor rolling hedged portfolio for only the buyback events for high and low quantile events.
+Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio.
 }
@@
 latex_render_data_frame(
-  pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)), 
+  pnl_matrix(remove_initialization_time(High_feature_Hedged_react,min_date=FirstTrade)), 
   title = paste("Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in the high quantile buybacks defined using the event characteristic",gsub("\\."," ", characteristic_single_analysis), sep=" "),
@@
 
-We define a customized Undervaluation index using the following event characteristics:
+We define a customized Undervaluation index using the following event characteristics: \Sexpr{gsub("\\.", " ", characteristic_irats1)} (sign is \Sexpr{ifelse(characteristic_irats1_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats2)} (sign is \Sexpr{ifelse(characteristic_irats2_sign, -1, +1)}),\Sexpr{gsub("\\.", " ", characteristic_irats3)} (sign is \Sexpr{ifelse(characteristic_irats3_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats4)} (sign is \Sexpr{ifelse(characteristic_irats4_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats5)} (sign is \Sexpr{ifelse(characteristic_irats5_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats6)} (sign is \Sexpr{ifelse(characteristic_irats6_sign, -1, +1)}).
+For each of these characteristics we define the high and low events as those that are in the top or bottom \Sexpr{100*quantile_used_ind}$\%$ of the events.
+We then assign a score of 2 for the high, 0 for the low, and 1 for the rest of the events for each of these characteristics, and we add up these scores to create the customized undervaluation index.
+Figure \ref{fig:undervaluationindex} shows the number of events for each of the values of this customized index.
+
+We then consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the quantiles of events defined using this customized Undervaluation Index.
+Table \ref{tbl:CUcharacteristic} shows the results.
+Figure \ref{fig:CUcharacteristic} shows the excess returns of a strategy for that trades only the high or low quantile stocks for this customized undervaluation index (the strategy is designed as described in the paper).
+Table \ref{tbl:CUcharacteristicpnl} shows the monthly and yearly returns of the "high" events strategy.
 
@@
 
-thesign = ifelse(input$characteristic_irats1_sign, -1, +1)
-thefeature1 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats1)]]  
-thefeature1Q = (thesign==-1) + thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_irats1)]]  
-High_feature_events1 = (scrub(thefeature1) >= quantile(thefeature1Q[!is.na(thefeature1Q)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
-Low_feature_events1 = (scrub(thefeature1) <= quantile(thefeature1Q[!is.na(thefeature1Q)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
+thesign = ifelse(characteristic_irats1_sign, -1, +1)
+thefeature1 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == characteristic_irats1)]]  
+thefeature1Q = (thesign==-1) + thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == characteristic_irats1)]]  
+High_feature_events1 = (scrub(thefeature1) >= quantile(thefeature1Q[!is.na(thefeature1Q)],1-as.numeric(quantile_used_ind)) & !is.na(thefeature1))
+Low_feature_events1 = (scrub(thefeature1) <= quantile(thefeature1Q[!is.na(thefeature1Q)],as.numeric(quantile_used_ind)) & !is.na(thefeature1))
 
@@
 
-if (input$characteristic_irats2 != "None"){
-  thesign = ifelse(input$characteristic_irats2_sign, -1, +1)
-  thefeature2 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats2)]]  
-  thefeature2Q = (thesign==-1) + thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_irats2)]]  
-  High_feature_events2 = (scrub(thefeature2) >= quantile(thefeature2Q[!is.na(thefeature2Q)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
-  Low_feature_events2 = (scrub(thefeature2) <= quantile(thefeature2Q[!is.na(thefeature2Q)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
+if (characteristic_irats2 != "None"){
+  thesign = ifelse(characteristic_irats2_sign, -1, +1)
+  thefeature2 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == characteristic_irats2)]]  
+  thefeature2Q = (thesign==-1) + thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == characteristic_irats2)]]  
+  High_feature_events2 = (scrub(thefeature2) >= quantile(thefeature2Q[!is.na(thefeature2Q)],1-as.numeric(quantile_used_ind)) & !is.na(thefeature2))
+  Low_feature_events2 = (scrub(thefeature2) <= quantile(thefeature2Q[!is.na(thefeature2Q)],as.numeric(quantile_used_ind)) & !is.na(thefeature2))
 }
-if (input$characteristic_irats3 != "None"){
-  thesign = ifelse(input$characteristic_irats3_sign, -1, +1)
-  thefeature3 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats3)]]  
-  High_feature_events3 = (scrub(thefeature3) >= quantile(thefeature3[!is.na(thefeature3)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature3))
-  Low_feature_events3 = (scrub(thefeature3) <= quantile(thefeature3[!is.na(thefeature3)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature3))
+if (characteristic_irats3 != "None"){
+  thesign = ifelse(characteristic_irats3_sign, -1, +1)
+  thefeature3 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == characteristic_irats3)]]  
+  High_feature_events3 = (scrub(thefeature3) >= quantile(thefeature3[!is.na(thefeature3)],1-as.numeric(quantile_used_ind)) & !is.na(thefeature3))
+  Low_feature_events3 = (scrub(thefeature3) <= quantile(thefeature3[!is.na(thefeature3)],as.numeric(quantile_used_ind)) & !is.na(thefeature3))
 }
-if (input$characteristic_irats4 != "None"){
-  thesign = ifelse(input$characteristic_irats4_sign, -1, +1)
-  thefeature4 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats4)]]  
-  High_feature_events4 = (scrub(thefeature4) >= quantile(thefeature4[!is.na(thefeature4)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature4))
-  Low_feature_events4 = (scrub(thefeature4) <= quantile(thefeature4[!is.na(thefeature4)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature4))
+if (characteristic_irats4 != "None"){
+  thesign = ifelse(characteristic_irats4_sign, -1, +1)
+  thefeature4 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == characteristic_irats4)]]  
+  High_feature_events4 = (scrub(thefeature4) >= quantile(thefeature4[!is.na(thefeature4)],1-as.numeric(quantile_used_ind)) & !is.na(thefeature4))
+  Low_feature_events4 = (scrub(thefeature4) <= quantile(thefeature4[!is.na(thefeature4)],as.numeric(quantile_used_ind)) & !is.na(thefeature4))
 }
-if (input$characteristic_irats5 != "None"){
-  thesign = ifelse(input$characteristic_irats5_sign, -1, +1)
-  thefeature5 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats5)]]  
-  High_feature_events5 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
-  Low_feature_events5 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
+if (characteristic_irats5 != "None"){
+  thesign = ifelse(characteristic_irats5_sign, -1, +1)
+  thefeature5 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == characteristic_irats5)]]  
+  High_feature_events5 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(quantile_used_ind)) & !is.na(thefeature5))
+  Low_feature_events5 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(quantile_used_ind)) & !is.na(thefeature5))
 }
-if (input$characteristic_irats6 != "None"){
-  thesign = ifelse(input$characteristic_irats6_sign, -1, +1)
-  thefeature6 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == input$characteristic_irats6)]]  
-  High_feature_events6 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
-  Low_feature_events6 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
+if (characteristic_irats6 != "None"){
+  thesign = ifelse(characteristic_irats6_sign, -1, +1)
+  thefeature6 = (thesign==-1) + thesign*DATASET_NEW$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW$BUYBACK_DATA_TOOL) == characteristic_irats6)]]  
+  High_feature_events6 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(quantile_used_ind)) & !is.na(thefeature5))
+  Low_feature_events6 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(quantile_used_ind)) & !is.na(thefeature5))
 }
@@
   2*High_feature_events1 + 1*(!High_feature_events1 & !Low_feature_events1) + 
-  (input$characteristic_irats2 != "None")*(2*High_feature_events2 + 1*(!High_feature_events2 & !Low_feature_events2) ) + 
-  (input$characteristic_irats3 != "None")*(2*High_feature_events3 + 1*(!High_feature_events3 & !Low_feature_events3) ) + 
-  (input$characteristic_irats4 != "None")*(2*High_feature_events4 + 1*(!High_feature_events4 & !Low_feature_events4) ) + 
-  (input$characteristic_irats5 != "None")*(2*High_feature_events5 + 1*(!High_feature_events5 & !Low_feature_events5) ) + 
-  (input$characteristic_irats6 != "None")*(2*High_feature_events6 + 1*(!High_feature_events6 & !Low_feature_events6) )
+  (characteristic_irats2 != "None")*(2*High_feature_events2 + 1*(!High_feature_events2 & !Low_feature_events2) ) + 
+  (characteristic_irats3 != "None")*(2*High_feature_events3 + 1*(!High_feature_events3 & !Low_feature_events3) ) + 
+  (characteristic_irats4 != "None")*(2*High_feature_events4 + 1*(!High_feature_events4 & !Low_feature_events4) ) + 
+  (characteristic_irats5 != "None")*(2*High_feature_events5 + 1*(!High_feature_events5 & !Low_feature_events5) ) + 
+  (characteristic_irats6 != "None")*(2*High_feature_events6 + 1*(!High_feature_events6 & !Low_feature_events6) )
 
@@
 thefeature = Index_Score_rect
-High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
-Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
+High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(quantile_used_all)) & !is.na(thefeature))
+Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(quantile_used_all)) & !is.na(thefeature))
 
@@
 thefeature = Index_Score_rect
-High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
+High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(quantile_used_all)) & !is.na(thefeature))
 High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW$DatesMonth, DATASET_NEW$returns_by_event_monthly,event=1),1,non_zero_mean)
@@
 thefeature = Index_Score_rect
-Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
+Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(quantile_used_all)) & !is.na(thefeature))
 Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW$DatesMonth, DATASET_NEW$returns_by_event_monthly,event=1),1,non_zero_mean)
@@
 
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+tmp = cbind(feature_IRATStable_index, feature_CALtable_index)[reported_times,]
+colnames(tmp)[1]<-colnames(tmp)[4] <-  "CAR"
+
+printLatexTable(
+  tmp,
+  columns = c("IRATS CAR","Calendar Time AR"),
+  title= "Buyback IRATS and Calendar Time Abnormals Returns for the Customized Undervaluation Index",
+  caption= "The tables presents the abnormal returns for firms after issue announcements from the announcement date until $t$ months after the announcement.
+Left table reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench1993} three-factor model and the Fama French (2015) five-factor model for the sample of firms that announced equity issuance plus various subsamples.
+The following regressions are run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + \\epsilon_{i,t}, \\\\
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+Right table reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
+",
+
+label = "tbl:CUcharacteristic",
+titleontop=T,
+metric = "CAR",
+scale=1,
+lastSpecial=T,
+dorotate=F
+)
+@
+
+\begin{figure}[H]
+\centering
+<< BBISSpnl, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
+
+plot(cumsum(100*Low_feature_Hedged_react_index),type="l",ylab="CAR", xlab = "",main = "Excess Returns of a Buyback Strategy based on the Customized Undervaluation Index", axes = FALSE, ylim=c(min(c(100*cumsum(Low_feature_Hedged_react_index),cumsum(100*High_feature_Hedged_react_index))), max(c(cumsum(100*Low_feature_Hedged_react_index),cumsum(100*High_feature_Hedged_react_index)))), cex.lab=1.1)
+axis(1,at=seq(1,length(Low_feature_Hedged_react_index),length.out=10),labels=str_sub(names(Low_feature_Hedged_react_index)[seq(1,length(Low_feature_Hedged_react_index),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
+axis(2,cex.axis=1.1)
+lines(cumsum(100*High_feature_Hedged_react_index), lty = 2,lwd=1.4)
+for (iter in floor(100*min(c(cumsum(Low_feature_Hedged_react),cumsum(High_feature_Hedged_react_index)))/100):floor(100*max(c(cumsum(Low_feature_Hedged_react_index),cumsum(High_feature_Hedged_react_index)))/100))
+  abline(h = 100*iter)
+#plot_crisis_dates(Low_feature_Hedged_react) 
+legend(x="topleft",
+       c("High Cusomized U-Index","Low Cusomized U-Index"),
+       lty=c("solid","dashed"),
+       lwd=c(2,2),
+       cex=1,bg="white",inset=0.01)
+
+@
+\caption{Buybacks: Returns of five-factor rolling hedged portfolio for only the buyback events for high and low quantile events defined using the Customized Undervaluation Index.
+Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio.
+}
+\label{fig:CUcharacteristic}
+\end{figure}
+
+<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+latex_render_data_frame(
+  pnl_matrix(remove_initialization_time(High_feature_Hedged_react_index,min_date=FirstTrade)), 
+  title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in the high quantile buybacks defined using the Customized Undervaluation Index",
+  caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of selected buybacks.
+The holding period for each buyback is 12 months per event.",
+  label="tbl:CUcharacteristicpnl", 
+  columns=NULL,
+  bigtitleontop = T,
+  show_rownames=TRUE,
+  scale = 0.9,
+  digits=1,
+  lastSpecial=F,dorotate=F
+)
+
+@
+
+\clearpage
+
 \end{document}

### 2016-05-16 index.Rmd
Fix all compilation and deployment issues

@@
 
-run_shiny_tool = 0
+run_shiny_tool = 1
 
@@
 
-if(!run_shiny_tool) {
-  library(googleVis)
-  library("shiny")
-  library("reshape2")  
-  library("ggplot2")
-  # Why are these not found when deployed?!
-  suppressWarnings(library("shiny"))
-  suppressWarnings(library("shinyjs"))
-  suppressWarnings(library("shinysky")) #  devtools::install_github("AnalytixWare/ShinySky")
-  suppressWarnings(library("htmlwidgets"))
-  library("stringr")
-  library("RcppArmadillo")
-  library("gtools")
-  library("timeDate")
-  library("dygraphs")
-  #library("reshape")
-  library("ggplot2")
-} #else{
-#install.packages("Rcpp")
-#}
+if(run_shiny_tool) suppressPackageStartupMessages({
+  library(htmlwidgets)
+  library(shiny)
+  library(shinyjs)
+  library(shinysky) #  devtools::install_github("AnalytixWare/ShinySky")
+  library(dygraphs)
+  library(Rcpp)
+  library(RcppArmadillo)
+  library(stringr)
+  library(gtools)
+  library(timeDate)
+})
 
@@
 
-**Note that it takes a few minutes (possibly more than five) to create and download the new paper (work in progress).
-Please wait without changing any parameters until you are prompted to download the new paper.**
+**Note that it takes a few minutes (possibly more than five) to compile the new paper. Please wait until the option to download the paper, becomes available.**
 
 ```{r, fig.width=6, fig.height=5,echo=FALSE}
-shinyApp(
-  ui = fluidPage(
-    useShinyjs(),
-    actionButton("compileReport","Compile Report",icon=icon("spinner")),
-    downloadButton("downloadReport", "Download Report")
-  ),
-  server = function(input, output, session) {
-    disable("downloadReport")
+useShinyjs(rmd=TRUE)
+fluidPage(
+  shiny::actionButton("compileReport","Compile Paper",icon=icon("spinner")),
+  shiny::downloadButton("downloadReport", "Download Paper")
+)
 report.data <- paste0("session.", session$token, ".report.data.Rdata")
@@
   disable("compileReport")
-      report.list <- list("startdate","enddate","market_cap_min","market_cap_max","characteristic", "characteristic_single_analysis", "quantile_used", "characteristic_single_analysis_sign", "high_EU_index_thres", "low_EU_index_thres", "quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
+  with(report.list <- new.env(), {
+    startdate <- isolate(input$startdate)
+    enddate <- isolate(input$enddate)
+    market_cap_min <- isolate(input$market_cap_min)
+    market_cap_max <- isolate(input$market_cap_max)
+    characteristic <- isolate(input$characteristic)
+    characteristic_single_analysis <- isolate(input$characteristic_single_analysis)
+    quantile_used <- isolate(input$quantile_used)
+    characteristic_single_analysis_sign <- isolate(input$characteristic_single_analysis_sign)
+    high_EU_index_thres <- isolate(input$high_EU_index_thres)
+    low_EU_index_thres <- isolate(input$low_EU_index_thres)
+    quantile_used_ind <- isolate(input$quantile_used_ind)
+    quantile_used_all <- isolate(input$quantile_used_all)
+    characteristic_irats1 <- isolate(input$characteristic_irats1)
+    characteristic_irats2 <- isolate(input$characteristic_irats2)
+    characteristic_irats3 <- isolate(input$characteristic_irats3)
+    characteristic_irats4 <- isolate(input$characteristic_irats4)
+    characteristic_irats5 <- isolate(input$characteristic_irats5)
+    characteristic_irats6 <- isolate(input$characteristic_irats6)
+    characteristic_irats1_sign <- isolate(input$characteristic_irats1_sign)
+    characteristic_irats2_sign <- isolate(input$characteristic_irats2_sign)
+    characteristic_irats3_sign <- isolate(input$characteristic_irats3_sign)
+    characteristic_irats4_sign <- isolate(input$characteristic_irats4_sign)
+    characteristic_irats5_sign <- isolate(input$characteristic_irats5_sign)
+    characteristic_irats6_sign <- isolate(input$characteristic_irats6_sign)
+    industry <- isolate(input$industry)
+  })
+  for (x in ls(report.list)) if (is.null(get(x, report.list))) warning(paste0("parameter '", x, "' is NULL"), call.=FALSE, immediate.=TRUE)
   save(report.list, file=report.data)
@@
   cat(paste0("load ('", report.data, "')\n"), file=report.script)
-      cat(paste0("knitr::knit2pdf('", report.source,"')\n"), file=report.script, append=TRUE)
+  cat(paste0("knitr::knit2pdf('", report.source,"', quiet=TRUE)\n"), file=report.script, append=TRUE)
   system(paste0("Rscript --vanilla ", report.script), wait=FALSE)
@@
   invalidateLater(1000, session)
-      if (file.exists(report.file)) enable("downloadReport")
+  toggleState("downloadReport", condition=file.exists(report.file))
 })
@@
     disable("downloadReport")
-      }
-    )
   }

### 2016-05-16 toolreport.Rnw
Fix all compilation and deployment issues

@@
 << eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+load("bb_issuersTOOL.Rdata")
+run_shiny_tool = 1
+if(run_shiny_tool) suppressPackageStartupMessages({
+  library(Rcpp)
+  library(RcppArmadillo)
+  library(stringr)
+  library(gtools)
+  library(timeDate)
+  library(Hmisc)
+})
 
+library(knitr)
+opts_chunk$set(cache=FALSE)
 inline_hook <- function (x) {
@@
 
-source("lib_helpers.R", chdir=TRUE)
+suppressPackageStartupMessages(source("lib_helpers.R", chdir=TRUE))
 source("latex_code.R")
@@
 
+value.weights = rep(1, length(BUYBACK_DATA_TOOL$Prior.Returns.Score))
 DATASET_NEW = list(
@@
 
-firstyear = as.character(format(stardate,"%Y"))
+firstyear = as.character(format(startdate,"%Y"))
 lastyear = as.character(format(enddate,"%Y"))
@@
 \documentclass{article}
+\usepackage{setspace}
+\usepackage{hyperref}
+\usepackage{float}
 
@@
 scale=1,
-lastSpecial=T,
-dorotate=F
+lastSpecial=T#,
+#dorotate=F
 )
@@
 \centering
-<< BBISSpnl, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
+<< BBISSpnl1, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
 
@@
   digits=1,
-  lastSpecial=F,dorotate=F
+  lastSpecial=F#,dorotate=F
 )
@@
 \centering
-<< BBISSpnl, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
+<< BBISSpnl2, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
 

### 2016-05-17 index.Rmd
Use a single busy indicator

@@
 })
+
+div(
+  style = "width:32px; height:32px; position:fixed; top:0; bottom:0; left:0; right:0; margin: auto; z-index:9999",
+  busyIndicator("", wait=111)
+)
 
@@
       tabPanel("Histogram",
-               busyIndicator("Please wait while we load the data for you... This shouldn't take more than a few seconds...",wait = 0),
                renderPlot({
@@
       tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
-               busyIndicator("Calculating results ...",wait = 0),
                renderTable({
@@
       tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
-               busyIndicator("Calculating results ...",wait = 0),
                renderTable({
@@
       tabPanel("Cumulative Abnormal Returns,High, 12m hold",
-               busyIndicator("Calculating results ...",wait = 0),
                renderDygraph({
@@
       tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
-               busyIndicator("Calculating results ...",wait = 0),
                renderDygraph({
@@
       tabPanel("Monthly and Yearly Returns, High, 12m hold",
-               busyIndicator("Calculating results ...",wait = 0),
                renderUI(
@@
       tabPanel("Monthly and Yearly Returns, Low, 12m hold",
-               busyIndicator("Calculating results ...",wait = 0),
                renderUI(
@@
       tabPanel("Number of Firms per EU Index Value",
-               busyIndicator("Calculating results ...",wait = 0),
                renderTable({
@@
       tabPanel("Histogram of the New Index",
-               busyIndicator("Calculating results ...",wait = 0),
                renderPlot({

### 2016-05-17 index.Rmd
update button

@@
 load("bb_issuersTOOL.Rdata")
+BUYBACK_DATA_TOOL$Industry_name <- as.character(BUYBACK_DATA_TOOL$Industry_name)
 
@@
   library(shiny)
-  library(shinyjs)
+  suppressWarnings(library(shinyjs))
   library(shinysky) #  devtools::install_github("AnalytixWare/ShinySky")
@@
 source("ff_industries_sic.R")
+useShinyjs(rmd=TRUE)
 
@@
 
-**NOTE:** Please always wait until all tables load (and "fade in")...
-
-<hr>
-
 This is an interactive tool for the article [Volatility and the Buyback Anomaly](http://tevgeniou.github.io/BuybacksIssuers/).
 Users can explore the effects of various parameters as well as data filtering choices.
-For any given choices, users can generate and download a new **customized pdf version of the paper** (work in progress) by clicking the button below at any time.
+Every time you change the parameters below, you can click on the **"Update Results"** button to see the new results.
+You may **need to wait a few seconds** until all results of this tool are updated (all tables/figures "fade in").
 
-**Note that it takes a few minutes (possibly more than five) to compile the new paper. Please wait until the option to download the paper, becomes available.**
+```{r, fig.width=6, fig.height=5,echo=FALSE}
+fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
+```
+<br>
+
+For any given choices of parameters, you can also download a pdf version of the results for the data sample you selected by clicking on the **Compile Report** button.
+**Note that it takes a few minutes (possibly more than five) to compile the new paper.
+Please wait until the option to download the paper, becomes available.**
 
@@
 fluidPage(
-  shiny::actionButton("compileReport","Compile Paper",icon=icon("spinner")),
-  shiny::downloadButton("downloadReport", "Download Paper")
+  shiny::actionButton("compileReport","Compile Report",icon=icon("spinner")),
+  shiny::downloadButton("downloadReport", "Download Report")
 )
+```
+
+<hr>
+
+### Dataset Filtering
+
+You can select some filters for the dataset. All analyses below will be done only for the events that are selected. 
+<br>
+Select the time period, the minimum and maximum market capitalization of the firms (in $millions - the maximum selected should be larger than the minimum, else the maximum is automatically set to infinity) for which you would like to do the analyses below.
+You can also see the effects of removing some industries by selecting also any industries to remove (make sure there are enough data left for the analysis)
+
+```{r, fig.width=6, fig.height=5,echo=FALSE}
+
 report.data <- paste0("session.", session$token, ".report.data.Rdata")
@@
 })
+
+dateInput("startdate", "Starting Date:", 
+          value = min(BUYBACK_DATA_TOOL$Event.Date) - 10, min = min(BUYBACK_DATA_TOOL$Event.Date), max = max(BUYBACK_DATA_TOOL$Event.Date)-3*370,
+          startview = "year",
+          width='100%')
+dateInput("enddate", "End Date (allow at least 3 years from the starting day you selected - else it will automatically use data up to 3 years after your start date):", 
+          value = max(BUYBACK_DATA_TOOL$Event.Date) + 10, 
+          min = min(BUYBACK_DATA_TOOL$Event.Date)+3*370, 
+          max = max(BUYBACK_DATA_TOOL$Event.Date)+10,startview = "year",
+          width='100%')
+
+selectInput("market_cap_min","Enter the Minimum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20))), selected = "0", width = "1000px")
+
+selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), 10e10)), selected = as.character(10e10), width = "1000px")
+
+selectInput("industry", "Select Industries to remove:", choices = unique(BUYBACK_DATA_TOOL$Industry_name),selected = NULL,multiple=TRUE,width="100%")
+
 output$downloadReport <- downloadHandler(
@@
 
-<hr>
-
-### Dataset Filtering
-
-You can select some filters for the dataset. All analyses below will be done only for the events that are selected.
-
-Every time you change these filters you may **need to wait a few seconds** until all results of this tool are updated (all tables/figures "fade in").
-
-<br>
-
-Select the time period for which you would like to do the analyses below:
-
-<br>
-
-```{r, eval=TRUE, echo = FALSE}
-dateInput("startdate", "Starting Date:", 
-          value = min(BUYBACK_DATA_TOOL$Event.Date) - 10, min = min(BUYBACK_DATA_TOOL$Event.Date), max = max(BUYBACK_DATA_TOOL$Event.Date)-3*370,
-          startview = "year",
-          width='100%')
-```
-<br>
-```{r, eval=TRUE, echo = FALSE}
-dateInput("enddate", "End Date (allow at least 3 years from the starting day you selected - else it will automatically use data up to 3 years after your start date):", 
-          value = max(BUYBACK_DATA_TOOL$Event.Date) + 10, 
-          min = min(BUYBACK_DATA_TOOL$Event.Date)+3*370, 
-          max = max(BUYBACK_DATA_TOOL$Event.Date)+10,startview = "year",
-          width='100%')
-```
-
-<br>
-
-Selet the minimum size of the firms (in $millions) for which you would like to do the analyses below.
-The maximum selected should be larger than the minimum, else the maximum is automatically set to infinity:
-
-```{r, eval=TRUE, echo = FALSE}
-selectInput("market_cap_min","Enter the Minimum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20))), selected = "0", width = "1000px")
-```
-<br>
-```{r, eval=TRUE, echo = FALSE}
-selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), 10e10)), selected = as.character(10e10), width = "1000px")
-```
-
-We can also see the effects of removing some industries: we can select industries to remove here (make sure there are enough data left for the analysis):
-
-<br>
-
-```{r, eval=TRUE, echo = FALSE}
-selectInput("industry", "Select Industries to remove:", choices = unique(BUYBACK_DATA_TOOL$Industry_name),selected = NULL,multiple=TRUE,width="100%") 
-```
-<br>
-
 ```{r, eval=TRUE, echo = FALSE}
 DATASET_NEW <- reactive({
+  input$computeButton
+  isolate({
+
     starting = input$startdate 
@@
   })
+})
 
+```
+
+```{r, fig.width=6, fig.height=5,echo=FALSE}
+fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
 ```
@@
 feature_IRATStable <- reactive({
+  input$computeButton
+  isolate({
+
     thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
@@
 
+})
+
 feature_CALtable <- reactive({
+  input$computeButton
+  isolate({
+
     thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
@@
   })
+})
 
 High_feature_Hedged_react <- reactive({
+  input$computeButton
+  isolate({
+
     thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
@@
   })
+})
 
 Low_feature_Hedged_react <- reactive({
+  input$computeButton
+  isolate({
+
     thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
@@
   })
+})
 
@@
 
+<br> 
+```{r, fig.width=6, fig.height=5,echo=FALSE}
+fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
+```
 <br>
@@
 <br>
+```{r, fig.width=6, fig.height=5,echo=FALSE}
+fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
+```
+<br>
 
@@
 EU_index_table <- reactive({
+  input$computeButton
+  isolate({
+
     thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]
@@
   })
+})
 
 feature_IRATStable_industry <- reactive({
+  input$computeButton
+  isolate({
+
     thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]
@@
   })
+})
 
 feature_CALtable_industry <- reactive({
+  input$computeButton
+  isolate({
+
     thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]
@@
     as.data.frame(res)
+  })
 })
@@
 
+<br>
+```{r, fig.width=6, fig.height=5,echo=FALSE}
+fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
+```
+<br>
+
 ```{r, eval=TRUE, echo = FALSE}
 selected_features = reactive({
+  input$computeButton
+  isolate({
+
     paste(setdiff(unique(c(input$characteristic_irats1,input$characteristic_irats2,input$characteristic_irats3,input$characteristic_irats4,input$characteristic_irats5,input$characteristic_irats6)), "None"), sep=",")
   })
-
+})
 ```
@@
 Index_Score_rect <- reactive({
+  input$computeButton
+  isolate({
 
@@
   })
+})
 
 feature_IRATStable_index <- reactive({
+  input$computeButton
+  isolate({
+
     thefeature = Index_Score_rect()
@@
   })
+})
 
 feature_CALtable_index <- reactive({
+  input$computeButton
+  isolate({
+
     thefeature = Index_Score_rect()
@@
   })
+})
 
 High_feature_Hedged_react_index <- reactive({
+  input$computeButton
+  isolate({
+
     thefeature = Index_Score_rect()
@@
   })
+})
+Low_feature_Hedged_react_index <- reactive({
+  input$computeButton
+  isolate({
 
-Low_feature_Hedged_react_index <- reactive({
     thefeature = Index_Score_rect()
@@
     remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
+  })
 })

### 2016-05-17 create_tool_data.R

@@ -30,7 +30,7 @@ BUYBACK_DATA_TOOL = data.frame(
   leverage.ratio = BUYBACK_DATA$DATASET$CRSP$leverage_lt_over_lt_plus_e,
   Event.Date = BUYBACK_DATA$DATASET$SDC$Event.Date,
   Event.Size = BUYBACK_DATA$DATASET$SDC$Event.Size,
-  Industry_name = BUYBACK_DATA$DATASET$SDC$Industry_name
+  Industry_name = as.character(BUYBACK_DATA$DATASET$SDC$Industry_name)
   
 )
 Risk_Factors_Monthly <- BUYBACK_DATA$Risk_Factors_Monthly

### 2016-05-17 index.Rmd
update buttons

@@
 load("bb_issuersTOOL.Rdata")
-BUYBACK_DATA_TOOL$Industry_name <- as.character(BUYBACK_DATA_TOOL$Industry_name)
 
@@
 ```{r, fig.width=6, fig.height=5,echo=FALSE}
-fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
+fluidPage(shiny::actionButton("computeButtonALL","Update Results",icon=icon("spinner")) )
 ```
@@
 DATASET_NEW <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
   isolate({
@@
 ```{r, fig.width=6, fig.height=5,echo=FALSE}
-fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
+fluidPage(shiny::actionButton("computeButtonALL2","Update Results",icon=icon("spinner")) )
 ```
@@
 feature_IRATStable <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonindi
+
   isolate({
@@
 feature_CALtable <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonindi
+
   isolate({
@@
 High_feature_Hedged_react <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonindi
+
   isolate({
@@
 Low_feature_Hedged_react <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonindi
+
   isolate({
@@
 ```{r, fig.width=6, fig.height=5,echo=FALSE}
-fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
+fluidPage(shiny::actionButton("computeButtonindi","Update Results",icon=icon("spinner")) )
 ```
@@
 ```{r, fig.width=6, fig.height=5,echo=FALSE}
-fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
+fluidPage(shiny::actionButton("computeButtonEU","Update Results",icon=icon("spinner")) )
 ```
@@
 EU_index_table <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonEU
   isolate({
@@
 feature_IRATStable_industry <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonEU
   isolate({
@@
 feature_CALtable_industry <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonEU
   isolate({
@@
 ```{r, fig.width=6, fig.height=5,echo=FALSE}
-fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
+fluidPage(shiny::actionButton("computeButtonCU","Update Results",icon=icon("spinner")) )
 ```
@@
 selected_features = reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonCU
   isolate({
@@
 Index_Score_rect <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonCU
   isolate({
@@
 feature_IRATStable_index <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonCU
   isolate({
@@
 feature_CALtable_index <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonCU
   isolate({
@@
 High_feature_Hedged_react_index <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonCU
   isolate({
@@
 Low_feature_Hedged_react_index <- reactive({
-  input$computeButton
+  input$computeButtonALL
+  input$computeButtonALL2
+  input$computeButtonCU
   isolate({

### 2016-05-17 create_tool_data.R

@@ -30,7 +30,9 @@ BUYBACK_DATA_TOOL = data.frame(
   leverage.ratio = BUYBACK_DATA$DATASET$CRSP$leverage_lt_over_lt_plus_e,
   Event.Date = BUYBACK_DATA$DATASET$SDC$Event.Date,
   Event.Size = BUYBACK_DATA$DATASET$SDC$Event.Size,
-  Industry_name = as.character(BUYBACK_DATA$DATASET$SDC$Industry_name)
+  Industry_name = as.character(BUYBACK_DATA$DATASET$SDC$Industry_name), 
+  
+  stringsAsFactors = F
   
 )
 Risk_Factors_Monthly <- BUYBACK_DATA$Risk_Factors_Monthly

### 2016-05-17 datasetcode/buybacks_rawdata_combine.R
some data code

@@ -1,0 +1,359 @@
+
+################################################################
+# INPUT FILES
+################################################################
+
+# Needs these 2 csv files (from SDC - see README)
+file_in_repurchases_dataset  = "rawdata_events_buybacks/sdc2016/sdc_output_buybacks_repurchases.csv"
+file_in_MnA_dataset  = "rawdata_events_buybacks/sdc2016/sdc_output_buybacks_ma.csv"
+
+################################################################
+# OUTPUT FILE
+################################################################
+
+# Passes this file to dataset/buybacks/standardise_data.R
+file_out_for_standardize_data  = "rawdata_events_buybacks/sdc2016/sdc_output_buybacks.csv"
+#all_buybacks_orig <- read.csv(file_out_for_standardize_data,header=T,stringsAsFactors = F,sep=",")
+
+
+################################################################
+
+buybacks_repurchases <- read.csv(file_in_repurchases_dataset,header=T,stringsAsFactors = F,sep=";", dec=",")
+buybacks_ma <- read.csv(file_in_MnA_dataset,header=T,stringsAsFactors = F,sep=";", dec=",")
+
+# just in case there is an empty column
+buybacks_repurchases$X <- NULL
+buybacks_ma$X <- NULL
+
+cleanup = list()
+cleanup$Standardise = list()
+
+cleanup$Standardise$initial_MA = length(buybacks_ma$Acquiror..CUSIP)
+cleanup$Standardise$initial_repurchase = length(buybacks_repurchases$Initial.Auth..Date)
+
+####################################################################################
+# First clean up the M&A data.  ALWAYS CHECK HOW MANY EVENTS ARE DROPPED. IF TOO MANY, INVESTIGATE...
+####################################################################################
+
+# Remove duplicate events
+buybacks_ma$tmp1 <- sapply(1:length(buybacks_ma$X.Deal.Number), function(i) 
+  paste(tolower(buybacks_ma$Acquiror..CUSIP[i]),
+        buybacks_ma$X..Date.Announced[i],
[…]

### 2016-05-17 datasetcode/standardise_data_buybacks.R

@@ -1,0 +1,120 @@
+#standardizes the SDC buyback data
+
+rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
+source("lib_helpers.R", chdir=TRUE)
+
+# In case we need to change these...
+FirstTrade = "1900-01-01"
+AbsoluteMinimumDate =  "1900-01-01"
+Last = Today()
+
+BUYBACK_DATA = list()
+
+################################################################
+
+# For  buybacks we do all the standarization when we merge the M&A and repurchases data!
+source('rawdata_events_buybacks/sdc2016/buybacks_rawdata_combine.R')
+#all_buybacks, cleanup
+SDC <- all_buybacks
+rm("all_buybacks")
+
+
+################################################################
+### SOME DATA CLEAN
+################################################################
+
+the_dates = SDC$Event.Date
+inside_range = ifelse(!is.na(the_dates), the_dates >= FirstTrade & the_dates <= Last, T)
+SDC = SDC[inside_range,]
+
+the_dates = SDC$Event.Date
+SDC_NODATE = (is.na(the_dates))  
+SDC_tooearly <- rep(F,length(SDC_NODATE))
+SDC_tooearly[!(is.na(the_dates))] <- the_dates[!(is.na(the_dates))] < AbsoluteMinimumDate
+SDC_NOCUSIP = (SDC$X6.CUSIP == "")  # Note that we check only the 6 digit CUSIP here, as the buybacks M&A have only that
+
+to_keep = !SDC_NODATE & !SDC_tooearly & !SDC_NOCUSIP
+total_orig = nrow(SDC)
+SDC = SDC[to_keep,]
+total_sdc_clean = nrow(SDC)
+
+SDC$X <- NULL # just in case there was any empty columns left (should not be as they are removed in buybacks_rawdata_combine.R)
+
+# We do no more filtering at this stage. All filtering will be done at the business decision level. For now we get all the data. 
+#useonly = (SDC$Tech..nique.Code %in% c("OP") & SDC$Trans..Type.Code %in% c("AU") 
+           #& as.Date(SDC$Initial.Auth..Date,format="%d/%m/%Y") >= First
+#           )
+#SDC = SDC[useonly,]
+
[…]

### 2016-05-17 datasetcode/standardise_data_issuers.R

@@ -1,0 +1,154 @@
+#standardizes the SDC issuers data
+
+rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
+source("lib_helpers.R", chdir=TRUE)
+
+# In case we need to change these...
+FirstTrade = "1900-01-01"
+AbsoluteMinimumDate =  "1900-01-01"
+Last = Today()
+
+ISSUERS_DATA = list()
+
+################################################################
+
+SDC <- read.csv("rawdata_events_issuers/sdc_output_issuers.csv",header=T,stringsAsFactors = F,sep=";")
+#Make sure we have: Event.Date, CUSIP, and all other standardised data characteristics as described in README in the datasets directory
+the_dates = as.Date(SDC$X.Filing...Date,format="%d/%m/%y",origin="19700101")
+inside_range = ifelse(!is.na(the_dates), the_dates >= FirstTrade & the_dates <= Last, T)
+SDC = SDC[inside_range,]
+
+the_dates = as.Date(SDC$X.Filing...Date,format="%d/%m/%y",origin="19700101")
+SDC_NODATE = (is.na(the_dates))  
+SDC_NOCUSIP = (SDC$X9.Digit.CUSIP == "")  
+
+to_keep = !SDC_NODATE & !SDC_NOCUSIP
+total_orig = nrow(SDC)
+SDC = SDC[to_keep,]
+total_sdc_clean = nrow(SDC)
+
+SDC$X <- NULL # just in case there was any empty column in the .csv from SDC
+
+# We do no more filtering at this stage. All filtering will be done at the business decision level. For now we get all the data. 
+#useonly = (SDC$IPO.Flag..Y.N. %in% c("No") & SDC$Issue.Type %in% c("FO")
+#           #& as.Date(SDC$X.Filing...Date,format="%d/%m/%y",origin="19700101") >= First
+#           )
+#SDC = SDC[useonly,]
+
+################################################################
+# THE REQUIRED FIELDS FIRST
+################################################################
+
+# THE REQUIRED FIELDS FIRST
+SDCstandardised <- data.frame(Event.Date = as.Date(SDC$X.Filing...Date,format="%d/%m/%y",origin="19700101"))
[…]

### 2016-05-17 toolreport.Rnw
errors
some data code
typos

@@
 \begin{abstract}
-\noindent This is a customized report of the online interactive tool for the paper "{\it Volatility and the Buyback Anomaly}" by T.
+\noindent This is a customized report of the online interactive tool for the paper {\it ``Volatility and the Buyback Anomaly''} by T.
 Evgeniou, Enric Junqu\'e de Fortuny, Nick Nassuphis, and Theo Vermaelen.
 
+There is no guarantee that there is no error in all possible customized reports.
+
 \end{abstract}
-\vspace{2cm}
+%\vspace{2cm}
 
@@
 We only consider firms with a market capitalization the month before the event being between \Sexpr{market_cap_min} and \Sexpr{market_cap_max}.
-In addition to the financial and utilities sectors, we also remove the following sectors: \Sexpr{paste(industry, collapse=", ")}.
+In addition to the financial and utilities sectors, we also remove the following sectors: \Sexpr{ifelse(length(industry) == 0, "None", paste(industry, collapse=", "))}.
 This leaves a total of \Sexpr{length(DATASET_NEW$value.weights)} buyback events.
@@
 
-Ww consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the quantiles of events defined using the selected event characteristic, namely \Sexpr{gsub("\\.", " ", characteristic_single_analysis)}.
+We consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the high and low quantiles of events defined using the selected event characteristic, namely \Sexpr{gsub("\\.", " ", characteristic_single_analysis)}.
 Table \ref{tbl:indcharacteristic} shows the results.
-Figure \ref{fig:indcharacteristic} shows the excess returns of a strategy for that trades only the high or low quantile stocks for this event characteristics (the strategy is designed as described in the paper).
-Table \ref{tbl:indcharacteristicpnl} shows the monthly and yearly returns of the "high" events strategy.
+Figure \ref{fig:indcharacteristic} shows the excess returns of a strategy  that trades only the high or low quantile stocks for this event characteristic (the strategy is designed as described in the paper).
+Table \ref{tbl:indcharacteristicpnl} shows the monthly and yearly returns of the high quantile events strategy.
 
@@
 
+\clearpage
+
 <<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
@@
 
+\clearpage
+
 \begin{figure}[H]
@@
 
+\clearpage
+
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
@@
 
-We define a customized Undervaluation index using the following event characteristics: \Sexpr{gsub("\\.", " ", characteristic_irats1)} (sign is \Sexpr{ifelse(characteristic_irats1_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats2)} (sign is \Sexpr{ifelse(characteristic_irats2_sign, -1, +1)}),\Sexpr{gsub("\\.", " ", characteristic_irats3)} (sign is \Sexpr{ifelse(characteristic_irats3_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats4)} (sign is \Sexpr{ifelse(characteristic_irats4_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats5)} (sign is \Sexpr{ifelse(characteristic_irats5_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats6)} (sign is \Sexpr{ifelse(characteristic_irats6_sign, -1, +1)}).
+We define a customized Undervaluation index using the following event characteristics: \Sexpr{ifelse(characteristic_irats1 != "None",  paste(gsub("\\.", " ", characteristic_irats1), " (sign is ", ifelse(characteristic_irats1_sign, "-1","+1"),")",sep = ""), " ") } \Sexpr{ifelse(characteristic_irats2 != "None",  paste(",", gsub("\\.", " ", characteristic_irats2), " (sign is ", ifelse(characteristic_irats2_sign, "-1","+1"),")",collapse = ""), " ") }  \Sexpr{ifelse(characteristic_irats3 != "None",  paste(",", gsub("\\.", " ", characteristic_irats3), " (sign is ", ifelse(characteristic_irats3_sign, "-1","+1"),")",collapse = ""), " ") } \Sexpr{ifelse(characteristic_irats4 != "None",  paste(",", gsub("\\.", " ", characteristic_irats4), " (sign is ", ifelse(characteristic_irats4_sign, "-1","+1"),")",collapse = ""), " ") } \Sexpr{ifelse(characteristic_irats5 != "None",  paste(",", gsub("\\.", " ", characteristic_irats5), " (sign is ", ifelse(characteristic_irats5_sign, "-1","+1"),")",collapse = ""), " ") } \Sexpr{ifelse(characteristic_irats6 != "None",  paste(",", gsub("\\.", " ", characteristic_irats6), " (sign is ", ifelse(characteristic_irats6_sign, "-1","+1"),")",collapse = ""), " ") }.
 For each of these characteristics we define the high and low events as those that are in the top or bottom \Sexpr{100*quantile_used_ind}$\%$ of the events.
@@
 
-We then consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the quantiles of events defined using this customized Undervaluation Index.
+We then consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the high/low quantiles of events defined using this customized Undervaluation Index.
 Table \ref{tbl:CUcharacteristic} shows the results.
-Figure \ref{fig:CUcharacteristic} shows the excess returns of a strategy for that trades only the high or low quantile stocks for this customized undervaluation index (the strategy is designed as described in the paper).
-Table \ref{tbl:CUcharacteristicpnl} shows the monthly and yearly returns of the "high" events strategy.
+Figure \ref{fig:CUcharacteristic} shows the excess returns of a strategy that trades only the high or low quantile stocks for this customized undervaluation index (the strategy is designed as described in the paper).
+Table \ref{tbl:CUcharacteristicpnl} shows the monthly and yearly returns of the high quantile events strategy.
 
@@
 \end{figure}
+
+\clearpage
 

### 2016-05-18 index.Rmd
fixes

@@
                              useonly_industry) 
-
+    # shiny seems to change the class of this matrix. needs investigation. 
+    tmp = apply(returns_by_event_monthly[,useonly_report,drop=F], 2, function(r) as.numeric(r))
+    colnames(tmp) <- colnames(returns_by_event_monthly[,useonly_report,drop=F])
+    rownames(tmp) <- rownames(returns_by_event_monthly[,useonly_report,drop=F])
     list(
       BUYBACK_DATA_TOOL=BUYBACK_DATA_TOOL[useonly_report,],
-      returns_by_event_monthly = returns_by_event_monthly[,useonly_report],
+      returns_by_event_monthly = tmp,
       DatesMonth  = DatesMonth[,useonly_report],

### 2016-05-18 toolreport.Rnw
fixes

@@
 Table \ref{tbl:indcharacteristic} shows the results.
-Figure \ref{fig:indcharacteristic} shows the excess returns of a strategy  that trades only the high or low quantile stocks for this event characteristic (the strategy is designed as described in the paper).
-Table \ref{tbl:indcharacteristicpnl} shows the monthly and yearly returns of the high quantile events strategy.
+Figure \ref{fig:indcharacteristic} shows the excess returns of a strategy  that trades only the high or low percentile stocks for this event characteristic (the strategy is designed as described in the paper).
+Table \ref{tbl:indcharacteristicpnl} shows the monthly and yearly returns of the high percentile events strategy.
 
@@
   tmp,
-  columns = c("IRATS CAR","Calendar Time AR"),
+  columns = c("IRATS CAR: LOW","HIGH","Calendar Time AR: LOW","HIGH"),
   title= paste("Buyback IRATS and Calendar Time Abnormals Returns for ",gsub("\\."," ", characteristic_single_analysis),sep=" "),
-  caption= "The tables presents the abnormal returns for firms after issue announcements from the announcement date until $t$ months after the announcement.
-Left table reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench1993} three-factor model and the Fama French (2015) five-factor model for the sample of firms that announced equity issuance plus various subsamples.
+  caption= "The tables presents the abnormal returns for firms after repurchase announcements from the announcement date until $t$ months after the announcement.
+Left tables report monthly cumulative average abnormal returns (CAR) in percent using Ibbotson (1975) returns across time and security (IRATS) method combined with the Fama French (2015) five-factor model for the low and high prcentile sample of firms using the selected ctiretion that announced an open market share repurchase.
 The following regressions are run each event month~$j$:
@@
 The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Right table reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+Right tables report monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the Fama and French (2015a) five-factor model.
 In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
@@
 titleontop=T,
-metric = "CAR",
+metric = "Ret.",
 scale=1,
@@
 @
-\caption{Buybacks: Returns of five-factor rolling hedged portfolio for only the buyback events for high and low quantile events.
+\caption{Buybacks: Returns of five-factor rolling hedged portfolio for only the buyback events for high and low percentile events.
 Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio.
@@
   pnl_matrix(remove_initialization_time(High_feature_Hedged_react,min_date=FirstTrade)), 
-  title = paste("Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in the high quantile buybacks defined using the event characteristic",gsub("\\."," ", characteristic_single_analysis), sep=" "),
+  title = paste("Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in the high percentile buybacks defined using the event characteristic",gsub("\\."," ", characteristic_single_analysis), sep=" "),
   caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of selected buybacks.
@@
 
-We define a customized Undervaluation index using the following event characteristics: \Sexpr{ifelse(characteristic_irats1 != "None",  paste(gsub("\\.", " ", characteristic_irats1), " (sign is ", ifelse(characteristic_irats1_sign, "-1","+1"),")",sep = ""), " ") } \Sexpr{ifelse(characteristic_irats2 != "None",  paste(",", gsub("\\.", " ", characteristic_irats2), " (sign is ", ifelse(characteristic_irats2_sign, "-1","+1"),")",collapse = ""), " ") }  \Sexpr{ifelse(characteristic_irats3 != "None",  paste(",", gsub("\\.", " ", characteristic_irats3), " (sign is ", ifelse(characteristic_irats3_sign, "-1","+1"),")",collapse = ""), " ") } \Sexpr{ifelse(characteristic_irats4 != "None",  paste(",", gsub("\\.", " ", characteristic_irats4), " (sign is ", ifelse(characteristic_irats4_sign, "-1","+1"),")",collapse = ""), " ") } \Sexpr{ifelse(characteristic_irats5 != "None",  paste(",", gsub("\\.", " ", characteristic_irats5), " (sign is ", ifelse(characteristic_irats5_sign, "-1","+1"),")",collapse = ""), " ") } \Sexpr{ifelse(characteristic_irats6 != "None",  paste(",", gsub("\\.", " ", characteristic_irats6), " (sign is ", ifelse(characteristic_irats6_sign, "-1","+1"),")",collapse = ""), " ") }.
+We define a customized Undervaluation index using the following event characteristics: \Sexpr{ifelse(characteristic_irats1 != "None",  paste(gsub("\\.", " ", characteristic_irats1), " (sign is ", ifelse(characteristic_irats1_sign, "-1","+1"),")",collapse = ""), "") } \Sexpr{ifelse(characteristic_irats2 != "None",  paste(",", gsub("\\.", " ", characteristic_irats2), " (sign is ", ifelse(characteristic_irats2_sign, "-1","+1"),")",collapse = ""), "") }  \Sexpr{ifelse(characteristic_irats3 != "None",  paste(",", gsub("\\.", " ", characteristic_irats3), " (sign is ", ifelse(characteristic_irats3_sign, "-1","+1"),")",collapse = ""), "") } \Sexpr{ifelse(characteristic_irats4 != "None",  paste(",", gsub("\\.", " ", characteristic_irats4), " (sign is ", ifelse(characteristic_irats4_sign, "-1","+1"),")",collapse = ""), "") } \Sexpr{ifelse(characteristic_irats5 != "None",  paste(",", gsub("\\.", " ", characteristic_irats5), " (sign is ", ifelse(characteristic_irats5_sign, "-1","+1"),")",collapse = ""), "") } \Sexpr{ifelse(characteristic_irats6 != "None",  paste(",", gsub("\\.", " ", characteristic_irats6), " (sign is ", ifelse(characteristic_irats6_sign, "-1","+1"),")",collapse = ""), "") }.
 For each of these characteristics we define the high and low events as those that are in the top or bottom \Sexpr{100*quantile_used_ind}$\%$ of the events.
@@
 Table \ref{tbl:CUcharacteristic} shows the results.
-Figure \ref{fig:CUcharacteristic} shows the excess returns of a strategy that trades only the high or low quantile stocks for this customized undervaluation index (the strategy is designed as described in the paper).
-Table \ref{tbl:CUcharacteristicpnl} shows the monthly and yearly returns of the high quantile events strategy.
+Figure \ref{fig:CUcharacteristic} shows the excess returns of a strategy that trades only the high or low percentile stocks for this customized undervaluation index (the strategy is designed as described in the paper).
+Table \ref{tbl:CUcharacteristicpnl} shows the monthly and yearly returns of the high percentile events strategy.
 
@@
   tmp,
-  columns = c("IRATS CAR","Calendar Time AR"),
+  columns = c("IRATS CAR: LOW","HIGH","Calendar Time AR: LOW","HIGH"),
   title= "Buyback IRATS and Calendar Time Abnormals Returns for the Customized Undervaluation Index",
-  caption= "The tables presents the abnormal returns for firms after issue announcements from the announcement date until $t$ months after the announcement.
-Left table reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench1993} three-factor model and the Fama French (2015) five-factor model for the sample of firms that announced equity issuance plus various subsamples.
+  caption= "The tables presents the abnormal returns for firms after repurchase announcements from the announcement date until $t$ months after the announcement.
+Left tables report monthly cumulative average abnormal returns (CAR) in percent using Ibbotson (1975) returns across time and security (IRATS) method combined with the Fama French (2015) five-factor model for the low and high prcentile sample of firms using the customized undervaluation index that announced an open market share repurchase.
 The following regressions are run each event month~$j$:
@@
 @
-\caption{Buybacks: Returns of five-factor rolling hedged portfolio for only the buyback events for high and low quantile events defined using the Customized Undervaluation Index.
+\caption{Buybacks: Returns of five-factor rolling hedged portfolio for only the buyback events for high and low percentile events defined using the Customized Undervaluation Index.
 Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio.
@@
   pnl_matrix(remove_initialization_time(High_feature_Hedged_react_index,min_date=FirstTrade)), 
-  title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in the high quantile buybacks defined using the Customized Undervaluation Index",
+  title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in the high percentile buybacks defined using the Customized Undervaluation Index",
   caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of selected buybacks.

### 2016-05-19 index.Rmd
plots

@@
       tabPanel("Cumulative Abnormal Returns,High, 12m hold",
-               renderDygraph({
-                 pnl_plot_interactive(High_feature_Hedged_react())
+               renderPlot({
+                 pnl_plot(High_feature_Hedged_react())
                })),
       tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
-               renderDygraph({
-                 pnl_plot_interactive(Low_feature_Hedged_react())
+               renderPlot({
+                 pnl_plot(Low_feature_Hedged_react())
                })),
@@
       tabPanel("Cumulative Abnormal Returns,High, 12m hold",
-               renderDygraph({
-                 pnl_plot_interactive(High_feature_Hedged_react_index())
+               renderPlot({
+                 pnl_plot(High_feature_Hedged_react_index())
                })),
       tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
-               renderDygraph({
-                 pnl_plot_interactive(Low_feature_Hedged_react_index())
+               renderPlot({
+                 pnl_plot(Low_feature_Hedged_react_index())
                })),

### 2017-02-08 manuscript.Rnw
update of paper

--- 2016-05-03 manuscriptJF.Rnw
@@
 #dev.off();
-#library(knitr); knit2pdf('manuscriptJF.Rnw', texi2dvi='texi2dvi'); file.remove(paste("manuscriptJF",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
+#library(knitr); knit2pdf('manuscriptRF.Rnw', texi2dvi='texi2dvi'); file.remove(paste("manuscriptRF",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
 #dir.create("tmpfiles") # need to comment this if the directory already exists
 # Then to make it into Word: 
-# system("pandoc -s manuscriptJF.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx")
+# system("pandoc -s manuscriptRF.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx")
 
@@
 
-%<<  Data loading, eval = TRUE,
 \documentclass[12pt]{article}
@@
 % DEFAULT PACKAGE SETUP
-\usepackage{setspace,graphicx,epstopdf,amsmath,amsfonts,amssymb,amsthm,versionPO}
+\usepackage{setspace,graphicx,epstopdf,amsmath,amsfonts,amssymb,amsthm,versionPO,tabularx,ltxtable}
 \usepackage{marginnote,datetime,enumitem,subfigure,rotating,fancyvrb,graphics,siunitx}
@@
 
-%\usepackage[dvipsnames]{xcolor} % Refer to colors by name
-%\usepackage[colorlinks=true,urlcolor=blue,linkcolor=Green,citecolor=RedViolet]{hyperref}           
-%\usepackage{xcolor}
-%\usepackage{colortbl}
-%\usepackage{changepage}
-%\usepackage{adjustbox}
-%\usepackage{multirow}
-%\usepackage{longtable}
+% Make subsubsections inline with a period after the title
+\usepackage{titlesec}
+\newcommand{\periodafter}[1]{#1.}
+\titleformat{\subsubsection}[runin]
+{\normalfont\bfseries}{\thesubsubsection}{1em}{\periodafter}
 
@@
 
-\usepackage[margin=1in,top=1.5in,bottom=1.5in]{geometry}%
+% Notes options
+\ifnotes{%
+\usepackage[margin=1in,paperwidth=10in,right=2.5in]{geometry}%
+\usepackage[textwidth=1.4in,shadow,colorinlistoftodos]{todonotes}%
+}{%
+\usepackage[margin=1in]{geometry}%
 \usepackage[disable]{todonotes}%
-%\linespread{1.3}
-\onehalfspacing      % Use 1.5 spacing
+}
 
@@
 
+\renewcommand{\thetable}{\Roman{table}}
+\renewcommand{\thefigure}{\Roman{figure}}
+
 % Command to start a new page, starting on odd-numbered page if twoside option 
@@
 
-% JF-specific includes:
-\usepackage{indentfirst} % Indent first sentence of a new section.
+% RFS-specific includes:
+
 \usepackage{endnotes}    % Use endnotes instead of footnotes
-\usepackage{jf}          % JF-specific formatting of sections, etc.
-\usepackage[labelfont=bf,labelsep=period,justification=centering]{caption}   % Format figure captions
-\captionsetup[table]{labelsep=newline,labelfont=bf,textfont=bf}
-\captionsetup[figure]{labelfont=bf,justification=justified}
-\pagestyle{myheadings}
-
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{assumption}{Assumption}[section]
+\usepackage{rfs}          % RFS-specific formatting of sections, etc.
+\newcommand{\citeRFS}[1]{\citeauthor{#1}~\citeyear{#1}} % Not very elegant...
+
+% Define theorem-like commands and a few random function names.
+\newtheorem{condition}{Condition}
+\newtheorem{corollary}{Corollary}
 \newtheorem{proposition}{Proposition}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{corollary}{Corollary}
-\newtheorem{condition}{Condition}
+\newtheorem{obs}{Observation}
+\newcommand{\argmax}{\mathop{\rm arg\,max}}
+\newcommand{\sign}{\mathop{\rm sign}}
+\newcommand{\defeq}{\stackrel{\rm def}{=}}
 
@@
 
-%%Blind title page
-%\begin{titlepage}
-%\begin{center}
-%  \centering
-%\vskip 60pt
-%\LARGE Share Buyback and Equity Issue Anomalies Revisited \par
-%\vskip 1.5em
-%\normalsize  \today
-%\noindent \\ 
-%\begin{abstract}
-%\noindent We re-examine the behavior of stock returns after net issue  announcements using the five-factor model proposed by Fama and French (2015a).
-We confirm their findings that the equity issue anomaly disappears  with the five-factor model, but the buyback anomaly does not.
-Buyback announcements by firms  with high pre-announcement (idiosyncratic) volatility  are followed by higher long-term abnormal returns.
-This is inconsistent with the widely documented low volatility anomaly, but consistent with Stambaugh, Yu, and Yuan (2015) who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.
-%\end{abstract}
-%\vspace{2cm}
-%\end{center}
-%\medskip
-%\noindent \textit{JEL classification}: G35
-%\medskip
-%\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings
-%\end{titlepage}
-
 \setlist{noitemsep}  % Reduce space between list items (itemize, enumerate, etc.)
-
+\doublespacing
+%\onehalfspacing      % Use 1.5 spacing
+
+\thispagestyle{empty}
+
+\newcommand{\tit}{Volatility and the Buyback Anomaly}
+
+\newcommand{\abs}{The buyback anomaly survives when using the five factor \cite{FamaFrench2015} and the four factor \cite{StambaughYuan2016} models: buyback announcements are followed by positive long-term excess returns that are positively related to (idiosyncratic) volatility, inconsistent with the low volatility anomaly.
+The results are consistent with the market timing hypothesis: the option to take advantage of undervalued stock is more valuable when firm value is more uncertain or is more driven by company-specific information.
+Combining volatility with undervaluation indicators proposed by \cite{PeyerVermaelen2009} improves the predictability of excess returns after buyback announcements.
+}
+
+\doublespacing
 % Use endnotes instead of footnotes - redefine \footnote command
-
-\title{\textbf{Volatility and the Buyback Anomaly}}%\footnotetext{}
-
-\author{\uppercase{ Theodoros Evgeniou$^*$, Enric Junqu\'e de Fortuny$^{**}$,\\
-Nick Nassuphis$^{***}$,} and \uppercase{Theo Vermaelen}\thanks{INSEAD, Bd de Constance, 77300 Fontainebleau, France, phone: +33(0)1 6072 4000, $^{**}$Rotterdam School of Management, Burgemeester Oudlaan 50, 3062 PA Rotterdam, The Netherlands, $^{***}$31, St.
-Martin's Lane WC2N 4ER London, United Kingdom, e-mail:   \href{mailto:theodoros.evgeniou@insead.edu}{theodoros.evgeniou@insead.edu}, \href{mailto:enric.junquedefortuny@insead.edu}{enric.junquedefortuny@rsm.nl},  \href{mailto:nicknassuphis@gmail.com}{nicknassuphis@gmail.com}, and \href{mailto:theo.vermaelen@insead.edu}{theo.vermaelen@insead.edu}.
-}}
-
-\date{\today}              % No date for final submission
-
-% Create title page with no page number
-
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-
-\singlespacing
-
-\maketitle
-
-\vspace{-.2in}
-\begin{abstract}
-\noindent  We find that, inconsistent with the low volatility anomaly, post-buyback announcement long-term abnormal returns are higher when the pre-announcement (idiosyncratic) volatility is high.
-This is consistent with \cite{Stambaugh2015} who find a positive relation between returns and idiosyncratic volatility for undervalued stocks, and with the prediction that a repurchase authorization is an option for undervalued stocks \citep{IkenberryVermaelen1996}.
-The buyback anomaly also survives  when using the five-factor model of Fama and French (2015a).
-Combining volatility with undervaluation indicators proposed by \cite{PeyerVermaelen2009} improves the predictive power of excess returns after buyback announcements.
-\end{abstract}
-\vspace{2cm}
-
+%\renewcommand{\footnote}{\endnote}  % Endnotes instead of footnotes
+
+\centerline{\Large \bf \tit}
+
+\vspace*{0.5in}
+
+\centerline{\bf Abstract}
 \medskip
-
-%\noindent  \textit{JEL classification}: G35; G14; G32
-
-\medskip
-%\noindent \textit{Keywords}: Share Buybacks; Seasoned Equity Offerings; Anomalies; Volatility
-
-\thispagestyle{empty}
+\abs
 
 \clearpage
-
-\onehalfspacing
-\setcounter{footnote}{0}
-\renewcommand{\thefootnote}{\arabic{footnote}}
-\setcounter{page}{1}
-
-\doublespacing
-
-\section{Introduction}
-\label{sec:Introduction}
-
-The main purpose of this paper is to test whether there is a link between two well-known anomalies: the net issue anomaly, i.e.
-the fact that share buybacks (equity issues) are followed by long run positive (negative) excess returns\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}.
-For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}, and the volatility anomaly, i.e.
-the fact that (idiosyncratic) volatility is negatively related to expected returns \citep{Ang2006}.
-This link is plausible considering the fact that \cite{Stambaugh2015} find that the relation between idiosyncratic volatility and future returns reverses and becomes {\it positive} for undervalued stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.} They argue that their result is consistent with the costly {\it arbitrage hypothesis}: idiosyncratic volatility represents risk that deters arbitrage and the resulting reduction in mispricing, hence among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.
-As the positive (negative) long run returns after buybacks (equity issues) are generally interpreted as evidence of undervaluation (overvaluation), we would predict also a positive (negative) relation between volatility and future returns after firms announce a buyback (equity issue).
-
-A positive relation between volatility and future returns after buyback authorization announcements is also expected based on the {\it option hypothesis} of \cite{IkenberryVermaelen1996}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks.
-If markets underestimate the value of this option at the time of the buyback authorization, long term excess returns should be positively correlated with volatility.
-Note that this option hypothesis makes no predictions about excess returns after equity issues which, unlike buyback authorizations, are firm commitments, not options.
-
-In the volatility literature idiosyncratic volatility is estimated by the residual variance of an asset pricing model such as the Fama-French three factor model.
-Empirically there is a very high correlation between residual variance and total variance (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study) so for the remainder of this paper we will use the latter when we refer to just volatility, the volatility anomaly, or the hypotheses above.
-We also use an alternative measure of idiosyncratic volatility that is not correlated (\Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study) with volatility: $1-R^2$.
-For the remainder of the paper we will use this when we refer to {\it idiosyncratic} volatility.
-It measures to what extent the volatility of stock returns is explained by company-specific (non-factor related) information [see also \cite{LiRajgopaletal2014}].
-The hypothesis that managers are able to time the market [e.g., \cite{IkenberryLakonishokVermaelen1995}] is based on the assumption that managers have superior knowledge about company-specific information.
-Hence the prediction of the {\it information advantage hypothesis} is that buyback announcements of firms with high idiosyncratic volatility will also generate higher long term excess returns.
-
-Before proceeding with examining the link between anomalies, it is important to verify that these anomalies are real and not simply a proxy for risk, or have disappeared in recent years as has happened with many other ones~\citep{McLean2016}.
-Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the \cite{Carhart1997} 4-factor model as benchmarks.
-However, \cite{FamaFrench2015b}  argue that many anomalies are weakened or  do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns.
-This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns \citep{NovyMarx2013}.
-They find that the volatility anomaly survives for small firms, but the net issue anomaly does not.
-If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research.
-Note, however, that \cite{FamaFrench2015b} do not exactly replicate the papers that first reported the anomalies.
-First, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date as e.g., \cite{PeyerVermaelen2009}.
-For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization \citep{StephensWeisbach1998}.
-Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues).
-The part of their sample where net equity issues are positive is defined as the ``buyback sample''.
-But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations.
-Moreover the idea of pooling buybacks and equity issues in ``net issues'' assumes that the decision to issue equity is simply the mirror of buying back shares.
-However, issuing stock to new investors is not the same as buying back stock from ``old'' selling investors.
-In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only affects selling shareholders who leave the firm.
-So before concluding that the buyback and equity issue anomalies have disappeared, they have to be examined separately, using announcement dates.
-
-So the second purpose of this paper is to verify whether the buyback and equity issue anomalies still exist using the more recent \cite{FamaFrench2015a} five-factor  model, for buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}.\footnote{Using throughout this paper the q-factor model of \cite{Houetal2015} instead of the five-factor model of \cite{FamaFrench2015a} leads to the same conclusions.} We confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
-However, even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio.
-An interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive.
-We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms.
-%, and that the anomaly does not disappear if we exclude specific industries. 
-The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2015}.
-
-It remains a fact though that the buyback anomaly is to some extent a small firm anomaly, as also found by \cite{PeyerVermaelen2009}: value-weighting all the events (as suggested by~\cite{MitchellStafford2000}) makes the (Calendar Time event study method) alphas disappear, although {\it not} for high volatility stocks as we note below.\footnote{Value weighted Calendar Time method results are available upon request.}  So the anomaly does not challenge the view that 99$\%$ of all stocks may well be priced efficiently.
-It simply shows that small cap firms are priced less efficiently and managers of these firms are able to take advantage of undervaluation, at least on average.
-Moreover, while we do not value-weight the events, as argued by \cite{PeyerVermaelen2009}, if anything, to increase the power of the test to detect mispricing, any weighting should be based on the inverse of size.
-However the negative relation between size and alpha may partly explain why this anomaly persists after 30 years and has attracted very little attention in the asset management industry.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA.
-The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization.
-We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} Indeed because management fees are proportional to fund size one expects relatively less interest in anomalies concentrated in small caps or microcaps.
 
@@
 
-After having established that the buyback anomaly survives the Fama-French five factor model and is robust over time, we test for the relation between volatility measures and long term excess returns.
-We find a significant {\it  positive} relation between excess returns and volatility as well as idiosyncratic volatility measured by $1-R^2$.
-%Note although there is a high correlation (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$) between total volatility and residual variance (the proxy used in the literature for idiosyncratic volatility), the correlation between standardized idiosyncratic volatility and total volatility is only \Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$.
-In summary, the positive relation between volatility and excess returns is consistent with the costly arbitrage hypothesis of~\cite{Stambaugh2015} as well as with the option hypothesis of~\cite{IkenberryVermaelen1996}, while the positive relation between $1-R^2$ and excess returns is consistent with the information advantage hypothesis.
-
-Combining  total volatility  and idiosyncratic volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index (EU-Index), improves the predictability of excess returns.
-In particular, during the four years following the buyback announcement, the high EU-Index Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
+\section{Introduction}
+\label{sec:Introduction}
+
+In this paper we first test whether previously reported positive (negative) long-term excess returns following share buyback (equity issue) announcements\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}.
+For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}   can be explained by  the recently proposed five factor \cite{FamaFrench2015}  or the four factor \cite{StambaughYuan2016} models.
+Excess returns in previous research are calculated using different benchmarks such as firms with similar size and book-to-market ratio \citep{IkenberryLakonishokVermaelen1995}, the  \cite{FamaFrench1993} three-factor model or the \cite{Carhart1997} 4-factor model \citep{PeyerVermaelen2009}.
+\cite{FamaFrench2015}\footnote{Note that the q-factor model of \cite{Houetal2015} also combines market and size factors with investment and profitability factors.
+In this paper, their model generates similar results as that of \cite{FamaFrench2015}.
+Results available upon request.}  add investment and profitability factors to the \cite{FamaFrench1993} model.
+Note that these factors were considered anomalies before.
+\cite{StambaughYuan2016} expand this approach and add two ''mispricing'' factors to the market and value ones.
+These factors are constructed by averaging rankings across a set of 11 prominent anomalies examined by \cite{Stambaugh2015}.
+Unlike \cite{FamaFrench2015} they don't argue that all their factors capture systematic risk: the mispricing factors can capture common sources of mispricing such as sentiment risk.
+\cite{StambaughYuan2016} show that their model explains a wide range of the 73 anomalies listed by \cite{Houetal2015}.
+
+It should be noted that this extensive list of 73 anomalies does not include the buyback anomaly we consider in this paper.
+The list includes the net issue anomaly which assumes that an equity issue is simply the opposite of a repurchase decision, a common assumption made in the asset pricing literature.
+For example, \cite{FamaFrench2016}  calculate returns after net equity issues defined as funds spent on buybacks minus funds spent on equity issues.
+They assume investors buy after the completion of the buyback and the equity issue, not around the announcement date of the buyback authorization as is done in previous research [e.g., \cite{IkenberryLakonishokVermaelen1995}].
+For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization, or not completed at all \citep{StephensWeisbach1998}.
+A firm may announce a buyback today because it believes it is undervalued, but the market may become efficient before the firm has completed a significant fraction of the repurchase.
+In other words, the excess returns may be realized before the actual repurchase is completed.
+That's why the proper way to test this anomaly is to follow an event study approach that starts computing excess returns in the month after the buyback authorization.
+
+Pooling buybacks and equity issues in a ''net issues'' measure ignores two other major differences between repurchases and equity issues which should have an effect on the ability and willingness to engage in market timing.
+First, an open market repurchase authorization creates an option to repurchase stock and the seller is not aware she is selling to the corporation, while in an equity issue the investor knows that the company is the issuer.
+Obviously this makes it easier to buy back undervalued shares than to issue overvalued shares.
+Second, issuing overvalued shares to new investors may hurt relations with these investors and make it more difficult  to convince them to buy new shares in a follow up secondary offering.\footnote{One of the arguments for IPO underpricing is that it creates a positive experience for investors making it easier to convince them to buy new shares in a follow up offering \citep{Ibbotson1975}.} On the other hand, repurchasing undervalued shares from investors who have decided to sell their shares anyway should not create an investor relations problem.
+So in order to test the buyback and equity issue anomalies one has to examine them separately, using an event study approach as we do in this paper.
+
+We find that both the \cite{FamaFrench2015} and \cite{StambaughYuan2016} models explain the equity issue anomaly, but not the buyback anomaly.
+Moreover, the \cite{FamaFrench2015} model does a better job than the \cite{StambaughYuan2016} one: during the 48 months after the buyback announcement the four factor model produces (statistically significant at the 1$\%$ level) excess returns of \Sexpr{round(CAL_table_all_bb["+48","CAL 5F"],2)}$\%$ per month versus \Sexpr{round(CAL_table_all_bb["+48","CAL 3F"],2)}$\%$  per month with the four factor model.
+Unlike other anomalies that disappear over time \citep{McLean2016}, the buyback anomaly persists over time and does not decline in recent years.
+\cite{PeyerVermaelen2009} show that long terms excess returns are negatively related to firm size, prior return and market to book ratio and summarize these characteristics in an undervaluation index (U-index).
+We also show that this conclusion holds for both factor models.
+
+%Why does the \cite{StambaughYuan2016} four factor model does a poor job explaining the buyback anomaly?
+The reason, we believe, is that the buyback anomaly is inconsistent with some of the major 11 anomalies used to construct the \cite{Stambaugh2015} mispricing index.
+For example, long-term excess returns after buyback announcements are negatively related to the returns in the 6 months prior to the buyback.
+As buyback stocks have negative momentum before the announcement, the momentum anomaly \citep{JegadeeshTitman1993} predicts lower returns not higher returns.
+Similarly, \cite{PeyerVermaelen2009} find that the most undervalued buyback stocks miss earnings forecast, which is the opposite of the \cite{Mendenhall2004} earnings drift anomaly which predicts negative excess returns after missing earnings forecasts.
+
+Having shown that the buyback anomaly survives the most recent factor models,  we address the second major question in this paper: are excess returns related to volatility?
+Such a relation is plausible, considering past research on anomalies and volatility.
+\cite{Ang2006} find that (idiosyncratic) volatility is negatively related to stock returns.
+However, \cite{Stambaugh2015} find that the relation between idiosyncratic volatility and future returns reverses and becomes positive for undervalued stocks, where undervaluation is measured by combining eleven major anomalies reported in the literature in a Mispricing Measure.
+They argue that their result is consistent with the costly arbitrage hypothesis: idiosyncratic volatility represents risk that deters arbitrage, hence among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.\footnote{Note that the relation between volatility and arbitrage risk has been studied extensively over the last twenty years: volatility captures risk that prevents arbitrageurs from stepping in [e.g., \cite{DeLongetal1990} and \cite{ShleiferVishny1997}].
+For example, \cite{Pontiff1996} finds that the closed end discount is stronger for high volatility stocks.
+\cite{Mendenhall2004}, \cite{Alietal2003}, \cite{LiLu2010} and \cite{WangYu2013} report similar conclusions for, respectively the post-earnings drift anomaly, the value premium anomaly, the asset growth anomaly and the return on assets anomaly.
+Note, however, that none of these anomalies use the \cite{FamaFrench2015} model to estimate expected returns.} With the same reasoning they argue that for overpriced stocks there should be a negative relation between idiosyncratic volatility and future returns.
+If repurchasing firms are undervalued and equity issuers are overvalued, this theory predicts a positive (negative) relation between idiosyncratic volatility and future returns after firms announce a buyback (equity issue).
+Moreover, \cite{Stambaugh2015} also argue that because limits to arbitrage are higher among overvalued stocks (e.g., most investors are reluctant or unable to short stocks), the volatility effect among equity issuers should be stronger than the volatility effect among repurchasing firms.
+
+We find results inconsistent with the costly arbitrage hypothesis.
+First, as mentioned supra, on average long term excess returns are positive after buybacks but the negative equity issue anomaly disappears.
+Second, while the volatility effect for repurchasing firms is positive, as predicted, there is no significant {\it negative} relation between volatility and excess returns after equity issues.
+
+We argue that the positive volatility effect after buybacks is consistent with the market timing hypothesis, the fundamental hypothesis behind the buyback anomaly.\footnote{Note that the market timing hypothesis is different from the signalling hypothesis which assumes that the purpose of the buyback is to correct undervaluation [e.g., \cite{Vermaelen1981}, \cite{BhattacharyaJacobsen2016}].
+The market timing hypothesis requires that the market underreacts to the buyback allowing long-term investors (including insiders) to benefit at the expense of selling shareholders.}   According to this hypothesis the ability to time the market depends on the extent a stock can be mispriced.
+\cite{IkenberryVermaelen1996} point out that open market repurchase programs are options to buy undervalued stock, not firm commitments.
+The larger the volatility the larger the value of this option.
+While they show that short-term announcement returns are positively correlated with volatility, if markets underreact, this {\it option hypothesis} would also predict a positive relation between long-term returns and volatility.
+Note that as equity issues are underwritten firm commitments, not options to issue equity, no such volatility effect is predicted in that case.
+The market timing hypothesis also assumes that managers have superior knowledge about company-specific information, not the overall market.
+Hence the prediction of the {\it information advantage hypothesis} is that buyback announcements of firms with high standardized idiosyncratic volatility, namely (1-$R^2$) measuring to what extent the volatility of stock returns is explained by company specific (non-factor related) information [e.g., see \cite{LiRajgopaletal2014}], will generate higher long term excess returns, which is also what we find.
+
+%The prediction of the costly arbitrage hypothesis is that there is a positive relation between volatility and excess returns after buybacks and a negative relation between volatility and excess returns after equity issues.
+While the first hypothesis is confirmed by the data, the second one is not.
+The results are more consistent with the options hypothesis of \cite{IkenberryVermaelen1996} who point out that open market repurchase authorizations are options to repurchase stock, not firm commitments.
+As a result, they predict that announcement returns should be positively related to volatility.
+
+%Moreover, because limits to arbitrage are higher among overvalued stocks (e.g.
+most investors are reluctant or unable to short stocks) the negative volatility effect among overvalued stocks should be stronger than the positive volatility effect among undervalued stocks.
+Indeed, \cite{Bravetal2010} find that the limits to arbitrage can explain some overvaluation anomalies but not undervaluation anomalies.
+So whether the costly arbitrage hypothesis can explain the buyback anomaly and/or the new equity issue anomaly is an empirical question.
+%The prediction of the costly arbitrage hypothesis is that there is a positive relation between volatility and excess returns after buybacks and a negative relation between volatility and excess returns after equity issues.
+While the first hypothesis is confirmed by the data, the second one is not.
+The results are more consistent with the options hypothesis of \cite{IkenberryVermaelen1996} who point out that open market repurchase authorizations are options to repurchase stock, not firm commitments.
+As a result, they predict that announcement returns should be positively related to volatility.
+Note that as equity issues are firm commitments, no such volatility effect is predicted.
+We also argue that the market timing hypothesis implicitly assumes that managers have superior knowledge about company-specific information, not the overall market.
+Hence the prediction of the information advantage hypothesis is that buyback announcements of firms with high standardized idiosyncratic volatility, measured by (1-$R^2$), will also generate higher long term excess returns.
+Indeed, it measures to what extent the volatility of stock returns is explained by company-specific (non-factor related) information [see also \citep{LiRajgopaletal2014}].
+
+After documenting that volatility as well as standardized idiosyncratic volatility are positively related to long-term excess returns after buybacks we test whether these variables can improve our ability to predict long-term excess returns, above the predictive ability of the undervaluation index (U-index) developed by \cite{PeyerVermaelen2009}.
+Combining total volatility and standardized idiosyncratic volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index (EU-Index) improves the predictability of excess returns.
+In particular, during the four years following the buyback announcement, the high EU-Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
 Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.
-
-%In order to address the issue of size (which suggests the buyback anomaly is not economically important), we close with a section on buyback anomalies for large firms.
-We find that there is a buyback anomaly for large firms, but only if we focus on large volatility stocks.
-This suggests that when there is large uncertainty about fundamental value, even in large firms the option to repurchase stock at prices below fair value is worth a lot.
-Note however that the alpha for these large high volatility firms is significantly smaller than the alpha of the high EU-Index index so there remains a tradeoff between excess returns and firm size.
-
-This paper is organized as follows.
-In section 2 we describe our data.
-In section 3 we test whether the buyback and equity issue anomalies survive when we use the \cite{FamaFrench2015a} five-factor model.
-We also compare firms that buy back stock and issue equity within 48 months of a buyback announcement with firms that do not issue stock subsequently.
-In section 4 we test whether the buyback anomaly is robust across time and investment horizon.
-%and industry. 
-In section 5 we test whether (total) volatility as well as idiosyncratic volatility ($1-R^2$) can improve the predictability of excess returns, relative to simply using the Undervaluation Index proposed by \cite{PeyerVermaelen2009}.
-Section 6 concludes.
+On the other hand, we show that the Mispricing Measure (MM) developed by \cite{Stambaugh2015} on the basis of 11 anomalies is not helpful in predicting long term excess returns after buyback authorization announcements.
+This again shows that the 11 anomaly indicators that may be relevant for average stocks don't apply to buyback stocks.
+
+%The fact that the buyback anomaly survives could still mean that the ''excess'' returns are compensating for some risks that the Fama-French 5-factor model does not account for - and is not related to any information advantage of company insiders.
+The third contribution of this paper is to provide further support for the hypothesis that excess returns after buybacks can be explained by information asymmetry rather than a risk-based story.
+One way to show that these excess returns reflect adjustment to undervaluation is to show that they are positively correlated with observable indicators of potential undervaluation and/or information advantage of the management.
+\cite{IkenberryLakonishokVermaelen1995} assume that value stocks are more likely to be undervalued than growth stocks.
+The fact that they find a positive relation between long-term excess returns and book-to-market supports the undervaluation hypothesis.
+The undervaluation index of \cite{PeyerVermaelen2009} assumes that buybacks announced by beaten up small cap value firms are more likely to be driven by undervaluation than other firms.
+consider three new indicators (firm size, prior return and stated motivation in the press release) and combine them with the book-to-market indicator in an undervaluation index (U-index).
+Adding these additional indicators improves the predictability of excess returns, which is consistent with the undervaluation hypothesis.
+In this paper we test whether two new indicators, standardized idiosyncratic volatility (measured by 1-$R^2$) and volatility can improve our understanding of excess returns by combining them with the U-index of \cite{PeyerVermaelen2009}.
+
+%It remains a fact though that the buyback anomaly is to some extent a small firm anomaly, as also found by \cite{PeyerVermaelen2009}: indeed, we find that value-weighting all the events [as suggested by \cite{MitchellStafford2000}] makes the (Calendar Time event study method) alphas disappear.
+However, if we exclude the firms in the largest size quartile, the anomaly persists (also for the Calendar Time event study method).
+This makes sense as small firms are more opaque and less followed by analysts.
+They also tend to be held more by insiders, so that in these case share buybacks are more similar to insider buying with company funds.
+If anything, to increase the power of the test to detect mispricing and the possibility that managers (at least in some firms) can time the market based on their information advantage relative to investors, any weighting should be based on the inverse of size.
+The fact that excess returns disappear when we value weight provides further support for the hypothesis that excess returns are driven by information asymmetry for some firms.
+The fact that this is a small cap anomaly may partly explain why this anomaly persists after 30 years and has attracted very little attention in the asset management industry.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA.
+The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization.
+We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.}  Indeed because management fees are proportional to fund size one expects relatively less interest in anomalies concentrated in small caps or microcaps.
+
+Summarizing, this paper makes four fundamental contributions.
+First we show that the buyback anomaly survives  after using the most recent factor models developed by \cite{FamaFrench2015} and \cite{StambaughYuan2016}.
+We argue that  this is a result of the fact that, unlike past research on anomalies in the asset pricing literature, we don't pool buybacks and equity issues in a ''net issue'' anomaly.
+Second, the fact that the buyback anomaly persists and the equity issuance anomaly disappears (i.e, we find no evidence that, on average, firms issue equity when they are overvalued) is inconsistent with the costly arbitrage hypothesis which predicts that anomalies that generate long-term negative excess returns are more difficult to arbitrage away than positive excess return anomalies.
+Third,  we find evidence that long-term excess returns after buybacks are positively related with total volatility and standardized company specific volatility, which is consistent with the hypothesis that buybacks are driven by market timing.
+Indeed, the option hypothesis  of \cite{IkenberryVermaelen1996} argues that an open market buyback authorization creates an option to take advantage of undervaluation and this option is more valuable for risky firms.
+The positive relation between idiosyncratic standardized volatility and long term excess returns is consistent with the  hypothesis that the information advantage of managers is larger when stock prices are less driven by common factors.
+Finally, we show that adding volatility and standardized idiosyncratic volatility to the factors proposed by previous research as undervaluation proxies and combining them in an Enhanced Undervaluation index improves our forecasting ability of excess returns after buyback authorization announcements.
+As a theoretical argument can be made that both measures are proxies for the competitive information advantage of managers-insiders, this strengthens the support for the undervaluation and market timing hypothesis.
+On the other hand, we show that the Mispricing Measure of \cite{Stambaugh2015} is not helpful in predicting excess returns after  buyback authorization announcements, indicating that the anomaly indicators of \cite{Stambaugh2015} are not relevant in the case of buybacks.
+
+%Finally, we show that adding volatility and standardized idiosyncratic volatility to the factors proposed by previous research as undervaluation proxies and combining them in an Enhanced Undervaluation index improves our forecasting ability of excess returns after buyback authorization announcements.
+As a theoretical argument can be made that both measures are proxies for the competitive information advantage of managers-insiders, this strengthens the support for the undervaluation and market timing hypothesis.
+However, it should be noted that the anomaly is more pronounced in small firms, which may explain why this anomaly has attracted little attention in the asset management industry.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% OLD INTRO
+
+%We study whether previously reported positive (negative) excess returns following share buyback (equity issue) announcements\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}.
+For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.} are compensation for risk using recently proposed risk models [specifically from \cite{FamaFrench2015} or \cite{Houetal2015}], or evidence for possible market timing by insiders of undervalued (overvalued) firms who may take advantage of information asymmetries.
+We also explore the impact of firm specific or total volatility on excess returns, as theoretical arguments can be made that high volatility makes arbitrage for outsiders costlier.
+Specifically, the first purpose of this paper is to test whether there is a link between two well-known anomalies: the net issue anomaly, i.e.
+the fact that share buybacks (equity issues) are followed by long run positive (negative) excess returns, and the volatility anomaly, i.e.
+the fact that (idiosyncratic) volatility is negatively related to expected returns \citep{Ang2006}.
+This link is plausible considering the fact that \cite{Stambaugh2015} find that the relation between idiosyncratic volatility, measured as residual variance, and future returns reverses and becomes {\it positive} for undervalued stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.} They argue that their result is consistent with the {\it costly  arbitrage hypothesis}: idiosyncratic volatility represents risk that deters arbitrage and the resulting reduction in mispricing, hence among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.
+As the positive (negative) long run returns after buybacks (equity issues) are generally interpreted as evidence of undervaluation (overvaluation) that firm insiders may take advantage of, we would predict also a positive (negative) relation between volatility and future returns after firms announce a buyback (equity issue): volatility may also make it easier for insiders to take advantage of undervaluation (overvaluation) based on an information advantage on the one hand and the challenge for outsiders to correct mispricing due to higher arbitrage costs on the other hand.
+
+%Moreover, \cite{Stambaugh2015} argue that, because limits to arbitrage are higher among overvalued stocks (e.g.
+most investors are reluctant or unable to short stocks) the negative volatility effect among overvalued stocks should be stronger than the positive volatility effect among undervalued stocks.
+Indeed, \cite{Bravetal2010} find that the limits to arbitrage can explain some overvaluation anomalies but not undervaluation anomalies such as the fact e.g.
+that positive earnings surprises are followed by positive excess returns.
+So whether the costly arbitrage hypothesis is also related to the buyback undervaluation anomaly is ultimately an empirical question.
+
+%The second purpose of this paper is to test whether the buyback and equity issue anomalies still exist and are not simply a proxy for risk, or have disappeared in recent years as has happened with other ones~\citep{McLean2016}.
+Unlike past work, we do so by both using the more recent \cite{FamaFrench2015} five-factor  model, for buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, and using event announcement dates and separating equity issues and buybacks.\footnote{Using throughout this paper the q-factor model of \cite{Houetal2015} instead of the five-factor model of \cite{FamaFrench2015} leads to the same conclusions.
+Results available upon request.
+} Excess returns in previous research are calculated using different benchmarks such as firms with similar size and book-to-market ratio \citep{IkenberryLakonishokVermaelen1995} or the \cite{FamaFrench1993} three-factor model or the \cite{Carhart1997} 4-factor model \citep{PeyerVermaelen2009}.
+However, \cite{FamaFrench2016}  argue that many anomalies are weakened or do not survive after using the more recent \cite{FamaFrench2015} five-factor asset pricing model as a model of expected returns.
+This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns \citep{NovyMarx2013}.
+They find that the volatility anomaly survives for small firms, but the net issue anomaly (i.e.
+equity issues minus buybacks) does not.
+If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research.
+
+%Moreover, \cite{FamaFrench2016} do not exactly replicate the papers that first reported the anomalies.
+Indeed, unlike the authors that ''discovered'' the anomalies they do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues).
+The part of their sample where net equity issues are positive is defined as the ''buyback sample''.
+But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations.
+Moreover, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date of the buyback authorization as is done in previous research [e.g., \cite{PeyerVermaelen2009}].
+For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization, or not completed at all \citep{StephensWeisbach1998}.
+This slow execution is partially driven by SEC regulations designed to minimize the impact on trading volume as well as tactical considerations.
+This may produce another downward bias in post-repurchase excess returns.
+For example, assume the stock price today is \$10 and the management believes its stock is undervalued and announces a typical buyback program for 7$\%$ of its outstanding shares.
+Suppose that one year later 2$\%$ of the shares are repurchased and the market corrects the undervaluation so that the company halts the program.
+At the end of the first year the firm is considered as a net repurchaser in the \cite{FamaFrench2016} sample, and no long-term excess return will be observed afterwards even though there were excess returns during the first post-announcement year.
+
+%Pooling buybacks and equity issues in a ''net issues'' measure assumes that the decision to issue equity is simply the mirror of buying back shares.
+This ignores two other major differences between repurchases and equity issues (besides the fact that a buyback program is an option, not a firm commitment as an equity issue).
+First, in an open market repurchase the seller is not aware she is selling to the corporation, while in an equity issue the investor knows that the company is the issuer.
+Obviously this makes it easier to buy back undervalued shares than to issue overvalued shares.
+Second, issuing overvalued shares to new investors may hurt relations with these investors.
+One of the arguments for IPO underpricing is that it creates a positive experience for investors making it easier to convince them to buy new shares in a follow up secondary offering \citep{Ibbotson1975}.
+Issuing overvalued stock creates a negative experience for new investors.
+On the other hand, repurchasing undervalued shares from investors who have decided to sell their shares anyway should not create an investor relations problem.
+So in order to test the buyback and equity issue anomalies one has to examine them separately, using announcement dates as we do in this paper.
+
+%We confirm the \cite{FamaFrench2016} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
+The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2016}.
+As we find that only the buyback anomaly survives, this paper focuses on buybacks, not equity issues.
+
+%The fact that the buyback anomaly survives could still mean that the ''excess'' returns are compensating for some risks that the Fama-French 5-factor model does not account for - and is not related to any information advantage of company insiders.
+The third contribution of this paper is to provide further support for the hypothesis that excess returns after buybacks can be explained by information asymmetry rather than a risk-based story.
+One way to show that these excess returns reflect adjustment to undervaluation is to show that they are positively correlated with observable indicators of potential undervaluation and/or information advantage of the management.
+\cite{IkenberryLakonishokVermaelen1995} assume that value stocks are more likely to be undervalued than growth stocks.
+The fact that they find a positive relation between long-term excess returns and book-to-market supports the undervaluation hypothesis.
+\cite{PeyerVermaelen2009} consider three new indicators (firm size, prior return and stated motivation in the press release) and combine them with the book-to-market indicator in an undervaluation index (U-index).
+Adding these additional indicators improves the predictability of excess returns, which is consistent with the undervaluation hypothesis.
+In this paper we test whether two new indicators, standardized idiosyncratic volatility (measured by $1-R^2$) and volatility can improve our understanding of excess returns by combining them with the U-index of \cite{PeyerVermaelen2009}.
+
+%An indicator that measures the competitive information advantage of managers is standardized idiosyncratic volatility, measured by $(1-R^2)$ where $R^2$ is, for example, that of a regression of the 6-months pre-announcement daily returns of the stock on the five factors of \cite{FamaFrench2015}.\footnote{Note that standardized idiosyncratic volatility differs from residual variance which is the measure of idiosyncratic volatility used in the volatility literature.
+Because of the high correlation between residual variance and total volatility (\Sexpr{round(100*cor(BUYBACK_DATA$DATASET$CRSP$pre_vol, BUYBACK_DATA$DATASET$CRSP$IVOL),2)}$\%$ in our sample) testing for the impact on volatility on stock returns is identical to testing for the impact of residual variance.
+Throughout this paper we use the term ''standardized idiosyncratic volatility'' to refer to $(1-R^2)$.} Indeed, it measures to what extent the volatility of stock returns is explained by company-specific (non-factor related) information [see also \citep{LiRajgopaletal2014}].
+The hypothesis that managers are able to time the market is based on the assumption that managers have superior knowledge about company-specific information, not the overall market.
+Hence the prediction of the {\it information advantage hypothesis} is that buyback announcements of firms with high standardized idiosyncratic volatility $(1-R^2)$ will also generate higher long term excess returns.
+
+%Adding (raw) volatility as a factor that explains excess returns can be justified by the \cite{Stambaugh2015} {\it costly arbitrage hypothesis} but also by the {\it option hypothesis} proposed by \cite{IkenberryVermaelen1996}:  a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks.
+In other words, the potential of managers to take advantage of undervaluation increases with the uncertainty about its fundamentals.
+This option could be quite valuable as buyback authorizations are typically granted for several years and are often extended.
+If the market is efficient this option effect should be incorporated in the stock price at the time of the buyback announcement.
+Indeed, \cite{IkenberryVermaelen1996} find that short-term announcement returns are positively related to volatility.
+However, if markets underestimate the value of this option at the time of the buyback authorization, long term excess returns should be positively correlated with volatility.
+Note that, unlike the costly arbitrage hypothesis, this option hypothesis does not predict a relation between volatility and excess returns after equity issues which, unlike buyback authorizations, are firm commitments, not options.
+
+%We find a significant positive relation between excess returns and volatility as well as standardized idiosyncratic volatility.
+Combining total volatility and standardized idiosyncratic volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index (EU-Index) also improves the predictability of excess returns.
+In particular, during the four years following the buyback announcement, the high EU-Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
+Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.
+
+%It remains a fact though that the buyback anomaly is to some extent a small firm anomaly, as also found by \cite{PeyerVermaelen2009}: indeed, we find that value-weighting all the events [as suggested by \cite{MitchellStafford2000}] makes the (Calendar Time event study method) alphas disappear.
+However, if we exclude the firms in the largest size quartile, the anomaly persists (also for the Calendar Time event study method).
+This makes sense as small firms are more opaque and less followed by analysts.
+They also tend to be held more by insiders, so that in these case share buybacks are similar to insider buying with company funds.
+If anything, to increase the power of the test to detect mispricing and the possibility that managers (at least in some firms) can time the market based on their information advantage relative to investors, any weighting should be based on the inverse of size.
+The fact that excess returns disappear when we value weight provides further support for the hypothesis that excess returns are driven by information asymmetry for some firms.
+At the same time the negative relation between size and alpha may partly explain why this anomaly persists after 30 years and has attracted very little attention in the asset management industry.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA.
+The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization.
+We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.}  Indeed because management fees are proportional to fund size one expects relatively less interest in anomalies concentrated in small caps or microcaps.
+
+%Summarizing, this paper makes three fundamental contributions.
+First we show that the buyback anomaly, but not the equity issue one, survives after using the 5-factor model of Fama and French if buybacks are separated from equity issues and excess returns are calculated after the authorization date.
+Second, in agreement with \cite{Stambaugh2015}, we find support for the  hypothesis that firms announce buybacks because they are undervalued and because of costly arbitrage there will be a positive relation between volatility and returns.
+The results are also consistent with the \cite{IkenberryVermaelen1996} option hypothesis.
+However, as the equity issue anomaly does not survive the Fama-French model we can't test the other prediction of \cite{Stambaugh2015}, i.e.
+that returns of overvalued firms will be negatively correlated with volatility and that this relation will be stronger for overvalued firms than undervalued firms.\footnote{Of course this does not mean that the \cite{Stambaugh2015} hypothesis is rejected as there could be other overvalued firms with a strong negative relation between excess returns and volatility.}  Finally, we show that adding volatility and standardized idiosyncratic volatility to the factors proposed by previous research as undervaluation proxies and combining them in an Enhanced Undervaluation index improves our forecasting ability of excess returns after buyback authorization announcements.
+As a theoretical argument can be made that both measures are proxies for the competitive information advantage of managers-insiders, this strengthens the support for the undervaluation and market timing hypothesis of some firms.
+
+So why does the buyback anomaly survive, unlike many of the 73 anomalies tested by \cite{StambaughYuan2016}?
+First, it should be noted that the anomaly is more pronounced in small firms, which may explain why this anomaly has attracted little attention in the asset management industry.
+Second, unlike anomalies based on firm characteristics, research on the buyback anomaly is motivated by surveys of CFOs who claim that the anomaly exists \citep{Bravetal2005}, i.e.
+they are able to time the market.
+Finally, firms that repurchase shares because of undervaluation don't look undervalued according to more general mispricing measures such as that of \cite{Stambaugh2015}.
+As buyback stocks have negative momentum before the announcement, the momentum anomaly \citep{JegadeeshTitman1993} predicts lower returns not higher returns.
+Similarly, \cite{PeyerVermaelen2009} find that the most undervalued buyback stocks miss earnings forecast, which is the opposite of the \cite{Mendenhall2004} earnings drift anomaly which predicts negative excess returns after missing earnings forecasts.
+In other words, an investor may be reluctant to buy stocks after a buyback announcement if there are other anomalies (such as, e.g., momentum) that suggest overvaluation.
+
+The paper is organized as follows.
+In section \ref{sec:Data} we describe our data.
+In section \ref{sec:PastFindingsBB} we test whether the buyback and equity issue anomalies survive when we use the \cite{FamaFrench2015} five-factor model and the \cite{StambaughYuan2016} four factor model.
+In section \ref{sec:robust} we test whether the buyback anomaly is robust across time and investment horizon.
+In section \ref{sec:infoassymetry} we test whether (total) volatility as well as standardized idiosyncratic volatility $(1-R^2)$ can improve the predictability of excess returns, relative to simply using the Undervaluation Index proposed by \cite{PeyerVermaelen2009}.
+Section \ref{sec:conclusion} concludes.
 
@@
 The Fama-French factors were obtained from Kenneth French's website.
-
-For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request.
-An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, will also be available at \href{http://tevgeniou.github.io/BuybacksIssuers/}{tevgeniou.github.io/BuybacksIssuers.}}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both.
+The \cite{StambaughYuan2016} factors and the Mispricing Measure were obtained from Yu Yuan's website.
+All variables used in this paper are described in the Appendix.
+
+For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.
+%\footnote{More information is available upon request.
+An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, will also be available at \href{http://tevgeniou.github.io/BuybacksIssuers/}{tevgeniou.github.io/BuybacksIssuers.}}
+We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both.
 Finally, we removed the following events: no CRSP returns or not all Compustat data available (\Sexpr{BUYBACK_DATA$cleanupNoPermno +  BUYBACK_DATA$cleanupNoCRSPdata + BUYBACK_DATA$cleanupMissingSomeValues} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).
@@
 The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms.
+Table \ref{tbl:descriptive} summarizes the key data in this study.
 The average percent of shares authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).
@@
 Our final sample contains \Sexpr{length(cusip_iss)} events made by \Sexpr{length(unique(cusip_iss))} firms.
-The average percent of shares issued was \Sexpr{datasummaryISS["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryISS["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{datasummaryISS["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryISS["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryISS["BE/ME", "Mean"]} (median of \Sexpr{datasummaryISS["BE/ME", "Median"]}).
+The average percent of shares issued (for the events for which this information was available) was \Sexpr{datasummaryISS["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryISS["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{datasummaryISS["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryISS["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryISS["BE/ME", "Mean"]} (median of \Sexpr{datasummaryISS["BE/ME", "Median"]}).
+Note also from Table \ref{tbl:descriptive} that the average and median Mispricing Measure developed by \cite{Stambaugh2015} is higher for equity issuers than for buyback stocks, which is consistent with the hypothesis that equity issuers are more likely to be overvalued than share repurchasers.
 
@@
 
-We start with revisiting past research but now using a longer and more recent time period and the five-factor model of \cite{FamaFrench2015a} to measure expected returns.
+We start with revisiting past research but now using a longer and more recent time period and the five-factor model of \cite{FamaFrench2015} as well as the four-factor model of \cite{StambaughYuan2016} to measure expected returns.
+In the tables below we refer to the first model as 5F and the second model as 4F.
 In particular, we test whether buyback (equity issue) announcements are followed by significant positive (negative) long term excess returns, and if so, whether the returns can be explained by proxies for undervaluation as proposed by \cite{PeyerVermaelen2009}.
 
-\subsection{Share buybacks and Equity Issues in Isolation }
-\label{sec:AbnormalBuybacks}
-
-Table~\ref{tbl:priorBuybacks}, Panel~A, shows long-term cumulative excess returns for various holding periods after the announcement using the Ibbotson RATS event study method.
+%\subsection{Share buybacks and Equity Issues in Isolation }
+%\label{sec:AbnormalBuybacks}
+
+Table~\ref{tbl:priorBuybacks}, Panel~A, shows long-term cumulative excess returns for various holding periods after the announcement using the Ibbotson RATS (IRATS) event study method \citep{Ibbotson1975}.
 Each event month~$t$ we run cross-sectional regressions of stock returns against the factors.
@@
 We then accumulate these excess returns over various time horizons (up to 48 months after the event).
-The advantage of this method is that each event gets the same weight and that factor betas are allowed to change in event time, something that may be important as capital structure changes may signal a change in risk~\citep{GrullonMichaely2004}.
-The table compares the excess returns using the \cite{FamaFrench1993} three-factor model and the \cite{FamaFrench2015a} five-factor model.
-The results show that, although using a five-factor model lowers excess returns, the excess returns are statistically significantly positive over all investment horizons and reach \Sexpr{IRATS_table_all_bb["+48","CAR 5F"]}$\%$ after 4 years (t=\Sexpr{IRATS_table_all_bb["+48",5]}).
-So the buyback anomaly does not disappear when we use a five-factor model.
+The advantage of this method is that each event gets the same weight and that factor betas are allowed to change in event time, something that may be important as capital structure changes may signal a change in risk.
+\cite{GrullonMichaely2004} argue that a repurchase signals a decline in growth opportunities.
+As growth opportunities are riskier than assets in place the overall risk of the firm should go down.
+If the market only slowly understands this, one will observe long-term positive excess returns.
+Moreover, \cite{Lietal2009} and \cite{Liuetal2009} use Q-theory to argue that when a firm experiences an increase in its cost of capital, it should pay out cash.
+So, in contrast to \cite{GrullonMichaely2004} they argue that buybacks should be associated with an increase rather than a decrease in risk.
+The IRATS procedure adjusts for event-induced risk changes.
+
+The results in Table~\ref{tbl:priorBuybacks}, Panel~A, show that using a five-factor the excess returns are statistically significantly positive over all investment horizons and reach \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ after 4 years (t=\Sexpr{IRATS_table_all_bb["+48",5]}).
+The results with the 4 factor model are even stronger with excess returns of \Sexpr{round(IRATS_table_all_bb["+48","CAR 3F"],2)}$\%$ (t=\Sexpr{round(IRATS_table_all_bb["+48",2],2)}) after 4 years.
 In all the tables we also calculate cumulative excess returns in the 6 months prior to the buyback.
@@
 
-Table~\ref{tbl:priorIssuers}, Panel~A, shows the results for all equity issues, using the same methodology as in Table~\ref{tbl:priorBuybacks}, Panel~A.
-Our results are largely consistent with \cite{FamaFrench2015b}.
-Using the three-factor model, we find statistically significant long term (after 48 months) negative cumulative excess returns of \Sexpr{IRATS_table_all_iss["+48","CAR 3F"]}$\%$ (t=\Sexpr{IRATS_table_all_iss["+48",2]}).
-However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months.
-This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure, as done by numerous authors.
-Unlike buybacks, equity issues are firm commitments announced and completed at the same point in time.
-Using actual shares issued, the measure used by \cite{FamaFrench2015b}, and equity announcements (our measure) should therefore produce similar results.
-Buyback authorization announcements on the other hand are not firm commitments and are often executed over a long period after the announcement.
-Actual repurchase dates thus do not correspond to announcement dates.
-Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(IRATS_table_all_iss[reported_times[1],1],0)}$\%$ in the 6 months prior to the equity issue.
-However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that, for example, these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.
-
-One critique of the \cite{ibbotson1975} RATS method is that the result may be time-specific.
-Indeed as every event is equally weighted the cumulative average abnormal returns are dominated by periods when there are a large number of events.
-So we also use the Calendar Time method where in each calendar month we form an equally-weighted portfolio of all firms that announced a buyback (or an equity issue) in the previous $t$~months.
-We then run a time series regression of the portfolio returns against the factors.
-The intercept of the regression is the average monthly excess return in the $t$~months after the event.
-The results are shown in Panel~B of Tables \ref{tbl:priorBuybacks} and  \ref{tbl:priorIssuers} and are similar to Panel~A of the same tables.
-Abnormal returns after buybacks are smaller when the five-factor model is used but remain statistically significant over all horizons.
-For example, over the 48 month horizon the average monthly excess return is \Sexpr{CAL_table_all_bb["+48","CAL 5F"]}$\%$ (t=\Sexpr{CAL_table_all_bb["+48",5]}) which corresponds to \Sexpr{48*CAL_table_all_bb["+48","CAL 5F"]}$\%$ over 48 months.
-Note also that excess returns fall when the investment horizon increases.
-The largest monthly excess return (\Sexpr{CAL_table_all_bb["+1","CAL 5F"]}$\%$) is earned by the portfolio that holds buyback stocks for one month  (not reported in Table \ref{tbl:priorBuybacks})  and the smallest excess return (\Sexpr{CAL_table_all_bb["+48","CAL 5F"]}$\%$) is earned by the portfolio that picks buybacks announced during the previous 48 months.
-This clearly shows that forming portfolios after buybacks are completed, as is done by measuring net issues in \cite{FamaFrench2015b}, is introducing a downward bias as many repurchase programs are completed several months (sometimes years) after the buyback announcement.
-Waiting until the buyback is completed means missing the largest excess returns earned shortly after the buyback authorization.
-Finally, there are no statistically significant excess returns after equity issues, regardless whether we use the three or five-factor model.
-
-So far all our events are equally weighted.
-\cite{MitchellStafford2000} argue that events should be value weighted to test whether they represent an economically important anomaly.
-However, as we know from past research, for theoretical as well as empirical reasons, one would expect that managers in small firms are better able and willing to take advantage of mispricing than in large firms.
-So value weighting would simply bias the results toward zero.
-And indeed, when we value-weight the events (results available upon request) long-term excess returns become statistically insignificantly different from zero when using the total sample of events.
-So the buyback anomaly is not economically important and does not challenge the basic premise that ``the market'' represented by a value-weighted index is priced correctly.
-
-Next we test whether the ``Undervaluation Index'' (U-index) developed by \cite{PeyerVermaelen2009} using buyback announcements from 1991 to 2002 is a robust indicator to separate companies that are buying back stock because they are undervalued from companies that repurchase shares for other reasons.
+In order to test the market timing hypothesis in the buyback sample,  we also test whether the ``Undervaluation Index'' (U-index) developed by \cite{PeyerVermaelen2009} remains a robust indicator to separate companies that are buying back stock because they are undervalued from companies that repurchase shares for other reasons.
 We calculate the U-index as follows.
-Companies get a size score from 1 (large firms) to 5 (small firms) depending on the quantile of their market value of equity in the month prior to the buyback announcement.
-Then, we calculate the 11-months pre-announcement absolute returns of months -12 to -1 before announcement for all events and assign a score of 5 to the low returns firms and 1 to the high returns ones.
-Finally, companies get a book value to market value (BE/ME) score depending on the quantile of their BE/ME value of equity in the year prior to the buyback announcement, with a score of 1 to small BE/ME firms and 5 to large ones.
-Like \cite{PeyerVermaelen2009} we use all CRSP companies to define the quantile thresholds each month.
+Companies get a size score from 1 (large firms) to 5 (small firms) depending on the quintile of their market value of equity in the month prior to the buyback announcement.
+Then, we calculate the 11-months  absolute returns of months -12 to -1 before announcement for all events and assign a score of 5 to the low returns firms and 1 to the high returns ones.
+Finally, companies get a book value to market value (BE/ME) score depending on the quintile of their BE/ME value of equity in the year prior to the buyback announcement, with a score of 1 to small BE/ME firms and 5 to large ones.
+Like \cite{PeyerVermaelen2009} we use all CRSP companies to define the quintile thresholds each month.
 
@@
 
-Table~\ref{tbl:priorBuybacks}, Panel~A, shows the three-factor as well as the five-factor IRATS for high U-index and low U-index firms.
+%The largest monthly excess return (\Sexpr{CAL_table_all_bb["+1","CAL 5F"]}$\%$) is earned by the portfolio that holds buyback stocks for one month  (not reported in Table \ref{tbl:priorBuybacks})  and the smallest excess return (\Sexpr{CAL_table_all_bb["+48","CAL 5F"]}$\%$) is earned by the portfolio that picks buybacks announced during the previous 48 months.
+This clearly shows that forming portfolios after buybacks are completed, as is done by measuring net issues in \cite{FamaFrench2016}, is introducing a downward bias as many repurchase programs are completed several months (sometimes years) after the buyback announcement.
+Waiting until the buyback is completed means missing the largest excess returns earned shortly after the buyback authorization.
+Finally, there are no statistically significant excess returns after equity issues, regardless whether we use the three or five-factor model.
+
+%So far all our events are equally weighted.
+\cite{MitchellStafford2000} argue that events should be value weighted to test whether they represent an economically important anomaly.
+However, as pointed out by Loughran and Ritter (2000), small firms are more likely to be mispriced as they are less followed by analysts.
+t Hence managers of small firms are better able  to take advantage of mispricing than managers of  large firms.
+So value weighting the events would simply bias the results toward zero.
+And indeed, when we value-weight the events (see Table \ref{tbl:valuetable} Panel~A) long-term excess returns become statistically insignificantly different from zero when using the total sample of events.
+So the buyback anomaly is not economically important and does not challenge the basic premise that ``the market'' represented by a value-weighted index is priced correctly.
+Note, however, if we eliminate the firms with are in the top $25^{th}$ market capitalization percentile (see Table \ref{tbl:valuetable}, Panel~B) the results become again significant.
+These firms had market capitalization less than \$\Sexpr{round(max(BUYBACK_DATA$DATASET$CRSP$Market.Cap[BUYBACK_DATA$DATASET$SDC$Event.Date >= "2015-01-01" & BUYBACK_DATA$DATASET$CRSP$Market.Cap_score < 0.75]))} million in 2015.
+The fact that the buyback anomaly is a small cap anomaly makes it more likely that excess returns are evidence that managers (at least in these firms) time the market based on their information advantage relative to investors.
+
+Table~\ref{tbl:priorBuybacks}, Panel A, shows the five-factor as well as the four-factor IRATS for high U-index and low U-index firms.
+The interesting conclusion is that for all horizons starting 24 months after the buyback announcement, regardless of the factor model used, high U-index firms beat low U-index firms.
+For comparable horizons and u-index categories, the 4 factor model always produces larger excess returns.
+Consistent with \cite{PeyerVermaelen2009} the low U-index buyback stocks earn significant positive excess returns as well.
+It is difficult to find a portfolio of buyback stocks that under-performs in the long run.
+
+One critique of the IRATS method is that the result may be time-specific.
+Indeed, as every event is equally weighted the cumulative average abnormal returns are dominated by periods when there are a large number of events.
+However, as \cite{LoughranRitter2000} point out, the fact that many firms decide to announce buybacks in a particular month may indicate that more firms believe markets are inefficient in that month.
+Giving equal weight to a calendar month with many buybacks and a calendar month with few buybacks may systematically bias excess returns downwards.
+So we also use the Calendar Time method where in each calendar month we form an equally-weighted portfolio of all firms that announced a buyback (or an equity issue) in the previous t months.
+We then run a time series regression of the portfolio returns against the factors.
+The intercept of the regression is the average monthly excess return in the t months after the event.
+The results are shown in Panel~B of Table \ref{tbl:priorBuybacks}.
+
+The calendar time results confirm the IRATS results.
+Regardless of the factor model and the investment horizon (24 months and beyond) long-term excess returns are positive a statistically significant at the 1$\%$ level.
+As in Panel A, excess returns are larger when the Stambaugh-Yuan four factor model is used as a benchmark.
+Specifically, during the 48-month period after the buyback announcement firms earn excess returns of \Sexpr{round(CAL_table_all_bb["+48","CAL 3F"],2)}$\%$ (t=\Sexpr{round(CAL_table_all_bb["+48",2],2)}) and \Sexpr{round(CAL_table_all_bb_undervaluation["+48","U:CAL3F"],2)}$\%$ (t=\Sexpr{round(CAL_table_all_bb_undervaluation["+48",2],2)}) in the case of high U-index firms.
+So we can conclude that the buyback anomaly and the relevance of the U-index survive the \cite{FamaFrench2015} and \cite{StambaughYuan2016} models.
+
+So far all our events are equally weighted.
+\cite{MitchellStafford2000} argue that events should be value weighted to test whether they represent an economically important anomaly.
+However, as pointed out by \cite{LoughranRitter2000}, small firms are more likely to be mispriced as they are less followed by analysts.
+Hence managers of small firms are better able to take advantage of mispricing than managers of large firms, which is the reason why firm size is one of the components of the U-index.
+So value weighting the events would simply bias the results toward zero.
+And indeed, when we value-weight the events (see Table \ref{tbl:valuetable} Panel A) long-term excess returns become statistically insignificantly different from zero when using the total sample of events.
+So the buyback anomaly is not economically important and does not challenge the basic premise that “the market” represented by a value-weighted index is priced correctly.
+Note, however, if we eliminate the firms with are in the top $25^{th}$ market capitalization percentile (see Table \ref{tbl:valuetable}, Panel~B) the results become again significant, especially for the high U-index firms.
+These firms had a market capitalization less than \$2,971 million in 2015.
+The fact that the buyback anomaly is a small cap anomaly makes it more likely that excess returns are evidence that managers (at least in these firms) time the market based on their information advantage relative to investors.
+It may also explain why the anomaly persists as the capacity of small cap funds (and therefore management fees) is smaller than the capacity of large cap funds.
+
+Table~\ref{tbl:priorIssuers}, shows the results for all equity issues.
+Note that because there is no undervaluation index for equity issues we use the Mispricing Measure (MM) of \cite{Stambaugh2015} to measure overvaluation.
+Specifically, we define all issuers in the top 20$^{th}$ MM percentile as High MM firms and issuers in the bottom 20$^{th}$ MM percentile as low MM firms.
+Note that high values of MM correspond to more overvaluation.
+Table~\ref{tbl:priorIssuers} panel A shows the IRATS results while panel B shows the Calendar Time results.
+For the total sample, the Fama-French five factor model fully explains the anomaly, regardless of the method to measure abnormal returns.
+However, using IRATS, the 4 factor model produces significant positive excess returns of \Sexpr{round(IRATS_table_all_iss["+48","CAR 3F"],2)}$\%$ after 4 years (t=\Sexpr{round(IRATS_table_all_iss["+48",2],2)}).
+With the calendar time method, the excess returns become less significant (t=\Sexpr{round(CAL_table_all_iss["+48",2],2)}) but have the same magnitude (\Sexpr{round(CAL_table_all_iss["+48","CAL 3F"],2)}$\%$ per month or \Sexpr{48*round(CAL_table_all_iss["+48","CAL 3F"],2)}$\%$  after 48 months).
+When splitting up the sample according to MM, the Fama-French five factor model shows no significant long-term excess returns regardless of the investment horizon and the method to measure excess returns.
+A similar result is found when we use the \cite{Stambaugh2015} four factor model and the Calendar Time method.
+
+Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(IRATS_table_all_iss["-6","CAR 3F"],2)}$\%$ in the 6 months prior to the equity issue.
+However, the lack of post announcement {\it negative} excess returns shows that this was not reflecting ''irrational exuberance'' but rather that, for example, these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.
+In summary, we find no robust evidence that firms issue stock because they are overvalued, irrespective of whether they are High or Low MM firms.
+
+Overall our results show that when searching for anomalies, buybacks and equity issues should not be pooled in a ''net issue'' measure, a common practice in the asset pricing literature.
+Both events may be motivated by different reasons.
+
+%Using IRATS, the 4 factor model produces significant positive excess returns of 12.66$\%$ after 4 years (t=5.24).
+With the calendar time method, the excess returns become less significant (t=1.81) but have the same magnitude (0.27$\%$ per month or 12.86$\%$ after 48 months).
+Clearly this is inconsistent with the idea that firms issue stock when they are overvalued.
+Our results are largely consistent with \cite{FamaFrench2016}.
+Using the three-factor model, we find statistically significant long term (after 48 months) negative cumulative excess returns of -7.40% (t=-3.36).
+However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months.
+Our results show that This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a “net issue” measure.
+Both events are clearly motivated by different reasons.
+As pointed out above, unlike buybacks, equity issues are firm commitments announced and completed at the same point in time, the buyer of the shares knows that the company is the issuer which makes trading against ”uninformed” investors more complicated and more controversial for a firm who wants to keep good relations with its long term investors.
+Note also that equity issues are typically preceded by large positive excess returns of around 37% in the 6 months prior to the equity issue.
+However, the lack of post announcement negative excess returns shows that this was not reflecting “irrational exuberance” but rather that, for example, these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.
+
+%shows a split according to volatility.
+We will return to this result next when we discuss the effect of volatility on returns in section 4.} using the same methodology as in Table~\ref{tbl:priorBuybacks}, Panel~A.
+Our results are largely consistent with \cite{FamaFrench2016}.
+Using the three-factor model, we find statistically significant long term (after 48 months) negative cumulative excess returns of \Sexpr{IRATS_table_all_iss["+48","CAR 3F"]}$\%$ (t=\Sexpr{IRATS_table_all_iss["+48",2]}).
+However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months.
+This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure.
+As pointed out above, unlike buybacks, equity issues are firm commitments announced and completed at the same point in time, the buyer of the shares knows that the company is the issuer which makes trading against ''uninformed'' investors more complicated and more controversial for a firm who wants to keep good relations with its long term investors.
+Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{floor(IRATS_table_all_iss[reported_times[1],4])}$\%$ in the 6 months prior to the equity issue.
+However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that, for example, these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.
+
+%Table~\ref{tbl:priorBuybacks}, Panel~A, shows the five-factor as well as the four-factor IRATS for high U-index and low U-index firms.
 The interesting conclusion is that using the five-factor model improves the predictive power of the U-index: high U-index firms earn 4 year excess returns of \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR5F"]}$\%$ (t=\Sexpr{IRATS_table_all_bb_undervaluation["+48",8]}) while low U-index firms only earn \Sexpr{IRATS_table_all_bb_undervaluation["+48","O:CAR5F"]}$\%$ (t=\Sexpr{IRATS_table_all_bb_undervaluation["+48",11]}), hence \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR5F"] - IRATS_table_all_bb_undervaluation["+48","O:CAR5F"]}$\%$ less than the high U-index ones.
-Starting from 12 months after the announcement, high U-index firms always beat low U-index firms.
+Starting from 24 months after the announcement, high U-index firms always beat low U-index firms.
 When we use the three-factor model, we find similar conclusions, but the results are weaker.
@@
 
-Table~\ref{tbl:priorBuybacks}, Panel~B, shows that this conclusion holds when we use the Calendar Time method.
-Regardless of the horizon, high U-index stocks almost always beat low U-index stocks.
+%Table~\ref{tbl:priorBuybacks}, Panel~B, shows that this conclusion holds when we use the Calendar Time method.
+High U-index stocks almost always beat low U-index stocks.
 As in the case of IRATS, the five-factor model improves the selectivity of the Undervaluation Index: low U-index now earn marginally significant excess returns after 48 months.
@@
 Results are shown for the total sample of buybacks and equity issues, as well as for high and low U-index buyback samples.
-
-\subsection{Buybacks followed by Equity Issues}
-\label{sec:Eventexit}
-
-The results so far show that firms that repurchase shares are good at market timing, in particular the small beaten up value stocks.
-On the other hand the average equity issuer does not seem to be driven by market timing in general.
-However, firms that are good at market timing when buying back undervalued stock are perhaps also good at recognizing when their shares are overvalued.
-Note that successful market timing requires two managerial characteristics: ability to time the market as well as willingness, i.e., accepting the idea that using superior information to benefit long term shareholders at the expense of other shareholders is the ``right'' thing to do.
 
@@
 
-During our sample period (\Sexpr{firstyear}-\Sexpr{lastyear}) \Sexpr{length(unique(intersect(cusip_bb,cusip_iss)))} companies in our data set both announced buybacks and issued equity, but in only \Sexpr{length(SEO_exit_days)}  cases a company announced a subsequent equity issue within 4 years after the buyback announcement.
-Of the \Sexpr{length(SEO_exit_days)} such events, \Sexpr{sum(abs(SEO_exit_days) < 1*365)} SEOs happen within 1 year from the buyback announcement, \Sexpr{sum(abs(SEO_exit_days) < 2*365)} happen within 2 years and \Sexpr{sum(abs(SEO_exit_days) < 3*365)} happen within 3 years.
-Note that this grouping of the events is done with hindsight: it is not possible to know at the time of the buyback announcement whether there will be a subsequent SEO or not.
-We are simply asking the question whether those firms that announced a buyback when they appeared undervalued issued equity when they were overvalued.
-Figure~\ref{fig:BBISSevents} shows the percentage of repurchasing firms that announced an equity issue within 48 months.
-The average percentage is \Sexpr{round(mean(BB_with_ISS_later_total),1)}$\%$ and there are only \Sexpr{sum(BB_with_ISS_later_total > 10)} years (1989 and 1990) where the percentage is larger than $10\%$.
-
-Table~\ref{tbl:BBISSexit}  shows that repurchasing firms that issued stock within 48 months after the buyback are remarkable timers.
-Long-term excess returns after 4 years are \Sexpr{Exit_on_SEO_Abn_table["+48",4]}$\%$ (t=\Sexpr{Exit_on_SEO_Abn_table["+48",5]}), about four times as large as for the overwhelming majority of firms that do not issue stock subsequently.
-These results are graphically displayed in Figure~\ref{fig:BBISSexit} (Panel~A).
-Repurchases by firms that do not issue equity in the next 48 months are followed by long term excess returns of only \Sexpr{Exit_on_SEO_Abn_table["+48",1]}$\%$.
-One interpretation is that these firms believe they are undervalued but as long as they remain undervalued they do not think it is appropriate to issue stock.
-
-The Calendar Method results in Panel B of Table~\ref{tbl:BBISSexit} show a relatively large drop of the excess returns over time (e.g., from \Sexpr{Exit_on_SEO_Abn_table_cal["+12",4]}$\%$ after 12 months to \Sexpr{Exit_on_SEO_Abn_table_cal["+48",4]}$\%$ after 48 months) indicating potential benefits of exiting a buyback position when there is a subsequent issue.
-Figure  \ref{fig:BBISSexit} (Panel~B) shows the benefits of exiting early.
-The figure shows a strategy with hindsight where, starting in \Sexpr{firstyear}, we invest in an equally weighted portfolio of only firms that announced a buyback and subsequently issued equity within the 48 months after the buyback announcement.
-The dashed line shows the cumulative excess return if we sold the stock whenever the firm issued shares within 48 months (the ``exit strategy'').
-The solid line shows the cumulative excess returns if we only sold 48 months after the buyback announcement (the ``no exit strategy'').
-The investor who had followed the exit strategy would have earned (after 30 years) a cumulative excess return of \Sexpr{round(tail(100*cumsum(BB_ISS_Exit_Hedged),1),1)}$\%$, compared to the \Sexpr{round(tail(100*cumsum(BB_ISS_NoExit_Hedged),1),1)}$\%$ of a buy and hold for 48 months strategy.
-Note, however, that because very few firms that buy back stock issue equity within 48 months,  a strategy ``without hindsight'' where one bought all companies after a buyback and sold only those after a subsequent equity issue would not substantially increase excess returns.
-
-%Table~\ref{tbl:BBISSexitAfter} shows the long run excess returns after the announcement of an equity issue for two samples.
-The first sample (After a Buyback) shows the excess returns for issues for which in the previous 48 months the firm announced a buyback.
-The second sample (No Prior Buyback) shows the excess returns for all other issue announcements.
-The fact that excess returns are not significantly different from zero for the post-buyback issuers agrees with the intuition of Figure~\ref{fig:BBISSexit}: exiting when there is a subsequent equity issue is a better strategy for the long-term buyback investor.
-
 \section{How robust is the buyback  anomaly?}
@@
 The results so far are based on a sample of all buyback and equity announcements over a thirty-year period.
-As the equity issue anomaly does not survive the \cite{FamaFrench2015a} five-factor model, the remainder of the paper focuses on better understanding the buyback anomaly and uses the five-factor model as a benchmark.\footnote{All analyses below are also done for equity announcements.
-However, in agreement with the results in Section \ref{sec:AbnormalBuybacks}, we find no consistent/robust results for issuers.
-All issuers results are available upon request.}  The purpose of this section is to test the robustness of this anomaly: has it become less important over time because markets have become more efficient?
+As the equity issue anomaly does not survive the \cite{FamaFrench2015} five-factor or the \cite{StambaughYuan2016} four-factor model, this section focuses on better understanding the buyback anomaly and uses the five-factor model as a benchmark.\footnote{All analyses below are also done for equity announcements.
+However, in agreement with the results in Section \ref{sec:PastFindingsBB}, we find no consistent/robust results for issuers.
+All issuers results are available upon request.}  We use the five factor model as Table \ref{tbl:priorBuybacks} shows that it better explains returns than the four-factor model.
+In other words, it is a more difficult benchmark to beat.\footnote{We also repeated the whole analysis below with the \cite{StambaughYuan2016} model but our main conclusions are essentially unchanged.
+Results are available upon request.} The purpose of this section is to test the robustness of this anomaly: has it become less important over time because markets have become more efficient?
 How sensitive is it to the length of the investment period?
@@
 Table~\ref{tbl:PastFindingsTimeBB} shows excess returns, using both the IRATS and Calendar Time method for different time periods.
-We consider time periods, which overlap to some extent with past research [\cite{IkenberryLakonishokVermaelen1995}; \cite{PeyerVermaelen2009}; \cite{ManconiPeyerVermaelen2015}; and \cite{FuHuang2015}]: 1985-1990; 1991-2000; 2001-2015 and 2008-2015.
+We consider time periods, which overlap to some extent with past research [\cite{IkenberryLakonishokVermaelen1995}; \cite{PeyerVermaelen2009}; \cite{ManconiPeyerVermaelen2015}; and \cite{FuHuang2016}]: 1985-1990; 1991-2000; 2001-2015 and 2008-2015.
 The last period was chosen to incorporate the financial crisis and to test whether indeed markets have become more efficient in recent years, or whether managers have for example been discouraged from market timing by the obvious mistakes that were made by buying back shares before a major financial crisis.
@@
 This result appears to also be inconsistent with \cite{PeyerVermaelen2009}.
-However, if one includes the financial sector firms or considers the three-factor model, as \cite{PeyerVermaelen2009} do, the calendar method abnormal returns do become significant.\footnote{Details available upon request.}
-
-Table~\ref{tbl:PastFindingsTimeUnderBB} re-examines whether the U-index of \cite{PeyerVermaelen2009} predicts the five factor excess returns for different time periods.
+However, if one includes the financial sector firms or considers the three-factor model, as \cite{PeyerVermaelen2009} do, the calendar method abnormal returns do become significant.\footnote{Details available upon request.} Note that the period 1991-2000 was a period characterized by a large number of buybacks near the end of the century (Figure 1).
+During the last two years there were several months with an exceptionally large number of buybacks.
+High buyback concentration will produce significant differences between IRATS and Calendar Time results.
+
+For comparison, we also tested the stability of the findings on equity issues in Table \ref{tbl:priorIssuers}.
+The results (available on request), using IRATS, are time- and model-specific.
+When we use the 4 factor model, long-term (48 months) excess returns are significantly negative during the 1985-1990 period, but significantly positive during the 1991-2000 and 2001-2015 periods.
+With the 5 factor model only the 2001-2015 period shows significant positive long-term excess returns.
+However, for all horizons and both factor models, all long-term excess returns become statistically insignificantly different from zero when we use the Calendar Time Method.
+
+%Table~\ref{tbl:PastFindingsTimeUnderBB} re-examines whether the U-index of \cite{PeyerVermaelen2009} predicts the five factor excess returns for different time periods.
 The first two columns show the IRATS results and the last two columns show the Calendar Time results.
@@
 An investor who wants to exploit the anomaly, however, may want to hedge market (and other) risk and would need to estimate betas using past data.
-If the buyback signals a change in risk \citep{GrullonMichaely2004} it is not obvious that such a hedged strategy would work, which may make a buyback strategy impractical for some funds.
+If the buyback signals a change in risk \citep{GrullonMichaely2004,Lietal2009,Liuetal2009} it is not obvious that such a hedged strategy would work, which may make a buyback strategy impractical for investors who want to arbitrage the anomaly away.
 
@@
 
-Despite using pre-portfolio formation data to estimate the betas, unlike both the IRATs and Calendar Time methods that use hindsight to estimate risk, the hedged portfolio indeed has very low betas with the five factors.
+Despite using pre-portfolio formation data to estimate the betas, unlike both the IRATS and Calendar Time methods that use hindsight to estimate risk, the hedged portfolio indeed has very low betas with the five factors.
 For example for the $N =12$ months holding period, the betas for the five factors Market, SMB, HML, RMW, and CMA are respectively \Sexpr{round(expost_betas[2,1],3)}, \Sexpr{round(expost_betas[3,1],3)}, \Sexpr{round(expost_betas[4,1],3)}, \Sexpr{round(expost_betas[5,1],3)} and \Sexpr{round(expost_betas[6,1],3)}.
@@
 
-Having established the robustness of the buyback anomaly also after using the 5-factor Fama-French model, we turn to our main question: are the buyback and volatility anomalies related?
-One of the most puzzling findings in the large literature on volatility and stock returns\footnote{For the most recent overview of the literature and potential hypotheses, see \cite{LiRodneyGarcia2016}.} is the fact that total volatility and idiosyncratic volatility (measured by residual variance which is, as noted above, highly correlated with total volatility, e.g., \Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study)  are negatively correlated with future abnormal returns, when expected returns are calculated using the 3-factor \cite{FamaFrench1993} model  [see e.g., \cite{Ang2006} (Table VII)].
-Fama and French (2015b) find that this volatility anomaly also survives after using the \cite{FamaFrench2015a} 5-factor model, at least for small firms.
+Having established the robustness of the buyback anomaly we turn to the second question of this paper: are the buyback anomaly and the volatility anomaly related?
+One of the most puzzling findings in the large literature on volatility and stock returns\footnote{For the most recent overview of the literature and potential hypotheses, see \cite{LiRodneyGarcia2016}.} is the fact that total volatility and idiosyncratic volatility (measured by residual variance which is highly correlated with total volatility, e.g., \Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study)  are negatively correlated with future abnormal returns, when expected returns are calculated using the 3-factor \cite{FamaFrench1993} model  [see e.g., \cite{Ang2006} (Table VII)].
+\cite{FamaFrench2016} find that this volatility anomaly also survives after using the \cite{FamaFrench2015} 5-factor model, at least for small firms.
 Perhaps the buyback and the volatility anomaly are related: are the buyback firms with the largest excess returns also firms with the smallest volatility?
@@
 that excess returns are related to the fact that managers are on average successful in taking advantage of an undervalued stock price?
-In that case we expect a negative relation using the \cite{Stambaugh2015} arbitrage hypothesis and the \cite{IkenberryVermaelen1996} option hypothesis.
-Moreover, what about $1-R^2$, a measure of ``standardized'' idiosyncratic risk that unlike residual variance is little correlated with total volatility and measures more precisely the fraction of total volatility explained by company-specific news?\footnote{As noted above, in our sample the correlation between $1-R^2$ and residual variance (the typical measure of idiosyncratic risk in the literature) is only \Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$, compared to that between residual variance (the measure of idiosyncratic risk used in the literature) and total volatility which is \Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$.
-See also \cite{LiRajgopaletal2014} for a related discussion on this issue.} We start with the latter first, then consider the former, and finally we combine the two in the next section.
-
-\subsection{Standardized Idiosyncratic Risk and excess returns}
-\label{sec:idiorisk}
-
-The main ``theory'' behind the buyback anomaly is that firms may have superior {\it company-specific} information.
-Such situations are more likely in industries or companies where the volatility is largely driven by company-specific volatility.
-So if buybacks are driven by market timing this superior information hypothesis predicts that there should be a positive relation between excess returns and the percentage of the volatility explained by company-specific factors, i.e.
-our measure of idiosyncratic volatility ($1-R^2$), however not to be confused with residual variance.
-
-To test this hypothesis, for each event we measure the five-factor regression $R^2$ using the 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month,  leads to the same conclusions - results available upon request.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$.
-We also define the idiosyncratic score of a firm to be the percentile of its $1-R^2$ across all CRSP firms that month.
-Table~\ref{tbl:industriesR2Vol}, columns (1) and (2) show the percentage of high and low idiosyncratic risk events across all industries for which we have at least 100 buyback events in our sample.
-The healthcare industry has the largest percentage of firms classified as ``high idiosyncratic'', while cyclical industries such as steel, construction and chemicals contain a large number of ``low idiosyncratic'' firms.
-
-Table~\ref{tbl:IdiosyncraticunderBB} shows the IRATS and Calendar Time abnormal returns for high and low idiosyncratic buyback events-companies.
-Focusing on IRATS, high idiosyncratic buyback stocks earn \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$  after 48 months, more than the excess returns of the low idiosyncratic announcements.
-The results using the Calendar Time method confirm these findings.
-Table~\ref{tbl:IdiosyncraticunderBB} also tests whether adjusting for idiosyncratic risk improves the predictive power of the U-index.
-Regardless of the time horizon and the event study method, the U-index works only for idiosyncratic companies.
-After 48 months, based on the IRATS methods, high U-index high idiosyncratic companies earn \Sexpr{R2_IRATStable_underBB["+48","High Idiosync.: U CAR"]}$\%$ (t=\Sexpr{R2_IRATStable_underBB["+48",8]}).
-Low idiosyncratic high U-index firms have only an insignificant excess return of \Sexpr{R2_IRATStable_underBB["+48",1]}$\%$ (t=\Sexpr{R2_IRATStable_underBB["+48",2]}), while for low idiosyncratic firms the low U-index IRATS excess returns are marginally significant (\Sexpr{R2_IRATStable_underBB["+48",4]}$\%$, t=\Sexpr{R2_IRATStable_underBB["+48",5]}).
-Note however that we only have few events in low idiosyncratic, high U-index (\Sexpr{R2_IRATStable_underBB["Observations",1]} events) and high idiosyncratic, low U-index (\Sexpr{R2_IRATStable_underBB["Observations",10]} events) categories.
-The Calendar Time results provide the same picture: only for the high idiosyncratic, high U-index firms we obtain significant (t=\Sexpr{R2_IRATStable_underBB_cal["+48",8]}) monthly excess returns of \Sexpr{R2_IRATStable_underBB_cal["+48",7]}$\%$.
-The high idiosyncratic and low U-index firms have  non-significant (t=\Sexpr{R2_IRATStable_underBB_cal["+48",11]}) monthly excess returns of \Sexpr{R2_IRATStable_underBB_cal["+48",10]}$\%$.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
-Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
-High idiosyncratic companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_Idiosyncr_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy.
-These excess returns are higher than the \Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_Idiosyncr_BB_Hedged48m),1),1)}$\%$) of the corresponding low idiosyncratic sample.}
-
-Figure \ref{fig:pastallidio} summarizes our results.
-It shows the CAR based on IRATS (Panel~A for the high U-index firms, B for the low U-index firms, and C for all firms).
-In agreement with Table~\ref{tbl:IdiosyncraticunderBB}, the striking result (Panel~A) is that the U-index is not a good predictor of excess returns for stocks largely driven by market factors (low idiosyncratic firms).
-This is strong evidence that excess returns after buybacks are driven by superior company-specific information of the management.
-
-%The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \citep{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns.
-However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks.
-Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing.
-Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks.
-Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).
-So our results are also consistent with the \cite{Stambaugh2015} interpretation.
-
-\subsection{Volatility and excess returns}
-\label{sec:volbuybacks}
-
+In this paper we will consider a number of theories that predict relations between volatility and returns: first, the costly arbitrage hypothesis of  \cite{Stambaugh2015} and second, two hypotheses predicted by market timing: the \cite{IkenberryVermaelen1996} options hypothesis and the information advantage hypothesis.
+
+\subsection{Costly arbitrage and volatility }
+
+\cite{Stambaugh2015} argue that anomalies are more likely to survive for stocks with higher idiosyncratic volatility as arbitraging the anomaly becomes costlier.
+Their theory predicts (1) a positive relation between idiosyncratic volatility and stock returns for undervaluation anomalies (such as the buyback anomaly) and (2) a negative relation between idiosyncratic volatility and stock returns for overvaluation anomalies (such as the equity issue anomaly).
+Their hypothesis also predicts that (3) overvaluation anomalies will persist longer than undervaluation anomalies as selling short is difficult and costly.
+Note that the results in Tables \ref{tbl:priorBuybacks} and \ref{tbl:priorIssuers} are inconsistent with the last hypothesis: the buyback anomaly persists but the equity anomaly does not.
+
+\cite{Stambaugh2015} argue that idiosyncratic volatility, and not total volatility, should be positively related to future returns for undervalued stocks.
+However, the empirical fact is that their estimate of idiosyncratic volatility (residual variance) is highly correlated (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$) with total volatility.
+Their argument is that idiosyncratic volatility represents risk that deters arbitrage and therefore creates mispricing.
+Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between residual variance and future returns for undervalued stocks.
+But considering the very high correlation between residual variance and total variance, their prediction can also be tested by using total volatility.
+
+%But considering the very high correlation between residual variance and total variance, their hypothesis would also predict a positive correlation between total volatility and future returns for undervalued stocks.
+Hence, perhaps total volatility is a better prediction of excess returns than (standardized) idiosyncratic volatility (defined as $1-R^2$) or the U-index of \cite{PeyerVermaelen2009}.
+Or perhaps volatility can be an additional, next to the U-index and standardized idiosyncratic volatility, indicator of the likelihood that the buyback is driven by undervaluation.\footnote{In contrast to the option hypothesis, \cite{Stambaugh2015} also predict a negative relation between volatility and returns for overvalued stocks.
+However, as with the Fama-French 5 factor model equity issuers don't appear to be overvalued, we can't test this ''second'' leg of their hypothesis.}
+
+For each event we measure the pre-announce returns volatility with the standard deviation of their daily stock returns over the 6 months prior to the buyback announcement.
+We define two types of events: ``low volatility'' and ``high volatility'' events, depending on whether volatility was in the top or bottom \Sexpr{round(100*quantile_VOL,2)}$\%$ of the volatilities of all CRSP companies before the event.
+In total we have \Sexpr{sum(High_VOL_eventsBB)} ``high volatility'' buybacks-events and \Sexpr{sum(Low_VOL_eventsBB)} ``low volatility'' ones.
+In the smaller equity issue sample 804 events are classified as high and low volatility.
+
+Starting with equity issues, Table~\ref{tbl:VOLunderBB} shows that, using the IRATS methodology, there is a positive relation between volatility and returns: the issuers with the lowest volatility tend be followed by significant negative returns and this result is independent of the factor model used.
+Issuers with high volatility are followed by significantly positive long-term excess returns, again independent of the factor model used.
+This is the opposite of the prediction of the costly arbitrage hypothesis.
+However, this result is not robust: when we move to the calendar time method the relation between volatility and returns disappears.
+
+Moving on to buybacks, Table~\ref{tbl:VOLunderBB} also shows a strong positive relation between volatility and excess returns independent of the factor model used.
+For example, using IRATS and the five factor model the cumulative average abnormal return is only \Sexpr{round(IRATS_table_lowvol_BB["+48","CAR 5F"],2)}$\%$  (t=\Sexpr{round(IRATS_table_lowvol_BB["+48",5],2)}) after 48 months in the low volatility sample and \Sexpr{round(IRATS_table_highvol_BB["+48","CAR 5F"],2)}$\%$ (t=\Sexpr{round(IRATS_table_highvol_BB["+48",5],2)}) in the high volatility sample.
+This time the calendar time method confirms the IRATS result: insignificant monthly excess returns of \Sexpr{round(CAL_table_lowvol_BB["+48","CAL 5F"],2)}$\%$  (t=\Sexpr{round(CAL_table_lowvol_BB["+48",5],2)}) in the low volatility sample versus significant positive monthly excess returns of \Sexpr{round(CAL_table_highvol_BB["+48","CAL 5F"],2)}$\%$ (t=\Sexpr{round(CAL_table_highvol_BB["+48",5],2)}) in the high volatility sample.
+
+\subsection{Market timing and volatility}
+\label{sec:vol}
+
+In this paper we argue that the market timing hypothesis, the fundamental hypothesis behind the buyback anomaly, also predicts a positive relation between excess returns and volatility.
 The announcement of a buyback program is not a firm commitment, but an option to buy back stock.
@@
 For example, the market may underestimate the maturity of the option if they do not realize that firms who are announcing a buyback authorization for say 2 years are likely to renew the authorization many times in the future.
-Moreover, although \cite{Stambaugh2015} argue that idiosyncratic volatility, and not total volatility, should be positively related to future returns for undervalued stocks, the empirical fact is that their estimate of idiosyncratic volatility (residual variance) is highly correlated (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$) with total volatility.
-Their argument is that idiosyncratic volatility represents risk that deters arbitrage and therefore creates mispricing.
-Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between residual variance and future returns for undervalued stocks.
-But considering the very high correlation between residual variance and total variance, their hypothesis would also predict a positive correlation between total volatility and future returns for undervalued stocks.
-Hence, perhaps total volatility is a better prediction of excess returns than (standardized) idiosyncratic volatility (defined as $1-R^2$) or the U-index of \cite{PeyerVermaelen2009}.
-Or perhaps volatility can be an additional, next to the U-index and idiosyncratic volatility, indicator of the likelihood that the buyback is driven by undervaluation.
-
-For each event we measure their pre-announce returns volatility with the standard deviation of their daily stock returns over the 6 months prior to the buyback announcement.
-We define two types of events: ``low volatility'' and ``high volatility'' events, depending on whether volatility was in the top or bottom \Sexpr{round(100*quantile_VOL,2)}$\%$ of the volatilities of all CRSP companies, as we did for $R^2$ above:
-each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' daily returns volatilities.
-We also define the volatility score of a firm to be the percentile of its volatility across all CRSP firms that month.
-For simplicity we focus again on the two extreme quantiles only.
-In total we have \Sexpr{sum(High_VOL_eventsBB)} ``high volatility'' buybacks-events and \Sexpr{sum(Low_VOL_eventsBB)} ``low volatility'' ones.
-Table~\ref{tbl:industriesR2Vol}, columns (3) and (4)  show the percentage of high and low volatility events across all industries for which we have at least 100 buyback events in our sample.
-Software and chips tend to be the most volatile sectors and they are also two of the three sectors where buybacks are more frequent.
-
-Table~\ref{tbl:VOLunderBB} shows the IRATS and Calendar Time abnormal returns for high and low volatility buybacks events-companies.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
+Hence the option hypothesis predicts that excess returns are positively correlated with volatility, which is consistent with the results in Table~\ref{tbl:VOLunderBB}.
+
+%Moreover, is our measure of standardized idiosyncratic volatility, $(1-R^2)$, positively correlated with excess returns, as predicted by the information advantage hypothesis?
+Note that this is a measure of idiosyncratic risk that, unlike residual variance is little correlated with total volatility (\Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study) and measures more precisely the fraction of total volatility explained by company-specific news.
+We start with the latter first, then consider the former, and finally we combine the two in the next section.
+
+Moreover, this market timing hypothesis assumes that that firms may have superior {\it company-specific} information.
+Such situations are more likely in industries or companies where the volatility is largely driven by company-specific volatility.
+So if buybacks are driven by market timing this superior information hypothesis predicts that there should be a positive relation between excess returns and the percentage of the volatility explained by company-specific factors, which we define as {\it standardized} idiosyncratic volatility, however not to be confused with residual variance.
+Unlike residual variance, this measure is little correlated with total volatility (\Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study) and measures more precisely the fraction of total volatility explained by company-specific news.
+
+This standardized volatility is defined as $1-R^2$,  where $R^2$ is estimated with the five-factor regression using 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month,  or the four factor regression leads to the same conclusions - results available upon request.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies.
+The healthcare industry has the largest percentage of firms classified as ``high idiosyncratic'', while cyclical industries such as steel, construction and chemicals contain a large number of ``low idiosyncratic'' firms.\footnote{Estimates of idiosyncratic volatility for a range of industries are available upon request.}
+
+Table~\ref{tbl:IdiosyncraticunderBB} shows the IRATS and Calendar Time abnormal returns for high and low idiosyncratic risk events-companies, both for buybacks and equity issues.
+Focusing on buybacks and IRATS, after 48 months high idiosyncratic buyback stocks earn \Sexpr{IRATS_table_highidio_BB["+48","CAR 5F"]}$\%$ (t = \Sexpr{IRATS_table_highidio_BB["+48",5]}) when we use the five factor model and \Sexpr{IRATS_table_highidio_BB["+48","CAR 3F"]}$\%$ (t = \Sexpr{IRATS_table_highidio_BB["+48",2]}) when we use the four factor model.
+When we use the five factor model  low idiosyncratic risk announcements are not followed by significant excess returns.
+Although the four factor model does show significant 48-month excess returns of \Sexpr{IRATS_table_lowidio_BB["+48","CAR 3F"]}$\%$ (t=\Sexpr{IRATS_table_lowidio_BB["+48",2]}) after low idiosyncratic risk events, the excess returns are more than 3 times smaller than for high idiosyncratic risk firms.
+The results using the Calendar Time method confirm these findings: only buybacks announced by firms with high idiosyncratic risk are followed by significant long-term excess returns, both for the five and four factor model.
+Hence the combined results of Table \ref{tbl:VOLunderBB} and \ref{tbl:IdiosyncraticunderBB} are consistent with the hypothesis that market timing is driving long-term excess returns.
+
+%Figure \ref{fig:pastallidio} summarizes our results.
+It shows the CAR based on IRATS (Panel~A for the high U-index firms, B for the low U-index firms, and C for all firms).
+In agreement with Table~\ref{tbl:IdiosyncraticunderBB}, the striking result (Panel~A) is that the U-index is not a good predictor of excess returns for stocks largely driven by market factors (low idiosyncratic firms).
+This is strong evidence that excess returns after buybacks are driven by superior company-specific information of the management.
+
+%The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \citep{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns.
+However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks.
+Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing.
+Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks.
+Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).
+So our results are also consistent with the \cite{Stambaugh2015} interpretation.
+
+%\subsection{Volatility and excess returns}
+%\label{sec:volbuybacks}
+
+%The announcement of a buyback program is not a firm commitment, but an option to buy back stock.
+\cite{IkenberryVermaelen1996} model this flexibility as an exchange option in which the market price of the stock is exchanged for the true value of the stock.
+They predict that, as with all options, the value increases with the volatility.
+The intuition is that the larger the volatility, the larger the probability that the market price may deviate from the true value.
+This enhances the timing ability of the manager-insider.
+They show that this option can have large value, something that may not be realized at the time of the announcement of the buyback authorization.
+For example, the market may underestimate the maturity of the option if they do not realize that firms who are announcing a buyback authorization for say 2 years are likely to renew the authorization many times in the future.
+Hence the option hypothesis predicts that excess returns are positively correlated with volatility.
+
+%Table~\ref{tbl:industriesR2Vol}, columns (3) and (4)  show the percentage of high and low volatility events across all industries for which we have at least 100 buyback events in our sample.
+Software and chips (different from the standardized idiosyncratic volatility case) tend to be the most volatile sectors and they are also two of the three sectors where buybacks are more frequent.
+
+%Table~\ref{tbl:VOLunderBB} shows the IRATS and Calendar Time abnormal returns for high and low volatility buybacks events-companies.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
 Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
 High volatility companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy, which are higher than the \Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged48m),1),1)}$\%$) of the corresponding low volatility sample.} Focusing on IRATS, high volatility buyback stocks earn \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$  after 48 months, while low volatility events have non significant abnormal returns for any period.
-The results using the Calendar Time method confirm these findings.\footnote{As mentioned in Section \ref{sec:Introduction}, the value weighted Calendar Time method alphas are also significant for the high volatility sample: for example the alpha after 48 months is \Sexpr{VOL_IRATStableBB_calValue["+48","CAL"]}$\%$ (t = \Sexpr{VOL_IRATStableBB_calValue["+48","t-stat"]}).
-} So we find support for the \cite{Stambaugh2015} costly arbitrage hypothesis as well as the option hypothesis proposed by \cite{IkenberryVermaelen1996}.
-
-Table~\ref{tbl:VOLunderBB} also tests whether the U-index can further differentiate high volatility events, as well as whether adjusting for volatility improves the predictive power of the U-index.
+The results using the Calendar Time method confirm these findings.
+So we find support for the \cite{Stambaugh2015} costly arbitrage hypothesis as well as the option hypothesis proposed by \cite{IkenberryVermaelen1996}.
+
+%Table~\ref{tbl:VOLunderBB} also tests whether the U-index can further differentiate high volatility events, as well as whether adjusting for volatility improves the predictive power of the U-index.
 Regardless of the time horizon and the event study method, the U-index works for high volatile companies.
@@
 
-\subsection{An Enhanced U-index for Buybacks}
+Turning to equity issues, we now find that firms with low idiosyncratic risk, i.e.
+firms largely driven by common factors, earn significant positive long-term excess returns and this conclusion holds for both the IRATs and the Calendar Time method, but only with the 4 factor model.
+Firms with high company specific risk earn no significant positive or negative long-run excess returns.
+While consistent with the view that managers in firms with higher idiosyncratic risk are better able to avoid selling undervalued stock, it does not correspond with the classic market timing story, i.e.
+that managers issue overvalued stock.
+In summary, throughout all equity issues results we only find significant negative long-term excess returns when low volatility companies issue equity, and only with the IRATS method (Table \ref{tbl:priorIssuers}).
+
+\subsection{Measuring Mispricing for Buyback stocks: the Enhanced U-index}
 \label{sec:newindex}
@@
 
-Table~\ref{tbl:underidioallBB} shows how the high/low U-index  high/low idiosyncratic risk, and high/low volatility buyback events overlap, while Table~\ref{tbl:underidioallBBcor} shows the correlations between the idiosyncratic, volatility, and U-index scores.
-Overall we see that although high U-index firms tend to have high idiosyncratic risk and high volatility, while high idiosyncratic risk firms tend to also have high volatility, the overlap is not very high.
-For example from Table~\ref{tbl:underidioallBB} we see that  only \Sexpr{round(Under_IdioBB["High Vol.","H Idiosync."],1)}$\%$ of the high volatility stocks that are classified as having either high or low idiosyncratic risk - note that we only consider the  \Sexpr{round(100*quantile_R2,2)}$\%$ tails - have high idiosyncratic risk.
-From Table~\ref{tbl:underidioallBBcor} we infer that the correlation between idiosyncratic risk and volatility scores is only \Sexpr{round(Under_IdioBB_cor["Volatility Score","Idiosyncratic Score"]*100,1)}$\%$.
-A natural question is therefore whether one can further enhance the \cite{PeyerVermaelen2009} U-index by incorporating information about the firms' pre-announce idiosyncratic risk and volatility.
+Table~\ref{tbl:underidioallBB} shows how the high/low U-index  high/low idiosyncratic risk, high/low volatility, and high/low MM buyback events overlap, while Table~\ref{tbl:underidioallBBcor} shows the correlations between the idiosyncratic risk, volatility, MM, and U-index scores.
+Overall we see that although high U-index firms tend to have high standardized idiosyncratic risk and high volatility, while high idiosyncratic risk firms tend to also have high volatility, the overlap is not very high.
+For example from Table~\ref{tbl:underidioallBB} we see that  only \Sexpr{round(Under_IdioBB["High Vol.","H Idiosync."],1)}$\%$ of the high volatility stocks that are classified as having either high or low standardized  idiosyncratic risk - note that we only consider the  \Sexpr{round(100*quantile_R2,2)}$\%$ tails - have high standardized idiosyncratic risk.
+From Table~\ref{tbl:underidioallBBcor} we also infer that the correlation between standardized idiosyncratic risk and volatility scores is only \Sexpr{round(Under_IdioBB_cor["Volatility Score","Idiosyncratic Score"]*100,1)}$\%$.
+We also see that the Mispricing Measure of \cite{Stambaugh2015} is not related to the other measures in the case of buybacks
+
+Based on these results, a natural question is whether one can further enhance the \cite{PeyerVermaelen2009} U-index by incorporating information about the firms' pre-announce standardized idiosyncratic risk and volatility.
 We consider one such combination where we simply take an equal-weighted combination of the 4 criteria into one ``Enhanced Undervaluation Index'' (EU-index).
@@
 They also tend to follow up more often with equity offerings after the buyback which suggests that they are more likely to be in the ``market timing'' business.
-Note that all these firm characteristics have not been used to define the EU-Index.
+Note that none of these firm characteristics has been used to define the EU-Index.
 
@@
 portfolios EU5 - EU6 in Table~\ref{tbl:EUunderBBcal}) is \$\Sexpr{tmp_market_cap} million (not indicated in the Table).
-So the buyback anomaly is to some extent a small cap anomaly.
+So indeed the buyback anomaly is to large extent a small cap anomaly.
 %, although portfolio EU3 for which the average market capitalization of its \Sexpr{sum(EUindex_bb==3)} firms is \$\Sexpr{round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb ==3]),1)} billion still has significant abnormal returns.
 
-Tables  \ref{tbl:EUunderBB} and \ref{tbl:EUunderBBcal} show respectively the IRATS and Calendar Time monthly abnormal returns for all values of the EU-index.
-Focusing on IRATS, as the EU-index increases, the long term abnormal returns increase (from \Sexpr{round(EU_IRATStable_bb["+48",1],1)}$\%$ to \Sexpr{round(EU_IRATStable_bb["+48",19],1)}$\%$).
+Tables  \ref{tbl:EUunderBB} and \ref{tbl:EUunderBBcal} show respectively the IRATS and Calendar Time monthly abnormal returns for all values of the EU-index using the five factor model.\footnote{The results using the four factor model are similar and are available upon request.} Focusing on IRATS, as the EU-index increases, the long term (48 months) abnormal returns increase (from \Sexpr{round(EU_IRATStable_bb["+48",1],2)}$\%$ to \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$).
 Figure~\ref{fig:Epastall} show the same results over time for each EU-index.
-Long-term cumulative excess returns after 48 months are becoming statistically significantly positive at EU-index levels of 3 and higher, and then steadily increase from \Sexpr{round(EU_IRATStable_bb["+48",10],1)}$\%$ to \Sexpr{round(EU_IRATStable_bb["+48",19],1)}$\%$.
-The Calendar Time results are similar although they only show significance starting at EU-index levels of 5.
+Long-term cumulative excess returns after 48 months are becoming statistically significantly positive at EU-index levels of 3 and higher, and then steadily increase from \Sexpr{round(EU_IRATStable_bb["+48",10],2)}$\%$ to \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$.
+The Calendar Time results in Table~\ref{tbl:EUunderBBcal} are similar although they only show significance starting at EU-index levels of 5.
 Investing in the very high EU index firms (EU=6) generates alphas of \Sexpr{round(EU_CALtable_bb["+48",19],2)}$\%$ per month for 48 months.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
@@
 
-The bottom line is that combining volatility, idiosyncratic risk and the U-index in one EU-index generates a more selective predictor of excess returns than each of the indicators separately.
-Indeed, high U-index stocks, stocks with high idiosyncratic risk, and high volatile stocks generate cumulative excess returns of respectively \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR5F"]}$\%$ (Table~\ref{tbl:priorBuybacks}), \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$ (Table~\ref{tbl:IdiosyncraticunderBB}) and \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$ (Table~\ref{tbl:VOLunderBB}).
+The bottom line is that combining volatility, standardized idiosyncratic risk and the U-index in one EU-index generates a more selective predictor of excess returns than each of the indicators separately.
+%Indeed, high U-index stocks, stocks with high standardized idiosyncratic risk, and high volatile stocks generate cumulative excess returns of respectively \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR5F"]}$\%$ (Table~\ref{tbl:priorBuybacks}), \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$ (Table~\ref{tbl:IdiosyncraticunderBB}) and \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$ (Table~\ref{tbl:VOLunderBB}).
 
@@
 
-As volatility and idiosyncratic risk are time dependent, the performance of the new EU-index may not be robust over time - e.g., relative to the U-index of \cite{PeyerVermaelen2009}.
-Tables \ref{tbl:EUTimeUnderBB} (IRATS) and \ref{tbl:EUTimeUnderBBcal} (Calendar Time method), like Table~\ref{tbl:PastFindingsTimeUnderBB} for the U-index, show the relative performance of high and low EU-index repurchases.
-In order to have roughly similar number of under/overvalued firms as when we use the U-index, we define low EU-index firms to be those for which the EU-index is 0-1, and high for which it is 5-6 (the index takes values from 0 to 6).
-With this definition we have \Sexpr{sum(low_EU_bb)} low EU-index and \Sexpr{sum(high_EU_bb)}  high EU-index firms in our sample (in comparison with \Sexpr{sum(company_subset_overvalued_bb)} low U-index and \Sexpr{sum(company_subset_undervalued_bb)} high U-index ones).
+As volatility and standardized idiosyncratic risk are time dependent, the performance of the new EU-index may not be robust over time - e.g., relative to the U-index of \cite{PeyerVermaelen2009}.
+Tables \ref{tbl:EUTimeUnderBB} (IRATS) and \ref{tbl:EUTimeUnderBBcal} (Calendar Time method) show the relative performance of high and low EU-index repurchases.
+We define low EU-index firms to be those for which the EU-index is 0-3, and high for which it is 4-6 (the index takes values from 0 to 6).
+With this definition we have \Sexpr{sum(low_EU_bb)} low EU-index and \Sexpr{sum(high_EU_bb)}  high EU-index firms in our sample.
 
@@
 
+\subsection{Mispricing measure versus EU-index}
+
+Both the EU index and the Mispricing Measure (MM) developed by \cite{Stambaugh2015} are measures of mispricing.
+The EU index is specific for firms that announce buybacks while the MM is developed for all firms.
+An interesting question is whether these two measures are substitutes in the case of firms that announce share repurchases.
+Specifically, will sorting buyback event firms on the basis of their MM also generate larger excess returns for low MM (undervalued) firms than high MM (overvalued) firms?
+And will this sort improve the EU-index classification?
+Note from Tables \ref{tbl:underidioallBB}  and \ref{tbl:underidioallBBcor} that the MM is not related to the other measures used as elements of the EU-index.
+
+Table~\ref{tbl:EUvsStambaughBB} Panel A compares long-term excess returns for high and low EU firms and MM firms using the five factor model.\footnote{Results (available upon request) are similar for the four factor model.}  Low MM firms, which are undervalued based on that measure, earn smaller excess returns than high MM firms, which demonstrates that the Mispricing Measure may work well for the average firm but not for buyback stocks.
+It also may explain why investors fail to respond to buyback announcements if the stocks have characteristics that are normally associated with overvalued stocks (such as negative momentum).
+Panel B considers four samples: (1) low MM/low EU firms, (2) low MM/high EU firms, (3) high MM/low EU firms and finally (4) high MM/high EU firms.
+Comparing these samples with the samples in Panel A shows that adding the Mispricing Measure does not improve the predictability of the EU index in any consistent way.
+For example, while the high MM/low EU sample does worse (\Sexpr{round(Stam_IRATStable_EU_BB["+48","High Mis.: L.
+EU CAR"],2)}$\%$) than the low EU sample by itself (\Sexpr{round(EU_IRATStableBB["+48","Low EU: CAR"],2)}$\%$),  investing in low MM/high EU stocks generates lower long-term 48-month excess returns (\Sexpr{round(Stam_IRATStable_EU_BB["+48","H.
+EU CAR"],2)}$\%$) than simply buying high EU stocks (\Sexpr{round(EU_IRATStableBB["+48","High EU: CAR"],2)}$\%$).
+The low MM/low EU sample generates basically the same excess returns (\Sexpr{round(Stam_IRATStable_EU_BB["+48","Low Mis.: L.
+EU CAR"],2)}$\%$) as the low EU sample by itself (\Sexpr{round(EU_IRATStableBB["+48","Low EU: CAR"],2)}$\%$).
+So, adding the Mispricing Measure of \cite{Stambaugh2015} does not help forecasting long-term excess returns after buyback announcements.
+
 \section{Conclusion}
@@
 The buyback anomaly first reported by \cite{IkenberryLakonishokVermaelen1995} is still present and robust.
-Long term excess returns are large, highly statistically significant and robust even when we replace the Fama-French three-factor model with the Fama-French five-factor model.
-We believe that the difference with the conclusions of \cite{FamaFrench2015b} is a result of the fact that we do not pool buybacks and equity issues in a ``net issuance'' anomaly, which unfortunately has become the standard in the anomaly literature.
+Long term excess returns are large, highly statistically significant and robust even when we replace the Fama-French three-factor model with the Fama-French five-factor model and the Stambaugh-Yuan four factor model.
+However, both models eliminate the equity issue anomaly, i.e.
+the finding of \cite{LoughranRitter1995} that equity issues are followed by long-term negative excess returns.
+Our results also show that  pooling buybacks and equity issues in a ''net issuance'' anomaly can be strongly misleading.
 A buyback is not simply the inverse of an equity issue, especially in a world with asymmetric information.
@@
 By the time the buyback is completed the firm may already have experienced significant excess returns.
-
-Not all buybacks are the same: we find that buybacks made by small beaten up risky low market to book companies earn the largest excess returns.
-We find that both idiosyncratic risk (small $R^2$) and total risk are positively correlated with future returns.
-This result is inconsistent with \cite{Ang2006} but consistent with \cite{Stambaugh2015} who show that for undervalued firms residual variance (almost perfectly correlated with total volatility) is positively related to future returns.
-It is also consistent with the argument of Ikenberry and Vermaelen (1996) that a buyback authorization creates an option to take advantage of an undervalued stock, and options on high volatility stocks are more valuable.
-We combine these characteristics in a new measure: the EU index or Enhanced Undervaluation Index, building on the analysis of \cite{PeyerVermaelen2009}.
-Investing in very high EU index firms generates Fama-French five-factor adjusted returns of \Sexpr{round(EU_CALtable_bb["+48",19],2)}$\%$ per month during the 48 months after the buyback announcement.
-These are also firms that are more likely to mention in their press releases that they are buying back stock because they are undervalued.
-%They are more likely to miss earnings forecasts relative to the other buyback firms and therefore falling out of favor with analysts.  
-However investing in high EU index firms to some extent implies investing in small caps and micro-caps, which may explain partially why the anomaly persists as these firms may not satisfy, for example, liquidity risk constraints of many funds.
+Finally, market timing is relatively easier in an open market repurchase setting as the seller is not aware that he is selling to the corporation.
+
+We also find that both standardized idiosyncratic risk (small $R^2$) and total risk are positively correlated with future returns.
+This result is consistent with the hypothesis that buybacks are driven by market timing: a buyback authorization creates an option to take advantage of an undervalued stock, and options on high volatility stocks are more valuable.
+Moreover, managers are more likely to have superior information when stock prices are driven by company-specific events.
+We combine these characteristics with the Undervaluation Index developed by \cite{PeyerVermaelen2009} in a new measure of the likelihood that the buyback is driven by undervaluation: the EU index or Enhanced Undervaluation Index.
+Investing in very high EU index firms generates excess returns of \Sexpr{round(EU_CALtable_bb["+48",19],2)}$\%$ per month during the 48 months after the buyback announcement.
+However investing in high EU index firms  implies investing in small caps and micro-caps, which may explain partially why the anomaly persists as these firms may not satisfy, for example, liquidity risk constraints of many funds.
+Finally, we find that the Misvaluation Measure of \cite{Stambaugh2015} is neither correlated with the buyback specific measures of undervaluation (e.g.
+the EU-index) nor can be used to better forecast post buyback announcement long term excess returns.
+This provides further evidence that the buyback anomaly may be different from the other anomalies.
 
 \newpage
+\appendix
+
+\section*{Appendix: Variable Definitions}
+
+\noindent {\bf BE/ME:} Ratio of the book value of equity to the market value of equity.
+Book value of equity is calculated using the following CCM variables: SEQ, CEQ, PSTK, PSTKRV, TXDITC, PRBA, DLC, DLTT, AT, LT.
+We follow \cite{FamaFrench2001}.
+Market value of equity is calculated as the price per share multiplied by the number of shares outstanding: CCM and CRSP Monthly Stocks.
+
+\noindent {\bf EU-index:}   The EU-Index of a repurchase firm is the sum of 3 indicators measured using firms characteristics scores the month before the repurchase announcement: the U-index, plus a score of 0, 1, 2 for low, middle, and high firms in terms of their volatility and standardized idiosyncratic volatility $(1-R^2)$ the month before the announcement.
+
+\noindent {\bf Mispricing Measure:}   The \cite{Stambaugh2015} mispricing measure the month of the repurchase or SEO announcement, taken from \url{http://users.cla.umn.edu/~jianfeng/Misp_Score.csv}.
+The higher the value, the greater the relative degree of overpricing of the firm.
+
+\noindent {\bf Leverage:} The ratio $debt/(debt+equity)$.
+Debt is the sum of the Compustat variables DLC+ DLTT.
+Equity is the Compustat variable SEQ.
+We make the winsorization and other data adjustments as in \url{http://www.ivo-welch.info/professional/leverage.placebo/}.
+
+\noindent {\bf Market Cap.:} Market value of equity, calculated as the price per share multiplied by
+the number of shares outstanding: CRSP Monthly Stocks.
+
+\noindent {\bf Percent Shares:} The percentage of shares authorized for repurchase in the case of buybacks, or issued for the case of issuers: SDC Database.
+
+\noindent {\bf Prior Returns:}  Cumulative return for the previous 6 months: CRSP Daily Stocks.
+
+\noindent {\bf Standardized Idiosyncratic Vol.
+$(1-R^2)$:}  The $R^2$ of the  \cite{FamaFrench2015} five factor model using returns over the previous 6 months: CRSP Daily Stocks and Kenneth French's Website.
+
+\noindent {\bf U-index:}    Based on \cite{PeyerVermaelen2009}, the U-Index of a repurchase firm is the sum of 3 indicators measured using firms characteristics scores the month before the repurchase announcement: 0, 1, 2 for low, middle, and high firms in terms of their size (2 is for large firms, 0 for small, and 1 for others), BE/ME (2 is for large BE/ME), and returns over the 6 months before the announcement (2 is for low returns).
+
+\noindent {\bf Volatility:} Standard deviation of daily returns over the previous 6 months: CRSP Daily Stocks.
+
+%{\small \singlespacing \LTXtable{\textwidth}{VariablesTable} }
+
+\clearpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+Descriptive_stats_BB1 <- apply(Descriptive_stats_BB,2,function(r) as.character(round(r,2)))
+rownames(Descriptive_stats_BB1) <- rownames(Descriptive_stats_BB)
+Descriptive_stats_BB1 = rbind(Descriptive_stats_BB1,rep(length(BUYBACK_DATA$DATASET$SDC$CUSIP), 5))
+rownames(Descriptive_stats_BB1)[nrow(Descriptive_stats_BB1)] <- "Observations"
+colnames(Descriptive_stats_BB1) <- NULL
+
+Descriptive_stats_ISS1 <- apply(Descriptive_stats_ISS,2,function(r) as.character(round(r,2)))
+rownames(Descriptive_stats_ISS1) <- rownames(Descriptive_stats_ISS)
+Descriptive_stats_ISS1 = rbind(Descriptive_stats_ISS1,rep(length(ISSUERS_DATA$DATASET$SDC$CUSIP),5))
+rownames(Descriptive_stats_ISS1)[nrow(Descriptive_stats_ISS1)] <- "Observations"
+colnames(Descriptive_stats_ISS1) <- NULL
+
+tmp = rbind(c("", "", "", "",""),
+            c("Mean","Median","Standard Dev.", "$20^{th}$ Percentile","$80^{th}$ Percentile"),
+            Descriptive_stats_BB1,
+            c("", "", "", "",""),
+            c("", "", "", "",""),
+            c("Mean","Median","Standard Dev.", "$20^{th}$ Percentile","$80^{th}$ Percentile"),
+            Descriptive_stats_ISS1
+)
+
+tmp = cbind(c("Panel A: Buybacks","",rownames(Descriptive_stats_BB1),"","Panel B: SEOs","",rownames(Descriptive_stats_ISS1)),tmp)
+
+# $20^{th}$ Percentile& $80^{th}$ Percentile   $(1-R^{2})$
+
+latex_render_data_frame(
+  tmp, 
+  title = "Buyback and SEO announcements during 1985-2015: Descriptive Statistics",
+  caption="This table reports descriptive statistics of our samples. Panel~A is for repurchases and Panel~B for SEOs. All variables are described in the Appendix.",
+  label = "tbl:descriptive",
+  columns=NULL,
+  bigtitleontop = T,
+  show_rownames=FALSE,
+  scale = 1,
+  digits=1,
+  lastSpecial=F,dorotate=F,
+  NAvalue = "", hlinerows = c(1,2,13,15,16)
+)
+
+@
 
@@
   cbind(CAL_table_all_bb,CAL_table_all_bb_undervaluation)[reported_times,],
-  columns = c("All 3F","All 5F","High U-index 3F","Low U-index 3F","High U-index 5F","Low U-index 5F"),
+  columns = c("All 4F","All 5F","High U-index 4F","Low U-index 4F","High U-index 5F","Low U-index 5F"),
   title="Buyback announcements during 1985-2015",
@@
 We include a version of the abnormal returns for the full sample and one for both companies with a high U-index and a low U-index.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench1993} three-factor model and the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{StambaughYuan2016} four-factor model (4F) and the \\cite{FamaFrench2015} five-factor model (5F) for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regressions are run each event month~$j$:\\vspace{-1em}
 \\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + \\epsilon_{i,t}, \\\\
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB'}_t + d_j {MGMT}_t + e_t {PERF}_t + \\epsilon_{i,t}, \\\\
 (R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
@@
 $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+${SMB}_t$, ${HML}_t$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+${SMB'}_t$, ${MGMT}_t$, ${PERF}_t$ are the \\cite{StambaughYuan2016} factors Size, Management Related (MGMT), and  Performance Related (PERF), respectively.
 The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
 The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015} five-factor model.
 In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of the \\cite{StambaughYuan2016} four factors (4F) or the \\cite{FamaFrench2015} five factors (5F) as the independent variables.
 The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
@@
 @
-\clearpage
 
@@
 printLatexTable2(
-  IRATS_table_all_iss[reported_times,],
-  CAL_table_all_iss[reported_times,],
-  columns = c("All 3F","All 5F"),
-  title="Issue announcements during 1985-2015",
+  cbind(CAL_table_all_bb_value,CAL_table_all_bb_undervaluation_value)[reported_times,],
+  cbind(CAL_table_all_bb_valueL,CAL_table_all_bb_undervaluation_valueL)[reported_times,],
+  columns = c("All 4F","All 5F","High U-index 4F","Low U-index 4F","High U-index 5F","Low U-index 5F"),
+  title="Buyback announcements during 1985-2015: Value Weighted Portfolios",
+  title1 = "Panel A: Calendar Method Monthly Value Weighted Abnormal Returns",
+  title2 = "Panel B: Calendar Method Monthly Value Weighted Abnormal Returns, No Large Firms",
+  caption= "The table presents the abnormal returns for firms after open market repurchase announcements from the announcement date until $t$ months after announcement.
+The table reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{StambaughYuan2016} four-factor model (4F) and the \\cite{FamaFrench2015} five-factor model (5F).
+In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month value weighted portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of the \\cite{StambaughYuan2016} four factors (4F) or the \\cite{FamaFrench2015} five factors (5F) as the independent variables.
+Panel~B uses only firms which at the month prior to the repurchase announcement were in the bottom $75^{th}$ percentile of all public firms reported in CRSP in terms of their market capitalization.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
+",
+
+label = "tbl:valuetable",
+bigtitleontop=T,
+titleontop=T,
+metric1 = "AR",
+metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=T
+)
+@
+
+\clearpage
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+printLatexTable2(
+  cbind(IRATS_table_all_iss,IRATS_table_lowMM_iss,IRATS_table_highMM_iss)[reported_times,],
+  cbind(CAL_table_all_iss,CAL_table_lowvol_iss,CAL_table_highvol_iss)[reported_times,],
+  columns = c("All 4F","All 5F","Low MM 4F","Low MM 5F","High MM 4F","High MM 5F"),
+  title="SEO announcements during 1985-2015",
   title1 = "Panel A: IRATs Cumulative Abnormal Returns",
@@
   caption= "The table presents the abnormal returns for firms after issue announcements from the announcement date until $t$ months after the announcement.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench1993} three-factor model and the Fama French (2015) five-factor model for the sample of firms that announced equity issuance plus various subsamples.
-The following regressions are run each event month~$j$:
+We include a version of the abnormal returns for the full sample and one for both companies with high low Mispricing Measure (MM) before the announcement.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{StambaughYuan2016} four-factor model (4F) and the \\cite{FamaFrench2015} five-factor model (5F) for the sample of firms that announced equity issuance plus various subsamples.
+The following regressions are run each event month~$j$:\\vspace{-1em}
 \\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + \\epsilon_{i,t}, \\\\
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB'}_t + d_j {MGMT}_t + e_t {PERF}_t + \\epsilon_{i,t}, \\\\
 (R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
 \\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the equity issuance.
 $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+${SMB}_t$, ${HML}_t$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+${SMB'}_t$, ${MGMT}_t$, ${PERF}_t$ are the \\cite{StambaughYuan2016} factors Size, Management Related (MGMT), and  Performance Related (PERF), respectively.
 The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
 The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios.
+In this method, event firms that have announced an equity issuance in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of the \\cite{StambaughYuan2016} four factors (4F) or the \\cite{FamaFrench2015} five factors (5F) as the independent variables.
 The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
@@
 
-%\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% TIME ROBUSTNESS ANALYSIS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Robustness over time}
+%\label{app:robusttime}
 
 <<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+tmp = BBtable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
+colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2015: CAR","t-stat","p-value","2008-2015: CAR","t-stat","p-value")
+tmp2 = BBtable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
+colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2015: CAL","t-stat","p-value","2008-2015: CAL","t-stat","p-value")
+
 printLatexTable2(
-  Exit_on_SEO_Abn_table[reported_times,],
-  Exit_on_SEO_Abn_table_cal[reported_times,],
-  columns = c("No Issue","Issue"),
-  title="Buybacks with and without subsequent issue",
+  tmp,
+  tmp2,
+  columns= c("1985-1990","1991-2000","2001-2015","2008-2015"),
+  title="Buyback returns over different time periods",
   title1 = "Panel A: IRATs Cumulative Abnormal Returns",
   title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="The table presents the long-run abnormal returns for firms repurchase announcements for events with and without a subsequent SEO announcement.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+  caption="The table presents the long-run abnormal returns for firms after repurchase announcements for different time periods.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
 The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-
-label = "tbl:BBISSexit",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=F
-)
-
-if (0){
-  colnames(ISS_for_BB_Abn_table)[1]<- "Post-buyback SEOs"
-  colnames(ISS_for_BB_Abn_table)[4]<- "Other SEOs"
-  printLatexTable(ISS_for_BB_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
-                  label  = "tbl:BBISSexitAfter",
-                  columns= c("After a Buyback","No Prior Buyback"),
-                  title  ="Issue announcements with and without a prior buyback",
-                  caption = "The table presents the long-run abnormal returns (CAR) for firms after issue announcements for events with and without a prior buyback announcement within 48 months.
-We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.",
-
-lastSpecial=T,
-titleontop = T
-  )
-}
-@
-
-%%%%%%%%
-
-%\clearpage
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-if (0){
-  printLatexTable2(
-    Exit_on_BB_Abn_table[reported_times,],
-    Exit_on_BB_Abn_table_cal[reported_times,],
-    columns = c("No Buyback","Buyback"),
-    title="SEOs with and without subsequent buyback",
-    title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-    title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-    caption="The table presents the long-run abnormal returns for firms after issue announcements with and without a subsequent buyback announcement on the full sample for different periods in time.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-
-label = "tbl:ISSBBexit",
-bigtitleontop=T,
-titleontop=T,
-scale=1,
-lastSpecial=T,
-dorotate=F
-  )
-
-  printLatexTable(BB_for_ISS_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
-                  label  = "tbl:ISSBBexitAfter",
-                  columns= c("post-Issue Buybacks: CAR","Other Buybacks: CAR"),
-                  title  ="Long-run IRATS abnormal return of only the buybacks that are announced within 48 months after an SEO announcement versus the remaining buyback events.",lastSpecial=T)
-}
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% TIME ROBUSTNESS ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Robustness over time}
-%\label{app:robusttime}
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-tmp = BBtable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2015: CAR","t-stat","p-value","2008-2015: CAR","t-stat","p-value")
-tmp2 = BBtable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2015: CAL","t-stat","p-value","2008-2015: CAL","t-stat","p-value")
-
-printLatexTable2(
-  tmp,
-  tmp2,
-  columns= c("1985-1990","1991-2000","2001-2015","2008-2015"),
-  title="Buyback returns over different time periods",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="The table presents the long-run abnormal returns for firms after repurchase announcements for different time periods.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015} five-factor model.
 In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
@@
 
-if (0){
-  tmp = ISStable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-  colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2015: CAR","t-stat","p-value","2008-2015: CAR","t-stat","p-value")
-  tmp2 = ISStable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-  colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2015: CAL","t-stat","p-value","2008-2015: CAL","t-stat","p-value")
-
+@
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% VOL ANALYSIS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
 printLatexTable2(
-    tmp,
-    tmp2,
-    columns= c("1985-1990","1991-2000","2001-2015","2008-2015"),
-    title="SEOs returns over different time periods",
+  cbind(IRATS_table_lowvol_BB,IRATS_table_highvol_BB,IRATS_table_lowvol_iss,IRATS_table_highvol_iss)[reported_times,],
+  cbind(CAL_table_lowvol_BB,CAL_table_highvol_BB,CAL_table_lowvol_iss,CAL_table_highvol_iss)[reported_times,],
+  columns= c("Buyback: Low Vol. 4F","5F","High Vol. 4F","5F","SEOs: Low Vol. 4F","5F","High Vol. 4F","5F"),
+  title="Buyback and SEOs for Low and High Volatility companies",
   title1 = "Panel A: IRATs Cumulative Abnormal Returns",
   title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-    caption="Long-run IRATS cumulative (Panel~A) and Calendar method monthly (Panel~B) abnormal return after issue announcements for different time periods.",
-    label = "tbl:PastFindingsTimeISS",
+  caption="This table presents the long-term abnormal return after open market repurchase (first 4 columns) and equity issuance (last 4 columns) announcements from the announcement date until $t$ months after, for low and high volatility companies.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{StambaughYuan2016} four-factor model (4F) and the \\cite{FamaFrench2015} five-factor model (5F).
+The following regressions are run each event month~$j$:\\vspace{-1em}
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB'}_t + d_j {MGMT}_t + e_t {PERF}_t + \\epsilon_{i,t}, \\\\
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the event (repurchase or equity issuance).
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML}_t$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+${SMB'}_t$, ${MGMT}_t$, ${PERF}_t$ are the \\cite{StambaughYuan2016} factors Size, Management Related (MGMT), and  Performance Related (PERF), respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios.
+In this method, event firms that have announced a repurchase (first 4 columns) or an equity issuance (last 4 columns) in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of the \\cite{StambaughYuan2016} four factors (4F) or the \\cite{FamaFrench2015} five factors (5F) as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
+label = "tbl:VOLunderBB",
 bigtitleontop=T,
 titleontop=T,
+metric1 = "CAR",
+metric2 = "AR",
 scale=1,
@@
 )
-}
-
 @
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% IDIOSYNCRATIC ANALYSIS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 <<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-one_table = cbind(BBtable_undertime[,7:12],BB_cal_table_undertime[,7:12],
-                  BBtable_undertime[,19:24],BB_cal_table_undertime[,19:24],
-                  BBtable_undertime[,31:36],BB_cal_table_undertime[,31:36],
-                  BBtable_undertime[,43:48],BB_cal_table_undertime[,43:48]
-)
-#one_table = BBtable_undertime
-printLatexTable(one_table[reported_times,1:12],
-                columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),
-                rowcolumn="1985-1990",
-                title="Buyback returns for the U-index over time",
-                caption="The table presents the long-run abnormal returns for firms after open market repurchase announcements for high and low U-index firms in different time periods and shows significantly larger returns by buybacks announced by high U-index firms compared to those with a low U-index.
-We report both the IRATS cumulative average abnormal returns (CAR, Panel~A) and the calender time method (AR, Panel~B) abnormal returns on the full sample.
-$t$-Statistics are provided and stars indicate significance at the $5\\%$ (*), and $1\\%$ level (**).
-\\\\",
-                label="tbl:PastFindingsTimeUnderBB",metric=c("CAR", "CAR", "AR", "AR"),
-                scale = 1,close=F,lastSpecial=T
-)
-printLatexTable(one_table[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
-printLatexTable(one_table[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
-printLatexTable(one_table[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
-
-if (0){
-  paste(printLatexTable(BB_cal_table_undertime[reported_times,1:12],
-                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
-                        rowcolumn="1985-1990",
-                        title="Calendar Method abnormal returns after open market repurchase announcements  for under and over valued companies over different time periods.",
-                        label="tbl:PastFindingsTimeUnderBBcal",
-                        scale = 0.8,close=F,lastSpecial=T
-  ),
-  printLatexTable(BB_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(BB_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(BB_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
-
-}
-if (0){
-  paste(printLatexTable(ISStable_undertime[reported_times,1:12],
-                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
-                        rowcolumn="1985-1990",
-                        title="Long-run IRATS abnormal returns after issue announcements  for under and over valued companies over different time periods.",
-                        label="tbl:PastFindingsTimeUnderISS",
-                        scale = 0.9,close=F,lastSpecial=T
-  ),
-  printLatexTable(ISStable_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISStable_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISStable_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
-
-  paste(printLatexTable(ISS_cal_table_undertime[reported_times,1:12],
-                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
-                        rowcolumn="1985-1990",
-                        title="Calendar Method abnormal returns after issue announcements  for under and over valued companies over different time periods.",
-                        label="tbl:PastFindingsTimeUnderISScal",
-                        scale = 0.9,close=F,lastSpecial=T
-  ),
-  printLatexTable(ISS_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISS_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISS_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
-}
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% INDUSTRIES ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
-tmp_cal = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,4:6] ))
-
-if (0){
+#cbind(R2_IRATStableBB,IRATS_table_lowidio_iss)[reported_times,],
+#cbind(R2_IRATStableBB_cal,R2_IRATStable_underBB_cal)[reported_times,],
+#columns= c("Low Id.","High Id.","Low Id./High U-Ind.","Low Id./Low U-Ind.","High Id./High U-Ind.","High Id./Low U-Ind."),
+#title="Buyback for Low and High idiosyncratic and  for Low and High U-index companies",
+
 printLatexTable2(
-    tmp[reported_times,1:(3*6)],
-    tmp[reported_times,(3*6+1):36],
-    columns= names(industry_BB)[1:6],
-    columns2= names(industry_BB)[7:12],
-    title="Buyback IRATS Abnormal Returns: Industry Robustness",
-    #title1 = "",
-    #title2 = "",
-    caption=paste("The table presents the long-run abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample.
-We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
+  cbind(IRATS_table_lowidio_BB,IRATS_table_highidio_BB,IRATS_table_lowidio_iss,IRATS_table_highidio_iss)[reported_times,],
+  cbind(CAL_table_lowidio_BB,CAL_table_highidio_BB,CAL_table_lowidio_iss,CAL_table_highidio_iss)[reported_times,],
+  columns= c("Buyback: Low Id. 4F","5F","High Id. 4F","5F","SEOs: Low Id. 4F","5F","High Id. 4F","5F"),
+  title="Buyback and SEOs for Low and High Idiosyncratic companies",
+  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
+  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
+  caption="This table presents the long-term abnormal return after open market repurchase (first 4 columns) and equity issuance (last 4 columns) announcements from the announcement date until $t$ months after, for low and high idiosyncratic companies.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{StambaughYuan2016} four-factor model (4F) and the \\cite{FamaFrench2015} five-factor model (5F).
+The following regressions are run each event month~$j$:\\vspace{-1em}
 \\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB'}_t + d_j {MGMT}_t + e_t {PERF}_t + \\epsilon_{i,t}, \\\\
 (R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
 \\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the event (repurchase or equity issuance).
 $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+${SMB}_t$, ${HML}_t$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+${SMB'}_t$, ${MGMT}_t$, ${PERF}_t$ are the \\cite{StambaughYuan2016} factors Size, Management Related (MGMT), and  Performance Related (PERF), respectively.
 The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
 The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-The 48 month abnormal return for the full sample is equal to ",round(IRATS_table_all_bb["+48","CAR 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),
-
-label = "tbl:IndustriesBB",
-bigtitleontop=T,
-metric1 = "CAR", metric2 = "CAR",
-#titleontop=T,
-scale=1,
-lastSpecial=T,
-dorotate=T
-  )
-
-  printLatexTable2(
-    tmp_cal[reported_times,1:(3*6)],
-    tmp_cal[reported_times,(3*6+1):36],
-    columns= names(industry_BB)[1:6],
-    columns2= names(industry_BB)[7:12],
-    title="Buyback Calendar Method Abnormal Returns: Industry Robustness",
-    #title1 = "",
-    #title2 = "",
-    caption=paste("The table presents the long-run calendar method abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample.
-Specifically, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors (the difference between the risk-free rate and the return on the equally weighted CRSP index, the monthly return on the size, book-to-market factor, profitability factor and investment factor in month) as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
-The 48 month abnormal return for the full sample is equal to ",round(CAL_table_all_bb["+48","CAL 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),
-    label = "tbl:IndustriesBB_cal",
-    bigtitleontop=T,
-    metric1 = "AR", metric2 = "AR",
-    #titleontop=T,
-    scale=1,
-    lastSpecial=T,
-    dorotate=T
-  )
-
-}
-@
-
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-if (0){
-  latex_render_data_frame(
-    pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)), 
-    title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all buybacks",
-    caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all buybacks.
-The holding period for each buyback is 12 months per event.",
-    label="tbl:allhedgedBB", 
-    columns=NULL,
-    bigtitleontop = T,
-    show_rownames=TRUE,
-    scale = 0.9,
-    digits=1,
-    lastSpecial=F,dorotate=F
-  )
-}
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Cross Relations
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\clearpage
-%\subsection{Enhanced U-index}
-%\label{app:enhanced}
-
-\small
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-tmp = industry_BB_features[,c(1:4,9:10)]
-if (colnames(tmp)[1] == "H Idsync.")
-  colnames(tmp) <- paste(colnames(tmp), " (",1:ncol(tmp), ")",sep="")
-latex_render_data_frame(
-  round(tmp,1), 
-  title = "Industry Characteristics",
-  caption="Percentage of high and low idiosyncratic risk  and volatility companies for all industries for which we have at least 100 events in our sample.",
-  label = "tbl:industriesR2Vol",
-  columns=NULL,
-  bigtitleontop = T,
-  show_rownames=TRUE,
-  scale = 1,
-  digits=1,
-  lastSpecial=F,dorotate=T
-)
-@
-\normalsize
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% IDIOSYNCRATIC ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  cbind(R2_IRATStableBB,R2_IRATStable_underBB)[reported_times,],
-  cbind(R2_IRATStableBB_cal,R2_IRATStable_underBB_cal)[reported_times,],
-  columns= c("Low Id.","High Id.","Low Id./High U-Ind.","Low Id./Low U-Ind.","High Id./High U-Ind.","High Id./Low U-Ind."),
-  title="Buyback for Low and High idiosyncratic and  for Low and and High U-index companies",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high idiosyncratic and for low and  high U-index companies.
-Regardless of event study method and time horizon, the U-index works only for idiosyncratic companies.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios.
+In this method, event firms that have announced a repurchase (first 4 columns) or an equity issuance (last 4 columns) in the last calendar months form the basis of the calendar month portfolio.
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of the \\cite{StambaughYuan2016} four factors (4F) or the \\cite{FamaFrench2015} five factors (5F) as the independent variables.
 The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
@@
 )
-
 @
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% VOL ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%
 
 <<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  cbind(VOL_IRATStableBB,VOL_IRATStable_underBB)[reported_times,],
-  cbind(VOL_IRATStableBB_cal,VOL_IRATStable_underBB_cal)[reported_times,],
-  columns= c("Low Vol.","High Vol.","Low Vol./High U-ind.","Low Vol./Low U-ind.","High Vol./High U-ind.","High Vol./Low U-ind."),
-  title="Buyback for Low and High Volatility and  for Low and and High U-index companies",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility and  for low and  high U-index companies.
-Regardless of event study method and time horizon, the U-index works only for idiosyncratic companies.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:VOLunderBB",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-rownames(Under_IdioBB)[1:2] <- c("high U-index", "low U-index")
+rownames(Under_IdioBB)[1:2] <- c("High U-index", "Low U-index")
 latex_render_data_frame(
-  round(Under_IdioBB[1:6,1:4],1), 
+  round(Under_IdioBB[1:8,1:4],1), 
   title = "Relations across firm characteristics for Buybacks",
@@
   title = "Correlations of Buybacks Characteristics",
-  caption="Correlation between the three buybacks characteristics considered: Idiosyncratic score (percentile across all CRSP companies of firm's $1-R^2$, 0 to 1), Volatility score  (percentile across all CRSP companies, 0 to 1) and U-index score (0 to 15).
+  caption="Correlation between the three buybacks characteristics considered: Idiosyncratic score (percentile across all CRSP companies of firm's $1-R^2$, 0 to 1), Volatility score  (percentile across all CRSP companies, 0 to 1), U-index score (0 to 15), and the Mispricing measure of Stambaugh et al.
+(2015).
 All scores are defined using the universe of all CRSP companies at the time of the announcement with data up to the month before the announcement.",
@@
 rownames(EU_relations)[2] <- "High Leverage"
+EU_relations <- EU_relations[setdiff(rownames(EU_relations), "Good purpose" ),]
 latex_render_data_frame(
@@
 Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores.
-For each EU-index value, we report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+For each EU-index value, we report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
 Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores.
-For each EU-index value, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+For each EU-index value, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015} five-factor model.
 In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
@@
   caption="Long-run abnormal returns five factor monthly abnormal returns after open market repurchase announcements for low and high Enhanced Undervaluation (EU) Index companies over different time periods.
-We define low EU-index firms those for which the EU-index is 0-1, and high for which it is 5-6 (note that the index takes values from 0 to 6).
+We define low EU-index firms those for which the EU-index is 0-3, and high for which it is 4-6 (note that the index takes values from 0 to 6).
 IRATS five factor cumulative abnormal returns after open market repurchase announcements for each EU-index value from 0 to 6.
@@
   caption="Long-term monthly abnormal returns after open market repurchase announcements for low and high Enhanced Undervaluation (EU) Index companies over different time periods.
-We define low EU-index firms those for which the EU-index is 0-1, and high for which it is 5-6 (note that the index takes values from 0 to 6).
+We define low EU-index firms those for which the EU-index is 0-3, and high for which it is 4-6 (note that the index takes values from 0 to 6).
 We calculate the EU-index simply as the sum of three numbers:  high \\cite{PeyerVermaelen2009} U-index terms get a score of 2, low get a 0; high idiosyncratic terms get a score of 2, low get a 0; and high volatility terms get a score of 2, low get a 0.
 Firms that get neither 0 nor 2 (hence are in the middle of the range) get a score of 1 for each of these 3 scores.
-For each EU-index value, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+For each EU-index value, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015} five-factor model.
 In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
@@
 )
+@
+
+\clearpage
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+printLatexTable2(
+  cbind(EU_IRATStableBB,Stam_IRATStableBB)[reported_times,],
+  Stam_IRATStable_EU_BB[reported_times,],
+  columns= c("Low EU","High EU","Low Mispr.","High Mispr."),
+  columns2= c("Low Mispr./Low EU","Low Mispr./High EU","High Mispr./Low EU","High Mispr./High EU"),
+  title="Buyback for Low and High EU-index and  for Low and High Mispricing measure companies",
+  title1 = "Panel A: IRATs Cumulative Abnormal Returns using single-sorting",
+  title2 = "Panel B: IRATs Cumulative Abnormal Returns using double-sorting",
+  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high EU-index and for low and  Misprising measure (of Stambaugh et al.
+(2015)) companies.
+Monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015} five-factor model for the sample of firms that announced an open market share repurchase are reported.
+The following regression is run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
+label = "tbl:EUvsStambaughBB",
+bigtitleontop=T,
+titleontop=T,
+metric1 = "CAR",
+metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=T
+)
+
 @
@@
 
-\begin{figure}[H]
-\centering
+%\begin{figure}[H]
+%\centering
 << BBISSevents, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
 #par(mfrow=c(2,1), mar=c(3.8,4,3.8,4))
-
+if (0){
   market_index = 100*(1+cumprod(1+Market_Monthly[names(Market_Monthly) >= "1985-01-01"]))
@@
   }
-@
-\caption{Buybacks with a follow-up equity issue within 48 months.
+}
+@
+%\caption{Buybacks with a follow-up equity issue within 48 months.
 We show the percent of announced buyback events each year, that had a follow-up issue within 48 months after the event.
@@
 %Top figure is buybacks and bottom is SEOs.
-}
-\label{fig:BBISSevents}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[H]
-\centering
+%}
+%\label{fig:BBISSevents}
+%\end{figure}
+
+%\clearpage
+%\begin{figure}[H]
+%\centering
 << BBISSpnl, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
+if (0){
   reported_times_plots_tmp = reported_times_plots
@@
   }
-@
-\caption{ Buybacks followed by equity issues within 48 months. 
-Top Panel~A:  Five factor IRATS CAR for all buyback events that had (with hindsight) no subsequent SEO event within the 48 months post buyback announcement (solid line) versus those that did have (dashed line).
+
+}
+@
+%\caption{ Buybacks followed by equity issues within 48 months. 
+%Top Panel~A:  Five factor IRATS CAR for all buyback events that had (with hindsight) no subsequent SEO event within the 48 months post buyback announcement (solid line) versus those that did have (dashed line).
 Bottom Panel~B: Abnormal (five-factor rolling hedged) returns of buybacks portfolio for only the \Sexpr{length(BB_with_ISS_later)} events for which there was a subsequent issue within 4 years.
@@
 Dashed line is if we exit these positions  the month after the subsequent buyback announcement  (Average annual returns: \Sexpr{round(pnl_stats(ISS_BB_Exit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(ISS_BB_Exit_Hedged)[3],1)}), and solid line is if we do not (Average annual returns: \Sexpr{round(pnl_stats(ISS_BB_NoExit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(ISS_BB_NoExit_Hedged)[3],1)}).
-}
-\label{fig:BBISSexit}
-\end{figure}
+%}
+%\label{fig:BBISSexit}
+%\end{figure}
 
@@
 
-\begin{figure}[H]
-\centering
+%\begin{figure}[H]
+%\centering
 << fig.width=8, fig.height=5, out.width='\\textwidth', echo=F >>=
-par(mfrow=c(2,2), mar=c(2.7,4,2.7,4))
 
@@
 R2_IRATStable_underBB_plot[rownames(R2_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)] <- -R2_IRATStable_underBB_plot[rownames(R2_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)]
+
+if (0){
+par(mfrow=c(2,2), mar=c(2.7,4,2.7,4))
 
@@
 abline(h=0, lwd=0.5)
-
-@
-\caption{Long-run five factors cumulative average abnormal returns (IRATS) of high (solid line) and low (dashed line) idiosyncratic buybacks.
+}
+@
+%\caption{Long-run five factors cumulative average abnormal returns (IRATS) of high (solid line) and low (dashed line) idiosyncratic buybacks.
 The x-axis indicates months from the date of the event announcement.
 Panel~A shows only the high  U-index companies, Panel~B  the low U-index ones, and bottom Panel C includes the whole sample.}
-\label{fig:pastallidio}
-\end{figure}
+%\label{fig:pastallidio}
+%\end{figure}
 
@@
 VOL_IRATStable_underBB_plot[rownames(VOL_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)] <- -VOL_IRATStable_underBB_plot[rownames(VOL_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)]
+
+if (0){
+par(mfrow=c(2,2), mar=c(2.7,4,2.7,4))
 
@@
 abline(h=0, lwd=0.5)
-
-@
-\caption{Volatility and the U-index.
+}
+@
+%\caption{Volatility and the U-index.
 Long-run five factors cumulative average abnormal returns (IRATS) of high (solid line) and low (dashed line) volatility buybacks.
@@
 Panel~A shows only the high  U-index companies, Panel~B  the low U-index ones, and bottom Panel C includes the whole sample.}
-\label{fig:pastallVOL}
-\end{figure}
+%\label{fig:pastallVOL}
+%\end{figure}
 
@@
 Returns of five-factor rolling hedged portfolio for only the buyback events for high and low EU-index companies.
-We define low EU-index firms those for which the EU-index is 0-1, and high for which it is 5-6 (note that the index takes values from 0 to 6).
+We define low EU-index firms those for which the EU-index is 0-3, and high for which it is 4-6 (note that the index takes values from 0 to 6).
 Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio; dashed line is ``high'' and a 48-months holding portfolio, dotted-dash line is ``low'' and a 48-months portfolio.
@@
 \bibliographystyle{jf}
-\bibliography{Bibliography}
+\bibliography{BibliographyInitname}
 
@@
 
-%%%% LARGE FIRMS ANALYSIS NOW
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% OLD TABLES IN CASE WE NEED THEM AGAIN
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\clearpage
 
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+if (0){
   printLatexTable2(
-  VOL_large_IRATStableBB[reported_times,],
-  VOL_large_IRATStableBB_cal[reported_times,],
-  columns= c("Low Vol.","High Vol."),
-  title="Buyback for Low and High Volatility for Large Firms only",
+    Exit_on_SEO_Abn_table[reported_times,],
+    Exit_on_SEO_Abn_table_cal[reported_times,],
+    columns = c("No Issue","Issue"),
+    title="Buybacks with and without subsequent issue",
     title1 = "Panel A: IRATs Cumulative Abnormal Returns",
     title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+    caption="The table presents the long-run abnormal returns for firms repurchase announcements for events with and without a subsequent SEO announcement.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
 The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015} five-factor model.
 In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
@@
 The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:VOLlargeunderBB",
+
+label = "tbl:BBISSexit",
 bigtitleontop=T,
@@
 lastSpecial=T,
-dorotate=T
-)
-@
-
+dorotate=F
+  )
+}
+
+if (0){
+  colnames(ISS_for_BB_Abn_table)[1]<- "Post-buyback SEOs"
+  colnames(ISS_for_BB_Abn_table)[4]<- "Other SEOs"
+  printLatexTable(ISS_for_BB_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
+                  label  = "tbl:BBISSexitAfter",
+                  columns= c("After a Buyback","No Prior Buyback"),
+                  title  ="Issue announcements with and without a prior buyback",
+                  caption = "The table presents the long-run abnormal returns (CAR) for firms after issue announcements for events with and without a prior buyback announcement within 48 months.
+We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+The following regression is run each event month~$j$:
+\\begin{eqnarray*}
+(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
+\\end{eqnarray*}
+where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
+$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
+${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
+The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
+The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.",
+
+lastSpecial=T,
+titleontop = T
+  )
+}
+@
+
+%%%%%%%%
+
+%\clearpage
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+if (0){
   printLatexTable2(
-  VOL_large_IRATStableBB_time[reported_times,],
-  VOL_large_time_cal[reported_times,],
-  columns= colnames(VOL_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High Volatility for Large Firms only over Time",
+    Exit_on_BB_Abn_table[reported_times,],
+    Exit_on_BB_Abn_table_cal[reported_times,],
+    columns = c("No Buyback","Buyback"),
+    title="SEOs with and without subsequent buyback",
     title1 = "Panel A: IRATs Cumulative Abnormal Returns",
     title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+    caption="The table presents the long-run abnormal returns for firms after issue announcements with and without a subsequent buyback announcement on the full sample for different periods in time.
+Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
 The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:VOLlargeunderBBTime",
+
+label = "tbl:ISSBBexit",
 bigtitleontop=T,
 titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
+scale=1,
+lastSpecial=T,
+dorotate=F
+  )
+
+  printLatexTable(BB_for_ISS_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
+                  label  = "tbl:ISSBBexitAfter",
+                  columns= c("post-Issue Buybacks: CAR","Other Buybacks: CAR"),
+                  title  ="Long-run IRATS abnormal return of only the buybacks that are announced within 48 months after an SEO announcement versus the remaining buyback events.",lastSpecial=T)
+}
+@
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+
+if (0){
+  tmp = ISStable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
+  colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2015: CAR","t-stat","p-value","2008-2015: CAR","t-stat","p-value")
+  tmp2 = ISStable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
+  colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2015: CAL","t-stat","p-value","2008-2015: CAL","t-stat","p-value")
+
+  printLatexTable2(
+    tmp,
+    tmp2,
+    columns= c("1985-1990","1991-2000","2001-2015","2008-2015"),
+    title="SEOs returns over different time periods",
+    title1 = "Panel A: IRATs Cumulative Abnormal Returns",
+    title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
+    caption="Long-run IRATS cumulative (Panel~A) and Calendar method monthly (Panel~B) abnormal return after issue announcements for different time periods.",
+    label = "tbl:PastFindingsTimeISS",
+    bigtitleontop=T,
+    titleontop=T,
     scale=1,
@@
   )
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% TO REMOVE LATER
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+}
+
+if (0){
+one_table = cbind(BBtable_undertime[,7:12],BB_cal_table_undertime[,7:12],
+                  BBtable_undertime[,19:24],BB_cal_table_undertime[,19:24],
+                  BBtable_undertime[,31:36],BB_cal_table_undertime[,31:36],
+                  BBtable_undertime[,43:48],BB_cal_table_undertime[,43:48]
+)
+#one_table = BBtable_undertime
+printLatexTable(one_table[reported_times,1:12],
+                columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),
+                rowcolumn="1985-1990",
+                title="Buyback returns for the U-index over time",
+                caption="The table presents the long-run abnormal returns for firms after open market repurchase announcements for high and low U-index firms in different time periods and shows significantly larger returns by buybacks announced by high U-index firms compared to those with a low U-index.
+We report both the IRATS cumulative average abnormal returns (CAR, Panel~A) and the calender time method (AR, Panel~B) abnormal returns on the full sample.
+$t$-Statistics are provided and stars indicate significance at the $5\\%$ (*), and $1\\%$ level (**).
+\\\\",
+                label="tbl:PastFindingsTimeUnderBB",metric=c("CAR", "CAR", "AR", "AR"),
+                scale = 1,close=F,lastSpecial=T
+)
+printLatexTable(one_table[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
+printLatexTable(one_table[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
+printLatexTable(one_table[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
+
+}
+
+if (0){
+  paste(printLatexTable(BB_cal_table_undertime[reported_times,1:12],
+                        columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),
+                        rowcolumn="1985-1990",
+                        title="Calendar Method abnormal returns after open market repurchase announcements  for under and over valued companies over different time periods.",
+                        label="tbl:PastFindingsTimeUnderBBcal",
+                        scale = 0.8,close=F,lastSpecial=T
+  ),
+  printLatexTable(BB_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
+  printLatexTable(BB_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
+  printLatexTable(BB_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
+
+}
+
+if (0){
+  paste(printLatexTable(ISStable_undertime[reported_times,1:12],
+                        columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),
+                        rowcolumn="1985-1990",
+                        title="Long-run IRATS abnormal returns after issue announcements  for under and over valued companies over different time periods.",
+                        label="tbl:PastFindingsTimeUnderISS",
+                        scale = 0.9,close=F,lastSpecial=T
+  ),
+  printLatexTable(ISStable_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
+  printLatexTable(ISStable_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
+  printLatexTable(ISStable_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
+
+  paste(printLatexTable(ISS_cal_table_undertime[reported_times,1:12],
+                        columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),
+                        rowcolumn="1985-1990",
+                        title="Calendar Method abnormal returns after issue announcements  for under and over valued companies over different time periods.",
+                        label="tbl:PastFindingsTimeUnderISScal",
+                        scale = 0.9,close=F,lastSpecial=T
+  ),
+  printLatexTable(ISS_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
+  printLatexTable(ISS_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
+  printLatexTable(ISS_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
+}
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% INDUSTRIES ANALYSIS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
 
 <<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+if (0){
+tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
+tmp_cal = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,4:6] ))
+
   printLatexTable2(
-  IVOL_large_IRATStableBB_time[reported_times,],
-  IVOL_large_time_cal[reported_times,],
-  columns= colnames(IVOL_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High IVOL for Large Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
+    tmp[reported_times,1:(3*6)],
+    tmp[reported_times,(3*6+1):36],
+    columns= names(industry_BB)[1:6],
+    columns2= names(industry_BB)[7:12],
+    title="Buyback IRATS Abnormal Returns: Industry Robustness",
+    #title1 = "",
+    #title2 = "",
+    caption=paste("The table presents the long-run abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample.
+We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
 The following regression is run each event month~$j$:
@@
 The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:IVOLlargeunderBBTime",
+The 48 month abnormal return for the full sample is equal to ",round(IRATS_table_all_bb["+48","CAR 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),
+
+label = "tbl:IndustriesBB",
 bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
+metric1 = "CAR", metric2 = "CAR",
+#titleontop=T,
 scale=1,
@@
   )
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
+
   printLatexTable2(
-  Idio_large_IRATStableBB_time[reported_times,],
-  Idio_large_time_cal[reported_times,],
-  columns= colnames(Idio_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High Idiosyncratic for Large Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
+    tmp_cal[reported_times,1:(3*6)],
+    tmp_cal[reported_times,(3*6+1):36],
+    columns= names(industry_BB)[1:6],
+    columns2= names(industry_BB)[7:12],
+    title="Buyback Calendar Method Abnormal Returns: Industry Robustness",
+    #title1 = "",
+    #title2 = "",
+    caption=paste("The table presents the long-run calendar method abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample.
+Specifically, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015} five-factor model.
 In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:IdiolargeunderBBTime",
+A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors (the difference between the risk-free rate and the return on the equally weighted CRSP index, the monthly return on the size, book-to-market factor, profitability factor and investment factor in month) as the independent variables.
+The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
+The 48 month abnormal return for the full sample is equal to ",round(CAL_table_all_bb["+48","CAL 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),
+    label = "tbl:IndustriesBB_cal",
     bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
+    metric1 = "AR", metric2 = "AR",
+    #titleontop=T,
     scale=1,
@@
   )
+
+}
 @
@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  Uindex_large_IRATStableBB_time[reported_times,],
-  Uindex_large_time_cal[reported_times,],
-  columns= colnames(Uindex_large_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High U-index for Large Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:UindexlargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-%%%%%%%%%
-
+if (0){
+  latex_render_data_frame(
+    pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)), 
+    title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all buybacks",
+    caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all buybacks.
+The holding period for each buyback is 12 months per event.",
+    label="tbl:allhedgedBB", 
+    columns=NULL,
+    bigtitleontop = T,
+    show_rownames=TRUE,
+    scale = 0.9,
+    digits=1,
+    lastSpecial=F,dorotate=F
+  )
+}
+@
+
+\small
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  VOL_small_IRATStableBB_time[reported_times,],
-  VOL_small_time_cal[reported_times,],
-  columns= colnames(VOL_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High Volatility for Small Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:VOLlargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  IVOL_small_IRATStableBB_time[reported_times,],
-  IVOL_small_time_cal[reported_times,],
-  columns= colnames(IVOL_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High IVOL for Small Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:IVOLlargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  Idio_small_IRATStableBB_time[reported_times,],
-  Idio_small_time_cal[reported_times,],
-  columns= colnames(Idio_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High Idiosyncratic for Small Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:IdiolargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-printLatexTable2(
-  Uindex_small_IRATStableBB_time[reported_times,],
-  Uindex_small_time_cal[reported_times,],
-  columns= colnames(Uindex_small_IRATStableBB_time)[c(1,4,7,10,13,16)],
-  title="Buyback for Low and High U-index for Small Firms only over Time",
-  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-  caption="This table presents the long-term abnormal return after open market repurchase announcements from the announcement date until $t$ months after, for low and high volatility large companies only.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-label = "tbl:UindexlargeunderBBTime",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=T
-)
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% TO REMOVE TILL HERE 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+if (0){
+
+tmp = industry_BB_features[,c(1:4,9:12)]
+if (colnames(tmp)[1] == "H Idsync.")
+  colnames(tmp) <- paste(colnames(tmp), " (",1:ncol(tmp), ")",sep="")
+latex_render_data_frame(
+  round(tmp,1), 
+  title = "Industry Characteristics",
+  caption="Percentage of high and low idiosyncratic risk  and volatility companies for all industries for which we have at least 100 events in our sample.",
+  label = "tbl:industriesR2Vol",
+  columns=NULL,
+  bigtitleontop = T,
+  show_rownames=TRUE,
+  scale = 1,
+  digits=1,
+  lastSpecial=F,dorotate=T
+)
+}
+@
+\normalsize

### 2017-02-08 bb_issuers_new.R

@@ -9,10 +9,12 @@
 
 rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
 
-source("lib_helpers.R", chdir=TRUE)
-source("latex_code.R")
-source("ff_industries_sic.R")
+source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
+source("../FinanceLibraries/latex_code.R")
+source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
 source("Paper_global_parameters.R")
+
+rm("three_factor_model", "five_factor_model")
 
 initial_vars = ls(all = TRUE) # takes time to save and load, so we save only what is needed at the end. 
 
@@ -24,10 +26,10 @@ if (continuous_valuation_index){
     ifelse(is.na(BUYBACK_DATA$DATASET$CRSP$Market.Cap_score), NA, (1-BUYBACK_DATA$DATASET$CRSP$Market.Cap_score)) + 
     ifelse(is.na(BUYBACK_DATA$DATASET$CRSP$BE.ME_score), NA, BUYBACK_DATA$DATASET$CRSP$BE.ME_score)
   
-  ISSUERS_DATA$Valuation_Index = 
-    ifelse(is.na(ISSUERS_DATA$DATASET$CRSP$recent_performance_score), NA, (1-ISSUERS_DATA$DATASET$CRSP$recent_performance_score)) +
+  ISSUERS_DATA$Valuation_Index =  # THIS IS AN OVERVAUATION INDEX: THE HIGHER, THE MORE OVERVALUED: High Perf + Low Size + Low B/M
+    ifelse(is.na(ISSUERS_DATA$DATASET$CRSP$recent_performance_score), NA, (ISSUERS_DATA$DATASET$CRSP$recent_performance_score)) +
     ifelse(is.na(ISSUERS_DATA$DATASET$CRSP$Market.Cap_score), NA, (1-ISSUERS_DATA$DATASET$CRSP$Market.Cap_score)) + 
-    ifelse(is.na(ISSUERS_DATA$DATASET$CRSP$BE.ME_score), NA, ISSUERS_DATA$DATASET$CRSP$BE.ME_score)
+    ifelse(is.na(ISSUERS_DATA$DATASET$CRSP$BE.ME_score), NA, (1-ISSUERS_DATA$DATASET$CRSP$BE.ME_score))
   
 } else {
   ###############################################################
@@ -52,10 +54,13 @@ if (continuous_valuation_index){
[…]

### 2017-02-08 filter_bbissuers_data.R

@@ -33,6 +33,7 @@ if (length(to_remove) > 0){
   BUYBACK_DATA$DATASET$returns_by_event_monthly <- BUYBACK_DATA$DATASET$returns_by_event_monthly[,-to_remove]
   BUYBACK_DATA$DATASET$SDC <- BUYBACK_DATA$DATASET$SDC[-to_remove,]
   for(field in ls(BUYBACK_DATA$DATASET$CRSP))  BUYBACK_DATA$DATASET$CRSP[[field]] <- BUYBACK_DATA$DATASET$CRSP[[field]][-to_remove]
+  for(field in ls(BUYBACK_DATA$DATASET$institutional))  BUYBACK_DATA$DATASET$institutional[[field]] <- BUYBACK_DATA$DATASET$institutional[[field]][-to_remove]
   for(field1 in ls(BUYBACK_DATA$DATASET$ibes))  
     for (field in ls(BUYBACK_DATA$DATASET$ibes[[field1]])) 
       BUYBACK_DATA$DATASET$ibes[[field1]][[field]]<- BUYBACK_DATA$DATASET$ibes[[field1]][[field]][-to_remove]
@@ -84,6 +85,7 @@ if (remove_missing_permnosV2){
     BUYBACK_DATA$DATASET$returns_by_event_monthly <- BUYBACK_DATA$DATASET$returns_by_event_monthly[,-to_remove]
     BUYBACK_DATA$DATASET$SDC <- BUYBACK_DATA$DATASET$SDC[-to_remove,]
     for(field in ls(BUYBACK_DATA$DATASET$CRSP))  BUYBACK_DATA$DATASET$CRSP[[field]] <- BUYBACK_DATA$DATASET$CRSP[[field]][-to_remove]
+    for(field in ls(BUYBACK_DATA$DATASET$institutional))  BUYBACK_DATA$DATASET$institutional[[field]] <- BUYBACK_DATA$DATASET$institutional[[field]][-to_remove]
     for(field1 in ls(BUYBACK_DATA$DATASET$ibes))  
       for (field in ls(BUYBACK_DATA$DATASET$ibes[[field1]])) 
         BUYBACK_DATA$DATASET$ibes[[field1]][[field]]<- BUYBACK_DATA$DATASET$ibes[[field1]][[field]][-to_remove]
@@ -133,7 +135,7 @@ major_markets_only = sapply(events$SDC$Stock.Exchange, function(i) sum(str_split
[…]

### 2017-02-17 manuscript.Rnw
clean up

@@
 if (generate_all_data == 1){
-  source("create_bbissuers_data.R")
+  source("create_project_data.R")
 }
 if (generate_rnw_data == 1){
-  source("bb_issuers_new.R")
+  source("process_project_data.R")
 } else {
-  load("bb_issuers_new.Rdata")
+  load("processed_project_data.Rdata")
 }
@@
 \doublespacing
-% Use endnotes instead of footnotes - redefine \footnote command
-%\renewcommand{\footnote}{\endnote}  % Endnotes instead of footnotes
 
@@
 
-%Why does the \cite{StambaughYuan2016} four factor model does a poor job explaining the buyback anomaly?
-The reason, we believe, is that the buyback anomaly is inconsistent with some of the major 11 anomalies used to construct the \cite{Stambaugh2015} mispricing index.
-For example, long-term excess returns after buyback announcements are negatively related to the returns in the 6 months prior to the buyback.
-As buyback stocks have negative momentum before the announcement, the momentum anomaly \citep{JegadeeshTitman1993} predicts lower returns not higher returns.
-Similarly, \cite{PeyerVermaelen2009} find that the most undervalued buyback stocks miss earnings forecast, which is the opposite of the \cite{Mendenhall2004} earnings drift anomaly which predicts negative excess returns after missing earnings forecasts.
-
 Having shown that the buyback anomaly survives the most recent factor models,  we address the second major question in this paper: are excess returns related to volatility?
@@
 
-%The prediction of the costly arbitrage hypothesis is that there is a positive relation between volatility and excess returns after buybacks and a negative relation between volatility and excess returns after equity issues.
-While the first hypothesis is confirmed by the data, the second one is not.
-The results are more consistent with the options hypothesis of \cite{IkenberryVermaelen1996} who point out that open market repurchase authorizations are options to repurchase stock, not firm commitments.
-As a result, they predict that announcement returns should be positively related to volatility.
-
-%Moreover, because limits to arbitrage are higher among overvalued stocks (e.g.
-most investors are reluctant or unable to short stocks) the negative volatility effect among overvalued stocks should be stronger than the positive volatility effect among undervalued stocks.
-Indeed, \cite{Bravetal2010} find that the limits to arbitrage can explain some overvaluation anomalies but not undervaluation anomalies.
-So whether the costly arbitrage hypothesis can explain the buyback anomaly and/or the new equity issue anomaly is an empirical question.
-%The prediction of the costly arbitrage hypothesis is that there is a positive relation between volatility and excess returns after buybacks and a negative relation between volatility and excess returns after equity issues.
-While the first hypothesis is confirmed by the data, the second one is not.
-The results are more consistent with the options hypothesis of \cite{IkenberryVermaelen1996} who point out that open market repurchase authorizations are options to repurchase stock, not firm commitments.
-As a result, they predict that announcement returns should be positively related to volatility.
-Note that as equity issues are firm commitments, no such volatility effect is predicted.
-We also argue that the market timing hypothesis implicitly assumes that managers have superior knowledge about company-specific information, not the overall market.
-Hence the prediction of the information advantage hypothesis is that buyback announcements of firms with high standardized idiosyncratic volatility, measured by (1-$R^2$), will also generate higher long term excess returns.
-Indeed, it measures to what extent the volatility of stock returns is explained by company-specific (non-factor related) information [see also \citep{LiRajgopaletal2014}].
-
 After documenting that volatility as well as standardized idiosyncratic volatility are positively related to long-term excess returns after buybacks we test whether these variables can improve our ability to predict long-term excess returns, above the predictive ability of the undervaluation index (U-index) developed by \cite{PeyerVermaelen2009}.
@@
 This again shows that the 11 anomaly indicators that may be relevant for average stocks don't apply to buyback stocks.
-
-%The fact that the buyback anomaly survives could still mean that the ''excess'' returns are compensating for some risks that the Fama-French 5-factor model does not account for - and is not related to any information advantage of company insiders.
-The third contribution of this paper is to provide further support for the hypothesis that excess returns after buybacks can be explained by information asymmetry rather than a risk-based story.
-One way to show that these excess returns reflect adjustment to undervaluation is to show that they are positively correlated with observable indicators of potential undervaluation and/or information advantage of the management.
-\cite{IkenberryLakonishokVermaelen1995} assume that value stocks are more likely to be undervalued than growth stocks.
-The fact that they find a positive relation between long-term excess returns and book-to-market supports the undervaluation hypothesis.
-The undervaluation index of \cite{PeyerVermaelen2009} assumes that buybacks announced by beaten up small cap value firms are more likely to be driven by undervaluation than other firms.
-consider three new indicators (firm size, prior return and stated motivation in the press release) and combine them with the book-to-market indicator in an undervaluation index (U-index).
-Adding these additional indicators improves the predictability of excess returns, which is consistent with the undervaluation hypothesis.
-In this paper we test whether two new indicators, standardized idiosyncratic volatility (measured by 1-$R^2$) and volatility can improve our understanding of excess returns by combining them with the U-index of \cite{PeyerVermaelen2009}.
-
-%It remains a fact though that the buyback anomaly is to some extent a small firm anomaly, as also found by \cite{PeyerVermaelen2009}: indeed, we find that value-weighting all the events [as suggested by \cite{MitchellStafford2000}] makes the (Calendar Time event study method) alphas disappear.
-However, if we exclude the firms in the largest size quartile, the anomaly persists (also for the Calendar Time event study method).
-This makes sense as small firms are more opaque and less followed by analysts.
-They also tend to be held more by insiders, so that in these case share buybacks are more similar to insider buying with company funds.
-If anything, to increase the power of the test to detect mispricing and the possibility that managers (at least in some firms) can time the market based on their information advantage relative to investors, any weighting should be based on the inverse of size.
-The fact that excess returns disappear when we value weight provides further support for the hypothesis that excess returns are driven by information asymmetry for some firms.
-The fact that this is a small cap anomaly may partly explain why this anomaly persists after 30 years and has attracted very little attention in the asset management industry.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA.
-The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization.
-We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.}  Indeed because management fees are proportional to fund size one expects relatively less interest in anomalies concentrated in small caps or microcaps.
 
@@
 
-%Finally, we show that adding volatility and standardized idiosyncratic volatility to the factors proposed by previous research as undervaluation proxies and combining them in an Enhanced Undervaluation index improves our forecasting ability of excess returns after buyback authorization announcements.
-As a theoretical argument can be made that both measures are proxies for the competitive information advantage of managers-insiders, this strengthens the support for the undervaluation and market timing hypothesis.
-However, it should be noted that the anomaly is more pronounced in small firms, which may explain why this anomaly has attracted little attention in the asset management industry.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%% OLD INTRO
-
-%We study whether previously reported positive (negative) excess returns following share buyback (equity issue) announcements\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}.
-For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.} are compensation for risk using recently proposed risk models [specifically from \cite{FamaFrench2015} or \cite{Houetal2015}], or evidence for possible market timing by insiders of undervalued (overvalued) firms who may take advantage of information asymmetries.
-We also explore the impact of firm specific or total volatility on excess returns, as theoretical arguments can be made that high volatility makes arbitrage for outsiders costlier.
-Specifically, the first purpose of this paper is to test whether there is a link between two well-known anomalies: the net issue anomaly, i.e.
-the fact that share buybacks (equity issues) are followed by long run positive (negative) excess returns, and the volatility anomaly, i.e.
-the fact that (idiosyncratic) volatility is negatively related to expected returns \citep{Ang2006}.
-This link is plausible considering the fact that \cite{Stambaugh2015} find that the relation between idiosyncratic volatility, measured as residual variance, and future returns reverses and becomes {\it positive} for undervalued stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.} They argue that their result is consistent with the {\it costly  arbitrage hypothesis}: idiosyncratic volatility represents risk that deters arbitrage and the resulting reduction in mispricing, hence among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.
-As the positive (negative) long run returns after buybacks (equity issues) are generally interpreted as evidence of undervaluation (overvaluation) that firm insiders may take advantage of, we would predict also a positive (negative) relation between volatility and future returns after firms announce a buyback (equity issue): volatility may also make it easier for insiders to take advantage of undervaluation (overvaluation) based on an information advantage on the one hand and the challenge for outsiders to correct mispricing due to higher arbitrage costs on the other hand.
-
-%Moreover, \cite{Stambaugh2015} argue that, because limits to arbitrage are higher among overvalued stocks (e.g.
-most investors are reluctant or unable to short stocks) the negative volatility effect among overvalued stocks should be stronger than the positive volatility effect among undervalued stocks.
-Indeed, \cite{Bravetal2010} find that the limits to arbitrage can explain some overvaluation anomalies but not undervaluation anomalies such as the fact e.g.
-that positive earnings surprises are followed by positive excess returns.
-So whether the costly arbitrage hypothesis is also related to the buyback undervaluation anomaly is ultimately an empirical question.
-
-%The second purpose of this paper is to test whether the buyback and equity issue anomalies still exist and are not simply a proxy for risk, or have disappeared in recent years as has happened with other ones~\citep{McLean2016}.
-Unlike past work, we do so by both using the more recent \cite{FamaFrench2015} five-factor  model, for buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, and using event announcement dates and separating equity issues and buybacks.\footnote{Using throughout this paper the q-factor model of \cite{Houetal2015} instead of the five-factor model of \cite{FamaFrench2015} leads to the same conclusions.
-Results available upon request.
-} Excess returns in previous research are calculated using different benchmarks such as firms with similar size and book-to-market ratio \citep{IkenberryLakonishokVermaelen1995} or the \cite{FamaFrench1993} three-factor model or the \cite{Carhart1997} 4-factor model \citep{PeyerVermaelen2009}.
-However, \cite{FamaFrench2016}  argue that many anomalies are weakened or do not survive after using the more recent \cite{FamaFrench2015} five-factor asset pricing model as a model of expected returns.
-This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns \citep{NovyMarx2013}.
-They find that the volatility anomaly survives for small firms, but the net issue anomaly (i.e.
-equity issues minus buybacks) does not.
-If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research.
-
-%Moreover, \cite{FamaFrench2016} do not exactly replicate the papers that first reported the anomalies.
-Indeed, unlike the authors that ''discovered'' the anomalies they do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues).
-The part of their sample where net equity issues are positive is defined as the ''buyback sample''.
-But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations.
-Moreover, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date of the buyback authorization as is done in previous research [e.g., \cite{PeyerVermaelen2009}].
-For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization, or not completed at all \citep{StephensWeisbach1998}.
-This slow execution is partially driven by SEC regulations designed to minimize the impact on trading volume as well as tactical considerations.
-This may produce another downward bias in post-repurchase excess returns.
-For example, assume the stock price today is \$10 and the management believes its stock is undervalued and announces a typical buyback program for 7$\%$ of its outstanding shares.
-Suppose that one year later 2$\%$ of the shares are repurchased and the market corrects the undervaluation so that the company halts the program.
-At the end of the first year the firm is considered as a net repurchaser in the \cite{FamaFrench2016} sample, and no long-term excess return will be observed afterwards even though there were excess returns during the first post-announcement year.
-
-%Pooling buybacks and equity issues in a ''net issues'' measure assumes that the decision to issue equity is simply the mirror of buying back shares.
-This ignores two other major differences between repurchases and equity issues (besides the fact that a buyback program is an option, not a firm commitment as an equity issue).
-First, in an open market repurchase the seller is not aware she is selling to the corporation, while in an equity issue the investor knows that the company is the issuer.
-Obviously this makes it easier to buy back undervalued shares than to issue overvalued shares.
-Second, issuing overvalued shares to new investors may hurt relations with these investors.
-One of the arguments for IPO underpricing is that it creates a positive experience for investors making it easier to convince them to buy new shares in a follow up secondary offering \citep{Ibbotson1975}.
-Issuing overvalued stock creates a negative experience for new investors.
-On the other hand, repurchasing undervalued shares from investors who have decided to sell their shares anyway should not create an investor relations problem.
-So in order to test the buyback and equity issue anomalies one has to examine them separately, using announcement dates as we do in this paper.
-
-%We confirm the \cite{FamaFrench2016} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant.
-The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2016}.
-As we find that only the buyback anomaly survives, this paper focuses on buybacks, not equity issues.
-
-%The fact that the buyback anomaly survives could still mean that the ''excess'' returns are compensating for some risks that the Fama-French 5-factor model does not account for - and is not related to any information advantage of company insiders.
-The third contribution of this paper is to provide further support for the hypothesis that excess returns after buybacks can be explained by information asymmetry rather than a risk-based story.
-One way to show that these excess returns reflect adjustment to undervaluation is to show that they are positively correlated with observable indicators of potential undervaluation and/or information advantage of the management.
-\cite{IkenberryLakonishokVermaelen1995} assume that value stocks are more likely to be undervalued than growth stocks.
-The fact that they find a positive relation between long-term excess returns and book-to-market supports the undervaluation hypothesis.
-\cite{PeyerVermaelen2009} consider three new indicators (firm size, prior return and stated motivation in the press release) and combine them with the book-to-market indicator in an undervaluation index (U-index).
-Adding these additional indicators improves the predictability of excess returns, which is consistent with the undervaluation hypothesis.
-In this paper we test whether two new indicators, standardized idiosyncratic volatility (measured by $1-R^2$) and volatility can improve our understanding of excess returns by combining them with the U-index of \cite{PeyerVermaelen2009}.
-
-%An indicator that measures the competitive information advantage of managers is standardized idiosyncratic volatility, measured by $(1-R^2)$ where $R^2$ is, for example, that of a regression of the 6-months pre-announcement daily returns of the stock on the five factors of \cite{FamaFrench2015}.\footnote{Note that standardized idiosyncratic volatility differs from residual variance which is the measure of idiosyncratic volatility used in the volatility literature.
-Because of the high correlation between residual variance and total volatility (\Sexpr{round(100*cor(BUYBACK_DATA$DATASET$CRSP$pre_vol, BUYBACK_DATA$DATASET$CRSP$IVOL),2)}$\%$ in our sample) testing for the impact on volatility on stock returns is identical to testing for the impact of residual variance.
-Throughout this paper we use the term ''standardized idiosyncratic volatility'' to refer to $(1-R^2)$.} Indeed, it measures to what extent the volatility of stock returns is explained by company-specific (non-factor related) information [see also \citep{LiRajgopaletal2014}].
-The hypothesis that managers are able to time the market is based on the assumption that managers have superior knowledge about company-specific information, not the overall market.
-Hence the prediction of the {\it information advantage hypothesis} is that buyback announcements of firms with high standardized idiosyncratic volatility $(1-R^2)$ will also generate higher long term excess returns.
-
-%Adding (raw) volatility as a factor that explains excess returns can be justified by the \cite{Stambaugh2015} {\it costly arbitrage hypothesis} but also by the {\it option hypothesis} proposed by \cite{IkenberryVermaelen1996}:  a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks.
-In other words, the potential of managers to take advantage of undervaluation increases with the uncertainty about its fundamentals.
-This option could be quite valuable as buyback authorizations are typically granted for several years and are often extended.
-If the market is efficient this option effect should be incorporated in the stock price at the time of the buyback announcement.
-Indeed, \cite{IkenberryVermaelen1996} find that short-term announcement returns are positively related to volatility.
-However, if markets underestimate the value of this option at the time of the buyback authorization, long term excess returns should be positively correlated with volatility.
-Note that, unlike the costly arbitrage hypothesis, this option hypothesis does not predict a relation between volatility and excess returns after equity issues which, unlike buyback authorizations, are firm commitments, not options.
-
-%We find a significant positive relation between excess returns and volatility as well as standardized idiosyncratic volatility.
-Combining total volatility and standardized idiosyncratic volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index (EU-Index) also improves the predictability of excess returns.
-In particular, during the four years following the buyback announcement, the high EU-Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
-Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.
-
-%It remains a fact though that the buyback anomaly is to some extent a small firm anomaly, as also found by \cite{PeyerVermaelen2009}: indeed, we find that value-weighting all the events [as suggested by \cite{MitchellStafford2000}] makes the (Calendar Time event study method) alphas disappear.
-However, if we exclude the firms in the largest size quartile, the anomaly persists (also for the Calendar Time event study method).
-This makes sense as small firms are more opaque and less followed by analysts.
-They also tend to be held more by insiders, so that in these case share buybacks are similar to insider buying with company funds.
-If anything, to increase the power of the test to detect mispricing and the possibility that managers (at least in some firms) can time the market based on their information advantage relative to investors, any weighting should be based on the inverse of size.
-The fact that excess returns disappear when we value weight provides further support for the hypothesis that excess returns are driven by information asymmetry for some firms.
-At the same time the negative relation between size and alpha may partly explain why this anomaly persists after 30 years and has attracted very little attention in the asset management industry.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA.
-The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization.
-We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.}  Indeed because management fees are proportional to fund size one expects relatively less interest in anomalies concentrated in small caps or microcaps.
-
-%Summarizing, this paper makes three fundamental contributions.
-First we show that the buyback anomaly, but not the equity issue one, survives after using the 5-factor model of Fama and French if buybacks are separated from equity issues and excess returns are calculated after the authorization date.
-Second, in agreement with \cite{Stambaugh2015}, we find support for the  hypothesis that firms announce buybacks because they are undervalued and because of costly arbitrage there will be a positive relation between volatility and returns.
-The results are also consistent with the \cite{IkenberryVermaelen1996} option hypothesis.
-However, as the equity issue anomaly does not survive the Fama-French model we can't test the other prediction of \cite{Stambaugh2015}, i.e.
-that returns of overvalued firms will be negatively correlated with volatility and that this relation will be stronger for overvalued firms than undervalued firms.\footnote{Of course this does not mean that the \cite{Stambaugh2015} hypothesis is rejected as there could be other overvalued firms with a strong negative relation between excess returns and volatility.}  Finally, we show that adding volatility and standardized idiosyncratic volatility to the factors proposed by previous research as undervaluation proxies and combining them in an Enhanced Undervaluation index improves our forecasting ability of excess returns after buyback authorization announcements.
-As a theoretical argument can be made that both measures are proxies for the competitive information advantage of managers-insiders, this strengthens the support for the undervaluation and market timing hypothesis of some firms.
-
 So why does the buyback anomaly survive, unlike many of the 73 anomalies tested by \cite{StambaughYuan2016}?
@@
 For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.
-%\footnote{More information is available upon request.
-An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, will also be available at \href{http://tevgeniou.github.io/BuybacksIssuers/}{tevgeniou.github.io/BuybacksIssuers.}}
 We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both.
@@
 A similar decline in IPOs is also observed by \cite{GaoRitterZhu2013}.
-%Figure \ref{fig:industryeventsBB} shows the number of buyback events per industry in our sample. The software, retail and semiconductor industries are the most active repurchasers.
 
@@
 In particular, we test whether buyback (equity issue) announcements are followed by significant positive (negative) long term excess returns, and if so, whether the returns can be explained by proxies for undervaluation as proposed by \cite{PeyerVermaelen2009}.
-
-%\subsection{Share buybacks and Equity Issues in Isolation }
-%\label{sec:AbnormalBuybacks}
 
@@
 
-%The largest monthly excess return (\Sexpr{CAL_table_all_bb["+1","CAL 5F"]}$\%$) is earned by the portfolio that holds buyback stocks for one month  (not reported in Table \ref{tbl:priorBuybacks})  and the smallest excess return (\Sexpr{CAL_table_all_bb["+48","CAL 5F"]}$\%$) is earned by the portfolio that picks buybacks announced during the previous 48 months.
-This clearly shows that forming portfolios after buybacks are completed, as is done by measuring net issues in \cite{FamaFrench2016}, is introducing a downward bias as many repurchase programs are completed several months (sometimes years) after the buyback announcement.
-Waiting until the buyback is completed means missing the largest excess returns earned shortly after the buyback authorization.
-Finally, there are no statistically significant excess returns after equity issues, regardless whether we use the three or five-factor model.
-
-%So far all our events are equally weighted.
-\cite{MitchellStafford2000} argue that events should be value weighted to test whether they represent an economically important anomaly.
-However, as pointed out by Loughran and Ritter (2000), small firms are more likely to be mispriced as they are less followed by analysts.
-t Hence managers of small firms are better able  to take advantage of mispricing than managers of  large firms.
-So value weighting the events would simply bias the results toward zero.
-And indeed, when we value-weight the events (see Table \ref{tbl:valuetable} Panel~A) long-term excess returns become statistically insignificantly different from zero when using the total sample of events.
-So the buyback anomaly is not economically important and does not challenge the basic premise that ``the market'' represented by a value-weighted index is priced correctly.
-Note, however, if we eliminate the firms with are in the top $25^{th}$ market capitalization percentile (see Table \ref{tbl:valuetable}, Panel~B) the results become again significant.
-These firms had market capitalization less than \$\Sexpr{round(max(BUYBACK_DATA$DATASET$CRSP$Market.Cap[BUYBACK_DATA$DATASET$SDC$Event.Date >= "2015-01-01" & BUYBACK_DATA$DATASET$CRSP$Market.Cap_score < 0.75]))} million in 2015.
-The fact that the buyback anomaly is a small cap anomaly makes it more likely that excess returns are evidence that managers (at least in these firms) time the market based on their information advantage relative to investors.
-
 Table~\ref{tbl:priorBuybacks}, Panel A, shows the five-factor as well as the four-factor IRATS for high U-index and low U-index firms.
@@
 
-%Using IRATS, the 4 factor model produces significant positive excess returns of 12.66$\%$ after 4 years (t=5.24).
-With the calendar time method, the excess returns become less significant (t=1.81) but have the same magnitude (0.27$\%$ per month or 12.86$\%$ after 48 months).
-Clearly this is inconsistent with the idea that firms issue stock when they are overvalued.
-Our results are largely consistent with \cite{FamaFrench2016}.
-Using the three-factor model, we find statistically significant long term (after 48 months) negative cumulative excess returns of -7.40% (t=-3.36).
-However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months.
-Our results show that This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a “net issue” measure.
-Both events are clearly motivated by different reasons.
-As pointed out above, unlike buybacks, equity issues are firm commitments announced and completed at the same point in time, the buyer of the shares knows that the company is the issuer which makes trading against ”uninformed” investors more complicated and more controversial for a firm who wants to keep good relations with its long term investors.
-Note also that equity issues are typically preceded by large positive excess returns of around 37% in the 6 months prior to the equity issue.
-However, the lack of post announcement negative excess returns shows that this was not reflecting “irrational exuberance” but rather that, for example, these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.
-
-%shows a split according to volatility.
-We will return to this result next when we discuss the effect of volatility on returns in section 4.} using the same methodology as in Table~\ref{tbl:priorBuybacks}, Panel~A.
-Our results are largely consistent with \cite{FamaFrench2016}.
-Using the three-factor model, we find statistically significant long term (after 48 months) negative cumulative excess returns of \Sexpr{IRATS_table_all_iss["+48","CAR 3F"]}$\%$ (t=\Sexpr{IRATS_table_all_iss["+48",2]}).
-However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months.
-This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure.
-As pointed out above, unlike buybacks, equity issues are firm commitments announced and completed at the same point in time, the buyer of the shares knows that the company is the issuer which makes trading against ''uninformed'' investors more complicated and more controversial for a firm who wants to keep good relations with its long term investors.
-Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{floor(IRATS_table_all_iss[reported_times[1],4])}$\%$ in the 6 months prior to the equity issue.
-However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that, for example, these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.
-
-%Table~\ref{tbl:priorBuybacks}, Panel~A, shows the five-factor as well as the four-factor IRATS for high U-index and low U-index firms.
-The interesting conclusion is that using the five-factor model improves the predictive power of the U-index: high U-index firms earn 4 year excess returns of \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR5F"]}$\%$ (t=\Sexpr{IRATS_table_all_bb_undervaluation["+48",8]}) while low U-index firms only earn \Sexpr{IRATS_table_all_bb_undervaluation["+48","O:CAR5F"]}$\%$ (t=\Sexpr{IRATS_table_all_bb_undervaluation["+48",11]}), hence \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR5F"] - IRATS_table_all_bb_undervaluation["+48","O:CAR5F"]}$\%$ less than the high U-index ones.
-Starting from 24 months after the announcement, high U-index firms always beat low U-index firms.
-When we use the three-factor model, we find similar conclusions, but the results are weaker.
-For example after 48 months the high U-index firms now earn excess returns of \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR3F"]}$\%$, which is only \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR3F"] - IRATS_table_all_bb_undervaluation["+48","O:CAR3F"]}$\%$ higher than the low-U-index firms.
-Note that, consistent with \cite{PeyerVermaelen2009} the low U-index buyback stocks earn significant positive excess returns too.
-It is difficult to find a portfolio of buyback stocks that under-performs in the long run.
-So the term ``overvaluation'' should be interpreted with caution.
-The Undervaluation Index is a proxy for the likelihood that the buyback is driven by undervaluation.
-It does not imply that low U-index firms are overvalued.
-It means that for these firms the buyback is less likely to be driven by undervaluation, but by other reasons such as managing capital structure, avoiding dilution from executive stock options etc.
-
-%Table~\ref{tbl:priorBuybacks}, Panel~B, shows that this conclusion holds when we use the Calendar Time method.
-High U-index stocks almost always beat low U-index stocks.
-As in the case of IRATS, the five-factor model improves the selectivity of the Undervaluation Index: low U-index now earn marginally significant excess returns after 48 months.
-
-%Figure~\ref{fig:pastall} summarizes the IRATS results in more detail by showing the cumulative abnormal returns during the 6 month pre and 48 month post event period, using the five-factor model.
-Results are shown for the total sample of buybacks and equity issues, as well as for high and low U-index buyback samples.
-
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
@@
 How sensitive is it to the length of the investment period?
-%Could the anomaly be industry-specific?
 
@@
 Table~\ref{tbl:PastFindingsTimeBB} shows that, regardless of the time period chosen or the method to calculate excess returns, the buyback anomaly remains economically and statistically significant and there is no clear time trend in the data that suggests that markets have become more efficient over time.
-%For example, although the 2001-2015 period shows smaller timing ability than the 1990-2000 period, excess returns in the 2008-2015 period are as large as in the 1991-2000 period: approximately \Sexpr{BBtable_time["+48",22]}$\%$  after 4 years using IRATS or \Sexpr{BBtable_time_cal["+48",22]}$\%$ per month (\Sexpr{48*BBtable_time_cal["+48",22]}$\%$ after 4 years) when we use the Calendar Time method.
 There is one exception to the consistency between the IRATS and the Calendar Time results: in the period of 1991-2000, the IRATS method generates excess returns after 48 months of \Sexpr{BBtable_time["+48",10]}$\%$ (t=\Sexpr{BBtable_time["+48",11]}) but the Calendar Time method produces statistically insignificant excess returns of \Sexpr{BBtable_time_cal["+48",10]}$\%$ per month.
@@
 However, for all horizons and both factor models, all long-term excess returns become statistically insignificantly different from zero when we use the Calendar Time Method.
-
-%Table~\ref{tbl:PastFindingsTimeUnderBB} re-examines whether the U-index of \cite{PeyerVermaelen2009} predicts the five factor excess returns for different time periods.
-The first two columns show the IRATS results and the last two columns show the Calendar Time results.
-Regardless of the method to compute excess returns, the U-index is an excellent predictor: except for the very short 1985-1990 period when we also have few events, buybacks announced by high U-index firms are followed by significantly larger returns than buybacks announced by low U-index firms.
-%There is also no evidence that the U-index is losing its predictive power over time: for example, in the 2001-2015 period the difference between high and low U-index firms (after 48 months, IRATS) was \Sexpr{BBtable_undertime["+48",31]-BBtable_undertime["+48",34]}$\%$, while in the most recent 2008-2015 period high U-index firms had \Sexpr{BBtable_undertime["+48",43]-BBtable_undertime["+48",46]}$\%$ larger abnormal returns than low U-index firms.
 
@@
 However, Figure~\ref{fig:ReturnsBB} also allows us to verify that the excess returns are not simply the result of outperformance during a particular time period.
-%Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.
-The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the excess returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}.
-In only one year (\Sexpr{rownames(tmp)[which.min(tmp[,13])]}) the strategy generates an abnormal loss larger than \Sexpr{round(abs(sort(tmp[,13])[2]),1)}$\%$.
-
-%\subsection{Robustness across Sectors}
-%\label{sec:AllIndustries}
-
-%<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-%tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
-%@
-
-%Figure~\ref{fig:industryeventsBB} shows the number of buyback events per industry in our sample.
-The software and semiconductor industries are the most active repurchasers.
-They also tend to be the most volatile industries, industries where disagreement about fundamental value is large - as we report later in Table \ref{tbl:industriesR2Vol}.
-Table~\ref{tbl:IndustriesBB} shows the IRATS cumulative abnormal returns and Table~\ref{tbl:IndustriesBB_cal} the Calendar Time method monthly average abnormal returns when we remove one industry at the time, for the top most frequent buyback industries (those for which there are at least \Sexpr{min_industry_sampleBB} events in our sample).
-Note from Table~\ref{tbl:priorBuybacks} that, after 48 months, the cumulative abnormal returns for the whole sample (using IRATS) is \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ and the monthly average excess return (Calendar Time) is \Sexpr{round(CAL_table_all_bb["+48","CAL 5F"],2)}$\%$.
-So the larger the difference between these numbers and the corresponding numbers for the industry indicated in Tables~\ref{tbl:IndustriesBB} and \ref{tbl:IndustriesBB_cal}, the larger the excess returns in the industry removed.
-For example, using IRATS, deleting the software industry lowers the CAR from \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ to \Sexpr{round(tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$, a \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"] - tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$ decline.
-This is the largest decline in Table~\ref{tbl:IndustriesBB}, indicating that buybacks in the software industry are followed by the largest excess returns.
-However, deleting Retail, Insurance, Machinery, Meals and especially Chemical stocks improves the excess returns.
-Of course, these differences could be explained by differences in U-index levels or other indicators of the likelihood of misvaluation, a topic we turn to next.
 
@@
 But considering the very high correlation between residual variance and total variance, their prediction can also be tested by using total volatility.
-
-%But considering the very high correlation between residual variance and total variance, their hypothesis would also predict a positive correlation between total volatility and future returns for undervalued stocks.
-Hence, perhaps total volatility is a better prediction of excess returns than (standardized) idiosyncratic volatility (defined as $1-R^2$) or the U-index of \cite{PeyerVermaelen2009}.
-Or perhaps volatility can be an additional, next to the U-index and standardized idiosyncratic volatility, indicator of the likelihood that the buyback is driven by undervaluation.\footnote{In contrast to the option hypothesis, \cite{Stambaugh2015} also predict a negative relation between volatility and returns for overvalued stocks.
-However, as with the Fama-French 5 factor model equity issuers don't appear to be overvalued, we can't test this ''second'' leg of their hypothesis.}
 
@@
 
-%Moreover, is our measure of standardized idiosyncratic volatility, $(1-R^2)$, positively correlated with excess returns, as predicted by the information advantage hypothesis?
-Note that this is a measure of idiosyncratic risk that, unlike residual variance is little correlated with total volatility (\Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study) and measures more precisely the fraction of total volatility explained by company-specific news.
-We start with the latter first, then consider the former, and finally we combine the two in the next section.
-
 Moreover, this market timing hypothesis assumes that that firms may have superior {\it company-specific} information.
@@
 Hence the combined results of Table \ref{tbl:VOLunderBB} and \ref{tbl:IdiosyncraticunderBB} are consistent with the hypothesis that market timing is driving long-term excess returns.
-
-%Figure \ref{fig:pastallidio} summarizes our results.
-It shows the CAR based on IRATS (Panel~A for the high U-index firms, B for the low U-index firms, and C for all firms).
-In agreement with Table~\ref{tbl:IdiosyncraticunderBB}, the striking result (Panel~A) is that the U-index is not a good predictor of excess returns for stocks largely driven by market factors (low idiosyncratic firms).
-This is strong evidence that excess returns after buybacks are driven by superior company-specific information of the management.
-
-%The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \citep{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns.
-However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks.
-Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing.
-Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks.
-Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).
-So our results are also consistent with the \cite{Stambaugh2015} interpretation.
-
-%\subsection{Volatility and excess returns}
-%\label{sec:volbuybacks}
-
-%The announcement of a buyback program is not a firm commitment, but an option to buy back stock.
-\cite{IkenberryVermaelen1996} model this flexibility as an exchange option in which the market price of the stock is exchanged for the true value of the stock.
-They predict that, as with all options, the value increases with the volatility.
-The intuition is that the larger the volatility, the larger the probability that the market price may deviate from the true value.
-This enhances the timing ability of the manager-insider.
-They show that this option can have large value, something that may not be realized at the time of the announcement of the buyback authorization.
-For example, the market may underestimate the maturity of the option if they do not realize that firms who are announcing a buyback authorization for say 2 years are likely to renew the authorization many times in the future.
-Hence the option hypothesis predicts that excess returns are positively correlated with volatility.
-
-%Table~\ref{tbl:industriesR2Vol}, columns (3) and (4)  show the percentage of high and low volatility events across all industries for which we have at least 100 buyback events in our sample.
-Software and chips (different from the standardized idiosyncratic volatility case) tend to be the most volatile sectors and they are also two of the three sectors where buybacks are more frequent.
-
-%Table~\ref{tbl:VOLunderBB} shows the IRATS and Calendar Time abnormal returns for high and low volatility buybacks events-companies.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
-Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
-High volatility companies earn cumulative excess returns of  \Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*High_VOL_BB_Hedged48m),1),1)}$\%$) for the 12 (48) month holding strategy, which are higher than the \Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged),1),1)}$\%$ (\Sexpr{round(tail(cumsum(100*Low_VOL_BB_Hedged48m),1),1)}$\%$) of the corresponding low volatility sample.} Focusing on IRATS, high volatility buyback stocks earn \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$  after 48 months, while low volatility events have non significant abnormal returns for any period.
-The results using the Calendar Time method confirm these findings.
-So we find support for the \cite{Stambaugh2015} costly arbitrage hypothesis as well as the option hypothesis proposed by \cite{IkenberryVermaelen1996}.
-
-%Table~\ref{tbl:VOLunderBB} also tests whether the U-index can further differentiate high volatility events, as well as whether adjusting for volatility improves the predictive power of the U-index.
-Regardless of the time horizon and the event study method, the U-index works for high volatile companies.
-After 48 months, based on the IRATS methods, high U-index high volatility companies earn \Sexpr{VOL_IRATStable_underBB["+48","High Vol: U CAR"]}$\%$ (t = \Sexpr{VOL_IRATStable_underBB["+48",8]}).
-Low U-index high volatility companies earn \Sexpr{VOL_IRATStable_underBB["+48",10]}$\%$ (t = \Sexpr{VOL_IRATStable_underBB["+48",11]}).
-The Calendar Time results provide the same picture.
-Figure~\ref{fig:pastallVOL} summarizes the results for the total sample and the high and low U-index sample.
 
@@
 We use the most recent data pre-announce, and make the winsorization and other adjustments as in the websites above.
-Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.}
-%``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. 
-``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement.
-Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available
-%\footnote{As this SDC data was not available for many events, we did not consider it in the U-index calculation.} 
-(this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.
+Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.} ``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement.
+Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available (this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.
 
@@
 This makes sense according to the static trade-off theory of optimal capital structure: high risky firms have more financial distress and should have less debt.
-%Second, the high EU index firms are more likely to miss earnings forecasts.
-To the extent that analysts base their recommendations on these earnings misses, stock prices may become undervalued.
-Evidence that analyst extrapolation forecast errors are a partial explanation for the buyback anomaly is documented by \cite{PeyerVermaelen2009}.
 High EU index firms are also more likely to mention ``undervaluation'' as a motivation for the buyback and to use cash.
@@
 So indeed the buyback anomaly is to large extent a small cap anomaly.
-%, although portfolio EU3 for which the average market capitalization of its \Sexpr{sum(EUindex_bb==3)} firms is \$\Sexpr{round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb ==3]),1)} billion still has significant abnormal returns.
 
@@
 The bottom line is that combining volatility, standardized idiosyncratic risk and the U-index in one EU-index generates a more selective predictor of excess returns than each of the indicators separately.
-%Indeed, high U-index stocks, stocks with high standardized idiosyncratic risk, and high volatile stocks generate cumulative excess returns of respectively \Sexpr{IRATS_table_all_bb_undervaluation["+48","U:CAR5F"]}$\%$ (Table~\ref{tbl:priorBuybacks}), \Sexpr{R2_IRATStableBB["+48","High Idiosync.: CAR"]}$\%$ (Table~\ref{tbl:IdiosyncraticunderBB}) and \Sexpr{VOL_IRATStableBB["+48","High Vol: CAR"]}$\%$ (Table~\ref{tbl:VOLunderBB}).
 
@@
 
-%{\small \singlespacing \LTXtable{\textwidth}{VariablesTable} }
-
 \clearpage
@@
 %%% FIRST ALL TABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% BASIC ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % TIME ROBUSTNESS ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Robustness over time}
-%\label{app:robusttime}
+
+\clearpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % VOL ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % IDIOSYNCRATIC ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-#cbind(R2_IRATStableBB,IRATS_table_lowidio_iss)[reported_times,],
-#cbind(R2_IRATStableBB_cal,R2_IRATStable_underBB_cal)[reported_times,],
-#columns= c("Low Id.","High Id.","Low Id./High U-Ind.","Low Id./Low U-Ind.","High Id./High U-Ind.","High Id./Low U-Ind."),
-#title="Buyback for Low and High idiosyncratic and  for Low and High U-index companies",
+
+<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
 
@@
 
-%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%
-
 <<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % NEW INDEX
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-
-#\\textit{Missed (Beat) EPS} measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. 
-#EU_relations <- EU_relations[-which(rownames(EU_relations) %in% c("Missed EPS","Beat EPS")),]
+
+<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
 
@@
 \clearpage
-
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-if (0){
-  latex_render_data_frame(
-    pnl_matrix(remove_initialization_time(High_EU_BB_Hedged,min_date=FirstTrade)), 
-    title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all high EU-index buybacks",
-    caption="Monthly and yearly  five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all high EU-index buybacks only.
-Holding period for each buyback is 12 months per event.",
-    label="tbl:EUhedgedBB", 
-    columns=NULL,
-    bigtitleontop = T,
-    show_rownames=TRUE,
-    scale = 0.9,
-    digits=1,
-    lastSpecial=F,dorotate=F
-  )
-}
-@
-
-%\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%XXXXXXX NOW ALL FIGURES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 <<  fig.width=10, fig.height=5, out.width='\\textwidth', echo=F >>=
-#par(mfrow=c(2,1), mar=c(2.3,4,2.3,4))
-#valuation_index_bb[which(valuation_index_bb==2)]<-3 # there is one company here. need to check why
 tmp = table(valuation_index_bb)
@@
 barplot(tmp,main = "", ylab = "Number of Events", xlab = "",las=2,space=0.5, cex.names=1)
-#tmp = table(valuation_index_iss)
-#tmp = structure(as.numeric(tmp), .Names = names(tmp))
-#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=1)
 rm("tmp")
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-%\begin{figure}[H]
-%\centering
-<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-if (0){
-  par(mfrow=c(2,2), mar=c(2.3,4,2.3,4))
-
-  IRATS_table_all_bb_plot = IRATS_table_all_bb
-  IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] <- -IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")]
-  IRATS_table_all_iss_plot = IRATS_table_all_iss
-  IRATS_table_all_iss_plot[rownames(IRATS_table_all_iss_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] <- -IRATS_table_all_iss_plot[rownames(IRATS_table_all_iss_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")]
-  IRATS_table_all_bb_undervaluation_plot = IRATS_table_all_bb_undervaluation
-  IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]
-  #IRATS_table_all_iss_undervaluation_plot = IRATS_table_all_iss_undervaluation
-  #IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]
-
-  ylimit = c(min(
-    #IRATS_table_all_bb_plot[reported_times_plots,"CAR 3F"], 
-    IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], 
-    #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
-    #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
-    IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
-    IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR5F"]), 
-    max(
-      #IRATS_table_all_bb_plot[reported_times_plots,"CAR 3F"], 
-      IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], 
-      #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
-      #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
-      IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
-      IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR5F"])
-  )
-
-  plot(IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="A. Buybacks - All", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #lines(IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"],  lty = 2,lwd=1.4)
-  abline(v=which(reported_times_plots == "0"), lwd=0.5)
-  abline(h=0, lwd=0.5)
-
-  plot(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="C. Buybacks - high/low U-index", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"U:CAR3F"]
-  #points(tmp, pch=0)
-  #lines(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR3F"],lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"O:CAR3F"]
-  #points(tmp, pch=3)
-  #lines(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"],lty = 3, lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"U:CAR5F"]
-  #points(tmp, pch=0)
-  lines(IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR5F"],  lty = 3,lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_bb_undervaluation_plot[plot_tickers,"O:CAR5F"]
-  #points(tmp, pch=3)
-  abline(v=which(reported_times_plots == "0"), lwd=0.5)
-  abline(h=0, lwd=0.5)
-
-  # SEOs
-  ylimit = c(min(
-    #IRATS_table_all_iss_plot[reported_times_plots,"CAR 3F"], 
-    IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"]#, 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR5F"]
-  ), 
-  max(
-    #IRATS_table_all_iss_plot[reported_times_plots,"CAR 3F"], 
-    IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"]#, 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
-    #IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR5F"]
-  )
-  )
-
-  plot(IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="B. SEOs - All", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #lines(IRATS_table_all_iss_plot[reported_times_plots,"CAR 5F"],  lty = 2,lwd=1.4)
-  abline(v=which(reported_times_plots == "0"), lwd=0.5)
-  abline(h=0, lwd=0.5)
-
-}
-if (0){
-  plot(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="SEOs - Under/Over-valuation", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"U:CAR3F"]
-  #points(tmp, pch=0)
-  #lines(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR3F"],lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"O:CAR3F"]
-  #points(tmp, pch=3)
-  #lines(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"U:CAR5F"],lty = 3, lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"U:CAR5F"]
-  #points(tmp, pch=0)
-  lines(IRATS_table_all_iss_undervaluation_plot[reported_times_plots,"O:CAR5F"],  lty = 3,lwd=1.6)
-  #tmp = rep(NA,length(reported_times_plots)); tmp[plot_tickers] <- IRATS_table_all_iss_undervaluation_plot[plot_tickers,"O:CAR5F"]
-  #points(tmp, pch=3)
-  abline(v=which(reported_times_plots == "0"), lwd=0.5)
-  abline(h=0, lwd=0.5)
-}
-@
-%\caption{Long-run five factors cumulative average abnormal returns (CAR) of buyback and SEO portfolios.
-The x-axis indicates months from the date of the event announcement.
-Panel~A shows all buyback events, whereas Panel C shows all high (solid line) and low (dashed lines) U-index buyback events.
-Panel~B includes all SEOs.}
-%\label{fig:pastall}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% CROSS-EVENTS ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-%\subsection{Combining Equity Issues and Stock Repurchases}
-%\label{app:combine}
-
-%\begin{figure}[H]
-%\centering
-<< BBISSevents, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-#par(mfrow=c(2,1), mar=c(3.8,4,3.8,4))
-if (0){
-  market_index = 100*(1+cumprod(1+Market_Monthly[names(Market_Monthly) >= "1985-01-01"]))
-  market_index = market_index[which(str_sub(names(market_index), start = 6, end = 7)=="12")]
-  names(market_index) <- str_sub(names(market_index), start = 1, end = 4)
-  df.bar <- barplot(BB_with_ISS_later_total,col=c("grey"),main = "", ylab = "Percent", xlab = "Years",las=2,space=0.5, cex.names=1)
-  for (iter in 1:floor(max(BB_with_ISS_later_total)/5))
-    abline(h = 5*iter)
-  #par(new = TRUE)
-  #plot(market_index,type="l", col="red", lwd = 4, lty=3,axes = FALSE, xlab = "", ylab = "")
-  #points(market_index, pch=1, col="red", lwd=2)
-  #axis(side=4, at = pretty(range(market_index)))
-  #mtext("Market Index", side=4, line=3)
-
-  if (0){
-    df.bar <- barplot(ISS_with_BB_later_total,col=c("grey"),main = "Issues with Follow-up Buyback", ylab = "Percent", xlab = "Years",las=2,space=0.5, cex.names=1)
-    for (iter in 1:floor(max(ISS_with_BB_later_total)/5))
-      abline(h = 5*iter)
-    par(new = TRUE)
-    plot(market_index,type="l", col="red", lwd = 4, lty=3,axes = FALSE, xlab = "", ylab = "")
-    points(market_index, pch=1, col="red", lwd=2)
-    axis(side=4, at = pretty(range(market_index)))
-    mtext("Market Index", side=4, line=3)
-  }
-}
-@
-%\caption{Buybacks with a follow-up equity issue within 48 months.
-We show the percent of announced buyback events each year, that had a follow-up issue within 48 months after the event.
-The average percentage is \Sexpr{round(mean(BB_with_ISS_later_total),1)}$\%$ and there are only \Sexpr{sum(BB_with_ISS_later_total > 10)} years (1989 and 1990) where the percentage is larger than $10\%$.
-%Top figure is buybacks and bottom is SEOs.
-%}
-%\label{fig:BBISSevents}
-%\end{figure}
-
-%\clearpage
-%\begin{figure}[H]
-%\centering
-<< BBISSpnl, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
-if (0){
-  reported_times_plots_tmp = reported_times_plots
-  reported_times_plots = reported_times_plots[8:length(reported_times_plots)]
-
-  #par(mfrow=c(2,2), mar=c(3.8,4,3.8,4))
-  par(mfrow=c(2,1), mar=c(3,4,3,4))
-
-  ylimit = c(min(Exit_on_SEO_Abn_table[reported_times_plots,1], Exit_on_SEO_Abn_table[reported_times_plots,4]), 
-             max(Exit_on_SEO_Abn_table[reported_times_plots,1], Exit_on_SEO_Abn_table[reported_times_plots,4]))
-  plot(Exit_on_SEO_Abn_table[reported_times_plots,4], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel A: Buybacks with SEO IRATS CAR", lwd=1.4)
-  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  lines(Exit_on_SEO_Abn_table[reported_times_plots,1],lty = 2,lwd=1.4)
-  abline(h=0, lwd=0.5)
-  abline(v=which(reported_times_plots == "0"), lwd=0.5)
-  legend(x="topleft",
-         c("Post Buyback Issuance","No Post Buyback Issuance"),
-         lty=c("solid","dashed"),
-         lwd=c(2,2),
-         cex=1,bg="white",inset=0.01)
-
-  if (0){
-    ylimit = c(min(Exit_on_SEO_Abn_table_cal[reported_times_plots,1], Exit_on_SEO_Abn_table_cal[reported_times_plots,4]), 
-               max(Exit_on_SEO_Abn_table_cal[reported_times_plots,1], Exit_on_SEO_Abn_table_cal[reported_times_plots,4]))
-    plot(Exit_on_SEO_Abn_table_cal[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: Buybacks with SEO: Calendar Method", lwd=1.4)
-    axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-    axis(2,cex.axis=1.1)
-    lines(Exit_on_SEO_Abn_table_cal[reported_times_plots,4],lty = 2,lwd=1.4)
-    abline(h=0, lwd=0.5)
-    abline(v=which(reported_times_plots == "0"), lwd=0.5)
-  }
-
-  reported_times_plots = reported_times_plots_tmp
-
-  pnl_Exit_Hedged = BB_ISS_Exit_Hedged
-  pnl_NoExit_Hedged = BB_ISS_NoExit_Hedged
-  plot(cumsum(100*pnl_NoExit_Hedged),type="l",ylab="CAR", xlab = "",main = "Panel B: Strategy Returns", axes = FALSE, ylim=c(min(c(100*cumsum(pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged))), max(c(cumsum(100*pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  lines(cumsum(100*pnl_Exit_Hedged), lty = 2,lwd=1.4)
-  for (iter in floor(100*min(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/100):floor(100*max(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/100))
-    abline(h = 100*iter)
-  #plot_crisis_dates(pnl_NoExit_Hedged) 
-  legend(x="topleft",
-         c("Without Exit","With Exit"),
-         lty=c("solid","dashed"),
-         lwd=c(2,2),
-         cex=1,bg="white",inset=0.01)
-
-  #### SEOs NOW (We combine the plots)
-  if (0){ 
-    reported_times_plots_tmp = reported_times_plots
-    reported_times_plots = reported_times_plots[8:length(reported_times_plots)]
-
-    ylimit = c(min(Exit_on_BB_Abn_table[reported_times_plots,1], Exit_on_BB_Abn_table[reported_times_plots,4]), 
-               max(Exit_on_BB_Abn_table[reported_times_plots,1], Exit_on_BB_Abn_table[reported_times_plots,4]))
-    plot(Exit_on_BB_Abn_table[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: SEO with Buyback IRATS CAR", lwd=1.4)
-    axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-    axis(2,cex.axis=1.1)
-    lines(Exit_on_BB_Abn_table[reported_times_plots,4],lty = 2,lwd=1.4)
-    abline(h=0, lwd=0.5)
-    abline(v=which(reported_times_plots == "0"), lwd=0.5)
-
-    if (0){
-      ylimit = c(min(Exit_on_BB_Abn_table_cal[reported_times_plots,1], Exit_on_BB_Abn_table_cal[reported_times_plots,4]), 
-                 max(Exit_on_BB_Abn_table_cal[reported_times_plots,1], Exit_on_BB_Abn_table_cal[reported_times_plots,4]))
-      plot(Exit_on_BB_Abn_table_cal[reported_times_plots,1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="SEO with Buyback: Calendar", lwd=1.4)
-      axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
-      axis(2,cex.axis=1.1)
-      lines(Exit_on_BB_Abn_table_cal[reported_times_plots,4],lty = 2,lwd=1.4)
-      abline(h=0, lwd=0.5)
-      abline(v=which(reported_times_plots == "0"), lwd=0.5)
-    }
-
-    reported_times_plots = reported_times_plots_tmp
-
-    pnl_Exit_Hedged = ISS_BB_Exit_Hedged
-    pnl_NoExit_Hedged = ISS_BB_NoExit_Hedged
-    plot(cumsum(100*pnl_NoExit_Hedged),type="l",ylab="CAR", xlab = "",main = "Strategy Returns",axes = FALSE, ylim=c(min(c(100*cumsum(pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged))), max(c(cumsum(100*pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged)))), cex.lab=1.1)
-    axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-    axis(2,cex.axis=1.1)
-    lines(cumsum(100*pnl_Exit_Hedged),lty = 2,lwd=1.4)
-    for (iter in floor(100*min(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/50):floor(100*max(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/50))
-      abline(h = 50*iter)
-    #plot_crisis_dates(pnl_NoExit_Hedged) 
-  }
-
-}
-@
-%\caption{ Buybacks followed by equity issues within 48 months. 
-%Top Panel~A:  Five factor IRATS CAR for all buyback events that had (with hindsight) no subsequent SEO event within the 48 months post buyback announcement (solid line) versus those that did have (dashed line).
-Bottom Panel~B: Abnormal (five-factor rolling hedged) returns of buybacks portfolio for only the \Sexpr{length(BB_with_ISS_later)} events for which there was a subsequent issue within 4 years.
-Dashed line is if we exit these positions the month after the subsequent SEO announcement.
-%(Average annual returns: \Sexpr{round(pnl_stats(BB_ISS_Exit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(BB_ISS_Exit_Hedged)[3],1)}), and solid line is if we do not (Average annual returns: \Sexpr{round(pnl_stats(BB_ISS_NoExit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(BB_ISS_NoExit_Hedged)[3],1)}).
-%{\bf Bottom Panel~B: Left:} Five factor IRATS CAR for all SEO events that had no subsequent buyback event within the 48 months post SEO announcement (black line) versus those that did have (dashed line).
-{\bf Right:} Abnormal (five-factor rolling hedged) returns of SEO portfolio for only the \Sexpr{length(ISS_with_BB_later)} events for which there was a subsequent buybacks announcement within 4 years.
-Dashed line is if we exit these positions  the month after the subsequent buyback announcement  (Average annual returns: \Sexpr{round(pnl_stats(ISS_BB_Exit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(ISS_BB_Exit_Hedged)[3],1)}), and solid line is if we do not (Average annual returns: \Sexpr{round(pnl_stats(ISS_BB_NoExit_Hedged)[1],1)}$\%$, Sharpe ratio: \Sexpr{round(pnl_stats(ISS_BB_NoExit_Hedged)[3],1)}).
-%}
-%\label{fig:BBISSexit}
-%\end{figure}
-
-\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % PORTFOLIO RETURNS ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% INDUSTRIES ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\clearpage
-%\subsection{Buybacks across Industries}
-%\label{app:industries}
-
-%\begin{landscape}
-%\begin{figure}[H]
-%\centering
-%<<  fig.width=10, fig.height=5, echo=F >>=
-%df.bar <- barplot(industry_tableBB,col=c("grey"),main = "", ylab = "Buybacks", xlab = "",las=2,space=0.9, cex.names=0.62)
-%for (iter in 1:floor(max(industry_tableBB)/100))
-%  abline(h = 100*iter)
-%@
-%\caption{Number of buyback announcements per industry. }
-%\label{fig:industryeventsBB}
-%\end{figure}
-%\end{landscape}
-%\begin{figure}[H]
-%\centering
-%<<  fig.width=10, fig.height=5, out.width='\\textwidth', echo=F >>=
-%df.bar <- barplot(industry_tableISS,col=c("grey"),main = "", ylab = "Issues", xlab = "",las=2,space=0.9, cex.names=1)
-%for (iter in 1:floor(max(industry_tableISS)/100))
-%  abline(h = 100*iter)
-%@
-%\caption{Number of issue announcements per industry.  }
-%\label{fig:industryeventsISS}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% IDIOSYNCRATIC ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\clearpage
-%\subsection{Idiosyncratic Risk and Buybacks}
-%\label{app:idiosync}
-
-%\begin{figure}[H]
-%\centering
-<< R2thresholds, fig.width=7, fig.height=4, out.width='\\textwidth', echo=F >>=
-if (0){
-  #par(mfrow=c(2,1), mar=c(2.7,4.5,2.7,4.5))
-  Market_Monthly_index = Market_Monthly
-  names(Market_Monthly_index) <- paste(str_sub(names(Market_Monthly_index),start=1,end=4),str_sub(names(Market_Monthly_index),start=6,end=7),sep="")
-
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[High_Idiosyncr_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$Rsq_returns[High_Idiosyncr_eventsBB]
-  names(tmp)<-all_dates
-  R2_thresholds_up_plot = sapply(names(Market_Monthly_index), function(i){
-    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
-  })
-  R2_thresholds_up_plot = R2_thresholds_up_plot[!is.na(R2_thresholds_up_plot)]
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[Low_Idiosyncr_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$Rsq_returns[Low_Idiosyncr_eventsBB]
-  names(tmp)<-all_dates
-  R2_thresholds_down_plot = sapply(names(Market_Monthly_index), function(i){
-    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
-  })
-  R2_thresholds_down_plot = R2_thresholds_down_plot[!is.na(R2_thresholds_down_plot)]
-
-  R2_thresholds_down_plot = R2_thresholds_down_plot[intersect(names(R2_thresholds_down_plot), names(R2_thresholds_up_plot))]
-  R2_thresholds_up_plot = R2_thresholds_up_plot[intersect(names(R2_thresholds_down_plot), names(R2_thresholds_up_plot))]
-  R2_thresholds_up_plot = R2_thresholds_up_plot[intersect(names(R2_thresholds_up_plot), names(Market_Monthly_index))]
-  R2_thresholds_down_plot = R2_thresholds_down_plot[names(R2_thresholds_up_plot)]
-  Market_Monthly_index = Market_Monthly_index[names(R2_thresholds_up_plot)]
-  market_index = 100*(1+cumprod(1+Market_Monthly))
-
-  plot(R2_thresholds_up_plot, col="black", axes=FALSE, ylab="five-factor R square", main = "Buybacks Average five-factor R square", xlab = "Time",ylim=c(min(c(R2_thresholds_down_plot[!is.na(R2_thresholds_down_plot)],R2_thresholds_up_plot[!is.na(R2_thresholds_up_plot)])), max(c(R2_thresholds_down_plot[!is.na(R2_thresholds_down_plot)],R2_thresholds_up_plot[!is.na(R2_thresholds_up_plot)]))),  cex.lab=1.1, type="l", lwd=2)
-  lines(R2_thresholds_down_plot, col="black", lwd=2,lty="dotted")
-  axis(1,at=seq(1,length(Market_Monthly_index),length.out=20),labels=str_sub(names(Market_Monthly_index)[seq(1,length(Market_Monthly_index),length.out=20)], start=1,end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #par(new = TRUE)
-  #plot(market_index,type="l", lwd = 2, axes = FALSE, xlab = "", ylab = "")
-  #axis(side=4, at = pretty(range(market_index)))
-  #mtext("Market Index", side=4, line=3)
-}
-@
-%\caption{Monthly average (across all buybacks events that month) $R^2$ defined using all buybacks events announced in a given month.
-Solid line is for high idiosyncratic events, dotted  line is for low.
-%Note that as the idiosyncratic risk is estimated using 6 months returns before announcement, there is a time shift relative to the market returns. 
-%}
-%\label{fig:R2thresholds}
-%\end{figure}
-
-%\clearpage
-
-%\clearpage
-
-%\begin{figure}[H]
-%\centering
-<< badpreviousR2, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-#par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))
-if (0){
-  plot(cumsum(100*High_Idiosyncr_BB_Hedged),type="l",ylab="CAR", xlab = "Time",main = "",  lwd=2, axes = FALSE, 
-       ylim=c(min(c(cumsum(100*High_Idiosyncr_BB_Hedged),cumsum(100*Low_Idiosyncr_BB_Hedged),cumsum(100*High_Idiosyncr_BB_Hedged48m),cumsum(100*Low_Idiosyncr_BB_Hedged48m))), 
-              max(c(cumsum(100*High_Idiosyncr_BB_Hedged),cumsum(100*Low_Idiosyncr_BB_Hedged),cumsum(100*High_Idiosyncr_BB_Hedged48m),cumsum(100*Low_Idiosyncr_BB_Hedged48m)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(High_Idiosyncr_BB_Hedged),length.out=10),labels=str_sub(names(High_Idiosyncr_BB_Hedged)[seq(1,length(High_Idiosyncr_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  lines(cumsum(100*Low_Idiosyncr_BB_Hedged),lty="dotted", lwd=2)
-  lines(cumsum(100*High_Idiosyncr_BB_Hedged48m),lty="dashed", lwd=2)
-  lines(cumsum(100*Low_Idiosyncr_BB_Hedged48m),lty="dotdash", lwd=2)
-  for (iter in 1:floor(100*max(c(cumsum(High_Idiosyncr_BB_Hedged),cumsum(Low_Idiosyncr_BB_Hedged)))/50))
-    abline(h = 50*iter)
-  abline(h = 200)
-  #plot_crisis_dates(High_Idiosyncr_BB_Hedged)
-  legend(x="topleft",
-         c("12 Month High Idiosyncratic","12 Month Low Idiosyncratic","48 Month High Idiosyncratic","48 Month Low Idiosyncratic"),
-         lty=c("solid","dotted","dashed","dotdash"),
-         lwd=c(2,2,2,2),
-         cex=1,bg="white",inset=0.01)
-
-  if (0){
-    plot(cumsum(100*High_Idiosyncr_ISS_Hedged),type="l",ylab="CAR", xlab = "Time",main = "SEOs", axes = FALSE, 
-         ylim=c(min(c(cumsum(100*High_Idiosyncr_ISS_Hedged),cumsum(100*Low_Idiosyncr_ISS_Hedged),cumsum(100*High_Idiosyncr_ISS_Hedged48m),cumsum(100*Low_Idiosyncr_ISS_Hedged48m))), 
-                max(c(cumsum(100*High_Idiosyncr_ISS_Hedged),cumsum(100*Low_Idiosyncr_ISS_Hedged),cumsum(100*High_Idiosyncr_ISS_Hedged48m),cumsum(100*Low_Idiosyncr_ISS_Hedged48m)))), cex.lab=1.1)
-    axis(1,at=seq(1,length(High_Idiosyncr_ISS_Hedged),length.out=10),labels=str_sub(names(High_Idiosyncr_ISS_Hedged)[seq(1,length(High_Idiosyncr_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-    axis(2,cex.axis=1.1)
-    lines(cumsum(100*Low_Idiosyncr_ISS_Hedged), col="red")
-    lines(cumsum(100*High_Idiosyncr_ISS_Hedged48m), col="blue")
-    lines(cumsum(100*Low_Idiosyncr_ISS_Hedged48m), col="green")
-    for (iter in 1:floor(100*max(c(cumsum(High_Idiosyncr_ISS_Hedged),cumsum(Low_Idiosyncr_ISS_Hedged)))/50))
-      abline(h = 50*iter)
-    #plot_crisis_dates(High_Idiosyncr_ISS_Hedged)
-  }
-}
-@
-%\caption{Buybacks: High versus Low Idiosyncratic Events.
-Returns of five-factor rolling hedged portfolio for only the buyback events for high and low idiosyncratic company.
-Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio; dashed line is ``high'' and a 48-months holding portfolio, dotted-dash line is ``low'' and a 48-months portfolio.
-%Red line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged)[3],1)}.
-Black line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged)[3],1)}.
-Green line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_Idiosyncr_BB_Hedged48m)[3],1)}.
-Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_Idiosyncr_BB_Hedged48m)[3],1)}.
-%We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
-%Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
-%}
-%\label{fig:badpreviousR2}
-%\end{figure}
-
-%\begin{figure}[H]
-%\centering
 << fig.width=8, fig.height=5, out.width='\\textwidth', echo=F >>=
-
 R2_IRATStableBB_plot = R2_IRATStableBB
@@
 R2_IRATStable_underBB_plot[rownames(R2_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)] <- -R2_IRATStable_underBB_plot[rownames(R2_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)]
-
-if (0){
-par(mfrow=c(2,2), mar=c(2.7,4,2.7,4))
-
-ylimit = c(min(R2_IRATStableBB_plot[reported_times_plots,"High Idiosync.: CAR"], 
-               R2_IRATStableBB_plot[reported_times_plots,"Low Idiosync.: CAR"],
-               R2_IRATStable_underBB_plot[reported_times_plots,"Low Idiosync.: U CAR"],
-               R2_IRATStable_underBB_plot[reported_times_plots,"High Idiosync.: U CAR"],
-               R2_IRATStable_underBB_plot[reported_times_plots,4],
-               R2_IRATStable_underBB_plot[reported_times_plots,10]), 
-           max(R2_IRATStableBB_plot[reported_times_plots,"High Idiosync.: CAR"], 
-               R2_IRATStableBB_plot[reported_times_plots,"Low Idiosync.: CAR"],
-               R2_IRATStable_underBB_plot[reported_times_plots,"Low Idiosync.: U CAR"],
-               R2_IRATStable_underBB_plot[reported_times_plots,"High Idiosync.: U CAR"],
-               R2_IRATStable_underBB_plot[reported_times_plots,4],
-               R2_IRATStable_underBB_plot[reported_times_plots,10]))
-
-plot(R2_IRATStable_underBB_plot[reported_times_plots,"High Idiosync.: U CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel A: High U-index buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
-axis(2,cex.axis=1.1)
-lines(R2_IRATStable_underBB_plot[reported_times_plots,"Low Idiosync.: U CAR"],lty = 2,lwd=1.6)
-abline(v=which(reported_times_plots == "0"), lwd=0.5)
-abline(h=0, lwd=0.5)
-
-plot(R2_IRATStable_underBB_plot[reported_times_plots,10], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: Low U-index buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
-axis(2,cex.axis=1.1)
-lines(R2_IRATStable_underBB_plot[reported_times_plots,4],lty = 2,lwd=1.6)
-abline(v=which(reported_times_plots == "0"), lwd=0.5)
-abline(h=0, lwd=0.5)
-
-plot(R2_IRATStableBB_plot[reported_times_plots,"High Idiosync.: CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel C: All buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
-axis(2,cex.axis=1.1)
-lines(R2_IRATStableBB_plot[reported_times_plots,"Low Idiosync.: CAR"],  lty = 2,lwd=1.4)
-abline(v=which(reported_times_plots == "0"), lwd=0.5)
-abline(h=0, lwd=0.5)
-}
-@
-%\caption{Long-run five factors cumulative average abnormal returns (IRATS) of high (solid line) and low (dashed line) idiosyncratic buybacks.
-The x-axis indicates months from the date of the event announcement.
-Panel~A shows only the high  U-index companies, Panel~B  the low U-index ones, and bottom Panel C includes the whole sample.}
-%\label{fig:pastallidio}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+@
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % VOL ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\clearpage
-%\subsection{Volatility and Buybacks}
-%\label{app:volatility}
-
-%\begin{figure}[H]
-%\centering
-<< VOLthresholds, fig.width=7, fig.height=4, out.width='\\textwidth', echo=F >>=
-#par(mfrow=c(2,1), mar=c(2.7,4.5,2.7,4.5))
-if (0){
-  Market_Monthly_index = Market_Monthly
-  names(Market_Monthly_index) <- paste(str_sub(names(Market_Monthly_index),start=1,end=4),str_sub(names(Market_Monthly_index),start=6,end=7),sep="")
-
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[High_VOL_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$pre_vol[High_VOL_eventsBB]
-  names(tmp)<-all_dates
-  VOL_thresholds_up_plot = sapply(names(Market_Monthly_index), function(i){
-    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
-  })
-  VOL_thresholds_up_plot = 100*VOL_thresholds_up_plot[!is.na(VOL_thresholds_up_plot)]
-  all_dates = paste(str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=1,end=4),str_sub((BUYBACK_DATA$DATASET$SDC$Event.Date),start=6,end=7),sep="")[Low_VOL_eventsBB]
-  tmp = BUYBACK_DATA$DATASET$SDC$pre_vol[Low_VOL_eventsBB]
-  names(tmp)<-all_dates
-  VOL_thresholds_down_plot = sapply(names(Market_Monthly_index), function(i){
-    ifelse(sum(names(tmp) == i) > 1, mean(tmp[names(tmp) == i]),NA)
-  })
-  VOL_thresholds_down_plot = 100*VOL_thresholds_down_plot[!is.na(VOL_thresholds_down_plot)]
-
-  VOL_thresholds_down_plot = VOL_thresholds_down_plot[intersect(names(VOL_thresholds_down_plot), names(VOL_thresholds_up_plot))]
-  VOL_thresholds_up_plot = VOL_thresholds_up_plot[intersect(names(VOL_thresholds_down_plot), names(VOL_thresholds_up_plot))]
-  VOL_thresholds_up_plot = VOL_thresholds_up_plot[intersect(names(VOL_thresholds_up_plot), names(Market_Monthly_index))]
-  VOL_thresholds_down_plot = VOL_thresholds_down_plot[names(VOL_thresholds_up_plot)]
-  Market_Monthly_index = Market_Monthly_index[names(VOL_thresholds_up_plot)]
-  market_index = 100*(1+cumprod(1+Market_Monthly))
-
-  plot(VOL_thresholds_up_plot, col="black", axes=FALSE, ylab="Average Volatility (percent)", main = "Buybacks pre-Announce Returns Volatility", xlab = "Time",ylim=c(min(c(VOL_thresholds_down_plot,VOL_thresholds_up_plot)), max(c(VOL_thresholds_down_plot,VOL_thresholds_up_plot))),  cex.lab=1.1, type="l", lwd=1.2)
-  lines(VOL_thresholds_down_plot, col="black", lwd=2,lty="dotted")
-  axis(1,at=seq(1,length(Market_Monthly_index),length.out=20),labels=str_sub(names(Market_Monthly_index)[seq(1,length(Market_Monthly_index),length.out=20)], start=1,end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  #par(new = TRUE)
-  #plot(market_index,type="l", lwd = 2, axes = FALSE, xlab = "", ylab = "")
-  #axis(side=4, at = pretty(range(market_index)))
-  #mtext("Market Index", side=4, line=3)
-}
-@
-%\caption{Monthly average (across all buybacks events that month) volatility (standard deviation of daily$\%$ returns over 6 months before announcement) defined using all buybacks events announced in a given month.
-Solid line is for high idiosyncratic events, dotted line is for low.
-%Note that as the volatility is estimated using 6 months returns before announcement, there is a time shift relative to the market returns.  
-%}
-%\label{fig:VOLthresholds}
-%\end{figure}
-
-%\begin{figure}[H]
-%\centering
-<< badpreviousVOL, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-#par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))
-if (0){
-  plot(cumsum(100*High_VOL_BB_Hedged),type="l",ylab="CAR", xlab = "Time",main = "", lwd=2, axes = FALSE, 
-       ylim=c(min(c(cumsum(100*High_VOL_BB_Hedged),cumsum(100*Low_VOL_BB_Hedged),cumsum(100*High_VOL_BB_Hedged48m),cumsum(100*Low_VOL_BB_Hedged48m))), 
-              max(c(cumsum(100*High_VOL_BB_Hedged),cumsum(100*Low_VOL_BB_Hedged),cumsum(100*High_VOL_BB_Hedged48m),cumsum(100*Low_VOL_BB_Hedged48m)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(High_VOL_BB_Hedged),length.out=10),labels=str_sub(names(High_VOL_BB_Hedged)[seq(1,length(High_VOL_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  lines(cumsum(100*Low_VOL_BB_Hedged),lty="dotted", lwd=2)
-  lines(cumsum(100*High_VOL_BB_Hedged48m),lty="dashed", lwd=2)
-  lines(cumsum(100*Low_VOL_BB_Hedged48m),lty="dotdash", lwd=2)
-  for (iter in 1:floor(100*max(c(cumsum(High_VOL_BB_Hedged),cumsum(Low_VOL_BB_Hedged)))/50))
-    abline(h = 50*iter)
-  #plot_crisis_dates(High_VOL_BB_Hedged)
-  legend(x="topleft",
-         c("12 Month High Volatility","12 Month Low Volatility","48 Month High Volatility","48 Month Low Volatility"),
-         lty=c("solid","dotted","dashed","dotdash"),
-         lwd=c(2,2,2,2),
-         cex=1,bg="white",inset=0.01)
-
-  if (0){
-    plot(cumsum(100*High_VOL_ISS_Hedged),type="l",ylab="CAR", xlab = "Time",main = "SEOs", lwd=2, axes = FALSE, 
-         ylim=c(min(c(cumsum(100*High_VOL_ISS_Hedged),cumsum(100*Low_VOL_ISS_Hedged),cumsum(100*High_VOL_ISS_Hedged48m),cumsum(100*Low_VOL_ISS_Hedged48m))), 
-                max(c(cumsum(100*High_VOL_ISS_Hedged),cumsum(100*Low_VOL_ISS_Hedged),cumsum(100*High_VOL_ISS_Hedged48m),cumsum(100*Low_VOL_ISS_Hedged48m)))), cex.lab=1.1)
-    axis(1,at=seq(1,length(High_VOL_ISS_Hedged),length.out=10),labels=str_sub(names(High_VOL_ISS_Hedged)[seq(1,length(High_VOL_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-    axis(2,cex.axis=1.1)
-    lines(cumsum(100*Low_VOL_ISS_Hedged),lty="dotted", lwd=2)
-    lines(cumsum(100*High_VOL_ISS_Hedged48m),lty="dashed", lwd=2)
-    lines(cumsum(100*Low_VOL_ISS_Hedged48m),lty="dotdash", lwd=2)
-    for (iter in 1:floor(100*max(c(cumsum(High_VOL_ISS_Hedged),cumsum(Low_VOL_ISS_Hedged)))/50))
-      abline(h = 50*iter)
-    #plot_crisis_dates(High_VOL_ISS_Hedged)
-  }
-}
-@
-%\caption{Buybacks: High vs Low Volatility Events.
-Returns of five-factor rolling hedged portfolio for only the buyback events for high and low volatility company.
-Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio; dashed line is ``high'' and a 48-months holding portfolio, dotted-dash line is ``low'' and a 48-months portfolio.
-%Red line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged)[3],1)}.
-Black line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged)[3],1)}.
-Green line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_VOL_BB_Hedged48m)[3],1)}.
-Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_VOL_BB_Hedged48m)[3],1)}.
-%We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
-%Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
-%}
-%\label{fig:badpreviousVOL}
-%\end{figure}
-
-%\begin{figure}[H]
-%\centering
+
 << fig.width=8, fig.height=5, out.width='\\textwidth', echo=F >>=
@@
 VOL_IRATStable_underBB_plot[rownames(VOL_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)] <- -VOL_IRATStable_underBB_plot[rownames(VOL_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)]
-
-if (0){
-par(mfrow=c(2,2), mar=c(2.7,4,2.7,4))
-
-ylimit = c(min(VOL_IRATStableBB_plot[reported_times_plots,"High Vol: CAR"], 
-               VOL_IRATStableBB_plot[reported_times_plots,"Low Vol: CAR"],
-               VOL_IRATStable_underBB_plot[reported_times_plots,"Low Vol: U CAR"],
-               VOL_IRATStable_underBB_plot[reported_times_plots,"High Vol: U CAR"],
-               VOL_IRATStable_underBB_plot[reported_times_plots,4],
-               VOL_IRATStable_underBB_plot[reported_times_plots,10]), 
-           max(VOL_IRATStableBB_plot[reported_times_plots,"High Vol: CAR"], 
-               VOL_IRATStableBB_plot[reported_times_plots,"Low Vol: CAR"],
-               VOL_IRATStable_underBB_plot[reported_times_plots,"Low Vol: U CAR"],
-               VOL_IRATStable_underBB_plot[reported_times_plots,"High Vol: U CAR"],
-               VOL_IRATStable_underBB_plot[reported_times_plots,4],
-               VOL_IRATStable_underBB_plot[reported_times_plots,10]))
-
-plot(VOL_IRATStable_underBB_plot[reported_times_plots,"High Vol: U CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel A: High U-index buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
-axis(2,cex.axis=1.1)
-lines(VOL_IRATStable_underBB_plot[reported_times_plots,"Low Vol: U CAR"],lty = 2,lwd=1.6)
-abline(v=which(reported_times_plots == "0"), lwd=0.5)
-abline(h=0, lwd=0.5)
-
-plot(VOL_IRATStable_underBB_plot[reported_times_plots,10], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel B: Low U-index buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
-axis(2,cex.axis=1.1)
-lines(VOL_IRATStable_underBB_plot[reported_times_plots,4],lty = 2,lwd=1.6)
-abline(v=which(reported_times_plots == "0"), lwd=0.5)
-abline(h=0, lwd=0.5)
-
-plot(VOL_IRATStableBB_plot[reported_times_plots,"High Vol: CAR"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Panel C: All buybacks", lwd=1.4)
-axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1.1,las=3)
-axis(2,cex.axis=1.1)
-lines(VOL_IRATStableBB_plot[reported_times_plots,"Low Vol: CAR"],  lty = 2,lwd=1.4)
-abline(v=which(reported_times_plots == "0"), lwd=0.5)
-abline(h=0, lwd=0.5)
-}
-@
-%\caption{Volatility and the U-index.
-Long-run five factors cumulative average abnormal returns (IRATS) of high (solid line) and low (dashed line) volatility buybacks.
-The x-axis indicates months from the date of the event announcement.
-Panel~A shows only the high  U-index companies, Panel~B  the low U-index ones, and bottom Panel C includes the whole sample.}
-%\label{fig:pastallVOL}
-%\end{figure}
-
-\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+@
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % NEW INDEX
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{figure}
-
-%\begin{figure}[H]
-%\centering
-<< badpreviousEU, fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-if (0){
-  #par(mfrow=c(2,1),mar=c(2.3,4,2.3,4))
-  plot(cumsum(100*High_EU_BB_Hedged),type="l",ylab="CAR", xlab = "Time",main = "", lwd=2, axes = FALSE, 
-       ylim=c(min(c(cumsum(100*High_EU_BB_Hedged),cumsum(100*Low_EU_BB_Hedged),cumsum(100*High_EU_BB_Hedged48m),cumsum(100*Low_EU_BB_Hedged48m))), 
-              max(c(cumsum(100*High_EU_BB_Hedged),cumsum(100*Low_EU_BB_Hedged),cumsum(100*High_EU_BB_Hedged48m),cumsum(100*Low_EU_BB_Hedged48m)))), cex.lab=1.1)
-  axis(1,at=seq(1,length(High_EU_BB_Hedged),length.out=10),labels=str_sub(names(High_EU_BB_Hedged)[seq(1,length(High_EU_BB_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-  axis(2,cex.axis=1.1)
-  lines(cumsum(100*Low_EU_BB_Hedged),lty="dotted", lwd=2)
-  lines(cumsum(100*High_EU_BB_Hedged48m),lty="dashed", lwd=2)
-  lines(cumsum(100*Low_EU_BB_Hedged48m),lty="dotdash", lwd=2)
-  for (iter in 1:floor(100*max(c(cumsum(High_EU_BB_Hedged),cumsum(Low_EU_BB_Hedged)))/50))
-    abline(h = 50*iter)
-  #plot_crisis_dates(High_EU_BB_Hedged)
-  legend(x="topleft",
-         c("12 Month High EU","12 Month Low EU","48 Month High EU","48 Month Low EU"),
-         lty=c("solid","dotted","dashed","dotdash"),
-         lwd=c(2,2,2,2),
-         cex=1,bg="white",inset=0.01)
-
-  if (0){
-    plot(cumsum(100*High_EU_ISS_Hedged),type="l",ylab="CAR", xlab = "Time",main = "SEOs", axes = FALSE, 
-         ylim=c(min(c(cumsum(100*High_EU_ISS_Hedged),cumsum(100*Low_EU_ISS_Hedged),cumsum(100*High_EU_ISS_Hedged48m),cumsum(100*Low_EU_ISS_Hedged48m))), 
-                max(c(cumsum(100*High_EU_ISS_Hedged),cumsum(100*Low_EU_ISS_Hedged),cumsum(100*High_EU_ISS_Hedged48m),cumsum(100*Low_EU_ISS_Hedged48m)))), cex.lab=1.1)
-    axis(1,at=seq(1,length(High_EU_ISS_Hedged),length.out=10),labels=str_sub(names(High_EU_ISS_Hedged)[seq(1,length(High_EU_ISS_Hedged),length.out=10)], start = 1, end=4),cex.axis=1,las=3)
-    axis(2,cex.axis=1.1)
-    lines(cumsum(100*Low_EU_ISS_Hedged), col="red")
-    lines(cumsum(100*High_EU_ISS_Hedged48m), col="blue")
-    lines(cumsum(100*Low_EU_ISS_Hedged48m), col="green")
-    for (iter in 1:floor(100*max(c(cumsum(High_EU_ISS_Hedged),cumsum(Low_VOL_ISS_Hedged)))/50))
-      abline(h = 50*iter)
-    #plot_crisis_dates(High_VOL_ISS_Hedged)
-  }
-}
-@
-%\caption{Buybacks: High vs Low EU-index Events.
-Returns of five-factor rolling hedged portfolio for only the buyback events for high and low EU-index companies.
-We define low EU-index firms those for which the EU-index is 0-3, and high for which it is 4-6 (note that the index takes values from 0 to 6).
-Solid line is ``high'' and a 12-months holding portfolio, dotted line is ``low'' and a 12-months holding portfolio; dashed line is ``high'' and a 48-months holding portfolio, dotted-dash line is ``low'' and a 48-months portfolio.
-%Red line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[3],1)}.
-Black line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[3],1)}.
-Green line: average annual abnormal returns of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(Low_EU_BB_Hedged48m)[3],1)}.
-Blue line: average annual abnormal returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[1],1)}$\%$, Sharpe ratio of \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[3],1)}.
-%We assume we enter each position \Sexpr{trading_day_after_announce} day after the corresponding event announcement. 
-%Vertical lines indicate \Sexpr{BEAR_YEARS_text$dotcom[1]}, \Sexpr{BEAR_YEARS_text$dotcom[2]}, \Sexpr{BEAR_YEARS_text$financial1[1]}, and \Sexpr{BEAR_YEARS_text$financial1[2]}. 
-%}
-%\label{fig:badpreviousEU}
-%\end{figure}
 
@@
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% OLD TABLES IN CASE WE NEED THEM AGAIN
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\clearpage
-
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-if (0){
-  printLatexTable2(
-    Exit_on_SEO_Abn_table[reported_times,],
-    Exit_on_SEO_Abn_table_cal[reported_times,],
-    columns = c("No Issue","Issue"),
-    title="Buybacks with and without subsequent issue",
-    title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-    title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-    caption="The table presents the long-run abnormal returns for firms repurchase announcements for events with and without a subsequent SEO announcement.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-
-label = "tbl:BBISSexit",
-bigtitleontop=T,
-titleontop=T,
-metric1 = "CAR",
-metric2 = "AR",
-scale=1,
-lastSpecial=T,
-dorotate=F
-  )
-}
-
-if (0){
-  colnames(ISS_for_BB_Abn_table)[1]<- "Post-buyback SEOs"
-  colnames(ISS_for_BB_Abn_table)[4]<- "Other SEOs"
-  printLatexTable(ISS_for_BB_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
-                  label  = "tbl:BBISSexitAfter",
-                  columns= c("After a Buyback","No Prior Buyback"),
-                  title  ="Issue announcements with and without a prior buyback",
-                  caption = "The table presents the long-run abnormal returns (CAR) for firms after issue announcements for events with and without a prior buyback announcement within 48 months.
-We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.",
-
-lastSpecial=T,
-titleontop = T
-  )
-}
-@
-
-%%%%%%%%
-
-%\clearpage
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-if (0){
-  printLatexTable2(
-    Exit_on_BB_Abn_table[reported_times,],
-    Exit_on_BB_Abn_table_cal[reported_times,],
-    columns = c("No Buyback","Buyback"),
-    title="SEOs with and without subsequent buyback",
-    title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-    title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-    caption="The table presents the long-run abnormal returns for firms after issue announcements with and without a subsequent buyback announcement on the full sample for different periods in time.
-Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
-
-label = "tbl:ISSBBexit",
-bigtitleontop=T,
-titleontop=T,
-scale=1,
-lastSpecial=T,
-dorotate=F
-  )
-
-  printLatexTable(BB_for_ISS_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
-                  label  = "tbl:ISSBBexitAfter",
-                  columns= c("post-Issue Buybacks: CAR","Other Buybacks: CAR"),
-                  title  ="Long-run IRATS abnormal return of only the buybacks that are announced within 48 months after an SEO announcement versus the remaining buyback events.",lastSpecial=T)
-}
-@
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-
-if (0){
-  tmp = ISStable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-  colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2015: CAR","t-stat","p-value","2008-2015: CAR","t-stat","p-value")
-  tmp2 = ISStable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
-  colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2015: CAL","t-stat","p-value","2008-2015: CAL","t-stat","p-value")
-
-  printLatexTable2(
-    tmp,
-    tmp2,
-    columns= c("1985-1990","1991-2000","2001-2015","2008-2015"),
-    title="SEOs returns over different time periods",
-    title1 = "Panel A: IRATs Cumulative Abnormal Returns",
-    title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
-    caption="Long-run IRATS cumulative (Panel~A) and Calendar method monthly (Panel~B) abnormal return after issue announcements for different time periods.",
-    label = "tbl:PastFindingsTimeISS",
-    bigtitleontop=T,
-    titleontop=T,
-    scale=1,
-    lastSpecial=T,
-    dorotate=T
-  )
-}
-
-if (0){
-one_table = cbind(BBtable_undertime[,7:12],BB_cal_table_undertime[,7:12],
-                  BBtable_undertime[,19:24],BB_cal_table_undertime[,19:24],
-                  BBtable_undertime[,31:36],BB_cal_table_undertime[,31:36],
-                  BBtable_undertime[,43:48],BB_cal_table_undertime[,43:48]
-)
-#one_table = BBtable_undertime
-printLatexTable(one_table[reported_times,1:12],
-                columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),
-                rowcolumn="1985-1990",
-                title="Buyback returns for the U-index over time",
-                caption="The table presents the long-run abnormal returns for firms after open market repurchase announcements for high and low U-index firms in different time periods and shows significantly larger returns by buybacks announced by high U-index firms compared to those with a low U-index.
-We report both the IRATS cumulative average abnormal returns (CAR, Panel~A) and the calender time method (AR, Panel~B) abnormal returns on the full sample.
-$t$-Statistics are provided and stars indicate significance at the $5\\%$ (*), and $1\\%$ level (**).
-\\\\",
-                label="tbl:PastFindingsTimeUnderBB",metric=c("CAR", "CAR", "AR", "AR"),
-                scale = 1,close=F,lastSpecial=T
-)
-printLatexTable(one_table[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
-printLatexTable(one_table[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
-printLatexTable(one_table[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
-
-}
-
-if (0){
-  paste(printLatexTable(BB_cal_table_undertime[reported_times,1:12],
-                        columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),
-                        rowcolumn="1985-1990",
-                        title="Calendar Method abnormal returns after open market repurchase announcements  for under and over valued companies over different time periods.",
-                        label="tbl:PastFindingsTimeUnderBBcal",
-                        scale = 0.8,close=F,lastSpecial=T
-  ),
-  printLatexTable(BB_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(BB_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(BB_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
-
-}
-
-if (0){
-  paste(printLatexTable(ISStable_undertime[reported_times,1:12],
-                        columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),
-                        rowcolumn="1985-1990",
-                        title="Long-run IRATS abnormal returns after issue announcements  for under and over valued companies over different time periods.",
-                        label="tbl:PastFindingsTimeUnderISS",
-                        scale = 0.9,close=F,lastSpecial=T
-  ),
-  printLatexTable(ISStable_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISStable_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISStable_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
-
-  paste(printLatexTable(ISS_cal_table_undertime[reported_times,1:12],
-                        columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),
-                        rowcolumn="1985-1990",
-                        title="Calendar Method abnormal returns after issue announcements  for under and over valued companies over different time periods.",
-                        label="tbl:PastFindingsTimeUnderISScal",
-                        scale = 0.9,close=F,lastSpecial=T
-  ),
-  printLatexTable(ISS_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISS_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
-  printLatexTable(ISS_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 4F","Over 4F","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
-}
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% INDUSTRIES ANALYSIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-if (0){
-tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
-tmp_cal = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,4:6] ))
-
-  printLatexTable2(
-    tmp[reported_times,1:(3*6)],
-    tmp[reported_times,(3*6+1):36],
-    columns= names(industry_BB)[1:6],
-    columns2= names(industry_BB)[7:12],
-    title="Buyback IRATS Abnormal Returns: Industry Robustness",
-    #title1 = "",
-    #title2 = "",
-    caption=paste("The table presents the long-run abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample.
-We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{Ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples.
-The following regression is run each event month~$j$:
-\\begin{eqnarray*}
-(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
-\\end{eqnarray*}
-where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement.
-$R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively.
-${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively.
-The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms.
-The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.
-The 48 month abnormal return for the full sample is equal to ",round(IRATS_table_all_bb["+48","CAR 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),
-
-label = "tbl:IndustriesBB",
-bigtitleontop=T,
-metric1 = "CAR", metric2 = "CAR",
-#titleontop=T,
-scale=1,
-lastSpecial=T,
-dorotate=T
-  )
-
-  printLatexTable2(
-    tmp_cal[reported_times,1:(3*6)],
-    tmp_cal[reported_times,(3*6+1):36],
-    columns= names(industry_BB)[1:6],
-    columns2= names(industry_BB)[7:12],
-    title="Buyback Calendar Method Abnormal Returns: Industry Robustness",
-    #title1 = "",
-    #title2 = "",
-    caption=paste("The table presents the long-run calendar method abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample.
-Specifically, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015} five-factor model.
-In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio.
-A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors (the difference between the risk-free rate and the return on the equally weighted CRSP index, the monthly return on the size, book-to-market factor, profitability factor and investment factor in month) as the independent variables.
-The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
-The 48 month abnormal return for the full sample is equal to ",round(CAL_table_all_bb["+48","CAL 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),
-    label = "tbl:IndustriesBB_cal",
-    bigtitleontop=T,
-    metric1 = "AR", metric2 = "AR",
-    #titleontop=T,
-    scale=1,
-    lastSpecial=T,
-    dorotate=T
-  )
-
-}
-@
-
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-if (0){
-  latex_render_data_frame(
-    pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)), 
-    title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all buybacks",
-    caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all buybacks.
-The holding period for each buyback is 12 months per event.",
-    label="tbl:allhedgedBB", 
-    columns=NULL,
-    bigtitleontop = T,
-    show_rownames=TRUE,
-    scale = 0.9,
-    digits=1,
-    lastSpecial=F,dorotate=F
-  )
-}
-@
-
-\small
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-if (0){
-
-tmp = industry_BB_features[,c(1:4,9:12)]
-if (colnames(tmp)[1] == "H Idsync.")
-  colnames(tmp) <- paste(colnames(tmp), " (",1:ncol(tmp), ")",sep="")
-latex_render_data_frame(
-  round(tmp,1), 
-  title = "Industry Characteristics",
-  caption="Percentage of high and low idiosyncratic risk  and volatility companies for all industries for which we have at least 100 events in our sample.",
-  label = "tbl:industriesR2Vol",
-  columns=NULL,
-  bigtitleontop = T,
-  show_rownames=TRUE,
-  scale = 1,
-  digits=1,
-  lastSpecial=F,dorotate=T
-)
-}
-@
-\normalsize

### 2017-02-17 process_project_data.R

@@ -9,9 +9,9 @@
 
 rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
 
-source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
-source("../FinanceLibraries/latex_code.R")
-source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
+source("library_files/lib_helpers.R", chdir=TRUE)
+source("library_files/latex_code.R")
+source("library_files/ff_industries_sic.R")
 source("Paper_global_parameters.R")
 
 initial_vars = ls(all = TRUE) # takes time to save and load, so we save only what is needed at the end. 
@@ -1392,472 +1392,6 @@ rm("tmp")
 ########################################################################################################
 # Keep all results ONLY IN THIS FILE just in case we need to rerun or add something... this is temporary
 
-save(list = setdiff(ls(all = TRUE),initial_vars), file = "bb_issuers_new.Rdata")
+save(list = setdiff(ls(all = TRUE),initial_vars), file = "processed_project_data.Rdata")
 
 
-
-########################################################################################################
-########################################################################################################
-########################################################################################################
-### THESE WE DON'T USE ANY MORE
-if (0){
-  
-  ########################################################################################################
-  # Short term analysis
-  
-  load("../FinanceData/created_projects_datasets/BUYBACK_otherdata.Rdata")
-  #logistic_data_all = logistic.data.all.yearly 
-  #yearly.regression.variable = yearly.regression.variable.yearly
[…]

### 2017-02-17 manuscript.Rnw
rename

@@
 if (generate_rnw_data == 1){
-  source("process_project_data.R")
+  source("process_data_for_paper.R")
 } else {
-  load("processed_project_data.Rdata")
+  load("data_for_paper.Rdata")
 }

### 2017-02-17 process_data_for_paper.R

@@ -21,7 +21,7 @@ initial_vars = ls(all = TRUE) # takes time to save and load, so we save only wha
 
 load("../FinanceData/created_projects_datasets/BUYBACKSnew.Rdata")
 # All the data filters are done in here - in case we want to change them for the paper
-source("filter_bbissuers_data.R")
+source("filter_data_for_paper.R")
 # Add some more data
 BUYBACK_DATA$DATASET$DatesMonth <- create_dates_month(BUYBACK_DATA$DATASET$SDC$Event.Date, rownames(BUYBACK_DATA$Risk_Factors_Monthly)) # We don't need this any more, can simplify to only get the dates needed... it's ok for now, as it is now slow
 colnames(BUYBACK_DATA$DATASET$DatesMonth) <- BUYBACK_DATA$DATASET$SDC$permno
@@ -1392,6 +1392,6 @@ rm("tmp")
 ########################################################################################################
 # Keep all results ONLY IN THIS FILE just in case we need to rerun or add something... this is temporary
 
-save(list = setdiff(ls(all = TRUE),initial_vars), file = "processed_project_data.Rdata")
+save(list = setdiff(ls(all = TRUE),initial_vars), file = "data_for_paper.Rdata")
 
 

### 2017-02-17 manuscript.Rnw
files

@@
 
-source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
-source("../FinanceLibraries/latex_code.R")
-source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
+source("library_files/lib_helpers.R", chdir=TRUE)
+source("library_files/latex_code.R")
+source("library_files/ff_industries_sic.R")
 source("Paper_global_parameters.R")

### 2017-02-17 manuscript.Rnw
clean up

@@
 #dev.off();
-#library(knitr); knit2pdf('manuscriptRF.Rnw', texi2dvi='texi2dvi'); file.remove(paste("manuscriptRF",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
+#library(knitr); knit2pdf('manuscript.Rnw', texi2dvi='texi2dvi'); file.remove(paste("manuscript",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
 #dir.create("tmpfiles") # need to comment this if the directory already exists
 # Then to make it into Word: 
-# system("pandoc -s manuscriptRF.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx")
+# system("pandoc -s manuscript.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx")
 
@@
 
-<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade))
-months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all3mshort_risk_factors,min_date=FirstTrade))
-months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all6mshort_risk_factors,min_date=FirstTrade))
-months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))
-months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all24mshort_risk_factors,min_date=FirstTrade))
-months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all36mshort_risk_factors,min_date=FirstTrade))
-months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all48mshort_risk_factors,min_date=FirstTrade))
-
-@
-
 \section{Introduction}
@@
 And indeed, when we value-weight the events (see Table \ref{tbl:valuetable} Panel A) long-term excess returns become statistically insignificantly different from zero when using the total sample of events.
-So the buyback anomaly is not economically important and does not challenge the basic premise that “the market” represented by a value-weighted index is priced correctly.
+So the buyback anomaly is not economically important and does not challenge the basic premise that ???the market???
+represented by a value-weighted index is priced correctly.
 Note, however, if we eliminate the firms with are in the top $25^{th}$ market capitalization percentile (see Table \ref{tbl:valuetable}, Panel~B) the results become again significant, especially for the high U-index firms.
@@
 \label{sec:newindex}
-
-<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-#EU_index_features = scrub(cbind(BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA$DATASET$SDC$pre_vol,BUYBACK_DATA$Valuation_Index))
-#colnames(EU_index_features) <- c("Idiosyncratic Score", "Volatility Score", "U-Index Score")
-#Under_IdioBB_cor = cor(EU_index_features)
-@
 
@@
   cbind(IRATS_table_all_iss,IRATS_table_lowMM_iss,IRATS_table_highMM_iss)[reported_times,],
-  cbind(CAL_table_all_iss,CAL_table_lowvol_iss,CAL_table_highvol_iss)[reported_times,],
+  cbind(CAL_table_all_iss,CAL_table_lowMM_iss,CAL_table_highMM_iss)[reported_times,],
   columns = c("All 4F","All 5F","Low MM 4F","Low MM 5F","High MM 4F","High MM 5F"),
@@
 
-<< fig.width=8, fig.height=5, out.width='\\textwidth', echo=F >>=
-R2_IRATStableBB_plot = R2_IRATStableBB
-R2_IRATStableBB_plot[rownames(R2_IRATStableBB_plot) %in% as.character((-6):(-1)),c("Low Idiosync.: CAR","High Idiosync.: CAR")] <- -R2_IRATStableBB_plot[rownames(R2_IRATStableBB_plot) %in% as.character((-6):(-1)),c("Low Idiosync.: CAR","High Idiosync.: CAR")]
-R2_IRATStable_underBB_plot = R2_IRATStable_underBB
-R2_IRATStable_underBB_plot[rownames(R2_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)] <- -R2_IRATStable_underBB_plot[rownames(R2_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)]
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% VOL ANALYSIS
-
-<< fig.width=8, fig.height=5, out.width='\\textwidth', echo=F >>=
-
-VOL_IRATStableBB_plot = VOL_IRATStableBB
-VOL_IRATStableBB_plot[rownames(VOL_IRATStableBB_plot) %in% as.character((-6):(-1)),c("Low Vol: CAR","High Vol: CAR")] <- -VOL_IRATStableBB_plot[rownames(VOL_IRATStableBB_plot) %in% as.character((-6):(-1)),c("Low Vol: CAR","High Vol: CAR")]
-VOL_IRATStable_underBB_plot = VOL_IRATStable_underBB
-VOL_IRATStable_underBB_plot[rownames(VOL_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)] <- -VOL_IRATStable_underBB_plot[rownames(VOL_IRATStable_underBB_plot) %in% as.character((-6):(-1)),c(1,4,7,10)]
-@
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-17 Paper_global_parameters.R

@@ -5,6 +5,7 @@
 ############################################################################################ 
 # All global parameters of the project
 ############################################################################################ 
+use_major_market_score = 0 # We use all CRSP universe for the scores 
 
 remove_financials_utilities = 1 # Remove the financials and utilities? (Default is 1)
 remove_missing_permnosV2 = 1 # remove also the permnos that are missing when they are found using the NCUSIP-Date? (Default is 1, to avoid any data issues) 
@@ -28,10 +29,11 @@ periods_considered = rbind(
 penny_stock_price_recent = 3 # penny stock threshold price - post 1990
 penny_stock_price_old = 1 # penny stock threshold price - pre 1990
 good_currencies = c("US")
-major_markets = c("N", "NM", "NY", "NK", "New York", "Nasdaq", "NYSE Amex", "American")
+major_markets = c("N", "NM", "NY", "NK",      "New York", "Nasdaq", "NYSE Amex", "American")
 major_markets_crsp = c(11,12,14)
 MIN_SIZE = 0 #micro caps are those with a market cap <300m
 MAX_SIZE = 1e20 #already in million (e6)
+MAX_SIZE_SCORE = 1e20
 MIN_EVENT_SIZE = 0 # Required minimum "event size" (e.g. % of shares repurchased/issued)
 MAX_EVENT_SIZE = 50 # not allow more than this percent of shares for the event
 CROSS_EVENTS_SINCE_LAST_EVENT = 4*365 # we require that there were at most that many days before the previous event
@@ -51,12 +53,8 @@ ISS_allowed_techniques = c("FIRMCOMMITMENT+NEGOTIATEDSALE", "NEGOTIATEDSALE+FIRM
 ##############################################################################
 # U-index parameters
 
-quantile_Uindex = 0.2 # Quantile for defining high/low U-index based on the U-index score
-quantile_R2 = 0.2 # quantile for high and low idiosyncratic risk companies
-quantile_VOL = 0.2 # quantile for high and low volcompanies
-quantile_LEV = 0.2 # quantile for high and low leverage companies
-quantile_EPS = 0.2 # quantile for high and low EPS companies
-
+quantile_simple = 0.2
+quantile_Uindex <- quantile_R2 <- quantile_VOL <- quantile_LEV <- quantile_EPS <- quantile_simple # Quantile for defining high/low U-index based on the U-index score
 years_across_cross_events = 4 # for BB then ISS or vice verca years.
 
[…]

### 2017-02-17 create_project_data.R

@@ -2,20 +2,34 @@
 #  by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
 #  Dual licensed under the MIT or GPL Version 2 licenses.
 
-if (memory.limit()<40*1024) memory.limit(40*1024) # allow at least 40GB of memory to be allocated (Windows)
-##########################################################################################
 # Creates the data for the Buybacks-Issuers paper
+
 ##########################################################################################
+# NOTE: THIS FILE REQUIRES ACCESS TO DATA FROM WRDS. OTHERWISE IT CANNOT BE USED
+##########################################################################################
+
+if (memory.limit()<40*1024) memory.limit(40*1024) # allow at least 40GB of memory to be allocated (Windows)
 
 rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
 
-use_major_market_score = 0 # We use all CRSP universe for the scores 
+
+################################################################################
+##### NOTE: HERE WE NEED TO USE A WRDS USERNAME AND PASSWORD
+################################################################################
+# Used to get WRDS data through the API
+source("../FinanceLibraries/wrds_helpers.R", chdir=TRUE)
+source("~/Documents/WRDS_Drivers/startWRDSconnection.R") # This file has the username pasword for WRDS. These lines below. See wrds_config.R in FinanceLibraries
+# wrds_user <- "my_username"
+# wrds_pass <- "{SAS002}DBCC5712369DE1C65B19864C1564FB850F398DCF"
+# wrds_path <- "C:\\Users\\my_user\\Documents\\WRDS_Drivers\\"
+wrds_handle <- wrdsConnect()
+################################################################################
+################################################################################
 
 source("library_files/lib_helpers.R", chdir=TRUE)
 source("library_files/latex_code.R")
 source("library_files/ff_industries_sic.R")
 source("Paper_global_parameters.R")
-
 
 ###################################################################################################
 # Get the raw data. These are not publicly available
@@ -26,13 +40,6 @@ load("../FinanceData/created_buyback_data/GLOBAL_BUYBACK.Rdata")
[…]

### 2017-02-17 library_files/latex_code.R

@@ -1,7 +1,7 @@
 #  Copyright 2013, Satrapade
 #  by T. Evgeniou, V. Kapartzianis, N. Nassuphis and D. Spinellis
 #  Dual licensed under the MIT or GPL Version 2 licenses.
-#  11/2015 functions printLatexTable and printLatexTable2 added by T. Evgeniou and E. Junqué de Fortuny
+#  11/2015 functions printLatexTable and printLatexTable2 added by T. Evgeniou and E. Junqu?? de Fortuny
 
 
 ######################################################################################
@@ -10,13 +10,32 @@
 
 tostars <- function(x) ifelse(abs(x)<=0.01,"**",ifelse(abs(x)<=0.05,"*",ifelse(abs(x)<=0.1,"$^+$","")))
 
+# THIS NEEDS FIXING...
+latex_print_number <- function(the_value, digits=2,digitssmall = 6, NAvalue = "-"){ 
+  if (!is.numeric(the_value))
+    res = the_value
+  else {
+    if (is.na(the_value)){
+      res = NAvalue
+    } else {
+      res = round(the_value,digits)
+      if (round(the_value,digits) == 0 & the_value !=0)
+        res = ifelse(abs(the_value) < 10^(-digitssmall), 0, format(the_value,scientific=TRUE,digits=digits,big.mark=","))
+    }
+  }
+  res  
+}
+
+#latex_print_number <- function(the_value, digits) ifelse(round(the_value) == the_value, the_value,formatC(the_value,format="f",dig=digits))
+
+
 # CAN EDIT TO PRINT OUT WHATEVER LATEX WE NEED  
-latex_render_data_frame<-function(x,y=NULL, title="",caption="",label="",columns=NULL,bigtitleontop = F,show_rownames=FALSE,red_text="",green_text="",blue_text="",scale=1,digits,lastSpecial=F,dorotate=F, tostars_used = function(r) "") {
+latex_render_data_frame<-function(x,y=NULL, title="",caption="",label="",columns=NULL,bigtitleontop = F,show_rownames=FALSE,red_text="",green_text="",blue_text="",scale=1,digits=2,digitssmall = 6,lastSpecial=F,dorotate=F, tostars_used = NULL, NAvalue = "-",hlinerows = NULL) {
   #Helper functions
   p <- function(...){paste(...)}
[…]

### 2017-02-17 library_files/lib_helpers.R

@@ -1,7 +1,7 @@
 #  Copyright 2013, Satrapade
 #  by T. Evgeniou, V. Kapartzianis, N. Nassuphis and D. Spinellis
 #  Dual licensed under the MIT or GPL Version 2 licenses.
-#  11/2015 functions car_table and calendar_table added by T. Evgeniou and E. Junqué de Fortuny
+#  11/2015 functions car_table and calendar_table added by T. Evgeniou and E. Junqu?? de Fortuny
 
 # Required R libraries (need to be installed - it can take a few minutes the first time you run the project)
 
@@ -16,13 +16,20 @@ if (ifelse(!exists("run_shiny_tool"), T, run_shiny_tool == 0)) { # When deployin
   }
   libraries_used=c("stringr","gtools","foreign","reshape2","digest","timeDate","devtools","knitr","graphics",
                    "grDevices","xtable","sqldf","stargazer","data.table","shiny","htmlwidgets",
-                   "Hmisc","vegan","fpc","GPArotation","FactoMineR","cluster",
+                   "Hmisc","vegan","fpc","GPArotation",
+                   #"FactoMineR",
+                   "cluster","dygraphs",
                    "psych","stringr","googleVis", "png","ggplot2","googleVis", "gridExtra","RcppArmadillo","xts","DescTools")
   
   get_libraries(libraries_used)
+  Rcpp::sourceCpp('lib_helpers.cpp', embeddedR=FALSE)
+} else {
+  lib_helpers_path <- try(suppressWarnings(dirname(sys.frame(1)$ofile)), silent=TRUE)
+  if (class(lib_helpers_path) == "try-error") lib_helpers_path <- "."
+  if (file.exists("lib_helpers.cpp")) lib_helpers_path <- "."
+  Rcpp::sourceCpp(file.path(lib_helpers_path,'lib_helpers.cpp'), embeddedR=FALSE)
 }
 
-Rcpp::sourceCpp('lib_helpers.cpp', embeddedR=FALSE)
 options(stringsAsFactors=FALSE)
 
 
@@ -79,11 +86,15 @@ sharpe<-function(x,exclude_zero=(x!=0), holidays = holidayNYSE() ) {
 
 bps<-function(x,exclude_zero=(x!=0))round(10000*mean(drop(x[exclude_zero])),digits=2)
 
[…]

### 2017-02-17 process_data_for_paper.R

@@ -2,9 +2,14 @@
 #  by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
 #  Dual licensed under the MIT or GPL Version 2 licenses.
 
+# NOTE: These data files need to be available:
+# load("../FinanceData/created_projects_datasets/BUYBACKS.Rdata") # GENERATED BY create_bbissuers_data.R
+# "../FinanceData/rawdata_stambaugh_mispricing_index/Stambaugh_Mispricing_Score.csv" # from http://www.saif.sjtu.edu.cn/facultylist/yyuan/Misp_Score.csv
+# which (see below) generates "../FinanceData/created_projects_datasets/StambaughBUYBACKS.Rdata"
+# ""../FinanceData/created_projects_datasets/Buybacks.Institutional.number.Rdata" created below
 
 ####################################################################################
-# These are one by one the tables in the .Rnw. 
+# These are all the tables used in the .Rnw for the paper
 ####################################################################################
 
 rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
@@ -18,8 +23,7 @@ initial_vars = ls(all = TRUE) # takes time to save and load, so we save only wha
 
 ############################################################################################################
 # GET THE DATA THAT WAS GENERATED BY create_bbissuers_data.R
-
-load("../FinanceData/created_projects_datasets/BUYBACKSnew.Rdata")
+load("../FinanceData/created_projects_datasets/BUYBACKS.Rdata")
 # All the data filters are done in here - in case we want to change them for the paper
 source("filter_data_for_paper.R")
 # Add some more data
@@ -38,7 +42,7 @@ if (do.value.weight == 1){
 }
 
 ############################################################################
[…]

### 2017-02-17 manuscript.Rnw
compiles all the way

@@
 And indeed, when we value-weight the events (see Table \ref{tbl:valuetable} Panel A) long-term excess returns become statistically insignificantly different from zero when using the total sample of events.
-So the buyback anomaly is not economically important and does not challenge the basic premise that ???the market???
-represented by a value-weighted index is priced correctly.
+So the buyback anomaly is not economically important and does not challenge the basic premise that the market represented by a value-weighted index is priced correctly.
 Note, however, if we eliminate the firms with are in the top $25^{th}$ market capitalization percentile (see Table \ref{tbl:valuetable}, Panel~B) the results become again significant, especially for the high U-index firms.
@@
 \bibliographystyle{jf}
-\bibliography{BibliographyInitname}
+\bibliography{Bibliography}
 

### 2017-03-23 manuscript.Rnw
refactor

@@
+% Style files dependencies:
+% - http://faculty.haas.berkeley.edu/stanton/texintro/jf/jf.bst
+% - http://faculty.haas.berkeley.edu/stanton/texintro/rfs/rfs.sty
+% - http://faculty.haas.berkeley.edu/stanton/texintro/sty/versionPO.sty
+
 << eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-#dev.off();
-#library(knitr); knit2pdf('manuscript.Rnw', texi2dvi='texi2dvi'); file.remove(paste("manuscript",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
+# dev.off();
+# library(knitr); knit2pdf('manuscript.Rnw', texi2dvi='texi2dvi'); file.remove(paste("manuscript",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
 #dir.create("tmpfiles") # need to comment this if the directory already exists
@@
   source("process_data_for_paper.R")
-} else {
+}
+
 load("data_for_paper.Rdata")
-}
-
-source("library_files/lib_helpers.R", chdir=TRUE)
-source("library_files/latex_code.R")
-source("library_files/ff_industries_sic.R")
+
+source("helpers/lib_helpers.R", chdir=TRUE)
+source("helpers/latex_code.R")
+source("helpers/ff_industries_sic.R")
 source("Paper_global_parameters.R")
@@
 We find that both the \cite{FamaFrench2015} and \cite{StambaughYuan2016} models explain the equity issue anomaly, but not the buyback anomaly.
-Moreover, the \cite{FamaFrench2015} model does a better job than the \cite{StambaughYuan2016} one: during the 48 months after the buyback announcement the four factor model produces (statistically significant at the 1$\%$ level) excess returns of \Sexpr{round(CAL_table_all_bb["+48","CAL 5F"],2)}$\%$ per month versus \Sexpr{round(CAL_table_all_bb["+48","CAL 3F"],2)}$\%$  per month with the four factor model.
+Moreover, the \cite{FamaFrench2015} model does a better job than the \cite{StambaughYuan2016} one: during the 48 months after the buyback announcement the four factor model produces (statistically significant at the 1$\%$ level) excess returns of \Sexpr{round(buyback_announcements_table$CAL$all["+48","CAL 5F"],2)}$\%$ per month versus \Sexpr{round(buyback_announcements_table$CAL$all["+48","CAL 3F"],2)}$\%$  per month with the four factor model.
 Unlike other anomalies that disappear over time \citep{McLean2016}, the buyback anomaly persists over time and does not decline in recent years.
@@
 Combining total volatility and standardized idiosyncratic volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index (EU-Index) improves the predictability of excess returns.
-In particular, during the four years following the buyback announcement, the high EU-Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
-Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.
+In particular, during the four years following the buyback announcement, the high EU-Index portfolio generates an excess return of \Sexpr{round(buybacks_eu_tables$CAL["+48",13+6],2)}$\%$ per month with the Calendar Time event study method.
+Using the IRATS method the cumulative excess return reaches \Sexpr{round(buybacks_eu_tables$IRATS["+48",19],2)}$\%$ after 48 months.
 On the other hand, we show that the Mispricing Measure (MM) developed by \cite{Stambaugh2015} on the basis of 11 anomalies is not helpful in predicting long term excess returns after buyback authorization announcements.
@@
 Table \ref{tbl:descriptive} summarizes the key data in this study.
-The average percent of shares authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).
+The average percent of shares authorized for these firms was \Sexpr{data_summary$bb["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{data_summary$bb["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{data_summary$bb["Market cap.", "Mean"]} Million (median of \$\Sexpr{data_summary$bb["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{data_summary$bb["BE/ME", "Mean"]} (median of \Sexpr{data_summary$bb["BE/ME", "Median"]}).
 
@@
 Our final sample contains \Sexpr{length(cusip_iss)} events made by \Sexpr{length(unique(cusip_iss))} firms.
-The average percent of shares issued (for the events for which this information was available) was \Sexpr{datasummaryISS["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryISS["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{datasummaryISS["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryISS["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryISS["BE/ME", "Mean"]} (median of \Sexpr{datasummaryISS["BE/ME", "Median"]}).
+The average percent of shares issued (for the events for which this information was available) was \Sexpr{data_summary$iss["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{data_summary$iss["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{data_summary$iss["Market cap.", "Mean"]} Million (median of \$\Sexpr{data_summary$iss["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{data_summary$iss["BE/ME", "Mean"]} (median of \Sexpr{data_summary$iss["BE/ME", "Median"]}).
 Note also from Table \ref{tbl:descriptive} that the average and median Mispricing Measure developed by \cite{Stambaugh2015} is higher for equity issuers than for buyback stocks, which is consistent with the hypothesis that equity issuers are more likely to be overvalued than share repurchasers.
@@
 
-The results in Table~\ref{tbl:priorBuybacks}, Panel~A, show that using a five-factor the excess returns are statistically significantly positive over all investment horizons and reach \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ after 4 years (t=\Sexpr{IRATS_table_all_bb["+48",5]}).
-The results with the 4 factor model are even stronger with excess returns of \Sexpr{round(IRATS_table_all_bb["+48","CAR 3F"],2)}$\%$ (t=\Sexpr{round(IRATS_table_all_bb["+48",2],2)}) after 4 years.
+The results in Table~\ref{tbl:priorBuybacks}, Panel~A, show that using a five-factor the excess returns are statistically significantly positive over all investment horizons and reach \Sexpr{round(buyback_announcements_table$IRATS$all["+48","CAR 5F"],2)}$\%$ after 4 years (t=\Sexpr{buyback_announcements_table$IRATS$all["+48",5]}).
+The results with the 4 factor model are even stronger with excess returns of \Sexpr{round(buyback_announcements_table$IRATS$all["+48","CAR 3F"],2)}$\%$ (t=\Sexpr{round(buyback_announcements_table$IRATS$all["+48",2],2)}) after 4 years.
 In all the tables we also calculate cumulative excess returns in the 6 months prior to the buyback.
-Consistent with past research [see e.g., \citep{PeyerVermaelen2009}] buyback authorization announcements are preceded by significant negative excess returns of around \Sexpr{round(IRATS_table_all_bb[reported_times[1],1],0)}$\%$.
+Consistent with past research [see e.g., \citep{PeyerVermaelen2009}] buyback authorization announcements are preceded by significant negative excess returns of around \Sexpr{round(buyback_announcements_table$IRATS$all[reported_times[1],1],0)}$\%$.
 This is consistent with the hypothesis that the typical repurchase announcement is triggered by a stock price decline that insiders may feel is not justified given their long-term prospects about the company.
@@
 Note that unlike \cite{PeyerVermaelen2009} we do not consider the stated reasons for the buyback in the press release, hence we define different thresholds for the high U-index and low U-index buyback firms.
-We end up with \Sexpr{sum(company_subset_undervalued_bb)} ``high U-index'' buyback stocks (\Sexpr{round(sum(company_subset_undervalued_bb)/length(cusip_bb)*100,2)}\% of all buyback events), and \Sexpr{sum(company_subset_overvalued_bb)} ``low U-index'' ones (\Sexpr{round(sum(company_subset_overvalued_bb)/length(cusip_bb)*100,2)}\% of all buyback events).
+We end up with \Sexpr{sum(company_subset$bb$undervalued)} ``high U-index'' buyback stocks (\Sexpr{round(sum(company_subset$bb$undervalued)/length(cusip_bb)*100,2)}\% of all buyback events), and \Sexpr{sum(company_subset$bb$overvalued)} ``low U-index'' ones (\Sexpr{round(sum(company_subset$bb$overvalued)/length(cusip_bb)*100,2)}\% of all buyback events).
 The distribution of the U-index of all buyback events is shown in Figure~\ref{fig:undervaluationindex}.
@@
 As in Panel A, excess returns are larger when the Stambaugh-Yuan four factor model is used as a benchmark.
-Specifically, during the 48-month period after the buyback announcement firms earn excess returns of \Sexpr{round(CAL_table_all_bb["+48","CAL 3F"],2)}$\%$ (t=\Sexpr{round(CAL_table_all_bb["+48",2],2)}) and \Sexpr{round(CAL_table_all_bb_undervaluation["+48","U:CAL3F"],2)}$\%$ (t=\Sexpr{round(CAL_table_all_bb_undervaluation["+48",2],2)}) in the case of high U-index firms.
+Specifically, during the 48-month period after the buyback announcement firms earn excess returns of \Sexpr{round(buyback_announcements_table$CAL$all["+48","CAL 3F"],2)}$\%$ (t=\Sexpr{round(buyback_announcements_table$CAL$all["+48",2],2)}) and \Sexpr{round(buyback_announcements_table$CAL$undervaluation["+48","U:CAL3F"],2)}$\%$ (t=\Sexpr{round(buyback_announcements_table$CAL$undervaluation["+48",2],2)}) in the case of high U-index firms.
 So we can conclude that the buyback anomaly and the relevance of the U-index survive the \cite{FamaFrench2015} and \cite{StambaughYuan2016} models.
@@
 For the total sample, the Fama-French five factor model fully explains the anomaly, regardless of the method to measure abnormal returns.
-However, using IRATS, the 4 factor model produces significant positive excess returns of \Sexpr{round(IRATS_table_all_iss["+48","CAR 3F"],2)}$\%$ after 4 years (t=\Sexpr{round(IRATS_table_all_iss["+48",2],2)}).
-With the calendar time method, the excess returns become less significant (t=\Sexpr{round(CAL_table_all_iss["+48",2],2)}) but have the same magnitude (\Sexpr{round(CAL_table_all_iss["+48","CAL 3F"],2)}$\%$ per month or \Sexpr{48*round(CAL_table_all_iss["+48","CAL 3F"],2)}$\%$  after 48 months).
+However, using IRATS, the 4 factor model produces significant positive excess returns of \Sexpr{round(issuers_announcements_table$IRATS$all["+48","CAR 3F"],2)}$\%$ after 4 years (t=\Sexpr{round(issuers_announcements_table$IRATS$all["+48",2],2)}).
+With the calendar time method, the excess returns become less significant (t=\Sexpr{round(issuers_announcements_table$CAL$all["+48",2],2)}) but have the same magnitude (\Sexpr{round(issuers_announcements_table$CAL$all["+48","CAL 3F"],2)}$\%$ per month or \Sexpr{48*round(issuers_announcements_table$CAL$all["+48","CAL 3F"],2)}$\%$  after 48 months).
 When splitting up the sample according to MM, the Fama-French five factor model shows no significant long-term excess returns regardless of the investment horizon and the method to measure excess returns.
@@
 
-Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(IRATS_table_all_iss["-6","CAR 3F"],2)}$\%$ in the 6 months prior to the equity issue.
+Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(issuers_announcements_table$IRATS$all["-6","CAR 3F"],2)}$\%$ in the 6 months prior to the equity issue.
 However, the lack of post announcement {\it negative} excess returns shows that this was not reflecting ''irrational exuberance'' but rather that, for example, these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.
@@
 Table~\ref{tbl:PastFindingsTimeBB} shows that, regardless of the time period chosen or the method to calculate excess returns, the buyback anomaly remains economically and statistically significant and there is no clear time trend in the data that suggests that markets have become more efficient over time.
-There is one exception to the consistency between the IRATS and the Calendar Time results: in the period of 1991-2000, the IRATS method generates excess returns after 48 months of \Sexpr{BBtable_time["+48",10]}$\%$ (t=\Sexpr{BBtable_time["+48",11]}) but the Calendar Time method produces statistically insignificant excess returns of \Sexpr{BBtable_time_cal["+48",10]}$\%$ per month.
+There is one exception to the consistency between the IRATS and the Calendar Time results: in the period of 1991-2000, the IRATS method generates excess returns after 48 months of \Sexpr{buyback_returns_periods_table$IRATS["+48",10]}$\%$ (t=\Sexpr{buyback_returns_periods_table$IRATS["+48",11]}) but the Calendar Time method produces statistically insignificant excess returns of \Sexpr{buyback_returns_periods_table$CAL["+48",10]}$\%$ per month.
 This result appears to also be inconsistent with \cite{PeyerVermaelen2009}.
@@
 We report the returns (unhedged strategy) and excess returns (hedged strategy) of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns.
-Specifically, at the end of \Sexpr{lastyear} the cumulative excess returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$.
+Specifically, at the end of \Sexpr{lastyear} the cumulative excess returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months[["1"]],1),1)}$\%$, \Sexpr{round(tail(months[["3"]],1),1)}$\%$, \Sexpr{round(tail(months[["6"]],1),1)}$\%$, \Sexpr{round(tail(months[["12"]],1),1)}$\%$, \Sexpr{round(tail(months[["24"]],1),1)}$\%$, \Sexpr{round(tail(months[["36"]],1),1)}$\%$ and \Sexpr{round(tail(months[["48"]],1),1)}$\%$.
 This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer.
@@
 We define two types of events: ``low volatility'' and ``high volatility'' events, depending on whether volatility was in the top or bottom \Sexpr{round(100*quantile_VOL,2)}$\%$ of the volatilities of all CRSP companies before the event.
-In total we have \Sexpr{sum(High_VOL_eventsBB)} ``high volatility'' buybacks-events and \Sexpr{sum(Low_VOL_eventsBB)} ``low volatility'' ones.
+In total we have \Sexpr{sum(VOL_events$bb$highvol)} ``high volatility'' buybacks-events and \Sexpr{sum(VOL_events$bb$lowvol)} ``low volatility'' ones.
 In the smaller equity issue sample 804 events are classified as high and low volatility.
@@
 Moving on to buybacks, Table~\ref{tbl:VOLunderBB} also shows a strong positive relation between volatility and excess returns independent of the factor model used.
-For example, using IRATS and the five factor model the cumulative average abnormal return is only \Sexpr{round(IRATS_table_lowvol_BB["+48","CAR 5F"],2)}$\%$  (t=\Sexpr{round(IRATS_table_lowvol_BB["+48",5],2)}) after 48 months in the low volatility sample and \Sexpr{round(IRATS_table_highvol_BB["+48","CAR 5F"],2)}$\%$ (t=\Sexpr{round(IRATS_table_highvol_BB["+48",5],2)}) in the high volatility sample.
-This time the calendar time method confirms the IRATS result: insignificant monthly excess returns of \Sexpr{round(CAL_table_lowvol_BB["+48","CAL 5F"],2)}$\%$  (t=\Sexpr{round(CAL_table_lowvol_BB["+48",5],2)}) in the low volatility sample versus significant positive monthly excess returns of \Sexpr{round(CAL_table_highvol_BB["+48","CAL 5F"],2)}$\%$ (t=\Sexpr{round(CAL_table_highvol_BB["+48",5],2)}) in the high volatility sample.
+For example, using IRATS and the five factor model the cumulative average abnormal return is only \Sexpr{round(buybacks_issuers_volatility_table$IRATS$bb$lowvol["+48","CAR 5F"],2)}$\%$  (t=\Sexpr{round(buybacks_issuers_volatility_table$IRATS$bb$lowvol["+48",5],2)}) after 48 months in the low volatility sample and \Sexpr{round(buybacks_issuers_volatility_table$IRATS$bb$highvol["+48","CAR 5F"],2)}$\%$ (t=\Sexpr{round(buybacks_issuers_volatility_table$IRATS$bb$highvol["+48",5],2)}) in the high volatility sample.
+This time the calendar time method confirms the IRATS result: insignificant monthly excess returns of \Sexpr{round(buybacks_issuers_volatility_table$CAL$bb$lowvol["+48","CAL 5F"],2)}$\%$  (t=\Sexpr{round(buybacks_issuers_volatility_table$CAL$bb$lowvol["+48",5],2)}) in the low volatility sample versus significant positive monthly excess returns of \Sexpr{round(buybacks_issuers_volatility_table$CAL$bb$highvol["+48","CAL 5F"],2)}$\%$ (t=\Sexpr{round(buybacks_issuers_volatility_table$CAL$bb$highvol["+48",5],2)}) in the high volatility sample.
 
@@
 Table~\ref{tbl:IdiosyncraticunderBB} shows the IRATS and Calendar Time abnormal returns for high and low idiosyncratic risk events-companies, both for buybacks and equity issues.
-Focusing on buybacks and IRATS, after 48 months high idiosyncratic buyback stocks earn \Sexpr{IRATS_table_highidio_BB["+48","CAR 5F"]}$\%$ (t = \Sexpr{IRATS_table_highidio_BB["+48",5]}) when we use the five factor model and \Sexpr{IRATS_table_highidio_BB["+48","CAR 3F"]}$\%$ (t = \Sexpr{IRATS_table_highidio_BB["+48",2]}) when we use the four factor model.
+Focusing on buybacks and IRATS, after 48 months high idiosyncratic buyback stocks earn \Sexpr{buybacks_issuers_idiosyncratic_table$IRATS$bb$highidio["+48","CAR 5F"]}$\%$ (t = \Sexpr{buybacks_issuers_idiosyncratic_table$IRATS$bb$highidio["+48",5]}) when we use the five factor model and \Sexpr{buybacks_issuers_idiosyncratic_table$IRATS$bb$highidio["+48","CAR 3F"]}$\%$ (t = \Sexpr{buybacks_issuers_idiosyncratic_table$IRATS$bb$highidio["+48",2]}) when we use the four factor model.
 When we use the five factor model  low idiosyncratic risk announcements are not followed by significant excess returns.
-Although the four factor model does show significant 48-month excess returns of \Sexpr{IRATS_table_lowidio_BB["+48","CAR 3F"]}$\%$ (t=\Sexpr{IRATS_table_lowidio_BB["+48",2]}) after low idiosyncratic risk events, the excess returns are more than 3 times smaller than for high idiosyncratic risk firms.
+Although the four factor model does show significant 48-month excess returns of \Sexpr{buybacks_issuers_idiosyncratic_table$IRATS$bb$lowidio["+48","CAR 3F"]}$\%$ (t=\Sexpr{buybacks_issuers_idiosyncratic_table$IRATS$bb$lowidio["+48",2]}) after low idiosyncratic risk events, the excess returns are more than 3 times smaller than for high idiosyncratic risk firms.
 The results using the Calendar Time method confirm these findings: only buybacks announced by firms with high idiosyncratic risk are followed by significant long-term excess returns, both for the five and four factor model.
@@
 Overall we see that although high U-index firms tend to have high standardized idiosyncratic risk and high volatility, while high idiosyncratic risk firms tend to also have high volatility, the overlap is not very high.
-For example from Table~\ref{tbl:underidioallBB} we see that  only \Sexpr{round(Under_IdioBB["High Vol.","H Idiosync."],1)}$\%$ of the high volatility stocks that are classified as having either high or low standardized  idiosyncratic risk - note that we only consider the  \Sexpr{round(100*quantile_R2,2)}$\%$ tails - have high standardized idiosyncratic risk.
-From Table~\ref{tbl:underidioallBBcor} we also infer that the correlation between standardized idiosyncratic risk and volatility scores is only \Sexpr{round(Under_IdioBB_cor["Volatility Score","Idiosyncratic Score"]*100,1)}$\%$.
+For example from Table~\ref{tbl:underidioallBB} we see that  only \Sexpr{round(buybacks_firm_characteristics_table["High Vol.","H Idiosync."],1)}$\%$ of the high volatility stocks that are classified as having either high or low standardized  idiosyncratic risk - note that we only consider the  \Sexpr{round(100*quantile_R2,2)}$\%$ tails - have high standardized idiosyncratic risk.
+From Table~\ref{tbl:underidioallBBcor} we also infer that the correlation between standardized idiosyncratic risk and volatility scores is only \Sexpr{round(buybacks_correlations_table["Volatility Score","Idiosyncratic Score"]*100,1)}$\%$.
 We also see that the Mispricing Measure of \cite{Stambaugh2015} is not related to the other measures in the case of buybacks
@@
 Figure~\ref{fig:Eundervaluationindex} shows the distribution of the EU-index.
-The index has a symmetric distribution with a mean of \Sexpr{round(mean(EUindex_bb),2)}.
+The index has a symmetric distribution with a mean of \Sexpr{round(mean(eu_index$bb),2)}.
 Table~\ref{tbl:EUrelations} shows how the EU-index relates to a number of firm characteristics.
@@
 <<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-tmp_market_cap = round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb %in% c(5:6)]),1)
+tmp_market_cap = round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[eu_index$bb %in% c(5:6)]),1)
 @
@@
 The table also shows a strong negative relation between market-to-book ratios and market capitalization and the EU index, which is not surprising as these are components of the index.
-It should be noted that the EU6 portfolio (consisting of all firms with EU index equal to 6) is composed of very small stocks with an average market capitalization of \$\Sexpr{round(EU_relations["Market Cap.","EU6"],1)} million.
+It should be noted that the EU6 portfolio (consisting of all firms with EU index equal to 6) is composed of very small stocks with an average market capitalization of \$\Sexpr{round(eu_firm_characteristics_table["Market Cap.","EU6"],1)} million.
 The average market capitalization of portfolios with long term (after 48 months) monthly excess return of larger than 0.5$\%$ (i.e.
@@
 
-Tables  \ref{tbl:EUunderBB} and \ref{tbl:EUunderBBcal} show respectively the IRATS and Calendar Time monthly abnormal returns for all values of the EU-index using the five factor model.\footnote{The results using the four factor model are similar and are available upon request.} Focusing on IRATS, as the EU-index increases, the long term (48 months) abnormal returns increase (from \Sexpr{round(EU_IRATStable_bb["+48",1],2)}$\%$ to \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$).
+Tables  \ref{tbl:EUunderBB} and \ref{tbl:EUunderBBcal} show respectively the IRATS and Calendar Time monthly abnormal returns for all values of the EU-index using the five factor model.\footnote{The results using the four factor model are similar and are available upon request.} Focusing on IRATS, as the EU-index increases, the long term (48 months) abnormal returns increase (from \Sexpr{round(buybacks_eu_tables$IRATS["+48",1],2)}$\%$ to \Sexpr{round(buybacks_eu_tables$IRATS["+48",19],2)}$\%$).
 Figure~\ref{fig:Epastall} show the same results over time for each EU-index.
-Long-term cumulative excess returns after 48 months are becoming statistically significantly positive at EU-index levels of 3 and higher, and then steadily increase from \Sexpr{round(EU_IRATStable_bb["+48",10],2)}$\%$ to \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$.
+Long-term cumulative excess returns after 48 months are becoming statistically significantly positive at EU-index levels of 3 and higher, and then steadily increase from \Sexpr{round(buybacks_eu_tables$IRATS["+48",10],2)}$\%$ to \Sexpr{round(buybacks_eu_tables$IRATS["+48",19],2)}$\%$.
 The Calendar Time results in Table~\ref{tbl:EUunderBBcal} are similar although they only show significance starting at EU-index levels of 5.
-Investing in the very high EU index firms (EU=6) generates alphas of \Sexpr{round(EU_CALtable_bb["+48",19],2)}$\%$ per month for 48 months.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
+Investing in the very high EU index firms (EU=6) generates alphas of \Sexpr{round(buybacks_eu_tables$CAL["+48",19],2)}$\%$ per month for 48 months.\footnote{We also calculated the returns of a hedged strategy similar to Figure~\ref{fig:ReturnsBB} (Panel~B).
 Starting in \Sexpr{firstyear} we form a portfolio of all stocks that announced a buyback during the previous $N$ months and hold the stock for $N$ months.
-The 12-month holding period high EU-index portfolio has average annual excess returns of \Sexpr{round(pnl_stats(High_EU_BB_Hedged)[1],1)}$\%$, while the low EU-index one earns only \Sexpr{round(pnl_stats(Low_EU_BB_Hedged)[1],1)}$\%$ annual excess returns.
-For the 48-month holding periods the high and low EU-index portfolio earn annual excess returns of  respectively, \Sexpr{round(pnl_stats(High_EU_BB_Hedged48m)[1],1)}$\%$ and \Sexpr{round(pnl_stats(Low_EU_BB_Hedged48m)[1],1)}$\%$.}
+The 12-month holding period high EU-index portfolio has average annual excess returns of \Sexpr{round(pnl_stats(eu_bb_data$pnl_hedged$high[["12"]])[1],1)}$\%$, while the low EU-index one earns only \Sexpr{round(pnl_stats(eu_bb_data$pnl_hedged$low[["12"]])[1],1)}$\%$ annual excess returns.
+For the 48-month holding periods the high and low EU-index portfolio earn annual excess returns of  respectively, \Sexpr{round(pnl_stats(eu_bb_data$pnl_hedged$high[["48"]])[1],1)}$\%$ and \Sexpr{round(pnl_stats(eu_bb_data$pnl_hedged$low[["48"]])[1],1)}$\%$.}
 
@@
 We define low EU-index firms to be those for which the EU-index is 0-3, and high for which it is 4-6 (the index takes values from 0 to 6).
-With this definition we have \Sexpr{sum(low_EU_bb)} low EU-index and \Sexpr{sum(high_EU_bb)}  high EU-index firms in our sample.
+With this definition we have \Sexpr{sum(eu_bb_data$binary$low)} low EU-index and \Sexpr{sum(eu_bb_data$binary$high)}  high EU-index firms in our sample.
 
 Tables \ref{tbl:EUTimeUnderBB} and \ref{tbl:EUTimeUnderBBcal} indicate that the EU-index is robust over time, with the exception of the 1985-1990 period.
-However during this period our high EU index sample only contains \Sexpr{ECAL_table_undervaluation_time_bb["Observations",1]} observations which results in statistically insignificant excess returns.% beyond the 12 month horizon.
+However during this period our high EU index sample only contains \Sexpr{buyback_returns_undervaluation_tables$CAL["Observations",1]} observations which results in statistically insignificant excess returns.% beyond the 12 month horizon.
 
 << fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
-tmp = pnl_matrix(remove_initialization_time(High_EU_BB_Hedged,min_date=FirstTrade))
+tmp = pnl_matrix(remove_initialization_time(eu_bb_data$pnl_hedged$high[["12"]],min_date=FirstTrade))
 tmp1 = pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))
@@
 Comparing these samples with the samples in Panel A shows that adding the Mispricing Measure does not improve the predictability of the EU index in any consistent way.
-For example, while the high MM/low EU sample does worse (\Sexpr{round(Stam_IRATStable_EU_BB["+48","High Mis.: L.
-EU CAR"],2)}$\%$) than the low EU sample by itself (\Sexpr{round(EU_IRATStableBB["+48","Low EU: CAR"],2)}$\%$),  investing in low MM/high EU stocks generates lower long-term 48-month excess returns (\Sexpr{round(Stam_IRATStable_EU_BB["+48","H.
-EU CAR"],2)}$\%$) than simply buying high EU stocks (\Sexpr{round(EU_IRATStableBB["+48","High EU: CAR"],2)}$\%$).
-The low MM/low EU sample generates basically the same excess returns (\Sexpr{round(Stam_IRATStable_EU_BB["+48","Low Mis.: L.
-EU CAR"],2)}$\%$) as the low EU sample by itself (\Sexpr{round(EU_IRATStableBB["+48","Low EU: CAR"],2)}$\%$).
+For example, while the high MM/low EU sample does worse (\Sexpr{round(buyback_returns_index_table$IRATS$Stam_EU["+48","High Mis.: L.
+EU CAR"],2)}$\%$) than the low EU sample by itself (\Sexpr{round(buyback_returns_index_table$IRATS$EU["+48","Low EU: CAR"],2)}$\%$),  investing in low MM/high EU stocks generates lower long-term 48-month excess returns (\Sexpr{round(buyback_returns_index_table$IRATS$Stam_EU["+48","H.
+EU CAR"],2)}$\%$) than simply buying high EU stocks (\Sexpr{round(buyback_returns_index_table$IRATS$EU["+48","High EU: CAR"],2)}$\%$).
+The low MM/low EU sample generates basically the same excess returns (\Sexpr{round(buyback_returns_index_table$IRATS$Stam_EU["+48","Low Mis.: L.
+EU CAR"],2)}$\%$) as the low EU sample by itself (\Sexpr{round(buyback_returns_index_table$IRATS$EU["+48","Low EU: CAR"],2)}$\%$).
 So, adding the Mispricing Measure of \cite{Stambaugh2015} does not help forecasting long-term excess returns after buyback announcements.
@@
 We combine these characteristics with the Undervaluation Index developed by \cite{PeyerVermaelen2009} in a new measure of the likelihood that the buyback is driven by undervaluation: the EU index or Enhanced Undervaluation Index.
-Investing in very high EU index firms generates excess returns of \Sexpr{round(EU_CALtable_bb["+48",19],2)}$\%$ per month during the 48 months after the buyback announcement.
+Investing in very high EU index firms generates excess returns of \Sexpr{round(buybacks_eu_tables$CAL["+48",19],2)}$\%$ per month during the 48 months after the buyback announcement.
 However investing in high EU index firms  implies investing in small caps and micro-caps, which may explain partially why the anomaly persists as these firms may not satisfy, for example, liquidity risk constraints of many funds.
@@
 <<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-Descriptive_stats_BB1 <- apply(Descriptive_stats_BB,2,function(r) as.character(round(r,2)))
-rownames(Descriptive_stats_BB1) <- rownames(Descriptive_stats_BB)
-Descriptive_stats_BB1 = rbind(Descriptive_stats_BB1,rep(length(BUYBACK_DATA$DATASET$SDC$CUSIP), 5))
-rownames(Descriptive_stats_BB1)[nrow(Descriptive_stats_BB1)] <- "Observations"
-colnames(Descriptive_stats_BB1) <- NULL
-
-Descriptive_stats_ISS1 <- apply(Descriptive_stats_ISS,2,function(r) as.character(round(r,2)))
-rownames(Descriptive_stats_ISS1) <- rownames(Descriptive_stats_ISS)
-Descriptive_stats_ISS1 = rbind(Descriptive_stats_ISS1,rep(length(ISSUERS_DATA$DATASET$SDC$CUSIP),5))
-rownames(Descriptive_stats_ISS1)[nrow(Descriptive_stats_ISS1)] <- "Observations"
-colnames(Descriptive_stats_ISS1) <- NULL
+descriptive_stats$bb1 <- apply(descriptive_stats$bb,2,function(r) as.character(round(r,2)))
+rownames(descriptive_stats$bb1) <- rownames(descriptive_stats$bb)
+descriptive_stats$bb1 = rbind(descriptive_stats$bb1,rep(length(BUYBACK_DATA$DATASET$SDC$CUSIP), 5))
+rownames(descriptive_stats$bb1)[nrow(descriptive_stats$bb1)] <- "Observations"
+colnames(descriptive_stats$bb1) <- NULL
+
+descriptive_stats$iss1 <- apply(descriptive_stats$iss,2,function(r) as.character(round(r,2)))
+rownames(descriptive_stats$iss1) <- rownames(descriptive_stats$iss)
+descriptive_stats$iss1 = rbind(descriptive_stats$iss1,rep(length(ISSUERS_DATA$DATASET$SDC$CUSIP),5))
+rownames(descriptive_stats$iss1)[nrow(descriptive_stats$iss1)] <- "Observations"
+colnames(descriptive_stats$iss1) <- NULL
 
@@
             c("Mean","Median","Standard Dev.", "$20^{th}$ Percentile","$80^{th}$ Percentile"),
-            Descriptive_stats_BB1,
+            descriptive_stats$bb1,
             c("", "", "", "",""),
@@
             c("Mean","Median","Standard Dev.", "$20^{th}$ Percentile","$80^{th}$ Percentile"),
-            Descriptive_stats_ISS1
-)
-
-tmp = cbind(c("Panel A: Buybacks","",rownames(Descriptive_stats_BB1),"","Panel B: SEOs","",rownames(Descriptive_stats_ISS1)),tmp)
+            descriptive_stats$iss1
+)
+
+tmp = cbind(c("Panel A: Buybacks","",rownames(descriptive_stats$bb1),"","Panel B: SEOs","",rownames(descriptive_stats$iss1)),tmp)
 
@@
 printLatexTable2(
-  cbind(IRATS_table_all_bb,IRATS_table_all_bb_undervaluation)[reported_times,],
-  cbind(CAL_table_all_bb,CAL_table_all_bb_undervaluation)[reported_times,],
+  cbind(buyback_announcements_table$IRATS$all,buyback_announcements_table$IRATS$undervaluation)[reported_times,],
+  cbind(buyback_announcements_table$CAL$all,buyback_announcements_table$CAL$undervaluation)[reported_times,],
   columns = c("All 4F","All 5F","High U-index 4F","Low U-index 4F","High U-index 5F","Low U-index 5F"),
@@
 printLatexTable2(
-  cbind(CAL_table_all_bb_value,CAL_table_all_bb_undervaluation_value)[reported_times,],
-  cbind(CAL_table_all_bb_valueL,CAL_table_all_bb_undervaluation_valueL)[reported_times,],
+  cbind(value_weighted_table$all_firms$all,value_weighted_table$all_firms$undervaluation)[reported_times,],
+  cbind(value_weighted_table$no_large_firms$all,value_weighted_table$no_large_firms$undervaluation)[reported_times,],
   columns = c("All 4F","All 5F","High U-index 4F","Low U-index 4F","High U-index 5F","Low U-index 5F"),
@@
 printLatexTable2(
-  cbind(IRATS_table_all_iss,IRATS_table_lowMM_iss,IRATS_table_highMM_iss)[reported_times,],
-  cbind(CAL_table_all_iss,CAL_table_lowMM_iss,CAL_table_highMM_iss)[reported_times,],
+  cbind(issuers_announcements_table$IRATS$all,issuers_announcements_table$IRATS$lowMM,issuers_announcements_table$IRATS$highMM)[reported_times,],
+  cbind(issuers_announcements_table$CAL$all,issuers_announcements_table$CAL$lowMM,issuers_announcements_table$CAL$highMM)[reported_times,],
   columns = c("All 4F","All 5F","Low MM 4F","Low MM 5F","High MM 4F","High MM 5F"),
@@
 <<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-tmp = BBtable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
+tmp = buyback_returns_periods_table$IRATS[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
 colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2015: CAR","t-stat","p-value","2008-2015: CAR","t-stat","p-value")
-tmp2 = BBtable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
+tmp2 = buyback_returns_periods_table$CAL[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
 colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2015: CAL","t-stat","p-value","2008-2015: CAL","t-stat","p-value")
@@
 printLatexTable2(
-  cbind(IRATS_table_lowvol_BB,IRATS_table_highvol_BB,IRATS_table_lowvol_iss,IRATS_table_highvol_iss)[reported_times,],
-  cbind(CAL_table_lowvol_BB,CAL_table_highvol_BB,CAL_table_lowvol_iss,CAL_table_highvol_iss)[reported_times,],
+  cbind(buybacks_issuers_volatility_table$IRATS$bb$lowvol,buybacks_issuers_volatility_table$IRATS$bb$highvol,buybacks_issuers_volatility_table$IRATS$iss$lowvol,buybacks_issuers_volatility_table$IRATS$iss$highvol)[reported_times,],
+  cbind(buybacks_issuers_volatility_table$CAL$bb$lowvol,buybacks_issuers_volatility_table$CAL$bb$highvol,buybacks_issuers_volatility_table$CAL$iss$lowvol,buybacks_issuers_volatility_table$CAL$iss$highvol)[reported_times,],
   columns= c("Buyback: Low Vol. 4F","5F","High Vol. 4F","5F","SEOs: Low Vol. 4F","5F","High Vol. 4F","5F"),
@@
 printLatexTable2(
-  cbind(IRATS_table_lowidio_BB,IRATS_table_highidio_BB,IRATS_table_lowidio_iss,IRATS_table_highidio_iss)[reported_times,],
-  cbind(CAL_table_lowidio_BB,CAL_table_highidio_BB,CAL_table_lowidio_iss,CAL_table_highidio_iss)[reported_times,],
+  cbind(buybacks_issuers_idiosyncratic_table$IRATS$bb$lowidio,buybacks_issuers_idiosyncratic_table$IRATS$bb$highidio,buybacks_issuers_idiosyncratic_table$IRATS$iss$lowidio,buybacks_issuers_idiosyncratic_table$IRATS$iss$highidio)[reported_times,],
+  cbind(buybacks_issuers_idiosyncratic_table$CAL$bb$lowisio,buybacks_issuers_idiosyncratic_table$CAL$bb$highidio,buybacks_issuers_idiosyncratic_table$CAL$iss$lowidio,buybacks_issuers_idiosyncratic_table$CAL$iss$highidio)[reported_times,],
   columns= c("Buyback: Low Id. 4F","5F","High Id. 4F","5F","SEOs: Low Id. 4F","5F","High Id. 4F","5F"),
@@
 <<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
-rownames(Under_IdioBB)[1:2] <- c("High U-index", "Low U-index")
+rownames(buybacks_firm_characteristics_table)[1:2] <- c("High U-index", "Low U-index")
 latex_render_data_frame(
-  round(Under_IdioBB[1:8,1:4],1), 
+  round(buybacks_firm_characteristics_table[1:8,1:4],1), 
   title = "Relations across firm characteristics for Buybacks",
@@
 latex_render_data_frame(
-  round(Under_IdioBB_cor,2), 
+  round(buybacks_correlations_table,2), 
   title = "Correlations of Buybacks Characteristics",
@@
 
-rownames(EU_relations)[1] <- "Low Leverage"
-rownames(EU_relations)[2] <- "High Leverage"
-EU_relations <- EU_relations[setdiff(rownames(EU_relations), "Good purpose" ),]
+rownames(eu_firm_characteristics_table)[1] <- "Low Leverage"
+rownames(eu_firm_characteristics_table)[2] <- "High Leverage"
+eu_firm_characteristics_table <- eu_firm_characteristics_table[setdiff(rownames(eu_firm_characteristics_table), "Good purpose" ),]
 latex_render_data_frame(
-  round(EU_relations,1), 
+  round(eu_firm_characteristics_table,1), 
   title = "EU relations with Firm Characteristics",
@@
 printLatexTable2(
-  EU_IRATStable_bb[reported_times,1:(3*4)],
-  EU_IRATStable_bb[reported_times,13:(3*7)],
+  buybacks_eu_tables$IRATS[reported_times,1:(3*4)],
+  buybacks_eu_tables$IRATS[reported_times,13:(3*7)],
   columns = c("EU-index 0", "EU-index 1","EU-index 2","EU-index 3"),
@@
 printLatexTable2(
-  EU_CALtable_bb[reported_times,1:(3*4)],
-  EU_CALtable_bb[reported_times,13:(3*7)],
+  buybacks_eu_tables$CAL[reported_times,1:(3*4)],
+  buybacks_eu_tables$CAL[reported_times,13:(3*7)],
   columns = c("EU-index 0", "EU-index 1","EU-index 2","EU-index 3"),
@@
 printLatexTable2(
-  EIRATS_table_undervaluation_time_bb[reported_times,1:(3*4)],
-  EIRATS_table_undervaluation_time_bb[reported_times,13:(3*8)],
+  buyback_returns_undervaluation_tables$IRATS[reported_times,1:(3*4)],
+  buyback_returns_undervaluation_tables$IRATS[reported_times,13:(3*8)],
   columns = c("1985-1990: High-EU", "Low-EU", "1991-2000: High-EU", "Low-EU"),
@@
 printLatexTable2(
-  ECAL_table_undervaluation_time_bb[reported_times,1:(3*4)],
-  ECAL_table_undervaluation_time_bb[reported_times,13:(3*8)],
+  buyback_returns_undervaluation_tables$CAL[reported_times,1:(3*4)],
+  buyback_returns_undervaluation_tables$CAL[reported_times,13:(3*8)],
   columns = c("1985-1990: High-EU", "Low-EU", "1991-2000: High-EU", "Low-EU"),
@@
 printLatexTable2(
-  cbind(EU_IRATStableBB,Stam_IRATStableBB)[reported_times,],
-  Stam_IRATStable_EU_BB[reported_times,],
+  cbind(buyback_returns_index_table$IRATS$EU,buyback_returns_index_table$IRATS$Stam)[reported_times,],
+  buyback_returns_index_table$IRATS$Stam_EU[reported_times,],
   columns= c("Low EU","High EU","Low Mispr.","High Mispr."),
@@
 << fig.width=10, fig.height=4, out.width='\\textwidth', echo=F >>=
-tmp = table(EUindex_bb)
+tmp = table(eu_index$bb)
 tmp = structure(as.numeric(tmp), .Names = names(tmp))
@@
 
-IRATS_table_all_bb_plot = EU_IRATStable_bb
-IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")] <- -IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")]
-
-ylimit = c(min(as.vector(IRATS_table_all_bb_plot[reported_times_plots,which(colnames(IRATS_table_all_bb_plot)=="CAR")])), max(as.vector(IRATS_table_all_bb_plot[reported_times_plots,which(colnames(IRATS_table_all_bb_plot)=="CAR")])))
-
-plot(IRATS_table_all_bb_plot[reported_times_plots,3*6+1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Buybacks - EU index", lwd=2, lty = "solid")
+buyback_announcements_table$IRATS$all_plot = buybacks_eu_tables$IRATS
+buyback_announcements_table$IRATS$all_plot[rownames(buyback_announcements_table$IRATS$all_plot) %in% as.character((-6):(-1)),which(colnames(buyback_announcements_table$IRATS$all_plot)=="CAR")] <- -buyback_announcements_table$IRATS$all_plot[rownames(buyback_announcements_table$IRATS$all_plot) %in% as.character((-6):(-1)),which(colnames(buyback_announcements_table$IRATS$all_plot)=="CAR")]
+
+ylimit = c(min(as.vector(buyback_announcements_table$IRATS$all_plot[reported_times_plots,which(colnames(buyback_announcements_table$IRATS$all_plot)=="CAR")])), max(as.vector(buyback_announcements_table$IRATS$all_plot[reported_times_plots,which(colnames(buyback_announcements_table$IRATS$all_plot)=="CAR")])))
+
+plot(buyback_announcements_table$IRATS$all_plot[reported_times_plots,3*6+1], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Buybacks - EU index", lwd=2, lty = "solid")
 axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
@@
 
-lines(IRATS_table_all_bb_plot[reported_times_plots,1],lwd = 2, lty="dotted")
-lines(IRATS_table_all_bb_plot[reported_times_plots,3*1+1],lwd = 2, lty="dotted")
-tmp = IRATS_table_all_bb_plot[reported_times_plots,3*1+1]
+lines(buyback_announcements_table$IRATS$all_plot[reported_times_plots,1],lwd = 2, lty="dotted")
+lines(buyback_announcements_table$IRATS$all_plot[reported_times_plots,3*1+1],lwd = 2, lty="dotted")
+tmp = buyback_announcements_table$IRATS$all_plot[reported_times_plots,3*1+1]
 tmp[c(3*(1:floor(length(tmp)/3)),3*(1:floor(length(tmp)/3))+1)] <- NA
@@
 
-lines(IRATS_table_all_bb_plot[reported_times_plots,3*2+1],lwd = 2, lty="dashed")
-lines(IRATS_table_all_bb_plot[reported_times_plots,3*3+1],lwd = 2, lty="dashed")
-tmp = IRATS_table_all_bb_plot[reported_times_plots,3*3+1]
+lines(buyback_announcements_table$IRATS$all_plot[reported_times_plots,3*2+1],lwd = 2, lty="dashed")
+lines(buyback_announcements_table$IRATS$all_plot[reported_times_plots,3*3+1],lwd = 2, lty="dashed")
+tmp = buyback_announcements_table$IRATS$all_plot[reported_times_plots,3*3+1]
 tmp[c(3*(1:floor(length(tmp)/3)),3*(1:floor(length(tmp)/3))+1)] <- NA
@@
 
-lines(IRATS_table_all_bb_plot[reported_times_plots,3*4+1],lwd = 2, lty="dotdash")
-
-lines(IRATS_table_all_bb_plot[reported_times_plots,3*5+1],lwd = 2, lty="solid")
-tmp = IRATS_table_all_bb_plot[reported_times_plots,3*5+1]
+lines(buyback_announcements_table$IRATS$all_plot[reported_times_plots,3*4+1],lwd = 2, lty="dotdash")
+
+lines(buyback_announcements_table$IRATS$all_plot[reported_times_plots,3*5+1],lwd = 2, lty="solid")
+tmp = buyback_announcements_table$IRATS$all_plot[reported_times_plots,3*5+1]
 tmp[c(3*(1:floor(length(tmp)/3)),3*(1:floor(length(tmp)/3))+1)] <- NA

### 2017-03-23 Paper_global_parameters.R

@@ -107,3 +107,8 @@ BEAR_YEARS_text = list( #http://www.gold-eagle.com/article/history-us-bear-bull-
   dotcom = c("March 2000", "October 2002"),
   financial1 = c("October 2007", "March 2009")
 )
+
+do_Stambaugh_calculation = FALSE
+use_mispricing_factors = TRUE
+use_q_factors = FALSE
+

### 2017-03-23 create_project_data.R

@@ -44,9 +44,9 @@ if (0){ # If we want to use wrds directly
 ###################################################################################################
 ###################################################################################################
 
-source("library_files/lib_helpers.R", chdir=TRUE)
-source("library_files/latex_code.R")
-source("library_files/ff_industries_sic.R")
+source("helpers/lib_helpers.R", chdir=TRUE)
+source("helpers/latex_code.R")
+source("helpers/ff_industries_sic.R")
 source("Paper_global_parameters.R")
 
 # Some extra universe data variables we need for this project (based on the raw data)

### 2017-03-23 filter_data_for_paper.R

@@ -1,7 +1,10 @@
 #  Copyright 2015, INSEAD
 #  by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
 #  Dual licensed under the MIT or GPL Version 2 licenses.
-
+#
+#  03/2017: Functions get_data, get_names_for_removal, 
+#           remove_elements_from_list_recursively, remove_elements_based_on_type, and
+#           remove_and_filter_events added by Orestis Tsinalis
 
 ##########################################################################################
 ##########################################################################################
@@ -10,331 +13,220 @@
 ##########################################################################################
 
 ##########################################################################################
-# Remove events for which we have missing values (for the main missing values)
+# Helper functions
 ##########################################################################################
 
-to_remove = which(
-  # just in alphabetic order not to forget any    
-  is.na(BUYBACK_DATA$BEME_used) | 
-    is.na(BUYBACK_DATA$Performance_used) | 
-    is.na(BUYBACK_DATA$Size_used) | 
-    is.na(BUYBACK_DATA$DATASET$CRSP$pre_vol_Score) |
-    is.na(BUYBACK_DATA$DATASET$CRSP$IVOL_score) |
-    is.na(BUYBACK_DATA$DATASET$CRSP$Rsq_score) |
-    is.na(BUYBACK_DATA$DATASET$CRSP$Market.Cap) 
-)
-if (length(to_remove) > 0){
-  # just in alphabetic order not to forget any    
-  BUYBACK_DATA$BEME_used <- BUYBACK_DATA$BEME_used[-to_remove]
-  BUYBACK_DATA$Performance_used <- BUYBACK_DATA$Performance_used[-to_remove]
-  BUYBACK_DATA$Size_used <- BUYBACK_DATA$Size_used[-to_remove]
-  BUYBACK_DATA$Valuation_Index <- BUYBACK_DATA$Valuation_Index[-to_remove]
-  
-  BUYBACK_DATA$DATASET$returns_by_event_monthly <- BUYBACK_DATA$DATASET$returns_by_event_monthly[,-to_remove]
-  BUYBACK_DATA$DATASET$SDC <- BUYBACK_DATA$DATASET$SDC[-to_remove,]
[…]

### 2017-03-23 helpers/curl_helpers.R

@@ -1,114 +1,0 @@
-library(RCurl)
-
-curlProgress <- function(down, up, pcur, width) {
-  total <- as.numeric(down[1]) # Total size as passed from curlPerform
-  cur <- as.numeric(down[2])   # Current size as passed from curlPerform
-  x <- cur/total
-  px <- round(100 * x)
-  if(!is.nan(x) && px!=pcur){
-    x <- round(width * x)
-    sc <- rev(which(total> c(1024^0, 1024^1, 1024^2, 1024^3)))[1] - 1
-    lb <- c('B', 'KB', 'MB', 'GB')[sc+1]
-    cat(paste(c(
-      "\r  |", rep.int(".", x), rep.int(" ", width - x),
-      sprintf("| %g%s of %g%s %3d%%", round(cur/1024^sc, 2), lb, round(total/1024^sc, 2), lb, px)),
-      collapse = ""))
-    flush.console()
-    return(px)
-  }
-  return(pcur)
-}
-
-curlDownload <- function(url, fname, verbose=FALSE) {
-  f <- CFILE(fname, mode="wb")
-  width <- getOption("width") - 25
-  pcur <- 0
-  result <- curlPerform(url=url, writedata=f@ref, noprogress=FALSE,
-                        progressfunction=function(down,up) pcur<<-curlProgress(down, up, pcur, width),
-                        followlocation=TRUE)
-  close(f)
-  if (verbose) cat('\n   Download ', names(result), ' (Result: ', result, ')\n', sep="")
-  invisible(result)
-}
-
-curlLoad <- function(url, envir=parent.frame(), verbose=FALSE) {
-  tmpFile <- tempfile()
-  curlDownload(url, tmpFile)
-  result <- load(tmpFile, envir, verbose)
-  file.remove(tmpFile)
-  invisible(result)
-}
-
-getURLHeaders <- function(url) {
-  h <- basicHeaderGatherer()
-  result <- curlPerform(url=url, customrequest='HEAD',
-                        nobody=1L, headerfunction=h$update, followlocation=T)
-  h$value()
-}
-
-# Dropbox specific
-curlCachedLoad.Dropbox <- function(url, envir=parent.frame(), verbose=FALSE, folder="cache") {
-  headers <- getURLHeaders(url)
-  etag <- headers["etag"]
-  filename <- sub("\"", "", sub("filename=\"", "", unlist(strsplit(headers["content-disposition"], "; "))[2]))
[…]

### 2017-03-23 helpers/ff_helpers.R

@@ -1,124 +1,0 @@
-#  Copyright 2016, INSEAD
-#  by V. Kapartzianis 
-#  Dual licensed under the MIT or GPL Version 2 licenses.
-
-
-# Fama/French
-# ===========
-# See http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_library.html
-
-library(xts)
-
-ffRetrieveData <- function(zip.file, section=NULL, field=NULL, start=as.Date("1980-01-01"), skip=NULL) {
-  # Retrieves Fama/French timeseries.
-  #
-  # Args:
-  #   zip.file: The source file to process, as provided by Ken French. You can
-  #     omit the path and the extension.
-  #   section (optional): The section to retrieve from the file. Sources, as
-  #     provided by Ken French, can contain different sections, for example the
-  #     monthly factors CSV also contains an "Annual Factors: January-December "
-  #     section. NOTE: you have to match the section name exactly, and specify
-  #     NULL to retrieve the first/only section (which is often un-named).
-  #   field (optional): A vector of columns to retrieve. This could be, for
-  #     example `c("Banks", "Fin")`.
-  #   start (optional): The first date in the timeseries to retrieve. Default is
-  #     `as.Date("1980-01-01")`.
-  #   skip (optional): The number of lines to skip before processing the file.
-  #     NOTE: the function can only skip up to 5 lines automatically, if this
-  #     parameter is left to its default value, `NULL`.
-  #
-  # Returns:
-  #   The specified Fama/French timeseries, as an `xts` matrix. NOTE: dimensions
-  #   are never dropped in the returned results, the function won't return an
-  #   `xts` vector even when a single field is specified or present in the file.
-  #
-  # Examples:
-  #   ffRetrieveData("http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/ftp/F-F_Research_Data_5_Factors_2x3_CSV.zip")
-  #   ffRetrieveData("F-F_Research_Data_5_Factors_2x3_CSV", section=" Annual Factors: January-December ")
-  #   ffRetrieveData("F-F_Research_Data_5_Factors_2x3_CSV", field="RF")
-  #   ffRetrieveData("49_Industry_Portfolios_CSV", field=c("Banks", "Fin"), skip=11)
-  
[…]

### 2017-03-23 helpers/ff_industries_sic.R

@@ -1,51 +1,0 @@
-FF_industries = list(
- Agriculture = c(0100:0199, 0200:0299, 0700:0799, 0910:0919, 2048:2048),
- Food_Production = c(2000:2009, 2010:2019, 2020:2029, 2030:2039, 2040:2046, 2050:2059, 2060:2063, 2070:2079, 2090:2092, 2095:2095, 2098:2099),
- Candy_and_Soda = c(2064:2068, 2086:2086, 2087:2087, 2096:2096, 2097:2097),
- Beer_and_Liquor = c(2080:2080, 2082:2082, 2083:2083, 2084:2084, 2085:2085),
- Tobacco = c(2100:2199),
- Recreation = c(0920:0999, 3650:3651, 3652:3652, 3732:3732, 3930:3931, 3940:3949),
- Entertainment = c(7800:7829, 7830:7833, 7840:7841, 7900:7900, 7910:7911, 7920:7929, 7930:7933, 7940:7949, 7980:7980, 7990:7999),
- Print_Publications = c(2700:2709, 2710:2719, 2720:2729, 2730:2739, 2740:2749, 2770:2771, 2780:2789, 2790:2799),
- Consumer_Goods = c(2047:2047, 2391:2392, 2510:2519, 2590:2599, 2840:2843, 2844:2844, 3160:3161, 3170:3171, 3172:3172, 3190:3199, 3229:3229, 3260:3260, 3262:3263, 3269:3269, 3230:3231, 3630:3639, 3750:3751, 3800:3800, 3860:3861, 3870:3873, 3910:3911, 3914:3914, 3915:3915, 3960:3962, 3991:3991, 3995:3995),
- Apparel = c(2300:2390, 3020:3021, 3100:3111, 3130:3131, 3140:3149, 3150:3151, 3963:3965),
- Healthcare = c(8000:8099),
- Medical_Equipment = c(3693:3693, 3840:3849, 3850:3851),
- Pharmaceutical_Products = c(2830:2830, 2831:2831, 2833:2833, 2834:2834, 2835:2835, 2836:2836),
- Chemicals = c(2800:2809, 2810:2819, 2820:2829, 2850:2859, 2860:2869, 2870:2879, 2890:2899),
- Plastic_Products = c(3031:3031, 3041:3041, 3050:3053, 3060:3069, 3070:3079, 3080:3089, 3090:3099),
[…]

### 2017-03-23 helpers/latex_code.R

@@ -1,704 +1,0 @@
-#  Copyright 2013, Satrapade
-#  by T. Evgeniou, V. Kapartzianis, N. Nassuphis and D. Spinellis
-#  Dual licensed under the MIT or GPL Version 2 licenses.
-#  11/2015 functions printLatexTable and printLatexTable2 added by T. Evgeniou and E. Junqu?? de Fortuny
-
-
-######################################################################################
-## Latex commands
-######################################################################################
-
-tostars <- function(x) ifelse(abs(x)<=0.01,"**",ifelse(abs(x)<=0.05,"*",ifelse(abs(x)<=0.1,"$^+$","")))
-
-# THIS NEEDS FIXING...
-latex_print_number <- function(the_value, digits=2,digitssmall = 6, NAvalue = "-"){ 
-  if (!is.numeric(the_value))
-    res = the_value
-  else {
-    if (is.na(the_value)){
-      res = NAvalue
-    } else {
-      res = round(the_value,digits)
-      if (round(the_value,digits) == 0 & the_value !=0)
-        res = ifelse(abs(the_value) < 10^(-digitssmall), 0, format(the_value,scientific=TRUE,digits=digits,big.mark=","))
-    }
-  }
-  res  
-}
-
-#latex_print_number <- function(the_value, digits) ifelse(round(the_value) == the_value, the_value,formatC(the_value,format="f",dig=digits))
-
-
-# CAN EDIT TO PRINT OUT WHATEVER LATEX WE NEED  
-latex_render_data_frame<-function(x,y=NULL, title="",caption="",label="",columns=NULL,bigtitleontop = F,show_rownames=FALSE,red_text="",green_text="",blue_text="",scale=1,digits=2,digitssmall = 6,lastSpecial=F,dorotate=F, tostars_used = NULL, NAvalue = "-",hlinerows = NULL) {
-  #Helper functions
-  p <- function(...){paste(...)}
-  pn <- function(...){paste(...,"\n")} #print newline
-  pc <- function(...){paste(...,"&")}  #print column
-  
-  if(dorotate){
-    width = "\\linewidth"
-  } else {
-    width = "\\textwidth"
-  }  
-  #Start the table definition
-  l <- ""  
[…]

### 2017-03-23 helpers/lib_helpers.R

@@ -1,952 +1,0 @@
-#  Copyright 2013, Satrapade
-#  by T. Evgeniou, V. Kapartzianis, N. Nassuphis and D. Spinellis
-#  Dual licensed under the MIT or GPL Version 2 licenses.
-#  11/2015 functions car_table and calendar_table added by T. Evgeniou and E. Junqu?? de Fortuny
-
-# Required R libraries (need to be installed - it can take a few minutes the first time you run the project)
-
-if (ifelse(!exists("run_shiny_tool"), T, run_shiny_tool == 0)) { # When deploying a shiny app on the shiny server we should not load all R libraries
-  # installs all necessary libraries from CRAN
-  get_libraries <- function(filenames_list) { 
-    lapply(filenames_list,function(thelibrary){    
-      if (do.call(require,list(thelibrary)) == FALSE) 
-        do.call(install.packages,list(thelibrary)) 
-      do.call(library,list(thelibrary))
-    })
-  }
-  libraries_used=c("stringr","gtools","timeDate","data.table","psych","RcppArmadillo","Hmisc","DescTools")
-  
-  get_libraries(libraries_used)
-  Rcpp::sourceCpp('lib_helpers.cpp', embeddedR=FALSE)
-} else {
-  lib_helpers_path <- try(suppressWarnings(dirname(sys.frame(1)$ofile)), silent=TRUE)
-  if (class(lib_helpers_path) == "try-error") lib_helpers_path <- "."
-  if (file.exists("lib_helpers.cpp")) lib_helpers_path <- "."
-  Rcpp::sourceCpp(file.path(lib_helpers_path,'lib_helpers.cpp'), embeddedR=FALSE)
-}
-
-options(stringsAsFactors=FALSE)
-
-
-non_na_mean <- function(x) { mean(x[!is.na(x)]) }
-
-remove_initialization_time <- function(x,min_date=NULL) { # Note: Added also min_date as an argument!! THis way we remove data from any given date!
-  if (!is.null(min_date)){
-    res = x[as.Date(names(x)) >= as.Date(min_date)]
-  } else {
-    if (x[1] != 0){
-      res = x
-    } else {
-      if (sum(x!=0) != 0){
-        tmp <- names(x)
-        ending <- -head(which(diff(x)!=0),1)
-        res = tail(x, ending)
-        names(res) <- tail(tmp, ending)
-      }
-    }
-  }
-  res
-}
-
[…]

### 2017-03-23 helpers/wrds_config.R

@@ -1,33 +1,0 @@
-
-# 1. Encode your WRDS Cloud password
-# ==================================
-# For detailed instructions, see 
-# https://wrds-web.wharton.upenn.edu/wrds/support/Accessing%20and%20Manipulating%20the%20Data/_010Encoding%20your%20WRDS%20Password.cfm
-#
-# 2. Setup SAS JDBC drivers
-# =========================
-# Download link:
-# https://wrds-web.wharton.upenn.edu/wrds/support/SAS-JDBC-Drivers.zip.cfm
-# 
-# Once you have downloaded and unzipped the drivers (you will notice that there
-# are two drivers), you'll need to place them somewhere permanent on your local
-# computer, as RStudio will need to use these drivers each time you connect. 
-# WRDS recommends storing them in a dedicated directory in your documents
-# folder, like so:
-# 
-# On a Mac:
-# /Users/my_user/Documents/WRDS_Drivers/sas.core.jar
-# /Users/my_user/Documents/WRDS_Drivers/sas.intrnet.javatools.jar
-# 
-# On a PC:
-# C:\Users\my_user\Documents\WRDS_Drivers\sas.core.jar
-# C:\Users\my_user\Documents\WRDS_Drivers\sas.intrnet.javatools.jar
-#
-# 3. Configure your WRDS Cloud access
-# ===================================
-# Uncomment the following template and replace your details in it. Do NOT commit
-# the file with your details in it.
-#
-# wrds_user <- "my_username"
-# wrds_pass <- "{SAS002}DBCC5712369DE1C65B19864C1564FB850F398DCF"
-# wrds_path <- "C:\\Users\\my_user\\Documents\\WRDS_Drivers\\"

### 2017-03-23 helpers/wrds_helpers.R

@@ -1,306 +1,0 @@
-#  Copyright 2016, INSEAD
-#  by V. Kapartzianis 
-#  Dual licensed under the MIT or GPL Version 2 licenses.
-
-# 1. Install Java
-# ===============
-# Choose 32-bit or 64-bit depending on whether you're using 32-bit or 64-bit R/RStudio
-# http://www.java.com/en/download/manual.jsp
-# 
-# If that doesn’t work, you could also manually set the directory of your Java location by setting it before loading the library:
-# 
-# Sys.setenv(JAVA_HOME='C:\\Program Files\\Java\\jre7') # for 64-bit version
-# Sys.setenv(JAVA_HOME='C:\\Program Files (x86)\\Java\\jre7') # for 32-bit version
-#
-# 2. Install R packages rJava and RJDBC
-# =====================================
-# You can do that in Rstudio by calling install.packages()
-#
-# install.packages(c("rJava", "RJDBC"))
-#
-# 3. Configure your WRDS Cloud access
-# ===================================
-# For detailed instructions, see wrds_config.R
-
-
-library(rJava)
-.jinit(parameters="-Xmx8g")
-library(RJDBC)
-source("wrds_config.R")
-library(xts)
-library(lubridate)
-
-## **** SEE ALSO 
-## https://wrds-web.wharton.upenn.edu/wrds/support/Accessing%20and%20Manipulating%20the%20Data/_007R%20Programming/_001Using%20R%20with%20WRDS.cfm
-## and ~/.Rprofile (in home directory of local computer)
-wrdsConnect <- function(user=wrds_user, pass=wrds_pass) {
-  sas_core <- paste0(wrds_path, "sas.core.jar")
-  sas_javatools <- paste0(wrds_path, "sas.intrnet.javatools.jar")
-  .jinit()
-  .jaddClassPath(c(sas_core, sas_javatools))
-  driver <- JDBC("com.sas.net.sharenet.ShareNetDriver", sas_javatools, identifier.quote="`")
-  wrds_handle <- dbConnect(driver, "jdbc:sharenet://wrds-cloud.wharton.upenn.edu:8551/", user, pass)
-  return(wrds_handle)
-}
-
-wrdsDisconnect <- function(wrds_handle) {
[…]

### 2017-03-23 library_files/lib_helpers.R

@@ -1,1476 +1,0 @@
-#  Copyright 2013, Satrapade
-#  by T. Evgeniou, V. Kapartzianis, N. Nassuphis and D. Spinellis
-#  Dual licensed under the MIT or GPL Version 2 licenses.
-#  11/2015 functions car_table and calendar_table added by T. Evgeniou and E. Junqu?? de Fortuny
-
-# Required R libraries (need to be installed - it can take a few minutes the first time you run the project)
-
-if (ifelse(!exists("run_shiny_tool"), T, run_shiny_tool == 0)) { # When deploying a shiny app on the shiny server we should not load all R libraries
-  # installs all necessary libraries from CRAN
-  get_libraries <- function(filenames_list) { 
-    lapply(filenames_list,function(thelibrary){    
-      if (do.call(require,list(thelibrary)) == FALSE) 
-        do.call(install.packages,list(thelibrary)) 
-      do.call(library,list(thelibrary))
-    })
-  }
-  libraries_used=c("stringr","gtools","foreign","reshape2","digest","timeDate","devtools","knitr","graphics",
-                   "grDevices","xtable","sqldf","stargazer","data.table","shiny","htmlwidgets",
-                   "Hmisc","vegan","fpc","GPArotation",
-                   #"FactoMineR",
-                   "cluster","dygraphs",
-                   "psych","stringr","googleVis", "png","ggplot2","googleVis", "gridExtra","RcppArmadillo","xts","DescTools")
-  
-  get_libraries(libraries_used)
-  Rcpp::sourceCpp('lib_helpers.cpp', embeddedR=FALSE)
-} else {
-  lib_helpers_path <- try(suppressWarnings(dirname(sys.frame(1)$ofile)), silent=TRUE)
-  if (class(lib_helpers_path) == "try-error") lib_helpers_path <- "."
-  if (file.exists("lib_helpers.cpp")) lib_helpers_path <- "."
-  Rcpp::sourceCpp(file.path(lib_helpers_path,'lib_helpers.cpp'), embeddedR=FALSE)
-}
-
-options(stringsAsFactors=FALSE)
-
-
-# Summary table
-my_summary <- function(x){
-  nas = sum(is.na(x))
-  x=x[!is.na(x)]
[…]

### 2017-03-23 library_files/lib_helpers.cpp

@@ -1,88 +1,0 @@
-//  Copyright 2016, INSEAD
-//  by V. Kapartzianis 
-//  Dual licensed under the MIT or GPL Version 2 licenses.
-
-#include <Rcpp.h>
-using namespace Rcpp;
-
-// [[Rcpp::plugins(openmp)]]
-
-// [[Rcpp::export]]
-NumericVector row_weights(NumericMatrix x, NumericVector weight) {
-  int nX = x.ncol();
-  int nY = x.nrow();
-  NumericVector v = no_init(nY);
-  
-  //#pragma omp parallel for schedule(static)
-  for (int i=0; i < nY; i++) {
-    NumericMatrix::Row row = x(i, _);
-
-    double w = 0;
-    for (int j=0; j < nX; j++) {
-      if(row[j]!=0 && !R_IsNA(row[j])) {
-        w += weight[j];
-      }
-    }
-
-    double o = 0;
-    if (w!=0) {
-      for(int j=0; j < nX; j++) {
-        if(row[j]!=0 && !R_IsNA(row[j])) {
-          o += row[j]*weight[j] / w;
-        }
-      }
-    }
-    
-    v[i] = o;
-  }
-  
-  v.attr("names") = rownames(x);
-  return v;
-}
-
-
-// [[Rcpp::export]]
-NumericMatrix calendar_table_helper1(NumericMatrix x, NumericVector Row_Date_number, NumericVector Event_Date_number, NumericVector hitnow) {
-//NOTE: it would be much faster to update the matrix without cloning it, but
-//that could lead to unexpected bugs, as R wouldn't know the matrix was updated.
-  NumericMatrix ret = Rcpp::clone(x);
-  int nX = ret.ncol();
-  int nY = ret.nrow();
-  
-  //#pragma omp parallel for schedule(static)
-  for (int col=0; col < nX; col++) {
-    for (int row=0; row < nY; row++) {
-      if (Row_Date_number[row] <= Event_Date_number[col] || Row_Date_number[row] > hitnow[col]) {
-        ret(row, col) = 0;
-      }
-    }
-  }
-  return ret;
-}
-// [[Rcpp::export]]
-NumericMatrix calendar_table_helper2(NumericMatrix x, NumericVector Row_Date_number, NumericVector Event_Date_number, NumericVector hitnow) {
-//NOTE: it would be much faster to update the matrix without cloning it, but
[…]

### 2017-03-23 process_data_for_paper.R

@@ -3,159 +3,263 @@
 #  Dual licensed under the MIT or GPL Version 2 licenses.
 
 # NOTE: These data files need to be available:
-# load("../FinanceData/created_projects_datasets/BUYBACKS.Rdata") # GENERATED BY create_bbissuers_data.R
-# "../FinanceData/rawdata_stambaugh_mispricing_index/Stambaugh_Mispricing_Score.csv" # from http://www.saif.sjtu.edu.cn/facultylist/yyuan/Misp_Score.csv
+
+# 1) GENERATED BY create_bbissuers_data.R:
+# "../FinanceData/created_projects_datasets/BUYBACKS.Rdata"
+
+# 2) from http://www.saif.sjtu.edu.cn/facultylist/yyuan/Misp_Score.csv 
+# "../FinanceData/rawdata_stambaugh_mispricing_index/Stambaugh_Mispricing_Score.csv" 
 # which (see below) generates "../FinanceData/created_projects_datasets/StambaughBUYBACKS.Rdata"
 # ""../FinanceData/created_projects_datasets/Buybacks.Institutional.number.Rdata" created below
 
-####################################################################################
+##########################################################################################
 # These are all the tables used in the .Rnw for the paper
-####################################################################################
+##########################################################################################
 
 rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
 
-source("library_files/lib_helpers.R", chdir=TRUE)
-source("library_files/latex_code.R")
-source("library_files/ff_industries_sic.R")
+source("helpers/lib_helpers.R", chdir=TRUE)
+source("helpers/latex_code.R")
+source("helpers/ff_industries_sic.R")
 source("Paper_global_parameters.R")
 
-initial_vars = ls(all = TRUE) # takes time to save and load, so we save only what is needed at the end. 
+# takes time to save and load, so we save only what is needed at the end.
+initial_vars = ls(all = TRUE) 
 
-############################################################################################################
+##########################################################################################
+# FILE LOCATIONS
[…]
